### 2022-11-01 analysis_vasseur_fox.Rmd
Add analysis of Vasseur and Fox (2007)

---
title: "Community biomass and species richness temporal trends reveal contrasting assembly and disassembly processes in natural food-webs"
author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine
date: \today
output:
  bookdown::pdf_document2:
    fig_caption: true 
    keep_tex: true
    toc: true
    fontsize: 12pt
    geometry: margin=2cm
    number_sections: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

```{r, results = FALSE}
library(tidyverse)
library(magrittr)
library(cowplot)
library(here)
require(rgl)
options(rgl.printRglwidget = TRUE)

mytheme <- theme_cowplot() +
background_grid()

theme_set(mytheme)
options(knitr.table.format = "latex")
```

```{r}
data <- read_csv(here("res", "vasseur_fox_res.csv"))
colnames(data)[1:2] <- c("rho", "sigma") 
```
```{r}
avg  <- data %>%
  group_by(sigma, rho) %>%
  summarise(across(everything(), mean))
```

```{r}
surface3d(avg$rho, avg$stab_pred, avg$sigma)
map(c("rho", "stab_pred", ))
```

```{r}
cons_sync <- avg %>%
  ggplot(aes(rho, sigma, z = sync_cons)) +
  geom_contour_filled() +
  labs(x = "Environmental correlation", y = "Fluctuation strength") +
  labs(fill = "Consumer synchrony")

pred_stab <- ggplot(avg, aes(rho, sigma, z = stab_pred)) +
  geom_contour_filled() +
  labs(x = "Environmental correlation", y = "Fluctuation strength") +
  labs(fill = "Predator stability")

cons1_stab <- avg %>%
  ggplot(aes(rho, sigma, z = stab_cons1)) +
  geom_contour_filled() +
  labs(x = "Environmental correlation", y = "Fluctuation strength") +
  labs(fill = "Consumer 1 stability")

cons2_stab <- avg %>%
  ggplot(aes(rho, sigma, z = stab_cons2)) +
  geom_contour_filled() +
  labs(x = "Environmental correlation", y = "Fluctuation strength") +
  labs(fill = "Consumer 2 stability")
```

```{r}
pp <- plot_grid(
  cons_sync, pred_stab, cons1_stab, cons2_stab,
  labels = "auto")
save_plot(
  filename = here("res", "vasseurfox2007fig2.pdf"),
  pp, ncol = 2, nrow = 2)
```

### 2022-11-01 draft.jl

@@ -7,82 +7,64 @@ using Plots
 using Debugger
 include("src/minmax.jl")
 
+Iₖ = ωₖ * x * y / B₀
 
-# Try the solver option with 
-function connectance(mat)
-    sum(mat) / size(mat,1)^2
+######
+# Define your own ModelParameters with an additional mortality term 
+#####
+
+# Define the composite type CritDeath
+mutable struct CritDeath 
+    d::Float64
 end
 
-foodweb = FoodWeb(nichemodel, 10,C = .14)
-while connectance(foodweb.A) != .14 
-    global foodweb = FoodWeb(nichemodel, 10,C = .14)
-end
-# Generally, reltol is the relative accuracy while abstol is the accuracy when u
-# is near zero. These tolerances are local tolerances and thus are not global
-# guarantees. However, a good rule of thumb is that the total solution
-# accuracy is 1-2 digits less than the relative tolerances. Thus for the
-# defaults abstol=1e-6 and reltol=1e-3, you can expect a global accuracy
-# of about 1-2 digits.
-q0 = 0.0:.025:.5
-params = ModelParameters(foodweb, functional_response = BioenergeticResponse(foodweb, h = 0.025 + 1))
-sol = simulate(
-               params,
-               rand(size(foodweb.A, 1));# repeat([.1], size(foodweb.A, 1)),
-               extinction_threshold = 1e-10, 
-               callback = CallbackSet(
-                                      BEFWM2.PositiveDomain(),
-                                      TerminateSteadyState(1e-6, 1e-4),
-                                      BEFWM2.ExtinguishSpecies(1e-10, false),
-                                     ),
-               reltol=1e-8, abstol=1e-8
-              )
-using DifferentialEquations
-using OrdinaryDiffEq
-
-
-function connectance(mat)
-    sum(mat) / size(mat,1)^2
+# Add a field crit_death to ModelParameters by defining a new composite type of subtype Params
+mutable struct CustomModelParameters <: Params
+    network::EcologicalNetwork
+    biorates::BioRates
+    environment::Environment
+    functional_response::FunctionalResponse
+    crit_death::CritDeath
 end
 
-Random.seed!(1234)
-foodweb = FoodWeb(nichemodel, 10,C = .14)
-# I would like a fw with c = 0.14 plz
-while connectance(foodweb.A) != .14 
-    global foodweb = FoodWeb(nichemodel, 10,C = .14)
+
+# Define the function of my custom ModelParameters
+function CustomModelParameters(
[…]

### 2022-11-01 report/project_definition.Rmd
Start a project rational document

---
title: "Post-doc project: A complex food-web theory of stability against perturbation"
author: "Alain Danet"
date: \today
output:
  bookdown::pdf_document2
bibliography: references.bib 
---

# Rationale

## Perturbation ecology

- Multiple perturbation affect simultaneously mortality rates of species
- We can assume that those multiple stressors can be summed into environmental
  stochasticity

## Correlation among pertubations

- Depending on the nature of the stressors and niche of species, we can expect
  different scenarios
- Perturbations such as fishing will affect primarily some species (e.g.
  top-trophic level)
- Perturbations in habitat quality will affect species more globally
  (however some might benefit).
- Perturbation in temperature will affect differently species according to their thermal niche

All the above scenarios can result in quite complex combinations of situation
that can be tricky to generalize. Another way to tackle this situation is to
test more general theories of ecological communities.

I see four different scenarios of perturbation correlations among species that I
name as the following homogeneous, null, guilds, hidden niches. The homogeneous
scenario considers that all species are affected in the same way, which would
correspond to a general perturbation such as a general improvement/depletion of
habitat quality. The null scenario considers that all species respond randomly
to stress, i.e. they do not share perturbation, i.e. their perturbations are
uncorrelated. The guilds scenario assumes that intra-guild perturbations are
positively correlated and that interguild perturbations are not correlated, it
is a scenario that assumes that species sharing the same trophic level share the
same niche, i.e. there is no intraguild response diversity. The hidden niche
scenario comes the theory of the same name[@scheffer_self-organized_2006;
@barabas_emergent_2013; @martinez-blancas_species_nodate]. It assumes that
cluster of species having similar traits (here food-web trophic position) would
have hidden niche dimensions that stabilize their coexistence, such as species
in the same guild will have response diversity (portfolio effect),
anti-correlated perturbations.

While all the above scenario can seem abstract at a first glance, it is possible
to draw realistic situations where they can apply.

The homogeneous scenario can apply in situations where stressors select for
homogeneous response to stressors as for example, as it might be the case in
altered environments where we can end up with the same functions (i.e. the same
food-web) but where the diversity of other niche dimensions have been shrunken
(lost of diversity hypothesis). The guild scenario supposes a full niche
conservatism where species on the same feeding guild are likely to share the
same evolutionary history and such their respond in the same way to
environmental perturbation. The hidden niche is the reverse of the former,
intraguild species are anti-correlated, such as there is maximal response
diversity (insurance hypothesis), which is the mechanism by which biodiversity
is thought to maintain long-term stability of ecosystem functions.

While response diversity has been well studied in small food-web modules and
competitive communities, it has been overlooked in more complex food-webs. The
complex relationships among species across food-web might dampens (compensate),
propagate or just scale with food-chain and small food-web modules.

## Stability in food-webs

The question at 1bn pound is "what is driving stability?", i.e. the propagation
of perturbations across food-webs. Early studies focused on the effect of
removing one species either by looking at the topology [e.g.,
@dunne_network_2002] or dynamic [@stouffer_compartmentalization_2011]. In that
sense, it would be interesting to see if environmental stochasticity predicts the same
pattern that species extinction (i.e. pertubation for one species only).

The big other ingredient of food-web stability is the strength of species
interactions. The tremendous early work of McCann and other authors about the
distribution of interaction strength is really interesting, showing that
coupling weak interactions to strong one stabilize food-web dynamics.
Interestingly, I see two schools on the definition of interaction strengths in
the Bioenergetic model. McCann defines it by modulating consumer preference
($\omega$) such as $I_{ki} = \omega_{ik}* x_i * y_i / B_{0i}$ while
@brose_allometric_2006 modules interaction strength by modulating predator/prey
mass ratios (Z) such as Z increases the metabolism of predators decreases
relative to prey (i.e. $x_i$ and $y_i$). Thus increasing Z decreases $I_{ki}$.
The main difference between Brose and McCann approaches is that the Brose
approach of modulating interactions also modulates metabolic losses ($x_iy_iB_i$).
Then the approach of McCann has the advantage to only change feeding rates but
it is rather phenomenological modelling while Brose approach is more mechanistic
(fully metabolic) but it changes two things at the same time.

### Stability in small modules

- @mccann_diversitystability_2000, @mccann_weak_1998,
  @vasseur_environmental_2007, @ripa_food_2003

### Stability in food-chains

- @barbier_pyramids_2019, @shanafelt_stability_2018

### Stability in complex food-web

- @thebault_stability_2010, @brose_allometric_2006

# Research questions

- How does response diversity drive food-web stability?
- How does response diversity affect coupling between predator and preys?
- How does response diversity effect on stability is modulated by interaction strength
  distribution?

# Methods

## Simulation framework:

- Start analysis with really robust food-webs (high Z and type III functional
  response) to avoid species extinction
- Really general propagation: one species pertubated at the time (are there
  differences with extinction pattern ?)
- Modulating interaction strength distribution: generate random asymetric
  consumer preference ($\omega_ij$) but with constraints on predator
  ($\sum\omega_i = 1$) and preys (prey should be involved in one strong
  interaction at the time may be).

# References {-}

### 2022-11-01 starting.jl

@@ -11,4 +11,11 @@ touch("draft.jl")
 Pkg.add("Plots")
 
 using Pkg
-Pkg.dev("~/Documents/post-these/sheffield/BEFWM2_fork/")
+Pkg.dev("../BEFWM2_fork/")
+
+mkdir("res")
+
+mkdir("report")
+touch("report/project_definition.Rmd")
+
+symlink("/home/alain/Documents/post-these/references.bib", "report/references.bib")

### 2022-11-15 use_case/analysis_vasseur_fox.Rmd
Finish with McCann / Brose

--- 2022-11-01 analysis_vasseur_fox.Rmd
@@
 ---
-title: "Community biomass and species richness temporal trends reveal contrasting assembly and disassembly processes in natural food-webs"
-author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine
+title: "Vasseur \& Fox (2007) replication"
+author: Alain Danet
 date: \today

### 2022-11-15 use_case/int_mccann_brose/int_calculus.Rmd
Finish with McCann / Brose

---
title: "Interaction strength: driven by metabolism or behavior? McCann vs Brose" 
author: Alain Danet
date: \today
output:
  bookdown::html_document2:
    fig_caption: true 
    toc: true
    fontsize: 12pt
    number_sections: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

```{r}
library(tidyverse)
library(magrittr)
library(plotly)
library(kableExtra)
library(cowplot)
```

```{r}
theme_set(theme_half_open() + background_grid())
```

```{r}
# From McCann diamond
x <- c(0, .40, .20, .08)
y <- c(0, 2.009, 3.50, 5.0)
b0 <- c(0.16129, .90, .5)
names(x) <- names(y) <- c("R1", "C1", "C2", "P")
names(b0) <- c("R01", "R02", "C0")
```

# Context

Brose's and McCann's body of work represent two different ways of seeing foodweb
assembly and dynamics. McCann considers that foodwebs are made of strong
interactions that are stabilized by weak interactions. A consequence of this is
that the asymmetry in consumer preference for resources plays a great role in
McCann's work ($\omega$), where the predator has a preference for the most
competitive prey (hierarchy mostly defined by the asymmetry in half saturation
constant $B_0$). We can see it as a strong role given to consumer preference as
a predominant role of foraging behavior in McCann work. This approach leads to
the construction of small and finely tuned foodweb module, up to four species
(one producer, two consumers and one predator).

In contrast, Brose's body of work does not make assumption on foraging behavior
and so on asymmetry of consumer preference. Furthermore, it does not assume
competitive difference between consumers for resources (same half-saturation
constants). In Brose's work, the interaction strength are only determined by the
trophic level and a constant body size ratio ($Z$ parameter) between pairs of
adjacent trophic levels. At the end, interaction strengths are solely determined
by metabolism, through body mass, which determines in turn maximum ingestion and
metabolism rates. In contrast with McCann approach, it enables to build
species-rich foodweb without having to finely tune each parameter, as the
metabolic parameters and interactions are (almost) solely determined by the body
mass ratio ($Z$) and the trophic level (T). This convenient parametrization of
complex food-webs has the cons to consider that there is no behavior or
competitive hierarchy in the food-web, all is solely determined by metabolism.

In a nutshell, McCann proposes that the balance of strong and weak interactions
driven by consumer preference and competitive hierarchy drive the stability of
foodweb while Brose proposes that stability emerge from weak interactions driven
by the slow metabolism of predators compared to the preys (high Z).

In this document, I try to derive the relationship among maximum interaction
strength, body mass ratio and consumer preferences to map the range of
interactions strength explored by Brose. I then map the McCann interaction
strength onto it by computing the body mass ratio (Z) between consumers and
predator. I finally try to estimate what would be the body mass ratio between
consumer and predator to mimic the interaction strength of McCann without
predator preference for any of the two consumers (i.e. $\omega = .5$).

# Maximum interaction strength from McCann

```{r}
max_int <- function(
  omega = .5,
  ax = 0.88,
  y = 5,
  x = NULL,
  ay = NULL,
  Z = 1,
  T = 2,
  b0 = 0.50) {

  if (is.null(ay) & !is.null(ax)) {
    ay <- ax * y
  }

  if (!is.null(Z)) {
    numerator <- omega * ax * ay * Z ^ ((T - 1) * (-0.5))
  } else {
    numerator <- omega * x * y
  }
  numerator / b0
}
```

From McCann, maximum interaction strength ($I_{ki}$) is equal to:

$$
I_{ki} = \dfrac{\omega_{ki} x_i y_i}{B_{0i}}
$$

```{r}
Imccann02_met <- max_int(omega = .02, y = y["P"], x = x["P"], ax = NULL, Z =
  NULL, T = 3, b0 = b0["C0"])
Imccann98_met <- max_int(omega = .98, ax = NULL, y = y["P"], x = x["P"], ay =
  NULL, Z = NULL, T = 3, b0 = b0["C0"])

ImccannC1R_met <- max_int(omega = 1, ax = NULL, y = y["C1"], x = x["C1"], ay =
  NULL, Z = NULL, T = 2, b0 = b0["R01"])

ImccannC2R_met <- max_int(omega = 1, ax = NULL, y = y["C2"], x = x["C2"], ay =
  NULL, Z = NULL, T = 2, b0 = b0["R02"])
```

```{r}
interaction_correspondance <- tibble(
  int = c("P-C1", "P-C2", "C1-R", "C2-R"),
  omega = c(.98, .02, 1, 1),
  I = map_dbl(c(Imccann98_met, Imccann02_met, ImccannC1R_met, ImccannC2R_met),
    ~round(.x, 2))
)
interaction_correspondance %>%
  kbl(
    caption = "Interaction strength from McCann 1998",
    label = "int"
  ) %>%
kable_styling()
```

From the first equation, we can compute $I$ of McCann from the metabolic rates,
giving interaction strengths presented in Table \@ref(tab:int).

From The formulation of $I$, we can compute $I(Z)$ if we replace $x_i$ and $y_i$ by $Z$.

Knowing that $x_i = a_xM_i^{-0.25}$, $y_i = a_yM_i^{-0.25}$ and that $M =
Z^{T-1}$, we can derive that: $x_i = a_x(Z^{T-1})^{-0.25}$

\begin{align}
I_{ki} &= \dfrac{\omega_{ki} a_x(Z^{T-1})^{-0.25} a_y(Z^{T-1})^{-0.25}}{B_{0i}} \\

I_{ki} &= \dfrac{\omega_{ki} a_x a_y ((Z^{T-1})^2)^{-0.25} }{B_{0i}} \\

I_{ki} &= \dfrac{\omega_{ki} a_x a_y (Z^{T-1})^{-0.5} }{B_{0i}} \\

I_{ki} &= \dfrac{\omega_{ki} a_x a_y Z^{-(T-1)/2}}{B_{0i}} \\

I_{ki} &= \dfrac{\omega_{ki} a_x a_y Z^{-(T-1)/2}}{B_{0i}}
\end{align}

Then we can compute maximum interaction strength from $Z$, $\omega$ and
$B_{0i}$.

```{r}
# Prepare Z and omega combination
comb_list <- list(
  Z = purrr::map_dbl(seq(-2, 5, .05), ~10^.x),
  omega = seq(0, 1, .05)
)
# Compute maximum interaction strength
result <- comb_list %>%
  expand.grid() %>%
  as_tibble() %>%
  mutate(
    I = map2_dbl(omega, Z, ~max_int(omega = .x, Z = .y, y = y["P"], T = 3))
  )

result_lg <- result %>%
  pivot_wider(names_from = "omega", values_from = "I")
res_mat <- as.matrix(result_lg[, -1])
row.names(res_mat) <- result_lg$Z

fig <- plot_ly(
  # Omega
  x = as.numeric(colnames(res_mat)),
  # Z 
  y = as.numeric(rownames(res_mat)),
  # I
  z = res_mat) %>%
  add_surface() %>%
  layout(
    title = "For predator of trophic level = 3",
    scene = list(
      xaxis = list(title = "Consumer preference"),
      yaxis = list(type = "log", title = "Z"),
      zaxis = list(title = "Maximum interaction strength")
    )
  )
```

```{r}
# Compute Z from McCann int strength taking in account omega 
z_from_int <- function(
  I = .48,
  b0 = .5,
  omega = .5,
  ax = .88,
  y = 5,
  T = 2
  ) {
  ay <- ax * y
  ((I * b0) / (omega * ax * ay)) ^ (- 2 / (T - 1))
}

Zmccann <- z_from_int(I = Imccann02_met, omega = .02, T = 3)
Zmccann <- z_from_int(I = Imccann98_met, omega = .98, T = 3)

ZmcannC1 <- z_from_int(I = ImccannC1R_met, omega = 1, T = 2)
ZmcannC2 <- z_from_int(I = ImccannC2R_met, omega = 1, T = 2)
```

```{r}
fig2 <- fig %>%
  add_markers(
    # Omega
    x = c(.02, .98),
    # Z
    y = c(Zmccann, Zmccann),
    # I
    z = c(Imccann02_met, Imccann98_met),
    color = I("blue")
    )
```

```{r}
Zbrose_int02 <- z_from_int(I = Imccann02_met, omega = .5, T = 3)
Zbrose_int98 <- z_from_int(I = Imccann98_met, omega = .5, T = 3)
```

```{r}
interaction_correspondance$Z <- c(Zmccann, Zmccann, ZmcannC1, ZmcannC2)
interaction_correspondance %>%
  kbl(
    caption = "Interaction strength from McCann 1998 and their corresponding
    translation in Z",
    label = "intZ"
  ) %>%
kable_styling()
```

We can then compute $Z$ from $I$ and $\omega$ such as

\begin{align}
Z^{-\dfrac{T-1}{2}} &= \dfrac{I_{ki} B_{0i}}{\omega a_x a_y} \\

Z &= \dfrac{I_{ki} B_{0i}}{\omega a_x a_y}^{-\dfrac{2}{T-1}}
\end{align}

It gives us what is the $Z$ equivalent of interaction strengths in McCann. We
can then plot the interaction of McCann in Brose framework (In blue, Fig.
\@ref(fig:intzomega)). We can furthermore infer what would be the equivalent of
McCann in Brose framework, i.e. with $\omega = .5$, i.e. in case that there are no
consumer preference. We found that the weak interaction (P-C2) would correspond
to $Z = `r Zbrose_int02`$ and the strong interaction (P-C1) to
$Z = `r Zbrose_int98`$ in Brose framework.

```{r}
intzomega_cap <- "Maximum interaction strength between a predator and consumer
of T = 3 and T = 2 according to Z and omega (range corresponding to Brose et al.
  2006). In blue are mapped the values corresponding to McCann P/C1 and P/C2
interactions. In red are mapped the values corresponding to McCann P/C1 and
P/C2, but in case where there is no consumer preference (Brose's framework)."
```

```{r intzomega, fig.cap=intzomega_cap}
fig2 %>%
  add_markers(
    # Omega
    x = c(.5, .5),
    # Z
    y = c(Zbrose_int02, Zbrose_int98),
    # I
    z = c(Imccann02_met, Imccann98_met),
    color = I("red"),
    labels = c("test", "test2")
    )
```

# Example of simulations

```{r}
species_replacement <- c("R", "C1", "C2", "P")
names(species_replacement) <- paste0("value", seq(1,4)) 
```

```{r}
mccann_origin <- read_csv("mcann_original.csv")
p_mccann_origin <- mccann_origin %>%
  pivot_longer(-timestamp, names_to = "species", values_to = "bm") %>%
  mutate(species = species_replacement[species]) %>%
  ggplot(aes(x = timestamp, y = bm, color = species)) +
  geom_line() +
  labs(x = "Time", y = "Biomass")

leg <- get_legend(p_mccann_origin + theme(legend.position = "bottom"))
```

```{r}
mccann_z <- read_csv("mcann_z.csv")
p_mccann_z <- mccann_z %>%
  pivot_longer(-timestamp, names_to = "species", values_to = "bm") %>%
  ggplot(aes(x = timestamp, y = bm, color = species)) +
  geom_line()+
  labs(x = "Time", y = "Biomass", color = "Species")
```

```{r}
brose_little_z <- read_csv("brose_little_z.csv")
p_brose_little_z <- brose_little_z %>%
  pivot_longer(-timestamp, names_to = "species", values_to = "bm") %>%
  ggplot(aes(x = timestamp, y = bm, color = species)) +
  geom_line() +
  labs(x = "Time", y = "Biomass")
```

```{r}
brose_big_z <- read_csv("brose_big_z.csv")
p_brose_big_z <- brose_big_z %>%
  pivot_longer(-timestamp, names_to = "species", values_to = "bm") %>%
  ggplot(aes(x = timestamp, y = bm, color = species)) +
  geom_line() +
  labs(x = "Time", y = "Biomass")
```

```{r}
sim_cap <- paste0("Simulation of the bioenergetic model for four simulations. (a)
  Original McCann model. (b) McCann model but metabolic rates have been
  drawn from the inferred Z between Predator and consumers (Z = ", Zmccann ,"), but
  does not consider that Z might be different for Predator/Consumer and
  Consumer/Resource. So, here everything crashes because interactions P/C might be
  too strong compared to C/R interactions. (c) Brose model with Z corresponding to
  the strong interaction P/C1. (d) Brose model with Z corresponding to the weak interaction P/C2.")

```

```{r sim, fig.cap=sim_cap}
top <- plot_grid(
  p_mccann_origin + theme(legend.position = "none"),
  p_mccann_z + theme(legend.position = "none"),
  p_brose_little_z + theme(legend.position = "none"),
  p_brose_big_z + theme(legend.position = "none"),
  ncol = 2,
  labels = "auto")
plot_grid(top, leg, nrow = 2, rel_heights = c(1, .1))
```

# Calculus trash

If you compute two Z (useless):

$$
I_{ki} = \dfrac{\omega_{ki} a_x a_y (Z^{T-1} Z^{T-1})^{-0.25} }{B_{0i}}
$$

You can also compute Z from metabolic parameters:

$Z_x^{T-1} = \dfrac{x_i}{a_x}$

$Z_x = (\dfrac{x_i}{a_x})^(1 / (T-1))$ because $(Z^{T-1})^{1/ (T-1)} = Z$

and

$Z_y = (\dfrac{y_i}{a_y})^(1 / (T - 1))$

Finally, from above equation, $Z = Z_x Z_y$

```{r}
z_from_y_x <- function(ax = .88, x = .08, y = 5, T = 3) {
  ay <- ax * y
  c(
    Zy = (y / ay) ^ (1 / (T - 1)),
    Zx = (x / ax) ^ (1 / (T - 1))
  )
}

# Z infered from parameters of McCann et al. 1998 and Vasseur and Fox
Zmccann <- Reduce(`*`, z_from_y_x(ax = .88, x = x["P"], y = y["P"], T = 2))
ZC1mccann <- Reduce(`*`, z_from_y_x(ax = .88, x = x["C1"], y = y["C1"], T = 2))
ZC2mccann <- Reduce(`*`, z_from_y_x(ax = .88, x = x["C2"], y = y["C2"], T = 2))
```

### 2022-11-15 misc/species_coherence_response.R

@@ -56,8 +56,9 @@ save_plot(
 # With four species
 ti <- tibble(
   rho = c(0, .8, -.8),
-  noise = map(rho, ~cross_correlated_response(rho = .x, evt_sd = 1, n = 4, time_len = 20))
-) 
+  noise = map(rho,
+    ~cross_correlated_response(rho = .x, evt_sd = 1, n = 4, time_len = 20))
+)
 
 p <- ti %>%
   unnest(noise) %>%
@@ -117,7 +118,8 @@ save_plot(
   tp
 )
 
-a <- t(sapply(c(3, 6), function(x) rnorm(10, x, .8)))
+set.seed(1)
+a <- t(sapply(c(3, 6), function(x) rnorm(10, x, 1)))
 dfr <- as.data.frame(t(a))  %>%
   mutate(species = seq_len(ncol(a))) %>%
   pivot_longer(-species, names_to = "com", values_to = "trait") %>%
@@ -128,9 +130,20 @@ dfr <- as.data.frame(t(a))  %>%
   group_by(com) %>%
   mutate(rel_abun = abun / sum(abun))
 
+library(scales) # ! important
+dfr %>%
+  ggplot(aes(x = trait, y = rel_abun, fill = com)) +
+  geom_col() +
+  geom_density(data = dfr,
+    aes(x = trait, y = ..density.. / 1.8, color = com, weight = rel_abun),
+    adjust = 1, inherit.aes = FALSE)
+
 p_trait <- dfr %>%
   ggplot(aes(x = trait, y = rel_abun, fill = com)) +
   geom_col() +
+  geom_density(data = dfr,
+    aes(x = trait, y = ..density.. / 2.5, color = com, weight = rel_abun),
+    adjust = .8, inherit.aes = FALSE) +
   geom_vline(xintercept = summarise(dfr, avg = sum(rel_abun * trait))$avg) +
   labs(x = "Trait", y = "Relative abundance") +
   cowplot::theme_half_open() +
@@ -140,6 +153,7 @@ p_trait <- dfr %>%
     axis.ticks = element_blank(),
     axis.text = element_blank()
   )
+
 save_plot(
   filename = here::here("fig/p_trait.pdf"),
   p_trait

### 2022-11-15 starting.jl

@@ -19,3 +19,4 @@ mkdir("report")
 touch("report/project_definition.Rmd")
 
 symlink("/home/alain/Documents/post-these/references.bib", "report/references.bib")
+

### 2022-11-15 use_case/int_mccann_brose/Pkg.jl

@@ -1,0 +1,6 @@
+# Will use the current develop version of BEFWM2
+using Pkg 
+Pkg.add(path = "/home/alain/Documents/post-these/sheffield/befwm2_dev/BEFWM2/")
+Pkg.add("Plots")
+Pkg.add(["CSV", "DataFrames"])
+

### 2022-11-15 use_case/int_mccann_brose/mccann_brose.jl

@@ -1,0 +1,162 @@
+using BEFWM2
+using Plots
+using DataFrames
+using CSV
+
+A = [0 0 0 0; 1 0 0 0; 1 0 0 0; 0 1 1 0] 
+foodweb = FoodWeb(A)
+
+# Functional response
+## Preference of consumer 
+myω = zeros(4, 4)
+myω[:,1] = [0, 1, .98, 0]
+myω[4,:] = [0, .92, 1 - .92, 0]
+## Predator interference
+myc = repeat([0], 4)
+myc
+
+# Half-saturation constant
+myB0 = [0, 0.16129, .90, .5]
+
+# Biological rates
+## Assimilitation efficiency or ingestion rates (in Vasseur & Fox, 2007)
+## Efficiency is implicitly one for all consumers in Vasseur & Fox
+mye = zeros(4, 4)
+# Consumer
+mye[:,1] = [0, 1, 1, 0] 
+# Predator
+mye[4,:] = [0, 1, 1, 0]
+
+# Metabolic rates and maximum ingestion rates 
+## From McCann (1998):
+x = [0, .40, .20, .08]
+y = [0, 2.009, 3.50, 5.0]
+
+#  
+
+####################
+#  McCann version  #
+####################
+# Define x and y
+
+bioener = BioenergeticResponse(foodweb,
+                               h = 1,
+                               # Half saturation-constant
+                               B0 = myB0,
+                               # Consumer preference
+                               ω = myω,
+                               # Predator interference
+                               c = myc
+                              )
+
+biorate = BioRates(foodweb,
+        r = [1.0, 0, 0, 0],
+        e = mye,
+        x = x, 
+        y = y
+       )
+
+params = ModelParameters(foodweb,
+                functional_response = bioener,
+                biorates = biorate,
+                environment = Environment(foodweb, K = 1.0)
+               )
+
+m = simulate(params, rand(4))
+df = DataFrame(m)
+CSV.write("./mcann_original.csv",df)
+
+mccann_fig = plot(m)
+
+
+###########################
+#  McCann version with Z  #
+###########################
+# myω
+
+fb = FoodWeb(A, Z = 9.68)
+bner = BioenergeticResponse(fb,
+                               h = 1,
+                               # Half saturation-constant
+                               B0 = myB0,
+                               # Consumer preference
+                               ω = myω,
+                               # Predator interference
[…]

### 2022-11-18 report/project_definition.Rmd
Clarify differences between McCann and Brose

@@
 
-The question at 1bn pound is "what is driving stability?", i.e. the propagation
+The question at 1bn pounds is "what is driving stability?", i.e. the propagation
 of perturbations across food-webs. Early studies focused on the effect of
@@
 The big other ingredient of food-web stability is the strength of species
-interactions. The tremendous early work of McCann and other authors about the
-distribution of interaction strength is really interesting, showing that
-coupling weak interactions to strong one stabilize food-web dynamics.
+interactions, as demonstrated by previous studies [@mccann_weak_1998;
+@brose_allometric_2006]. @mccann_weak_1998 showed that food-web having strong
+interactions can persist if the strong interactions are coupled with weak ones.
+Interestingly, a strong interaction needs to be coupled in two ways, by a
+feeding and a competitive interactions. @brose_allometric_2006 showed the
+strength of interactions are driven by body size, such larger body sized animals
+produce lower interaction strengths (because of their lower metabolic rates).
+
 Interestingly, I see two schools on the definition of interaction strengths in
@@
 @brose_allometric_2006 modules interaction strength by modulating predator/prey
-mass ratios (Z) such as Z increases the metabolism of predators decreases
+mass ratios (Z) such as Z decrease the metabolism of predators
 relative to prey (i.e. $x_i$ and $y_i$). Thus increasing Z decreases $I_{ki}$.
-The main difference between Brose and McCann approaches is that the Brose
+A common feature of both approaches is that they both consider that the strength
+of interactions decrease as the trophic level increases.
+
+A main difference between Brose and McCann approaches is that the Brose
 approach of modulating interactions also modulates metabolic losses ($x_iy_iB_i$).
@@
 (fully metabolic) but it changes two things at the same time.
+
+Although in complex food-webs, Brose method can create strong asymetry in
+interaction strength by coupling specialists and generalists, as they
+respectively generate strong and weak interactions. Such mechanism is
+triggered by the fact that consumer preference is equally shared among preys
+($\omega_ki = 1 \ \sum_k 1 $, such as $\omega_{ki} = 1$ or .1 for a consumer
+having one prey or 10 preys).
 
@@
 
+## Stochasticity in food-webs
+
+@vasseur_environmental_2007 found that Stochasticity and response diversity can
+stabilize food-web in a McCann model with strong asymetry in species interactions.
+Is it valid also with a Brose model without this asymetry? Is it also valid with
+different functional responses?
+
 # Research questions
+
+## Response diversity
 

### 2022-12-06 report/mccann_brose.Rmd
Analysis Vasseur & Fox version Brose

---
title: "Brose for Vasseur and Fox"
author: "Alain Danet"
date: \today
output:
  bookdown::pdf_document2:
    fig_caption: true
    keep_tex: true
    toc: true
    fontsize: 12pt
    geometry: margin=2cm
    number_sections: true
bibliography: references.bib
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

```{r, results = FALSE}
library(tidyverse)
library(magrittr)
library(cowplot)
library(here)

mytheme <- theme_cowplot(font_size = 8) +
background_grid() +
theme(legend.position = "bottom")

theme_set(mytheme)
```

```{r}
sim_brut <- read_csv(here("res", "vasseur_fox__brose_res.csv"))

sim <- sim_brut %>%
  rename_with(~str_replace_all(., c("ρ" = "rho", "σₑ" = "sigma"))) %>%
  group_by(Z, fr, rho, sigma) %>%
  summarise(across(everything(), median)) %>%
  select(-rep, -sim_timing)
```

```{r}
sim %>%
  filter(stab_com > 10)
```

```{r}
sim %>%
  ggplot(aes(y = stab_com, x = fr)) +
  geom_boxplot() +
  scale_y_log10()
```

```{r}
cons_sync <- sim %>%
  ggplot(aes(rho, sigma, z = sync_cons)) +
  geom_contour_filled() +
  facet_grid(rows = vars(fr), cols = vars(Z)) +
  labs(x = "Environmental correlation", y = "Fluctuation strength") +
  labs(fill = "Consumer synchrony")

pred_stab <- ggplot(sim, aes(rho, sigma, z = log10(stab_pred))) +
  geom_contour_filled() +
  facet_grid(rows = vars(fr), cols = vars(Z)) +
  labs(x = "Environmental correlation", y = "Fluctuation strength") +
  labs(fill = "Predator stability")

cons1_stab <- sim %>%
  ggplot(aes(rho, sigma, z = log10(stab_cons1))) +
  geom_contour_filled() +
  facet_grid(rows = vars(fr), cols = vars(Z)) +
  labs(x = "Environmental correlation", y = "Fluctuation strength") +
  labs(fill = "Consumer 1 stability")

cons2_stab <- sim %>%
  ggplot(aes(rho, sigma, z = log10(stab_cons2))) +
  geom_contour_filled() +
  facet_grid(rows = vars(fr), cols = vars(Z)) +
  labs(x = "Environmental correlation", y = "Fluctuation strength") +
  labs(fill = "Consumer 2 stability")
```

# Vasseur/Fox vs Brose

```{r}
cons_sync_cap <- "Column facets represent increasing Z, row ones respectively
Predator interference (PI, h = 1, c = 1), type II (h = 1, c = 0) and type III (h
  = 2, c = 0)"
```

```{r cs, fig.cap=cons_sync_cap}
cons_sync
```

We find that the strength of environmental fluctuations desynchronises consumer
fluctuations for very low strength of environmental fluctuations, and
has mostly no effects for higher strength of environmental fluctuations (Fig.
\@ref(fig:cs)). This
result constrasts with previous results that showed that the strength of
environmental fluctuations synchronises consumer fluctuations
@vasseur_environmental_2007. Furthermore, we find that it is environmental
correlation that drives consumer synchrony, negative correlations promoting
synchrony while positive correlations promote synchrony. Again it contrasts with
@vasseur_environmental_2007, which found that environmental correlations had
little effects on consumer synchrony.

```{r ps, fig.cap="Stability as 1/CV. See fig. 1 for facets"}
pred_stab
```

In turn, we find that predator stability decreases with increasing environmental
fluctuations , but is little affected by environmental
synchrony of consumer (Fig. \@ref(fig:ps)). It contrasts with
@vasseur_environmental_2007 which found an island of high predator stability for
intermediation strength of environmental fluctuation and high positive
correlation of environmental fluctuations between consumers. Overall, the
stability are really high, between 1 and $2.10^5$ (median: 90). It is surely
because both the metabolism and the interaction strenghs are too weak, so
fluctuations are really tiny and fluctuations does not propagate much . I should
try lower Z.

```{r}
stab <- ggplot(sim, aes(rho, sigma, z = log10(stab_com))) +
  geom_contour_filled() +
  facet_grid(rows = vars(fr), cols = vars(Z)) +
  labs(x = "Environmental correlation", y = "Fluctuation strength") +
  labs(fill = "Community stability")

sp_stab <- ggplot(sim, aes(rho, sigma, z = log10(1 / avg_cv_sp))) +
  geom_contour_filled() +
  facet_grid(rows = vars(fr), cols = vars(Z)) +
  labs(x = "Environmental correlation", y = "Fluctuation strength") +
  labs(fill = "Average species stab")

sync <- sim %>%
  ggplot(aes(rho, sigma, z = sync)) +
  geom_contour_filled() +
  facet_grid(rows = vars(fr), cols = vars(Z)) +
  labs(x = "Environmental correlation", y = "Fluctuation strength") +
  labs(fill = "Community synchrony")
```

# References {-}

### 2022-12-06 report/project_definition.Rmd
Analysis Vasseur & Fox version Brose

@@
 ---
+
+```{r, results = FALSE}
+library(tidyverse)
+library(magrittr)
+library(cowplot)
+library(here)
+
+mytheme <- theme_cowplot(font_size = 10) +
+background_grid() +
+theme(legend.position = "bottom")
+
+theme_set(mytheme)
+```
 
@@
 
+# Early results
+
+```{r}
+sim_brut <- read_csv(here("res", "hpc_test.csv"))
+
+sim <- sim_brut %>%
+  filter(!is.na(persistence), Z > .1) %>%
+  mutate(sim_time_m = sim_time / 60)
+```
+
+```{r}
+sim %>%
+  select(rep:fr_type, persistence:sync) %>%
+  pivot_longer(-c(rep:fr_type), names_to = "metric", values_to = "values") %>%
+  ggplot(aes(y = log(values), x = S, color = fr_type)) +
+  geom_quantile(quantiles = .5, size = 2) +
+  facet_grid(rows = vars(metric), cols = vars(Z), scales = "free_y") +
+  theme(legend.position = "bottom")
+```
+
+```{r}
+sim %>%
+  ggplot(aes(y = log(stab_com), x = S, color = fr_type)) +
+  geom_jitter() +
+  geom_quantile(quantiles = .5, size = 2) +
+  facet_grid(cols = vars(Z), scales = "free_y")
+```
+
+```{r}
+sim %>%
+  ggplot(aes(y = log(sync), x = S, color = fr_type)) +
+  geom_jitter() +
+  geom_quantile(quantiles = .5, size = 2) +
+  facet_grid(cols = vars(Z), scales = "free_y")
+```
+
+```{r}
+sim %>%
+  ggplot(aes(y = log(avg_cv_sp), x = S, color = fr_type)) +
+  geom_jitter(alpha = .3) +
+  geom_quantile(quantiles = .5, size = 2) +
+  facet_grid(cols = vars(Z), scales = "free_y")
+```
+
 # References {-}

### 2022-12-14 report/project_definition.Rmd
Add simulations with some modules

@@
 ---
+
+```{r, echo = FALSE}
+knitr::opts_chunk$set(
+  cache = FALSE,
+  collapse = TRUE,
+  comment = "#>",
+  #fig.dim = c(7, 7),
+  fig.fullwidth = TRUE,
+  fig.show = "hold",
+  echo = FALSE,
+  message = FALSE,
+  warning = FALSE,
+  results = TRUE,
+  fig.path="figures/"
+)
+```
 
@@
 the Bioenergetic model. McCann defines it by modulating consumer preference
-($\omega$) such as $I_{ki} = \omega_{ik}* x_i * y_i / B_{0i}$ while
+($\omega$) such as $I_{ki} = \omega_{ik} x_i  y_i / B_{0i}$ while
 @brose_allometric_2006 modules interaction strength by modulating predator/prey
@@
 triggered by the fact that consumer preference is equally shared among preys
-($\omega_ki = 1 \ \sum_k 1 $, such as $\omega_{ki} = 1$ or .1 for a consumer
+($\omega_{ki} = 1 \ \sum_k 1$, such as $\omega_{ki} = 1$ or .1 for a consumer
 having one prey or 10 preys).
@@
 
+## Module and stability
+
+```{r}
+PlotWeb <- function (TL, webTL,colnode,abund,collink="grey70", scale_abun = 0.01, rel_abun = TRUE, log_abun = FALSE){
+
+  Sweb<-length(TL)
+  g=matrix(0,nrow=Sweb,ncol=3)
+
+  if (log_abun) {
+    # to not have negative abun:
+    if(any(abund < 1)) {
+      abund <- abund + 1
+    }
+    abund <- log(abund)
+
+  }
+
+  if (rel_abun) {
+    g[,3]<- scale_abun * abund / sum(abund)
+  } else {
+    g[,3]<- scale_abun * abund
+  }
+  g[,2]<-TL/sum(TL)
+  TLround<-round(TL)
+  for (i in 1:max(round(TL))) {
+    a<-TLround==i
+    b<-1:Sweb
+    b<-b[a]
+    xaxis<-(1:length(b))/length(b)
+    g[a,1]<-xaxis+ 0.5 - sum(xaxis)/length(b)
+  }
+  symbols(g[,1],g[,2],circles=g[,3],inches=FALSE,bg=colnode,fg=colnode,xlab="",ylab="",bty="n",xaxt="n",yaxt="n")
+  for (i in 1:Sweb){
+    for (j in 1:Sweb){
+      if (webTL[i,j]>0){
+         arrows(g[i,1],g[i,2],g[j,1],g[j,2],lwd=1, col=collink,length=0)
+         }
+    }
+  }
+  symbols(g[,1],g[,2],circles=g[,3],inches=FALSE,bg=colnode,fg=colnode,add=TRUE)
+}
+```
+
+```{r, fig.width = 12}
+null_mat <- matrix(0, nrow = 6, ncol = 6)
+gen <- null_mat
+gen[c(4,5,6), c(1,2,3)] <- 1
+spe <- gen
+spe[4, c(2,3)] <- spe[5, c(1,3)] <- spe[6, c(1,2)] <- 0
+
+top_spe <- spe %>% rbind(., c(0, 0, 0, 1, 1, 1)) %>%
+cbind(., rep(0, 7))
+
+top_gen <- gen %>% rbind(., c(0, 0, 0, 1, 1, 1)) %>%
+cbind(., rep(0, 7))
+
+top_omn_spe <- top_spe
+top_omn_spe[7, ] <- c(rep(1, 6), 0)
+
+top_omn_gen <- top_gen
+top_omn_gen[7, ] <- c(rep(1, 6), 0)
+
+repl_module <- c(
+  "spe" = "Specialist",
+  "gen" = "Generalist",
+  "top_spe" = "Top specialist",
+  "top_gen" = "Top generalist",
+  "top_omn_spe" = "Top omnivore\nspecialist",
+  "top_omn_gen" = "Top omnivore\ngeneralist"
+)
+```
+
+```{r}
+par(mar = c(1.1, 1.1, 1.1, 1.1))
+
+p_top_omn_gen <- ~PlotWeb(
+  NetIndices::TrophInd(t(top_omn_gen))$TL,
+  t(top_omn_gen),
+  abund = rep(1, nrow(top_omn_gen)), colnode = "black")
+p_top_omn_spe <- ~PlotWeb(
+  NetIndices::TrophInd(t(top_omn_spe))$TL,
+  t(top_omn_spe),
+  abund = rep(1, nrow(top_omn_spe)), colnode = "black")
+p_gen <- ~PlotWeb(
+  NetIndices::TrophInd(t(gen))$TL,
+  t(gen),
+  abund = rep(1, nrow(gen)), colnode = "black")
+p_spe <- ~PlotWeb(
+  NetIndices::TrophInd(t(spe))$TL,
+  t(spe),
+  abund = rep(1, nrow(spe)), colnode = "black")
+p_top_spe <- ~PlotWeb(
+  NetIndices::TrophInd(t(top_spe))$TL,
+  t(top_spe),
+  abund = rep(1, nrow(top_spe)), colnode = "black")
+p_top_gen <- ~PlotWeb(
+  NetIndices::TrophInd(t(top_gen))$TL,
+  t(top_gen),
+  abund = rep(1, nrow(top_gen)), colnode = "black")
+
+p_fw <- plot_grid(
+  p_spe, p_gen,
+  p_top_spe, p_top_gen,
+  p_top_omn_spe, p_top_omn_gen,
+  ncol = 2,
+  label_size = 8,
+  labels = repl_module
+)
+save_plot(
+  here("report", "figures", "p_fw.pdf"),
+  p_fw, ncol = 2, nrow = 3,
+  base_asp = 1, base_height = 2)
+```
+
+```{r}
+png(here("report", "figures", "spe_top_spe.png"),
+  width = 480 * 1.618, height = 480, units = "px", bg = "transparent")
+par(mfrow = c(1, 2))
+PlotWeb(
+  NetIndices::TrophInd(t(top_spe))$TL,
+  t(top_spe),
+  abund = rep(1, nrow(top_spe)), scale_abun = .3, colnode = "red")
+title("Top generalist")
+PlotWeb(
+  NetIndices::TrophInd(t(spe))$TL,
+  t(spe),
+  abund = rep(1, nrow(spe)), scale_abun = .3, colnode = "green")
+title("Specialist")
+dev.off()
+```
+
+```{r}
+gen_stab <- read_csv(here("generalism_stoch.csv"))
+
+gen_stab %>%
+  select(1:5) %>%
+  mutate(
+    stab_com = 1 / cv_com,
+    fw = repl_module[fw]
+    ) %>%
+  pivot_longer(c(stab_com, avg_cv_sp, synchrony),
+    names_to = "metric", values_to = "values") %>%
+  ggplot(aes(x = fw, y = values)) +
+  geom_boxplot()  +
+  facet_wrap(~metric, scales = "free_y")
+```
+
+```{r}
+p_gen_pred <- gen_stab %>%
+  select(1:5) %>%
+  filter(fw %in% c("spe", "top_spe")) %>%
+  mutate(
+    stab_com = 1 / cv_com,
+    fw = c(
+      "spe" = "Specialist\nconsumers",
+      "top_spe" = "Generalist\ntop predator"
+      )[fw]
+    ) %>%
+  pivot_longer(c(stab_com, avg_cv_sp, synchrony),
+    names_to = "metric", values_to = "values") %>%
+  mutate(metric = c("stab_com" = "Stability", "avg_cv_sp" = "Avg CVsp",
+      "synchrony" = "Synchrony")[metric]) %>%
+  ggplot(aes(x = fw, y = values, fill = fw)) +
+  geom_boxplot() +
+  labs(x = "Food web structure") +
+  scale_fill_manual(values = c("red", "green")) +
+  facet_wrap(~metric, scales = "free_y") +
+  theme_cowplot(font_size = 14) +
+  theme(
+    axis.title.y = element_blank(),
+    axis.title.x = element_blank(),
+    legend.position = "none"
+  )
+
+p_gen_pred
+
+save_plot(
+  here("report", "figures", "model_spe_top.png"),
+  p_gen_pred,
+  ncol = 3,
+  base_asp = 1
+)
+```
+
 # References {-}

### 2022-12-14 use_case/analysis_vasseur_fox.Rmd
Add simulations with some modules

@@
 
-mytheme <- theme_cowplot() +
-background_grid()
+mytheme <- theme_cowplot(font_size = 12) +
+  background_grid() +
+  theme(legend.position = "bottom")
 
@@
 
+# Some simulations with stochasticity
+
+```{r}
+sim <- read_csv(here("use_case", "vasseur_fox_sim_ts_ex.csv")) %>%
+  pivot_longer(c(resource:pred), names_to = "species", values_to = "bm") %>%
+  mutate(species = str_replace_all(species, c(
+        "pred" = "Predator",
+        "cons1" = "Consumer 1",
+        "cons2" = "Consumer 2",
+        "resource" = "Resource"
+        )))
+
+sim0 <- sim %>%
+  filter(sigma == 0)
+unique(sim$sigma)
+unique(sim$rho)
+```
+
+```{r}
+p0 <- sim %>%
+  filter(sigma == 0) %>%
+  ggplot(aes(x = time, y = bm, color = species)) +
+  geom_line()
+save_plot(
+  filename = here("use_case", "int_mccann_brose", "figures", "mccann_sim.png"),
+  p0)
+p_stoch <- sim %>%
+  filter(sigma == 0.3, rho == 0.0) %>%
+  ggplot(aes(x = time, y = bm, color = species)) +
+  geom_line()
+p_stoch_rho <- sim %>%
+  filter(sigma == 0.3, rho == 1) %>%
+  ggplot(aes(x = time, y = bm, color = species)) +
+  geom_line()
+```
+
+```{r}
+```
+
+# Reproduce Vasseur & Fox
+
 ```{r}
@@
 ```
+
 ```{r}

### 2022-12-14 use_case/consumer_generalism.jl

@@ -1,0 +1,410 @@
+# Test Thebault et al.
+#
+
+import Pkg
+Pkg.activate("..")
+using BEFWM2, LinearAlgebra, DifferentialEquations, DataFrames, CSV, Distributed, Distributions, ProgressMeter, BenchmarkTools
+using Plots
+
+include("src/stochastic_mortality_model.jl")
+include("src/sim.jl")
+
+import Random.seed!
+
+seed!(22)
+
+specialist = [
+     0 0 0 0 0 0;
+     0 0 0 0 0 0;
+     0 0 0 0 0 0;
+     1 0 0 0 0 0;
+     0 1 0 0 0 0;
+     0 0 1 0 0 0;
+    ]
+generalist = [
+     0 0 0 0 0 0;
+     0 0 0 0 0 0;
+     0 0 0 0 0 0;
+     1 1 1 0 0 0;
+     1 1 1 0 0 0;
+     1 1 1 0 0 0;
+             ]
+foodweb = FoodWeb(specialist, Z = 100)
+nprod = sum(foodweb.metabolic_class .== "producer")
+param = ModelParameters(foodweb,
+                       environment = Environment(foodweb,K = 3/nprod),
+                       functional_response = BioenergeticResponse(foodweb, h = 1)
+                      )
+spe_sim = simulate(param, rand(length(foodweb.species)), tmax = 500, callback = nothing)
+foodweb_cv(spe_sim, last = 100)
+plot(spe_sim)
+
+
+foodweb = FoodWeb(generalist, Z = 100)
+nprod = sum(foodweb.metabolic_class .== "producer")
+param = ModelParameters(foodweb,
+                       environment = Environment(foodweb,K = 3/nprod),
+                       functional_response = BioenergeticResponse(foodweb, h = 1)
+                      )
+gen_sim = simulate(param, rand(length(foodweb.species)), tmax = 500, callback = nothing)
+foodweb_cv(gen_sim, last = 100)
+plot(gen_sim)
+
+
+foodweb_cv(spe_sim, last = 50)
+foodweb_cv(gen_sim, last = 50)
+
+# Add environmental stochasticity
+#
+#
+function stochastic_process(dW, B, params, t)
+
+    S = length(params.network.species)
+
+    # Biomass dynamics have no stochasticity
+    for i in 1:2*S
+        dW[i] = 0.0
+    end
+
+    # Stochastic mortality variable for consumer is... Stochastic!!!
[…]

### 2023-01-12 report/project_definition.Rmd
Add module

@@
 ```
+```{r, out.height = "80%"}
+knitr::include_graphics(here("report", "figures", "spe_top_spe.png"))
+```
 
-```{r}
+```{r, fig.height = 10}
 gen_stab <- read_csv(here("generalism_stoch.csv"))
@@
   geom_boxplot()  +
-  facet_wrap(~metric, scales = "free_y")
+  facet_wrap(~metric, scales = "free_y", ncol = 1)
 ```

### 2023-01-12 use_case/module.jl

@@ -1,0 +1,142 @@
+##############################
+#  Module and stochasticity  #
+##############################
+
+
+import Pkg
+Pkg.activate("..")
+using BEFWM2, LinearAlgebra, DifferentialEquations, DataFrames, CSV, Distributed, Distributions, ProgressMeter, BenchmarkTools
+using Plots
+
+include("src/stochastic_mortality_model.jl")
+include("src/sim.jl")
+
+import Random.seed!
+
+fw_module = (
+          prod = [0 0; 0 0],
+          chain1 = [0 0; 1 0],
+          cons = [0 0 0; 0 0 0; 1 1 0],
+          cons_spe = [0 0 0 0; 0 0 0 0; 1 0 0 0; 0 1 0 0],
+          cons_gen = [0 0 0 0; 0 0 0 0; 1 1 0 0; 1 1 0 0],
+          cons_spe_top = [0 0 0 0 0; 0 0 0 0 0; 1 0 0 0 0; 0 1 0 0 0; 0 0 1 1 0],
+          cons_gen_top = [0 0 0 0 0; 0 0 0 0 0; 1 1 0 0 0; 1 1 0 0 0; 0 0 1 1 0],
+         )
+
+foodweb = FoodWeb(specialist, Z = 100)
+nprod = sum(foodweb.metabolic_class .== "producer")
+param = ModelParameters(foodweb,
+                       environment = Environment(foodweb,K = 3/nprod),
+                       functional_response = BioenergeticResponse(foodweb, h = 1)
+                      )
+
+function simCS(A, σₑ, alpha_ij; Z, h, c, K, max = 50000, last = 25000, dt = 0.1, return_sol = false)
+
+    fw = FoodWeb(A, Z = Z)
+
+    # Parameters of the functional response
+    funcrep = BioenergeticResponse(fw; h = h, c = c)
+    # generate the model parameters
+    p = ModelParameters(fw;
+                        functional_response = funcrep,
+                        environment = Environment(fw, K = K),
+                        producer_competition = ProducerCompetition(fw, αii = 1.0, αij = alpha_ij),
+                        env_stoch = EnvStoch(σₑ)
+                       )
+    stoch_starting_val = repeat([0], S)
+    u0 = [rand(S); stoch_starting_val]
+
+    # Make the stochastic matrix
+    corr_mat = Diagonal(repeat([1.0], S * 2))
+    # Generate the Wiener Process
[…]

### 2023-01-14 report/cs_analysis.Rmd
Sim modules Z

---
title: big sim
author: Alain Danet
output:
  bookdown::pdf_document2
---

```{r}
library(tidyverse)
library(magrittr)
```

```{r}
df_brut <- read_csv(here::here("res", "cs_sim.csv"))
df <- df_brut %>%
  select(where(is.double))
```

```{r}
summary(df)

df %>%
  filter(stab_com <= 1000) %>%
  ggplot(aes(x = as.factor(richness), y = stab_com, color = as.factor(ct))) +
  geom_boxplot()
```

```{r}
corrplot::corrplot(
  cor(df %>% select(-rep, -Z, -env_stoch, -sim_timing), method = "spearman"),
  diag = FALSE, type = "upper"
)
```

### 2023-01-14 report/module_analysis.Rmd
Sim modules Z

---
title: big stoch sim
author: alain
date: 2022-09-12
format:
  html:
    embed-resources: false
---

```{r}
library(arrow)
library(tidyverse)
library(magrittr)
```

```{r}
pq_brut <- open_dataset(here::here("res", "sim_module.arrow"), format = "arrow")
df <- pq_brut %>%
  collect()
colnames(df)
```

```{r}
df %>%
  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
  "values") %>%
  ggplot(aes(x = module, y = values, color = as.factor(alphaij))) +
  geom_boxplot()+
  facet_grid(
    rows = vars(stab),
    scales = "free_y")
```

### 2023-01-14 draft.jl

@@ -11,24 +11,38 @@ using JSON3
 using CSV
 include("src/minmax.jl")
 include("src/interaction_strength.jl")
+include("src/stochastic_mortality_model.jl")
+include("src/sim.jl")
 
-mat = zeros(3, 3)
-sparse(mat)
-
-ct = .25
+ct = .1
 S = 20
 
 global fw
 c = 0
-while c != ct
-    fw = FoodWeb(nichemodel, 20, C = ct, Z = 4)
-    c = round(connectance(fw), digits = 2)
+try
+    while c != ct
+        fw = FoodWeb(nichemodel, 20, C = ct, Z = 4)
+        c = round(connectance(fw), digits = 2)
+    end
+catch
+   fw = missing
 end
 fw
 
+#simCS(C, S, Z, h, c, σₑ, K; max = 50000, last = 25000, dt = 0.1, return_sol = false)
+ti = simCS(0.1, 20, 100, 2.0, 1.0, 1.0, 5; max = 5000, last = 1000, dt = 0.1, return_sol = false)
+plot(ti, idxs = collect(1:1:length(get_parameters(ti).network.species)))
+cv(ti, last = 10, idxs = collect(1:1:length(get_parameters(ti).network.species)))
+biomass(ti, last = 10, idxs = collect(1:1:length(get_parameters(ti).network.species)))
+BEFWM2.filter_sim(ti)
+get_parameters(ti)
 
 
+
+
+fw = FoodWeb([0 0 0; 1 0 0; 0 1 0])
 p = ModelParameters(fw, functional_response = BioenergeticResponse(fw, h = 2, c = 1), env_stoch = EnvStoch(.3))
+S = size(fw.A, 1)
 
 
 stoch_starting_val = repeat([0], S)
@@ -54,14 +68,16 @@ m = solve(prob;
       dt = .1,
       adaptive = false
      )
+cv(m, last = 10, idxs = collect(1:1:S))
+biomass(m, last = 10, idxs = collect(1:1:S))
+BEFWM2.filter_sim(m)
+get_parameters(m)
 
-include("src/stochastic_mortality_model.jl")
-include("src/interaction_strength.jl")
-include("src/sim.jl")
+
+
 
 ti = mysim(A, 1, 4, (h = 2, c = 1), 0, .3, max = 5000, last = 4000, dt = .1, corr_mat = vc, return_sol = true)
 
[…]

### 2023-01-14 src/sim.jl

@@ -129,6 +129,118 @@ function simCS(C, S, Z, h, c, σₑ, K; max = 50000, last = 25000, dt = 0.1, ret
     out
 end
 
+function sim_int_mat(A; σₑ = .5, alpha_ij = 0, Z = 100, h = 2.0, c = 1.0, K = 1.0, max = 50000, last = 25000, dt = 0.1, return_sol = false)
+
+    fw = FoodWeb(A, Z = Z)
+    S = size(A, 1)
+
+    # Parameters of the functional response
+    funcrep = BioenergeticResponse(fw; h = h, c = c)
+    # generate the model parameters
+    p = ModelParameters(fw;
+                        functional_response = funcrep,
+                        environment = Environment(fw, K = K),
+                        producer_competition = ProducerCompetition(fw, αii = 1.0, αij = alpha_ij),
+                        env_stoch = EnvStoch(σₑ)
+                       )
+    stoch_starting_val = repeat([0], S)
+    u0 = [rand(S); stoch_starting_val]
+
+    # Make the stochastic matrix
+    corr_mat = Diagonal(repeat([1.0], S * 2))
+    # Generate the Wiener Process
+    wiener = CorrelatedWienerProcess(corr_mat, 0.0, zeros(size(corr_mat, 1)))
+
+    prob = SDEProblem(
+                      mydBdt!,
+                      gen_stochastic_process,
+                      u0,
+                      [0, max],
+                      p,
+                      noise = wiener
+                     )
+    # Simulate
+    timing = @elapsed m = try
+        solve(prob;
+              saveat = collect(0:1:max),
+              dt = dt,
+              adaptive = false
+             )
+
+    catch
+        (t = 0, x = missing)
+    end
+
+    if return_sol
+        return m
+    end
+
+    if length(m.t) == max + 1
+        bm_cv = cv(m, last = last, idxs = collect(1:1:S))
+        bm = biomass(m, last = last, idxs = collect(1:1:S))
+        int_strength = empirical_interaction_strength(m, p, last = last)
+        non_zero_int = [i for i in int_strength if i != 0]
+        max_int = max_interaction_strength(p)
+        non_zero_max_int = [i for i in max_int if i != 0]
+        tlvl = trophic_levels(fw)
+
+        out = (
+               begin_richness    = S,
+               Z                 = Z,
+               env_stoch         = σₑ,
+               sim_timing        = timing,
[…]

### 2023-01-14 use_case/module.jl

@@ -6,22 +6,52 @@
 import Pkg
 Pkg.activate(".")
 using BEFWM2, LinearAlgebra, DifferentialEquations, DataFrames, CSV, Distributed, Distributions, ProgressMeter, BenchmarkTools
-using Plots
+using Plots, SparseArrays
+using Arrow
 
 include("src/stochastic_mortality_model.jl")
 include("src/sim.jl")
+include("src/interaction_strength.jl")
 
 import Random.seed!
 
 fw_module = (
-          prod = [0 0; 0 0],
+          # prod = [0 0; 0 0],
           chain1 = [0 0; 1 0],
+          chain2 = [0 0 0; 1 0 0; 0 1 0],
+          chain3 = [0 0 0 0; 1 0 0 0; 0 1 0 0; 0 0 1 0],
+          chain4 = [0 0 0 0;
+                    1 0 0 0;
+                    0 1 0 0;
+                    0 0 1 0],
           cons = [0 0 0; 0 0 0; 1 1 0],
-          cons_spe = [0 0 0 0; 0 0 0 0; 1 0 0 0; 0 1 0 0],
-          cons_gen = [0 0 0 0; 0 0 0 0; 1 1 0 0; 1 1 0 0],
-          cons_spe_top = [0 0 0 0 0; 0 0 0 0 0; 1 0 0 0 0; 0 1 0 0 0; 0 0 1 1 0],
-          cons_gen_top = [0 0 0 0 0; 0 0 0 0 0; 1 1 0 0 0; 1 1 0 0 0; 0 0 1 1 0],
+          cons2_spe = [0 0 0 0; 0 0 0 0; 1 0 0 0; 0 1 0 0],
+          cons2_spe_top = [0 0 0 0 0;
+                           0 0 0 0 0;
+                           1 0 0 0 0;
+                           0 1 0 0 0;
+                           0 0 1 1 0],
+          cons3_spe = [0 0 0 0 0 0;
+                       0 0 0 0 0 0;
+                       1 0 0 0 0 0;
+                       0 1 0 0 0 0;
+                       0 0 1 0 0 0;
+                       0 0 0 1 0 0],
+          cons2_gen = [0 0 0 0; 0 0 0 0; 1 1 0 0; 1 1 0 0],
+          cons2_gen_top = [0 0 0 0 0;
+                           0 0 0 0 0;
+                           1 1 0 0 0;
+                           1 1 0 0 0;
+                           0 0 1 1 0],
[…]

### 2023-01-15 report/module_analysis.Rmd
Make module simulation with natural death

@@
 ```
+
+# Stochastic natural death
+
+```{r}
+pq_brut <- open_dataset(here::here("res", "sim_module_d.arrow"), format = "arrow")
+df <- pq_brut %>%
+  collect()
+colnames(df)
+```
+
+```{r}
+df %>%
+  filter(env_stoch == 0.5) %>%
+  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
+  "values") %>%
+  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
+  geom_boxplot()+
+  facet_grid(
+    rows = vars(stab), cols = vars(ρ),
+    scales = "free_y")
+```

### 2023-01-15 draft.jl

@@ -14,21 +14,6 @@ include("src/interaction_strength.jl")
 include("src/stochastic_mortality_model.jl")
 include("src/sim.jl")
 
-ct = .1
-S = 20
-
-global fw
-c = 0
-try
-    while c != ct
-        fw = FoodWeb(nichemodel, 20, C = ct, Z = 4)
-        c = round(connectance(fw), digits = 2)
-    end
-catch
-   fw = missing
-end
-fw
-
 #simCS(C, S, Z, h, c, σₑ, K; max = 50000, last = 25000, dt = 0.1, return_sol = false)
 ti = simCS(0.1, 20, 100, 2.0, 1.0, 1.0, 5; max = 5000, last = 1000, dt = 0.1, return_sol = false)
 plot(ti, idxs = collect(1:1:length(get_parameters(ti).network.species)))
@@ -39,85 +24,52 @@ get_parameters(ti)
 
 
 
-
-fw = FoodWeb([0 0 0; 1 0 0; 0 1 0])
-p = ModelParameters(fw, functional_response = BioenergeticResponse(fw, h = 2, c = 1), env_stoch = EnvStoch(.3))
+# fw = FoodWeb([0 0 0; 1 0 0; 0 1 0], Z = 100)
+fw = FoodWeb([0 0 0; 0 0 0; 0 0 0], Z = 100)
+p = ModelParameters(fw,
+                    functional_response = BioenergeticResponse(fw, h = 2, c = 1),
+                    producer_competition = ProducerCompetition(fw; αij = .5),
+                    env_stoch = EnvStoch(.5),
+                    biorates = BioRates(fw; d = 0.05)
+                   )
 S = size(fw.A, 1)
-
 
 stoch_starting_val = repeat([0], S)
 u0 = [rand(S); stoch_starting_val]
 
 # Make the stochastic matrix
 corr_mat = zeros(S * 2, S * 2)
+corr_mat .= 1.0
 corr_mat[diagind(corr_mat)] .= 1.0
 # Generate the Wiener Process
 wiener = CorrelatedWienerProcess(corr_mat, 0.0, zeros(size(corr_mat, 1)))
 
 prob = SDEProblem(
-                  mydBdt!,
+                  stoch_d_dBdt!,
                   gen_stochastic_process,
                   u0,
-                  [0, 50],
+                  [0, 1000],
[…]

### 2023-01-15 src/sim.jl

@@ -129,15 +129,16 @@ function simCS(C, S, Z, h, c, σₑ, K; max = 50000, last = 25000, dt = 0.1, ret
     out
 end
 
-function sim_int_mat(A; σₑ = .5, alpha_ij = 0, Z = 100, h = 2.0, c = 1.0, K = 1.0, max = 50000, last = 25000, dt = 0.1, return_sol = false)
+function sim_int_mat(A; d = 0, ρ = 0.0, σₑ = .5, alpha_ij = 0, Z = 100, h = 2.0, c = 1.0, K = 1.0, fun = stoch_d_dBdt!, max = 50000, last = 25000, dt = 0.1, return_sol = false)
 
-    fw = FoodWeb(A, Z = Z)
-    S = size(A, 1)
+    fw = FoodWeb(A, Z = Z, quiet = true)
+    S = richness(fw)
 
     # Parameters of the functional response
     funcrep = BioenergeticResponse(fw; h = h, c = c)
     # generate the model parameters
     p = ModelParameters(fw;
+                        biorates = BioRates(fw; d = d),
                         functional_response = funcrep,
                         environment = Environment(fw, K = K),
                         producer_competition = ProducerCompetition(fw, αii = 1.0, αij = alpha_ij),
@@ -147,12 +148,14 @@ function sim_int_mat(A; σₑ = .5, alpha_ij = 0, Z = 100, h = 2.0, c = 1.0, K =
     u0 = [rand(S); stoch_starting_val]
 
     # Make the stochastic matrix
-    corr_mat = Diagonal(repeat([1.0], S * 2))
+    corr_mat = zeros(S * 2, S * 2)
+    corr_mat .= ρ
+    corr_mat[diagind(corr_mat)] .= 1.0
     # Generate the Wiener Process
     wiener = CorrelatedWienerProcess(corr_mat, 0.0, zeros(size(corr_mat, 1)))
 
     prob = SDEProblem(
-                      mydBdt!,
+                      fun,
                       gen_stochastic_process,
                       u0,
                       [0, max],
@@ -175,7 +178,44 @@ function sim_int_mat(A; σₑ = .5, alpha_ij = 0, Z = 100, h = 2.0, c = 1.0, K =
         return m
     end
 
-    if length(m.t) == max + 1
+    out = get_stab_fw(m; last = last)
+
+    out = merge(
+                (S = S, rho = ρ, env_stoch = σₑ, alpha_ij = alpha_ij, Z = Z),
[…]

### 2023-01-15 src/stochastic_mortality_model.jl

@@ -1,22 +1,27 @@
 function mydBdt!(dB, B, params::ModelParameters, t)
 
+    # params, extinct_sp = p # unpack input
+
     # Set up - Unpack parameters
-    S = length(params.network.species)
+    S = richness(params.network)
     response_matrix = params.functional_response(B[1:S], params.network)
     r = params.biorates.r # vector of intrinsic growth rates
+    d = params.biorates.d # vector of natural death
     K = params.environment.K # vector of carrying capacities
+    α = params.producer_competition.α # matrix of producer competition
     network = params.network
     θ = 1
 
-    # Compute ODE terms for each species
+
     for i in 1:S
-        growth = BEFWM2.logisticgrowth(i, B[1:S], r[i], K[i], network)
-        eating, being_eaten = BEFWM2.consumption(i, B[1:S], params, response_matrix)
-        # Metabolic loss as basal mortality times exponentional stochastic noise
+        # sum(α[i, :] .* B)) measures competitive effects (s)
+        growth = BEFWM2.logisticgrowth(i, B, r[i], K[i], sum(α[i, :] .* B[1:S]), network)
+        eating, being_eaten = BEFWM2.consumption(i, B, params, response_matrix)
         metabolism_loss = params.biorates.x[i] * exp(B[i+S]) * B[i]
+        natural_death = BEFWM2.natural_death_loss(i, B, params)
         net_growth_rate = growth + eating - metabolism_loss
-        # net_growth_rate = BEFWM2.effect_competition(net_growth_rate, i, B, network)
-        dB[i] = net_growth_rate - being_eaten
+        # net_growth_rate = effect_competition(net_growth_rate, i, B, network)
+        dB[i] = net_growth_rate - being_eaten - natural_death
     end
 
     # Compute stochastic mortality variable for all species
@@ -24,6 +29,52 @@ function mydBdt!(dB, B, params::ModelParameters, t)
         # Ornstein-Uhlenbeck process
         dB[i] = θ * (0 - B[i])
     end
+
+    # Avoid zombie species by forcing extinct biomasses to zero.
+    # https://github.com/BecksLab/BEFWM2/issues/65
+    # for sp in keys(extinct_sp)
+        # B[sp] = 0.0
+    # end
+end
+
+function stoch_d_dBdt!(dB, B, params::ModelParameters, t)
+
+    # params, extinct_sp = p # unpack input
+
+    # Set up - Unpack parameters
+    S = richness(params.network)
[…]

### 2023-01-15 use_case/module.jl

@@ -4,14 +4,28 @@
 
 
 import Pkg
-Pkg.activate(".")
-using BEFWM2, LinearAlgebra, DifferentialEquations, DataFrames, CSV, Distributed, Distributions, ProgressMeter, BenchmarkTools
-using Plots, SparseArrays
-using Arrow
+Pkg.instantiate()
+using Distributed, Serialization
 
-include("src/stochastic_mortality_model.jl")
-include("src/sim.jl")
-include("src/interaction_strength.jl")
+ncpu = length(Sys.cpu_info())
+
+#Flag enables all the workers to start on the project of the current dir
+flag = "--project=~/xStressorsStabBEFW/"
+#flag = "--project=."
+println("Workers run with flag: $(flag)")
+#addprocs(ncpu - 2, exeflags=flag)
+addprocs(5, exeflags=flag)
+println("Using $(ncpu -2) cores")
+
+@everywhere import Pkg
+@everywhere using DifferentialEquations, BEFWM2, Distributions, ProgressMeter, SparseArrays, LinearAlgebra, DataFrames, CSV, Arrow
+@everywhere include("../src/stochastic_mortality_model.jl")
+@everywhere include("../src/sim.jl")
+@everywhere include("../src/interaction_strength.jl")
+
+# include("src/stochastic_mortality_model.jl")
+# include("src/sim.jl")
+# include("src/interaction_strength.jl")
 
 import Random.seed!
 
@@ -61,35 +75,36 @@ param = ModelParameters(foodweb,
                       )
 
 #sim_int_mat(A; σₑ = .5, alpha_ij = 0, Z = 100, h = 2.0, c = 1.0, K = 1.0, max = 50000, last = 25000, dt = 0.1, return_sol = false)
-sim = map(x -> sim_int_mat(x, .5, .5; Z = 100, h = 2.0, c = 1.0, K = 3, max = 5000, last = 1000, dt = 0.1, return_sol = false), fw_module)
+#
+sim = map(x -> sim_int_mat(x;
+                                 ρ = 0, alpha_ij = 1.0,
+                                 σₑ = .5,
+                                 d = 0.1,
+                                 Z = 100, h = 2.0, c = 1.0, K = 3.0,
+                                 fun = stoch_d_dBdt!,
+                                 max = 1000, last = 100, dt = 0.1, return_sol = false)
+                     , fw_module)
 
-rep = 1:20
+rep = 1:50
 fw_module_names = keys(fw_module)
-Z = [5, 10, 100]
-sigma = 0.5:1
[…]

### 2023-01-19 report/cs_analysis.Rmd
Simulations filtered by faisability of FW (C/S) + test garbage collector

@@
 ---
-title: big sim
+title: Simulation connectance richness
 author: Alain Danet
@@
 
-```{r}
+```{r, echo = FALSE}
+knitr::opts_chunk$set(
+  cache = FALSE,
+  collapse = TRUE,
+  comment = "#>",
+  #fig.dim = c(7, 7),
+  fig.fullwidth = TRUE,
+  fig.show = "hold",
+  echo = FALSE,
+  message = FALSE,
+  warning = FALSE,
+  results = TRUE,
+  fig.path="figures/"
+)
+```
+
+```{r, results = FALSE}
 library(tidyverse)
 library(magrittr)
+library(cowplot)
+library(here)
+
+mytheme <- theme_cowplot(font_size = 8) +
+background_grid() +
+theme(legend.position = "bottom")
+
+theme_set(mytheme)
 ```
@@
   select(where(is.double))
+summary(df)
 ```
@@
 ```{r}
-summary(df)
-
 df %>%
   filter(stab_com <= 1000) %>%
-  ggplot(aes(x = as.factor(richness), y = stab_com, color = as.factor(ct))) +
-  geom_boxplot()
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  ggplot(aes(x = as.factor(richness), y = stab, color = as.factor(ct))) +
+  geom_boxplot() +
+  facet_grid(rows = vars(metric), scales = "free_y") +
+  labs(
+    color = "Connectance",
+    x = "Species richness",
+    y = "Stability component"
+  )
 ```
@@
 ```
+
+- Main results:
+  - Stability increases with richness but not connectance (no overall effect)
+  - Richness increases stability by increasing maximum and average trophic
+    level, but also by decreasing interaction strength and increasing asymetry
+    in trophic interaction, and finally by increasing total biomass (I need to control for that).
+  - Synchrony decreases with species richness, max and average trophic level but increases with
+    average interaction strength and symetry of interaction distributions.
+  - Population varibility decreases with species richness, average and maximum
+    trophic level, asymetry of interaction strength but it is increased by
+    average interaction strength
+  - Same effects of food-web structure on both Synchrony and Population variability
+    - Surpringly, as in Danet et al. (2021), connectance has little effect on
+      temporal stability and its components!
+
+# Covariation
+
+It seems that the effects of food-web structure are mainly richness effects!
+
+```{r}
+df %>%
+  filter(stab_com <= 1000) %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  ggplot(aes(x = avg_max_int, y = stab, color = as.factor(richness))) +
+  geom_point() +
+  geom_smooth() +
+  facet_grid(rows = vars(metric), scales = "free_y") +
+  labs(
+    color = "Richness",
+    x = "Avg interaction strength",
+    y = "Stability component"
+  )
+
+```
+
+```{r}
+df %>%
+  filter(stab_com <= 1000) %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  ggplot(aes(x = gini_max_int, y = stab, color = as.factor(richness))) +
+  geom_point() +
+  geom_smooth() +
+  facet_grid(rows = vars(metric), scales = "free_y") +
+  labs(
+    color = "Richness",
+    x = "Gini interaction strength",
+    y = "Stability component"
+  )
+
+```
+
+```{r}
+df %>%
+  filter(stab_com <= 1000) %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  ggplot(aes(x = ct, y = stab, color = as.factor(richness))) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_grid(rows = vars(metric), scales = "free_y") +
+  labs(
+    color = "Richness",
+    x = "Connectance",
+    y = "Stability component"
+  )
+```
+
+```{r}
+df %>%
+  filter(stab_com <= 1000) %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  ggplot(aes(x = w_avg_tlvl, y = stab, color = as.factor(richness))) +
+  geom_point() +
+  geom_smooth() +
+  facet_grid(rows = vars(metric), scales = "free_y") +
+  labs(
+    color = "Richness",
+    x = "Avg trophic level",
+    y = "Stability component"
+  )
+```

### 2023-01-19 report/module_analysis.Rmd
Simulations filtered by faisability of FW (C/S) + test garbage collector

--- 2023-01-14 report/module_analysis.Rmd
@@
 date: 2022-09-12
-format:
-  html:
-    embed-resources: false
+output:
+  bookdown::pdf_document2
 ---
 
-```{r}
-library(arrow)
+```{r, echo = FALSE}
+knitr::opts_chunk$set(
+  cache = FALSE,
+  collapse = TRUE,
+  comment = "#>",
+  #fig.dim = c(7, 7),
+  fig.fullwidth = TRUE,
+  fig.show = "hold",
+  echo = FALSE,
+  message = FALSE,
+  warning = FALSE,
+  results = TRUE,
+  fig.path="figures/"
+)
+```
+
+```{r, results = FALSE}
 library(tidyverse)
 library(magrittr)
+library(cowplot)
+library(here)
+library(arrow)
+
+mytheme <- theme_cowplot(font_size = 8) +
+background_grid() +
+theme(legend.position = "bottom")
+
+theme_set(mytheme)
 ```
@@
 ```
+
+# Stochastic natural death
+
+## Competition
+
+```{r}
+comp_brut <- open_dataset(here::here("res", "sim_module_competition.arrow"), format = "arrow")
+comp <- comp_brut %>%
+  collect()
+colnames(comp)
+```
+
+```{r, eval = FALSE}
+unique(comp$env_stoch)
+summary(comp$total_biomass)
+```
+
+```{r}
+comp %>%
+  filter(env_stoch == 0.5) %>%
+  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
+  "values") %>%
+  ggplot(aes(x = as.factor(richness), y = values, color = as.factor(alpha_ij))) +
+  geom_boxplot() +
+  facet_grid(
+    rows = vars(stab), cols = vars(rho),
+    scales = "free_y") +
+  labs(x = "Species richness", y = "Stability component", color = "Interspecific competition")
+```
+
+- Main results:
+  - Species richness increases stability
+  - Interspecific competition does not affect stability expect when
+    interspecific competition equals to intraspecific competition (decrease the effect of species richness).
+  - Interspecific competition desynchronises primary producers but increases
+    varibility
+  - The decrease of response diversity decreases the effect of species richness on stability
+  - The decrease of response diversity increase synchrony but decrease
+    population variability
+
+## Modules
+
+```{r}
+mod_brut <- open_dataset(here::here("res", "sim_module_d.arrow"), format = "arrow")
+mod <- mod_brut %>%
+  collect() %>%
+  select(where(is.numeric) | starts_with("module"))
+colnames(mod)
+```
+
+```{r, eval = FALSE}
+unique(mod$env_stoch)
+summary(as_tibble(mod))
+```
+
+```{r}
+mod %>%
+  filter(rho == 0, env_stoch == .5) %>%
+  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
+  "values") %>%
+  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
+  geom_boxplot() +
+  facet_grid(rows = vars(stab), scales = "free_y")
+
+```
+
+```{r}
+mod %>%
+  filter(rho == 0.5, env_stoch == .5) %>%
+  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
+  "values") %>%
+  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
+  geom_boxplot() +
+  facet_grid(rows = vars(stab), scales = "free_y")
+
+```

### 2023-01-19 draft.jl

@@ -7,12 +7,31 @@ using Statistics
 using DataFrames
 using Plots
 using Debugger
-using JSON3
 using CSV
+using Arrow
 include("src/minmax.jl")
 include("src/interaction_strength.jl")
 include("src/stochastic_mortality_model.jl")
 include("src/sim.jl")
+include("src/plot.jl")
+include("src/get_modules.jl")
+
+##########
+#  Plot  #
+##########
+
+webplot(get_fw_modules()[10]; consasrow = true)
+webplot([0 0 0; 1 1 0; 1 1 0]; consasrow = true)
+ti = map(x -> webplot(x; consasrow = true), get_fw_modules())
+length(ti)
+plot(ti..., layout = (4, 4))
+plot(ti[1], ti[2], ti[3], layout = (1, 3))
+plot((ti[i] for i in 1:length(ti))..., layout = (4, 3))
+
+#########
+#  Sim  #
+#########
+
 
 #simCS(C, S, Z, h, c, σₑ, K; max = 50000, last = 25000, dt = 0.1, return_sol = false)
 ti = simCS(0.1, 20, 100, 2.0, 1.0, 1.0, 5; max = 5000, last = 1000, dt = 0.1, return_sol = false)

### 2023-01-19 job/cs_sharc.sh

@@ -1,0 +1,21 @@
+#!/bin/bash
+
+
+# Job name
+#$ -N cs
+
+# Error message
+#$ -e cs.error
+#$ -o cs.out
+
+# Amount of RAM requested per node
+#$ -l rmem=64G
+
+# Replace by the path to the folder where your script lives if necessary
+DIR_ENV=/home/${USER}/xStressorsStabBEFW
+DIR_SCRIPT=scripts
+
+# Load modules
+module load apps/julia
+
+cd ${DIR_ENV} && julia --project=${DIR_ENV} ${DIR_ENV}/${DIR_SCRIPT}/connectance_richness_stoch.jl ${DIR_ENV}

### 2023-01-19 scripts/connectance_richness_stoch.jl

@@ -1,0 +1,111 @@
+println("Rundir is $(pwd())")
+
+import Pkg
+Pkg.instantiate()
+using Distributed, Serialization
+
+ncpu = length(Sys.cpu_info())
+
+#Flag enables all the workers to start on the project of the current dir
+flag = "--project=~/xStressorsStabBEFW/"
+#flag = "--project=."
+println("Workers run with flag: $(flag)")
+addprocs(ncpu - 2, exeflags=flag)
+#addprocs(5, exeflags=flag)
+println("Using $(ncpu -2) cores")
+
+@everywhere import Pkg
+@everywhere using DifferentialEquations, BEFWM2, Distributions, ProgressMeter, SparseArrays, LinearAlgebra, DataFrames
+@everywhere using StatsBase, CSV, Arrow
+@everywhere include("../src/stochastic_mortality_model.jl")
+@everywhere include("../src/sim.jl")
+@everywhere include("../src/interaction_strength.jl")
+
+import Random.seed!
+
+seed!(22)
+
+rep = 1:50
+S = [5, 10, 20, 40, 80, 100]
+C = 0.02:.05:.32
+sigma = [0.5, 1.0]
+ρ = [0, .5, 1]
+names = (:rep, :richness, :connectance, :sigma, :rho)
+param = map(p -> (;Dict(k => v for (k, v) in zip(names, p))...), Iterators.product(rep, S, C, sigma, ρ))[:]
+
+
+# Filter impossible combination of C/S
+limitCS = (
+           S = S,
+           Cmin = round.([(i - 1)/ i^2 + .01 for i in S], digits = 2),
+           Cmax = [.32, .31, .24, .15, .09, .07]
+          )
+# Select good combinations
+goodCSparam_v = [
+                 findall(x ->
+                         (x.connectance >= limitCS.Cmin[i] && x.connectance <= limitCS.Cmax[i]) && x.richness == limitCS.S[i], param)
+                 for i in 1:length(limitCS.S)
+                ]
+goodCSparam_idxs = reduce(vcat, goodCSparam_v)
+bad_param = param[1:length(param) .∉ Ref(goodCSparam_idxs)]
+good_param = param[StatsBase.sample(goodCSparam_idxs, length(goodCSparam_idxs), replace=false)]
+
+# Warm-up
+test_i = 2400
+simCS(bad_param[test_i].connectance, bad_param[test_i].richness;
+      Z = 100,
[…]

### 2023-01-19 scripts/module.jl

@@ -22,6 +22,7 @@ println("Using $(ncpu -2) cores")
 @everywhere include("src/stochastic_mortality_model.jl")
 @everywhere include("src/sim.jl")
 @everywhere include("src/interaction_strength.jl")
+@everywhere include("src/get_modules.jl")
 
 # include("src/stochastic_mortality_model.jl")
 # include("src/sim.jl")
@@ -29,41 +30,7 @@ println("Using $(ncpu -2) cores")
 
 import Random.seed!
 
-fw_module = (
-          # prod = [0 0; 0 0],
-          chain1 = [0 0; 1 0],
-          chain2 = [0 0 0; 1 0 0; 0 1 0],
-          chain3 = [0 0 0 0; 1 0 0 0; 0 1 0 0; 0 0 1 0],
-          chain4 = [0 0 0 0;
-                    1 0 0 0;
-                    0 1 0 0;
-                    0 0 1 0],
-          cons = [0 0 0; 0 0 0; 1 1 0],
-          cons2_spe = [0 0 0 0; 0 0 0 0; 1 0 0 0; 0 1 0 0],
-          cons2_spe_top = [0 0 0 0 0;
-                           0 0 0 0 0;
-                           1 0 0 0 0;
-                           0 1 0 0 0;
-                           0 0 1 1 0],
-          cons3_spe = [0 0 0 0 0 0;
-                       0 0 0 0 0 0;
-                       1 0 0 0 0 0;
-                       0 1 0 0 0 0;
-                       0 0 1 0 0 0;
-                       0 0 0 1 0 0],
-          cons2_gen = [0 0 0 0; 0 0 0 0; 1 1 0 0; 1 1 0 0],
-          cons2_gen_top = [0 0 0 0 0;
-                           0 0 0 0 0;
-                           1 1 0 0 0;
-                           1 1 0 0 0;
-                           0 0 1 1 0],
-          cons3_gen = [0 0 0 0 0 0;
-                       0 0 0 0 0 0;
-                       1 1 0 0 0 0;
-                       1 1 0 0 0 0;
-                       0 0 1 1 0 0;
-                       0 0 1 1 0 0],
-         )
+fw_module = get_fw_modules()
 
 #sim_int_mat(A; σₑ = .5, alpha_ij = 0, Z = 100, h = 2.0, c = 1.0, K = 1.0, max = 50000, last = 25000, dt = 0.1, return_sol = false)
 #

### 2023-01-19 src/get_modules.jl

@@ -1,0 +1,37 @@
+function get_fw_modules()
+    (
+     # prod = [0 0; 0 0],
+     chain1 = [0 0; 1 0],
+     chain2 = [0 0 0; 1 0 0; 0 1 0],
+     chain3 = [0 0 0 0; 1 0 0 0; 0 1 0 0; 0 0 1 0],
+     chain4 = [0 0 0 0;
+               1 0 0 0;
+               0 1 0 0;
+               0 0 1 0],
+     cons = [0 0 0; 0 0 0; 1 1 0],
+     cons2_spe = [0 0 0 0; 0 0 0 0; 1 0 0 0; 0 1 0 0],
+     cons2_spe_top = [0 0 0 0 0;
+                      0 0 0 0 0;
+                      1 0 0 0 0;
+                      0 1 0 0 0;
+                      0 0 1 1 0],
+     cons3_spe = [0 0 0 0 0 0;
+                  0 0 0 0 0 0;
+                  1 0 0 0 0 0;
+                  0 1 0 0 0 0;
+                  0 0 1 0 0 0;
+                  0 0 0 1 0 0],
+     cons2_gen = [0 0 0 0; 0 0 0 0; 1 1 0 0; 1 1 0 0],
+     cons2_gen_top = [0 0 0 0 0;
+                      0 0 0 0 0;
+                      1 1 0 0 0;
+                      1 1 0 0 0;
+                      0 0 1 1 0],
+     cons3_gen = [0 0 0 0 0 0;
+                  0 0 0 0 0 0;
+                  1 1 0 0 0 0;
+                  1 1 0 0 0 0;
+                  0 0 1 1 0 0;
+                  0 0 1 1 0 0],
+    )
+end

### 2023-01-19 src/plot.jl

@@ -1,0 +1,117 @@
+###################################
+#  Gently given from Eva Delmas!  #
+###################################
+
+
+"""
+Plot the interaction matrix :tada: with consumer as either rows or columns :tada:
+whichever you prefer!
+
+    `plot(A, consasrow)`
+
+- use `plot(A, true)` to have consumers in rows
+- use `plot(A, false)` to have consumers in columns
+"""
+function webplot(A::Array{Int64,2}; consasrow = true, z = [], clr = :heat, w = 300, h = 300)
+    S = size(A,1)
+    length(z) != 0 &&  @assert size(z) == (S, S)
+    if !consasrow
+        if length(z) != 0
+            plt = heatmap(z'[end:-1:1,:], c = clr, margin = 5Plots.mm)
+        else
+            z = fill(NaN, S, S)
+            plt = heatmap(z)
+        end
+        floatA = Float64.(A)
+        listA = matrix_to_list(floatA')
+        plt = scatter!(listA[:,2], invert(listA[:,1], S)
+            , ms = 3, c = :black
+            , size = (w,h), leg = false
+            , framestyle = :box, ticks = ([1.5:1:S;], repeat([""], S))
+            , foreground_color_axis = :white
+            , xlims = (0.5,S+0.5), ylims = (0.5,S+0.5))
+        plot!([1,S], [S,1], c = :black, linestyle = :dash)
+        xlabel!("consumers")
+        ylabel!("resources")
+    else
+        if length(z) != 0
+            plt = heatmap(z[end:-1:1,:], c = clr, margin = 5Plots.mm)
+        else
+            z = fill(NaN, S, S)
+            plt = heatmap(z)
+        end
+        floatA = Float64.(A)
+        listA = matrix_to_list(floatA)
+        plt = scatter!(listA[:,2], invert(listA[:,1],S)
+            , ms = 3, c = :black
+            , size = (w,h), leg = false
+            , framestyle = :box, ticks = ([1.5:1:S;], repeat([""], S))
+            , foreground_color_axis = :white
+            , xlims = (0.5,S+0.5), ylims = (0.5,S+0.5))
+        plot!([1,S], [S,1], c = :black, linestyle = :dash)
+        ylabel!("consumers")
+        xlabel!("resources")
+    end
+    return plt
+end
+
[…]

### 2023-01-19 src/sim.jl

@@ -1,14 +1,26 @@
-function simCS(C, S, Z, h, c, σₑ, K; max = 50000, last = 25000, dt = 0.1, return_sol = false)
+function simCS(C, S;
+        Z = 100,
+        d = 0, σₑ = .5, ρ = 0.0,
+        h = 2.0, c = 1.0,
+        r = 1.0, K = 1.0, alpha_ij = 0.5,
+        max = 5000, last = 1000, dt = 0.1,
+        fun = stoch_d_dBdt!,
+        return_sol = false,
+        K_alpha_corrected = true,
+        Ctol = .02,
+        gc_thre = .02
+    )
+
+    if rand(Uniform(0, 1)) < gc_thre
+        println("")
+        GC.gc()
+        ccall(:malloc_trim, Cvoid, (Cint,), 0)
+        GC.safepoint()
+    end
 
     # Generate a food-web with a given connectance
     fw = try
-        global tmp_fw
-        ct = 0
-        while ct != C
-            tmp_fw = FoodWeb(nichemodel, S, C = C, Z = Z)
-            ct = round(connectance(tmp_fw), digits = 2)
-        end
-        tmp_fw
+        FoodWeb(nichemodel, S, C = C, Z = Z, tol = Ctol)
     catch
         missing
     end
@@ -21,21 +33,34 @@ function simCS(C, S, Z, h, c, σₑ, K; max = 50000, last = 25000, dt = 0.1, ret
     if !ismissing(fw)
         # Parameters of the functional response
         funcrep = BioenergeticResponse(fw; h = h, c = c)
+        # Carrying capacity
+        env = Environment(fw,
+                          K = if K_alpha_corrected
+                              nprod = length(producers(fw))
+                              # Loreau & de Mazancourt (2008), Ives et al. (1999)
+                              K * (1 + (alpha_ij * (nprod - 1))) / nprod
+                          else
+                              K
+                          end
+                         )
         # generate the model parameters
         p = ModelParameters(fw;
+                            biorates = BioRates(fw; r = r, d = d),
                             functional_response = funcrep,
-                            environment = Environment(fw, K = K/length(BEFWM2.producers(fw))),
+                            environment = env,
+                            producer_competition = ProducerCompetition(fw, αii = 1.0, αij = alpha_ij),
                             env_stoch = EnvStoch(σₑ))
         stoch_starting_val = repeat([0], S)
         u0 = [rand(S); stoch_starting_val]
 
[…]

### 2023-01-19 use_case/connectance_richness_stoch.jl

@@ -14,60 +14,149 @@ println("Workers run with flag: $(flag)")
 addprocs(5, exeflags=flag)
 println("Using $(ncpu -2) cores")
 
-@everywhere import Pkg
-@everywhere using DifferentialEquations, BEFWM2, Distributions, ProgressMeter, SparseArrays, LinearAlgebra, DataFrames, CSV
-@everywhere include("../src/stochastic_mortality_model.jl")
-@everywhere include("../src/sim.jl")
-@everywhere include("../src/interaction_strength.jl")
-# @everywhere include("src/stochastic_mortality_model.jl")
-# @everywhere include("src/sim.jl")
-# @everywhere include("src/interaction_strength.jl")
+import Pkg
+using DifferentialEquations, BEFWM2, Distributions, ProgressMeter, SparseArrays, LinearAlgebra, DataFrames, CSV
+using StatsBase
+include("src/stochastic_mortality_model.jl")
+include("src/sim.jl")
+include("src/interaction_strength.jl")
 
 import Random.seed!
 
 seed!(22)
 
-ti = simCS(.1, 10, 100, 2.0, 1.0, 0.5, 5; max = 50, last = 10, dt = 0.1, return_sol = false)
+ti = simCS(.4, 90;
+           Z = 100,
+           d = 0.1, σₑ = .5, ρ = 0.0,
+           h = 2.0, c = 1.0,
+           r = 1.0, K = 1.0, alpha_ij = 0.5,
+           max = 50, last = 10, dt = 0.1,
+           fun = stoch_d_dBdt!,
+           K_alpha_corrected = true,
+           return_sol = false
+          )
+
+# Max
+FoodWeb(nichemodel, 5, C = .32, tol = .01)
+# Min
+FoodWeb(nichemodel, 5, C = .16, tol = .01)
+
+# Max
+FoodWeb(nichemodel, 10, C = .31, tol = .01)
+# Min
+FoodWeb(nichemodel, 10, C = .09, tol = .01)
+
+# Max
+FoodWeb(nichemodel, 20, C = .24, tol = .01)
+# Min
+FoodWeb(nichemodel, 20, C = .05, tol = .01)
+
+# Max
+FoodWeb(nichemodel, 40, C = .15, tol = .01)
+# Min
+FoodWeb(nichemodel, 40, C = .03, tol = .01)
+
+# Max
[…]

### 2023-01-31 report/cs_analysis.Rmd
Add varying Z for various interaction strengths

@@
 ```
+
+# SEM
+
+```{r}
+library(piecewiseSEM)
+library(semEff)
+```
+
+```{r}
+df_sem <- df %>%
+  filter(stab_com < 1000) %>%
+  mutate(across(c(sync, avg_cv_sp, stab_com, richness, avg_max_int, gini_max_int), log, , .names = "log_{.col}"))
+```
+
+```{r}
+pairs(
+  df_sem %>%
+    select(ct, log_richness, max_tlvl,
+      log_gini_max_int, log_avg_max_int, log_sync,
+      log_avg_cv_sp, log_stab_com),
+    pch = 19)
+```
+
+```{r}
+sem_list <- list(
+  max_tlvl = lm(max_tlvl ~ log_richness + ct, df_sem),
+  gini_max_int = lm(gini_max_int ~ log_richness + ct + max_tlvl, df_sem),
+  log_avg_max_int = lm(log_avg_max_int ~ log_richness + ct + max_tlvl, df_sem),
+  log_sync = lm(log_sync ~ ct + log_richness + max_tlvl + gini_max_int, df_sem),
+  log_avg_cv_sp = lm(log_avg_cv_sp ~ ct + log_richness + max_tlvl +  gini_max_int, df_sem),
+  log_stab_com = lm(log_stab_com ~ log_sync + log_avg_cv_sp, df_sem)#~,
+  #log_avg_max_int %~~% log_richness
+)
+
+sem <- as.psem(sem_list)
+```
+
+```{r}
+map_dfr(setNames(sem_list, names(sem_list)), performance::check_collinearity)
+map_dfr(sem_list, rsquared)
+summary(sem)
+```
+
+```{r}
+plot(sem)
+```
+
+```{r}
+boot_eff <- semEff(sem, R = 50, ci.type =  "perc")
+summary(boot_eff)
+```
+
+```{r}
+sem_int_list <- list(
+  max_tlvl = lm(max_tlvl ~ log_richness + ct, df_sem),
+  gini_max_int = lm(gini_max_int ~ log_richness + ct + max_tlvl, df_sem),
+  log_avg_max_int = lm(log_avg_max_int ~ log_richness + ct + max_tlvl, df_sem),
+  log_sync = lm(log_sync ~ log_richness + log_avg_max_int + gini_max_int, df_sem),
+  log_avg_cv_sp = lm(log_avg_cv_sp ~ log_richness + log_avg_max_int + gini_max_int, df_sem),
+  log_stab_com = lm(log_stab_com ~ log_sync + log_avg_cv_sp, df_sem)
+)
+
+sem_int <- as.psem(sem_int_list)
+plot(sem_int)
+```
+
+```{r}
+map(setNames(sem_int_list, names(sem_int_list)), performance::check_collinearity)
+map_dfr(sem_list, rsquared)
+summary(sem)
+```
+
+```{r}
+boot_int <- semEff(sem_int, R = 50, ci.type =  "perc")
+summary(boot_int)
+```

### 2023-01-31 report/module_analysis.Rmd
Add varying Z for various interaction strengths

--- 2023-01-14 report/module_analysis.Rmd
@@
 ---
-title: big stoch sim
+title: Module analysis
 author: alain
 date: 2022-09-12
-format:
-  html:
-    embed-resources: false
+output:
+  bookdown::pdf_document2
 ---
 
-```{r}
-library(arrow)
+```{r, echo = FALSE}
+knitr::opts_chunk$set(
+  cache = FALSE,
+  collapse = TRUE,
+  comment = "#>",
+  #fig.dim = c(7, 7),
+  fig.fullwidth = TRUE,
+  fig.show = "hold",
+  echo = FALSE,
+  message = FALSE,
+  warning = FALSE,
+  results = TRUE,
+  fig.path="figures/"
+)
+```
+
+```{r, results = FALSE}
 library(tidyverse)
 library(magrittr)
+library(cowplot)
+library(here)
+library(arrow)
+
+mytheme <- theme_cowplot(font_size = 8) +
+background_grid() +
+theme(legend.position = "bottom")
+
+theme_set(mytheme)
+```
+
+# Stochastic natural death
+
+## Competition
+
+```{r}
+comp_brut <- open_dataset(here::here("res", "sim_module_competition.arrow"), format = "arrow")
+comp <- comp_brut %>%
+  collect() %>%
+  select(where(is.double))
+colnames(comp)
+```
+
+```{r, eval = FALSE}
+unique(comp$env_stoch)
+summary(comp$total_biomass)
 ```
@@
 ```{r}
-pq_brut <- open_dataset(here::here("res", "sim_module.arrow"), format = "arrow")
-df <- pq_brut %>%
-  collect()
-colnames(df)
+comp %>%
+  filter(env_stoch == 0.9) %>%
+  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
+  "values") %>%
+  ggplot(aes(x = as.factor(richness), y = values, color = as.factor(alpha_ij))) +
+  geom_boxplot() +
+  facet_grid(
+    rows = vars(stab), cols = vars(rho),
+    scales = "free_y") +
+  labs(x = "Species richness", y = "Stability component", color = "Interspecific competition")
+```
+
+- Main results:
+  - Species richness increases stability
+  - Interspecific competition does not affect stability expect when
+    interspecific competition equals to intraspecific competition (decrease the effect of species richness).
+  - Interspecific competition desynchronises primary producers but increases
+    varibility
+  - The decrease of response diversity decreases the effect of species richness on stability
+  - The decrease of response diversity increase synchrony but decrease
+    population variability
+
+## Modules
+
+```{r}
+mod_brut <- open_dataset(here::here("res", "sim_module_d.arrow"), format = "arrow")
+mod <- mod_brut %>%
+  collect() %>%
+  select(where(is.numeric) | starts_with("module")) %>%
+  filter(richness / S == 1.0)
+colnames(mod)
+```
+
+```{r, eval = FALSE}
+unique(mod$env_stoch)
+summary(as_tibble(mod))
 ```
@@
 ```{r}
-df %>%
+mod %>%
+  filter(rho == 0, env_stoch == .9) %>%
   pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
   "values") %>%
-  ggplot(aes(x = module, y = values, color = as.factor(alphaij))) +
-  geom_boxplot()+
-  facet_grid(
-    rows = vars(stab),
-    scales = "free_y")
+  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
+  geom_boxplot() +
+  facet_grid(rows = vars(stab), scales = "free_y")
 ```
+
+```{r}
+mod %>%
+  filter(rho == 0.5, env_stoch == .9) %>%
+  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
+  "values") %>%
+  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
+  geom_boxplot() +
+  facet_grid(rows = vars(stab), scales = "free_y")
+
+```
+
+```{r}
+mod %>%
+  filter(rho == 1, env_stoch == .9) %>%
+  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
+  "values") %>%
+  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
+  geom_boxplot() +
+  facet_grid(rows = vars(stab), scales = "free_y")
+```

### 2023-01-31 draft.jl

@@ -16,6 +16,51 @@ include("src/sim.jl")
 include("src/plot.jl")
 include("src/get_modules.jl")
 
+function kuramoto_module()
+    (
+    prod_gen_k3 = [0 0 0 0 0 0;
+                   0 0 0 0 0 0;
+                   0 0 0 0 0 0;
+                   1 1 1 0 0 0;
+                   1 1 1 0 0 0;
+                   1 1 1 0 0 0],
+
+    prod_spe_km3 = [0 0 0 0 0 0;
+                    0 0 0 0 0 0;
+                    0 0 0 0 0 0;
+                    1 0 0 0 0 0;
+                    0 1 0 0 0 0;
+                    0 0 1 0 0 0],
+
+    prod_spe_km1 = [0 0 0 0 0 0;
+                    0 0 0 0 0 0;
+                    0 0 0 0 0 0;
+                    1 1 0 0 0 0;
+                    1 1 0 0 0 0;
+                    0 0 1 0 0 0],
+
+    prod_spe_k1 = [0 0 0 0 0 0;
+                   0 0 0 0 0 0;
+                   0 0 0 0 0 0;
+                   1 1 1 0 0 0;
+                   1 1 0 0 0 0;
+                   1 0 1 0 0 0],
+   )
+end
+
+###########
+#  Motif  #
+###########
+
+fw = FoodWeb(nichemodel, 20, C = .05)
+fw = FoodWeb(nichemodel, 80, C = .05)
+EcologicalNetworks.find_motif(fw.A, unipartitemotifs().S1)
+mot = find_motif(UnipartiteNetwork(fw.A), unipartitemotifs().S1) |> length
+map(x -> find_motif(UnipartiteNetwork(fw.A), x) |> length, unipartitemotifs())
+
+# Diamond
+map(x -> find_motif(UnipartiteNetwork([0 0 0 0; 1 0 0 0; 1 0 0 0; 0 1 1 0] .> 0), x) |> length, unipartitemotifs())
+
 ##########
 #  Plot  #
 ##########
@@ -31,7 +76,6 @@ plot((ti[i] for i in 1:length(ti))..., layout = (4, 3))
 #########
 #  Sim  #
 #########
-
 
 #simCS(C, S, Z, h, c, σₑ, K; max = 50000, last = 25000, dt = 0.1, return_sol = false)
 ti = simCS(0.1, 20, 100, 2.0, 1.0, 1.0, 5; max = 5000, last = 1000, dt = 0.1, return_sol = false)

### 2023-01-31 scripts/connectance_richness_stoch.jl

@@ -25,13 +25,14 @@ import Random.seed!
 
 seed!(22)
 
-rep = 1:40
+rep = 1:20
 S = [5, 10, 20, 40, 60]
 C = 0.02:.05:.32
 sigma = [0.5, 1.0]
+Z = [10, 1000]
 ρ = [0, .5, 1]
-names = (:rep, :richness, :connectance, :sigma, :rho)
-param = map(p -> (;Dict(k => v for (k, v) in zip(names, p))...), Iterators.product(rep, S, C, sigma, ρ))[:]
+names = (:rep, :richness, :connectance, :Z, :sigma, :rho)
+param = map(p -> (;Dict(k => v for (k, v) in zip(names, p))...), Iterators.product(rep, S, C, Z, sigma, ρ))[:]
 
 
 # Filter impossible combination of C/S
@@ -63,33 +64,13 @@ simCS(bad_param[test_i].connectance, bad_param[test_i].richness;
       return_sol = false
      )
 
-### TEST
-#
-timing = @elapsed sim = @showprogress pmap(p ->
-                         merge(
-                               (rep = p.rep, ),
-                               simCS(p.connectance, p.richness;
-                                     Z = 100,
-                                     d = 0.1, σₑ = p.sigma, ρ = p.rho,
-                                     h = 2.0, c = 1.0,
-                                     r = 1.8, K = 20.0,
-                                     alpha_ij = 0.5,
-                                     max = 5000, last = 100, dt = 0.1,
-                                     fun = stoch_d_dBdt!,
-                                     K_alpha_corrected = true,
-                                     return_sol = false,
-                                     gc_thre = .2
-                                    )
-                              ),
-                         good_param[[1, 2]]
-                        )
 println("$(length(sim)) simulations took $(round(timing / 60, digits = 2)) minutes to run")
 
 timing = @elapsed sim = @showprogress pmap(p ->
                          merge(
                                (rep = p.rep, ),
                                simCS(p.connectance, p.richness;
-                                     Z = 100,
+                                     Z = p.Z,
                                      d = 0.1, σₑ = p.sigma, ρ = p.rho,
                                      h = 2.0, c = 1.0,
                                      r = 1.8, K = 20.0,
@@ -108,4 +89,4 @@ timing = @elapsed sim = @showprogress pmap(p ->
 df = DataFrame(sim)
[…]

### 2023-01-31 src/get_modules.jl

@@ -2,14 +2,28 @@ function get_fw_modules()
     (
      # prod = [0 0; 0 0],
      chain1 = [0 0; 1 0],
-     chain2 = [0 0 0; 1 0 0; 0 1 0],
-     chain3 = [0 0 0 0; 1 0 0 0; 0 1 0 0; 0 0 1 0],
-     chain4 = [0 0 0 0;
+     chain2 = [0 0 0;
+               1 0 0;
+               0 1 0],
+     chain3 = [0 0 0 0;
                1 0 0 0;
                0 1 0 0;
                0 0 1 0],
-     cons = [0 0 0; 0 0 0; 1 1 0],
-     cons2_spe = [0 0 0 0; 0 0 0 0; 1 0 0 0; 0 1 0 0],
+     chain4 = [0 0 0 0 0;
+               1 0 0 0 0;
+               0 1 0 0 0;
+               0 0 1 0 0;
+               0 0 0 1 0],
+     chain5 = [0 0 0 0 0 0;
+               1 0 0 0 0 0;
+               0 1 0 0 0 0;
+               0 0 1 0 0 0;
+               0 0 0 1 0 0;
+               0 0 0 0 1 0],
+     cons2_spe = [0 0 0 0;
+                  0 0 0 0;
+                  1 0 0 0;
+                  0 1 0 0],
      cons2_spe_top = [0 0 0 0 0;
                       0 0 0 0 0;
                       1 0 0 0 0;
@@ -21,7 +35,13 @@ function get_fw_modules()
                   0 1 0 0 0 0;
                   0 0 1 0 0 0;
                   0 0 0 1 0 0],
-     cons2_gen = [0 0 0 0; 0 0 0 0; 1 1 0 0; 1 1 0 0],
+     cons = [0 0 0;
+             0 0 0;
+             1 1 0],
+     cons2_gen = [0 0 0 0;
+                  0 0 0 0;
+                  1 1 0 0;
+                  1 1 0 0],
      cons2_gen_top = [0 0 0 0 0;
                       0 0 0 0 0;
                       1 1 0 0 0;

### 2023-01-31 use_case/connectance_richness_stoch.jl

@@ -81,10 +81,11 @@ FoodWeb(nichemodel, 80, C = .02, tol = .01)
 #
 #
 #
-rep = 1:50
-S = [5, 10, 20, 40, 80, 100]
+rep = 1:30
+S = [5, 10, 20, 40, 60]
 C = 0.02:.05:.32
 sigma = 0.5
+Z = [10, 100, 1000]
 ρ = [0, .5, 1]
 names = (:rep, :richness, :connectance, :sigma, :rho)
 param = map(p -> (;Dict(k => v for (k, v) in zip(names, p))...), Iterators.product(rep, S, C, sigma, ρ))[:]

### 2023-01-31 report/module_analysis.Rmd
Add modules + Z variation

@@
 
+### low Stochasticity (sigma = .5)
+
+```{r}
+mod %>%
+  filter(rho == 0, env_stoch == .5) %>%
+  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
+  "values") %>%
+  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
+  geom_boxplot() +
+  facet_grid(rows = vars(stab), scales = "free_y")
+```
+
+```{r}
+mod %>%
+  filter(rho == 0.5, env_stoch == .5) %>%
+  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
+  "values") %>%
+  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
+  geom_boxplot() +
+  facet_grid(rows = vars(stab), scales = "free_y")
+```
+
+```{r}
+mod %>%
+  filter(rho == 1, env_stoch == .5) %>%
+  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
+  "values") %>%
+  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
+  geom_boxplot() +
+  facet_grid(rows = vars(stab), scales = "free_y")
+```
+
+### low Stochasticity (sigma = .9)
+
 ```{r}
@@
   facet_grid(rows = vars(stab), scales = "free_y")
-
 ```

### 2023-01-31 scripts/module.jl

@@ -46,10 +46,11 @@ sim = map(x -> sim_int_mat(x;
 rep = 1:20
 fw_module_names = keys(fw_module)
 ρ = [0.0, .5, 1.0]
-alphaij = [0.0, .5, 1]
-sigma = [0.5, 0.9]
-param_names = (:rep, :module, :rho, :alphaij,:sigma)
-param = map(p -> (;Dict(k => v for (k, v) in zip(param_names, p))...), Iterators.product(rep, fw_module_names, ρ, alphaij, sigma))[:]
+alphaij = [0.0, .5, .8, 1]
+sigma = [0, 0.5, .8]
+Z = [5, 10, 100]
+param_names = (:rep, :module, :rho, :alphaij,:sigma, :Z)
+param = map(p -> (;Dict(k => v for (k, v) in zip(param_names, p))...), Iterators.product(rep, fw_module_names, ρ, alphaij, sigma, Z))[:]
 
 sim = @showprogress pmap(p -> merge(
                      (rep = p.rep, module_name = p.module),
@@ -57,7 +58,7 @@ sim = @showprogress pmap(p -> merge(
                                  ρ = p.rho, alpha_ij = p.alphaij,
                                  σₑ = p.sigma,
                                  d = 0.1,
-                                 Z = 10, h = 2.0, c = 1.0,
+                                 Z = p.Z, h = 2.0, c = 1.0,
                                  r = 1.8, K = 20.0,
                                  fun = stoch_d_dBdt!,
                                  max = 5000, last = 1000, dt = 0.1, return_sol = false)
@@ -66,34 +67,4 @@ sim = @showprogress pmap(p -> merge(
                         )
 
 df = DataFrame(sim)
-Arrow.write("sim_module_d.arrow", df)
-
-################################################################################
-#                             Competition modules                              #
-################################################################################
-
-rep = 1:20
-S = 1:10
-ρ = [0.0, .5, 1.0]
-alphaij = [0, .2, .5, .8, 1.0]
-sigma = [.5, .9]
-param_names = (:rep, :S, :rho, :alphaij,:sigma)
-param = map(p -> (;Dict(k => v for (k, v) in zip(param_names, p))...), Iterators.product(rep, S, ρ, alphaij, sigma))[:]
-
-sim_competition = @showprogress pmap(p -> merge(
-                     (rep = p.rep, S = p.S),
-                     sim_int_mat(zeros(p.S, p.S);
[…]

### 2023-01-31 scripts/module_competition.jl

@@ -1,0 +1,55 @@
+
+##############################
+#  Module and stochasticity  #
+##############################
+
+
+import Pkg
+Pkg.instantiate()
+using Distributed, Serialization
+
+ncpu = length(Sys.cpu_info())
+
+#Flag enables all the workers to start on the project of the current dir
+flag = "--project=~/xStressorsStabBEFW/"
+#flag = "--project=."
+println("Workers run with flag: $(flag)")
+#addprocs(ncpu - 2, exeflags=flag)
+addprocs(5, exeflags=flag)
+println("Using $(ncpu -2) cores")
+
+@everywhere import Pkg
+@everywhere using DifferentialEquations, BEFWM2, Distributions, ProgressMeter, SparseArrays, LinearAlgebra, DataFrames, CSV, Arrow
+@everywhere include("../src/stochastic_mortality_model.jl")
+@everywhere include("../src/sim.jl")
+@everywhere include("../src/interaction_strength.jl")
+
+################################################################################
+#                             Competition modules                              #
+################################################################################
+
+rep = 1:20
+S = 1:10
+ρ = [0.0, .5, 1.0]
+alphaij = [0, .2, .5, .8, 1.0]
+sigma = [.5, .9]
+param_names = (:rep, :S, :rho, :alphaij,:sigma)
+param = map(p -> (;Dict(k => v for (k, v) in zip(param_names, p))...), Iterators.product(rep, S, ρ, alphaij, sigma))[:]
+
+sim_competition = @showprogress pmap(p -> merge(
+                     (rep = p.rep, S = p.S),
+                     sim_int_mat(zeros(p.S, p.S);
+                                 ρ = p.rho, alpha_ij = p.alphaij,
+                                 σₑ = p.sigma,
+                                 d = 0.1,
+                                 Z = 10, h = 2.0, c = 1.0,
+                                 r = 1.8, K = 20.0,
+                                 K_alpha_corrected = true,
+                                 fun = stoch_d_dBdt!,
+                                 max = 2000, last = 1000, dt = 0.1, return_sol = false)
+                    ),
+                                     param
+                                    )
+
+df_competition = DataFrame(sim_competition)
+Arrow.write("sim_module_competition.arrow", df_competition)

### 2023-01-31 src/get_modules.jl

@@ -20,38 +20,52 @@ function get_fw_modules()
                0 0 1 0 0 0;
                0 0 0 1 0 0;
                0 0 0 0 1 0],
-     cons2_spe = [0 0 0 0;
+     cons_spe2_gen = [0 0 0 0;
                   0 0 0 0;
                   1 0 0 0;
                   0 1 0 0],
-     cons2_spe_top = [0 0 0 0 0;
+     cons_spe2_top = [0 0 0 0 0;
                       0 0 0 0 0;
                       1 0 0 0 0;
                       0 1 0 0 0;
                       0 0 1 1 0],
-     cons3_spe = [0 0 0 0 0 0;
+     cons_spe3 = [0 0 0 0 0 0;
                   0 0 0 0 0 0;
                   1 0 0 0 0 0;
                   0 1 0 0 0 0;
                   0 0 1 0 0 0;
                   0 0 0 1 0 0],
-     cons = [0 0 0;
+     cons_spe3_top = [0 0 0 0 0 0 0;
+                      0 0 0 0 0 0 0;
+                      1 0 0 0 0 0 0;
+                      0 1 0 0 0 0 0;
+                      0 0 1 0 0 0 0;
+                      0 0 0 1 0 0 0;
+                      0 0 0 0 1 1 0],
+     cons_gen = [0 0 0;
              0 0 0;
              1 1 0],
-     cons2_gen = [0 0 0 0;
+     cons_gen2 = [0 0 0 0;
                   0 0 0 0;
                   1 1 0 0;
                   1 1 0 0],
-     cons2_gen_top = [0 0 0 0 0;
+     cons_gen2_top = [0 0 0 0 0;
                       0 0 0 0 0;
                       1 1 0 0 0;
                       1 1 0 0 0;
                       0 0 1 1 0],
-     cons3_gen = [0 0 0 0 0 0;
+     cons_gen3 = [0 0 0 0 0 0;
                   0 0 0 0 0 0;
                   1 1 0 0 0 0;
                   1 1 0 0 0 0;
                   0 0 1 1 0 0;
                   0 0 1 1 0 0],
+     cons_gen3_top = [0 0 0 0 0 0 0;
+                      0 0 0 0 0 0 0;
+                      1 1 0 0 0 0 0;
+                      1 1 0 0 0 0 0;
+                      0 0 1 1 0 0 0;
+                      0 0 1 1 0 0 0;
+                      0 0 0 0 1 1 0],
     )
 end

### 2023-02-24 report/cs_analysis.Rmd
Add some Z variation

--- 2023-01-14 report/cs_analysis.Rmd
@@
 ---
-title: big sim
+title: Simulation connectance richness
 author: Alain Danet
 output:
-  bookdown::pdf_document2
+  bookdown::psim_document2
 ---
 
-```{r}
+```{r, echo = FALSE}
+knitr::opts_chunk$set(
+  cache = FALSE,
+  collapse = TRUE,
+  comment = "#>",
+  #fig.dim = c(7, 7),
+  fig.fullwidth = TRUE,
+  fig.show = "hold",
+  echo = FALSE,
+  message = FALSE,
+  warning = FALSE,
+  results = TRUE,
+  fig.path="figures/"
+)
+```
+
+```{r, results = FALSE}
 library(tidyverse)
 library(magrittr)
+library(cowplot)
+library(here)
+library(arrow)
+
+mytheme <- theme_cowplot(font_size = 8) +
+background_grid() +
+theme(legend.position = "bottom")
+
+theme_set(mytheme)
+```
+```{r}
+sim_brut <- open_dataset(here::here("res", "sim_cs_stdK.arrow"),
+  format = "arrow")
+sim <- sim_brut %>%
+  collect() %>%
+  mutate(across(where(is.list), as.list)) %>%
+  mutate(across(c(int_strength, max_int),
+      ~map2(.x, S,
+        function(y, rich) {
+          matrix(y, nrow = rich)
+        }
+      )
+  )
+    ) %>%
+  mutate(max_int_alive  = map2(max_int, bm_sp,
+      function(mat, bm) {
+        mask <- bm > 10^-16
+        mat[mask, mask]
+      }
+      ),
+    ct_alive = map_dbl(max_int_alive, ~ sum(.x > 0) / ((ncol(.x) - 1)^2)),
+    bm_sp_alive = map(bm_sp, ~.x[.x > 10^-16]),
+    tlvl_alive = map2(tlvl, bm_sp, ~.x[.y > 10^-16]),
+    max_tlvl_alive = map_dbl(tlvl_alive, max),
+    w_avg_tlvl_alive = map2_dbl(tlvl_alive, bm_sp_alive, ~sum(.x * (.y / sum(.y)))),
+    max_max_int_alive = map_dbl(max_int_alive, ~max(.x[.x > 0])),
+    avg_max_int_alive = map_dbl(max_int_alive, ~mean(.x[.x > 0])),
+    #gini_max_int_alive = map_dbl(max_int_alive, ),
+  )
+```
+```{r}
+simZ <- open_dataset(here::here("res", "sim_csZ.arrow"),
+  format = "arrow") %>%
+  collect() %>%
+  filter(!is.na(richness)) %>%
+  mutate(across(where(is.list), as.list)) %>%
+  mutate(across(c(int_strength, max_int),
+      ~map2(.x, S,
+        function(y, rich) {
+          matrix(y, nrow = rich)
+        }
+      )
+  )
+    ) %>%
+  mutate(max_int_alive  = map2(max_int, bm_sp,
+      function(mat, bm) {
+        mask <- bm > 10^-16
+        mat[mask, mask]
+      }
+      ),
+    ct_alive = map_dbl(max_int_alive, ~ sum(.x > 0) / ((ncol(.x) - 1)^2)),
+    bm_sp_alive = map(bm_sp, ~.x[.x > 10^-16]),
+    tlvl_alive = map2(tlvl, bm_sp, ~.x[.y > 10^-16]),
+    max_tlvl_alive = map_dbl(tlvl_alive, max),
+    w_avg_tlvl_alive = map2_dbl(tlvl_alive, bm_sp_alive, ~sum(.x * (.y / sum(.y)))),
+    max_max_int_alive = map_dbl(max_int_alive, ~max(.x[.x > 0])),
+    avg_max_int_alive = map_dbl(max_int_alive, ~mean(.x[.x > 0])),
+    #gini_max_int_alive = map_dbl(max_int_alive, ),
+  )
+```
+
+```{r, eval = FALSE}
+colnames(sim)
+unique(sim$env_stoch)
+summary(sim$total_biomass)
 ```
@@
 ```{r}
-df_brut <- read_csv(here::here("res", "cs_sim.csv"))
-df <- df_brut %>%
-  select(where(is.double))
-```
-
-```{r}
-summary(df)
-
-df %>%
-  filter(stab_com <= 1000) %>%
-  ggplot(aes(x = as.factor(richness), y = stab_com, color = as.factor(ct))) +
-  geom_boxplot()
+sim %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  ggplot(aes(x = richness, y = stab)) +
+  geom_point() +
+  facet_grid(rows = vars(metric), scales = "free_y") +
+  labs(
+    color = "Connectance",
+    x = "Species richness",
+    y = "Stability component"
+  )
 ```
@@
 corrplot::corrplot(
-  cor(df %>% select(-rep, -Z, -env_stoch, -sim_timing), method = "spearman"),
+  cor(sim %>% select(
+      c(S, richness, ct, ct_alive, total_biomass, avg_max_int_alive, w_avg_tlvl_alive,
+        max_tlvl_alive, rho, env_stoch, stab_com, avg_cv_sp, sync
+        )
+      ),
+    method = "spearman"),
   diag = FALSE, type = "upper"
@@
 ```
+
+- Main results:
+  - Stability increases with richness but not connectance (no overall effect)
+  - Richness increases stability by increasing maximum and average trophic
+    level, but also by decreasing interaction strength and increasing asymetry
+    in trophic interaction, and finally by increasing total biomass (I need to control for that).
+  - Synchrony decreases with species richness, max and average trophic level but increases with
+    average interaction strength and symetry of interaction distributions.
+  - Population varibility decreases with species richness, average and maximum
+    trophic level, asymetry of interaction strength but it is increased by
+    average interaction strength
+  - Same effects of food-web structure on both Synchrony and Population variability
+    - Surpringly, as in Danet et al. (2021), connectance has little effect on
+      temporal stability and its components!
+
+# Covariation
+
+It seems that the effects of food-web structure are mainly richness effects!
+
+```{r}
+sim %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  ggplot(aes(x = avg_max_int_alive, y = stab, color = richness)) +
+  geom_point() +
+  geom_smooth() +
+  facet_grid(rows = vars(metric), scales = "free_y") +
+  labs(
+    color = "Richness",
+    x = "Avg interaction strength",
+    y = "Stability component"
+  )
+
+```
+
+```{r}
+sim%>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  ggplot(aes(x = gini_max_int, y = stab, color = richness)) +
+  geom_point() +
+  geom_smooth() +
+  facet_grid(rows = vars(metric), scales = "free_y") +
+  labs(
+    color = "Richness",
+    x = "Gini interaction strength",
+    y = "Stability component"
+  )
+
+```
+
+```{r}
+sim %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  ggplot(aes(x = ct_alive, y = stab, color = richness)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_grid(rows = vars(metric), scales = "free_y") +
+  labs(
+    color = "Richness",
+    x = "Connectance",
+    y = "Stability component"
+  )
+```
+
+```{r}
+sim %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  ggplot(aes(x = max_tlvl_alive, y = stab, color = richness)) +
+  geom_point() +
+  geom_smooth() +
+  facet_grid(rows = vars(metric), scales = "free_y") +
+  labs(
+    color = "Richness",
+    x = "Avg trophic level",
+    y = "Stability component"
+  )
+```
+
+# SEM
+
+```{r}
+library(piecewiseSEM)
+library(semEff)
+```
+
+```{r}
+sim_sem <- sim %>%
+  filter(rho == 0, env_stoch == .5) %>%
+  mutate(across(c(sync, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}"))
+```
+
+```{r}
+pairs(
+  sim_sem %>%
+    select(ct_alive, log_richness, max_tlvl_alive,
+      log_gini_max_int, log_avg_max_int_alive, log_sync,
+      log_avg_cv_sp, log_stab_com),
+    pch = 19)
+```
+
+```{r}
+sem_list <- list(
+  max_tlvl = lm(max_tlvl_alive ~ log_richness + ct_alive, sim_sem),
+  gini_max_int = lm(gini_max_int ~ log_richness + ct_alive + max_tlvl_alive, sim_sem),
+  log_avg_max_int = lm(log_avg_max_int_alive ~ log_richness + ct_alive + max_tlvl_alive, sim_sem),
+  log_sync = lm(log_sync ~ ct_alive + log_richness + max_tlvl_alive + gini_max_int, sim_sem),
+  log_avg_cv_sp = lm(log_avg_cv_sp ~ ct_alive + log_richness + max_tlvl_alive +  gini_max_int, sim_sem),
+  log_stab_com = lm(log_stab_com ~ log_sync + log_avg_cv_sp, sim_sem)
+)
+
+sem <- as.psem(sem_list)
+```
+
+```{r}
+map_dfr(setNames(sem_list, names(sem_list)), performance::check_collinearity)
+map_dfr(sem_list, rsquared)
+summary(sem)$coefficients[, c(1, 2, 8, 9)]
+```
+
+```{r}
+plot(sem)
+```
+
+```{r}
+boot_eff <- semEff(sem, R = 50, ci.type =  "perc")
+summary(boot_eff)
+```
+
+```{r}
+sem_int_list <- list(
+  max_tlvl = lm(max_tlvl_alive ~ log_richness + ct_alive, sim_sem),
+  gini_max_int = lm(gini_max_int ~ log_richness + ct_alive + max_tlvl_alive, sim_sem),
+  log_avg_max_int = lm(log_avg_max_int_alive ~ log_richness + ct_alive + max_tlvl_alive, sim_sem),
+  log_sync = lm(log_sync ~ log_richness + log_avg_max_int_alive + max_tlvl_alive + gini_max_int, sim_sem),
+  log_avg_cv_sp = lm(log_avg_cv_sp ~ log_richness + log_avg_max_int_alive + max_tlvl_alive + gini_max_int, sim_sem),
+  log_stab_com = lm(log_stab_com ~ log_sync + log_avg_cv_sp, sim_sem)
+)
+
+sem_int <- as.psem(sem_int_list)
+plot(sem_int)
+```
+
+```{r}
+map(setNames(sem_int_list, names(sem_int_list)), performance::check_collinearity)
+map_dfr(sem_int_list, rsquared)
+summary(sem_int)$coefficients[, c(1, 2, 8, 9)]
+```
+
+```{r}
+boot_int <- semEff(sem_int, R = 50, ci.type =  "perc")
+summary(boot_int)
+```
+
+# With Z
+
+```{r}
+colnames(simZ)
+corrplot::corrplot(
+  cor(simZ %>%
+    mutate(persistence = richness / S) %>%
+    select(
+      c(S, richness, persistence, ct, ct_alive, total_biomass, avg_max_int_alive,
+        max_max_int_alive, gini_max_int, w_avg_tlvl_alive, max_tlvl_alive, Z,
+        rho, env_stoch, stab_com, avg_cv_sp, sync
+        )
+      ),
+    method = "spearman"),
+  diag = FALSE, type = "upper"
+)
+```

### 2023-02-24 scripts/connectance_richness_stoch.jl

@@ -15,7 +15,8 @@ addprocs(ncpu - 1, exeflags=flag)
 println("Using $(ncpu -2) cores")
 
 @everywhere import Pkg
-@everywhere using DifferentialEquations, BEFWM2, Distributions, ProgressMeter, SparseArrays, LinearAlgebra, DataFrames
+@everywhere using DifferentialEquations, BEFWM2, SparseArrays,LinearAlgebra, DataFrames
+@everywhere using qistributions, ProgressMeter
 @everywhere using StatsBase, CSV, Arrow
 @everywhere include("../src/stochastic_mortality_model.jl")
 @everywhere include("../src/sim.jl")
@@ -29,7 +30,7 @@ rep = 1:20
 S = [5, 10, 20, 40, 60]
 C = 0.02:.05:.32
 sigma = [0.5, 1.0]
-Z = [10, 1000]
+Z = [50, 200, 500]
 ρ = [0, .5, 1]
 names = (:rep, :richness, :connectance, :Z, :sigma, :rho)
 param = map(p -> (;Dict(k => v for (k, v) in zip(names, p))...), Iterators.product(rep, S, C, Z, sigma, ρ))[:]
@@ -87,4 +88,4 @@ timing = @elapsed sim = @showprogress pmap(p ->
 df = DataFrame(sim)
 println("$(length(sim)) simulations took $(round(timing /60, digits = 2)) minutes to run")
 
-Arrow.write("sim_csZ.arrow", df)
+Arrow.write("sim_csZ2.arrow", df)

### 2023-02-28 report/cs_analysis.Rmd
Add Z to report

@@
 output:
-  bookdown::psim_document2
+  bookdown::pdf_document2
 ---
@@
 library(arrow)
+library(piecewiseSEM)
+library(semEff)
 
@@
 ```{r}
-sim_brut <- open_dataset(here::here("res", "sim_cs_stdK.arrow"),
+sim_brut <- open_dataset(
+  here::here("res", "sim_cs.arrow"),
+  #here::here("res", "sim_cs_stdK.arrow"),
   format = "arrow")
@@
   format = "arrow") %>%
-  collect() %>%
+  collect()
+simZ2 <- open_dataset(here::here("res", "sim_csZ2.arrow"),
+  format = "arrow") %>%
+  collect()
+
+# TODO set extinction threshold in simulations
+simZ <- map_dfr(list(simZ, simZ2),
+  function (x) {
+    x %>%
       filter(!is.na(richness)) %>%
@@
       )
+
+  }
+) %>%
+filter(max_max_int_alive != -Inf) %>%
+mutate(persistence = richness / S)
 ```
@@
 ```{r}
-library(piecewiseSEM)
-library(semEff)
-```
-
-```{r}
 sim_sem <- sim %>%
   filter(rho == 0, env_stoch == .5) %>%
-  mutate(across(c(sync, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}"))
+  mutate(across(c(sync, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
+  as.data.frame() %>%
+  select(c(ct_alive, log_richness, max_tlvl_alive, Z, gini_max_int, log_avg_max_int_alive, env_stoch, log_stab_com, log_sync, log_avg_cv_sp))
 ```
@@
     select(ct_alive, log_richness, max_tlvl_alive,
-      log_gini_max_int, log_avg_max_int_alive, log_sync,
+      gini_max_int, log_avg_max_int_alive, log_sync,
       log_avg_cv_sp, log_stab_com),
@@
   cor(simZ %>%
-    mutate(persistence = richness / S) %>%
     select(
@@
 ```
+
+```{r}
+unique(simZ$richness)
+simZ %>%
+  ggplot(aes(x = as.factor(Z), y = avg_cv_sp, fill = richness)) +
+  geom_boxplot()
+```
+
+```{r}
+sim_sem <- simZ %>%
+  filter(S == richness) %>%
+  filter(rho == 0) %>%
+  mutate(across(c(sync, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
+  select(c(ct_alive, log_richness, max_tlvl_alive, Z, gini_max_int, log_avg_max_int_alive, env_stoch, log_stab_com, log_sync, log_avg_cv_sp)) %>%
+  as.data.frame()
+```
+
+```{r}
+sem_int_list <- list(
+  ct = lm(ct_alive ~ log_richness, sim_sem),
+  max_tlvl = lm(max_tlvl_alive ~ log_richness + Z + ct_alive, sim_sem),
+  gini_max_int = lm(gini_max_int ~ log_richness + ct_alive + max_tlvl_alive + Z, sim_sem),
+  log_avg_max_int = lm(log_avg_max_int_alive ~ log_richness + ct_alive + max_tlvl_alive + Z, sim_sem),
+  log_sync = lm(log_sync ~ log_richness + log_avg_max_int_alive + max_tlvl_alive + gini_max_int + env_stoch + Z, sim_sem),
+  log_avg_cv_sp = lm(log_avg_cv_sp ~ log_richness + log_avg_max_int_alive + max_tlvl_alive + gini_max_int + env_stoch + Z, sim_sem),
+  log_stab_com = lm(log_stab_com ~ log_sync + log_avg_cv_sp, sim_sem)
+)
+
+sem_int <- as.psem(sem_int_list)
+plot(sem_int)
+```
+
+```{r}
+map(setNames(sem_int_list, names(sem_int_list)), performance::check_collinearity)
+map_dfr(sem_int_list, rsquared)
+summary(sem_int)$coefficients[, c(1, 2, 8, 9)]
+```
+
+```{r}
+summary(sim_sem$richness)
+summary(sim_sem$S)
+summary(sim_sem$persistence)
+```
+
+```{r}
+boot_int <- semEff(sem_int, ci.type = "perc", R = 50, ncpus = 2)
+summary(boot_int)
+```
+
+```{r}
+unique(simZ$Z)
+sim_sem <- simZ %>%
+  filter(rho == 0, Z == 50) %>%
+  mutate(across(c(sync, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
+  select(c(ct_alive, log_richness, max_tlvl_alive, Z, gini_max_int, log_avg_max_int_alive, env_stoch, log_stab_com, log_sync, log_avg_cv_sp)) %>%
+  as.data.frame()
+```
+
+```{r}
+sem_int_list <- list(
+  ct = lm(ct_alive ~ log_richness, sim_sem),
+  max_tlvl = lm(max_tlvl_alive ~ log_richness + ct_alive, sim_sem),
+  gini_max_int = lm(gini_max_int ~ log_richness + ct_alive + max_tlvl_alive , sim_sem),
+  log_avg_max_int = lm(log_avg_max_int_alive ~ log_richness + ct_alive + max_tlvl_alive, sim_sem),
+  log_sync = lm(log_sync ~ log_richness + log_avg_max_int_alive + max_tlvl_alive + gini_max_int + env_stoch , sim_sem),
+  log_avg_cv_sp = lm(log_avg_cv_sp ~ log_richness + log_avg_max_int_alive + max_tlvl_alive + gini_max_int + env_stoch , sim_sem),
+  log_stab_com = lm(log_stab_com ~ log_sync + log_avg_cv_sp, sim_sem)
+)
+
+sem_int <- as.psem(sem_int_list)
+plot(sem_int)
+```
+
+```{r}
+boot_int <- semEff(sem_int, ci.type = "perc", R = 50, ncpus = 2)
+summary(boot_int)
+```
+
+```{r}
+unique(simZ$Z)
+sim_sem <- simZ %>%
+  filter(rho == 1) %>%
+  mutate(across(c(ct_alive, sync, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, .names = "log_{.col}")) %>%
+  select(c(log_ct_alive, log_richness, max_tlvl_alive, Z, gini_max_int, log_avg_max_int_alive, env_stoch, log_stab_com, log_sync, log_avg_cv_sp)) %>%
+  as.data.frame()
+pairs(sim_sem, pch = 19)
+```
+
+```{r}
+sem_int_list <- list(
+  ct = lm(log_ct_alive ~ log_richness, sim_sem),
+  max_tlvl = lm(max_tlvl_alive ~ log_richness + Z, sim_sem),
+  gini_max_int = lm(gini_max_int ~ log_ct_alive + max_tlvl_alive , sim_sem),
+  log_avg_max_int = lm(log_avg_max_int_alive ~ log_ct_alive + max_tlvl_alive + Z, sim_sem),
+  log_sync = lm(log_sync ~ log_richness + log_avg_max_int_alive + gini_max_int + env_stoch, sim_sem),
+  log_avg_cv_sp = lm(log_avg_cv_sp ~ log_richness + log_avg_max_int_alive + gini_max_int + env_stoch , sim_sem),
+  log_stab_com = lm(log_stab_com ~ log_sync + log_avg_cv_sp, sim_sem)
+)
+
+sem_int <- as.psem(sem_int_list)
+plot(sem_int)
+```
+
+```{r}
+map(setNames(sem_int_list, names(sem_int_list)), performance::check_collinearity)
+map_dfr(sem_int_list, rsquared)
+summary(sem_int)$coefficients[, c(1, 2, 8, 9)]
+```
+
+```{r}
+boot_int <- semEff(sem_int, ci.type = "perc", R = 50, ncpus = 2)
+summary(boot_int)
+```
+
+```{r}
+simZ %>%
+  ggplot(aes(y = persistence, x = as.factor(Z))) +
+  geom_boxplot()
+```

### 2023-04-17 report/cs_analysis.Rmd
Add stability decomposition

--- 2023-01-31 report/cs_analysis.Rmd
@@
 library(here)
+library(arrow)
+library(piecewiseSEM)
+library(semEff)
+library(easystats)
 
@@
 theme(legend.position = "bottom")
-
 theme_set(mytheme)
+source(here::here("R", "network_metrics.R"))
 ```
@@
 ```{r}
-df_brut <- read_csv(here::here("res", "cs_sim.csv"))
-df <- df_brut %>%
-  select(where(is.double))
-summary(df)
+sim_files <- list.files(here("res", "simCSZenrich"))
+sim_list <- map(sim_files, function (x) {
+  open_dataset(here::here("res", "simCSZenrich", x),
+    format = "arrow") %>%
+  collect()
+})
 ```
@@
 ```{r}
-df %>%
-  filter(stab_com <= 1000) %>%
+# TODO set extinction threshold in simulations
+simZ_prep <- map_dfr(sim_list,
+  function (x) {
+    x %>%
+      # Remove simulation that have failed to run
+      filter(!is.na(richness)) %>%
+      # Transform back interaction strength into matrices
+      mutate(across(where(is.list), as.list)) %>%
+      mutate(across(c(int_strength, max_int),
+          ~map2(.x, S,
+            function(y, rich) {
+              matrix(y, nrow = rich)
+            }
+          )
+      )
+        ) %>%
+      # Get matrix of alive species
+      mutate(max_int_alive  = map2(max_int, bm_sp,
+          function(mat, bm) {
+            mask <- bm > 10^-6
+            mat[mask, mask, drop = FALSE]
+          }
+        )
+        )
+  }
+)
+# Compute metrics of interest
+simZ <- simZ_prep %>%
+  mutate(
+    persistence = richness / S,
+    ct_alive = map_dbl(max_int_alive,
+      ~ifelse(sum(.x) == 0, 0,
+      sum(.x > 0) / ((ncol(.x) - 1)^2))),
+    bm_sp_alive = map(bm_sp, ~.x[.x > 10^-6]),
+    tlvl_alive = map2(tlvl, bm_sp, ~.x[.y > 10^-6]),
+    max_tlvl_alive = map_dbl(tlvl_alive, max),
+    w_avg_tlvl_alive = map2_dbl(tlvl_alive, bm_sp_alive, ~sum(.x * (.y / sum(.y)))),
+    max_max_int_alive = map_dbl(max_int_alive,
+      ~ifelse(length(.x[.x > 0]) == 0, 0, max(.x[.x > 0]))
+      ),
+    avg_max_int_alive = map_dbl(max_int_alive,
+      ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
+      ),
+    gini_max_int_alive = map_dbl(max_int_alive, ~gini(.x))
+      )
+```
+
+```{r, eval = FALSE}
+colnames(sim)
+unique(simZ$env_stoch)
+summary(simZ$total_biomass)
+summary(simZ$persistence)
+summary(simZ$ct_alive)
+summary(simZ$gini_max_int_alive)
+```
+
+```{r}
+simZ %>%
+  filter(rho == 0) %>%
   mutate(stab_pop = 1/ avg_cv_sp) %>%
   pivot_longer(
-    c(stab_com, stab_pop, sync),
+    c(stab_com, stab_pop, sync, total_biomass),
     names_to = "metric",
     values_to = "stab") %>%
-  ggplot(aes(x = as.factor(richness), y = stab, color = as.factor(ct))) +
-  geom_boxplot() +
-  facet_grid(rows = vars(metric), scales = "free_y") +
+  ggplot(aes(x = richness, y = stab, color = factor(env_stoch))) +
+  geom_point() +
+  facet_grid(rows = vars(metric), cols = vars(productivity), scales = "free_y") +
   labs(
-    color = "Connectance",
+    color = "Evironmental stochasticity",
     x = "Species richness",
@@
 ```{r}
-corrplot::corrplot(
-  cor(df %>% select(-rep, -Z, -env_stoch, -sim_timing), method = "spearman"),
+simZ %>%
+  filter(rho == 1) %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync, total_biomass),
+    names_to = "metric",
+    values_to = "stab") %>%
+  ggplot(aes(x = richness, y = stab, color = factor(env_stoch))) +
+  geom_point() +
+  facet_grid(rows = vars(metric), cols = vars(productivity), scales = "free_y") +
+  labs(
+    color = "Evironmental stochasticity",
+    x = "Species richness",
+    y = "Stability component"
+  )
+```
+
+```{r}
+p_basic <- ~corrplot::corrplot(
+  cor(simZ %>%
+    filter(productivity == "enrichment") %>%
+    select(c(S, richness, ct, Z, ct_alive, total_biomass, avg_max_int_alive,
+        w_avg_tlvl_alive, max_tlvl_alive, rho, env_stoch, stab_com, avg_cv_sp,
+        sync)),
+    method = "spearman"),
   diag = FALSE, type = "upper"
+)
+p_enrich <- ~corrplot::corrplot(
+  cor(simZ %>%
+    filter(productivity == "basic") %>%
+    select(c(S, richness, ct, Z, ct_alive, total_biomass, avg_max_int_alive,
+        w_avg_tlvl_alive, max_tlvl_alive, rho, env_stoch, stab_com, avg_cv_sp,
+        sync)),
+    method = "spearman"),
+  diag = FALSE, type = "upper"
+)
+plot_grid(
+  ggdraw(p_basic),
+  ggdraw(p_enrich)
 )
@@
 
-It seems that the effects of food-web structure are mainly richness effects!
-
 ```{r}
-df %>%
-  filter(stab_com <= 1000) %>%
-  mutate(stab_pop = 1/ avg_cv_sp) %>%
-  pivot_longer(
-    c(stab_com, stab_pop, sync),
-    names_to = "metric",
-    values_to = "stab") %>%
-  ggplot(aes(x = avg_max_int, y = stab, color = as.factor(richness))) +
-  geom_point() +
-  geom_smooth() +
-  facet_grid(rows = vars(metric), scales = "free_y") +
-  labs(
-    color = "Richness",
-    x = "Avg interaction strength",
-    y = "Stability component"
+compute_rotated_pca <- function(.data = NULL, naxis = 2) {
+  .data <- na.omit(.data)
+  pca <- ade4::dudi.pca(as.data.frame(.data),
+    scannf = FALSE, nf = naxis, center = TRUE, scale = TRUE
+  )
+  pca_rotated <- psych::principal(.data,
+    rotate = "varimax", nfactors = naxis,
+    scores = TRUE
   )
 
+  return(list(normal = pca, rotated = pca_rotated))
+}
 ```
@@
 ```{r}
-df %>%
-  filter(stab_com <= 1000) %>%
-  mutate(stab_pop = 1/ avg_cv_sp) %>%
-  pivot_longer(
-    c(stab_com, stab_pop, sync),
-    names_to = "metric",
-    values_to = "stab") %>%
-  ggplot(aes(x = gini_max_int, y = stab, color = as.factor(richness))) +
-  geom_point() +
-  geom_smooth() +
-  facet_grid(rows = vars(metric), scales = "free_y") +
-  labs(
-    color = "Richness",
-    x = "Gini interaction strength",
-    y = "Stability component"
+library(glmmTMB)
+sim_sem <- simZ %>%
+  filter(rho == 0) %>%
+  mutate(across(c(sync, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
+  mutate(
+    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
+    productivity_f = factor(productivity)
+
+    ) %>%
+  as.data.frame() %>%
+  select(c(
+      ct_alive, log_richness, max_tlvl_alive, Z,
+      gini_max_int, avg_max_int_alive, log1_avg_max_int_alive, env_stoch,
+      log_stab_com, log_sync, log_avg_cv_sp, productivity, productivity_f)
   )
-
+test <- sim_sem %>%
+  mutate(across(where(is.double), ~scale(.x)[,1]))
 ```
@@
 ```{r}
-df %>%
-  filter(stab_com <= 1000) %>%
-  mutate(stab_pop = 1/ avg_cv_sp) %>%
-  pivot_longer(
-    c(stab_com, stab_pop, sync),
-    names_to = "metric",
-    values_to = "stab") %>%
-  ggplot(aes(x = ct, y = stab, color = as.factor(richness))) +
-  geom_point() +
-  geom_smooth(method = "lm") +
-  facet_grid(rows = vars(metric), scales = "free_y") +
-  labs(
-    color = "Richness",
-    x = "Connectance",
-    y = "Stability component"
+pred_may <- "log1_avg_max_int_alive*log_richness*ct_alive*productivity + env_stoch"
+rand <- "(1 | Z)"
+
+mod_may_single <- lm(formula(str_replace_all(paste0("log_stab_com ~ ", pred_may), "\\*", "+")), test)
+performance::check_collinearity(mod_may_single)
+```
+
+```{r}
+mod_may <- glmmTMB(formula(paste0("log_stab_com ~ ", pred_may, " + ", rand)), test)
+
+r2_nakagawa(mod_may)
+plot(parameters(mod_may))
+```
+
+```{r}
+mod_may_sync <- glmmTMB(formula(paste0("log_sync ~ ", pred_may, " + ", rand)),
+  test)
+r2_nakagawa(mod_may_sync)
+plot(parameters(mod_may_sync))
+```
+
+```{r}
+mod_may_cv_sp <- glmmTMB(formula(paste0("log_avg_cv_sp ~ ", pred_may, " + ", rand)),
+  test)
+r2_nakagawa(mod_may_cv_sp)
+plot(parameters(mod_may_cv_sp))
+```
+
+## Rho model
+
+```{r}
+sim_rho <- simZ %>%
+  mutate(across(c(sync, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
+  mutate(
+    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
+    productivity_f = factor(productivity)
+
+    ) %>%
+  as.data.frame() %>%
+  select(c(
+      ct_alive, log_richness, max_tlvl_alive, Z, rho,
+      gini_max_int, avg_max_int_alive, log1_avg_max_int_alive, env_stoch,
+      log_stab_com, log_sync, log_avg_cv_sp, productivity, productivity_f,
+      persistence)
+  )
+sim_rho_scaled <- sim_rho %>%
+  mutate(across(where(is.double), ~scale(.x)[,1]))
+```
+
+```{r}
+pred_rho <- "log1_avg_max_int_alive * log_richness * rho +
+log1_avg_max_int_alive * log_richness * productivity +
+log1_avg_max_int_alive * log_richness * ct_alive +
+log1_avg_max_int_alive * ct_alive * rho +
+log1_avg_max_int_alive * ct_alive * rho +
+log1_avg_max_int_alive * ct_alive * productivity +
+log_richness * rho * productivity +
+log_richness * ct_alive * productivity +
+log_richness * ct_alive * rho +
+env_stoch"
+rand <- "(1 | Z)"
+
+mod_rho_single <- lm(formula(str_replace_all(paste0("log_stab_com ~ ", pred_rho), "\\*", "+")),
+  sim_rho_scaled)
+performance::check_collinearity(mod_rho_single)
+```
+
+```{r}
+mod_rho <- glmmTMB(formula(paste0("log_stab_com ~ ", pred_rho, " + ", rand)),
+  sim_rho_scaled)
+
+r2_nakagawa(mod_rho)
+plot(parameters(mod_rho))
+```
+
+```{r}
+mod_rho_sync <- glmmTMB(formula(paste0("log_sync ~ ", pred_rho, " + ", rand)),
+  sim_rho_scaled)
+
+r2_nakagawa(mod_rho_sync)
+p_mod_rho_sync <- plot(parameters(mod_rho_sync))
+```
+
+```{r}
+mod_rho_cv_sp <- glmmTMB(formula(paste0("log_avg_cv_sp ~ ", pred_rho, " + ", rand)),
+  sim_rho_scaled)
+
+r2_nakagawa(mod_rho_cv_sp)
+p_mod_rho_cv_sp <- plot(parameters(mod_rho_cv_sp))
+```
+
+```{r}
+plot_grid(
+  p_mod_rho_sync,
+  p_mod_rho_cv_sp
 )
@@
 ```{r}
-df %>%
-  filter(stab_com <= 1000) %>%
-  mutate(stab_pop = 1/ avg_cv_sp) %>%
-  pivot_longer(
-    c(stab_com, stab_pop, sync),
-    names_to = "metric",
-    values_to = "stab") %>%
-  ggplot(aes(x = w_avg_tlvl, y = stab, color = as.factor(richness))) +
-  geom_point() +
-  geom_smooth() +
-  facet_grid(rows = vars(metric), scales = "free_y") +
-  labs(
-    color = "Richness",
-    x = "Avg trophic level",
-    y = "Stability component"
+sim_rho_pers <- simZ %>%
+  mutate(across(c(S, ct, avg_max_int, gini_max_int), log, , .names = "log_{.col}")) %>%
+  mutate(
+    log1_avg_max_int = log(avg_max_int + 1),
+    productivity_f = factor(productivity)
+    ) %>%
+  as.data.frame() %>%
+  select(c(
+      log_S, ct, max_tlvl, Z, rho,
+      gini_max_int, avg_max_int, log1_avg_max_int, env_stoch,
+      productivity, productivity_f,
+      persistence)
   )
+sim_rho_pers_scaled <- sim_rho_pers %>%
+  mutate(across(where(is.double), ~scale(.x)[,1]))
+
+pred_rho_pers <- "log1_avg_max_int * log_S * rho +
+log1_avg_max_int * log_S * productivity +
+log1_avg_max_int * log_S * ct +
+log1_avg_max_int * ct * rho +
+log1_avg_max_int * ct * rho +
+log1_avg_max_int * ct * productivity +
+log_S * rho * productivity +
+log_S * ct * productivity +
+log_S * ct * rho +
+env_stoch"
+rand <- "(1 | Z)"
+
+mod_rho_pers <- glmmTMB(formula(paste0("persistence ~ ", pred_rho_pers, " + ", rand)),
+  sim_rho_pers_scaled)
+
+r2_nakagawa(mod_rho_pers)
+plot(parameters(mod_rho_pers))
+```
+
+```{r}
+
 ```
@@
 ```{r}
-library(piecewiseSEM)
-library(semEff)
-```
 
-```{r}
-df_sem <- df %>%
-  filter(stab_com < 1000) %>%
-  mutate(across(c(sync, avg_cv_sp, stab_com, richness, avg_max_int, gini_max_int), log, , .names = "log_{.col}"))
+sim_sem_basic <- sim_sem %>%
+  filter(productivity == "basic")
+
+sim_sem_enrich <- sim_sem %>%
+  filter(productivity == "enrichment")
 ```
@@
 pairs(
-  df_sem %>%
-    select(ct, log_richness, max_tlvl,
-      log_gini_max_int, log_avg_max_int, log_sync,
+  sim_sem %>%
+    select(ct_alive, log_richness, max_tlvl_alive,
+      gini_max_int, log1_avg_max_int_alive, log_sync,
       log_avg_cv_sp, log_stab_com),
@@
 sem_list <- list(
-  max_tlvl = lm(max_tlvl ~ log_richness + ct, df_sem),
-  gini_max_int = lm(gini_max_int ~ log_richness + ct + max_tlvl, df_sem),
-  log_avg_max_int = lm(log_avg_max_int ~ log_richness + ct + max_tlvl, df_sem),
-  log_sync = lm(log_sync ~ ct + log_richness + max_tlvl + gini_max_int, df_sem),
-  log_avg_cv_sp = lm(log_avg_cv_sp ~ ct + log_richness + max_tlvl +  gini_max_int, df_sem),
-  log_stab_com = lm(log_stab_com ~ log_sync + log_avg_cv_sp, df_sem)#~,
-  #log_avg_max_int %~~% log_richness
+  max_tlvl = lm(max_tlvl_alive ~ log_richness + ct_alive, sim_sem),
+  gini_max_int = lm(gini_max_int ~ log_richness + ct_alive + max_tlvl_alive, sim_sem),
+  log_avg_max_int = lm(log1_avg_max_int_alive ~ log_richness + ct_alive + max_tlvl_alive + Z, sim_sem),
+  log_sync = lm(log_sync ~ ct_alive + log_richness + max_tlvl_alive + gini_max_int, sim_sem),
+  log_avg_cv_sp = lm(log_avg_cv_sp ~ ct_alive + log_richness + max_tlvl_alive +  gini_max_int, sim_sem),
+  log_stab_com = lm(log_stab_com ~ log_sync + log_avg_cv_sp, sim_sem)
 )
@@
 sem <- as.psem(sem_list)
+
+ti <- psem(
+  max_tlvl = lm(max_tlvl_alive ~ log_richness + ct_alive, sim_sem),
+  gini_max_int = lm(gini_max_int ~ log_richness + ct_alive + max_tlvl_alive, sim_sem),
+  log_avg_max_int = lm(log1_avg_max_int_alive ~ log_richness + ct_alive + max_tlvl_alive + Z, sim_sem),
+  log_sync = lm(log_sync ~ ct_alive + log_richness + max_tlvl_alive + gini_max_int, sim_sem),
+  log_avg_cv_sp = lm(log_avg_cv_sp ~ ct_alive + log_richness + max_tlvl_alive +  gini_max_int, sim_sem)
+)
+
+group_sem <- multigroup(ti, group = "productivity_f")
 ```
@@
 ```{r}
-map_dfr(setNames(sem_list, names(sem_list)), performance::check_collinearity)
-map_dfr(sem_list, rsquared)
-summary(sem)
+sem_list_basic <- list(
+  max_tlvl = lm(max_tlvl_alive ~ log_richness + ct_alive, sim_sem_basic),
+  gini_max_int = lm(gini_max_int ~ log_richness + ct_alive + max_tlvl_alive, sim_sem_basic),
+  log_avg_max_int = lm(log1_avg_max_int_alive ~ log_richness + ct_alive + max_tlvl_alive + Z, sim_sem_basic),
+  log_sync = lm(log_sync ~ ct_alive + log_richness + max_tlvl_alive + gini_max_int, sim_sem),
+  log_avg_cv_sp = lm(log_avg_cv_sp ~ ct_alive + log_richness + max_tlvl_alive +  gini_max_int, sim_sem_basic),
+  log_stab_com = lm(log_stab_com ~ log_sync + log_avg_cv_sp, sim_sem_basic)
+)
+
+sem_basic <- as.psem(sem_list_basic)
+
+map_dfr(setNames(sem_list_basic, names(sem_list_basic)), performance::check_collinearity, .id = "response")
+map_dfr(sem_list_basic, rsquared)
+summary(sem)$coefficients[, c(1, 2, 8, 9)]
 ```
@@
 ```{r}
-plot(sem)
+sem_int_list_basic <- list(
+  max_tlvl = lm(max_tlvl_alive ~ log_richness + ct_alive + Z, sim_sem_basic),
+  gini_max_int = lm(gini_max_int ~ log_richness + ct_alive + max_tlvl_alive + Z, sim_sem_basic),
+  log_avg_max_int = lm(log1_avg_max_int_alive ~ log_richness + ct_alive + max_tlvl_alive + Z,
+    sim_sem_basic),
+  log_sync = lm(log_sync ~ log_richness + log1_avg_max_int_alive + max_tlvl_alive + gini_max_int + Z,
+    sim_sem_basic),
+  log_avg_cv_sp = lm(log_avg_cv_sp ~ log_richness + log1_avg_max_int_alive + max_tlvl_alive + gini_max_int + Z,
+    sim_sem_basic),
+  log_stab_com = lm(log_stab_com ~ log_sync + log_avg_cv_sp,
+    sim_sem_basic)
+)
+
+sem_int_basic <- as.psem(sem_int_list_basic)
+plot(sem_int_basic)
 ```
@@
 ```{r}
-boot_eff <- semEff(sem, R = 50, ci.type =  "perc")
-summary(boot_eff)
+map_dfr(setNames(sem_int_list_basic, names(sem_int_list_basic)),
+  performance::check_collinearity, .id = "response")
+map_dfr(sem_int_list_basic, rsquared)
+summary(sem_int_basic)$coefficients[, c(1, 2, 8, 9)]
 ```
@@
 ```{r}
-sem_int_list <- list(
-  max_tlvl = lm(max_tlvl ~ log_richness + ct, df_sem),
-  gini_max_int = lm(gini_max_int ~ log_richness + ct + max_tlvl, df_sem),
-  log_avg_max_int = lm(log_avg_max_int ~ log_richness + ct + max_tlvl, df_sem),
-  log_sync = lm(log_sync ~ log_richness + log_avg_max_int + gini_max_int, df_sem),
-  log_avg_cv_sp = lm(log_avg_cv_sp ~ log_richness + log_avg_max_int + gini_max_int, df_sem),
-  log_stab_com = lm(log_stab_com ~ log_sync + log_avg_cv_sp, df_sem)
+sem_int_list_enrich <- list(
+  max_tlvl = lm(max_tlvl_alive ~ log_richness + ct_alive + Z, sim_sem_enrich),
+  gini_max_int = lm(gini_max_int ~ log_richness + ct_alive + max_tlvl_alive + Z, sim_sem_enrich),
+  log_avg_max_int = lm(log1_avg_max_int_alive ~ log_richness + ct_alive + max_tlvl_alive + Z, sim_sem_enrich),
+  log_sync = lm(log_sync ~ log_richness + log1_avg_max_int_alive + max_tlvl_alive + gini_max_int + Z, sim_sem_enrich),
+  log_avg_cv_sp = lm(log_avg_cv_sp ~ log_richness + log1_avg_max_int_alive + max_tlvl_alive + gini_max_int + Z, sim_sem_enrich),
+  log_stab_com = lm(log_stab_com ~ log_sync + log_avg_cv_sp, sim_sem_enrich)
 )
 
-sem_int <- as.psem(sem_int_list)
-plot(sem_int)
+sem_int_enrich <- as.psem(sem_int_list_enrich)
+plot(sem_int_enrich)
 ```
@@
 ```{r}
-map(setNames(sem_int_list, names(sem_int_list)), performance::check_collinearity)
-map_dfr(sem_list, rsquared)
-summary(sem)
+map_dfr(setNames(sem_int_list_enrich, names(sem_int_list_enrich)),
+  performance::check_collinearity, .id = "response")
+map_dfr(sem_int_list_enrich, rsquared)
+summary(sem_int_enrich)$coefficients[, c(1, 2, 8, 9)]
 ```
@@
 ```{r}
-boot_int <- semEff(sem_int, R = 50, ci.type =  "perc")
-summary(boot_int)
+summary(sem_int_basic)$coefficients[, c(1, 2, 8, 9)]
+summary(sem_int_enrich)$coefficients[, c(1, 2, 8, 9)]
 ```
+
+```{r}
+boot_int_basic <- semEff(sem_int_basic, R = 50, ci.type =  "perc")
+boot_int_enrich <- semEff(sem_int_enrich, R = 50, ci.type =  "perc")
+summary(boot_int_basic)
+summary(boot_int_enrich)
+```
+```{r}
+tot_sem_int <- rbind(
+  from_semEff_to_table(boot_int_basic) %>%
+    mutate(productivity = "basic"),
+  from_semEff_to_table(boot_int_enrich) %>%
+    mutate(productivity = "enrichment")
+)
+```
+
+```{r}
+tot_sem_int %>%
+  filter(
+    effect_type == "total",
+    response %in% c("log_stab_com", "log_sync", "log_avg_cv_sp"),
+    !predictor %in% c("log_sync", "log_avg_cv_sp"),
+
+    ) %>%
+  ggplot(aes(
+      y = predictor, x = effect,
+      xmin = lower_ci, xmax = upper_ci,
+      color = productivity)
+    ) +
+  geom_pointrange() +
+  facet_grid(cols = vars(response))
+```
+
+# Effect of species richness
+
+```{r}
+unique(simZ$Z)
+```
+
+```{r}
+sim_rich_prod <- simZ %>%
+  filter(
+    Z == 100,
+    env_stoch == .5,
+    rho %in% c(0, 1)
+  )
+```
+
+```{r}
+p_sim_rich_prod <- sim_rich_prod %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  mutate(
+    metric = var_replacement()[metric],
+    rho = rho_replacement()[as.character(rho)]
+  ) %>%
+  ggplot(aes(x = richness, y = stab, color = factor(productivity))) +
+  geom_point(alpha = .1, shape = 20) +
+  geom_smooth() +
+  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
+  labs(
+    color = "Productivity",
+    x = "Species richness",
+    y = "Stability component"
+  ) +
+  scale_x_continuous(
+    sec.axis = sec_axis(~ . ,
+      name = "Response diversity",
+      breaks = NULL,
+      labels = NULL)
+  )
+ggsave(
+  filename = here::here("fig", "stability_rich.pdf"),
+  p_sim_rich_prod,
+  scale = 1.8,
+  width = 88,
+  height = 88 * .6,
+  units = "mm"
+)
+```
+
+```{r}
+sim_rich_prod %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  mutate(
+    metric = var_replacement()[metric],
+    rho = rho_replacement()[as.character(rho)]
+  ) %>%
+  ggplot(aes(x = avg_max_int_alive, y = stab, color = factor(productivity))) +
+  geom_point(alpha = .1, shape = 20) +
+  geom_smooth() +
+  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y")
+```
+
+```{r}
+library(easystats)
+
+sim_sem <- simZ %>%
+  filter(env_stoch == .5) %>%
+  mutate(across(c(sync, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
+  mutate(
+    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
+    productivity_f = factor(productivity)
+
+    ) %>%
+  as.data.frame() %>%
+  select(c(
+      ct_alive, log_richness, max_tlvl_alive, Z, rho, w_avg_tlvl_alive,
+      gini_max_int, avg_max_int_alive, log1_avg_max_int_alive, env_stoch,
+      log_stab_com, log_sync, log_avg_cv_sp, productivity, productivity_f)
+  )
+
+#model <- lm(log_stab_com ~ log_richness * log1_avg_max_int_alive * rho * productivity_f, data = sim_sem)
+#
+#vizdata <- sim_sem %>%
+#  visualisation_matrix(at = c("log_richness", "log1_avg_max_int_alive"), length = 2) %>%
+#  visualisation_matrix("ct_alive", length = 3, numerics = "all")
+#vizdata$Predicted <- insight::get_predicted(model, vizdata)
+#vizdata
+```
+
+```{r}
+sim_sem %>%
+  filter(log1_avg_max_int_alive > 0, rho == 0) %>%
+  mutate(
+   cat_log1_avg_max_int_alive = cut(
+     log1_avg_max_int_alive,
+     breaks= 3, ordered_result = TRUE)
+
+  ) %>%
+  ggplot(aes(x = log_richness, y = log_stab_com, color =
+      cat_log1_avg_max_int_alive)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_grid(cols = vars(productivity_f)) +
+  #  geom_line(data = vizdata, aes(y = Predicted, group = log1_avg_max_int_alive), size = 1) +
+  theme_modern()
+```
+
+```{r}
+sim_sem %>%
+  filter(rho == 0) %>%
+  mutate(
+   cat_max_tlvl_alive = cut(
+     max_tlvl_alive,
+     breaks= 3, ordered_result = TRUE)
+  ) %>%
+  ggplot(aes(x = log_richness, y = log_stab_com, color =
+      cat_max_tlvl_alive)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_grid(cols = vars(productivity_f)) +
+  #  geom_line(data = vizdata, aes(y = Predicted, group = log1_avg_max_int_alive), size = 1) +
+  theme_modern()
+```
+
+```{r}
+sim_sem %>%
+  filter(rho == 0) %>%
+  mutate(
+   cat_w_avg_tlvl_alive = cut(
+     w_avg_tlvl_alive,
+     breaks= 3, ordered_result = TRUE)
+  ) %>%
+  ggplot(aes(
+      x = log_richness,
+      y = log_stab_com,
+      color = cat_w_avg_tlvl_alive)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_grid(cols = vars(productivity_f)) +
+  #  geom_line(data = vizdata, aes(y = Predicted, group = log1_avg_max_int_alive), size = 1) +
+  theme_modern()
+```
+
+```{r}
+sim_sem %>%
+  filter(rho == 0) %>%
+  mutate(
+   cat_ct_alive = cut(
+     ct_alive,
+     breaks = 3,
+     ordered_result = TRUE)
+  ) %>%
+  ggplot(aes(x = log_richness, y = log_stab_com, color =
+      cat_ct_alive)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_grid(cols = vars(productivity_f)) +
+  theme_modern()
+```
+
+```{r}
+sim_sem %>%
+  ggplot(aes(x = log_richness, y = log_stab_com, color =
+      as.factor(rho))) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_grid(cols = vars(productivity_f)) +
+  #  geom_line(data = vizdata, aes(y = Predicted, group = log1_avg_max_int_alive), size = 1) +
+  theme_modern()
+```
+
+```{r}
+sim_rich_prod %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  mutate(
+    metric = var_replacement()[metric],
+    rho = rho_replacement()[as.character(rho)]
+  ) %>%
+  ggplot(aes(x = max_tlvl_alive, y = stab, color = factor(productivity))) +
+  geom_point(alpha = .1, shape = 20) +
+  geom_smooth() +
+  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y")
+```

### 2023-04-17 R/cross_correlated_error.R

@@ -1,0 +1,24 @@
+# From
+# Ripa & Ives (2003): https://www.sciencedirect.com/science/article/pii/S0040580903000893
+# Vasseur & Fox (2007): http://doi.wiley.com/10.1111/j.1461-0248.2007.01099.x
+# Gouhier et al. (2010): https://www.journals.uchicago.edu/doi/full/10.1086/649579
+cross_correlated_response <- function(rho = 0, evt_sd = 1, n = 2, time_len = 100, return_tbl = TRUE) {
+
+  # Independant timeseries
+  a <- t(sapply(seq_len(n), function(x) rnorm(time_len, 0, evt_sd)))
+
+  cov_mat <- matrix(rho * evt_sd^2, nrow = nrow(a), ncol = nrow(a))
+  diag(cov_mat) <- evt_sd^2
+
+  out <- cov_mat %*% a
+
+  if (return_tbl) {
+
+    dfr <- as.data.frame(t(out))  %>%
+      mutate(time = seq_len(ncol(a))) %>%
+      pivot_longer(-time, names_to = "species", values_to = "error")
+    return(dfr)
+  }
+
+  return(out)
+}

### 2023-04-17 R/network_metrics.R

@@ -1,0 +1,5 @@
+gini <- function(x) {
+    n <- length(x)
+    xx <- sort(x)
+    2 * (sum(seq(1, n) * xx)) / (n * sum(xx)) - 1
+}

### 2023-04-17 R/sem_helpers.R

@@ -1,0 +1,44 @@
+get_table_semEff <- function(semeff = NULL) {
+
+  effect_type <-  c("^DIRECT", "^INDIRECT", "TOTAL", "MEDIATORS")
+  x  <- semeff[-1, ]
+  effect_type_col <- x[[1]]
+  predictor <- x[[2]]
+
+  row_effect_type <- map_int(effect_type, ~which(str_detect(x[[1]], .x)))
+
+  numeric_table <- map(x, as.numeric)
+  # suppr table columns
+  mask_chr_column <- map_lgl(numeric_table, ~all(is.na(.x)))
+  # Keep the second columns:
+  mask_chr_column[2] <- FALSE
+
+  tab <- x[, !mask_chr_column]
+  colnames(tab)[1] <- "predictor"
+
+  output <- rbind(
+    cbind(effect_type = "direct", tab[row_effect_type[1]:row_effect_type[2]-1, ]),
+    cbind(effect_type = "indirect", tab[row_effect_type[2]:row_effect_type[3]-1, ]),
+    cbind(effect_type = "total", tab[row_effect_type[3]:row_effect_type[4]-1, ]),
+    cbind(effect_type = "mediators", tab[row_effect_type[4]:nrow(tab), ])
+  )
+
+  numeric_rows <- str_detect(output[["Effect"]], "\\d")
+  output <- output[numeric_rows,]
+  output[, -c(1:2)] <- apply(output[, -c(1:2)], 2, as.numeric)
+
+  janitor::clean_names(output)
+}
+
+from_semEff_to_table <- function(x = NULL) {
+
+  output <- map_dfr(x$Summary[-1], get_table_semEff, .id = "response") %>%
+    as_tibble()
+
+  output[, c("response", "predictor")] <- apply(
+    output[, c("response", "predictor")], 2,
+    function(x) str_replace_all(x, c("\\." = "_", "\\s" = ""))
+  )
+  output[, colnames(output) != "bias"]
+
+}

### 2023-04-17 R/stability_decomposition.R

@@ -1,0 +1,72 @@
+statistical_averaging_effect <- function(mat) {
+
+  var_sp <- apply(mat, 2, var)
+  sd_sp <- apply(mat, 2, sd)
+
+  statistical_averaging <- sum(sd_sp) / sqrt(sum(var_sp))
+  statistical_averaging_even <- sqrt(ncol(mat))
+  eveness <- statistical_averaging / statistical_averaging_even
+
+  c(
+    total = statistical_averaging,
+    even = statistical_averaging_even,
+    eveness = eveness
+  )
+}
+
+compensatory_effect <- function(mat) {
+  cov_mat <- cov(mat)
+  var_sp <- diag(cov_mat)
+  var_tot <- sum(cov_mat)
+  sqrt(sum(var_sp)) / sqrt(var_tot)
+}
+
+asynchrony <- function(mat) {
+
+  cov_mat <- cov(mat)
+  var_sp <- diag(cov_mat)
+  var_tot <- sum(cov_mat)
+
+  sum(sqrt(var_sp)) / sqrt(var_tot)
+}
+
+population_stability <- function(mat) {
+
+  bm_sp <- colMeans(mat)
+  bm_tot <- sum(bm_sp)
+
+  sd_sp <- apply(mat, 2, sd)
+
+  bm_tot / sum(sd_sp)
+}
+
+community_stability <- function(mat) {
+
+  bm_sp <- colMeans(mat)
+  bm_tot <- sum(bm_sp)
+
+  cov_mat <- cov(mat)
+  var_tot <- sum(cov_mat)
+
+  bm_tot / sqrt(var_tot)
+}
+
+compensatory_effect_env <- function(mat, rho = 0) {
+  cov_mat <- cov(mat)
+  sd_sp <- sqrt(diag(cov_mat))
+
+  # Build variance-covariance matrix with rho as species cross correlation
+  env_mat <- matrix(data = NA, ncol = length(sd_sp), nrow = length(sd_sp))
+  for (i in seq_along(sd_sp)) {
+    env_mat[i, ] <- sd_sp[i] * sd_sp
+  }
+  diag_env_mat <- diag(env_mat)
+  env_mat <- env_mat * rho
+  diag(env_mat) <- diag_env_mat
+
+  sqrt(sum(diag(cov_mat))) / sqrt(sum(env_mat))
+}
+
+compensatory_effect_int <- function(mat, rho = 0) {
+ compensatory_effect(mat) / compensatory_effect_env(mat, rho = rho)
+}

### 2023-04-17 job/job_sharc.sh

@@ -2,7 +2,7 @@
 
 
 # Job name
-#$ -N cs_stoch 
+#$ -N cs_stoch
 
 # Error message
 #$ -e cs_stoch.error
@@ -16,6 +16,6 @@ DIR_ENV=/home/${USER}/xStressorsStabBEFW
 DIR_SCRIPT=use_case
 
 # Load modules
-module load apps/julia
+module load apps/julia/1.8.5/binary
 
 julia --project=${DIR_ENV} ${DIR_ENV}/${DIR_SCRIPT}/connectance_richness_stoch.jl ${DIR_ENV} #vasseur_fox_2007.jl

### 2023-04-17 misc/species_coherence_response.R

@@ -36,22 +36,28 @@ cross_correlated_response <- function(rho = 0, evt_sd = 1, n = 2, time_len = 100
 
 # With two species
 ti <- tibble(
-  rho = c(0, .8, -.8),
+  rho = c(0, .8),
   noise = map(rho, ~cross_correlated_response(rho = .x, evt_sd = 1, n = 2, time_len = 20))
 )
 
 
 p <- ti %>%
   unnest(noise) %>%
-  ggplot(aes(x = time, y = error, color = species))+
+  ggplot(aes(x = time, y = error, color = species)) +
   geom_line() +
-  facet_grid(cols = vars(rho)) +
+  labs(x = "Time", y = "Error") +
+  facet_grid(rows = vars(rho)) +
+  viridis::scale_color_viridis(discrete = TRUE) +
   cowplot::theme_half_open() +
   theme(legend.position = "none")
 
-save_plot(
-  "~/Téléchargements/coherence_two_sp.png",
-  p
+ggsave(
+  filename = here::here("fig", "coherence_two_sp.pdf"),
+  p,
+  scale = 1.5,
+  width = 88,
+  height = 88 * 1.1,
+  units = "mm"
 )
 
 # With four species

### 2023-05-13 report/cs_analysis.Rmd
Update report

--- 2023-02-24 report/cs_analysis.Rmd
@@
 library(arrow)
+library(piecewiseSEM)
+library(semEff)
+library(easystats)
+library(glmmTMB)
 
@@
 theme(legend.position = "bottom")
+theme_set(mytheme)
+source(here::here("R", "network_metrics.R"))
+source(here::here("R", "string_replacements.R"))
+```
 
-theme_set(mytheme)
+```{r}
+sim_files <- list.files(here("res", "simCSZenrich"))
+sim_list <- map(sim_files, function (x) {
+  open_dataset(here::here("res", "simCSZenrich", x),
+    format = "arrow") %>%
+  collect()
+})
 ```
+
 ```{r}
-sim_brut <- open_dataset(here::here("res", "sim_cs_stdK.arrow"),
-  format = "arrow")
-sim <- sim_brut %>%
-  collect() %>%
+# TODO set extinction threshold in simulations
+simZ_prep <- map_dfr(sim_list,
+  function (x) {
+    x %>%
+      # Remove simulation that have failed to run
+      filter(!is.na(richness)) %>%
+      # Transform back interaction strength into matrices
       mutate(across(where(is.list), as.list)) %>%
@@
         ) %>%
+      # Get matrix of alive species
       mutate(max_int_alive  = map2(max_int, bm_sp,
           function(mat, bm) {
-        mask <- bm > 10^-16
-        mat[mask, mask]
-      }
-      ),
-    ct_alive = map_dbl(max_int_alive, ~ sum(.x > 0) / ((ncol(.x) - 1)^2)),
-    bm_sp_alive = map(bm_sp, ~.x[.x > 10^-16]),
-    tlvl_alive = map2(tlvl, bm_sp, ~.x[.y > 10^-16]),
-    max_tlvl_alive = map_dbl(tlvl_alive, max),
-    w_avg_tlvl_alive = map2_dbl(tlvl_alive, bm_sp_alive, ~sum(.x * (.y / sum(.y)))),
-    max_max_int_alive = map_dbl(max_int_alive, ~max(.x[.x > 0])),
-    avg_max_int_alive = map_dbl(max_int_alive, ~mean(.x[.x > 0])),
-    #gini_max_int_alive = map_dbl(max_int_alive, ),
-  )
-```
-```{r}
-simZ <- open_dataset(here::here("res", "sim_csZ.arrow"),
-  format = "arrow") %>%
-  collect() %>%
-  filter(!is.na(richness)) %>%
-  mutate(across(where(is.list), as.list)) %>%
-  mutate(across(c(int_strength, max_int),
-      ~map2(.x, S,
-        function(y, rich) {
-          matrix(y, nrow = rich)
+            mask <- bm > 10^-6
+            mat[mask, mask, drop = FALSE]
           }
@@
         )
-    ) %>%
-  mutate(max_int_alive  = map2(max_int, bm_sp,
-      function(mat, bm) {
-        mask <- bm > 10^-16
-        mat[mask, mask]
   }
-      ),
-    ct_alive = map_dbl(max_int_alive, ~ sum(.x > 0) / ((ncol(.x) - 1)^2)),
-    bm_sp_alive = map(bm_sp, ~.x[.x > 10^-16]),
-    tlvl_alive = map2(tlvl, bm_sp, ~.x[.y > 10^-16]),
+)
+# Compute metrics of interest
+simZ <- simZ_prep %>%
+  mutate(
+    persistence = richness / S,
+    async = 1 / sync,
+    stab_pop = 1 / avg_cv_sp,
+    ct_alive = map_dbl(max_int_alive,
+      ~ifelse(sum(.x) == 0, 0,
+      sum(.x > 0) / ((ncol(.x))^2))),
+    bm_sp_alive = map(bm_sp, ~.x[.x > 10^-6]),
+    tlvl_alive = map2(tlvl, bm_sp, ~.x[.y > 10^-6]),
     max_tlvl_alive = map_dbl(tlvl_alive, max),
     w_avg_tlvl_alive = map2_dbl(tlvl_alive, bm_sp_alive, ~sum(.x * (.y / sum(.y)))),
-    max_max_int_alive = map_dbl(max_int_alive, ~max(.x[.x > 0])),
-    avg_max_int_alive = map_dbl(max_int_alive, ~mean(.x[.x > 0])),
-    #gini_max_int_alive = map_dbl(max_int_alive, ),
+    max_max_int_alive = map_dbl(max_int_alive,
+      ~ifelse(length(.x[.x > 0]) == 0, 0, max(.x[.x > 0]))
+      ),
+    avg_max_int_alive = map_dbl(max_int_alive,
+      ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
+      ),
+    gini_max_int_alive = map_dbl(max_int_alive, ~gini(.x))
       )
+simZ$tlvl_alive[[3]]
+simZ$max_int_alive[[3]]
 ```
@@
 colnames(sim)
-unique(sim$env_stoch)
-summary(sim$total_biomass)
+unique(simZ$env_stoch)
+summary(simZ$total_biomass)
+summary(simZ$persistence)
+summary(simZ$ct_alive)
+summary(simZ$gini_max_int_alive)
 ```
@@
 ```{r}
-sim %>%
-  mutate(stab_pop = 1/ avg_cv_sp) %>%
+simZ %>%
+  filter(rho == 0) %>%
   pivot_longer(
-    c(stab_com, stab_pop, sync),
+    c(stab_com, stab_pop, sync, total_biomass),
     names_to = "metric",
     values_to = "stab") %>%
-  ggplot(aes(x = richness, y = stab)) +
+  ggplot(aes(x = richness, y = stab, color = factor(env_stoch))) +
   geom_point() +
-  facet_grid(rows = vars(metric), scales = "free_y") +
+  facet_grid(rows = vars(metric), cols = vars(productivity), scales = "free_y") +
   labs(
-    color = "Connectance",
+    color = "Evironmental stochasticity",
     x = "Species richness",
@@
 ```{r}
-corrplot::corrplot(
-  cor(sim %>% select(
-      c(S, richness, ct, ct_alive, total_biomass, avg_max_int_alive, w_avg_tlvl_alive,
-        max_tlvl_alive, rho, env_stoch, stab_com, avg_cv_sp, sync
+simZ %>%
+  filter(rho == 1) %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync, total_biomass),
+    names_to = "metric",
+    values_to = "stab") %>%
+  ggplot(aes(x = richness, y = stab, color = factor(env_stoch))) +
+  geom_point() +
+  facet_grid(rows = vars(metric), cols = vars(productivity), scales = "free_y") +
+  labs(
+    color = "Evironmental stochasticity",
+    x = "Species richness",
+    y = "Stability component"
   )
-      ),
+```
+
+```{r}
+p_basic <- ~corrplot::corrplot(
+  cor(simZ %>%
+    filter(productivity == "enrichment") %>%
+    select(c(S, richness, ct, Z, ct_alive, total_biomass, avg_max_int_alive,
+        w_avg_tlvl_alive, max_tlvl_alive, rho, env_stoch, stab_com, avg_cv_sp,
+        sync)),
     method = "spearman"),
   diag = FALSE, type = "upper"
+)
+p_enrich <- ~corrplot::corrplot(
+  cor(simZ %>%
+    filter(productivity == "basic") %>%
+    select(c(S, richness, ct, Z, ct_alive, total_biomass, avg_max_int_alive,
+        w_avg_tlvl_alive, max_tlvl_alive, rho, env_stoch, stab_com, avg_cv_sp,
+        sync)),
+    method = "spearman"),
+  diag = FALSE, type = "upper"
+)
+plot_grid(
+  ggdraw(p_basic),
+  ggdraw(p_enrich),
+  nrow = 2
 )
@@
 
-It seems that the effects of food-web structure are mainly richness effects!
+```{r}
+compute_rotated_pca <- function(.data = NULL, naxis = 2) {
+  .data <- na.omit(.data)
+  pca <- ade4::dudi.pca(as.data.frame(.data),
+    scannf = FALSE, nf = naxis, center = TRUE, scale = TRUE
+  )
+  pca_rotated <- psych::principal(.data,
+    rotate = "varimax", nfactors = naxis,
+    scores = TRUE
+  )
+
+  return(list(normal = pca, rotated = pca_rotated))
+}
+```
 
 ```{r}
-sim %>%
+sim_sem <- simZ %>%
+  filter(rho == 0) %>%
+  mutate(across(c(async, sync, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
+  mutate(
+    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
+    productivity_f = factor(productivity)
+
+    ) %>%
+  as.data.frame() %>%
+  select(c(
+      ct_alive, log_richness, max_tlvl_alive, Z,
+      gini_max_int, avg_max_int_alive, log1_avg_max_int_alive, env_stoch,
+      log_stab_com, log_sync, log_async, log_avg_cv_sp, productivity, productivity_f)
+  )
+scaled_sim_sem <- sim_sem %>%
+  mutate(across(where(is.double), ~scale(.x)[,1]))
+```
+
+```{r}
+pred_may <- "log1_avg_max_int_alive*log_richness*ct_alive*productivity + env_stoch"
+rand <- "(1 | Z)"
+
+mod_may_single <- lm(formula(str_replace_all(paste0("log_stab_com ~ ", pred_may), "\\*", "+")),
+  scaled_sim_sem)
+performance::check_collinearity(mod_may_single)
+```
+
+```{r}
+mod_may <- glmmTMB(formula(paste0("log_stab_com ~ ", pred_may, " + ", rand)), scaled_sim_sem)
+
+r2_nakagawa(mod_may)
+par_mod_may <- parameters(mod_may)
+plot(parameters(mod_may))
+```
+
+```{r}
+mod_may_sync <- glmmTMB(formula(paste0("log_sync ~ ", pred_may, " + ", rand)),
+  scaled_sim_sem)
+r2_nakagawa(mod_may_sync)
+plot(parameters(mod_may_sync))
+```
+
+```{r}
+mod_may_cv_sp <- glmmTMB(formula(paste0("log_avg_cv_sp ~ ", pred_may, " + ", rand)),
+  scaled_sim_sem)
+r2_nakagawa(mod_may_cv_sp)
+plot(parameters(mod_may_cv_sp))
+```
+
+## Rho model
+
+- Should be include also the monotrophic communities ? I.e. Communities
+  containing only plants?
+
+```{r}
+sim_rho <- simZ %>%
+  #filter(ct_alive != 0) %>%
+  mutate(across(c(async, sync, stab_pop, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
+  mutate(
+    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
+    productivity_f = factor(productivity)
+
+    ) %>%
+  select(c(
+      ct_alive, log_richness, max_tlvl_alive, Z, rho,
+      gini_max_int, avg_max_int_alive, log1_avg_max_int_alive, env_stoch,
+      log_stab_com, log_sync, log_async, log_stab_pop, log_avg_cv_sp, productivity, productivity_f,
+      persistence)
+  )
+sim_rho_scaled <- sim_rho %>%
+  mutate(across(where(is.double), ~scale(.x)[,1]))
+```
+
+```{r}
+sim_rho %>%
+  filter(ct_alive == 0, env_stoch == 0.5) %>%
+  ggplot(aes(x = log_richness, y = log_stab_com)) +
+  geom_point() +
+  geom_smooth() +
+  facet_grid(cols = vars(rho), rows = vars(productivity_f))
+```
+
+```{r}
+pred_rho <- "log_richness +
+ct_alive +
+log1_avg_max_int_alive +
+productivity +
+rho +
+I(rho^2) +
+env_stoch +
+
+log_richness:ct_alive +
+log_richness:log1_avg_max_int_alive +
+log_richness:productivity +
+log_richness:rho +
+
+log1_avg_max_int_alive:ct_alive +
+log1_avg_max_int_alive:productivity +
+log1_avg_max_int_alive:rho +
+
+ct_alive:rho +
+ct_alive:productivity +
+rho:productivity +
+I(rho^2):productivity +
+
+log_richness:log1_avg_max_int_alive:ct_alive +
+log_richness:log1_avg_max_int_alive:productivity +
+log_richness:log1_avg_max_int_alive:rho +
+log_richness:ct_alive:productivity +
+log_richness:ct_alive:rho +
+log_richness:rho:productivity +
+
+log1_avg_max_int_alive:ct_alive:rho +
+log1_avg_max_int_alive:ct_alive:productivity +
+log1_avg_max_int_alive:rho:productivity +
+
+ct_alive:rho:productivity"
+rand <- "(1 | Z)"
+
+mod_rho_single <- lm(formula(str_replace_all(paste0("log_stab_com ~ ", pred_rho), "(\\*|:)", "+")),
+  sim_rho_scaled)
+performance::check_collinearity(mod_rho_single)
+```
+
+```{r}
+model2tibble <- function(x, response = NULL) {
+  out <- parameters(x) %>%
+    filter(Effects == "fixed", Parameter != "(Intercept)") %>%
+    as_tibble() %>%
+    janitor::clean_names() %>%
+    mutate(
+      response = var_replacement()[as.character(formula(x)[2])],
+      parameter = str_replace_all(parameter, var_replacement()),
+      count_int = str_count(parameter, ":"),
+      effect_type = case_when(
+        count_int == 0 ~ "single",
+        count_int == 1 ~ "double",
+        count_int == 2 ~ "triple",
+        TRUE ~ "other"
+
+      )
+    ) %>%
+    select(response, parameter:ci_high, effect_type)
+    out
+}
+plot_effect_type <- function(x) {
+  effect <- c("single", "double", "triple")
+  p <- map(effect,
+    function(y) {
+      x %>%
+        filter(effect_type == y) %>%
+        arrange(coefficient) %>%
+        ggplot(aes(
+            y = reorder(parameter, -coefficient),
+            x = coefficient,xmin = ci_low, xmax = ci_high,
+            color = response
+            )) +
+        geom_vline(xintercept = 0, color = "black", linetype = "dashed", linewidth = 1.5) +
+        geom_pointrange(position = position_dodge(width = 0.5)) +
+        labs(x = "Standardized Coefficients")
+    }
+  )
+  names(p) <- effect
+  p
+}
+```
+
+```{r}
+mod_rho_scaled <- map(setNames(
+    c("log_stab_com", "log_stab_pop", "log_async"),
+    c("log_stab_com", "log_stab_pop", "log_async")
+    ),
+  function (x) {
+    glmmTMB(formula(paste0(x, " ~ ", pred_rho, " + ", rand)),
+      sim_rho_scaled)
+  }
+)
+coef_mod_rho_scaled <- map_dfr(mod_rho_scaled, ~model2tibble(.x))
+ti <- map_dfr(mod_rho_scaled, ~as.data.frame(r2_nakagawa(.x)), .id = "response") %>%
+  mutate(response = var_replacement()[response])
+p_mod_rho_scaled <- plot_effect_type(coef_mod_rho_scaled)
+plot_grid(plotlist = p_mod_rho_scaled)
+```
+
+```{r}
+mod_rho <- map(setNames(
+    c("log_stab_com", "log_stab_pop", "log_async"),
+    c("log_stab_com", "log_stab_pop", "log_async")
+    ),
+  function (x) {
+    glmmTMB(formula(paste0(x, " ~ ", pred_rho, " + ", rand)),
+      sim_rho)
+  }
+)
+coef_mod_rho <- map_dfr(mod_rho, ~model2tibble(.x))
+ti <- map_dfr(mod_rho, ~as.data.frame(r2_nakagawa(.x)), .id = "response") %>%
+  mutate(response = var_replacement()[response])
+p_mod_rho <- plot_effect_type(coef_mod_rho)
+plot_grid(plotlist = p_mod_rho)
+```
+
+```{r, eval = FALSE}
+sim_rho
+```
+
+```{r}
+pred_list <- list(
+  log_richness = c(log(1), log(5), log(10), log(20), log(30), log(50)),
+  ct_alive = c(0, .10, .20),
+  rho = c(0, .5, 1),
+  log1_avg_max_int_alive = c(log(0 + 1), round(log(.81 + 1), 1), round(log(5.65 + 1), 1)),
+  env_stoch = .5,
+  productivity = c("basic", "enrichment"),
+  Z = 100
+)
+pred_rho <- expand.grid(pred_list) %>%
+  filter(
+    !(log1_avg_max_int_alive == 0 & ct_alive != 0 | ct_alive == 0 & log1_avg_max_int_alive != 0)
+  )
+
+pred_rho$log_stab_com <- predict(mod_rho[["log_stab_com"]], newdata = pred_rho)
+
+pred_rho %>%
+  ggplot(aes(
+      y = log_stab_com,
+      x = log_richness,
+      color = factor(ct_alive),
+      linewidth = factor(log1_avg_max_int_alive)
+      )) +
+  geom_line() +
+  facet_grid(
+    rows = vars(rho),
+    cols = vars(productivity)
+  )
+```
+
+```{r, eval = FALSE}
+mod_rho_tot <- glmmTMB(
+  log_stab_com ~ log1_avg_max_int_alive*log_richness*ct_alive*rho*productivity +
+    env_stoch + (1 | Z),
+  sim_rho_scaled)
+coef_mod_rho_tot <- model2tibble(mod_rho_tot)
+coef_mod_rho_tot %>%
+  ggplot(aes(y = parameter, x = coefficient, xmin = ci_low, xmax = ci_high)) +
+  geom_pointrange() +
+  labs(x = "Standardized Coefficients")
+```
+
+```{r}
+sim_rho_pers <- simZ %>%
+  mutate(across(c(S, ct, avg_max_int, gini_max_int), log, , .names = "log_{.col}")) %>%
+  mutate(
+    log1_avg_max_int = log(avg_max_int + 1),
+    productivity_f = factor(productivity)
+    ) %>%
+  as.data.frame() %>%
+  select(c(
+      log_S, ct, max_tlvl, Z, rho,
+      gini_max_int, avg_max_int, log1_avg_max_int, env_stoch,
+      productivity, productivity_f,
+      persistence)
+  )
+sim_rho_pers_scaled <- sim_rho_pers %>%
+  mutate(across(where(is.double), ~scale(.x)[,1]))
+
+pred_rho_pers <- "log1_avg_max_int * log_S * rho +
+log1_avg_max_int * log_S * productivity +
+log1_avg_max_int * log_S * ct +
+log1_avg_max_int * ct * rho +
+log1_avg_max_int * ct * rho +
+log1_avg_max_int * ct * productivity +
+log_S * rho * productivity +
+log_S * ct * productivity +
+log_S * ct * rho +
+env_stoch"
+rand <- "(1 | Z)"
+
+mod_rho_pers <- glmmTMB(formula(paste0("persistence ~ ", pred_rho_pers, " + ", rand)),
+  sim_rho_pers_scaled)
+
+r2_nakagawa(mod_rho_pers)
+plot(parameters(mod_rho_pers))
+```
+
+## Regression tree
+
+```{r}
+```
+
+```{r, eval = FALSE}
+library(rpart)
+library(rpart.plot)
+set.seed(123)
+m1 <- rpart(
+  formula = log_stab_com ~ .,
+  data    = sim_rho %>%
+    select(log_stab_com, log_richness, ct_alive, rho, env_stoch,
+      gini_max_int, max_tlvl_alive, log1_avg_max_int_alive, productivity),
+  method  = "anova"
+  )
+rpart.plot(m1)
+```
+
+```{r, eval=FALSE}
+bagged_m1 <- bagging(
+  formula = log_stab_com ~ .,
+  data    = sim_rho %>%
+    select(log_stab_com, log_richness, ct_alive, rho, env_stoch,
+      gini_max_int, max_tlvl_alive, log1_avg_max_int_alive, productivity),
+  coob    = TRUE
+)
+```
+
+```{r}
+library(ipred)
+ctrl <- trainControl(method = "cv",  number = 10)
+
+# CV bagged model
+bagged_cv <- train(
+  Sale_Price ~ .,
+  data = ames_train,
+  method = "treebag",
+  trControl = ctrl,
+  importance = TRUE
+  )
+```
+
+# Effect of species richness
+
+```{r}
+sim_rich_prod <- simZ %>%
+  filter(
+    Z == 100,
+    env_stoch == .5,
+    rho %in% c(0, 1)
+  )
+```
+
+```{r}
+p_sim_rich_prod <- sim_rich_prod %>%
   mutate(stab_pop = 1/ avg_cv_sp) %>%
@@
     values_to = "stab") %>%
-  ggplot(aes(x = avg_max_int_alive, y = stab, color = richness)) +
-  geom_point() +
+  mutate(
+    metric = var_replacement()[metric],
+    rho = rho_replacement()[as.character(rho)]
+  ) %>%
+  ggplot(aes(x = richness, y = stab, color = factor(productivity))) +
+  geom_point(alpha = .1, shape = 20) +
   geom_smooth() +
-  facet_grid(rows = vars(metric), scales = "free_y") +
+  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
   labs(
-    color = "Richness",
-    x = "Avg interaction strength",
+    color = "Productivity",
+    x = "Species richness",
     y = "Stability component"
+  ) +
+  scale_x_continuous(
+    sec.axis = sec_axis(~ . ,
+      name = "Response diversity",
+      breaks = NULL,
+      labels = NULL)
   )
-
-```
-
-```{r}
-sim%>%
-  mutate(stab_pop = 1/ avg_cv_sp) %>%
-  pivot_longer(
-    c(stab_com, stab_pop, sync),
-    names_to = "metric",
-    values_to = "stab") %>%
-  ggplot(aes(x = gini_max_int, y = stab, color = richness)) +
-  geom_point() +
-  geom_smooth() +
-  facet_grid(rows = vars(metric), scales = "free_y") +
-  labs(
-    color = "Richness",
-    x = "Gini interaction strength",
-    y = "Stability component"
-  )
-
-```
-
-```{r}
-sim %>%
-  mutate(stab_pop = 1/ avg_cv_sp) %>%
-  pivot_longer(
-    c(stab_com, stab_pop, sync),
-    names_to = "metric",
-    values_to = "stab") %>%
-  ggplot(aes(x = ct_alive, y = stab, color = richness)) +
-  geom_point() +
-  geom_smooth(method = "lm") +
-  facet_grid(rows = vars(metric), scales = "free_y") +
-  labs(
-    color = "Richness",
-    x = "Connectance",
-    y = "Stability component"
+ggsave(
+  filename = here::here("fig", "stability_rich.pdf"),
+  p_sim_rich_prod,
+  scale = 1.8,
+  width = 88,
+  height = 88 * .6,
+  units = "mm"
 )
 ```
-
-```{r}
-sim %>%
-  mutate(stab_pop = 1/ avg_cv_sp) %>%
-  pivot_longer(
-    c(stab_com, stab_pop, sync),
-    names_to = "metric",
-    values_to = "stab") %>%
-  ggplot(aes(x = max_tlvl_alive, y = stab, color = richness)) +
-  geom_point() +
-  geom_smooth() +
-  facet_grid(rows = vars(metric), scales = "free_y") +
-  labs(
-    color = "Richness",
-    x = "Avg trophic level",
-    y = "Stability component"
-  )
-```
-
-# SEM
-
-```{r}
-library(piecewiseSEM)
-library(semEff)
-```
-
-```{r}
-sim_sem <- sim %>%
-  filter(rho == 0, env_stoch == .5) %>%
-  mutate(across(c(sync, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}"))
-```
-
-```{r}
-pairs(
-  sim_sem %>%
-    select(ct_alive, log_richness, max_tlvl_alive,
-      log_gini_max_int, log_avg_max_int_alive, log_sync,
-      log_avg_cv_sp, log_stab_com),
-    pch = 19)
-```
-
-```{r}
-sem_list <- list(
-  max_tlvl = lm(max_tlvl_alive ~ log_richness + ct_alive, sim_sem),
-  gini_max_int = lm(gini_max_int ~ log_richness + ct_alive + max_tlvl_alive, sim_sem),
-  log_avg_max_int = lm(log_avg_max_int_alive ~ log_richness + ct_alive + max_tlvl_alive, sim_sem),
-  log_sync = lm(log_sync ~ ct_alive + log_richness + max_tlvl_alive + gini_max_int, sim_sem),
-  log_avg_cv_sp = lm(log_avg_cv_sp ~ ct_alive + log_richness + max_tlvl_alive +  gini_max_int, sim_sem),
-  log_stab_com = lm(log_stab_com ~ log_sync + log_avg_cv_sp, sim_sem)
-)
-
-sem <- as.psem(sem_list)
-```
-
-```{r}
-map_dfr(setNames(sem_list, names(sem_list)), performance::check_collinearity)
-map_dfr(sem_list, rsquared)
-summary(sem)$coefficients[, c(1, 2, 8, 9)]
-```
-
-```{r}
-plot(sem)
-```
-
-```{r}
-boot_eff <- semEff(sem, R = 50, ci.type =  "perc")
-summary(boot_eff)
-```
-
-```{r}
-sem_int_list <- list(
-  max_tlvl = lm(max_tlvl_alive ~ log_richness + ct_alive, sim_sem),
-  gini_max_int = lm(gini_max_int ~ log_richness + ct_alive + max_tlvl_alive, sim_sem),
-  log_avg_max_int = lm(log_avg_max_int_alive ~ log_richness + ct_alive + max_tlvl_alive, sim_sem),
-  log_sync = lm(log_sync ~ log_richness + log_avg_max_int_alive + max_tlvl_alive + gini_max_int, sim_sem),
-  log_avg_cv_sp = lm(log_avg_cv_sp ~ log_richness + log_avg_max_int_alive + max_tlvl_alive + gini_max_int, sim_sem),
-  log_stab_com = lm(log_stab_com ~ log_sync + log_avg_cv_sp, sim_sem)
-)
-
-sem_int <- as.psem(sem_int_list)
-plot(sem_int)
-```
-
-```{r}
-map(setNames(sem_int_list, names(sem_int_list)), performance::check_collinearity)
-map_dfr(sem_int_list, rsquared)
-summary(sem_int)$coefficients[, c(1, 2, 8, 9)]
-```
-
-```{r}
-boot_int <- semEff(sem_int, R = 50, ci.type =  "perc")
-summary(boot_int)
-```
-
-# With Z
-
-```{r}
-colnames(simZ)
-corrplot::corrplot(
-  cor(simZ %>%
-    mutate(persistence = richness / S) %>%
-    select(
-      c(S, richness, persistence, ct, ct_alive, total_biomass, avg_max_int_alive,
-        max_max_int_alive, gini_max_int, w_avg_tlvl_alive, max_tlvl_alive, Z,
-        rho, env_stoch, stab_com, avg_cv_sp, sync
-        )
-      ),
-    method = "spearman"),
-  diag = FALSE, type = "upper"
-)
-```

### 2023-05-13 R/string_replacements.R

@@ -1,0 +1,28 @@
+var_replacement <- function() {
+  c(
+    stab_com = "Community stability",
+    log_stab_com = "Community stability",
+    stab_pop = "Population stability",
+    log_stab_pop = "Population stability",
+    log_avg_cv_sp = "Population variability",
+    sync = "Synchrony",
+    log_sync = "Synchrony",
+    log_async = "Asynchrony",
+    async = "Asynchrony",
+    log1_avg_max_int_alive = "Interaction strength",
+    ct_alive = "Connectance",
+    log_richness = "Richness",
+    rho = "Env Corr",
+    productivityenrichment = "Enrichment",
+    env_stoch = "Env variance"
+
+  )
+}
+rho_replacement <- function() {
+  c(
+    `0` = "Maximum",
+    `0.5` = "Medium",
+    `1` = "No"
+  )
+
+}

### 2023-05-14 _targets.Rmd
Add targets for result analysis

---
title: "Target Markdown"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Target Markdown is a powerful R Markdown interface for reproducible analysis pipelines, and the chapter at https://books.ropensci.org/targets/markdown.html walks through it in detail. This R Markdown report the example from the chapter. Try it out in both interactive and non-interactive modes, either by running the code chunks in different ways or setting the `tar_interactive` chunk option.

# Packages

The example requires several R packages, and `targets` must be version 0.5.0.9000 or above.

```{r, eval = FALSE}
install.packages(c("biglm", "dplyr", "ggplot2", "readr", "targets", "tidyr"))
```

# Setup

If you are using old versions of `targets` (<= 0.7.0) and/or `knitr` (<= 1.33), you will need to load the `targets` package in the R Markdown document in order for Target Markdown code chunks to work.

```{r}
library(targets)
```

Near the top of the document, you may also wish to remove the `_targets_r` directory previously written by non-interactive runs of the report. Otherwise, your pipeline may contain superfluous targets.

```{r}
library(targets)
tar_unscript()
```

# Globals

We first define some global options/functions common to all targets. The function below plots a histogram of ozone concentrations, and our histogram target will need it.

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB"))
source(here::here("R", "network_metrics.R"))
source(here::here("R", "string_replacements.R"))
```

# Targets

Our first target borrows the `airquality` dataset built into base R.

```{targets raw-data}
list(
  tar_target(sim_list, {
    sim_files <- list.files(here("res", "simCSZenrich"))
    map(sim_files,
      function (x) {
        open_dataset(here::here("res", "simCSZenrich", x),
          format = "arrow") %>%
        collect()
      })
}
    ),
  tar_target(simZ_prep,
    map_dfr(sim_list,
      function (x) {
        x %>%
          # Remove simulation that have failed to run
          filter(!is.na(richness)) %>%
          # Transform back interaction strength into matrices
          mutate(across(where(is.list), as.list)) %>%
          mutate(across(c(int_strength, max_int),
              ~map2(.x, S,
                function(y, rich) {
                  matrix(y, nrow = rich)
                }
              )
          )
            ) %>%
          # Get matrix of alive species
          mutate(max_int_alive  = map2(max_int, bm_sp,
              function(mat, bm) {
                mask <- bm > 10^-6
                mat[mask, mask, drop = FALSE]
              }
            )
          )
      }
    )
    ),
  tar_target(simZ,
    simZ_prep %>%
      mutate(
        persistence = richness / S,
        async = 1 / sync,
        stab_pop = 1 / avg_cv_sp,
        ct_alive = map_dbl(max_int_alive,
          ~ifelse(sum(.x) == 0, 0,
            sum(.x > 0) / ((ncol(.x))^2))),
        bm_sp_alive = map(bm_sp, ~.x[.x > 10^-6]),
        tlvl_alive = map2(tlvl, bm_sp, ~.x[.y > 10^-6]),
        max_tlvl_alive = map_dbl(tlvl_alive, max),
        w_avg_tlvl_alive = map2_dbl(tlvl_alive, bm_sp_alive,
          ~sum(.x * (.y / sum(.y)))
          ),
        max_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, max(.x[.x > 0]))
          ),
        avg_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
          ),
        sd_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, sd(.x[.x > 0]))
          ),
        cv_max_int_alive = sd_max_int_alive / avg_max_int_alive,
        gini_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, gini(.x[.x > 0])))
      )
  )
)
```

```{targets sim_rho, tar_simple = TRUE}
simZ %>%
  mutate(across(c(async, sync, stab_pop, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
  mutate(
    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
    productivity_f = factor(productivity)
    ) %>%
  select(c(
      ct_alive, log_richness, max_tlvl_alive, Z, rho,
      gini_max_int, avg_max_int_alive, log1_avg_max_int_alive, env_stoch,
      log_stab_com, log_sync, log_async, log_stab_pop, log_avg_cv_sp, productivity, productivity_f,
      persistence)
  )
```

```{targets sim_rho_scaled, tar_simple = TRUE}
sim_rho %>%
  mutate(across(where(is.double), ~scale(.x)[,1]))
```

# Pipeline

If you ran all the `{targets}` chunks in non-interactive mode, then your R scripts are set up to run the pipeline.

```{r}
tar_make()
```

# Output

You can retrieve results from the `_targets/` data store using `tar_read()` or `tar_load()`.

```{r, message = FALSE}
library(tidyverse)
library(magrittr)
library(cowplot)
library(here)
library(arrow)
library(piecewiseSEM)
library(semEff)
library(easystats)
library(glmmTMB)
library(biglm)
```

```{r}
tar_read(sim_rho)
```

The `targets` dependency graph helps your readers understand the steps of your pipeline at a high level.

```{r}
tar_visnetwork()
```

At this point, you can go back and run `{targets}` chunks in interactive mode without interfering with the code or data of the non-interactive pipeline.

### 2023-05-14 report/cs_analysis.Rmd
Add targets for result analysis

@@
 library(magrittr)
+library(ggcorrplot)
 library(cowplot)
@@
 library(glmmTMB)
+library(targets)
+
+library(rpart)
+library(rpart.plot)
+library(caret)
+library(ipred)
 
@@
 
-```{r}
-sim_files <- list.files(here("res", "simCSZenrich"))
-sim_list <- map(sim_files, function (x) {
-  open_dataset(here::here("res", "simCSZenrich", x),
-    format = "arrow") %>%
-  collect()
-})
-```
-
-```{r}
-# TODO set extinction threshold in simulations
-simZ_prep <- map_dfr(sim_list,
-  function (x) {
-    x %>%
-      # Remove simulation that have failed to run
-      filter(!is.na(richness)) %>%
-      # Transform back interaction strength into matrices
-      mutate(across(where(is.list), as.list)) %>%
-      mutate(across(c(int_strength, max_int),
-          ~map2(.x, S,
-            function(y, rich) {
-              matrix(y, nrow = rich)
-            }
-          )
-      )
-        ) %>%
-      # Get matrix of alive species
-      mutate(max_int_alive  = map2(max_int, bm_sp,
-          function(mat, bm) {
-            mask <- bm > 10^-6
-            mat[mask, mask, drop = FALSE]
-          }
-        )
-        )
-  }
-)
-# Compute metrics of interest
-simZ <- simZ_prep %>%
-  mutate(
-    persistence = richness / S,
-    async = 1 / sync,
-    stab_pop = 1 / avg_cv_sp,
-    ct_alive = map_dbl(max_int_alive,
-      ~ifelse(sum(.x) == 0, 0,
-      sum(.x > 0) / ((ncol(.x))^2))),
-    bm_sp_alive = map(bm_sp, ~.x[.x > 10^-6]),
-    tlvl_alive = map2(tlvl, bm_sp, ~.x[.y > 10^-6]),
-    max_tlvl_alive = map_dbl(tlvl_alive, max),
-    w_avg_tlvl_alive = map2_dbl(tlvl_alive, bm_sp_alive, ~sum(.x * (.y / sum(.y)))),
-    max_max_int_alive = map_dbl(max_int_alive,
-      ~ifelse(length(.x[.x > 0]) == 0, 0, max(.x[.x > 0]))
-      ),
-    avg_max_int_alive = map_dbl(max_int_alive,
-      ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
-      ),
-    gini_max_int_alive = map_dbl(max_int_alive, ~gini(.x))
-      )
-simZ$tlvl_alive[[3]]
-simZ$max_int_alive[[3]]
-```
-
 ```{r, eval = FALSE}
@@
 summary(simZ$gini_max_int_alive)
+```
+
+# Introduction
+
+- Response diversity is key in driving stability in ecological communities
+- Response diversity control asynchrony with richness
+- Mainly done in plants
+- Food-webs structure can also modulate synchrony by predator-prey relationships
+- Interaction strength, connectance, richness and enrichment can also drive more
+
+# Research questions
+
+##  What are the mecanisms driving stability in food-webs ?
+
+- How structure of food-webs (connectance, species richness, prey-predator
+     size ratio) gives emergence to food-web structure (max trophic level,
+     weighted avg trophic level, omnivory) ?
+- How food-web structure influence biomass fluxes (avg interaction
+     strength, sd of interaction strength, asymetry)?
+- How food-web structure and biomass fluxes affect stability components?
+     total biomass, species variability, statistical averaging, evenness,
+     compensatory dynamics (interaction and environment)?
+
+# What is the effects of species richness on stability facing multiple stressors in competitive and food-webs communities?
+
+- How do species richness drive average population stability and asynchrony
+  in competitive and food-webs communities ?
+- How is it affected by enrichment and response diversity?
+
+# Material & Methods
+
+## Bioenergetic model
+
+TO Complete
+
+- Important bits:
+  - Niche model (Connectance highly constrained by richness)
+  - Type III functional response
+  - No predator interference
+  - Standardize carrying capacity? (Remove the effect of species richness on
+    total biomass, i.e. remove the effect of niche complementarity on biomass
+    produced by primary producers)
+
+## Variables
+
+- S: 5 to 60
+- C: .02 to .3
+- K: 1 and 20
+- $\rho$: 0 to 1
+- Z: 10 to 1000
+
+```{r}
+tar_load(simZ)
+tar_load(sim_rho)
+tar_load(sim_rho_scaled)
 ```
@@
 ```{r}
-p_basic <- ~corrplot::corrplot(
-  cor(simZ %>%
+cor_enrich <- cor(simZ %>%
     filter(productivity == "enrichment") %>%
@@
         sync)),
-    method = "spearman"),
-  diag = FALSE, type = "upper"
-)
-p_enrich <- ~corrplot::corrplot(
-  cor(simZ %>%
+    method = "spearman")
+cor_basic <- cor(simZ %>%
     filter(productivity == "basic") %>%
@@
         sync)),
-    method = "spearman"),
-  diag = FALSE, type = "upper"
+    method = "spearman")
+p_cor_basic <- ggcorrplot(cor_basic, type = "lower",
+   lab = TRUE)
+p_cor_enrich <- ggcorrplot(cor_enrich, type = "lower",
+   lab = TRUE)
+p_cor <- plot_grid(
+  p_cor_basic,
+  p_cor_enrich,
+  ncol = 2
 )
-plot_grid(
-  ggdraw(p_basic),
-  ggdraw(p_enrich),
-  nrow = 2
+ggsave(here("report", "figures", "p_cor.pdf"),
+  plot = p_cor,
+  device = NULL,
+  path = NULL,
+  scale = 3.0,
+  units = "mm",
+  width = 140,
+  height = 140 * .5,
+  dpi = 300,
+  limitsize = TRUE,
+  bg = NULL
 )
@@
       temporal stability and its components!
+
+# Effect of species richness
+
+```{r}
+sim_rich_prod <- simZ %>%
+  filter(
+    Z == 100,
+    env_stoch == .5,
+    rho %in% c(0, 1)
+  )
+```
+
+```{r}
+p_sim_rich_prod <- sim_rich_prod %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  mutate(
+    metric = var_replacement()[metric],
+    rho = rho_replacement()[as.character(rho)]
+  ) %>%
+  ggplot(aes(x = richness, y = stab, color = factor(productivity))) +
+  geom_point(alpha = .1, shape = 20) +
+  geom_smooth() +
+  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
+  labs(
+    color = "Productivity",
+    x = "Species richness",
+    y = "Stability component"
+  ) +
+  scale_x_continuous(
+    sec.axis = sec_axis(~ . ,
+      name = "Response diversity",
+      breaks = NULL,
+      labels = NULL)
+  )
+ggsave(
+  filename = here::here("fig", "stability_rich.pdf"),
+  p_sim_rich_prod,
+  scale = 1.8,
+  width = 88,
+  height = 88 * .6,
+  units = "mm"
+)
+```
+
+```{r}
+p_sim_rich_prod <- sim_rich_prod %>%
+  filter(ct_alive != 0) %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  mutate(
+    metric = var_replacement()[metric],
+    rho = rho_replacement()[as.character(rho)]
+  ) %>%
+  ggplot(aes(x = richness, y = stab, color = factor(productivity))) +
+  geom_point(alpha = .1, shape = 20) +
+  geom_smooth() +
+  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
+  labs(
+    color = "Productivity",
+    x = "Species richness",
+    y = "Stability component"
+  ) +
+  scale_x_continuous(
+    sec.axis = sec_axis(~ . ,
+      name = "Response diversity",
+      breaks = NULL,
+      labels = NULL)
+  )
+ggsave(
+  filename = here::here("fig", "stability_rich_fw_only.pdf"),
+  p_sim_rich_prod,
+  scale = 1.8,
+  width = 88,
+  height = 88 * .6,
+  units = "mm"
+)
+```
+
+```{r}
+p_sim_rich_prod_p_only <- sim_rich_prod %>%
+  filter(ct_alive == 0) %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  mutate(
+    metric = var_replacement()[metric],
+    rho = rho_replacement()[as.character(rho)]
+  ) %>%
+  ggplot(aes(x = richness, y = stab, color = factor(productivity))) +
+  geom_point(alpha = .1, shape = 20) +
+  geom_smooth() +
+  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
+  labs(
+    color = "Productivity",
+    x = "Species richness",
+    y = "Stability component"
+  ) +
+  scale_x_continuous(
+    sec.axis = sec_axis(~ .,
+      name = "Response diversity",
+      breaks = NULL,
+      labels = NULL)
+  )
+ggsave(
+  filename = here::here("fig", "stability_rich_p_only.pdf"),
+  p_sim_rich_prod_p_only,
+  scale = 1.8,
+  width = 88,
+  height = 88 * .6,
+  units = "mm"
+)
+```
 
@@
   containing only plants?
-
-```{r}
-sim_rho <- simZ %>%
-  #filter(ct_alive != 0) %>%
-  mutate(across(c(async, sync, stab_pop, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
-  mutate(
-    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
-    productivity_f = factor(productivity)
-
-    ) %>%
-  select(c(
-      ct_alive, log_richness, max_tlvl_alive, Z, rho,
-      gini_max_int, avg_max_int_alive, log1_avg_max_int_alive, env_stoch,
-      log_stab_com, log_sync, log_async, log_stab_pop, log_avg_cv_sp, productivity, productivity_f,
-      persistence)
-  )
-sim_rho_scaled <- sim_rho %>%
-  mutate(across(where(is.double), ~scale(.x)[,1]))
-```
 
@@
 ```{r}
-sim_rich_prod <- simZ %>%
-  filter(
-    Z == 100,
-    env_stoch == .5,
-    rho %in% c(0, 1)
+ctrl <- trainControl(method = "cv",  number = 10)
+
+# CV bagged model
+bagged_cv <- train(
+  stab_com ~ richness + ct_alive + rho + productivity + max_tlvl_alive +
+    avg_max_int_alive,
+  data = simZ,
+  cp = .2,
+  maxdepth = 6,
+  method = "treebag",
+  trControl = ctrl,
+  importance = TRUE
   )
+plot(varImp(bagged_cv), 20)
+plot(bagged_cv)
 ```
@@
 ```{r}
-p_sim_rich_prod <- sim_rich_prod %>%
-  mutate(stab_pop = 1/ avg_cv_sp) %>%
-  pivot_longer(
-    c(stab_com, stab_pop, sync),
-    names_to = "metric",
-    values_to = "stab") %>%
-  mutate(
-    metric = var_replacement()[metric],
-    rho = rho_replacement()[as.character(rho)]
-  ) %>%
-  ggplot(aes(x = richness, y = stab, color = factor(productivity))) +
-  geom_point(alpha = .1, shape = 20) +
-  geom_smooth() +
-  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
-  labs(
-    color = "Productivity",
-    x = "Species richness",
-    y = "Stability component"
-  ) +
-  scale_x_continuous(
-    sec.axis = sec_axis(~ . ,
-      name = "Response diversity",
-      breaks = NULL,
-      labels = NULL)
+m1 <- rpart(
+  formula = stab_com ~ richness + ct_alive + rho + productivity + max_tlvl_alive +
+    avg_max_int_alive,
+  data    = simZ,
+  method  = "anova"
   )
-ggsave(
-  filename = here::here("fig", "stability_rich.pdf"),
-  p_sim_rich_prod,
-  scale = 1.8,
-  width = 88,
-  height = 88 * .6,
-  units = "mm"
-)
+rpart.plot(m1)
 ```

### 2023-05-17 _targets.Rmd
Update report

@@
 
-Target Markdown is a powerful R Markdown interface for reproducible analysis pipelines, and the chapter at https://books.ropensci.org/targets/markdown.html walks through it in detail.
-This R Markdown report the example from the chapter.
-Try it out in both interactive and non-interactive modes, either by running the code chunks in different ways or setting the `tar_interactive` chunk option.
+Target Markdown is a powerful R Markdown interface for reproducible analysis
+pipelines, and the chapter at https://books.ropensci.org/targets/markdown.html
+walks through it in detail. This R Markdown report the example from the chapter.
+Try it out in both interactive and non-interactive modes, either by running the
+code chunks in different ways or setting the `tar_interactive` chunk option.
 
@@
 source(here::here("R", "string_replacements.R"))
+source(here::here("R", "model_helpers.R"))
 ```
@@
         sd_max_int_alive = map_dbl(max_int_alive,
-          ~ifelse(length(.x[.x > 0]) == 0, 0, sd(.x[.x > 0]))
+          ~ifelse(length(.x[.x > 0]) <= 1, 0, sd(.x[.x > 0]))
           ),
         cv_max_int_alive = sd_max_int_alive / avg_max_int_alive,
+        inv_sd_max_int_alive = 1 / sd_max_int_alive,
         gini_max_int_alive = map_dbl(max_int_alive,
@@
 simZ %>%
+  filter(ct_alive != 0, avg_max_int_alive != 0) %>%
   mutate(across(c(async, sync, stab_pop, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
@@
   mutate(across(where(is.double), ~scale(.x)[,1]))
+```
+
+```{targets rho_model}
+list(
+  tar_target(formula_fixed_rho, "log_richness +
+    ct_alive +
+    log1_avg_max_int_alive +
+    productivity +
+    rho +
+    I(rho^2) +
+    env_stoch +
+
+    log_richness:ct_alive +
+    log_richness:log1_avg_max_int_alive +
+    log_richness:productivity +
+    log_richness:rho +
+
+    log1_avg_max_int_alive:ct_alive +
+    log1_avg_max_int_alive:productivity +
+    log1_avg_max_int_alive:rho +
+
+    ct_alive:rho +
+    ct_alive:productivity +
+    rho:productivity +
+    I(rho^2):productivity +
+
+    log_richness:log1_avg_max_int_alive:ct_alive +
+    log_richness:log1_avg_max_int_alive:productivity +
+    log_richness:log1_avg_max_int_alive:rho +
+    log_richness:ct_alive:productivity +
+    log_richness:ct_alive:rho +
+    log_richness:rho:productivity +
+
+    log1_avg_max_int_alive:ct_alive:rho +
+    log1_avg_max_int_alive:ct_alive:productivity +
+    log1_avg_max_int_alive:rho:productivity +
+
+    ct_alive:rho:productivity"
+    ),
+  tar_target(formula_rand_rho, "(1 | Z)"),
+  tar_target(mod_rho, map(setNames(
+    c("log_stab_com", "log_stab_pop", "log_async"),
+    c("log_stab_com", "log_stab_pop", "log_async")
+    ),
+  function (x) {
+    glmmTMB(formula(paste0(x, " ~ ", formula_fixed_rho, " + ", formula_rand_rho)),
+      sim_rho)
+  }
+  )),
+  tar_target(coef_mod_rho, map_dfr(mod_rho, ~model2tibble(.x))),
+  tar_target(r2_mod_rho, map_dfr(mod_rho, ~as.data.frame(r2_nakagawa(.x)), .id = "response") %>%
+  mutate(response = var_replacement()[response])),
+  tar_target(p_mod_rho, plot_effect_type(coef_mod_rho)),
+  tar_target(mod_rho_scaled, map(setNames(
+    c("log_stab_com", "log_stab_pop", "log_async"),
+    c("log_stab_com", "log_stab_pop", "log_async")
+    ),
+  function (x) {
+    glmmTMB(formula(paste0(x, " ~ ", formula_fixed_rho, " + ", formula_rand_rho)),
+      sim_rho_scaled)
+  }
+)
+    ),
+  tar_target(coef_mod_rho_scaled, map_dfr(mod_rho_scaled, ~model2tibble(.x))),
+  tar_target(r2_mod_rho_scaled,
+    map_dfr(mod_rho_scaled, ~as.data.frame(r2_nakagawa(.x)), .id = "response") %>%
+      mutate(response = var_replacement()[response])),
+  tar_target(colin_rho, performance::check_collinearity(lm(formula(str_replace_all(paste0("log_stab_com ~ ", formula_fixed_rho), "(\\*|:)", "+")),
+  sim_rho_scaled))),
+    tar_target(p_mod_rho_scaled, plot_effect_type(coef_mod_rho_scaled))
+)
+```
+
+```{targets pred_rho}
+tar_target(pred_rho,
+  {
+  pred_rho <- list(
+    log_richness = c(log(1), log(5), log(10), log(20), log(30), log(50)),
+    ct_alive = c(.05, .10, .40),
+    rho = c(0, .5, 1),
+    log1_avg_max_int_alive = c(log(0.2 + 1), round(log(.81 + 1), 1), round(log(5.65 + 1), 1)),
+    env_stoch = .5,
+    productivity = c("basic", "enrichment"),
+    Z = 100
+    ) %>% expand.grid() %>%
+  filter(
+    !(log1_avg_max_int_alive == 0 & ct_alive != 0 | ct_alive == 0 & log1_avg_max_int_alive != 0)
+  )
+  pred_rho$log_stab_com <- predict(mod_rho[["log_stab_com"]], newdata = pred_rho)
+  pred_rho
+  }
+)
 ```

### 2023-05-17 report/cs_analysis.Rmd
Update report

@@
   comment = "#>",
+  fig.pos = "H",  # pdf mode
   #fig.dim = c(7, 7),
@@
 library(ipred)
+library(kableExtra)
 
@@
 - Response diversity control asynchrony with richness
-- Mainly done in plants
-- Food-webs structure can also modulate synchrony by predator-prey relationships
-- Interaction strength, connectance, richness and enrichment can also drive more
+- Mainly done in plants or in same food-web modules
+- Food-webs structure can also modulate synchrony and population stability by
+  the strength of trophic interactions
 
 # Research questions
+
+For me, there are two ways to see the question.
 
@@
 
-# What is the effects of species richness on stability facing multiple stressors in competitive and food-webs communities?
+## What is the effects of species richness on stability facing multiple stressors in competitive and food-webs communities?
 
@@
   - No predator interference
-  - Standardize carrying capacity? (Remove the effect of species richness on
+  - Enrichment: K = 1 or 20
+  - Standardized carrying capacity (Remove the effect of species richness on
     total biomass, i.e. remove the effect of niche complementarity on biomass
@@
 - $\rho$: 0 to 1
-- Z: 10 to 1000
+- Z: 5 to 1000
 
@@
 ```{r}
-simZ %>%
-  filter(rho == 0) %>%
-  pivot_longer(
-    c(stab_com, stab_pop, sync, total_biomass),
-    names_to = "metric",
-    values_to = "stab") %>%
-  ggplot(aes(x = richness, y = stab, color = factor(env_stoch))) +
-  geom_point() +
-  facet_grid(rows = vars(metric), cols = vars(productivity), scales = "free_y") +
-  labs(
-    color = "Evironmental stochasticity",
-    x = "Species richness",
-    y = "Stability component"
-  )
-```
-
-```{r}
-simZ %>%
-  filter(rho == 1) %>%
-  mutate(stab_pop = 1/ avg_cv_sp) %>%
-  pivot_longer(
-    c(stab_com, stab_pop, sync, total_biomass),
-    names_to = "metric",
-    values_to = "stab") %>%
-  ggplot(aes(x = richness, y = stab, color = factor(env_stoch))) +
-  geom_point() +
-  facet_grid(rows = vars(metric), cols = vars(productivity), scales = "free_y") +
-  labs(
-    color = "Evironmental stochasticity",
-    x = "Species richness",
-    y = "Stability component"
-  )
-```
-
-```{r}
 cor_enrich <- cor(simZ %>%
@@
     select(c(S, richness, ct, Z, ct_alive, total_biomass, avg_max_int_alive,
+        sd_max_int_alive, cv_max_int_alive,
+        gini_max_int_alive,
         w_avg_tlvl_alive, max_tlvl_alive, rho, env_stoch, stab_com, avg_cv_sp,
-        sync)),
+        sync)) %>% na.omit(),
     method = "spearman")
@@
 select(c(S, richness, ct, Z, ct_alive, total_biomass, avg_max_int_alive,
+        sd_max_int_alive, cv_max_int_alive,
+        gini_max_int_alive,
         w_avg_tlvl_alive, max_tlvl_alive, rho, env_stoch, stab_com, avg_cv_sp,
-        sync)),
+        sync)) %>% na.omit(),
     method = "spearman")
@@
   p_cor_enrich,
-  ncol = 2
+  ncol = 2,
+  labels = "auto"
 )
@@
 
-- Main results:
-  - Stability increases with richness but not connectance (no overall effect)
-  - Richness increases stability by increasing maximum and average trophic
-    level, but also by decreasing interaction strength and increasing asymetry
-    in trophic interaction, and finally by increasing total biomass (I need to control for that).
-  - Synchrony decreases with species richness, max and average trophic level but increases with
-    average interaction strength and symetry of interaction distributions.
-  - Population varibility decreases with species richness, average and maximum
-    trophic level, asymetry of interaction strength but it is increased by
-    average interaction strength
-  - Same effects of food-web structure on both Synchrony and Population variability
-    - Surpringly, as in Danet et al. (2021), connectance has little effect on
-      temporal stability and its components!
+```{r}
+cor_cap <- "Correlation among foodweb structure and stability for basic (a) and
+enriched (b) environments."
+```
+
+```{r, fig.cap=cor_cap}
+knitr::include_graphics(here::here("report", "figures", "p_cor.pdf"))
+```
 
@@
   filter(
-    Z == 100,
-    env_stoch == .5,
-    rho %in% c(0, 1)
+    env_stoch == .5
   )
@@
 ggsave(
-  filename = here::here("fig", "stability_rich.pdf"),
+  filename = here::here("report", "figures", "stability_rich.pdf"),
   p_sim_rich_prod,
@@
 ```{r}
-p_sim_rich_prod <- sim_rich_prod %>%
-  filter(ct_alive != 0) %>%
+p_sim_rich_prod_fw_only <- sim_rich_prod %>%
+  filter(ct_alive != 0, avg_max_int_alive != 0) %>%
   mutate(stab_pop = 1/ avg_cv_sp) %>%
@@
   ) %>%
-  ggplot(aes(x = richness, y = stab, color = factor(productivity))) +
+  ggplot(aes(x = log(richness), y = log(stab), color = factor(productivity))) +
   geom_point(alpha = .1, shape = 20) +
-  geom_smooth() +
+  geom_smooth(method = "lm") +
   facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
@@
 ggsave(
-  filename = here::here("fig", "stability_rich_fw_only.pdf"),
-  p_sim_rich_prod,
+  filename = here("report", "figures", "p_sim_rich_prod_fw_only.pdf"),
+  p_sim_rich_prod_fw_only,
   scale = 1.8,
@@
 ggsave(
-  filename = here::here("fig", "stability_rich_p_only.pdf"),
+  filename = here("report", "figures", "p_sim_rich_prod_p_only.pdf"),
   p_sim_rich_prod_p_only,
@@
 
-# Covariation
+```{r, fig.cap = "Food-Web only."}
+knitr::include_graphics(here("report", "figures", "p_sim_rich_prod_fw_only.pdf"))
+```
+
+```{r, fig.cap = "Primary producers only."}
+knitr::include_graphics(here::here("report", "figures", "p_sim_rich_prod_p_only.pdf"))
+```
+
+- Enrichment decreases the effect of response diversity of stability
+- Enrichment increases synchrony
+- Richness decreases population stability, but increases it in absence of response
+  diversity
+- Food-web maintains some asynchrony despite the absence of response
+  diversity but synchrony increase with richness in basic environment
+
+```{r}
+simZ %>%
+  filter(rho == 1) %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync, total_biomass),
+    names_to = "metric",
+    values_to = "stab") %>%
+  ggplot(aes(x = richness, y = stab, color = factor(env_stoch))) +
+  geom_point() +
+  facet_grid(rows = vars(metric), cols = vars(productivity), scales = "free_y") +
+  labs(
+    color = "Evironmental stochasticity",
+    x = "Species richness",
+    y = "Stability component"
+  )
+```
+
+# Food-web structure and interaction strength drive stability
 
@@
 sim_sem <- simZ %>%
-  filter(rho == 0) %>%
-  mutate(across(c(async, sync, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
+  filter(ct_alive != 0, env_stoch == 0.5, rho == 0) %>%
+  mutate(across(c(async, stab_pop, stab_com, richness, ct_alive, sd_max_int_alive, avg_max_int_alive), log, , .names = "log_{.col}")) %>%
   mutate(
     log1_avg_max_int_alive = log(avg_max_int_alive + 1),
+    log1_sd_max_int_alive = log(sd_max_int_alive + 1),
     productivity_f = factor(productivity)
-
     ) %>%
-  as.data.frame() %>%
-  select(c(
-      ct_alive, log_richness, max_tlvl_alive, Z,
-      gini_max_int, avg_max_int_alive, log1_avg_max_int_alive, env_stoch,
-      log_stab_com, log_sync, log_async, log_avg_cv_sp, productivity, productivity_f)
-  )
+  as.data.frame()
 scaled_sim_sem <- sim_sem %>%
@@
 ```{r}
-pred_may <- "log1_avg_max_int_alive*log_richness*ct_alive*productivity + env_stoch"
-rand <- "(1 | Z)"
-
-mod_may_single <- lm(formula(str_replace_all(paste0("log_stab_com ~ ", pred_may), "\\*", "+")),
-  scaled_sim_sem)
-performance::check_collinearity(mod_may_single)
+var_fw_struct <- c("richness", "ct_alive", "Z")
+var_fw_emergent_struct <- c("max_tlvl_alive", "w_avg_tlvl_alive")
+var_fw_flux <- c("gini_max_int_alive", "avg_max_int_alive", "sd_max_int_alive",
+  "cv_max_int_alive")
+var_stab <- c("async", "stab_com", "stab_pop")
 ```
@@
 ```{r}
-mod_may <- glmmTMB(formula(paste0("log_stab_com ~ ", pred_may, " + ", rand)), scaled_sim_sem)
+#colnames(simZ)
+pairs(sim_sem %>%
+  filter(env_stoch == .5) %>%
+  select(c(var_fw_struct, var_fw_emergent_struct, var_fw_flux, stab_pop)))
+```
 
-r2_nakagawa(mod_may)
-par_mod_may <- parameters(mod_may)
-plot(parameters(mod_may))
+```{r, eval = FALSE}
+performance::check_collinearity(lm(w_avg_tlvl_alive ~ max_tlvl_alive,sim_sem))
+performance::check_collinearity(lm(w_avg_tlvl_alive ~ ct_alive + richness,sim_sem))
+performance::check_collinearity(lm(w_avg_tlvl_alive ~ ct_alive + richness,sim_sem))
+performance::check_collinearity(lm(avg_max_int_alive ~ w_avg_tlvl_alive + ct_alive + richness,sim_sem))
+performance::check_collinearity(lm(avg_max_int_alive ~ max_tlvl_alive + ct_alive,sim_sem))
+performance::check_collinearity(lm(stab_com ~ log_richness + log1_avg_max_int_alive + log1_sd_max_int_alive + w_avg_tlvl_alive + ct_alive,sim_sem))
+performance::check_collinearity(lm(stab_com ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive,sim_sem))
 ```
@@
 ```{r}
-mod_may_sync <- glmmTMB(formula(paste0("log_sync ~ ", pred_may, " + ", rand)),
-  scaled_sim_sem)
-r2_nakagawa(mod_may_sync)
-plot(parameters(mod_may_sync))
+sem_list_basic <- list(
+  w_avg_tlvl_alive = lm(w_avg_tlvl_alive ~ richness + ct_alive, sim_sem),
+  sd_max_int_alive = lm(sd_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive, sim_sem),
+  avg_max_int_alive = lm(avg_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive, sim_sem),
+  log_async = lm(log_async ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem),
+  log_stab_pop = lm(log_stab_pop ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem),
+  log_stab_com = lm(log_stab_com ~ log_async + log_stab_pop, sim_sem)
+)
+sem_basic <- as.psem(sem_list_basic)
 ```
@@
 ```{r}
-mod_may_cv_sp <- glmmTMB(formula(paste0("log_avg_cv_sp ~ ", pred_may, " + ", rand)),
-  scaled_sim_sem)
-r2_nakagawa(mod_may_cv_sp)
-plot(parameters(mod_may_cv_sp))
+ti <- summary(sem_basic)$coefficients[, c(1, 2, 8, 9)]
+colnames(ti)[4] <- "Signif"
+ti %>%
+  mutate(
+    Response = var_replacement()[Response],
+    Predictor = var_replacement()[Predictor]
+  ) %>%
+  kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
+  collapse_rows(1, valign = "middle") %>%
+  kable_styling()
 ```
 
-## Rho model
+```{r, eval = FALSE}
+ti <- map_dfr(setNames(sem_list_basic, names(sem_list_basic)),
+  performance::check_collinearity,
+  .id = "response") %>%
+  as_tibble
+ti %>%
+  mutate(
+    response = var_replacement()[response],
+    Term = var_replacement()[Term]
+  ) %>%
+  kable(caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
+  kable_styling()
+```
 
-- Should be include also the monotrophic communities ? I.e. Communities
-  containing only plants?
-
-```{r}
-sim_rho %>%
-  filter(ct_alive == 0, env_stoch == 0.5) %>%
-  ggplot(aes(x = log_richness, y = log_stab_com)) +
-  geom_point() +
-  geom_smooth() +
-  facet_grid(cols = vars(rho), rows = vars(productivity_f))
+```{r, eval = FALSE}
+map_dfr(sem_list_basic, rsquared) %>%
+  mutate(Response = var_replacement()[Response]) %>%
+  select(Response, R.squared) %>%
+  kable(caption = "Rsquared for the Structural Equation Model.") %>%
+  kable_styling()
 ```
@@
 ```{r}
-pred_rho <- "log_richness +
-ct_alive +
-log1_avg_max_int_alive +
-productivity +
-rho +
-I(rho^2) +
-env_stoch +
-
-log_richness:ct_alive +
-log_richness:log1_avg_max_int_alive +
-log_richness:productivity +
-log_richness:rho +
-
-log1_avg_max_int_alive:ct_alive +
-log1_avg_max_int_alive:productivity +
-log1_avg_max_int_alive:rho +
-
-ct_alive:rho +
-ct_alive:productivity +
-rho:productivity +
-I(rho^2):productivity +
-
-log_richness:log1_avg_max_int_alive:ct_alive +
-log_richness:log1_avg_max_int_alive:productivity +
-log_richness:log1_avg_max_int_alive:rho +
-log_richness:ct_alive:productivity +
-log_richness:ct_alive:rho +
-log_richness:rho:productivity +
-
-log1_avg_max_int_alive:ct_alive:rho +
-log1_avg_max_int_alive:ct_alive:productivity +
-log1_avg_max_int_alive:rho:productivity +
-
-ct_alive:rho:productivity"
-rand <- "(1 | Z)"
-
-mod_rho_single <- lm(formula(str_replace_all(paste0("log_stab_com ~ ", pred_rho), "(\\*|:)", "+")),
-  sim_rho_scaled)
-performance::check_collinearity(mod_rho_single)
+sim_sem_nodivresp <- simZ %>%
+  filter(ct_alive != 0, env_stoch == 0.5, rho == 1) %>%
+  mutate(across(c(async, stab_pop, stab_com, richness, ct_alive, sd_max_int_alive, avg_max_int_alive), log, , .names = "log_{.col}")) %>%
+  mutate(
+    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
+    log1_sd_max_int_alive = log(sd_max_int_alive + 1),
+    productivity_f = factor(productivity)
+    ) %>%
+  as.data.frame()
 ```
@@
 ```{r}
-model2tibble <- function(x, response = NULL) {
-  out <- parameters(x) %>%
-    filter(Effects == "fixed", Parameter != "(Intercept)") %>%
-    as_tibble() %>%
-    janitor::clean_names() %>%
-    mutate(
-      response = var_replacement()[as.character(formula(x)[2])],
-      parameter = str_replace_all(parameter, var_replacement()),
-      count_int = str_count(parameter, ":"),
-      effect_type = case_when(
-        count_int == 0 ~ "single",
-        count_int == 1 ~ "double",
-        count_int == 2 ~ "triple",
-        TRUE ~ "other"
-
+sem_list_nodivresp <- list(
+  w_avg_tlvl_alive = lm(w_avg_tlvl_alive ~ richness + ct_alive, sim_sem_nodivresp),
+  sd_max_int_alive = lm(sd_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive, sim_sem_nodivresp),
+  avg_max_int_alive = lm(avg_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive, sim_sem_nodivresp),
+  log_async = lm(log_async ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem_nodivresp),
+  log_stab_pop = lm(log_stab_pop ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem_nodivresp),
+  log_stab_com = lm(log_stab_com ~ log_async + log_stab_pop, sim_sem_nodivresp)
 )
-    ) %>%
-    select(response, parameter:ci_high, effect_type)
-    out
-}
-plot_effect_type <- function(x) {
-  effect <- c("single", "double", "triple")
-  p <- map(effect,
-    function(y) {
-      x %>%
-        filter(effect_type == y) %>%
-        arrange(coefficient) %>%
-        ggplot(aes(
-            y = reorder(parameter, -coefficient),
-            x = coefficient,xmin = ci_low, xmax = ci_high,
-            color = response
-            )) +
-        geom_vline(xintercept = 0, color = "black", linetype = "dashed", linewidth = 1.5) +
-        geom_pointrange(position = position_dodge(width = 0.5)) +
-        labs(x = "Standardized Coefficients")
-    }
-  )
-  names(p) <- effect
-  p
-}
+sem_nodivresp <- as.psem(sem_list_nodivresp)
 ```
@@
 ```{r}
-mod_rho_scaled <- map(setNames(
-    c("log_stab_com", "log_stab_pop", "log_async"),
-    c("log_stab_com", "log_stab_pop", "log_async")
-    ),
-  function (x) {
-    glmmTMB(formula(paste0(x, " ~ ", pred_rho, " + ", rand)),
-      sim_rho_scaled)
-  }
-)
-coef_mod_rho_scaled <- map_dfr(mod_rho_scaled, ~model2tibble(.x))
-ti <- map_dfr(mod_rho_scaled, ~as.data.frame(r2_nakagawa(.x)), .id = "response") %>%
-  mutate(response = var_replacement()[response])
-p_mod_rho_scaled <- plot_effect_type(coef_mod_rho_scaled)
-plot_grid(plotlist = p_mod_rho_scaled)
+coef_sem_nodivresp <- summary(sem_nodivresp)$coefficients[, c(1, 2, 8, 9)]
+colnames(coef_sem_nodivresp)[4] <- "Signif"
+coef_sem_nodivresp %>%
+  mutate(
+    Response = var_replacement()[Response],
+    Predictor = var_replacement()[Predictor]
+  ) %>%
+  kable(caption = "Standardized estimates for the Structural Equation Models with no response diversity.") %>%
+  collapse_rows(1, valign = "middle") %>%
+  kable_styling()
 ```
 
+# Effect of multiple stressors on stability in monotrophic and food-webs
+
 ```{r}
-mod_rho <- map(setNames(
-    c("log_stab_com", "log_stab_pop", "log_async"),
-    c("log_stab_com", "log_stab_pop", "log_async")
-    ),
-  function (x) {
-    glmmTMB(formula(paste0(x, " ~ ", pred_rho, " + ", rand)),
-      sim_rho)
-  }
+tar_load(p_mod_rho_scaled)
+p_mod_rho_scaled_tot <- plot_grid(plotlist = p_mod_rho_scaled)
+ggsave(here("report", "figures", "p_mod_rho_scaled_tot.pdf"),
+  plot = p_mod_rho_scaled_tot,
+  device = NULL,
+  path = NULL,
+  scale = 2.4,
+  units = "mm",
+  width = 140,
+  height = 140 * .5,
+  dpi = 300,
+  limitsize = TRUE,
+  bg = NULL
 )
-coef_mod_rho <- map_dfr(mod_rho, ~model2tibble(.x))
-ti <- map_dfr(mod_rho, ~as.data.frame(r2_nakagawa(.x)), .id = "response") %>%
-  mutate(response = var_replacement()[response])
-p_mod_rho <- plot_effect_type(coef_mod_rho)
+```
+
+```{r, eval = FALSE}
+tar_load(p_mod_rho)
 plot_grid(plotlist = p_mod_rho)
@@
 ```{r}
-pred_list <- list(
-  log_richness = c(log(1), log(5), log(10), log(20), log(30), log(50)),
-  ct_alive = c(0, .10, .20),
-  rho = c(0, .5, 1),
-  log1_avg_max_int_alive = c(log(0 + 1), round(log(.81 + 1), 1), round(log(5.65 + 1), 1)),
-  env_stoch = .5,
-  productivity = c("basic", "enrichment"),
-  Z = 100
-)
-pred_rho <- expand.grid(pred_list) %>%
-  filter(
-    !(log1_avg_max_int_alive == 0 & ct_alive != 0 | ct_alive == 0 & log1_avg_max_int_alive != 0)
-  )
-
-pred_rho$log_stab_com <- predict(mod_rho[["log_stab_com"]], newdata = pred_rho)
-
-pred_rho %>%
+tar_load(pred_rho)
+p_pred_rho <- pred_rho %>%
+  mutate(rho = rho_replacement()[as.character(rho)]) %>%
   ggplot(aes(
@@
   geom_line() +
+  labs(
+    color = "Connectance",
+    linewidth = "Avg interaction strength",
+    y = "Community stability",
+    x = "Species richness (log)"
+    ) +
   facet_grid(
@@
   )
+ggsave(here("report", "figures", "p_pred_rho.pdf"),
+  plot = p_pred_rho,
+  device = NULL,
+  path = NULL,
+  scale = 2.4,
+  units = "mm",
+  width = 140,
+  height = 140 * .5,
+  dpi = 300,
+  limitsize = TRUE,
+  bg = NULL
+)
 ```
+
+```{r}
+predS_cap <- "Predictions for the model of drivers of community stability in
+basic and enriched environments (columns) and across varying response diversity
+(rows)."
+```
+
+```{r predS, fig.cap = predS_cap}
+knitr::include_graphics(here("report", "figures", "p_pred_rho.pdf"))
+```
+
+```{r}
+coef_rho_cap <- "Coefficients for the model of drivers of community stability,
+population stability and asynchrony. See predictions for a more simple overview."
+```
+
+```{r coef-rho, fig.cap = coef_rho_cap}
+knitr::include_graphics(here("report", "figures", "p_mod_rho_scaled_tot.pdf"))
+```
+
+- From the predictions of the model:
+  - Stong interaction among interaction strength, connectance and species
+    richness, enrichment and response diversity = *Food-web structure effects on
+    stability is context dependant*
+  - High connectance and high interaction strength is generally destabilizing,
+    driving negative relationships between stability and species richness in
+    enrichment context (high $K$)
+  - At the reverse, low connectance and high interaction strength is stabilizing
+  - In basic environment, high interaction strength stabilise the community
+    biomass in the absence of response diversity. At the opposite, low
+    interaction strength generate a negative stability richness relationship.
+  - In enrichment context, response diversity has little effect on stability!
+  - In enrichment context, High interaction strength is generally stabilizing!
 
@@
 
-```{r}
+```{r, eval = FALSE}
 sim_rho_pers <- simZ %>%
@@
 
-```{r}
-```
-
 ```{r, eval = FALSE}
@@
 
-```{r}
+```{r, eval = FALSE}
 library(ipred)
@@
 
-# Effect of species richness
-
-```{r}
+```{r, fig.cap = "Variable importance from bagged regression tree."}
 ctrl <- trainControl(method = "cv",  number = 10)
@@
 bagged_cv <- train(
-  stab_com ~ richness + ct_alive + rho + productivity + max_tlvl_alive +
-    avg_max_int_alive,
-  data = simZ,
+  stab_com ~ richness + ct_alive + max_tlvl_alive +
+    w_avg_tlvl_alive + avg_max_int_alive + sd_max_int_alive + rho + productivity,
+  data = simZ %>% filter(ct_alive != 0, avg_max_int_alive != 0),
   cp = .2,
@@
   )
-plot(varImp(bagged_cv), 20)
-plot(bagged_cv)
+plot(varImp(bagged_cv), 8)
 ```
 
-```{r}
+```{r, fig.cap="Regression tree "}
 m1 <- rpart(
-  formula = stab_com ~ richness + ct_alive + rho + productivity + max_tlvl_alive +
-    avg_max_int_alive,
-  data    = simZ,
+  formula = stab_com ~ richness + ct_alive + rho + productivity + w_avg_tlvl_alive + max_tlvl_alive +
+    avg_max_int_alive + sd_max_int_alive,
+  data    = simZ %>%
+    filter(ct_alive != 0, avg_max_int_alive != 0),
   method  = "anova"

### 2023-05-17 R/model_helpers.R

@@ -1,0 +1,41 @@
+model2tibble <- function(x, response = NULL) {
+  out <- parameters(x) %>%
+    filter(Effects == "fixed", Parameter != "(Intercept)") %>%
+    as_tibble() %>%
+    janitor::clean_names() %>%
+    mutate(
+      response = var_replacement()[as.character(formula(x)[2])],
+      parameter = str_replace_all(parameter, var_replacement()),
+      count_int = str_count(parameter, ":"),
+      effect_type = case_when(
+        count_int == 0 ~ "single",
+        count_int == 1 ~ "double",
+        count_int == 2 ~ "triple",
+        TRUE ~ "other"
+
+      )
+    ) %>%
+    select(response, parameter:ci_high, effect_type)
+    out
+}
+plot_effect_type <- function(x) {
+  effect <- c("single", "double", "triple")
+  p <- map(effect,
+    function(y) {
+      x %>%
+        filter(effect_type == y) %>%
+        arrange(coefficient) %>%
+        ggplot(aes(
+            y = reorder(parameter, -coefficient),
+            x = coefficient,xmin = ci_low, xmax = ci_high,
+            color = response
+            )) +
+        geom_vline(xintercept = 0, color = "black", linetype = "dashed", linewidth = 1.5) +
+        geom_pointrange(position = position_dodge(width = 0.5)) +
+        labs(x = "Standardized Coefficients")
+    }
+  )
+  names(p) <- effect
+  p
+}
+

### 2023-05-17 R/string_replacements.R

@@ -10,8 +10,12 @@ var_replacement <- function() {
     log_async = "Asynchrony",
     async = "Asynchrony",
     log1_avg_max_int_alive = "Interaction strength",
+    avg_max_int_alive = "Avg interaction strength",
+    sd_max_int_alive = "SD interaction strength",
+    w_avg_tlvl_alive = "Avg trophic level",
     ct_alive = "Connectance",
     log_richness = "Richness",
+    richness = "Richness",
     rho = "Env Corr",
     productivityenrichment = "Enrichment",
     env_stoch = "Env variance"
@@ -24,5 +28,4 @@ rho_replacement <- function() {
     `0.5` = "Medium",
     `1` = "No"
   )
-
 }

### 2023-05-19 _targets.Rmd
Sim with higher persistence hopefully: low Z and K gradient

@@
 source(here::here("R", "string_replacements.R"))
+source(here::here("R", "stability_decomposition.R"))
 source(here::here("R", "model_helpers.R"))
@@
       )
+  )
+)
+```
+
+```{targets raw_sim}
+list(
+  tar_target(var_param_sim, c("rep", "productivity", "S", "ct", "rho", "env_stoch", "Z")),
+  tar_target(sim_files, list.files(here::here("res", "simCSZenrich2/simCSZenrich2"))),
+  tar_target(sim_ts,
+    map_dfr(sim_files,
+      function (x) {
+        open_dataset(here::here("res", "simCSZenrich2/simCSZenrich2", x),
+          format = "arrow") %>%
+        collect() %>%
+      filter(!is.na(richness)) %>%
+      select(c(var_param_sim, "species", "stoch")) %>%
+      # Transform back interaction strength into matrices
+      mutate(across(where(is.list), as.list)) %>%
+      mutate(
+        stoch_d = map2(species, stoch, function(bm, d_stoch) {
+          .1 * bm * exp(d_stoch)
+          }),
+        species = map(species, ~matrix(.x, nrow = 100)),
+        stoch = map(stoch, ~matrix(.x, nrow = 100)),
+        stoch_d = map(stoch_d, ~matrix(.x, nrow = 100)),
+        cpe = map_dbl(species, compensatory_effect),
+        cpe_env = map_dbl(stoch_d, compensatory_effect),
+        cpe_int = cpe / cpe_env,
+        stab_com = map_dbl(species, community_stability),
+        pop_stab = map_dbl(species, population_stability),
+        async = map_dbl(species, asynchrony),
+        sae = map(species, statistical_averaging_effect)
+      )
+      })
+  ),
+  tar_target(sim_stab, sim_ts %>% select(-species, -stoch_d, -stoch)),
+  tar_target(sim_prep,
+map_dfr(sim_files,
+      function (x) {
+        open_dataset(here::here("res", "simCSZenrich2/simCSZenrich2", x),
+          format = "arrow") %>%
+        collect() %>%
+      filter(!is.na(richness)) %>%
+      select(-species, -stoch, -A) %>%
+      # Transform back interaction strength into matrices
+      mutate(across(where(is.list), as.list)) %>%
+      mutate(across(c(int_strength, max_int),
+          ~map2(.x, S,
+            function(y, rich) {
+              matrix(y, nrow = rich)
+            }
+          )
+      )
+        ) %>%
+      # Get matrix of alive species
+      mutate(max_int_alive  = map2(max_int, bm_sp,
+          function(mat, bm) {
+            mask <- bm > 10^-6
+            mat[mask, mask, drop = FALSE]
+          }
+        )
+      )
+      }
+
+    )),
+  tar_target(sim,
+    sim_prep %>%
+      mutate(
+        persistence = richness / S,
+        async = 1 / sync,
+        stab_pop = 1 / avg_cv_sp,
+        ct_alive = map_dbl(max_int_alive,
+          ~ifelse(sum(.x) == 0, 0,
+            sum(.x > 0) / ((ncol(.x))^2))),
+        bm_sp_alive = map(bm_sp, ~.x[.x > 10^-6]),
+        tlvl_alive = map2(tlvl, bm_sp, ~.x[.y > 10^-6]),
+        max_tlvl_alive = map_dbl(tlvl_alive, max),
+        w_avg_tlvl_alive = map2_dbl(tlvl_alive, bm_sp_alive,
+          ~sum(.x * (.y / sum(.y)))
+          ),
+        max_max_int_alive = map_dbl(max_int_alive,
+          ~ifelse(length(.x[.x > 0]) == 0, 0, max(.x[.x > 0]))
+          ),
+        avg_max_int_alive = map_dbl(max_int_alive,
+          ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
+          ),
+        sd_max_int_alive = map_dbl(max_int_alive,
+          ~ifelse(length(.x[.x > 0]) <= 1, 0, sd(.x[.x > 0]))
+          ),
+        cv_max_int_alive = sd_max_int_alive / avg_max_int_alive,
+        inv_sd_max_int_alive = 1 / sd_max_int_alive,
+        gini_max_int_alive = map_dbl(max_int_alive,
+          ~ifelse(length(.x[.x > 0]) == 0, 0, gini(.x[.x > 0]))),
+        avg_omnivory = map_dbl(omnivory, mean),
+        disconnected_prod = map_lgl(max_int_alive,
+        ~any(colSums(.x) == 0 & rowSums(.x) == 0))
+      ) %>%
+    select(!where(is.list))
   )
@@
 library(glmmTMB)
-library(biglm)
+```
+
+```{r}
+tar_read(sim_ts)
 ```

### 2023-05-19 report/cs_analysis.Rmd
Sim with higher persistence hopefully: low Z and K gradient

@@
   bookdown::pdf_document2
+always_allow_html: true
+bibliography: references.bib
 ---
@@
 ```{r, results = FALSE}
+library(targets)
 library(tidyverse)
@@
 library(glmmTMB)
-library(targets)
 
@@
 
-```{r, eval = FALSE}
-colnames(sim)
-unique(simZ$env_stoch)
-summary(simZ$total_biomass)
-summary(simZ$persistence)
-summary(simZ$ct_alive)
-summary(simZ$gini_max_int_alive)
+# Introduction
+
+Understanding the drivers of temporal stability is a key question in Ecology.
+BEF theory shows that species richness is a key driver to understand the
+temporal stability of community biomass.
+
+Species richness was demonstrated to increase community stability by driving higher
+asynchrony in community in various assemblages and ecosystems. In particular,
+high response diversity, which drives independant species fluctuations, seems to a key
+factor driving the positive effect of species richness of stability
+[@loreau_species_2008; @thibaut_understanding_2013; @zhao_biodiversity_2022]. However,
+those studies were often limited to monotrophic assemblages. As natural
+communities are often composed of multiple trophic level, our understanding of
+community stability needs to incorporate food-web structure.
+
+Food-web structure has been shown to have tremendous effect on community
+stability. The degree of generalism of predator was shown to modulate
+stability-richness relationships [@thebault_trophic_2005]. The strength and distribution of
+interaction strength was also shown to be strong driver of community stability
+[@mccann_weak_1998]. Omnivory was also shown to drive higher stability
+[@mccann_reevaluating_1997]. However, it is quite unkown how those food-web
+structure elements would affect stability-species richness relationships.
+
+The effect of environmental stressors can also strongly affect community
+variability. Higher environmental stress and variability may dampens the effect
+of richness on stability [@loreau_biodiversity_2001]. Lastly, productivity of a
+system, as the quantity of biomass input in the ecosystem, can have tremendous
+effect on both community structure and stabilty [@lindeman_trophic-dynamic_1942;
+@binzer_dynamics_2012; @binzer_interactive_2016]. Productivity can increase
+species richness in the food-web by increasing the level of energy input
+[@lindeman_trophic-dynamic_1942] but also destabilises community biomass by
+increasing population variability, a behavior coined as the paradox of
+enrichment [@rosenzweig_paradox_1971]. A better understanding of the effect of
+species richness on community stability should then include environmental
+gradient and stressors.
+
+Community stability can itself be partitioned in several components, i.e.
+population stability and population asynchrony [@thibaut_understanding_2013;
+@zhao_biodiversity_2022]. Population stability can be itself partioned in total
+biomass and population variability effect. Population asynchrony can further be
+partioned in statistical averaging effect and compensatory dynamics effects
+[@zhao_biodiversity_2022]. Partitioning stability allows to better understand
+how food-web structure and external factors affect stability. For exemple,
+environmental stochasticity is expected to primarily affect population
+stability, while response diversity should affect primarily compensatory
+dynamics.
+
+```{r}
+concept_cap <- "Food-web structure, response diversity and enviromental gradient
+can modulate stability-richness relationships. (a & b) Food-web structure may
+modulate stability-richness relationships additively (a) or interactively (b).
+(c) Decrease in response diversity and increase in environmental variability
+should dampen stability-richness relationships. While the loss of response
+diversity should dampen the effect of species richness on asynchrony, the
+increase in environmental variability should decrease primarily population
+stability. (d) Increase in productivity should increase species richness
+(trophic energy hypothesis) but also dampens the relationship between stability
+and species richness (paradox of enrichment). (e) Summary of the framework, how
+food-web structure and external perturbations modulate the effects of species
+richness on community stability. More precisely, how they affect the different
+components of stability: total biomass, population variability, statistical
+averaging effects and compensatory dynamics."
 ```
 
-# Introduction
+```{r, fig.cap=concept_cap}
+knitr::include_graphics(here("report", "figures", "conceptual_figures.pdf"))
+```
 
-- Response diversity is key in driving stability in ecological communities
-- Response diversity control asynchrony with richness
-- Mainly done in plants or in same food-web modules
-- Food-webs structure can also modulate synchrony and population stability by
-  the strength of trophic interactions
+```{r}
+tribble(
+  ~Type, ~`Food-web structure`, ~`Effect on stability-richness`,
+  "Food-web structure", "Connectance", "Strengthen (Miele et al., 2016) / No effect (Thébault & Loreau, 2005)",
+  "Food-web structure", "Omnivory", "Strengthen (Mccann et al., 1997)",
+  "Food-web structure", "Interaction strength", "Destabilising (Mccann et al., 1998) / Stabilising in
+  productive (Binzer et al., 2012; Binzer et al., 2016; Tabi et al., 2019)",
+  "Response diversity", "", "Dampens",
+  "Productivity", "", "Dampens (Binzer et al., 2012; Binzer et al., 2016; Tabi et al., 2019)",
+  "Environmental variability", "", "Dampens",
+)
+```
+
+```{r, eval = FALSE}
+tar_load(sim_prep)
+# test for disconnected species
+ti <- sim_prep %>%
+  filter(max_tlvl > 1) %>%
+  mutate(
+    disconnected_prod = map_lgl(max_int_alive,
+      # which species has no predator (colsum) is not a predator
+      ~any(colSums(.x) == 0 & rowSums(.x) == 0)
+    )
+  )
+
+ti %>%
+  ggplot(aes(x = as.factor(disconnected_prod), y = stab_com)) +
+  geom_boxplot()
+```
+
+```{r}
+tar_load(sim_stab)
+sim_stab %<>%
+  mutate(
+    sae_even = map_dbl(sae, ~.x["even"]),
+    evenness_sae = map_dbl(sae, ~.x["eveness"]),
+    sae_total = map_dbl(sae, ~.x["total"])
+  )
+tar_load(sim)
+sim_ok <- sim %>%
+  select(-stab_com, -async) %>%
+  left_join(sim_stab) %>%
+  mutate(inv_sum_pop_var = pop_stab / total_biomass)
+```
+
+```{r}
+sim_ok %>%
+  filter(ct_alive != 0, rho == 0, env_stoch == .1)
+sim_sem <- sim_ok %>%
+  filter(ct_alive != 0) %>%
+  mutate(across(c(stab_com, async, pop_stab, total_biomass, inv_sum_pop_var, sae_even, evenness_sae, cpe_env, cpe_int), log, , .names = "log_{.col}")) %>%
+  na.omit()
+```
+
+```{r}
+sem_list_basic <- list(
+  w_avg_tlvl_alive = lm(w_avg_tlvl_alive ~ richness + ct_alive, sim_sem),
+#  avg_omnivory = lm(avg_omnivory ~ richness + ct_alive + w_avg_tlvl_alive, sim_sem),
+  sd_max_int_alive = lm(sd_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive + Z, sim_sem),
+  avg_max_int_alive = lm(avg_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive + Z, sim_sem),
+  log_inv_sum_pop_var = lm(log_inv_sum_pop_var ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive + env_stoch + rho, sim_sem),
+  log_total_biomass = lm(log_total_biomass ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive + env_stoch + rho, sim_sem),
+  log_sae_even = lm(log_sae_even ~ richness, sim_sem),
+  log_evenness_sae = lm(log_evenness_sae ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem),
+  log_cpe_env = lm(log_cpe_env ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive + rho + env_stoch, sim_sem),
+  log_cpe_int = lm(log_cpe_int ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem),
+  log_async = lm(log_async ~ log_sae_even + log_evenness_sae + log_cpe_env + log_cpe_int, sim_sem),
+  #log_stab_pop = lm(log_pop_stab ~ log_total_biomass + log_inv_sum_pop_var, sim_sem),
+  log_stab_com = lm(log_stab_com ~ log_total_biomass + log_inv_sum_pop_var + log_async, sim_sem)
+)
+sem_basic <- as.psem(sem_list_basic)
+ti <- summary(sem_basic)$coefficients[, c(1, 2, 8, 9)]
+colnames(ti)[4] <- "Signif"
+ti
+```
+```{r, eval = FALSE}
+lm(
+  log_stab_com ~ log_total_biomass + log_inv_sum_pop_var + log_async,
+  sim_ok %>%
+    filter(ct_alive == 0) %>%
+    mutate(across(c(stab_com, async, pop_stab, total_biomass, inv_sum_pop_var, sae_even, evenness_sae, cpe_env, cpe_int), log, , .names = "log_{.col}"))%>%
+    mutate(across(where(is.double), ~scale(.x)[,1]))
+)
+```
+
+```{r}
+sim_stab %>%
+  ggplot(aes(x = as.factor(rho), y = cpe_env)) +
+  geom_boxplot() +
+  geom_hline(yintercept = 1)
+sim_stab %>%
+  ggplot(aes(x = as.factor(env_stoch), y = cpe)) +
+  geom_boxplot() +
+  geom_hline(yintercept = 1)
+
+sim_stab %>%
+  ggplot(aes(x = as.factor(env_stoch), y = stab_com)) +
+  geom_boxplot() +
+  geom_hline(yintercept = 1)
+sim_stab %>%
+  ggplot(aes(x = as.factor(rho), y = stab_com)) +
+  geom_boxplot() +
+  geom_hline(yintercept = 1)
+sim_stab %>%
+  ggplot(aes(x = as.factor(rho), y = evenness_sae)) +
+  geom_boxplot() +
+  geom_hline(yintercept = 1)
+sim_stab %>%
+  ggplot(aes(x = as.factor(rho), y = sae_total)) +
+  geom_boxplot() +
+  geom_hline(yintercept = 1)
+
+sim_stab %>%
+  ggplot(aes(x = as.factor(env_stoch), y = sae_total)) +
+  geom_boxplot() +
+  geom_hline(yintercept = 1)
+sim_stab %>%
+  ggplot(aes(x = as.factor(env_stoch), y = evenness_sae)) +
+  geom_boxplot() +
+  geom_hline(yintercept = 1)
+
+sim_stab %>%
+  ggplot(aes(x = as.factor(env_stoch), y = pop_stab)) +
+  geom_boxplot() +
+  geom_hline(yintercept = 1)
+sim_stab %>%
+  ggplot(aes(x = as.factor(rho), y = pop_stab)) +
+  geom_boxplot() +
+  geom_hline(yintercept = 1)
+```
+
+```{r}
+sim %>%
+  filter(ct_alive != 0) %>%
+  ggplot(aes(y = avg_omnivory, x = richness)) +
+  geom_point()
+
+sim %>%
+  filter(ct_alive != 0) %>%
+  ggplot(aes(y = avg_omnivory, x = ct_alive)) +
+  geom_point()
+
+sim %>%
+  filter(ct_alive != 0) %>%
+  ggplot(aes(x = avg_omnivory, y = 1/avg_cv_sp)) +
+  geom_point()
+
+sim %>%
+  filter(ct_alive != 0) %>%
+  ggplot(aes(x = avg_omnivory, y = sync)) +
+  geom_point()
+
+sim %>%
+  filter(ct_alive != 0) %>%
+  ggplot(aes(x = Z, y = max_tlvl_alive)) +
+  geom_point()
+```
+
+```{r}
+p_sim_sync_rich <- sim %>%
+  filter(ct_alive != 0) %>%
+  ggplot(aes(x = richness, y = sync, color = as.factor(env_stoch))) +
+  geom_point() +
+  geom_smooth() +
+  facet_grid(cols = vars(productivity), rows = vars(rho))
+
+p_sim_pop_rich <- sim %>%
+  filter(ct_alive != 0) %>%
+  ggplot(aes(x = richness, y = 1/avg_cv_sp, color = as.factor(env_stoch))) +
+  geom_point() +
+  geom_smooth() +
+  facet_grid(cols = vars(productivity), rows = vars(rho))
+```
+
+```{r}
+p_sim_stab_rich <- sim %>%
+  filter(ct_alive != 0) %>%
+  ggplot(aes(x = richness, y = stab_com, color = as.factor(env_stoch))) +
+  geom_point() +
+  geom_smooth() +
+  facet_grid(cols = vars(productivity), rows = vars(rho))
+ggsave(
+  filename = here("report", "figures", "sim_stab_richnness_rho_stoch.pdf"),
+  p_sim_stab_rich,
+  width = 80,
+  height = 80 * 4,
+  units = "mm",
+  scale = 2.4
+)
+```
+
+```{r}
+knitr::include_graphics(here::here("report", "figures", "sim_stab_richnness_rho_stoch.pdf"))
+```
+
+# Annexes
 
@@
     produced by primary producers)
+
+- Brose started with 5 basal species and K = 1, so his minimum total K is 5
 
@@
 ```
+
+# Appendix
+
+```{r}
+sim_ok %>%
+  ggplot(aes(x = as.factor(Z), y = max_tlvl_alive, color = as.factor(S))) +
+  geom_boxplot() +
+  facet_grid(cols = vars(productivity))
+sim_ok %>%
+  ggplot(aes(x = as.factor(Z), y = max_tlvl_alive, color = as.factor(S))) +
+  geom_boxplot() +
+  facet_grid(cols = vars(env_stoch), rows = vars(productivity))
+sim_ok %>%
+  ggplot(aes(x = as.factor(Z), y = avg_max_int_alive, color = as.factor(S))) +
+  geom_boxplot() +
+  facet_grid(cols = vars(productivity))
+
+sim_ok %>%
+  ggplot(aes(x = as.factor(Z), y = persistence, color = as.factor(S))) +
+  geom_boxplot() +
+  facet_grid(cols = vars(env_stoch), rows = vars(productivity))
+sim_ok %>%
+  ggplot(aes(x = as.factor(Z), y = pop_stab, color = as.factor(S))) +
+  geom_boxplot() +
+  facet_grid(cols = vars(env_stoch), rows = vars(productivity))
+sim_ok %>%
+  ggplot(aes(x = ct_alive, y = persistence, color = as.factor(S))) +
+  geom_point()
+```
+
+- K = 1 is too low for meaningful food-webs, I should start with K = 5 as in
+  Brose et al. (2006)

### 2023-05-19 use_case/cpe_decomposition.Rmd
Sim with higher persistence hopefully: low Z and K gradient

---
title: "Test CPE decomposition"
author: Alain Danet
date: \today
output:
  bookdown::pdf_document2:
    fig_caption: true
    keep_tex: true
    toc: true
    fontsize: 12pt
    geometry: margin=2cm
    number_sections: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

```{r, results = FALSE}
library(tidyverse)
library(magrittr)
library(cowplot)
library(here)
library(arrow)

source(here::here("R", "stability_decomposition.R"))
source(here::here("R", "cross_correlated_error.R"))

mytheme <- theme_cowplot(font_size = 12) +
  background_grid() +
  theme(legend.position = "bottom")
theme_set(mytheme)
options(knitr.table.format = "latex")
```

# Toy examples

```{r}
# No interaction, common environment response, CPE inf to 1
mat <- matrix(
  c(1, 1,
    0, 0,
    1, 1,
    0, 0), byrow = T, ncol = 2)
compensatory_effect(mat)
```

```{r}
# No interaction, opposite environment response, CPE sup to 1
mat <- matrix(
  c(1, 0,
    1, 1,
    1, 0,
    0, 1), byrow = T, ncol = 2)
compensatory_effect(mat)
```

# In simulation without interactions

```{r}
# Common environmental response + no interaction
ti <- cross_correlated_response(
  rho = 1,
  evt_sd = .6, n = 10, time_len = 1000,
  return_tbl = TRUE) %>%
mutate(
  bm_brut = rnorm(length(error), mean = 100, sd = 1),
  stoch_d = .1 * bm_brut * exp(error),
  bm = bm_brut - stoch_d
)
mat <- ti %>%
  pivot_wider(c(time), names_from = "species", values_from = "bm") %>%
  select(-time) %>%
  as.matrix()

mat_stoch <- ti %>%
  pivot_wider(c(time), names_from = "species", values_from = "stoch_d") %>%
  select(-time) %>%
  as.matrix()
# Due to interaction, should be 1
compensatory_effect(mat) / compensatory_effect(mat_stoch)
# Due to common environmental response, should be less than 1, destabilizing:
compensatory_effect(mat_stoch)
```

```{r}
# Independent fluctuations + no interaction
ti <- cross_correlated_response(
  rho = 0,
  evt_sd = .6, n = 10, time_len = 1000,
  return_tbl = TRUE) %>%
mutate(
  bm_brut = rnorm(length(error), mean = 100, sd = 1),
  stoch_d = .1 * bm_brut * exp(error),
  bm = bm_brut - stoch_d
)
mat <- ti %>%
  pivot_wider(c(time), names_from = "species", values_from = "bm") %>%
  select(-time) %>%
  as.matrix()

mat_stoch <- ti %>%
  pivot_wider(c(time), names_from = "species", values_from = "stoch_d") %>%
  select(-time) %>%
  as.matrix()
# Due to interaction, should be 1
compensatory_effect(mat) / compensatory_effect(mat_stoch)
# Due to Independent environmental response, should be 1, i.e:
compensatory_effect(mat_stoch)
```

```{r}
data_raw <- open_dataset(here::here("res", "simCSZenrich2", "sim_toy_compensatory_dyn.arrow"),
          format = "arrow") %>%
collect() %>%
filter(!is.na(richness)) %>%
mutate(
  stoch_d = map2(species, stoch, function(bm, d_stoch) {
    .1 * bm * exp(d_stoch)
    }),
  species = map(species, ~matrix(.x, nrow = 100)),
  stoch = map(stoch, ~matrix(.x, nrow = 100)),
  stoch_d = map(stoch_d, ~matrix(.x, nrow = 100)),
  cpe = map_dbl(species, compensatory_effect),
  cpe_env = map_dbl(stoch_d, compensatory_effect),
  cpe_int = cpe / cpe_env
)
```

```{r}
data_raw %>%
  ggplot(aes(x = as.factor(rho), y = cpe_env)) +
  geom_boxplot() +
  geom_hline(yintercept = 1) +
  geom_hline(yintercept = .5, linetype = "dashed")

data_raw %>%
  ggplot(aes(x = as.factor(rho), y = cpe)) +
  geom_boxplot() +
  geom_hline(yintercept = 1) +
  geom_hline(yintercept = 2, linetype = "dotted") +
  geom_hline(yintercept = .5, linetype = "dashed")

data_raw %>%
  ggplot(aes(x = as.factor(rho), y = cpe_int)) +
  geom_boxplot() +
  geom_hline(yintercept = 1) +
  geom_hline(yintercept = 2, linetype = "dashed")
```

### 2023-05-19 R/network_metrics.R

@@ -3,3 +3,30 @@ gini <- function(x) {
     xx <- sort(x)
     2 * (sum(seq(1, n) * xx)) / (n * sum(xx)) - 1
 }
+
+#function omnivory(A; weighted = true)
+    ## Convert to Bool if preference matrix
+    #tlvl = trophic_levels(A .!= 0)
+    #omnivory = []
+    #for i in 1:size(A, 1)
+        #link_indexes = findall(!=(0), A[i,:])
+        #prey_tlvl = tlvl[link_indexes]
+        ## Relative preference:
+        #if sum(A[i,:]) == 0 # if no prey
+            #rel_pref = []
+            #push!(omnivory, 0)
+            #out = 0
+        #else
+            ## To vector if sparse vector
+            #prey_tlvl_var = (prey_tlvl .- mean(prey_tlvl)).^2
+            #if weighted
+                #rel_pref = Vector(A[i,link_indexes] ./ sum(A[i,:]))
+                #out = sum(prey_tlvl_var .* rel_pref)
+            #else
+                #out = sum(prey_tlvl_var)
+            #end
+            #push!(omnivory, out)
+        #end
+    #end
+    #omnivory
+#end

### 2023-05-19 draft.jl

@@ -18,6 +18,27 @@ include("src/sim.jl")
 include("src/plot.jl")
 include("src/get_modules.jl")
 
+files = readdir("res/simCSZenrich2")
+df = DataFrame(Arrow.Table(join(["res/simCSZenrich2/", files[1]])))
+
+select(df, [:species, :stoch])
+for i in files[isfile.([join(["res/simCSZenrich2/", i]) for i in files])]
+    df = DataFrame(Arrow.Table(join(["res/simCSZenrich2/", i])))
+    select!(df, Not([:cv_sp]))
+    Arrow.write(join(["res/simCSZenrich2/simCSZenrich2/", i]), df, ntasks = 2)
+end
+
+
+arrow = Arrow.Table("res/simCSZenrich2/simCSZ_4001_8000.arrow")
+df = DataFrame(arrow)
+filter(:rho => x -> x == 1.0, df)[3, [:cv_sp, :bm_sp]]
+filter(:cv_sp => x -> ismissing(x), df)
+filter(:cv_sp => x -> !ismissing(x) , df)
+df.cv_sp
+
+toy = select(df, [:rep, :productivity, :richness, :ct, :Z, :rho, :env_stoch, :species, :stoch])
+Arrow.write("res/simCSZenrich2/simCSZenrich2/sim_toy_compensatory_dyn.arrow", toy)
+
 #########
 #  Sim  #
 #########
@@ -25,12 +46,21 @@ include("src/get_modules.jl")
 #simCS(C, S, Z, h, c, σₑ, K; max = 50000, last = 25000, dt = 0.1, return_sol = false)
 using Distributions
 
-ti = simCS(0.4, 20;
-           d = .1,
-           Z = 100, h = 2.0, c = 0.0,
-           σₑ = 1.0, K = 5, max = 5000,
+ti = simCS(.4, 5;
+           d = .2,
+           Z = 1, h = 2.0, ρ = -1,
+           σₑ = 1.0, K = .5, max = 500,
            last = 100, dt = 0.1, return_sol = false
           )
+map(typeof, ti)
+convert.(Float64, ti.omnivory)
+
+
+nb_alive_species = try
+    length(trophic_structure(ti, last = 1000).alive_species)
+catch
+    missing
+end
 
 plot(ti, idxs = collect(1:1:length(get_parameters(ti).network.species)))
 cv(ti, last = 100, idxs = collect(1:1:length(get_parameters(ti).network.species)))
[…]

### 2023-05-19 scripts/connectance_richness_stoch_array.jl

@@ -34,13 +34,13 @@ param = NamedTuple.(eachrow(param))
 
 
 pm = sample(param)
-println("Running warmup: r = $(pm.enrich.r), K = $(pm.enrich.K), σₑ = $(pm.sigma), ρ = $(pm.rho)")
+println("Running warmup: r = $(pm.r), K = $(pm.K), σₑ = $(pm.sigma), ρ = $(pm.rho)")
 
 warmup = simCS(pm.connectance, pm.richness;
       Z = 100,
       d = 0.1, σₑ = pm.sigma, ρ = pm.rho,
       h = 2.0, c = 0.0,
-      r = pm.enrich.r, K = pm.enrich.K, alpha_ij = 0.5,
+      r = 1.0, K = pm.K, alpha_ij = 0.5,
       max = 50, last = 10, dt = 0.1,
       K_alpha_corrected = true,
       return_sol = false
@@ -55,12 +55,12 @@ println("Running param sim from lines $first_sim to $last_sim")
 
 timing = @elapsed sim = @showprogress pmap(p ->
                          merge(
-                               (rep = p.rep, productivity = p.enrich.name),
+                               (rep = p.rep, productivity = p.K),
                                simCS(p.connectance, p.richness;
                                      Z = p.Z,
                                      d = 0.1, σₑ = p.sigma, ρ = p.rho,
                                      h = 2.0, c = 0.0,
-                                     r = p.enrich.r, K = p.enrich.K,
+                                     r = 1.0, K = p.K,
                                      alpha_ij = 0.5,
                                      max = 5000, last = 100, dt = 0.1,
                                      K_alpha_corrected = true,
@@ -75,5 +75,7 @@ timing = @elapsed sim = @showprogress pmap(p ->
 df = DataFrame(sim)
 println("$(length(sim)) simulations took $(round(timing /60, digits = 2)) minutes to run")
 
+file_ts = string("simCSZ_", first_sim, "_", last_sim, "_ts.arrow")
+Arrow.write(file_ts, select(df, [:species, :stoch]))
 file = string("simCSZ_", first_sim, "_", last_sim, ".arrow")
-Arrow.write(file, df)
+Arrow.write(file, select(df, Not([:species, :stoch])))

### 2023-05-19 scripts/param_comb_connectance_richness.jl

@@ -1,19 +1,16 @@
-import Pkg
-Pkg.instantiate()
 using CSV, StatsBase, DataFrames, Arrow
 
-rep = 1:20
+rep = 1:50
 S = [5, 10, 20, 40, 60]
 C = 0.02:.05:.32
-sigma = .1:.1:.6
-Z = [5, 10, 50, 100, 250, 500, 1000]
-ρ = 0:.1:1
-enrich = [(K = 1.0, r = 1.0, name = "basic"),
-          (K = 20.0, r = 1.0, name = "enrichment")]
+sigma = .2:.2:1.0
+Z = [1, 2, 5, 10, 20, 40, 100]
+ρ = 0:.2:1
+K = [5, 10, 20, 30]
 
-names = (:rep, :richness, :connectance, :Z, :sigma, :rho, :enrich)
+names = (:rep, :richness, :connectance, :Z, :sigma, :rho, :K)
 param = map(p -> (;Dict(k => v for (k, v) in zip(names, p))...),
-            Iterators.product(rep, S, C, Z, sigma, ρ, enrich)
+            Iterators.product(rep, S, C, Z, sigma, ρ, K)
            )[:]
 
 

### 2023-05-19 src/interaction_strength.jl

@@ -116,14 +116,14 @@ omnivory(p; weighted = false)
 function omnivory(A; weighted = true)
     # Convert to Bool if preference matrix
     tlvl = trophic_levels(A .!= 0)
-    omnivory = []
+    omnivory = Float64[]
     for i in 1:size(A, 1)
         link_indexes = findall(!=(0), A[i,:])
         prey_tlvl = tlvl[link_indexes]
         # Relative preference:
         if sum(A[i,:]) == 0 # if no prey
             rel_pref = []
-            push!(omnivory, 0)
+            push!(omnivory, 0.0)
             out = 0
         else
             # To vector if sparse vector

### 2023-05-19 src/sim.jl

@@ -1,8 +1,8 @@
 function simCS(C, S;
         Z = 100,
         d = 0, σₑ = .5, ρ = 0.0,
-        h = 2.0, c = 1.0,
-        r = 1.0, K = 1.0, alpha_ij = 0.5,
+        h = 2.0, c = 0.0,
+        r = 1.0, K = 5.0, alpha_ij = 0.5,
         max = 5000, last = 1000, dt = 0.1,
         return_sol = false,
         K_alpha_corrected = true,
@@ -54,6 +54,7 @@ function simCS(C, S;
                             environment = env,
                             producer_competition = ProducerCompetition(fw, αii = 1.0, αij = alpha_ij),
                             env_stoch = EnvStoch(σₑ))
+        ω = p.functional_response.ω
     B0 = rand(S)
     # Simulate
     timing = @elapsed m = try
@@ -71,6 +72,7 @@ function simCS(C, S;
     else
         m = (t = 0, x = missing)
         timing = missing
+        ω = missing
     end
 
     if return_sol
@@ -82,7 +84,7 @@ function simCS(C, S;
     time_series = get_time_series(m; last = last)
 
     out = merge(
-                (S = S, ct = C, A = A, rho = ρ, env_stoch = σₑ, Z = Z, timing = timing),
+                (S = S, ct = C, omega = ω, rho = ρ, env_stoch = σₑ, Z = Z, timing = timing),
                 out,
                 time_series
                )
@@ -178,6 +180,7 @@ function get_stab_fw(m; last = 10)
                     :total_biomass     ,
                     :bm_sp             ,
                     :cv_sp             ,
+                    :alive_species     ,
                     :tlvl              ,
                     :w_avg_tlvl        ,
                     :max_tlvl          ,
@@ -190,8 +193,9 @@ function get_stab_fw(m; last = 10)
                     :avg_max_int       ,
                     :max_max_int       ,
                     :min_max_int       ,
-                    :gini_max_int,
-                    :omnivory
+                    :gini_max_int      ,
+                    :omnivory          ,
+                    :avg_omnivory
                    )
 
     if length(m.t) >= last
@@ -204,6 +208,8 @@ function get_stab_fw(m; last = 10)
         max_int = max_interaction_strength(p)
         non_zero_max_int = [i for i in max_int if i != 0]
         troph_struc = trophic_structure(m, last = last)
+        alive_species = troph_struc.alive_species
[…]

### 2023-07-06 report/cs_analysis.Rmd
Improve intro

@@
 
-Understanding the drivers of temporal stability is a key question in Ecology.
-BEF theory shows that species richness is a key driver to understand the
-temporal stability of community biomass.
-
-Species richness was demonstrated to increase community stability by driving higher
-asynchrony in community in various assemblages and ecosystems. In particular,
-high response diversity, which drives independant species fluctuations, seems to a key
-factor driving the positive effect of species richness of stability
-[@loreau_species_2008; @thibaut_understanding_2013; @zhao_biodiversity_2022]. However,
-those studies were often limited to monotrophic assemblages. As natural
-communities are often composed of multiple trophic level, our understanding of
-community stability needs to incorporate food-web structure.
-
+Global change and their effects constitute major treats to ecosystem stability.
+Among them, global change is predicted to lead dramatically more variable
+environments [@pachauri_climate_2015]. This new threat adds to current
+eutrophication in many ecosystems [@maure_globally_2021, add ref], which is
+known to dramatically impair ecosystem functioning. Understanding how
+environmental variability and eutrophication will alter ecosystem stability is
+then a timely question.
+
+Biodiversity, in terms of species richness, has been repeatedly shown to drive
+higher temporal stability of ecological communities, across various taxa and
+ecosystems. Species richness can dampen the effects of perturbations on the
+temporal variability of community biomass because more diverse communities
+contain species with more diversity of responses to perturbations, which
+generates asynchrony in population fluctuations, thereby stabilizing community
+biomass fluctuations [@loreau_species_2008; @thibaut_understanding_2013;
+@zhao_biodiversity_2022]. In turn, the effects of human pressures on biotic
+homogenization reported in various ecosystems [@buisson_toward_2013;
+@muthukrishnan_invasive_2020; @saladin_rapid_2020] is another threat, which
+might in turn affect dampens the effects of species richness on ecosystem
+stability. However, the joint effects of external stressors such as
+environmental variability and eutrophication and internal stressors such as the
+loss response diversity has been rarely assessed in temporal stability areas.
+
+The question of stressors can even become complex in multitrophic communities,
+where species richness corresponds both to horizontal and vertical diversity.
 Food-web structure has been shown to have tremendous effect on community
 stability. The degree of generalism of predator was shown to modulate
-stability-richness relationships [@thebault_trophic_2005]. The strength and distribution of
-interaction strength was also shown to be strong driver of community stability
-[@mccann_weak_1998]. Omnivory was also shown to drive higher stability
-[@mccann_reevaluating_1997]. However, it is quite unkown how those food-web
-structure elements would affect stability-species richness relationships.
-
-The effect of environmental stressors can also strongly affect community
-variability. Higher environmental stress and variability may dampens the effect
-of richness on stability [@loreau_biodiversity_2001]. Lastly, productivity of a
-system, as the quantity of biomass input in the ecosystem, can have tremendous
-effect on both community structure and stabilty [@lindeman_trophic-dynamic_1942;
-@binzer_dynamics_2012; @binzer_interactive_2016]. Productivity can increase
-species richness in the food-web by increasing the level of energy input
-[@lindeman_trophic-dynamic_1942] but also destabilises community biomass by
-increasing population variability, a behavior coined as the paradox of
-enrichment [@rosenzweig_paradox_1971]. A better understanding of the effect of
-species richness on community stability should then include environmental
-gradient and stressors.
-
-Community stability can itself be partitioned in several components, i.e.
-population stability and population asynchrony [@thibaut_understanding_2013;
-@zhao_biodiversity_2022]. Population stability can be itself partioned in total
-biomass and population variability effect. Population asynchrony can further be
-partioned in statistical averaging effect and compensatory dynamics effects
-[@zhao_biodiversity_2022]. Partitioning stability allows to better understand
-how food-web structure and external factors affect stability. For exemple,
-environmental stochasticity is expected to primarily affect population
-stability, while response diversity should affect primarily compensatory
-dynamics.
+stability-richness relationships [@thebault_trophic_2005]. The strength and
+distribution of interaction strength was also shown to be strong driver of
+community stability [@mccann_weak_1998]. Omnivory was also shown to drive higher
+stability [@mccann_reevaluating_1997]. The effects of food-web structure on
+ecosystem stability has been mostly assessed with small modules [but see
+@eschenbrenner_diversity_nodate], and we know very little how food-web structure
+affects the relationships between species richness and temporal stability.
+
+Both stressors and food-web structure are expected to have different effects on
+temporal stability. Stability of community biomass can itself be partitioned in
+several components, i.e. population stability and population asynchrony
+[@thibaut_understanding_2013; @zhao_biodiversity_2022]. Population stability can
+be itself partioned in total biomass and population variability effect.
+Population asynchrony can further be partioned in statistical averaging effect
+and compensatory dynamics effects [@zhao_biodiversity_2022]. Partitioning
+stability allows to better understand how food-web structure and external
+factors affect stability. We expect that environmental variability will
+primarily affect. For exemple, environmental stochasticity is expected to
+primarily affect population variance. Productivity is expected to have two
+effects on stability. First, productivity may increase species richness and
+average trophic level by increasing the flux of biomass in the system
+[@lindeman_trophic-dynamic_1942] but on the other side, the resulting higher growth rate
+of primary producers may increase the population variability
+[@binzer_interactive_2016] and thus decreases the temporal stability of
+community biomass. Response diversity is expected to act primarily on
+compensatory dynamics in the food-webs, as low response diversity will decrease
+the effects. Higher connectance and interaction strength are expected to dampens
+population variability but to lead to higher synchrony at the same time.
+
+---
+#Understanding the mechanisms that determine temporal
+#stability of ecosystem functioning is a long standing
+#question in Ecology [@may_will_1972; @angelis_stability_1975;
+#@mccann_diversitystability_2000; @tilman_biodiversity_2006;
+#@donohue_navigating_2016; @kefi_advancing_2019].
+---
+
+In this study, we investigated both the effects of stressors (productivity,
+environnmental variability and response diversity) and of food-web structure
+(connectance, average interaction strength, average trophic level) on species
+richness-stability relationships. To do, we used a bioenergetic food-web model
+[@yodzis_body_1992; @brose_allometric_2006; @delmas_simulations_2017] added to
+environmental stochasticity.
 
@@
   "Productivity", "", "Dampens (Binzer et al., 2012; Binzer et al., 2016; Tabi et al., 2019)",
-  "Environmental variability", "", "Dampens",
-)
+  "Environmental variability", "", "Dampens",) %>%
+kbl(caption = "Predictions of stability-richness relationship from the literature.") %>%
+kable_styling()
 ```
@@
 ```{r}
-sim_ok %>%
-  filter(ct_alive != 0, rho == 0, env_stoch == .1)
 sim_sem <- sim_ok %>%
-  filter(ct_alive != 0) %>%
+  filter(max_tlvl_alive > 1) %>%
   mutate(across(c(stab_com, async, pop_stab, total_biomass, inv_sum_pop_var, sae_even, evenness_sae, cpe_env, cpe_int), log, , .names = "log_{.col}")) %>%
   na.omit()
+```
+
+```{r}
+summary(sim_sem$max_tlvl_alive)
+```
+
+```{r}
+p_sim_rich_prod_fw_only <- sim_sem %>%
+  mutate(stab_pop = 1/ avg_cv_sp) %>%
+  filter(rho %in% c(0, 1)) %>%
+  pivot_longer(
+    c(stab_com, stab_pop, sync),
+    names_to = "metric",
+    values_to = "stab") %>%
+  mutate(
+    metric = var_replacement()[metric],
+    rho = rho_replacement()[as.character(rho)]
+  ) %>%
+  ggplot(aes(x = log(richness), y = log(stab), color = factor(productivity))) +
+  geom_point(alpha = .1, shape = 20) +
+  geom_smooth(method = "lm") +
+  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
+  labs(
+    color = "Productivity",
+    x = "Species richness",
+    y = "Stability component"
+  ) +
+  scale_x_continuous(
+    sec.axis = sec_axis(~ . ,
+      name = "Response diversity",
+      breaks = NULL,
+      labels = NULL)
+  )
+ggsave(
+  filename = here("report", "figures", "p_sim_rich_prod_fw_only.png"),
+  p_sim_rich_prod_fw_only,
+  scale = 1.4,
+  width = 88,
+  height = 88 * 1,
+  units = "mm"
+)
+colnames(sim_sem)
+```
+
+```{r}
+p_sim_rich_prod_fw_only_cpe <- sim_sem %>%
+  mutate(stab_pop = 1/ avg_cv_sp, ) %>%
+  filter(rho %in% c(0, 1)) %>%
+  pivot_longer(
+    c(sae_total, cpe),
+    names_to = "metric",
+    values_to = "stab") %>%
+  mutate(
+    metric = var_replacement()[metric],
+    rho = rho_replacement()[as.character(rho)]
+  ) %>%
+  ggplot(aes(x = log(richness), y = log(stab), color = factor(productivity))) +
+  geom_point(alpha = .1, shape = 20) +
+  geom_smooth(method = "lm") +
+  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
+  labs(
+    color = "Productivity",
+    x = "Species richness",
+    y = "Stability component"
+  ) +
+  scale_x_continuous(
+    sec.axis = sec_axis(~ . ,
+      name = "Response diversity",
+      breaks = NULL,
+      labels = NULL)
+  )
+ggsave(
+  filename = here("report", "figures", "p_sim_rich_prod_fw_only_cpe.png"),
+  p_sim_rich_prod_fw_only_cpe,
+  scale = 1.4,
+  width = 88,
+  height = 88 * 1,
+  units = "mm"
+)
 ```
@@
 ```{r}
+sim_ok %>%
+  filter(max_tlvl_alive > 1)
+```
+
+```{r}
 sim_stab %>%
@@
   geom_boxplot() +
-  geom_hline(yintercept = 1)
+  geom_hline(yintercept = c(.5, 1))
+sim_stab %>%
+  ggplot(aes(x = as.factor(env_stoch), y = cpe_env)) +
+  geom_boxplot() +
+  geom_hline(yintercept = c(.5, 1))
 sim_stab %>%
@@
   ggplot(aes(x = as.factor(rho), y = evenness_sae)) +
+  geom_boxplot() +
+  geom_hline(yintercept = 1)
+sim_ok %>%
+  filter(max_tlvl_alive > 1) %>%
+  ggplot(aes(x = as.factor(as.integer(richness)), y = evenness_sae)) +
+  geom_boxplot() +
+  geom_hline(yintercept = 1)
+sim_ok %>%
+  filter(max_tlvl_alive > 1) %>%
+  ggplot(aes(x = as.factor(as.integer(max_tlvl_alive)), y = evenness_sae)) +
   geom_boxplot() +

### 2023-07-06 R/string_replacements.R

@@ -18,7 +18,9 @@ var_replacement <- function() {
     richness = "Richness",
     rho = "Env Corr",
     productivityenrichment = "Enrichment",
-    env_stoch = "Env variance"
+    env_stoch = "Env variance",
+    sae_total = "Stat Avg eff",
+    cpe = "Compensatory eff"
 
   )
 }

### 2023-07-06 draft.jl

@@ -104,6 +104,23 @@ sim_int_mat([0 0 0; 0 0 0; 1 1 0];
             fun = stoch_d_dBdt!,
             max = 500, last = 100, dt = 0.1, return_sol = false)
 
+#############
+#  testing  #
+#############
+
+fw = FoodWeb([0 0; 0 0])
+p = ModelParameters(fw)
+# Default
+sim = simulate(p, [1, 1], tmax = 2000, callback = CallbackSet(
+          TerminateSteadyState(1e-6, 1e-4),
+          ExtinctionCallback(10e-6, true),
+      ),)
+out_inv = simulate(p, b0_Inv, tmax = 2000, callback = DifferentialEquations.CallbackSet(
+          ExtinctionCallback(10^-4, true),
+      ))
+maximum(sim.t)
+
+sim2 = simulate(p, [1, 1], tmax = 2000, callback = ExtinctionCallback())
 
 
 ###########

### 2023-07-06 use_case/two_species_kuramoto.jl

@@ -4,6 +4,7 @@
 using EcologicalNetworksDynamics
 using Plots
 
+
 function get_parameters_two_species_kuramoto(;
         ### Mortality rates for consumers
         dcons = .1,
@@ -82,10 +83,11 @@ end
 # Trophic coupling
 p = get_parameters_two_species_kuramoto(B = 0.01, α = 0)
 m = simulate(p, [.1, .3, .1, .3],
-             tmax = 600,
+             tmax = 2000,
              callback = nothing
             );
 p1 = plot(m, idxs = [3, 4], legend = false, title = "Trophic coupling")
+coefficient_of_variation(m, idxs = [3, 4])
 
 # Resource coupling
 p = get_parameters_two_species_kuramoto(B = 0.00, α = .1)

### 2023-07-11 _targets.Rmd
Redo analysis with new simulations

--- 2023-05-17 _targets.Rmd
@@
 options(tidyverse.quiet = TRUE)
-tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB"))
+tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"))
 source(here::here("R", "network_metrics.R"))
 source(here::here("R", "string_replacements.R"))
+source(here::here("R", "stability_decomposition.R"))
 source(here::here("R", "model_helpers.R"))
@@
 
+# New simulation
+
+```{targets raw_sim}
+list(
+  tar_target(var_param_sim, c("rep", "productivity", "S", "ct", "rho", "env_stoch", "Z")),
+  tar_target(sim_files_out, list.files(here::here("res", "simCSZenrich3/simCSZenrich3"))),
+  tar_target(sim_files_ts,
+    list.files(here::here("res", "simCSZenrich3")) %>% #
+      .[str_detect(., "_ts")]
+    ),
+  tar_target(sim_param,
+    map_dfr(sim_files_out,
+      function (x) {
+        open_dataset(here::here("res", "simCSZenrich3/simCSZenrich3", x),
+          format = "arrow") %>%
+        collect() %>%
+        select(all_of(var_param_sim))
+      })
+    ),
+  # Because I had to remove one ts that failed...
+  tar_target(sim_param_ts,
+    map_dfr(str_remove(sim_files_ts, "_ts")[str_remove(sim_files_ts, "_ts") %in% sim_files_out],
+      function (x) {
+        open_dataset(here::here("res", "simCSZenrich3/simCSZenrich3", x),
+          format = "arrow") %>%
+        collect() %>%
+        select(all_of(var_param_sim))
+      })
+  ),
+  tar_target(sim_prep,
+        open_dataset(here::here("res", "simCSZenrich3/simCSZenrich3", sim_files_out),
+          format = "arrow") %>%
+        collect() %>%
+        # Transform back interaction strength into matrices
+        mutate(across(where(is.list), as.list)) %>%
+        filter(!is.na(richness)) %>%
+        mutate(across(c(int_strength, max_int),
+            ~map2(.x, S,
+              function(y, rich) {
+                matrix(y, nrow = rich)
+              }
+            )
+          )
+          ) %>%
+        # Get matrix of alive species
+        mutate(max_int_alive  = map2(max_int, bm_sp,
+            function(mat, bm) {
+              mask <- bm > 10^-6
+              mat[mask, mask, drop = FALSE]
+            }
+          )
+        ) %>%
+        select(-max_int),
+        pattern = sim_files_out
+      ),
+  tar_target(sim_net,
+    sim_prep %>%
+      mutate(
+        persistence = richness / S,
+        async = 1 / sync,
+        stab_pop = 1 / avg_cv_sp,
+        ct_alive = map_dbl(max_int_alive,
+          ~ifelse(sum(.x) == 0, 0,
+            sum(.x > 0) / ((ncol(.x))^2))),
+        max_max_int_alive = map_dbl(max_int_alive,
+          ~ifelse(length(.x[.x > 0]) == 0, 0, max(.x[.x > 0]))
+          ),
+        avg_max_int_alive = map_dbl(max_int_alive,
+          ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
+          ),
+        sd_max_int_alive = map_dbl(max_int_alive,
+          ~ifelse(length(.x[.x > 0]) <= 1, 0, sd(.x[.x > 0]))
+          ),
+        cv_max_int_alive = sd_max_int_alive / avg_max_int_alive,
+        inv_sd_max_int_alive = 1 / sd_max_int_alive,
+        gini_max_int_alive = map_dbl(max_int_alive,
+          ~ifelse(length(.x[.x > 0]) == 0, 0, gini(.x[.x > 0]))),
+        avg_omnivory = map_dbl(omnivory, mean),
+        disconnected_prod = map_lgl(max_int_alive,
+          ~any(colSums(.x) == 0 & rowSums(.x) == 0))
+        ) %>%
+    select(!where(is.list))
+  ),
+  tar_target(sim_ts2_null,
+    open_dataset(here::here("res", "simCSZenrich3", sim_files_ts),
+          format = "arrow") %>%
+        collect() %>%
+        # Transform back interaction strength into matrices
+        mutate(across(where(is.list), as.list)) %>%
+        mutate(is_null = map_lgl(species, is.null)) %>%
+        select(is_null),
+        pattern = sim_files_ts
+        ),
+  tar_target(sim_ts2,
+    open_dataset(here::here("res", "simCSZenrich3", sim_files_ts),
+          format = "arrow") %>%
+        collect() %>%
+        # Transform back interaction strength into matrices
+        mutate(across(where(is.list), as.list)) %>%
+        filter(!map_lgl(species, is.null)) %>%
+        mutate(
+          stoch_d = map2(species, stoch, function(bm, d_stoch) {
+            .1 * bm * exp(d_stoch)
+            }),
+          species = map(species, ~matrix(.x, nrow = 100)),
+          stoch = map(stoch, ~matrix(.x, nrow = 100)),
+          stoch_d = map(stoch_d, ~matrix(.x, nrow = 100)),
+          cpe = map_dbl(species, compensatory_effect),
+          cpe_env = map_dbl(stoch_d, compensatory_effect),
+          cpe_int = cpe / cpe_env,
+          stab_com = map_dbl(species, community_stability),
+          pop_stab = map_dbl(species, population_stability),
+          bm_sp = map(species, ~colMeans(.x)),
+          bm_total = map_dbl(bm_sp, ~sum(.x)),
+          sd_sp = map(species, ~apply(.x, 2, sd)),
+          sum_sd_sp = map_dbl(sd_sp, ~sum(.x)),
+          async = map_dbl(species, asynchrony),
+          sae = map(species, statistical_averaging_effect),
+          sae_total = map_dbl(sae, ~.x["total"]),
+          sae_even = map_dbl(sae, ~.x["even"]),
+          evenness_sae = map_dbl(sae, ~.x["eveness"])
+        ) %>%
+        select(-species, -stoch_d, -stoch),
+        pattern = sim_files_ts
+  ),
+  tar_target(sim_stab, cbind(sim_param[!sim_ts2_null$is_null,], sim_ts2) %>% as_tibble()),
+  tar_target(sim, left_join(sim_net %>% select(-async, -stab_com), sim_stab, by = var_param_sim)),
+  tar_target(sim_fw,
+    sim %>%
+      filter(
+        max_tlvl > 1,
+        sum_sd_sp != Inf,
+        bm_total > 10^-5,
+        !disconnected_prod
+        )
+   ),
+   tar_target(sim_fw_df, as.data.frame(sim_fw))
+  )
+```
+
+## Species bm, sd and tlvl
+
+```{targets sim_sp, tar_simple = TRUE}
+sim_stab %>%
+  select(all_of(c(var_param_sim, "sd_sp", "bm_sp"))) %>%
+  left_join(
+    sim_prep %>%
+      select(all_of(c(var_param_sim, "tlvl", "alive_species")))
+  ) %>%
+  mutate(
+    sd_sp = map2(sd_sp, alive_species, ~.x[.y]),
+    bm_sp = map2(bm_sp, alive_species, ~.x[.y]),
+    cv_sp = map2(sd_sp, bm_sp, ~.x / .y),
+    tlvl_bm_sd_sp = pmap(list(tlvl, bm_sp, sd_sp, cv_sp, alive_species),
+      function(x, y, z, a, b) {
+        rbind.data.frame(list(
+        species = b,
+            tlvl = x,
+            bm_sp = y,
+            sd_sp = z,
+            cv_sp = a
+        )
+        )
+      }),
+    check = map_lgl(tlvl_bm_sd_sp, ~is.null(nrow(.x)))
+  ) %>%
+  filter(!check) %>%
+  select(all_of(c(var_param_sim, "tlvl_bm_sd_sp"))) %>%
+  unnest(c(tlvl_bm_sd_sp))
+```
+
+## SEM
+
+```{targets sem-process}
+list(
+  tar_target(sem_model_list,
+    list(
+      ct_alive = lm(ct_alive ~ ct + S, sim_fw_df),
+      richness = lm(richness ~ ct + S, sim_fw_df),
+      #  max_tlvl = lm(max_tlvl ~ ct + S + Z + productivity, sim_fw_df),
+      w_avg_tlvl = lm(w_avg_tlvl ~ richness + ct_alive + productivity, sim_fw_df),
+      avg_omnivory = lm(avg_omnivory ~ w_avg_tlvl + ct_alive + richness + productivity, sim_fw_df),
+      avg_int_strength = lm(avg_int_strength ~ w_avg_tlvl + ct_alive + richness + productivity, sim_fw_df),
+      pop_stab = lm(pop_stab ~ Z + richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + env_stoch + productivity, sim_fw_df),
+      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive, sim_fw_df),
+      sae_even = lm(sae_even ~ richness, sim_fw_df),
+      cpe_int = lm(cpe_int ~ richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + productivity, sim_fw_df),
+      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_df)
+    )
+    ),
+  tar_target(sem, as.psem(sem_model_list)),
+  tar_target(sem_coeff, {
+    ti <- summary(sem)$coefficients[, c(1, 2, 8, 9)]
+    colnames(ti)[4] <- "Signif"
+    ti #%>%
+      #filter(abs(Std.Estimate) > 0.1)# %>%
+#  mutate(
+#    Response = var_replacement()[Response],
+#    Predictor = var_replacement()[Predictor]
+#  ) %>%
+    }),
+  tar_target(tab_sem_coeff,
+    sem_coeff %>%
+      kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
+      collapse_rows(1, valign = "middle") %>%
+      kable_styling()
+    ),
+  tar_target(sem_collinearity,
+    map_dfr(setNames(sem_model_list, names(sem_model_list)),
+      performance::check_collinearity,
+      .id = "response") %>%
+    as_tibble),
+  tar_target(sem_rsquared,
+    map_dfr(sem_model_list, rsquared) %>%
+      mutate(Response = var_replacement()[Response]) %>%
+      select(Response, R.squared)
+    ),
+  tar_target(tab_sem_vif,
+    sem_collinearity %>%
+      mutate(
+        response = var_replacement()[response],
+        Term = var_replacement()[Term]
+        ) %>%
+      kable(
+        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
+      kable_styling()
+    ),
+  tar_target(tab_sem_rsquared,
+    sem_rsquared %>%
+      kable(caption = "Rsquared for the Structural Equation Model.") %>%
+      kable_styling()
+  )
+)
+```
+
+# plot
+
+```{targets p-stab}
+list(
+  tar_target(p_cpe_env_rho, sim_fw %>%
+    ggplot(aes(x = as.factor(1 - rho), y = cpe_env)) +
+    geom_hline(yintercept = 1, linetype = "dashed") +
+    geom_hline(yintercept = .5, linetype = "dashed", color = "red") +
+    geom_boxplot() +
+    labs(x = "Response diversity", y = "Env. Compensatory effect") +
+    theme_bw()),
+  tar_target(p_stoch_pop_stab,
+    sim_fw %>%
+      ggplot(aes(x = as.factor(env_stoch), y = pop_stab)) +
+      geom_boxplot() +
+      labs(x = "Environmental stochasticity", y = "Population stability") +
+      theme_bw()),
+    tar_target(p_prod_bm,
+      sim_fw %>%
+        filter(bm_total > 10^-5) %>%
+        ggplot(aes(x = as.factor(productivity), y = log(bm_total))) +
+        geom_boxplot() +
+        labs(x = "Productivity", y = "Total biomass") +
+        theme_bw()
+      ),
+    tar_target(p_prod_pop_stab,
+      sim_fw %>%
+        ggplot(aes(x = as.factor(productivity), y = log(pop_stab))) +
+        geom_boxplot() +
+        labs(x = "Productivity", y = "Population stability") +
+        theme_bw()
+    ),
+    tar_target(p_stab_comp_stress,
+      plot_grid(
+        p_cpe_env_rho,
+        p_stoch_pop_stab,
+        p_prod_bm,
+        p_prod_pop_stab,
+        labels = "auto"
+      )
+
+    )
+
+)
+
+```
+
+## Stability-diversity relationship
+
+```{targets p-stab-rich}
+list(
+  tar_target(p_stab_s_prod,
+    sim_fw %>%
+      filter(productivity %in% c(5, 30), rho == 0, env_stoch == .2) %>%
+      ggplot(aes(x = richness, y = stab_com, color = as.factor(productivity))) +
+      geom_point() +
+      geom_smooth() +
+      labs(x = "Species richness", y = "Community stability", color = "Productivity") +
+      theme_bw()),
+    tar_target(p_stab_s_env_stoch,
+      sim_fw %>%
+        filter(env_stoch %in% c(.2, .6), rho == 0, productivity == 5) %>%
+        ggplot(aes(x = richness, y = stab_com, color = as.factor(env_stoch))) +
+        geom_point() +
+        geom_smooth() +
+        labs(x = "Species richness", y = "Community stability", color = "Env. variability") +
+        theme_bw()),
+      tar_target(p_stab_s_resp_div,
+        sim_fw %>%
+          filter(rho %in% c(0, 1), productivity == 5, env_stoch == .2) %>%
+          ggplot(aes(x = richness, y = stab_com, color = as.factor(1 - rho))) +
+          geom_point() +
+          geom_smooth() +
+          labs(x = "Species richness", y = "Community stability", color = "Response diversity") +
+          theme_bw()
+      ),
+      tar_target(p_stab_s_stress,
+         plot_grid(
+           p_stab_s_prod,
+           p_stab_s_env_stoch,
+           p_stab_s_resp_div,
+           labels = "auto"
+         )
+      )
+)
+```
+
+## Interaction strength effect
+
+```{targets p_int_stab, tar_simple = TRUE}
+sim_fw %>%
+  filter(rho %in% c(0), productivity == 5, env_stoch == .2) %>%
+  pivot_longer(c(stab_com, async, sae_total, cpe,
+      sae_even, evenness_sae,
+      cpe_int, cpe_env, stab_pop
+      ), names_to = "async_decomp", values_to = "values") %>%
+  mutate(async_decomp = var_replacement()[async_decomp]) %>%
+  ggplot(aes(x = avg_int_strength, y = values)) +
+  geom_point() +
+  geom_smooth() +
+  labs(x = "Avg feeding rate", y = "Asynchrony component") +
+  facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
+  theme_bw()
+```
+
+```{targets p_int_fw, tar_simple = TRUE}
+sim_fw %>%
+  filter(rho %in% c(0), productivity == 5, env_stoch == .2) %>%
+  pivot_longer(c(richness, ct_alive, max_tlvl, avg_omnivory, w_avg_tlvl
+      ), names_to = "fw_str", values_to = "values") %>%
+  mutate(fw_str = var_replacement()[fw_str]) %>%
+  ggplot(aes(x = avg_int_strength, y = values)) +
+  geom_point() +
+  geom_smooth() +
+  labs(x = "Avg feeding rate", y = "Food-web structure") +
+  facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
+  theme_bw()
+```
+
+## Avg Omnivory
+
+```{targets p-omn}
+list(
+  tar_target(p_omn_stab,
+    sim_fw %>%
+      filter(rho %in% c(0), env_stoch == .2) %>%
+      pivot_longer(c(stab_com, pop_stab, async
+          ), names_to = "stab_comp", values_to = "values") %>%
+      mutate(stab_comp = var_replacement()[stab_comp]) %>%
+      ggplot(aes(x = avg_omnivory, y = values)) +
+      geom_point() +
+      geom_smooth() +
+      labs(x = "Avg omnivory", y = "Stability component") +
+      facet_wrap(~stab_comp, ncol = 3, scales = "free_y") +
+      theme_bw()),
+  tar_target(p_omn_fw,
+    sim_fw %>%
+      filter(rho %in% c(0), env_stoch == .2) %>%
+      pivot_longer(c(richness, ct_alive, w_avg_tlvl, max_tlvl
+          ), names_to = "fw_str", values_to = "values") %>%
+      mutate(fw_str = var_replacement()[fw_str]) %>%
+      ggplot(aes(x = avg_omnivory, y = values)) +
+      geom_point() +
+      geom_smooth() +
+      labs(x = "Avg. Omnivory", y = "Food-web structure") +
+      facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
+      theme_bw()
+  )
+)
+```
+
+```{targets p-ct-rich-stab}
+list(
+  tar_target(p_ct_stab,
+    sim_fw %>%
+      filter(rho %in% c(0), productivity == 5, env_stoch == .2) %>%
+      pivot_longer(c(stab_com, async, sae_total, cpe,
+          sae_even, evenness_sae,
+          cpe_int, cpe_env, stab_pop
+          ), names_to = "async_decomp", values_to = "values") %>%
+      mutate(async_decomp = var_replacement()[async_decomp]) %>%
+      ggplot(aes(x = ct_alive, y = values)) +
+      geom_point() +
+      geom_smooth() +
+      labs(x = "Connectance", y = "Asynchrony component") +
+      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
+      theme_bw()
+    ),
+  tar_target(p_rich_stab,
+    sim_fw %>%
+      filter(rho %in% c(0), productivity == 5, env_stoch == .2) %>%
+      pivot_longer(c(stab_com, async, sae_total, cpe,
+          sae_even, evenness_sae,
+          cpe_int, cpe_env, stab_pop
+          ), names_to = "async_decomp", values_to = "values") %>%
+      mutate(async_decomp = var_replacement()[async_decomp]) %>%
+      ggplot(aes(x = richness, y = values)) +
+      geom_point() +
+      geom_smooth() +
+      labs(x = "Species richness", y = "Asynchrony component") +
+      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
+      theme_bw()
+    )
+)
+```
+
+```{targets p_cor, tar_simple = TRUE}
+cor_var <- cor(
+  sim_fw %>%
+    select(c(richness, ct_alive, Z, bm_total,
+        avg_int_strength, avg_omnivory, max_tlvl,
+        rho, env_stoch, productivity,
+        stab_com, pop_stab, async, sae_total, sae_even,
+        evenness_sae, cpe, cpe_int, cpe_env)) %>%
+  na.omit() %>%
+  rename(any_of(get_rev_vec_name_val(var_replacement()))),
+    method = "spearman")
+ggcorrplot(cor_var, type = "lower", lab = TRUE)
+```
+
 # Pipeline
@@
 library(glmmTMB)
-library(biglm)
+library(ggcorrplot)
+source(here::here("R", "network_metrics.R"))
+source(here::here("R", "string_replacements.R"))
+source(here::here("R", "stability_decomposition.R"))
+source(here::here("R", "model_helpers.R"))
 ```
@@
 ```{r}
-tar_read(sim_rho)
+tar_load(sim_prep)
+map(sim_prep$omega[1:5], length)
+```
+
+```{r}
+tar_load(sim_fw)
+colnames(sim_fw)
+summary(sim_fw$avg_int_strength)
+unique(sim_fw$Z)
+tar_read(p_cor)
+tar_read(p_prod_pop_stab)
+tar_read(p_stab_s_stress)
+
+sim_fw %>%
+  filter(env_stoch == .2, rho %in% c(0, .4, 1), productivity == 5) %>%
+  ggplot(aes(x = richness, y = cpe_env, color = as.factor(rho))) +
+  geom_point() +
+  labs(x = "Species richness", y = "Comp. effects (Environment)") +
+  theme_bw()
+
+sim_fw %>%
+  filter(env_stoch == .2, rho == 0) %>%
+  ggplot(aes(x = as.factor(productivity), y = pop_stab, color = as.factor(Z))) +
+  geom_boxplot() +
+  labs(x = "Productivity", y = "Population stability") +
+  theme_bw()
+
+sim_fw %>%
+  filter(env_stoch == .2, rho == 0) %>%
+  ggplot(aes(x = as.factor(productivity), y = stab_com, color = as.factor(Z))) +
+  geom_boxplot() +
+  labs(x = "Productivity", y = "Population stability") +
+  theme_bw()
+
+sim_fw %>%
+  filter(env_stoch == .2, rho == 0) %>%
+  ggplot(aes(x = as.factor(Z), y = pop_stab, color = as.factor(productivity))) +
+  geom_boxplot() +
+  labs(x = "Productivity", y = "Population stability") +
+  theme_bw()
+
+sim_fw %>%
+  filter(env_stoch == .2, rho == 0) %>%
+  ggplot(aes(x = as.factor(Z), y = avg_int_strength, color = as.factor(productivity))) +
+  geom_boxplot() +
+  labs(x = "Productivity", y = "Population stability") +
+  theme_bw()
+
+sim_fw %>%
+  filter(env_stoch == .2, rho == 0, bm_total > 10^-5) %>%
+  ggplot(aes(x = as.factor(Z), y = bm_total, color = as.factor(productivity))) +
+  geom_boxplot() +
+  labs(x = "Productivity", y = "Population stability") +
+  theme_bw()
+
+sim_fw %>%
+  filter(env_stoch == .2, rho == 0) %>%
+  ggplot(aes(x = as.factor(Z), y = evenness_sae, color = as.factor(productivity))) +
+  geom_boxplot() +
+  labs(x = "Productivity", y = "Population stability") +
+  theme_bw()
+
+sim_fw %>%
+  filter(env_stoch == .2, rho == 0) %>%
+  ggplot(aes(x = as.factor(productivity), y = cpe_int, color = as.factor(Z))) +
+  geom_boxplot() +
+  labs(x = "Productivity", y = "Population stability") +
+  theme_bw()
+```
+
+```{r}
+var_fw_struct <- c("richness", "ct_alive", "Z")
+var_fw_emergent_struct <- c("max_tlvl", "w_avg_tlvl", "avg_omnivory")
+var_fw_flux <- c("avg_int_strength")
+var_stab <- c("async", "stab_com", "pop_stab")
+```
+
+```{r, eval = FALSE}
+#colnames(simZ)
+pairs(sim_fw %>%
+  filter(env_stoch == .2) %>%
+  select(c(var_fw_struct, var_fw_emergent_struct, var_fw_flux, stab_pop)))
+```
+
+```{r}
+tar_load(sim_sp)
+
+sim_sp %>%
+  filter(env_stoch == .2, rho == 1, Z == 10) %>%
+  ggplot(aes(x = tlvl, y = log(cv_sp))) +
+  geom_point() +
+  geom_smooth()
+```
+
+```{r}
+
+tar_read(sem_coeff) %>%
+  filter(abs(Std.Estimate) > .1)
+tar_read(sem_rsquared)
+tar_load(sem_collinearity)
+sem_collinearity %>%
+  print(., n = 38)
+```
+
+```{r}
+tar_load(sem_model_list)
+tar_load(sim_fw_df)
+sem_boot <- bootEff(sem_model_list,
+  R = 10, seed = 13, parallel = "no")
+
+sem_eff <- semEff(sem_model_list, ci.type = "perc", R = 10, seed = 13, parallel = "no")
+```
+
+```{r}
+mod_tot_scaled <- lm(stab_com ~
+  richness + productivity + rho + env_stoch +
+  ct_alive + avg_int_strength + avg_omnivory + w_avg_tlvl +
+  richness : productivity +
+  richness : rho +
+  richness : env_stoch +
+  richness : ct_alive +
+  richness : avg_int_strength +
+  richness : avg_omnivory +
+  richness : w_avg_tlvl +
+  richness : productivity : ct_alive +
+  richness : productivity : w_avg_tlvl +
+  richness : productivity : avg_int_strength +
+  richness : productivity : avg_omnivory +
+  richness : rho : ct_alive +
+  richness : rho : w_avg_tlvl +
+  richness : rho : avg_int_strength +
+  richness : rho : avg_omnivory +
+  richness : env_stoch : ct_alive +
+  richness : env_stoch : w_avg_tlvl +
+  richness : env_stoch : avg_int_strength +
+  richness : env_stoch : avg_omnivory,
+sim_fw %>%
+  mutate(across(c("stab_com", "richness", "productivity", "rho", "env_stoch", "ct_alive", "avg_int_strength", "avg_omnivory", "w_avg_tlvl"), scale))
+
+  )
+summary(mod_tot)
+predict(mod_tot)
+summary(sim_fw$avg_int_strength)
+summary(sim_fw$w_avg_tlvl)
+summary(sim_fw$avg_omnivory)
+
+mod_tot <- lm(stab_com ~
+  richness + productivity + rho + env_stoch +
+  ct_alive + avg_int_strength + avg_omnivory + w_avg_tlvl +
+  richness * productivity +
+  richness * rho +
+  richness * env_stoch +
+  richness * ct_alive +
+  richness * avg_int_strength +
+  richness * avg_omnivory +
+  richness * w_avg_tlvl +
+  richness * productivity * ct_alive +
+  richness * productivity * w_avg_tlvl +
+  richness * productivity * avg_int_strength +
+  richness * productivity * avg_omnivory +
+  richness * rho * ct_alive +
+  richness * rho * w_avg_tlvl +
+  richness * rho * avg_int_strength +
+  richness * rho * avg_omnivory +
+  richness * env_stoch * ct_alive +
+  richness * env_stoch * w_avg_tlvl +
+  richness * env_stoch * avg_int_strength +
+  richness * env_stoch * avg_omnivory,
+mutate(sim_fw, across(c(stab_com, richness), log)) #, richness
+  )
+check_collinearity(lm(stab_com ~ richness + productivity + rho + env_stoch +
+  ct_alive + avg_int_strength + avg_omnivory + w_avg_tlvl, sim_fw))
+plot(mod_tot)
+
+pred_data <- list(
+  richness = log(seq(5, 30, 1)),
+  ct_alive = c(.05, .10, .30),
+  rho = c(0, .5, 1),
+  avg_int_strength = c(.02, .04, .1),
+  env_stoch = c(.2, .6),
+  w_avg_tlvl = c(1.5, 1.7, 2),
+  avg_omnivory = c(.01, .05, .1),
+  productivity = c(5, 30),
+  Z = 10
+  ) %>% expand.grid()
+pred_data$stab_com <- predict(mod_tot, newdata = pred_data)
+
+```
+
+```{r}
+pred_data %>%
+  filter(
+    productivity == 5,
+    ct_alive %in% c(.1, .3),
+    rho %in% c(0, 1),
+    avg_int_strength %in% c(.02, .1),
+    avg_omnivory == .05,
+    w_avg_tlvl == 1.7) %>%
+  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
+  geom_line() +
+  facet_grid(cols = vars(env_stoch), rows = vars(rho))
+
+pred_data %>%
+  filter(
+    rho == 0,
+    ct_alive %in% c(.1, .3),
+    avg_int_strength %in% c(.02, .1),
+    avg_omnivory == .05,
+    w_avg_tlvl == 1.7) %>%
+  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
+  geom_line() +
+  facet_grid(cols = vars(env_stoch), rows = vars(productivity), labeller = label_both)
+
+pred_data %>%
+  filter(
+    env_stoch == 0.2,
+    ct_alive %in% c(.1, .3),
+    rho %in% c(0, 1),
+    avg_int_strength %in% c(.02, .1),
+    avg_omnivory == .05,
+    w_avg_tlvl == 1.7) %>%
+  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
+  geom_line() +
+  facet_grid(cols = vars(rho), rows = vars(productivity), labeller = label_both) +
+  theme_bw() +
+  labs(
+    x = "Species richness",
+    y = "Community stability",
+    linewidth = "Avg. Int",
+    color = "Connectance"
+  )
+```
+
+```{r}
+pred_data %>%
+  filter(
+    env_stoch == 0.6,
+    ct_alive %in% c(.1, .3),
+    rho %in% c(0, 1),
+    avg_int_strength %in% c(.02, .1),
+    avg_omnivory == .05,
+    w_avg_tlvl == 1.7) %>%
+  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
+  geom_line() +
+  facet_grid(cols = vars(rho), rows = vars(productivity)) +
+  theme_bw()
 ```

### 2023-07-11 report/cs_analysis.Rmd
Redo analysis with new simulations

@@
 
-Global change and their effects constitute major treats to ecosystem stability.
-Among them, global change is predicted to lead dramatically more variable
-environments [@pachauri_climate_2015]. This new threat adds to current
-eutrophication in many ecosystems [@maure_globally_2021, add ref], which is
-known to dramatically impair ecosystem functioning. Understanding how
-environmental variability and eutrophication will alter ecosystem stability is
-then a timely question.
+Global change and its simultaneous increasing stressors constitute a major
+threat to biodiversity and ecosystem functioning [@pachauri_climate_2015;
+@simmons_refocusing_2021]. Among them, climate change is predicted to lead
+dramatically more variable environments [@pachauri_climate_2015], adding to
+other persistent stressors such as eutrophication [@maure_globally_2021, add
+ref]. Understanding how environmental variability and eutrophication will
+affects ecosystem stability is then a timely question.
 
@@
 @eschenbrenner_diversity_nodate], and we know very little how food-web structure
-affects the relationships between species richness and temporal stability.
+affects the relationships between species richness and temporal stability in
+complex food-webs.
 
@@
 ```
+
+\pagebreak
 
@@
   - No predator interference
-  - Enrichment: K = 1 or 20
+  - Enrichment: K = 5 to 30
   - Standardized carrying capacity (Remove the effect of species richness on
@@
 - C: .02 to .3
-- K: 1 and 20
+- K: 1 and 30
 - $\rho$: 0 to 1
+- $\sigma_e$: from 0.2 to 0.6
 - Z: 5 to 1000
-
-```{r}
-tar_load(simZ)
-tar_load(sim_rho)
-tar_load(sim_rho_scaled)
-```
-
-```{r}
-cor_enrich <- cor(simZ %>%
-    filter(productivity == "enrichment") %>%
-    select(c(S, richness, ct, Z, ct_alive, total_biomass, avg_max_int_alive,
-        sd_max_int_alive, cv_max_int_alive,
-        gini_max_int_alive,
-        w_avg_tlvl_alive, max_tlvl_alive, rho, env_stoch, stab_com, avg_cv_sp,
-        sync)) %>% na.omit(),
-    method = "spearman")
-cor_basic <- cor(simZ %>%
-    filter(productivity == "basic") %>%
-select(c(S, richness, ct, Z, ct_alive, total_biomass, avg_max_int_alive,
-        sd_max_int_alive, cv_max_int_alive,
-        gini_max_int_alive,
-        w_avg_tlvl_alive, max_tlvl_alive, rho, env_stoch, stab_com, avg_cv_sp,
-        sync)) %>% na.omit(),
-    method = "spearman")
-p_cor_basic <- ggcorrplot(cor_basic, type = "lower",
-   lab = TRUE)
-p_cor_enrich <- ggcorrplot(cor_enrich, type = "lower",
-   lab = TRUE)
-p_cor <- plot_grid(
-  p_cor_basic,
-  p_cor_enrich,
-  ncol = 2,
-  labels = "auto"
-)
-ggsave(here("report", "figures", "p_cor.pdf"),
-  plot = p_cor,
-  device = NULL,
-  path = NULL,
-  scale = 3.0,
-  units = "mm",
-  width = 140,
-  height = 140 * .5,
-  dpi = 300,
-  limitsize = TRUE,
-  bg = NULL
-)
-```
 
@@
 ```{r, fig.cap=cor_cap}
-knitr::include_graphics(here::here("report", "figures", "p_cor.pdf"))
+tar_read(p_cor)
 ```
@@
 
-```{r}
-sim_rich_prod <- simZ %>%
-  filter(
-    env_stoch == .5
-  )
-```
-
-```{r}
-p_sim_rich_prod <- sim_rich_prod %>%
-  mutate(stab_pop = 1/ avg_cv_sp) %>%
-  pivot_longer(
-    c(stab_com, stab_pop, sync),
-    names_to = "metric",
-    values_to = "stab") %>%
-  mutate(
-    metric = var_replacement()[metric],
-    rho = rho_replacement()[as.character(rho)]
-  ) %>%
-  ggplot(aes(x = richness, y = stab, color = factor(productivity))) +
-  geom_point(alpha = .1, shape = 20) +
-  geom_smooth() +
-  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
-  labs(
-    color = "Productivity",
-    x = "Species richness",
-    y = "Stability component"
-  ) +
-  scale_x_continuous(
-    sec.axis = sec_axis(~ . ,
-      name = "Response diversity",
-      breaks = NULL,
-      labels = NULL)
-  )
-ggsave(
-  filename = here::here("report", "figures", "stability_rich.pdf"),
-  p_sim_rich_prod,
-  scale = 1.8,
-  width = 88,
-  height = 88 * .6,
-  units = "mm"
-)
-```
-
-```{r}
-p_sim_rich_prod_fw_only <- sim_rich_prod %>%
-  filter(ct_alive != 0, avg_max_int_alive != 0) %>%
-  mutate(stab_pop = 1/ avg_cv_sp) %>%
-  pivot_longer(
-    c(stab_com, stab_pop, sync),
-    names_to = "metric",
-    values_to = "stab") %>%
-  mutate(
-    metric = var_replacement()[metric],
-    rho = rho_replacement()[as.character(rho)]
-  ) %>%
-  ggplot(aes(x = log(richness), y = log(stab), color = factor(productivity))) +
-  geom_point(alpha = .1, shape = 20) +
-  geom_smooth(method = "lm") +
-  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
-  labs(
-    color = "Productivity",
-    x = "Species richness",
-    y = "Stability component"
-  ) +
-  scale_x_continuous(
-    sec.axis = sec_axis(~ . ,
-      name = "Response diversity",
-      breaks = NULL,
-      labels = NULL)
-  )
-ggsave(
-  filename = here("report", "figures", "p_sim_rich_prod_fw_only.pdf"),
-  p_sim_rich_prod_fw_only,
-  scale = 1.8,
-  width = 88,
-  height = 88 * .6,
-  units = "mm"
-)
-```
-
-```{r}
-p_sim_rich_prod_p_only <- sim_rich_prod %>%
-  filter(ct_alive == 0) %>%
-  mutate(stab_pop = 1/ avg_cv_sp) %>%
-  pivot_longer(
-    c(stab_com, stab_pop, sync),
-    names_to = "metric",
-    values_to = "stab") %>%
-  mutate(
-    metric = var_replacement()[metric],
-    rho = rho_replacement()[as.character(rho)]
-  ) %>%
-  ggplot(aes(x = richness, y = stab, color = factor(productivity))) +
-  geom_point(alpha = .1, shape = 20) +
-  geom_smooth() +
-  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
-  labs(
-    color = "Productivity",
-    x = "Species richness",
-    y = "Stability component"
-  ) +
-  scale_x_continuous(
-    sec.axis = sec_axis(~ .,
-      name = "Response diversity",
-      breaks = NULL,
-      labels = NULL)
-  )
-ggsave(
-  filename = here("report", "figures", "p_sim_rich_prod_p_only.pdf"),
-  p_sim_rich_prod_p_only,
-  scale = 1.8,
-  width = 88,
-  height = 88 * .6,
-  units = "mm"
-)
-```
-
-```{r, fig.cap = "Food-Web only."}
-knitr::include_graphics(here("report", "figures", "p_sim_rich_prod_fw_only.pdf"))
-```
-
-```{r, fig.cap = "Primary producers only."}
-knitr::include_graphics(here::here("report", "figures", "p_sim_rich_prod_p_only.pdf"))
+```{r, fig.cap = "Effect of stressors on community stability."}
+tar_read(p_stab_s_stress)
 ```
@@
   diversity but synchrony increase with richness in basic environment
-
-```{r}
-simZ %>%
-  filter(rho == 1) %>%
-  mutate(stab_pop = 1/ avg_cv_sp) %>%
-  pivot_longer(
-    c(stab_com, stab_pop, sync, total_biomass),
-    names_to = "metric",
-    values_to = "stab") %>%
-  ggplot(aes(x = richness, y = stab, color = factor(env_stoch))) +
-  geom_point() +
-  facet_grid(rows = vars(metric), cols = vars(productivity), scales = "free_y") +
-  labs(
-    color = "Evironmental stochasticity",
-    x = "Species richness",
-    y = "Stability component"
-  )
-```
-
-# Food-web structure and interaction strength drive stability
-
-```{r}
-compute_rotated_pca <- function(.data = NULL, naxis = 2) {
-  .data <- na.omit(.data)
-  pca <- ade4::dudi.pca(as.data.frame(.data),
-    scannf = FALSE, nf = naxis, center = TRUE, scale = TRUE
-  )
-  pca_rotated <- psych::principal(.data,
-    rotate = "varimax", nfactors = naxis,
-    scores = TRUE
-  )
-
-  return(list(normal = pca, rotated = pca_rotated))
-}
-```
-
-```{r}
-sim_sem <- simZ %>%
-  filter(ct_alive != 0, env_stoch == 0.5, rho == 0) %>%
-  mutate(across(c(async, stab_pop, stab_com, richness, ct_alive, sd_max_int_alive, avg_max_int_alive), log, , .names = "log_{.col}")) %>%
-  mutate(
-    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
-    log1_sd_max_int_alive = log(sd_max_int_alive + 1),
-    productivity_f = factor(productivity)
-    ) %>%
-  as.data.frame()
-scaled_sim_sem <- sim_sem %>%
-  mutate(across(where(is.double), ~scale(.x)[,1]))
-```
-
-```{r}
-var_fw_struct <- c("richness", "ct_alive", "Z")
-var_fw_emergent_struct <- c("max_tlvl_alive", "w_avg_tlvl_alive")
-var_fw_flux <- c("gini_max_int_alive", "avg_max_int_alive", "sd_max_int_alive",
-  "cv_max_int_alive")
-var_stab <- c("async", "stab_com", "stab_pop")
-```
-
-```{r}
-#colnames(simZ)
-pairs(sim_sem %>%
-  filter(env_stoch == .5) %>%
-  select(c(var_fw_struct, var_fw_emergent_struct, var_fw_flux, stab_pop)))
-```
-
-```{r, eval = FALSE}
-performance::check_collinearity(lm(w_avg_tlvl_alive ~ max_tlvl_alive,sim_sem))
-performance::check_collinearity(lm(w_avg_tlvl_alive ~ ct_alive + richness,sim_sem))
-performance::check_collinearity(lm(w_avg_tlvl_alive ~ ct_alive + richness,sim_sem))
-performance::check_collinearity(lm(avg_max_int_alive ~ w_avg_tlvl_alive + ct_alive + richness,sim_sem))
-performance::check_collinearity(lm(avg_max_int_alive ~ max_tlvl_alive + ct_alive,sim_sem))
-performance::check_collinearity(lm(stab_com ~ log_richness + log1_avg_max_int_alive + log1_sd_max_int_alive + w_avg_tlvl_alive + ct_alive,sim_sem))
-performance::check_collinearity(lm(stab_com ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive,sim_sem))
-```
-
-```{r}
-sem_list_basic <- list(
-  w_avg_tlvl_alive = lm(w_avg_tlvl_alive ~ richness + ct_alive, sim_sem),
-  sd_max_int_alive = lm(sd_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive, sim_sem),
-  avg_max_int_alive = lm(avg_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive, sim_sem),
-  log_async = lm(log_async ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem),
-  log_stab_pop = lm(log_stab_pop ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem),
-  log_stab_com = lm(log_stab_com ~ log_async + log_stab_pop, sim_sem)
-)
-sem_basic <- as.psem(sem_list_basic)
-```
-
-```{r}
-ti <- summary(sem_basic)$coefficients[, c(1, 2, 8, 9)]
-colnames(ti)[4] <- "Signif"
-ti %>%
-  mutate(
-    Response = var_replacement()[Response],
-    Predictor = var_replacement()[Predictor]
-  ) %>%
-  kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
-  collapse_rows(1, valign = "middle") %>%
-  kable_styling()
-```
-
-```{r, eval = FALSE}
-ti <- map_dfr(setNames(sem_list_basic, names(sem_list_basic)),
-  performance::check_collinearity,
-  .id = "response") %>%
-  as_tibble
-ti %>%
-  mutate(
-    response = var_replacement()[response],
-    Term = var_replacement()[Term]
-  ) %>%
-  kable(caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
-  kable_styling()
-```
-
-```{r, eval = FALSE}
-map_dfr(sem_list_basic, rsquared) %>%
-  mutate(Response = var_replacement()[Response]) %>%
-  select(Response, R.squared) %>%
-  kable(caption = "Rsquared for the Structural Equation Model.") %>%
-  kable_styling()
-```
 

### 2023-07-11 R/string_replacements.R

@@ -3,24 +3,34 @@ var_replacement <- function() {
     stab_com = "Community stability",
     log_stab_com = "Community stability",
     stab_pop = "Population stability",
+    pop_stab = "Population stability",
     log_stab_pop = "Population stability",
     log_avg_cv_sp = "Population variability",
     sync = "Synchrony",
     log_sync = "Synchrony",
     log_async = "Asynchrony",
     async = "Asynchrony",
+    cpe = "Compensatory effect",
+    cpe_int = "Comp. effect (Interaction)",
+    cpe_env = "Comp. effect (Environment)",
+    sae_total = "Stat. Avg. effect",
+    sae_even = "Stat. Avg. effect (Even)",
+    evenness_sae = "Stat. Avg. effect (Evenness)",
     log1_avg_max_int_alive = "Interaction strength",
     avg_max_int_alive = "Avg interaction strength",
+    avg_int_strength = "Avg interaction",
     sd_max_int_alive = "SD interaction strength",
     w_avg_tlvl_alive = "Avg trophic level",
     ct_alive = "Connectance",
+    max_tlvl = "Max. trophic level",
+    w_avg_tlvl = "Avg. trophic level",
+    avg_omnivory = "Avg. omnivory",
     log_richness = "Richness",
     richness = "Richness",
     rho = "Env Corr",
     productivityenrichment = "Enrichment",
     env_stoch = "Env variance",
-    sae_total = "Stat Avg eff",
-    cpe = "Compensatory eff"
+    Z = "PPMR"
 
   )
 }
@@ -30,4 +40,10 @@ rho_replacement <- function() {
     `0.5` = "Medium",
     `1` = "No"
   )
+}
+
+get_rev_vec_name_val <- function(x = NULL) {
+  y <- names(x)
+  names(y) <- x
+  return(y)
 }

### 2023-08-07 _targets.Rmd
test

@@
 
-```{targets raw_sim}
+```{r targets raw_sim}
 list(
-  tar_target(var_param_sim, c("rep", "productivity", "S", "ct", "rho", "env_stoch", "Z")),
-  tar_target(sim_files_out, list.files(here::here("res", "simCSZenrich3/simCSZenrich3"))),
-  tar_target(sim_files_ts,
-    list.files(here::here("res", "simCSZenrich3")) %>% #
-      .[str_detect(., "_ts")]
-    ),
-  tar_target(sim_param,
-    map_dfr(sim_files_out,
-      function (x) {
-        open_dataset(here::here("res", "simCSZenrich3/simCSZenrich3", x),
-          format = "arrow") %>%
-        collect() %>%
-        select(all_of(var_param_sim))
-      })
-    ),
-  # Because I had to remove one ts that failed...
-  tar_target(sim_param_ts,
-    map_dfr(str_remove(sim_files_ts, "_ts")[str_remove(sim_files_ts, "_ts") %in% sim_files_out],
-      function (x) {
-        open_dataset(here::here("res", "simCSZenrich3/simCSZenrich3", x),
-          format = "arrow") %>%
-        collect() %>%
-        select(all_of(var_param_sim))
-      })
-  ),
-  tar_target(sim_prep,
-        open_dataset(here::here("res", "simCSZenrich3/simCSZenrich3", sim_files_out),
-          format = "arrow") %>%
-        collect() %>%
-        # Transform back interaction strength into matrices
-        mutate(across(where(is.list), as.list)) %>%
-        filter(!is.na(richness)) %>%
-        mutate(across(c(int_strength, max_int),
-            ~map2(.x, S,
-              function(y, rich) {
-                matrix(y, nrow = rich)
-              }
 )
-          )
-          ) %>%
-        # Get matrix of alive species
-        mutate(max_int_alive  = map2(max_int, bm_sp,
-            function(mat, bm) {
-              mask <- bm > 10^-6
-              mat[mask, mask, drop = FALSE]
-            }
-          )
-        ) %>%
-        select(-max_int),
-        pattern = sim_files_out
-      ),
-  tar_target(sim_net,
-    sim_prep %>%
-      mutate(
-        persistence = richness / S,
-        async = 1 / sync,
-        stab_pop = 1 / avg_cv_sp,
-        ct_alive = map_dbl(max_int_alive,
-          ~ifelse(sum(.x) == 0, 0,
-            sum(.x > 0) / ((ncol(.x))^2))),
-        max_max_int_alive = map_dbl(max_int_alive,
-          ~ifelse(length(.x[.x > 0]) == 0, 0, max(.x[.x > 0]))
-          ),
-        avg_max_int_alive = map_dbl(max_int_alive,
-          ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
-          ),
-        sd_max_int_alive = map_dbl(max_int_alive,
-          ~ifelse(length(.x[.x > 0]) <= 1, 0, sd(.x[.x > 0]))
-          ),
-        cv_max_int_alive = sd_max_int_alive / avg_max_int_alive,
-        inv_sd_max_int_alive = 1 / sd_max_int_alive,
-        gini_max_int_alive = map_dbl(max_int_alive,
-          ~ifelse(length(.x[.x > 0]) == 0, 0, gini(.x[.x > 0]))),
-        avg_omnivory = map_dbl(omnivory, mean),
-        disconnected_prod = map_lgl(max_int_alive,
-          ~any(colSums(.x) == 0 & rowSums(.x) == 0))
-        ) %>%
-    select(!where(is.list))
-  ),
-  tar_target(sim_ts2_null,
-    open_dataset(here::here("res", "simCSZenrich3", sim_files_ts),
-          format = "arrow") %>%
-        collect() %>%
-        # Transform back interaction strength into matrices
-        mutate(across(where(is.list), as.list)) %>%
-        mutate(is_null = map_lgl(species, is.null)) %>%
-        select(is_null),
-        pattern = sim_files_ts
-        ),
-  tar_target(sim_ts2,
-    open_dataset(here::here("res", "simCSZenrich3", sim_files_ts),
-          format = "arrow") %>%
-        collect() %>%
-        # Transform back interaction strength into matrices
-        mutate(across(where(is.list), as.list)) %>%
-        filter(!map_lgl(species, is.null)) %>%
-        mutate(
-          stoch_d = map2(species, stoch, function(bm, d_stoch) {
-            .1 * bm * exp(d_stoch)
-            }),
-          species = map(species, ~matrix(.x, nrow = 100)),
-          stoch = map(stoch, ~matrix(.x, nrow = 100)),
-          stoch_d = map(stoch_d, ~matrix(.x, nrow = 100)),
-          cpe = map_dbl(species, compensatory_effect),
-          cpe_env = map_dbl(stoch_d, compensatory_effect),
-          cpe_int = cpe / cpe_env,
-          stab_com = map_dbl(species, community_stability),
-          pop_stab = map_dbl(species, population_stability),
-          bm_sp = map(species, ~colMeans(.x)),
-          bm_total = map_dbl(bm_sp, ~sum(.x)),
-          sd_sp = map(species, ~apply(.x, 2, sd)),
-          sum_sd_sp = map_dbl(sd_sp, ~sum(.x)),
-          async = map_dbl(species, asynchrony),
-          sae = map(species, statistical_averaging_effect),
-          sae_total = map_dbl(sae, ~.x["total"]),
-          sae_even = map_dbl(sae, ~.x["even"]),
-          evenness_sae = map_dbl(sae, ~.x["eveness"])
-        ) %>%
-        select(-species, -stoch_d, -stoch),
-        pattern = sim_files_ts
-  ),
-  tar_target(sim_stab, cbind(sim_param[!sim_ts2_null$is_null,], sim_ts2) %>% as_tibble()),
-  tar_target(sim, left_join(sim_net %>% select(-async, -stab_com), sim_stab, by = var_param_sim)),
-  tar_target(sim_fw,
-    sim %>%
-      filter(
-        max_tlvl > 1,
-        sum_sd_sp != Inf,
-        bm_total > 10^-5,
-        !disconnected_prod
-        )
-   ),
-   tar_target(sim_fw_df, as.data.frame(sim_fw))
-  )
-```
 
-## Species bm, sd and tlvl
-
-```{targets sim_sp, tar_simple = TRUE}
-sim_stab %>%
-  select(all_of(c(var_param_sim, "sd_sp", "bm_sp"))) %>%
-  left_join(
-    sim_prep %>%
-      select(all_of(c(var_param_sim, "tlvl", "alive_species")))
-  ) %>%
-  mutate(
-    sd_sp = map2(sd_sp, alive_species, ~.x[.y]),
-    bm_sp = map2(bm_sp, alive_species, ~.x[.y]),
-    cv_sp = map2(sd_sp, bm_sp, ~.x / .y),
-    tlvl_bm_sd_sp = pmap(list(tlvl, bm_sp, sd_sp, cv_sp, alive_species),
-      function(x, y, z, a, b) {
-        rbind.data.frame(list(
-        species = b,
-            tlvl = x,
-            bm_sp = y,
-            sd_sp = z,
-            cv_sp = a
-        )
-        )
-      }),
-    check = map_lgl(tlvl_bm_sd_sp, ~is.null(nrow(.x)))
-  ) %>%
-  filter(!check) %>%
-  select(all_of(c(var_param_sim, "tlvl_bm_sd_sp"))) %>%
-  unnest(c(tlvl_bm_sd_sp))
 ```

### 2023-08-07 job/csh_allo_d_stanage_array.sh

@@ -1,0 +1,29 @@
+#!/bin/bash
+#
+#SBATCH --job-name=allo_d
+# Set number of iteration
+#SBATCH --array=1-54%20
+# Amount of RAM requested per job
+#SBATCH --mem=64G
+# Nb of threads requested per job (smp = shared memory)
+#SBATCH --cpus-per-task=15
+#SBATCH --ntasks=1
+
+# Replace by the path to the folder where your script lives if necessary
+DIR_ENV=/users/${USER}/xStressorsStabBEFW
+DIR_SCRIPT=scripts
+
+# Load modules
+#module load apps/julia/1.8.5/binary
+
+# Put 1.8.5
+JULIA="/users/bi1ahd/.juliaup/bin/julialauncher +release"
+
+STEPSIZE=4000
+
+START=$((1 + ${STEPSIZE} * (${SLURM_ARRAY_TASK_ID} - 1)))
+END=$((${STEPSIZE} * ${SLURM_ARRAY_TASK_ID}))
+
+echo "Starting task from ${START} to ${END}"
+
+cd ${DIR_ENV} && ${JULIA} --project=${DIR_ENV} ${DIR_ENV}/${DIR_SCRIPT}/ct_S_h_d_allometric_array.jl ${START} ${END}

### 2023-08-07 job/csh_allo_d_stanage_array_fixed.sh

@@ -1,0 +1,31 @@
+#!/bin/bash
+#
+#SBATCH --job-name=allo_d_completion
+# Set number of iteration
+#SBATCH --array=1-36%20
+# Amount of RAM requested per job
+#SBATCH --mem=64G
+# Nb of threads requested per job (smp = shared memory)
+#SBATCH --cpus-per-task=20
+#SBATCH --ntasks=1
+# Request
+#SBATCH --time=2-00:00:00
+
+# Replace by the path to the folder where your script lives if necessary
+DIR_ENV=/users/${USER}/xStressorsStabBEFW
+DIR_SCRIPT=scripts
+
+# Load modules
+#module load apps/julia/1.8.5/binary
+
+# Put 1.8.5
+JULIA="/users/bi1ahd/.juliaup/bin/julialauncher +release"
+
+STEPSIZE=2000
+
+START=$((1 + ${STEPSIZE} * (${SLURM_ARRAY_TASK_ID} - 1)))
+END=$((${STEPSIZE} * ${SLURM_ARRAY_TASK_ID}))
+
+echo "Starting task from ${START} to ${END}"
+
+cd ${DIR_ENV} && ${JULIA} --project=${DIR_ENV} ${DIR_ENV}/${DIR_SCRIPT}/ct_S_h_d_allometric_array.jl ${START} ${END}

### 2023-08-07 scripts/param_comb_ct_S_h_d_allometric.jl

@@ -7,6 +7,8 @@ param.sigma = replace(param.sigma, 0.1 => 0.5)
 param.sigma = replace(param.sigma, 0.3 => 1)
 param.sigma = replace(param.sigma, 0.6 => 1.5)
 
+param = filter(:K => k -> k == 5, param)
+
 unique(param.sigma)
 
 param.sim_id = 1:nrow(param)

### 2023-08-07 scripts/param_comb_ct_S_h_d_allometric2.jl

@@ -1,0 +1,139 @@
+using CSV, StatsBase, DataFrames, Arrow, EcologicalNetworksDynamics
+
+nrep = 50
+sigma = [0.0, 0.1, 0.3, 0.6]#.1:.2:0.6
+Z = [1, 25, 50, 100]
+ρ = 0:.25:1
+K = [10]
+h = [2.0, 3.0]
+S = [10, 20, 40, 60]
+C = 0.02:.02:.32
+
+########################
+#  Generate Food-webs  #
+########################
+
+rep = 1:1
+names = (:rep, :richness, :connectance)
+param = map(p -> (;Dict(k => v for (k, v) in zip(names, p))...),
+            Iterators.product(rep, S, C)
+           )[:]
+
+# # Filter impossible combination of C/S
+# limitCS = (
+           # S = S,
+           # Cmin = round.([(i - 1)/ i^2 + .01 for i in S], digits = 2),
+           # Cmax = [.32, .31, .24, .15, .09, .07]
+          # )
+# # Select good combinations
+# goodCSparam_v = [
+                 # findall(x ->
+                         # (
+                          # x.connectance >= limitCS.Cmin[i] &&
+                          # x.connectance <= limitCS.Cmax[i]) &&
+                         # x.richness == limitCS.S[i],
+                         # param
+                        # )
+                 # for i in 1:length(limitCS.S)
+                # ]
+# goodCSparam_idxs = reduce(vcat, goodCSparam_v)
+# param = param[goodCSparam_idxs]
+
+fw_test = map(p -> try
+                  FoodWeb(nichemodel, p.richness, C = p.connectance,
+                          Z = 100, tol_C = .02,
+                          check_cycle = true,
+                          check_disconnected = true)
+              catch
+                  missing
+              end,
+              param
+             )
+
+
+param[.! ismissing.(fw_test)]
+fw_test[.! ismissing.(fw_test)]
+
+
+fw_test2 = map(p -> try
+                  FoodWeb(nichemodel, p.richness, C = p.connectance,
+                          Z = 100, tol_C = .02,
+                          check_cycle = true,
+                          check_disconnected = true)
+              catch
+                  missing
+              end,
+              param[.! ismissing.(fw_test)]
+             )
+
+param2 = param[.! ismissing.(fw_test2)]
+
+
+# Try to get same number of sampling per richness
[…]

### 2023-08-07 _targets.Rmd
take sim_fw from upstream

@@
 list(
+tar_target(sim_fw_file, here::here("data", "sim_fw"), format = "file"),
+  tar_target(sim_fw, readRDS(sim_fw_file)),
+  tar_target(sim_fw_df, as.data.frame(sim_fw)),
+  tar_target(sim_fw_cons, readRDS(here::here("data", "sim_fw_cons"))),
+  tar_target(sim_fw_cons_df, as.data.frame(sim_fw_cons))
   )
+```
 
-```
+>>>>>>> Stashed changes
 
@@
     list(
-      ct_alive = lm(ct_alive ~ ct + S, sim_fw_df),
-      richness = lm(richness ~ ct + S, sim_fw_df),
-      #  max_tlvl = lm(max_tlvl ~ ct + S + Z + productivity, sim_fw_df),
-      w_avg_tlvl = lm(w_avg_tlvl ~ richness + ct_alive + productivity, sim_fw_df),
-      avg_omnivory = lm(avg_omnivory ~ w_avg_tlvl + ct_alive + richness + productivity, sim_fw_df),
-      avg_int_strength = lm(avg_int_strength ~ w_avg_tlvl + ct_alive + richness + productivity, sim_fw_df),
-      pop_stab = lm(pop_stab ~ Z + richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + env_stoch + productivity, sim_fw_df),
+      #ct_alive = lm(ct_alive ~ ct + S, sim_fw_df),
+      #richness = lm(richness ~ ct + S, sim_fw_df),
+      #  max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_df),
+      w_avg_tlvl = lm(w_avg_tlvl ~ richness + ct_alive, sim_fw_df),
+      avg_omnivory = lm(avg_omnivory ~ w_avg_tlvl + ct_alive + richness, sim_fw_df),
+      avg_int_strength = lm(avg_int_strength ~ w_avg_tlvl + ct_alive + richness + h, sim_fw_df),
+      pop_stab = lm(pop_stab ~ Z + richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_df),
       evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive, sim_fw_df),
       sae_even = lm(sae_even ~ richness, sim_fw_df),
-      cpe_int = lm(cpe_int ~ richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + productivity, sim_fw_df),
+      cpe_int = lm(cpe_int ~ richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + h, sim_fw_df),
       cpe_env = lm(cpe_env ~ richness + rho, sim_fw_df)
@@
 list(
-  tar_target(p_stab_s_prod,
-    sim_fw %>%
-      filter(productivity %in% c(5, 30), rho == 0, env_stoch == .2) %>%
-      ggplot(aes(x = richness, y = stab_com, color = as.factor(productivity))) +
-      geom_point() +
-      geom_smooth() +
-      labs(x = "Species richness", y = "Community stability", color = "Productivity") +
-      theme_bw()),
+#  tar_target(p_stab_s_prod,
+#    sim_fw %>%
+#      filter(productivity %in% c(5, 30), rho == 0, env_stoch == .3) %>%
+#      ggplot(aes(x = richness, y = stab_com, color = as.factor(productivity))) +
+#      geom_point() +
+#      geom_smooth() +
+#      labs(x = "Species richness", y = "Community stability", color = "Productivity") +
+#      theme_bw()),
     tar_target(p_stab_s_env_stoch,
       sim_fw %>%
-        filter(env_stoch %in% c(.2, .6), rho == 0, productivity == 5) %>%
+        filter(env_stoch %in% c(.5, 1.5), rho == 0, productivity == 5) %>%
         ggplot(aes(x = richness, y = stab_com, color = as.factor(env_stoch))) +
@@
         sim_fw %>%
-          filter(rho %in% c(0, 1), productivity == 5, env_stoch == .2) %>%
+          filter(rho %in% c(0, 1), productivity == 5, env_stoch == .5) %>%
           ggplot(aes(x = richness, y = stab_com, color = as.factor(1 - rho))) +
@@
          plot_grid(
-           p_stab_s_prod,
+#           p_stab_s_prod,
            p_stab_s_env_stoch,
@@
 sim_fw %>%
-  filter(rho %in% c(0), productivity == 5, env_stoch == .2) %>%
+  filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
   pivot_longer(c(stab_com, async, sae_total, cpe,
@@
 sim_fw %>%
-  filter(rho %in% c(0), productivity == 5, env_stoch == .2) %>%
+  filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
   pivot_longer(c(richness, ct_alive, max_tlvl, avg_omnivory, w_avg_tlvl
@@
     sim_fw %>%
-      filter(rho %in% c(0), env_stoch == .2) %>%
+      filter(rho %in% c(0), env_stoch == .5) %>%
       pivot_longer(c(stab_com, pop_stab, async
@@
     sim_fw %>%
-      filter(rho %in% c(0), env_stoch == .2) %>%
+      filter(rho %in% c(0), env_stoch == .5) %>%
       pivot_longer(c(richness, ct_alive, w_avg_tlvl, max_tlvl
@@
     sim_fw %>%
-      filter(rho %in% c(0), productivity == 5, env_stoch == .2) %>%
+      filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
       pivot_longer(c(stab_com, async, sae_total, cpe,
@@
         avg_int_strength, avg_omnivory, max_tlvl,
-        rho, env_stoch, productivity,
+        w_avg_tlvl,
+        rho, env_stoch, h,
         stab_com, pop_stab, async, sae_total, sae_even,
@@
 ```{r, message = FALSE}
+library(targets)
 library(tidyverse)
@@
 ```{r}
-tar_load(sim_prep)
-map(sim_prep$omega[1:5], length)
-```
-
-```{r}
-tar_load(sim_fw)
+tar_load(c(sim_fw))
 colnames(sim_fw)
 summary(sim_fw$avg_int_strength)
-unique(sim_fw$Z)
+unique(sim_fw$env_stoch)
 tar_read(p_cor)
@@
 tar_read(p_stab_s_stress)
+tar_read(p_ct_stab)
+tar_read(p_rich_stab)
+
+summary(lm(cpe_env ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
+summary(lm(cpe_int ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
+summary(lm(cpe ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
+performance::check_collinearity(lm(cpe_env ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
+mod_cpe <- lm(cpe ~ avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + productivity + rho, sim_fw)
+summary(mod_cpe_int)
+performance::check_collinearity(mod_cpe_int)
+
+mod_cpe <- lm(log(cpe) ~ avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + productivity + rho, sim_fw)
+
+summary(mod_cpe)
+plot(mod_cpe)
+performance::check_collinearity(mod_cpe_int)
 
 sim_fw %>%
-  filter(env_stoch == .2, rho %in% c(0, .4, 1), productivity == 5) %>%
+  filter(env_stoch == 0.3, rho %in% c(0, .5, 1), productivity == 5) %>%
   ggplot(aes(x = richness, y = cpe_env, color = as.factor(rho))) +
@@
 sim_fw %>%
-  filter(env_stoch == .2, rho == 0) %>%
+  filter(env_stoch == .6, rho == 0) %>%
   ggplot(aes(x = as.factor(productivity), y = pop_stab, color = as.factor(Z))) +
@@
 sim_fw %>%
-  filter(env_stoch == .2, rho == 0) %>%
+  filter(env_stoch == .3, rho == 0) %>%
   ggplot(aes(x = as.factor(productivity), y = stab_com, color = as.factor(Z))) +
@@
 ```{r}
+unique(sim_fw$Z)
+```
+
+```{r}
+sim_fw %>%
+  filter(
+    rho %in% c(0), productivity == 5, env_stoch == .5
+    ) %>%
+  ggplot(aes(y = stab_pop, x = as.factor(Z))) +
+  geom_boxplot()
+```
+
+```{r}
+sim_fw %>%
+  filter(
+    rho %in% c(0), productivity == 5, env_stoch == .5,
+    Z == 500
+    ) %>%
+  pivot_longer(c(stab_com, async, sae_total, cpe,
+      sae_even, evenness_sae,
+      cpe_int, cpe_env, stab_pop
+      ), names_to = "async_decomp", values_to = "values") %>%
+  mutate(async_decomp = var_replacement()[async_decomp]) %>%
+  ggplot(aes(x = as.factor(richness), y = values)) +
+  geom_boxplot() +
+  labs(x = "Connectance", y = "Asynchrony component") +
+  facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
+  theme_bw()
+```
+
+```{r}
+tar_load(sim_fw_cons)
+sim_fw_cons %>%
+  filter(env_stoch == .6, rho == 1, Z == 100, productivity == 5) %>%
+  ggplot(aes(x = richness, y = stab_com, color = as.factor(h))) +
+  geom_point() +
+  geom_smooth()
+
+sim_fw %>%
+  filter(env_stoch == .6, rho == 0, Z == 100, productivity == 15) %>%
+  ggplot(aes(x = richness, y = async, color = as.factor(h))) +
+  geom_point() +
+  geom_smooth()
+
+sim_fw_cons %>%
+  filter(env_stoch == .6, rho == 0, Z == 100, productivity == 30) %>%
+  ggplot(aes(x = richness, y = pop_stab, color = as.factor(h))) +
+  geom_point() +
+  geom_smooth()
+```
+
+```{r}
+plot(richness ~ Z, sim_fw)
+```
+
+```{r}
 tar_load(sim_sp)
@@
 sim_sp %>%
-  filter(env_stoch == .2, rho == 1, Z == 10) %>%
+  filter(env_stoch == .3, rho == 1, Z == 100) %>%
   ggplot(aes(x = tlvl, y = log(cv_sp))) +
@@
 ```{r}
-
 tar_read(sem_coeff) %>%
-  filter(abs(Std.Estimate) > .1)
+  filter(abs(Std.Estimate) > .05)
 tar_read(sem_rsquared)
@@
 predict(mod_tot)
+summary(sim_fw$stab_com)
 summary(sim_fw$avg_int_strength)
@@
 ```{r}
-pred_data %>%
+p_pred_sr_ct_int <- pred_data %>%
   filter(
@@
   geom_line() +
-  facet_grid(cols = vars(env_stoch), rows = vars(rho))
+  facet_grid(cols = vars(env_stoch), rows = vars(rho), labeller = label_both) +
+  theme_bw()
+ggsave(
+  here("report", "figures", "p_pred_sr_ct_int.png"),
+  plot = p_pred_sr_ct_int,
+  scale = 2.4,
+  width = 88,
+  height = 88 * 1,
+  units = "mm"
+)
+p_pred_sr_omn <- pred_data %>%
+  filter(
+    productivity == 5,
+    ct_alive %in% c(.1),
+    rho %in% c(0, 1),
+    avg_int_strength %in% .02,
+    avg_omnivory %in% c(.01, .1),
+    w_avg_tlvl == 1.7) %>%
+  ggplot(aes(x=richness, y = stab_com, color = as.factor(avg_omnivory))) +
+  geom_line() +
+  facet_grid(cols = vars(env_stoch), rows = vars(rho), labeller = label_both) +
+  theme_bw()
+ggsave(
+  here("report", "figures", "p_pred_sr_omn.png"),
+  plot = p_pred_sr_omn,
+  scale = 2.4,
+  width = 88,
+  height = 88 * 1,
+  units = "mm"
+)
+
+p_pred_sr_avg_tlvl <- pred_data %>%
+  filter(
+    productivity == 5,
+    ct_alive %in% c(.1),
+    rho %in% c(0, 1),
+    avg_int_strength %in% .02,
+    avg_omnivory %in% c(.05),
+    w_avg_tlvl == c(1.5, 2)) %>%
+  ggplot(aes(x=richness, y = stab_com, color = as.factor(w_avg_tlvl))) +
+  geom_line() +
+  facet_grid(cols = vars(env_stoch), rows = vars(rho), labeller = label_both) +
+  theme_bw()
+ggsave(
+  here("report", "figures", "p_pred_sr_avg_tlvl.png"),
+  plot = p_pred_sr_avg_tlvl,
+  scale = 2.4,
+  width = 88,
+  height = 88 * 1,
+  units = "mm"
+)
 

### 2023-08-07 R/string_replacements.R

@@ -30,8 +30,8 @@ var_replacement <- function() {
     rho = "Env Corr",
     productivityenrichment = "Enrichment",
     env_stoch = "Env variance",
-    Z = "PPMR"
-
+    Z = "PPMR",
+    h = "FR type"
   )
 }
 rho_replacement <- function() {

### 2023-08-07 draft.jl

@@ -18,7 +18,9 @@ include("src/plot.jl")
 include("src/get_modules.jl")
 
 fw = FoodWeb(nichemodel,10, C = .3, Z = 100)
-p = ModelParameters(fw, biorates = BioRates(fw; d = allometric_rate(fw, DefaultMortalityParams())))
+p = ModelParameters(fw)
+B0 = rand(richness(fw))
+simulate(p, B0,tmax = 100, callback = EcologicalNetworksDynamics.CallbackSet(ExtinctionCallback(10^-6, true)))
 
 
 #########
@@ -137,7 +139,7 @@ timing = @elapsed sim = @showprogress pmap(p ->
                          batch_size = 1
                         )
 DataFrame(sim)
-fw = FoodWeb(nichemodel, 20, C = .22, check_cycle = true)
+fw = FoodWeb(nichemodel, 10, C = .33, check_cycle = true, check_disconnected = true)
 max_trophic_level(fw.A)
 A= fw.A
 
@@ -145,9 +147,9 @@ w = sim_int_mat(A;
             ρ = 0.0, alpha_ij = 0.5,
             d = nothing,
             da = (ap = .4, ai = .4, ae = .4),
-            K = 15.0,
-            σₑ = 1.0,
-            Z = 100, h = 2.0, c = 0.0,
+            K = 10.0,
+            σₑ = .6,
+            Z = 10, h = 2.0, c = 0.0,
             dbdt = EcologicalNetworksDynamics.stoch_d_dBdt!,
             max = 1000, last = 500, dt = .1, return_sol = false, digits = 5);
 w

### 2023-08-10 _targets.Rmd
Add a pre-draft

@@
 source(here::here("R", "model_helpers.R"))
+source(here::here("R", "sem_helpers.R"))
 ```
@@
 
-```{r targets raw_sim}
+```{targets raw_sim}
 list(
@@
 
->>>>>>> Stashed changes
-
 ## SEM
@@
 list(
+  tar_target(sim_fw_sem,
+    sim_fw_df %>%
+      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
+            sae_even, cpe_int, cpe_env), log))
+    ),
   tar_target(sem_model_list,
     list(
-      #ct_alive = lm(ct_alive ~ ct + S, sim_fw_df),
-      #richness = lm(richness ~ ct + S, sim_fw_df),
-      #  max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_df),
-      w_avg_tlvl = lm(w_avg_tlvl ~ richness + ct_alive, sim_fw_df),
-      avg_omnivory = lm(avg_omnivory ~ w_avg_tlvl + ct_alive + richness, sim_fw_df),
-      avg_int_strength = lm(avg_int_strength ~ w_avg_tlvl + ct_alive + richness + h, sim_fw_df),
-      pop_stab = lm(pop_stab ~ Z + richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_df),
-      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive, sim_fw_df),
-      sae_even = lm(sae_even ~ richness, sim_fw_df),
-      cpe_int = lm(cpe_int ~ richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + h, sim_fw_df),
-      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_df)
+      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
+      richness = lm(richness ~ ct + S, sim_fw_sem),
+      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
+      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
+      avg_omnivory = lm(avg_omnivory ~ ct + S, sim_fw_sem),
+      avg_int_strength = lm(avg_int_strength ~ ct + S + h + Z, sim_fw_sem),
+      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h + Z, sim_fw_sem),
+      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
+      sae_even = lm(sae_even ~ richness, sim_fw_sem),
+      cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
+      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_sem),
+      async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_sem),
+      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
     )
     ),
-  tar_target(sem, as.psem(sem_model_list)),
+  tar_target(sem, {
+    ti <- as.psem(sem_model_list)
+    update(ti, avg_omnivory %~~% w_avg_tlvl)
+    }
+    ),
   tar_target(sem_coeff, {
@@
     }),
+  tar_target(sim_eff_file, here::here("data", "sem_eff"), format = "file"),
+  tar_target(sem_eff, {
+    readRDS(sim_eff_file)
+    #semEff(sem, ci.type = "perc", R = 10, seed = 13, parallel = "no", data = sim_fw_sem)
+    }
+    ),
+  tar_target(sem_eff_tab, from_semEff_to_table(sem_eff)),
   tar_target(tab_sem_coeff,
@@
 )
-
 ```
@@
       sim_fw %>%
-        filter(env_stoch %in% c(.5, 1.5), rho == 0, productivity == 5) %>%
+        filter(env_stoch %in% c(.5, 1.5), rho == 0) %>%
         ggplot(aes(x = richness, y = stab_com, color = as.factor(env_stoch))) +
@@
 )
+```
+
+```{targets p_stab_rich_env_rho, tar_simple = TRUE}
+sim_fw %>%
+  filter(env_stoch %in% c(.1, .6), rho %in% c(0, .75), h == 3, Z == 100) %>%
+  ggplot(aes(x = log(richness), y = log(stab_com), color = as.factor(rho))) +
+  geom_point(alpha = .3) +
+  geom_smooth(method = "lm") +
+  facet_grid(cols = vars(env_stoch), labeller = label_both) +
+  labs(
+    x = "Species richness (Log)", y = "Community stability (Log)",
+    color = "Environmental correlation"
+  ) +
+  theme_bw() +
+  theme(legend.position = "bottom")
 ```
@@
     sim_fw %>%
-      filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
+      filter(rho %in% c(0), env_stoch == .1) %>%
       pivot_longer(c(stab_com, async, sae_total, cpe,
@@
 
+```{targets p_int_fw_str, tar_simple = TRUE}
+p1 <- sim_fw %>%
+  ggplot(aes(x = as.factor(richness), y = avg_int_strength)) +
+  geom_point() +
+  labs(x = "Species richness", y = "Avg. Interaction strength") +
+  theme_bw()
+p2 <- sim_fw %>%
+  ggplot(aes(x = as.factor(Z), y = avg_int_strength)) +
+  geom_boxplot() +
+  labs(x = "PPBR", y = "Avg. Interaction strength") +
+  theme_bw()
+p3 <- sim_fw %>%
+  filter(Z == 100) %>%
+  ggplot(aes(x = as.factor(h), y = avg_int_strength)) +
+  geom_boxplot() +
+  labs(x = "Hill exponent", y = "Avg. Interaction strength") +
+  theme_bw()
+plot_grid(p1, p2, p3, ncol = 2)
+```
+
 ```{targets p_cor, tar_simple = TRUE}
@@
 ggcorrplot(cor_var, type = "lower", lab = TRUE)
+```
+
+```{targets p_sem_tot_stab, tar_simple=TRUE}
+tar_read(sem_eff_tab) %>%
+  filter(effect_type == "total") %>%
+  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
+  filter(!predictor %in% c("evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async")) %>%
+  mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
+  ggplot(aes(
+      x = predictor,
+      y = effect,
+      ymin = lower_ci,
+      ymax = upper_ci)
+    ) +
+  geom_pointrange() +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  facet_grid(cols = vars(response)) +
+  labs(x = "Predictor", y = "Total effect") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 20, hjust = 1))
 ```
@@
 ```{r}
+tar_load(sim_fw_df)
+sim_fw_df %<>%
+  mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae, sae_even, cpe_int, cpe_env), log))
+
+tu <- list(
+      #ct_alive = lm(ct_alive ~ ct + S, sim_fw_df),
+      #richness = lm(richness ~ ct + S, sim_fw_df),
+      #  max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_df),
+      w_avg_tlvl = lm(w_avg_tlvl ~ richness + ct_alive + Z, sim_fw_df),
+      avg_omnivory = lm(avg_omnivory ~ ct_alive + richness, sim_fw_df),
+      avg_int_strength = lm(avg_int_strength ~ ct_alive + richness + h, sim_fw_df),
+      pop_stab = lm(pop_stab ~ Z + richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_df),
+      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive, sim_fw_df),
+      sae_even = lm(sae_even ~ richness, sim_fw_df),
+      cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_df),
+      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_df),
+      async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_df),
+      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_df)
+    )
+map_dfr(tu, check_collinearity)
+sem <- as.psem(tu)
+sem <- update(sem, avg_omnivory %~~% w_avg_tlvl)
+```
+
+```{r}
+ti <- compute_rotated_pca(sim_fw_df %>% select(
+    richness, w_avg_tlvl, avg_omnivory, avg_int_strength,
+    max_tlvl
+    ), naxis = 2)
+p <- plot_rotated_pca(pca_rotated = ti, axis = c(1, 2))
+p[[1]]
+```
+
+```{r}
+ti <- compute_rotated_pca(sim_fw_df %>% select(
+    w_avg_tlvl, avg_omnivory, avg_int_strength
+    ), naxis = 2)
+p <- plot_rotated_pca(pca_rotated = ti, axis = c(1, 2))
+p[[1]]
+p$rotated
+cor(ti$rotated$scores[, "RC1"], sim_fw_df[,"richness"])
+```
+
+```{r}
 tar_load(c(sim_fw))
@@
 tar_read(p_rich_stab)
-
-summary(lm(cpe_env ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
-summary(lm(cpe_int ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
-summary(lm(cpe ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
-performance::check_collinearity(lm(cpe_env ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
-mod_cpe <- lm(cpe ~ avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + productivity + rho, sim_fw)
-summary(mod_cpe_int)
-performance::check_collinearity(mod_cpe_int)
-
-mod_cpe <- lm(log(cpe) ~ avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + productivity + rho, sim_fw)
-
-summary(mod_cpe)
-plot(mod_cpe)
-performance::check_collinearity(mod_cpe_int)
 
@@
 ```{r}
-tar_load(sim_fw_cons)
-sim_fw_cons %>%
-  filter(env_stoch == .6, rho == 1, Z == 100, productivity == 5) %>%
-  ggplot(aes(x = richness, y = stab_com, color = as.factor(h))) +
-  geom_point() +
-  geom_smooth()
-
-sim_fw %>%
-  filter(env_stoch == .6, rho == 0, Z == 100, productivity == 15) %>%
-  ggplot(aes(x = richness, y = async, color = as.factor(h))) +
-  geom_point() +
-  geom_smooth()
-
-sim_fw_cons %>%
-  filter(env_stoch == .6, rho == 0, Z == 100, productivity == 30) %>%
-  ggplot(aes(x = richness, y = pop_stab, color = as.factor(h))) +
-  geom_point() +
-  geom_smooth()
-```
-
-```{r}
-plot(richness ~ Z, sim_fw)
-```
-
-```{r}
 tar_load(sim_sp)
@@
 tar_read(sem_coeff) %>%
-  filter(abs(Std.Estimate) > .05)
-tar_read(sem_rsquared)
+  filter(abs(Std.Estimate) > .1) %>%
+  mutate(Std.Estimate = round(Std.Estimate, 1))
+tar_read(sem_rsquared) %>%
+  mutate(R.squared = round(R.squared, 2))
 tar_load(sem_collinearity)
-sem_collinearity %>%
+tar_read(sem_collinearity) %>%
   print(., n = 38)
@@
 ```{r}
-tar_load(sem_model_list)
-tar_load(sim_fw_df)
-sem_boot <- bootEff(sem_model_list,
-  R = 10, seed = 13, parallel = "no")
-
-sem_eff <- semEff(sem_model_list, ci.type = "perc", R = 10, seed = 13, parallel = "no")
-```
-
-```{r}
+tar_load(c(sim_fw_sem, sim_fw))
 mod_tot_scaled <- lm(stab_com ~
-  richness + productivity + rho + env_stoch +
-  ct_alive + avg_int_strength + avg_omnivory + w_avg_tlvl +
-  richness : productivity +
+  richness + rho + env_stoch +
+  ct_alive + avg_int_strength + w_avg_tlvl +
   richness : rho +
@@
   richness : avg_int_strength +
-  richness : avg_omnivory +
   richness : w_avg_tlvl +
-  richness : productivity : ct_alive +
-  richness : productivity : w_avg_tlvl +
-  richness : productivity : avg_int_strength +
-  richness : productivity : avg_omnivory +
   richness : rho : ct_alive +
@@
   richness : rho : avg_int_strength +
-  richness : rho : avg_omnivory +
   richness : env_stoch : ct_alive +
   richness : env_stoch : w_avg_tlvl +
-  richness : env_stoch : avg_int_strength +
-  richness : env_stoch : avg_omnivory,
-sim_fw %>%
+  richness : env_stoch : avg_int_strength,
+sim_fw_sem %>%
   mutate(across(c("stab_com", "richness", "productivity", "rho", "env_stoch", "ct_alive", "avg_int_strength", "avg_omnivory", "w_avg_tlvl"), scale))
@@
   )
-summary(mod_tot)
-predict(mod_tot)
 summary(sim_fw$stab_com)
@@
 mod_tot <- lm(stab_com ~
-  richness + productivity + rho + env_stoch +
-  ct_alive + avg_int_strength + avg_omnivory + w_avg_tlvl +
-  richness * productivity +
+  richness  + rho + env_stoch +
+  ct_alive + w_avg_tlvl + Z +
+  avg_int_strength +
+  h +
   richness * rho +
@@
   richness * avg_int_strength +
-  richness * avg_omnivory +
+  richness * h +
   richness * w_avg_tlvl +
-  richness * productivity * ct_alive +
-  richness * productivity * w_avg_tlvl +
-  richness * productivity * avg_int_strength +
-  richness * productivity * avg_omnivory +
+  richness * Z +
   richness * rho * ct_alive +
@@
   richness * rho * avg_int_strength +
-  richness * rho * avg_omnivory +
+  richness * rho * h +
+  richness * rho * Z +
   richness * env_stoch * ct_alive +
-  richness * env_stoch * w_avg_tlvl +
-  richness * env_stoch * avg_int_strength +
-  richness * env_stoch * avg_omnivory,
+  richness * env_stoch * Z +
+  richness * env_stoch * avg_int_strength+
+  richness * env_stoch * h +
+  richness * env_stoch * w_avg_tlvl,
   mutate(sim_fw, across(c(stab_com, richness), log)) #, richness
   )
-check_collinearity(lm(stab_com ~ richness + productivity + rho + env_stoch +
-  ct_alive + avg_int_strength + avg_omnivory + w_avg_tlvl, sim_fw))
+check_collinearity(lm(stab_com ~ richness + rho +
+    env_stoch + avg_int_strength +
+  ct_alive + w_avg_tlvl + Z + h, sim_fw))
 plot(mod_tot)
@@
 pred_data <- list(
-  richness = log(seq(5, 30, 1)),
+  richness = log(seq(1, 30, 1)),
   ct_alive = c(.05, .10, .30),
-  rho = c(0, .5, 1),
-  avg_int_strength = c(.02, .04, .1),
-  env_stoch = c(.2, .6),
-  w_avg_tlvl = c(1.5, 1.7, 2),
-  avg_omnivory = c(.01, .05, .1),
-  productivity = c(5, 30),
-  Z = 10
+  rho = c(0, .75, 1),
+  avg_int_strength = c(.01, .02, .05, .1),
+  env_stoch = c(.1, .3),
+  w_avg_tlvl = c(1.5, 2, 3),
+  Z = c(10, 100),
+  h = c(2, 3)
   ) %>% expand.grid()
 pred_data$stab_com <- predict(mod_tot, newdata = pred_data)
-
 ```
@@
 ```{r}
-p_pred_sr_ct_int <- pred_data %>%
+p_pred_sr_int <- pred_data %>%
   filter(
-    productivity == 5,
-    ct_alive %in% c(.1, .3),
-    rho %in% c(0, 1),
-    avg_int_strength %in% c(.02, .1),
-    avg_omnivory == .05,
-    w_avg_tlvl == 1.7) %>%
-  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
-  geom_line() +
-  facet_grid(cols = vars(env_stoch), rows = vars(rho), labeller = label_both) +
-  theme_bw()
+    ct_alive %in% c(.1),
+    rho %in% c(0, .75),
+    Z == 10,
+    h %in% c(3),
+    avg_int_strength %in% c(.01, .05),
+    w_avg_tlvl == 1.5
+    ) %>%
+  ggplot(aes(
+      x = richness, y = stab_com,
+      color = as.factor(rho),
+      linetype = as.factor(avg_int_strength),
+      )) +
+  geom_line(linewidth = 2) +
+  facet_grid(cols = vars(env_stoch), labeller = label_both) +
+  labs(
+    x = "Species richness (Log)", y = "Community stability (Log)",
+    linetype = "Avg. Interaction strength",
+    color = "Environmental correlation"
+  ) +
+  theme_bw() +
+  theme(legend.position = "bottom")
 ggsave(
-  here("report", "figures", "p_pred_sr_ct_int.png"),
-  plot = p_pred_sr_ct_int,
+  here("report", "figures", "p_pred_sr_int.png"),
+  plot = p_pred_sr_int,
   scale = 2.4,
@@
 )
-p_pred_sr_omn <- pred_data %>%
+```
+
+```{r}
+plot_grid(
+  tar_read(p_stab_rich_env_rho) + theme(legend.position = "none"),
+  p_pred_sr_int)
+```
+
+```{r}
+
+p_pred_sr_avg_tlvl_h <- pred_data %>%
   filter(
-    productivity == 5,
-    ct_alive %in% c(.1),
+    ct_alive %in% c(.3),
+    h %in% c(2,3),
     rho %in% c(0, 1),
-    avg_int_strength %in% .02,
-    avg_omnivory %in% c(.01, .1),
-    w_avg_tlvl == 1.7) %>%
-  ggplot(aes(x=richness, y = stab_com, color = as.factor(avg_omnivory))) +
+    Z == 10,
+    avg_int_strength %in% c(.1),
+    w_avg_tlvl == c(1.5, 3)) %>%
+  ggplot(aes(x = richness, y = stab_com, linewidth = as.factor(w_avg_tlvl), color = as.factor(h))) +
   geom_line() +
@@
 ggsave(
-  here("report", "figures", "p_pred_sr_omn.png"),
-  plot = p_pred_sr_omn,
-  scale = 2.4,
-  width = 88,
-  height = 88 * 1,
-  units = "mm"
-)
-
-p_pred_sr_avg_tlvl <- pred_data %>%
-  filter(
-    productivity == 5,
-    ct_alive %in% c(.1),
-    rho %in% c(0, 1),
-    avg_int_strength %in% .02,
-    avg_omnivory %in% c(.05),
-    w_avg_tlvl == c(1.5, 2)) %>%
-  ggplot(aes(x=richness, y = stab_com, color = as.factor(w_avg_tlvl))) +
-  geom_line() +
-  facet_grid(cols = vars(env_stoch), rows = vars(rho), labeller = label_both) +
-  theme_bw()
-ggsave(
-  here("report", "figures", "p_pred_sr_avg_tlvl.png"),
+  here("report", "figures", "p_pred_sr_avg_tlvl_h.png"),
   plot = p_pred_sr_avg_tlvl,
@@
 )
-
-pred_data %>%
-  filter(
-    rho == 0,
-    ct_alive %in% c(.1, .3),
-    avg_int_strength %in% c(.02, .1),
-    avg_omnivory == .05,
-    w_avg_tlvl == 1.7) %>%
-  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
-  geom_line() +
-  facet_grid(cols = vars(env_stoch), rows = vars(productivity), labeller = label_both)
-
-pred_data %>%
-  filter(
-    env_stoch == 0.2,
-    ct_alive %in% c(.1, .3),
-    rho %in% c(0, 1),
-    avg_int_strength %in% c(.02, .1),
-    avg_omnivory == .05,
-    w_avg_tlvl == 1.7) %>%
-  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
-  geom_line() +
-  facet_grid(cols = vars(rho), rows = vars(productivity), labeller = label_both) +
-  theme_bw() +
-  labs(
-    x = "Species richness",
-    y = "Community stability",
-    linewidth = "Avg. Int",
-    color = "Connectance"
-  )
 ```
@@
 ```{r}
-pred_data %>%
-  filter(
-    env_stoch == 0.6,
-    ct_alive %in% c(.1, .3),
-    rho %in% c(0, 1),
-    avg_int_strength %in% c(.02, .1),
-    avg_omnivory == .05,
-    w_avg_tlvl == 1.7) %>%
-  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
-  geom_line() +
-  facet_grid(cols = vars(rho), rows = vars(productivity)) +
-  theme_bw()
+```
+
+```{r}
+tar_load(sem_eff_tab)
+sem_eff_tab %>%
+  filter(abs(effect) > .1) %>%
+  filter(effect_type == "direct") %>%
+  print(., n = 30)
+
+```
+
+```{r}
+tar_load(sim_fw_sem)
+sim_fw_sem %<>% mutate(richness = sqrt(richness))
+ti <- as.psem(sem_model_list)
+update(ti, avg_omnivory %~~% w_avg_tlvl)
+sem_coeff <- summary(ti)$coefficients[, c(1, 2, 8, 9)]
+map_dfr(sem_model_list, rsquared) %>%
+      mutate(Response = var_replacement()[Response]) %>%
+      select(Response, R.squared)
+```
+
+```{r}
+sem_model_list <- list(
+      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
+      richness = lm(richness ~ ct + S, sim_fw_sem),
+      #max_tlvl = lm(max_tlvl ~ ct + S, sim_fw_sem),
+      #w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
+      #avg_omnivory = lm(avg_omnivory ~ ct + S, sim_fw_sem),
+      avg_int_strength = lm(avg_int_strength ~ ct + S + h + Z, sim_fw_sem),
+      pop_stab = lm(pop_stab ~ richness + avg_int_strength + ct_alive + env_stoch, sim_fw_sem),
+      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + ct_alive, sim_fw_sem),
+      sae_even = lm(sae_even ~ richness, sim_fw_sem),
+      cpe_int = lm(cpe_int ~ richness + avg_int_strength + ct_alive, sim_fw_sem),
+      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_sem),
+      async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_sem),
+      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
+    )
+ti <- as.psem(sem_model_list)
+update(ti, avg_omnivory %~~% w_avg_tlvl)
+sem_coeff <- summary(ti)$coefficients[, c(1, 2, 8, 9)]
+map_dfr(sem_model_list, rsquared) %>%
+      mutate(Response = var_replacement()[Response]) %>%
+      select(Response, R.squared)
 ```

### 2023-08-10 paper/manuscript.Rmd
Add a pre-draft

---
title: Food-web structure, stochasticity and response diversity drive temporal stability in complex communities
author: Alain Danet, Andrew P. Beckerman
output:
  bookdown::pdf_document2
always_allow_html: true
toc: false
bibliography: references.bib
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.pos = "H",  # pdf mode
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

```{r, results = FALSE}

sapply(c("targets", "tidyverse", "magrittr", "cowplot", "here", "piecewiseSEM", "semEff", "ggcorrplot", "kableExtra"), require, character.only = TRUE)

mytheme <- theme_cowplot(font_size = 8) +
background_grid() +
theme(legend.position = "bottom")
theme_set(mytheme)
sapply(list.files(here("R"), full.names = TRUE), source)
```

# Introduction

Global change and its simultaneous increasing stressors constitute a major
threat to biodiversity and ecosystem functioning [@pachauri_climate_2015;
@simmons_refocusing_2021]. Among them, climate change is predicted to lead
dramatically more variable environments [@pachauri_climate_2015]. Understanding
how environmental variability will affect ecosystem
stability is then a timely question.

Biodiversity, in terms of species richness, has been repeatedly shown to drive
higher temporal stability of ecological communities, across various taxa and
ecosystems. Species richness can dampen the effects of perturbations on the
temporal variability of community biomass because more diverse communities
contain species with more diversity of responses to perturbations, which
generates asynchrony in population fluctuations, thereby stabilizing community
biomass fluctuations [@loreau_species_2008; @thibaut_understanding_2013;
@zhao_biodiversity_2022]. In turn, the effects of human pressures on biotic
homogenization reported in various ecosystems [@buisson_toward_2013;
@muthukrishnan_invasive_2020; @saladin_rapid_2020] is another threat, which
might in turn affect dampens the effects of species richness on ecosystem
stability. However, the joint effects of external stressors such as
environmental variabilityand internal stressors such as the
loss response diversity has been rarely assessed in temporal stability areas.

The question of stressors can even become complex in multitrophic communities,
where species richness corresponds both to horizontal and vertical diversity.
Food-web structure has been shown to have tremendous effect on community
stability. The degree of generalism of predator was shown to modulate
stability-richness relationships [@thebault_trophic_2005]. The strength and
distribution of interaction strength was also shown to be strong driver of
community stability [@mccann_weak_1998]. Omnivory was also shown to drive higher
stability [@mccann_reevaluating_1997]. The effects of food-web structure on
ecosystem stability has been mostly assessed with small modules [but see
@eschenbrenner_diversity_nodate], and we know very little how food-web structure
affects the relationships between species richness and temporal stability in
complex food-webs.

Both stressors and food-web structure are expected to have different effects on
temporal stability. Stability of community biomass can itself be partitioned in
several components, i.e. population stability and population asynchrony
[@thibaut_understanding_2013; @zhao_biodiversity_2022]. Population stability can
be itself partioned in total biomass and population variability effect.
Population asynchrony can further be partioned in statistical averaging effect
and compensatory dynamics effects [@zhao_biodiversity_2022]. Partitioning
stability allows to better understand how food-web structure and external
factors affect stability. We expect that environmental variability will
primarily affect. For exemple, environmental stochasticity is expected to
primarily affect population variance. Response diversity is expected to act
primarily on compensatory dynamics in the food-webs, as low response diversity
will decrease the effects. Higher connectance and interaction strength are
expected to dampens population variability but to lead to higher synchrony at
the same time.

---
#Understanding the mechanisms that determine temporal
#stability of ecosystem functioning is a long standing
#question in Ecology [@may_will_1972; @angelis_stability_1975;
#@mccann_diversitystability_2000; @tilman_biodiversity_2006;
#@donohue_navigating_2016; @kefi_advancing_2019].
---

In this study, we investigated both the effects of stressors ( environnmental
variability and response diversity) and of food-web structure (connectance,
average interaction strength, average trophic level) on species
richness-stability relationships. To do, we used a bioenergetic food-web model
[@yodzis_body_1992; @brose_allometric_2006; @delmas_simulations_2017] added to
environmental stochasticity.

```{r}
concept_cap <- "Food-web structure, response diversity and enviromental gradient
can modulate stability-richness relationships. (a & b) Food-web structure may
modulate stability-richness relationships additively (a) or interactively (b).
(c) Decrease in response diversity and increase in environmental variability
should dampen stability-richness relationships. While the loss of response
diversity should dampen the effect of species richness on asynchrony, the
increase in environmental variability should decrease primarily population
stability. (d) Increase in productivity should increase species richness
(trophic energy hypothesis) but also dampens the relationship between stability
and species richness (paradox of enrichment). (e) Summary of the framework, how
food-web structure and external perturbations modulate the effects of species
richness on community stability. More precisely, how they affect the different
components of stability: total biomass, population variability, statistical
averaging effects and compensatory dynamics."
```

```{r, fig.cap=concept_cap}
knitr::include_graphics(here("report", "figures", "conceptual_figures.pdf"))
```

```{r, eval = FALSE}
tribble(
  ~Type, ~`Food-web structure`, ~`Effect on stability-richness`,
  "Food-web structure", "Connectance", "Strengthen (Miele et al., 2016) / No effect (Thébault & Loreau, 2005)",
  "Food-web structure", "Omnivory", "Strengthen (Mccann et al., 1997)",
  "Food-web structure", "Interaction strength", "Destabilising (Mccann et al., 1998) / Stabilising in
  productive (Binzer et al., 2012; Binzer et al., 2016; Tabi et al., 2019)",
  "Response diversity", "", "Dampens",
  "Productivity", "", "Dampens (Binzer et al., 2012; Binzer et al., 2016; Tabi et al., 2019)",
  "Environmental variability", "", "Dampens",) %>%
kbl(caption = "Predictions of stability-richness relationship from the literature.") %>%
kable_styling()
```

\pagebreak

# Methods

## The model

We simulated the dynamics of complex food-webs using the allometric bioenergetic
model [@yodzis_body_1992; @brose_allometric_2006; @delmas_simulations_2017].
[DESCRIPTION of the  MODEL]

We added a stochastic natural mortality rate to the species dynamics, that
represent variation in mortality due to variation in environment. Based on the
litterature and previous models [@vasseur_environmental_2007], we assumed that
natural mortality rates scales inversely with the species body mass ($d_i =
d_0M_i^{-1/4}$, ), as all other physiological parameters. We used a basal
natural mortality rate of $d_0 = .4$, as done in previous
studies[@vasseur_environmental_2007].

## Environmental stochasticity and response diversity

We introduced environmental stochasticity by
considering stochastic variation of mortality rates. Doing so allows to consider
stochasticity without modifying species interactions themselves
[@vasseur_environmental_2007]. The stochastic part of the mortality rates
($\epsilon_{i, t}$) follow a normal distribution 0 centered
($\epsilon_{i, t} \sim N(0,\sigma^2_e)$) with a variance ($\sigma^2_e$). The mortality rate each
species at the time $t$ equals to $d_{i,t} = d_i e^{\epsilon_{i, t}}$. We did so
to ensure to not have negative mortality rates [@vasseur_environmental_2007]. We
simulated $\epsilon$ using an Ornstein-Uhlenbeck process, which is a modified
browian motion where the stochastic values tend to come back to the central
value (i.e. $\epsilon = 0$) such as $\epsilon_t$ varies according to this
stochastic differential equation: $d\epsilon_t = (0 - \epsilon_t)d_t + \sigma_e
dW_t$, where $dW_t$ is a Browian motion. The strength of environmental
stochasticity was then controlled by $\sigma_e$.

Response diversity was controlled by the correlation  among species stochastic
mortality rates ($\rho_{ij, i \neq j}$) such as response diversity is maximal when species mortality
rates are uncorrelated ($\rho = 0$) and null when species mortality
rates are perfectly correlated ($\rho = 1$) [@ripa_food_2003;
@vasseur_environmental_2007; @gouhier_synchrony_2010]. So the species mortality
rates were a product of the stochastic mortality rates generated by the
Ornstein-Uhlenbeck process and a variance-covariance matrix such as:

$$
\epsilon_{i, t} =
  \begin{bmatrix}
     \rho_{11}\sigma^2_e & \rho_{12}\sigma^2_e & \cdots & \rho_{1n}\sigma^2_e \\
     \rho_{21}\sigma^2_e & \rho_{22}\sigma^2_e & \cdots & \rho_{2n}\sigma^2_e \\
     \vdots  & \vdots  & \ddots & \vdots  \\
     \rho_{n1}\sigma^2_e & \rho_{n2}\sigma^2_e & \cdots & \rho_{nn}\sigma^2_e
  \end{bmatrix}
  \begin{bmatrix}
     a_{1,t} \\
     a_{2,t} \\
     \vdots  \\
     a_{n,t}
  \end{bmatrix}
$$

where $a_{i,t}$ the stochastic value generated by the Ornstein-Uhlenbeck
process at time $t$, $\rho_{ii} = 1.0$ while all $\rho_{ij, i \neq j}$ were equal and control
the level of response diversity.

## Simulation

We generated food-web structure using the niche model [@williams_simple_2000]
with species richness from 10 to 60, and connectance from $0.02$ to $.32$. We
generated food-webs without cannibalistic links and checked for the absence of
disconnected species.

To vary interaction strength and mortality rates in the community,
we varied the Predator-Prey Bodysize Ratio (PPBR) from 1 to 100. We further
varied the functional reponse of consumer from type II to type III (resp. $h=2$
and $h=3$, eq XX) as it was shown to have a tremendous role on stability
[@brose_allometric_2006]. We set $K = XX$ to ensure that consumers were not
limited by the biomass input in the food-web.

We varied the strength of environmental stochasticity by varying $\sigma_e$ from
0.1 to 0.6, the range of mortality rates observed in
protists [@vasseur_environmental_2007]. We decreased response diversity by
increasing $\rho$ from 0 to 1.

We numerically solved the simulation with a $dt$ = .1 during 5000 timesteps
and collected the last 500 timesteps. We set extinction threshold to $10^{-5}$
and if an extinction happened in the last 500 timesteps, we continued to run the
simulation for another 500 timesteps until there was no extinction events.

## Simulation analysis

We measured food-web structure and dynamics that have been shown to be linked
with stability. We collected total biomass, species richness, connectance,
average trophic level weighted by biomass, average omnivory and average per
capita interaction strength.

We assessed the effects of food-web structure, environmental stochasticity and
response diversity on temporal stability of biomass. We measured temporal stability of biomass
as the inverse of the coefficient of variation. We further partitioned stability
into population stability ($S_{pop}$) and asynchrony ($\phi$) such as:

\begin{equation}
\begin{aligned}
S_{com} = S_{pop} \times \phi
(\#eq:scom)
\end{aligned}
\end{equation}

with $S_{com} = \mu_{tot} / \sigma_{tot}$, $S_{pop} = \mu_{tot} / \sum_i \sigma_i$,
$\phi = \sum_i \sigma_i / \sigma_{tot}$.

$\mu_{tot}$ and $\sigma_{tot}$ being respectively average total biomass and standard
deviation of total biomass.

To further get a mechanistic insight about the effects of stressors and food-web structure on stability,
we partionned asynchrony into statistical averaging effect (SAE) and compensatory
dynamics effect (CPE) [@zhao_biodiversity_2022]. SAE controls for ..., while CPE describes compensatory
dynamics emerging from species interactions and differential responses to
environmental stochasticity.

\begin{equation}
\begin{aligned}
S_{com} = S_{pop} \times SAE \times CPE
(\#eq:scom)
\end{aligned}
\end{equation}

\begin{equation}
\begin{aligned}
SAE = SAE_{even} \times EVN
(\#eq:sae)
\end{aligned}
\end{equation}

Statistical averaging effect is the share of asynchrony assuming that species are
independant, meaning that the variance total of the community is equal to the
sum of species variances only (i.e. species covariances are null). We can
define community stability ($S_{com, IP}$) in that scenario and then derive $SAE$.

\begin{equation}
\begin{aligned}
S_{com, IP} &= \dfrac{\mu_{tot}}{\sqrt{\sum_i \sigma^2_i}} = SAE \times S_{pop} \\
SAE &= \dfrac{S_{com, IP}}{S_{pop}} = \dfrac{\sum_i \sigma_i}{\sqrt{\sum_i \sigma^2_i}}\\
(\#eq:sae2)
\end{aligned}
\end{equation}

As SAE is further dependant of biomass evenness in food-webs, we
partionned $SAE$ into $SAE_{even}$ and evenness $EVN$, such as $SAE_{even} =
\sqrt{S}$ and $EVN = SAE / SAE_{even}$.

Compensatory dynamics in the food-webs is then the remaining part of asynchony:

\begin{equation}
\begin{aligned}
CPE &= \dfrac{S_{com}}{SAE \times S_{pop}} = \dfrac{\sqrt{\sum_i \sigma^2_i}}{\sigma_{tot}}\\
(\#eq:cpe)
\end{aligned}
\end{equation}

Compensatory dynamics can arise from predator-prey interactions
($CPE_{int}$) or from differential response of species to enviromental
stochasticity ($CPE_{env}$). From the deterministic and stochastic parts of
mortality rates, we computed the compensatory dynamics linked to the environment
such as:

\begin{equation}
\begin{aligned}
CPE_{env} = \mathbf{B} \times \mathrm{diag}(d_i) \times e^\mathbf{E}
(\#eq:cpenv)
\end{aligned}
\end{equation}

with $\mathbf{B}$ and $\mathbf{E}$ being the matrices time x species for species biomass
and stochastic mortality rates respectively. Then compensatory dynamics raising
from species interactions were computed as: $CPE_{int} = CPE / CPE_{env}$.

## Statistical analysis

Using a structural equation model, we disantengled the complex effects of
food-web structure, environmental stochasticity and response diversity on the
different facets of temporal stability of biomass (i.e. population stability,
statistical averaging effects and compensatory dynamic effects). We set the
paths of the path of the model according to theorical expectations. We tested
the effects of species richness, connectance, and the Predator-Prey size ratio
on secondary structure of the food-webs, the average trophic level, the average
omnivory and the interaction strength. We also tested the effects of  on  We
expected that richness affect population stability by modifying the average
population biomass for exemple [@thibaut_understanding_2013]. Grounded in
theoretical ecological, we expected that average trophic level, the average
omnivory and the interaction strength modulated population stability
[@mccann_weak_1998; @mccann_reevaluating_1997; @shanafelt_stability_2018].
Previous studies have also the Predator-Prey size ratio modulate population
stability [@brose_allometric_2006]. Finally, the effect of enviromental
stochasticity was assumed to be mainly associated to population stability (i.e.
by increasing amplitude of population fluctuations).

Regarding asynchrony, we tested the effects of species richness, connectance,
weighted average trophic level and interaction strength on the evenness of
biomass which in turn affect total statistical averaging effects. We expected
that those same food-web structural properties also affected compensatory
dynamics due to interactions ($CPE_{int}$). Finally, we tested the effects of
species richness and species cross-correlation in mortality rates on the
compensatory dynamics due to stochastic fluctuations ($CPE_{env}$). We completed
the structural equation model with the mathematical relationship linking
compensatory dynamics and statistical averaging effects to asynchrony, and from
asynchrony and population stability to community stability.

Prior to test the structural equation model, we logged all the stability
components to transform their relation from multiplicative to additive (eq XX).
We ensure that all the linear models composing the structural equation model
presented low multicollinearity (Variance Inflation Factor < 5, Table SXX). The
structural equation model using the R package `PiecewiseSEM`
[@lefcheck_piecewisesem_2016]. We then bootstrapped (N = 100) the SEM to obtain
confidence interval on the estimated effects and computed the sum of the direct
and indirect effects using `semEff` R package [@murphy_semeff_2021]. In the
main text, we reported standardized coefficients which are obtained by scaling
the coefficients by the stardard deviation of the response and predictor
variable (add formula). Finally, because we analyzed simulation, we reported
only the direct standardized coefficients that had an absolute value above $0.1$.

In a second analysis, we aimed to test how stability-species richness
relationships were modulated by food-web structure and the two stressors:
environmental stochasticity and response diversity. We modelled temporal
stability of biomass according to food-web structure: species richness, weighted average trophic
level, connectance, hill exponent, predator-prey size ratio, and average
interaction strength, as well as enviromental stochasticity and species
cross-correlation. We further included the two way interactions between species
richness and food-web structure, plus between species richness and stressors.
Finally we added the three way interaction between species richness, food-web
structure and stressors. The VIF were inferior to 5, indicating low
multicollinearity.

# Results

## Drivers of stability

```{r}
sem_cap <- paste0("Structural equation model. Only standardized coefficients
  whose absolute values are superior to 0.1 are displayed. [To complete with the links from initial structure]")
```

```{r sem, fig.cap=sem_cap}
knitr::include_graphics(here("report", "figures", "sem_stab2.pdf"))
```

```{r}
tar_load(sem_eff_tab)

get_eff <- function(y = "pop_stab", x = "richness", d = 2, effect_type = "direct") {
  mask <- sem_eff_tab$response == y & sem_eff_tab$predictor == x &
    sem_eff_tab$effect_type == effect_type
  round(sem_eff_tab[mask, ]$effect, d)
}

rpt <- get_eff(y = "pop_stab", x = "w_avg_tlvl")
rph <- get_eff(y = "pop_stab", x = "h")
rpe <- get_eff(y = "pop_stab", x = "env_stoch")
rsr <- get_eff(y = "sae_even", x = "richness")
ret <- get_eff(y = "evenness_sae", x = "w_avg_tlvl")
rer <- get_eff(y = "evenness_sae", x = "richness")
rea <- get_eff(y = "evenness_sae", x = "avg_int_strength")
rec <- get_eff(y = "evenness_sae", x = "ct_alive")
reh <- get_eff(y = "evenness_sae", x = "h")

ria <- get_eff(y = "cpe_int", x = "avg_int_strength")
ric <- get_eff(y = "cpe_int", x = "ct_alive")
rih <- get_eff(y = "cpe_int", x = "h")
rir <- get_eff(y = "cpe_int", x = "richness")

rvr <- get_eff(y = "cpe_env", x = "richness")
rvo <- get_eff(y = "cpe_env", x = "rho")
```
```{r, eval = FALSE}
sem_eff_tab %>%
  filter(abs(effect) > .1, effect_type == "direct")
```

We found that food-web structure had significant effect on temporal population
stability such as average trophic level and type III functional response (i.e. h = 3)
increase population stability (resp. $r_\delta$= `r rpt` and `r rph`, $r_\delta$
being the standardized coefficient, Fig. \@ref(fig:sem)). However the strength
of environmental stochasticity had a strong negative effect on population
stability ($r_\delta$= `r rpe`).

We further found that food-web structure had a strong impact on statistical
averaging effects, which raises from independant species fluctuations weigthed
the evenness of their biomass. As expected the mathematical relationship (eq. XX),
species richness was the only driver of even statistical averaging effect
($r_\delta$= `r rsr`, Fig. \@ref(fig:sem)). Average trophic level had a strong negative effect on
evenness ($r_\delta$= `r ret`), meaning that biomass are more inequally
distributed among species, thereby downplaying the portefolio effect raised from
species richness. But richness had also a small negative effect on evenness
($r_\delta$= `r rer`). Constrastingly, connectance, average interaction
strength, and type III functional response all increased biomass evenness
(resp. $r_\delta$= `r rec`, `r rea`, and `r reh`).

Food-web structure and cross-correlation among species mortality rates had
strong effects on compensatory dynamics. Average trophic level, connectance and
type III functional response had a negative effect on compensatory effect
raising from species interaction (resp. $r_\delta$= `r ria`, `r ric`, `r rih`,
Fig. \@ref(fig:sem)) there decreasing asynchony, while richness had a positive
effect ($r_\delta$= `r rir`), there increasingasynchrony. In turn, richness and
cross-correlation among species mortality rates had a negative effect on
compensatory dynamic raising from environmental stochasticity
($r_\delta$= `r rvr` and `r rvo`).

```{r}
rscp <- get_eff(y = "stab_com", x = "pop_stab")
rsca <- get_eff(y = "stab_com", x = "async")

rav <- get_eff(y = "async", x = "cpe_env")
rae <- get_eff(y = "async", x = "evenness_sae")

rass <- get_eff(y = "async", x = "sae_even")
rasi <- get_eff(y = "async", x = "cpe_int")
```

Population stability had a positive effect twice higher than asynchrony on the
temporal stability of community (resp. $r_\delta$= `r rscp` and `r rsca`). In turn, asynchrony
was mostly driven by evenness of biomass distribution and compensatory dynamics
raising from environmental stochasticity (resp. $r_\delta$= `r rae` and `r rav`, Fig.
\@ref(fig:sem)) than from statistical averaging emerging from species richness
(i.e. even) and compensatory dynamics emerging from species interaction (resp.
$r_\delta$= `r rass` and `r rasi`).

```{r}
semtot_cap <- "Total effect of food-web structure and stressors on community
stability, asynchony, and population stability. The total effects were derived
from the structural equation model."
```

```{r semtot, fig.cap = semtot_cap}
tar_read(p_sem_tot_stab)
```

Deriving the sum of direct and indirect effects from the structural equation
model, we show that both enviromental stochasticity and cross-correlation among
species had by far the most negative effect on community stability (XX, Fig.
\@ref(fig:semtot)). Average trophic level, type III functional response and
predator prey bodysize ratio had total positive effects on community stability.
Those positive effects are raising from sometimes contrasting effects on
population stability and asynchrony such as Average trophic level, type III
functional response and predator prey bodysize ratio which have positive effects
on population stability (resp. XXX) but a negative one on asynchrony (resp. XXX).

## Stability-richness relationship

```{r}
pred_cap <- "Relationship between community stability and species richness
according to environmental stochasticity and response diversity. (a) Simulation [add parameters selected], (b) Prediction from the linear model. "
```

```{r pred, fig.cap = pred_cap}
knitr::include_graphics(here("report", "figures", "p_sim_pred.pdf"))
```

Using a more complex linear model (i.e. containing interaction), we investigated more
in detail the relationship between community stability and species richness and
how this relation is affected by environmental stochasticity and cross
correlation among species mortality rates. We found that environmental
stochasticity decrease overall community stability but does not change the shape
of the community stability-species richness relationship (put some numbers, Fig.
\@ref(fig:pred)a and b). In contrasts, cross correlation among species mortality rates
both decreases overall community stability and nullifies the community
stability-species richness relationship. Surpringly, we found that
despite average interaction strength has a small overall effect on
community stability, high average interaction strength change the shape of the
community stability-species richness relationship from positive to negative when
response diversity is low (put some numbers, Fig. \@ref(fig:pred)b).

```{r, eval = FALSE}
tar_read(p_int_fw_str)
```

# Discussion

## Food-web structure and stressors affects population stability and asynchony

Our results shows that community stability in complex food-webs is mainly driven
by population stability rather than synchrony, confirming previous results in
empirical data [@danet_species_2021]. We further found that average trophic
level and functional response of type III increased average population
stability, confirming previous results [@brose_allometric_2006;
@shanafelt_stability_2018; @danet_species_2021;
@eschenbrenner_diversity_nodate]. Higher average trophic level stabilises
populations because higher predator are themselves more stable and because they
control the amplitude of the fluctuations of their prey [REF, we can test
that?]. Furthermore, average omnivory was strongly correlated with average
trophic level, suggesting that average omnivory also stabilise population
stability, in line with previous theoretical results in small modules
[@mccann_reevaluating_1997]. In turn, functional response of type III decreases
the feeding rates of consumers when their preys have a low biomass which leads
to a less dramatic fluctuations of prey biomass [@uszco_effects_2017;
@brose_allometric_2006]. We however found no big effect of species richness on
population stability, which has been reported to be negative, positive or
neutral in previous studies [@ruijven_contrasting_2007;
@houlahan_negative_2018].

Our results shows that asynchrony is mainly decreased by the cross-correlation
among species mortality rates and mediated by compensatory dynamics, indicating
that the loss of response diversity suppressed the positive effects of species
richness on stability. Our result shows that evenness of biomass plays an
significant role in driving statistical averaging effect (i.e. portefolio
effects). Our results shows that average trophic level decreases strongly the
evenness of biomass variability, thereby limiting the effect of species richness on the
portefolio effects. Furthermore, increase in species richness also resulted in
less even biomass variability. Our results also suggest that stronger species
interaction, higher generalism, and functional response of type III are
associated with a more even variability, thereby raising the portefolio
effects. The importance of evenness in driving portefolio effects has been
recognised early by theoretical studies [@thibaut_understanding_2013], but
rather in terms of abundance than in variability [@zhao_biodiversity_2022].
We suggest that higher average trophic level decreases evenness of variability
because the model assumes that species of higher trophic level have a lower
overall mortality rates, similarly to previous studies [@vasseur_environmental_2007].

Our results further suggest that higher average trophic level results in lower
compensatory dynamics raising from species interactions. It might be explained
by the fact that average trophic level is strongly associated with average
omnivory, which might tamper synchronized predator-prey oscillations that can
raise compensatory dynamics [@mccann_reevaluating_1997]. Higher generalism in
also drives lower compensatory dynamics due to species interaction and then lend
to the same hypothesis such as more trophic links per consumer should decrease
overall amplitude of oscillations due to prey switching. Furthermore, functional
response of type III which drives prey switching at low abundance of the
prefered prey also lend toward this interpretation
[@mccann_diversitystability_2000]. [Do not have clear idea for richness at this
time]. Surpringly however, average interaction strength had no effects on
compensatory dynamics that is not already captured by other food-web structural
properties. Compensatory dynamics due to environment was decreased by both
species richness and cross-correlation among species mortality rates (i.e. loss
of response diversity). Our interpretation is that higher species richness
syncronize more species fluctuations due to mortality because each added species
adds (S - 1, S being richness) positive covariance terms in the stochastic
mortality rates, thereby increasing the overall synchrony in mortality rates
when cross correlation are not null.

## Stochasticity and response diversity affect stability-richness relationship

Our results suggest that, confirming the result of the structural equation
model, that in maximal response diversity environmental stochasticity primarily
drives average stability, without changing the shape of the stability-richess
relationship. The reason is that the strength of environmental stochasticity
only affect population stability and not asynchrony, the latter being the driver
of species-richness relationships. In turn, a decrease in response diversity
dampens the stability-richness relationship [@thibaut_understanding_2013].
Interestingly, our results also suggest that high response diversity also
decrease the destabilising effects of average interaction strength on
stability-richness relationships. Indeed, in low response diversity, we found
high interaction strength leads to negative stability-richness relationships.

## Implication for real world

Our results highlight that population stability is the primary driver of
community stability. In the context of global changes in which environmental
variability is expected to increase tremendously, we expect to see a strong
decrease in community stability, despite high response diversity. But ongoing
biotic homogenization [@olden_homogocene_2018; @muthukrishnan_invasive_2020;
@wang_biotic_2021] is also suggested to descrease response diversity
[@wang_biotic_2021; @su_human_2021], which in turn is expected to further
decrease stability despite high species richness, even more in food-web
communities composed of high interaction strength. Then, our study reinforces
that the restauration of ecosystems along with a restauration of landscape
complexity that provides refuges from extrem environment are key to maintain
temporal stability of ecological communities [@ryser_landscape_2021].

# Conclusion

TODO

# References {-}

### 2023-08-10 R/pca_methods.R

@@ -1,0 +1,33 @@
+compute_rotated_pca <- function(.data = NULL, naxis = 2) {
+  .data <- na.omit(.data)
+  pca <- ade4::dudi.pca(as.data.frame(.data),
+    scannf = FALSE, nf = naxis, center = TRUE, scale = TRUE
+  )
+  pca_rotated <- psych::principal(.data,
+    rotate = "varimax", nfactors = naxis,
+    scores = TRUE
+  )
+
+  return(list(normal = pca, rotated = pca_rotated))
+}
+
+plot_rotated_pca <- function(pca_rotated = NULL, axis = c(1, 2)) {
+  {
+    adegraphics::adegpar()$plabels
+    ade4::s.corcircle(
+      pca_rotated$rotated$loadings[1:nrow(pca_rotated$rotated$loadings), ],
+      xax = axis[1],
+      yax = axis[2], box = TRUE
+    )
+    mtext(paste0("RC ", axis[1]), side = 1, adj = .5, line = -1)
+    mtext(paste0("RC ", axis[2]), side = 2, adj = .5, line = -5)
+    rotated_plot <- grDevices::recordPlot()
+  }
+  pca_plot <- factoextra::fviz_pca_var(pca_rotated$normal,
+    axes = axis,
+    col.var = "contrib", # Color by contributions to the PC
+    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+    repel = TRUE # Avoid text overlapping
+  )
+  return(list(rotated = rotated_plot, normal = pca_plot))
+}

### 2023-08-10 scripts/param_comb_ct_S_h_d_allometric2.jl

@@ -1,7 +1,7 @@
 using CSV, StatsBase, DataFrames, Arrow, EcologicalNetworksDynamics
 
 nrep = 50
-sigma = [0.0, 0.1, 0.3, 0.6]#.1:.2:0.6
+sigma = [0.1, 0.3, 0.6]#.1:.2:0.6
 Z = [1, 25, 50, 100]
 ρ = 0:.25:1
 K = [10]
@@ -66,7 +66,7 @@ fw_test2 = map(p -> try
               param[.! ismissing.(fw_test)]
              )
 
-param2 = param[.! ismissing.(fw_test2)]
+param2 = param[.! ismissing.(fw_test)][.! ismissing.(fw_test2)]
 
 
 # Try to get same number of sampling per richness
@@ -98,6 +98,11 @@ function try_foodweb(S; C = .1, tol_C = .05, n = 5, kwargs...)
     fw
 end
 
+fw = try_foodweb(10; C = 0.5,
+            tol_C = .05,
+            check_cycle = true,
+            check_disconnected = true).A
+
 
 df4 = repeat(df3, nrep)
 df4[!, :rep] = reduce(vcat, [repeat([i], nrow(df3)) for i in 1:nrep])
@@ -111,7 +116,7 @@ foodweb = map(p -> (rep = p.rep, S = p.richness, C = p.connectance,
              NamedTuple.(eachrow(df4))
             )
 df_fw = DataFrame(foodweb)
-df_fw = df_fw[.! ismissing.(df_fw.A)]
+df_fw = df_fw[.! ismissing.(df_fw.fw),:]
 # Create a foodweb_id
 df_fw[!, :fw_id] = 1:nrow(df_fw)
 Arrow.write("../fw_comb_ct_S_h_d2.arrow", df_fw)

### 2023-10-11 _targets.Rmd
New plots

@@
   filter(response %in% c("async", "pop_stab", "stab_com")) %>%
-  filter(!predictor %in% c("evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async")) %>%
+  filter(!predictor %in% c("evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async", "S", "ct")) %>%
   mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
@@
   )
+mod_tot_async <- lm(async ~
+  richness  + rho + env_stoch +
+  ct_alive + w_avg_tlvl + Z +
+  avg_int_strength +
+  h +
+  richness * rho +
+  richness * env_stoch +
+  richness * ct_alive +
+  richness * avg_int_strength +
+  richness * h +
+  richness * w_avg_tlvl +
+  richness * Z +
+  richness * rho * ct_alive +
+  richness * rho * w_avg_tlvl +
+  richness * rho * avg_int_strength +
+  richness * rho * h +
+  richness * rho * Z +
+  richness * env_stoch * ct_alive +
+  richness * env_stoch * Z +
+  richness * env_stoch * avg_int_strength+
+  richness * env_stoch * h +
+  richness * env_stoch * w_avg_tlvl,
+  mutate(sim_fw, across(c(async, richness), log)) #, richness
+  )
+mod_tot_pop_stab <- lm(pop_stab ~
+  richness  + rho + env_stoch +
+  ct_alive + w_avg_tlvl + Z +
+  avg_int_strength +
+  h +
+  richness * rho +
+  richness * env_stoch +
+  richness * ct_alive +
+  richness * avg_int_strength +
+  richness * h +
+  richness * w_avg_tlvl +
+  richness * Z +
+  richness * rho * ct_alive +
+  richness * rho * w_avg_tlvl +
+  richness * rho * avg_int_strength +
+  richness * rho * h +
+  richness * rho * Z +
+  richness * env_stoch * ct_alive +
+  richness * env_stoch * Z +
+  richness * env_stoch * avg_int_strength+
+  richness * env_stoch * h +
+  richness * env_stoch * w_avg_tlvl,
+  mutate(sim_fw, across(c(pop_stab, richness), log)) #, richness
+  )
 check_collinearity(lm(stab_com ~ richness + rho +
@@
   avg_int_strength = c(.01, .02, .05, .1),
-  env_stoch = c(.1, .3),
+  env_stoch = c(.1, .6),
   w_avg_tlvl = c(1.5, 2, 3),
@@
 pred_data$stab_com <- predict(mod_tot, newdata = pred_data)
+pred_data$async <- predict(mod_tot_async, newdata = pred_data)
+pred_data$pop_stab <- predict(mod_tot_pop_stab, newdata = pred_data)
+pred_data$resp_div <- rho_replacement()[as.character(pred_data$rho)]
 ```
@@
 p_pred_sr_int <- pred_data %>%
+  filter(
+    ct_alive %in% c(.1),
+    rho %in% c(0, .75),
+    richness >= 1,
+    Z == 10,
+    h %in% c(3),
+    avg_int_strength %in% c(.01, .1),
+    w_avg_tlvl == 1.5
+    ) %>%
+  ggplot(aes(
+      x = richness, y = stab_com,
+      color = as.factor(resp_div),
+      linetype = as.factor(avg_int_strength),
+      alpha = as.factor(avg_int_strength)
+      )) +
+  ylim(2, 8) +
+  geom_line(linewidth = 1) +
+   scale_alpha_manual(values=c(1, 0), guide = "none") +
+  facet_grid(cols = vars(env_stoch), labeller = label_both) +
+  labs(
+    x = "Species richness (Log)", y = "Community stability (Log)",
+    linetype = "Avg. Interaction strength",
+    color = "Response diversity"
+  ) +
+  theme_bw() +
+  theme(legend.position = "bottom")
+```
+
+```{r}
+p_pred_sr_int1 <- pred_data %>%
   filter(
@@
     h %in% c(3),
-    avg_int_strength %in% c(.01, .05),
+    avg_int_strength %in% c(.01, .1),
     w_avg_tlvl == 1.5
@@
       x = richness, y = stab_com,
+      color = as.factor(resp_div),
+      linetype = as.factor(avg_int_strength),
+      alpha = as.factor(avg_int_strength)
+      )) +
+  geom_line(linewidth = 1) +
+   scale_alpha_manual(values=c(1, 0), guide = "none") +
+  facet_grid(cols = vars(env_stoch), labeller = label_both) +
+  labs(
+    x = "Species richness (Log)", y = "Community stability (Log)",
+    linetype = "Avg. Interaction strength",
+    color = "Response diversity"
+  ) +
+  theme_bw() +
+  theme(legend.position = "bottom")
+p_pred_sr_int2 <- p_pred_sr_int1 +
+   scale_alpha_manual(values=c(1, 1), guide = "none")
+ggsave(
+  here("report", "figures", "p_pred_sr_int1.png"),
+  plot = p_pred_sr_int1,
+  scale = 2.4,
+  width = 88,
+  height = 88 * .5,
+  units = "mm"
+)
+ggsave(
+  here("report", "figures", "p_pred_sr_int2.png"),
+  plot = p_pred_sr_int2,
+  scale = 2.4,
+  width = 88,
+  height = 88 * .5,
+  units = "mm"
+)
+```
+
+```{r}
+pred_data_show <- pred_data %>%
+  filter(
+    ct_alive %in% c(.3),
+    rho %in% c(0, .75),
+    Z == 100,
+    h %in% c(3),
+    avg_int_strength %in% c(.01, .1),
+    w_avg_tlvl == 1.5
+    )
+
+sim_fw %>%
+  filter(env_stoch %in% c(.1, .6), rho %in% c(0, .75), h == 3, Z == 100) %>%
+  ggplot(aes(x = log(richness), y = log(stab_com), color = as.factor(rho))) +
+  geom_point(alpha = .3) +
+  geom_line(data = pred_data_show,
+    aes(x = richness, y = stab_com,
+      color = as.factor(rho),
+      linetype = as.factor(avg_int_strength),
+      alpha = as.factor(avg_int_strength))
+    ) +
+  scale_alpha_manual(values=c(1, 0), guide = "none") +
+  facet_grid(cols = vars(env_stoch), labeller = label_both) +
+  labs(
+    x = "Species richness (Log)", y = "Community stability (Log)",
+    color = "Environmental correlation"
+  ) +
+  theme_bw() +
+  theme(legend.position = "bottom")
+```
+
+```{r}
+leg_pred <- get_legend(p_pred_sr_int)
+p_sim_pred <- plot_grid(
+  plot_grid(
+    tar_read(p_stab_rich_env_rho) + theme(legend.position = "none"),
+    p_pred_sr_int + theme(legend.position = "none"),
+  labels = "auto"
+  ),
+  leg_pred,
+  nrow = 2,
+  rel_heights = c(1, .1)
+)
+ggsave(
+  here("report", "figures", "p_sim_pred.pdf"),
+  plot = p_sim_pred,
+  scale = 2.4,
+  width = 88,
+  height = 88 * .4,
+  units = "mm"
+)
+```
+
+```{r}
+p_pred_sr_int_async <- pred_data %>%
+  filter(
+    ct_alive %in% c(.1),
+    rho %in% c(0, .75),
+    Z == 10,
+    h %in% c(3),
+    avg_int_strength %in% c(.01, .1),
+    w_avg_tlvl == 1.5
+    ) %>%
+  ggplot(aes(
+      x = richness, y = async,
       color = as.factor(rho),
@@
       )) +
-  geom_line(linewidth = 2) +
+  geom_line(linewidth = 1) +
   facet_grid(cols = vars(env_stoch), labeller = label_both) +
   labs(
-    x = "Species richness (Log)", y = "Community stability (Log)",
+    x = "Species richness (Log)", y = "Asynchrony (Log)",
     linetype = "Avg. Interaction strength",
@@
 ggsave(
-  here("report", "figures", "p_pred_sr_int.png"),
-  plot = p_pred_sr_int,
+  here("report", "figures", "p_pred_sr_int_async.png"),
+  plot = p_pred_sr_int_async,
   scale = 2.4,
   width = 88,
-  height = 88 * 1,
+  height = 88 * .5,
   units = "mm"
@@
 ```{r}
-plot_grid(
-  tar_read(p_stab_rich_env_rho) + theme(legend.position = "none"),
-  p_pred_sr_int)
-```
-
-```{r}
-
+p_pred_sr_int_pop_stab <- pred_data %>%
+  filter(
+    ct_alive %in% c(.1),
+    rho %in% c(0, .75),
+    Z == 10,
+    h %in% c(3),
+    avg_int_strength %in% c(.01, .1),
+    w_avg_tlvl == 1.5
+    ) %>%
+  ggplot(aes(
+      x = richness, y = pop_stab,
+      color = as.factor(rho),
+      linetype = as.factor(avg_int_strength),
+      )) +
+  geom_line(linewidth = 1) +
+  facet_grid(cols = vars(env_stoch), labeller = label_both) +
+  labs(
+    x = "Species richness (Log)", y = "Population stability (Log)",
+    linetype = "Avg. Interaction strength",
+    color = "Environmental correlation"
+  ) +
+  theme_bw() +
+  theme(legend.position = "bottom")
+ggsave(
+  here("report", "figures", "p_pred_sr_int_pop_stab.png"),
+  plot = p_pred_sr_int_pop_stab,
+  scale = 2.4,
+  width = 88,
+  height = 88 * .5,
+  units = "mm"
+)
+```
+
+```{r}
 p_pred_sr_avg_tlvl_h <- pred_data %>%
   filter(
-    ct_alive %in% c(.3),
-    h %in% c(2,3),
-    rho %in% c(0, 1),
+    ct_alive %in% c(.1),
+    h == c(3),
+    rho %in% c(0, .75),
     Z == 10,
@@
     w_avg_tlvl == c(1.5, 3)) %>%
-  ggplot(aes(x = richness, y = stab_com, linewidth = as.factor(w_avg_tlvl), color = as.factor(h))) +
+  ggplot(aes(x = richness, y = stab_com,
+      linetype = as.factor(w_avg_tlvl), color = as.factor(rho))) +
   geom_line() +
-  facet_grid(cols = vars(env_stoch), rows = vars(rho), labeller = label_both) +
+  facet_grid(cols = vars(env_stoch), labeller = label_both) +
   theme_bw()

### 2023-10-11 paper/manuscript.Rmd
New plots

@@
 bibliography: references.bib
+header-includes:
+  - \usepackage[left]{lineno}
+  - \linenumbers
+  - \usepackage{setspace}\doublespacing
 ---
@@
 
+# IDEA, meeting with Sonia
+
+- Simplifying SEM in main text, move details to appendix
+- State diagram for stability - richness relationships along two food-web
+  metrics and panels varying response diversity.
+- Look at the french data for portefolio and compensatory dynamics effects.
+- Mid-October
+
+# Abstract
+
+Current biotic homogenization and increasing frequency of extreme events are
+projected to dramatically destabilize ecological communities. Understanding how
+complex communities such as food-webs respond to such threats is crucial to take
+adequate conservation measures. We then investigated how response diversity,
+environmental stochasticity, and food-web structure drive temporal stability of
+biomass in complex food-webs, using a stochastic bioenergetic food-web model. We
+found that higher average trophic level, omnivory degree and generalism
+increased  average population stability while species richness had little
+effects. At the opposite higher average trophic level, omnivory degree and
+generalism decreased asynchrony and compensatory dynamics raising trophic
+interactions. We further found that that high interaction strength drive
+negative stability-species richness when response diversity is low but that high
+response diversity always drive positive stability-richness relationship. Our
+study reveals that response diversity and food-web structure drive temporal
+stability and further improve our understanding of biodiversity-stability
+relationships in complex trophic communities.
+
 # Introduction
@@
 stability. However, the joint effects of external stressors such as
-environmental variabilityand internal stressors such as the
+environmental variability and internal stressors such as the
 loss response diversity has been rarely assessed in temporal stability areas.
@@
 
-```{r, fig.cap=concept_cap}
+```{r, eval = FALSE, fig.cap=concept_cap}
 knitr::include_graphics(here("report", "figures", "conceptual_figures.pdf"))

### 2023-10-11 R/plotting_methods.R

@@ -1,0 +1,3 @@
+ggsave_multiple <- function(fns, ...) {
+  map(fns, function(x) ggsave(x, ...))
+}

### 2023-10-11 R/string_replacements.R

@@ -36,8 +36,9 @@ var_replacement <- function() {
 }
 rho_replacement <- function() {
   c(
-    `0` = "Maximum",
+    `0` = "High",
     `0.5` = "Medium",
+    `0.75` = "Low",
     `1` = "No"
   )
 }

### 2023-10-11 _targets.Rmd
Compute stability-richness slope vs other variables

@@
 tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"))
-source(here::here("R", "network_metrics.R"))
-source(here::here("R", "string_replacements.R"))
-source(here::here("R", "stability_decomposition.R"))
-source(here::here("R", "model_helpers.R"))
-source(here::here("R", "sem_helpers.R"))
+# Load custom functions
+lapply(list.files(here::here("R"), full.names = TRUE), source)
 ```
@@
       kable_styling()
+  )
+)
+```
+
+```{targets simplified-sem}
+list(
+  tar_target(sem_simplified_model_list,
+    list(
+      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
+      richness = lm(richness ~ ct + S, sim_fw_sem),
+      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
+      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
+      avg_omnivory = lm(avg_omnivory ~ ct + S, sim_fw_sem),
+      avg_int_strength = lm(avg_int_strength ~ ct + S + h + Z, sim_fw_sem),
+      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h + Z, sim_fw_sem),
+      sae_total = lm(sae_total ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
+      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z + rho, sim_fw_sem),
+      async = lm(async ~ sae_total + cpe, sim_fw_sem),
+      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
+    )
+    ),
+  tar_target(sem_simplified, {
+    ti <- as.psem(sem_simplified_model_list)
+    update(ti, avg_omnivory %~~% w_avg_tlvl)
+    }
+    ),
+  tar_target(sem_simplified_coeff, {
+    ti <- summary(sem_simplified)$coefficients[, c(1, 2, 8, 9)]
+    colnames(ti)[4] <- "Signif"
+    ti
+    }),
+  tar_target(sem_simplified_collinearity,
+    map_dfr(setNames(sem_simplified_model_list, names(sem_simplified_model_list)),
+      performance::check_collinearity,
+      .id = "response") %>%
+    as_tibble),
+  tar_target(sem_simplified_rsquared,
+    map_dfr(sem_simplified_model_list, rsquared) %>%
+      mutate(Response = var_replacement()[Response]) %>%
+      select(Response, R.squared)
+    ),
+  tar_target(tab_sem_simplified_vif,
+    sem_simplified_collinearity %>%
+      mutate(
+        response = var_replacement()[response],
+        Term = var_replacement()[Term]
+        ) %>%
+      kable(
+        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
+      kable_styling()
+    ),
+  tar_target(tab_sem_simplified_rsquared,
+    sem_simplified_rsquared %>%
+      kable(caption = "Rsquared for the Structural Equation Model.") %>%
+      kable_styling()
+  )
+)
+```
+
+```{targets model-to-pred}
+list(
+  tar_target(model_fw_stab,
+    glmmTMB(formula_stab_fw_model(
+        rand_effect = TRUE,
+        term_to_del = "richness : rho : Z +"),
+      data = mutate(sim_fw, across(c(stab_com, richness), log))
+      )),
+  tar_target(model_fw_stab_scaled,
+    glmmTMB(formula_stab_fw_model(
+        rand_effect = TRUE,
+        term_to_del = "richness : rho : Z +"
+        ),
+      data = sim_fw %>%
+        select(-productivity) %>%
+        mutate(across(c(stab_com, richness), log)) %>%
+        mutate(across(c(sim_id, fw_id), as.factor)) %>%
+        mutate(
+          across(c(stab_com, richness,
+              env_stoch, rho, Z,
+              ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
+            ~scale(.x)[, 1])
+        )
+        )
+    ),
+  tar_target(model_fw_stab_scaled_coeff,
+    confint(tar_read(model_fw_stab_scaled), level = 0.95) %>%
+      as.data.frame() %>%
+      rownames_to_column("term") %>%
+      as_tibble() %>%
+      mutate(term = str_replace(term, "cond\\.", ""))
+    ),
+  tar_target(pred_data, {
+    to <- list(
+      richness = log(seq(1, 30, 1)),
+      ct_alive = c(.05, .10, .30),
+      rho = c(0, .75, 1),
+      avg_int_strength = c(.01, .02, .05, .1),
+      env_stoch = c(.1, .6),
+      w_avg_tlvl = c(1.5, 2, 3),
+      Z = c(10, 100),
+      h = c(2, 3),
+      fw_id = NA) %>% expand.grid()
+    ti <- predict(model_fw_stab,
+      se.fit = TRUE, re.form = NA,
+      newdata = to)
+    to$stab_com <- ti$fit
+    to$stab_com_se <- ti$se.fit
+    to$resp_div <- rho_replacement()[as.character(to$rho)]
+    to
+    }),
+  tar_target(fix_fw_stab, fixef(model_fw_stab)$cond),
+  tar_target(pred_sr_rho_int,
+    list(
+      rho = seq(0, 1, .02),
+      avg_int_strength = seq(0.01, 0.2, .01)
+      ) %>%
+    expand.grid() %>%
+    mutate(
+      slope_richness = map2_dbl(rho, avg_int_strength,
+        ~get_slope_change(
+          coeff = fix_fw_stab,
+          gen_term = "richness",
+          coeff_values = c(
+            "rho" = .x,
+            "env_stoch" = .1,
+            "ct_alive" = .2,
+            "avg_int_strength" = .y,
+            "h" = 2,
+            "w_avg_tlvl" = 1.5,
+            "Z" = 100
+          )
+        )
+      )
+    )
   )
@@
 library(ggcorrplot)
-source(here::here("R", "network_metrics.R"))
-source(here::here("R", "string_replacements.R"))
-source(here::here("R", "stability_decomposition.R"))
-source(here::here("R", "model_helpers.R"))
-```
+lapply(list.files(here::here("R"), full.names = TRUE), source)
+```
+
+```{r}
+
+# plot just the interactions
+# TODO: order by values
+ti %>%
+  filter(str_detect(term, ":")) %>%
+  ggplot(aes(x = Estimate, y = term)) +
+  geom_point()
+```
+```{r}
+p_pred_sr_rho_int <- tar_read(pred_sr_rho_int) %>%
+  ggplot(aes(x = rho, y = avg_int_strength)) +
+  geom_raster(aes(fill = slope_richness)) +
+  scale_fill_gradient2(
+    low = "red",
+    mid = "white",
+    high = "blue",
+    midpoint = 0,
+    space = "Lab",
+    na.value = "grey50",
+    guide = "colourbar",
+    aesthetics = "fill") +
+  labs(
+    x = "Environmental correlation",
+    y = "Avg interaction strength",
+    fill = "Slope Stability-Richness"
+  ) +
+theme(legend.position = "bottom")
+ggsave(
+  here("paper", "figures", "p_pred_sr_rho_int.pdf"),
+  plot = p_pred_sr_rho_int,
+  scale = 2.4,
+  width = 88,
+  height = 88 * 1,
+  units = "mm"
+)
+
+```
+
+```{r}
+tar_load(pred_data)
+pred_data %>%
+  filter(
+    ct_alive %in% c(.1),
+    rho %in% c(0, .75),
+    richness >= 1,
+    Z == 10,
+    h %in% c(3),
+    avg_int_strength %in% c(.01, .1),
+    w_avg_tlvl == 1.5
+    ) %>%
+  ggplot(aes(
+      x = richness, y = stab_com,
+      color = as.factor(resp_div),
+      linetype = as.factor(avg_int_strength),
+      alpha = as.factor(avg_int_strength)
+      )) +
+  ylim(2, 8) +
+  geom_line(linewidth = 1) +
+  scale_alpha_manual(values=c(1, 1), guide = "none") +
+  facet_grid(cols = vars(env_stoch), labeller = label_both) +
+  labs(
+    x = "Species richness (Log)", y = "Community stability (Log)",
+    linetype = "Avg. Interaction strength",
+    color = "Response diversity"
+  ) +
+  theme_bw() +
+  theme(legend.position = "bottom")
+
+#pred_data$async <- predict(mod_tot_async, newdata = pred_data)
+#pred_data$pop_stab <- predict(mod_tot_pop_stab, newdata = pred_data)
+```
+
+## Simplified SEM
+
+simplified SEM for main text
+
+```{r}
+tar_read(sem_simplified_coeff)
+```
+
+```{r}
+tar_load(sim_fw)
+colnames(sim_fw)
+length(unique(sim_fw$fw_id))
+```
+
+## Modelling interaction between stability and food-web structure
+
+```{r}
+model_fw_stab <- glmmTMB(formula_stab_fw_model(
+    rand_effect = TRUE,
+    term_to_del = "richness : rho : Z +"),
+  data = mutate(sim_fw, across(c(stab_com, richness), log))
+)
+diagnose(model_fw_stab)
+
+model_fw_stab_scaled <- glmmTMB(formula_stab_fw_model(rand_effect = TRUE),
+  data = sim_fw %>%
+    select(-productivity) %>%
+    mutate(across(c(stab_com, richness), log)) %>%
+    mutate(across(c(sim_id, fw_id), as.factor)) %>%
+    mutate(
+      across(c(stab_com, richness,
+          env_stoch, rho, Z,
+          ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
+        ~scale(.x)[,1])
+    )
+)
+fixef(model_fw_stab_scaled)
+diagnose(model_fw_stab_scaled)
+```
+
+```{r}
+mod_tot <- lm(stab_com ~
+  richness + rho + env_stoch +
+  ct_alive + w_avg_tlvl + Z +
+  avg_int_strength +
+  h +
+  richness * rho +
+  richness * env_stoch +
+  richness * ct_alive +
+  richness * avg_int_strength +
+  richness * h +
+  richness * w_avg_tlvl +
+  richness * Z +
+  richness * rho * ct_alive +
+  richness * rho * w_avg_tlvl +
+  richness * rho * avg_int_strength +
+  richness * rho * h +
+  richness * rho * Z +
+  richness * env_stoch * ct_alive +
+  richness * env_stoch * Z +
+  richness * env_stoch * avg_int_strength +
+  richness * env_stoch * h +
+  richness * env_stoch * w_avg_tlvl,
+  mutate(sim_fw, across(c(stab_com, richness), log)) #, richness
+  )
+```
+
+##
 
@@
   filter(
-    rho %in% c(0), productivity == 5, env_stoch == .5
+    rho %in% c(0), env_stoch == .3
     ) %>%
@@
   filter(
-    rho %in% c(0), productivity == 5, env_stoch == .5,
-    Z == 500
-    ) %>%
+    rho %in% c(0), env_stoch == .3, Z == 25) %>%
   pivot_longer(c(stab_com, async, sae_total, cpe,
@@
   geom_boxplot() +
-  labs(x = "Connectance", y = "Asynchrony component") +
+  labs(x = "Species richness", y = "Asynchrony component") +
   facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
@@
 sim_sp %>%
-  filter(env_stoch == .3, rho == 1, Z == 100) %>%
+  filter(env_stoch == .4, rho == 1, Z == 100) %>%
   ggplot(aes(x = tlvl, y = log(cv_sp))) +
@@
   here("report", "figures", "p_pred_sr_avg_tlvl_h.png"),
-  plot = p_pred_sr_avg_tlvl,
+  plot = p_pred_sr_avg_tlvl_h,
   scale = 2.4,
@@
 
-```{r}
-tar_load(sim_fw_sem)
-sim_fw_sem %<>% mutate(richness = sqrt(richness))
-ti <- as.psem(sem_model_list)
-update(ti, avg_omnivory %~~% w_avg_tlvl)
-sem_coeff <- summary(ti)$coefficients[, c(1, 2, 8, 9)]
-map_dfr(sem_model_list, rsquared) %>%
-      mutate(Response = var_replacement()[Response]) %>%
-      select(Response, R.squared)
-```
-
-```{r}
-sem_model_list <- list(
-      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
-      richness = lm(richness ~ ct + S, sim_fw_sem),
-      #max_tlvl = lm(max_tlvl ~ ct + S, sim_fw_sem),
-      #w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
-      #avg_omnivory = lm(avg_omnivory ~ ct + S, sim_fw_sem),
-      avg_int_strength = lm(avg_int_strength ~ ct + S + h + Z, sim_fw_sem),
-      pop_stab = lm(pop_stab ~ richness + avg_int_strength + ct_alive + env_stoch, sim_fw_sem),
-      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + ct_alive, sim_fw_sem),
-      sae_even = lm(sae_even ~ richness, sim_fw_sem),
-      cpe_int = lm(cpe_int ~ richness + avg_int_strength + ct_alive, sim_fw_sem),
-      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_sem),
-      async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_sem),
-      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
-    )
-ti <- as.psem(sem_model_list)
-update(ti, avg_omnivory %~~% w_avg_tlvl)
-sem_coeff <- summary(ti)$coefficients[, c(1, 2, 8, 9)]
-map_dfr(sem_model_list, rsquared) %>%
-      mutate(Response = var_replacement()[Response]) %>%
-      select(Response, R.squared)
-```
-
 The `targets` dependency graph helps your readers understand the steps of your pipeline at a high level.

### 2023-10-11 R/model_helpers.R

@@ -1,3 +1,85 @@
+formula_stab_fw_model <- function(
+  resp = "stab_com",
+  rand_effect = TRUE,
+  term_to_del = "richness : rho : Z +"
+  ) {
+
+  fixed_part <- "richness + rho + env_stoch +
+  ct_alive + w_avg_tlvl + Z +
+  avg_int_strength +
+  h +
+  richness : rho +
+  richness : env_stoch +
+  richness : ct_alive +
+  richness : avg_int_strength +
+  richness : h +
+  richness : w_avg_tlvl +
+  richness : Z +
+  richness : rho : ct_alive +
+  richness : rho : w_avg_tlvl +
+  richness : rho : avg_int_strength +
+  richness : rho : h +
+  richness : rho : Z +
+  richness : env_stoch : ct_alive +
+  richness : env_stoch : Z +
+  richness : env_stoch : avg_int_strength +
+  richness : env_stoch : h +
+  richness : env_stoch : w_avg_tlvl"
+
+  if (rand_effect) {
+   rand_part <- "+\n (1|fw_id)"
+  } else {
+   rand_part <- ""
+  }
+
+  form <- paste0(resp, " ~\n", fixed_part, rand_part)
+  if (!is.null(term_to_del)) {
+    form <- str_remove(form, term_to_del)
+  }
+  as.formula(form)
+
+}
+
+get_slope_change <- function(
+  coeff = fix_fw_stab,
+  gen_term = "richness",
+  coeff_values = NULL
+    ) {
+
+  term <- coeff[str_detect(names(coeff), gen_term)]
+  term
+
+  # Get unique term varying with gen_term
+  co_varying <- unique(unlist(str_split(names(term), ":")))
+  co_varying <- co_varying[!str_detect(co_varying, gen_term)]
+
+  if (!all(co_varying %in% names(coeff_values))) {
+    coeff_notin <- co_varying[which(!co_varying %in% names(coeff_values))]
+    warning(cat("The coefficients:", coeff_notin, "are not controlled for.\n"))
+  }
+
+  # Map over coefficients
+  tu <- map_dbl(names(term),
+    function(x) {
+      # Extract control variables present in each coefficients:
+      my_pattern <- paste0("\\b", names(coeff_values), "\\b")
+      detected_ctrl_var <- coeff_values[str_detect(x, my_pattern)]
+
+      if (length(detected_ctrl_var) == 0) {
+        # if no match, return the coefficient
+        out <- term[x]
+      } else {
[…]

### 2023-10-12 _targets.Rmd
Compute interaction plots + make simplified SEM fig

@@
       w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
-      avg_omnivory = lm(avg_omnivory ~ ct + S, sim_fw_sem),
-      avg_int_strength = lm(avg_int_strength ~ ct + S + h + Z, sim_fw_sem),
-      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h + Z, sim_fw_sem),
-      sae_total = lm(sae_total ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
-      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z + rho, sim_fw_sem),
+      avg_omnivory = lm(avg_omnivory ~ ct + S + Z, sim_fw_sem),
+      avg_int_strength = lm(avg_int_strength ~ ct + S + Z, sim_fw_sem),
+      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_sem),
+      sae_total = lm(sae_total ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_sem),
+      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + rho, sim_fw_sem),
       async = lm(async ~ sae_total + cpe, sim_fw_sem),
@@
     list(
-      rho = seq(0, 1, .02),
-      avg_int_strength = seq(0.01, 0.2, .01)
+      rho = seq(0, 1, length.out = 50),
+      avg_int_strength = seq(0.01, 0.2, length.out = 50)
       ) %>%
@@
             "w_avg_tlvl" = 1.5,
-            "Z" = 100
-          )
-        )
-      )
+            "Z" = 100))))),
+  tar_target(pred_sr_rho_tlvl,
+    list(
+      rho = seq(0, 1, length.out = 50),
+      w_avg_tlvl = seq(1.5, 3.5, length.out = 50)
+      ) %>%
+    expand.grid() %>%
+    mutate(
+      slope_richness = map2_dbl(rho, w_avg_tlvl,
+        ~get_slope_change(
+          coeff = fix_fw_stab,
+          gen_term = "richness",
+          coeff_values = c(
+            "rho" = .x,
+            "env_stoch" = .1,
+            "ct_alive" = .2,
+            "avg_int_strength" = .01,
+            "h" = 2,
+            "w_avg_tlvl" = .y,
+            "Z" = 100))))),
+  tar_target(pred_sr_rho_ct,
+    list(
+      rho = seq(0, 1, length.out = 50),
+      ct_alive = seq(.02, .3, length.out = 50)
+      ) %>%
+    expand.grid() %>%
+    mutate(
+      slope_richness = map2_dbl(rho, ct_alive,
+        ~get_slope_change(
+          coeff = fix_fw_stab,
+          gen_term = "richness",
+          coeff_values = c(
+            "rho" = .x,
+            "env_stoch" = .1,
+            "ct_alive" = .y,
+            "avg_int_strength" = .01,
+            "h" = 2,
+            "w_avg_tlvl" = 1.5,
+            "Z" = 100))))),
+  tar_target(pred_sr_rho,
+    map_dfr(list(pred_sr_rho_int, pred_sr_rho_ct, pred_sr_rho_tlvl),
+      ~.x %>%
+         pivot_longer(2, names_to = "variable", values_to = "values")
    )
@@
 
-```{r}
+```{r tar-make}
 tar_make()
@@
 ```{r}
-
-# plot just the interactions
-# TODO: order by values
-ti %>%
-  filter(str_detect(term, ":")) %>%
-  ggplot(aes(x = Estimate, y = term)) +
-  geom_point()
-```
+tar_load(model_fw_stab_scaled_coeff)
+
+pattern <- c(var_replacement(), get_term_replacement())
+names(pattern) <- paste0("\\b", names(pattern), "\\b")
+```
+
+```{r}
+model_fw_stab_scaled_coeff %>%
+  rename(lower_ci = `2.5 %`, upper_ci = `97.5 %`) %>%
+  rename_with(tolower) %>%
+  filter(!str_detect(term, "(Intercept)")) %>%
+  mutate(
+    type = ifelse(str_detect(term, ":"), "interaction", "single"),
+    term = str_replace_all(term, pattern)
+    ) %>%
+  filter(type == "interaction") %>%
+  ggplot(aes(x = estimate, y = term, xmin = lower_ci, xmax = upper_ci)) +
+  geom_vline(xintercept = 0, linetype = "dashed") +
+  geom_pointrange() +
+  labs(x = "Standardised coefficients") +
+  theme_bw() +
+  theme(axis.title.y = element_blank())
+```
+
+```{r}
+tar_load(fix_fw_stab)
+```
+
+```{r}
+pred_sr_rho_tlvl %>%
+  ggplot(aes(x = rho, y = w_avg_tlvl)) +
+  geom_raster(aes(fill = slope_richness)) +
+  scale_fill_gradient2(
+    low = "red",
+    mid = "white",
+    high = "blue",
+    midpoint = 0,
+    space = "Lab",
+    na.value = "grey50",
+    guide = "colourbar",
+    aesthetics = "fill") +
+  labs(
+    x = "Environmental correlation",
+    y = "Avg trophic level",
+    fill = "Slope Stability-Richness"
+  ) +
+theme(legend.position = "bottom")
+```
+
+```{r}
+tar_load(pred_sr_rho)
+p_pred_sr_rho <- pred_sr_rho %>%
+  mutate(variable = var_replacement()[variable]) %>%
+  ggplot(aes(x = rho, y = values, fill = slope_richness)) +
+  geom_raster() +
+  facet_wrap(~variable, scales = "free_y") +
+  coord_cartesian(expand = FALSE) +
+  scale_fill_gradient2(
+    low = "red",
+    mid = "white",
+    high = "blue",
+    midpoint = 0,
+    space = "Lab",
+    na.value = "grey50",
+    guide = "colourbar",
+    aesthetics = "fill") +
+  labs(
+    x = "Environmental correlation",
+    y = "Food-web structure",
+    fill = "Slope Stability-Richness"
+    ) +
+  theme(legend.position = "bottom")
+ggsave_multiple(
+  paste0("p_pred_sr_rho", c(".png", ".pdf")),
+  plot = p_pred_sr_rho,
+  path = here::here("report", "figures"),
+  scale = 2.2,
+  dpi = 400,
+  width = 88,
+  height = 88 * .45,
+  units = "mm")
+```
+
+```{r}
+pred_sr_rho_ct %>%
+  ggplot(aes(x = rho, y = ct_alive)) +
+  geom_raster(aes(fill = slope_richness)) +
+  scale_fill_gradient2(
+    low = "red",
+    mid = "white",
+    high = "blue",
+    midpoint = 0,
+    space = "Lab",
+    na.value = "grey50",
+    guide = "colourbar",
+    aesthetics = "fill") +
+  labs(
+    x = "Environmental correlation",
+    y = "Avg trophic level",
+    fill = "Slope Stability-Richness"
+  ) +
+theme(legend.position = "bottom")
+```
+
 ```{r}
@@
 ```{r}
-tar_read(sem_simplified_coeff)
-```
-
-```{r}
-tar_load(sim_fw)
-colnames(sim_fw)
-length(unique(sim_fw$fw_id))
+tar_read(sem_simplified_coeff) %>%
+  filter(abs(Std.Estimate) > .1) %>%
+  janitor::clean_names() %>%
+  mutate(std_estimate = round(std_estimate, 1))
+tar_read(sem_simplified_rsquared) %>%
+  janitor::clean_names() %>%
+  mutate(r_squared = round(r_squared, 2))
 ```
@@
 ## Modelling interaction between stability and food-web structure
-
-```{r}
-model_fw_stab <- glmmTMB(formula_stab_fw_model(
-    rand_effect = TRUE,
-    term_to_del = "richness : rho : Z +"),
-  data = mutate(sim_fw, across(c(stab_com, richness), log))
-)
-diagnose(model_fw_stab)
-
-model_fw_stab_scaled <- glmmTMB(formula_stab_fw_model(rand_effect = TRUE),
-  data = sim_fw %>%
-    select(-productivity) %>%
-    mutate(across(c(stab_com, richness), log)) %>%
-    mutate(across(c(sim_id, fw_id), as.factor)) %>%
-    mutate(
-      across(c(stab_com, richness,
-          env_stoch, rho, Z,
-          ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
-        ~scale(.x)[,1])
-    )
-)
-fixef(model_fw_stab_scaled)
-diagnose(model_fw_stab_scaled)
-```
-
-```{r}
-mod_tot <- lm(stab_com ~
-  richness + rho + env_stoch +
-  ct_alive + w_avg_tlvl + Z +
-  avg_int_strength +
-  h +
-  richness * rho +
-  richness * env_stoch +
-  richness * ct_alive +
-  richness * avg_int_strength +
-  richness * h +
-  richness * w_avg_tlvl +
-  richness * Z +
-  richness * rho * ct_alive +
-  richness * rho * w_avg_tlvl +
-  richness * rho * avg_int_strength +
-  richness * rho * h +
-  richness * rho * Z +
-  richness * env_stoch * ct_alive +
-  richness * env_stoch * Z +
-  richness * env_stoch * avg_int_strength +
-  richness * env_stoch * h +
-  richness * env_stoch * w_avg_tlvl,
-  mutate(sim_fw, across(c(stab_com, richness), log)) #, richness
-  )
-```
-
-##
 

### 2023-10-12 R/string_replacements.R

@@ -11,29 +11,34 @@ var_replacement <- function() {
     log_async = "Asynchrony",
     async = "Asynchrony",
     cpe = "Compensatory effect",
-    cpe_int = "Comp. effect (Interaction)",
-    cpe_env = "Comp. effect (Environment)",
-    sae_total = "Stat. Avg. effect",
-    sae_even = "Stat. Avg. effect (Even)",
-    evenness_sae = "Stat. Avg. effect (Evenness)",
-    log1_avg_max_int_alive = "Interaction strength",
+    cpe_int = "Comp effect (Interaction)",
+    cpe_env = "Comp effect (Environment)",
+    sae_total = "Stat Avg effect",
+    sae_even = "Stat Avg effect (Even)",
+    evenness_sae = "Stat Avg effect (Evenness)",
+    log1_avg_max_int_alive = "Avg interaction strength",
     avg_max_int_alive = "Avg interaction strength",
-    avg_int_strength = "Avg interaction",
+    avg_int_strength = "Avg interaction strength",
     sd_max_int_alive = "SD interaction strength",
     w_avg_tlvl_alive = "Avg trophic level",
     ct_alive = "Connectance",
-    max_tlvl = "Max. trophic level",
-    w_avg_tlvl = "Avg. trophic level",
-    avg_omnivory = "Avg. omnivory",
+    max_tlvl = "Max trophic level",
+    w_avg_tlvl = "Avg trophic level",
+    avg_omnivory = "Avg omnivory",
     log_richness = "Richness",
     richness = "Richness",
     rho = "Env Corr",
     productivityenrichment = "Enrichment",
     env_stoch = "Env variance",
     Z = "PPMR",
-    h = "FR type"
+    h = "Hill exponent"
   )
 }
+
+get_term_replacement <- function() {
+  c(":" = " x\n")
+}
+
 rho_replacement <- function() {
   c(
     `0` = "High",

### 2023-10-12 _targets.Rmd
Compute stability component models

@@
       )),
+  tar_target(stab_com_part_var, c("stab_com", "pop_stab", "async")),
+  tar_target(model_fw_stab_comp,
+    tibble(
+      response = stab_com_part_var,
+      model = list(glmmTMB(formula_stab_fw_model(
+      resp = stab_com_part_var,
+      rand_effect = TRUE,
+      term_to_del = "richness : rho : Z +"),
+      data = mutate(sim_fw,
+      across(c(stab_com, pop_stab, async, richness), log)
+      ))
+        )),
+        pattern = stab_com_part_var
+  ),
   tar_target(model_fw_stab_scaled,
@@
         )
+    ),
+  tar_target(model_fw_stab_comp_scaled,
+    tibble(
+      response = stab_com_part_var,
+      model = list(glmmTMB(formula_stab_fw_model(
+        resp = stab_com_part_var,
+        rand_effect = TRUE,
+        term_to_del = "richness : rho : Z +"
+        ),
+      data = sim_fw %>%
+        select(-productivity) %>%
+        mutate(across(c(stab_com, richness), log)) %>%
+        mutate(across(c(sim_id, fw_id), as.factor)) %>%
+        mutate(
+          across(c(stab_com, pop_stab, async, richness,
+              env_stoch, rho, Z, h,
+              ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
+            ~scale(.x)[, 1])
+        )
+        ))),
+        pattern = stab_com_part_var
+  ),
+  tar_target(model_fw_stab_comp_scaled_coeff,
+    model_fw_stab_comp_scaled %>%
+      mutate(
+        coeff = map(model, function(x) {
+          confint(x, level = 0.95) %>%
+          as.data.frame() %>%
+          rownames_to_column("term") %>%
+          as_tibble() %>%
+          mutate(term = str_replace(term, "cond\\.", ""))
+        })
+      ) %>%
+      select(-model)
   ),
@@
   tar_target(fix_fw_stab, fixef(model_fw_stab)$cond),
+  tar_target(fix_fw_stab_comp,
+    model_fw_stab_comp %>%
+      mutate(
+      fix_effect = map(model, ~fixef(.x)$cond)
+      ) %>%
+      select(-model)
+  ),
   tar_target(pred_sr_rho_int,
@@
 tar_load(fix_fw_stab)
-```
-
-```{r}
-pred_sr_rho_tlvl %>%
-  ggplot(aes(x = rho, y = w_avg_tlvl)) +
-  geom_raster(aes(fill = slope_richness)) +
-  scale_fill_gradient2(
-    low = "red",
-    mid = "white",
-    high = "blue",
-    midpoint = 0,
-    space = "Lab",
-    na.value = "grey50",
-    guide = "colourbar",
-    aesthetics = "fill") +
-  labs(
-    x = "Environmental correlation",
-    y = "Avg trophic level",
-    fill = "Slope Stability-Richness"
-  ) +
-theme(legend.position = "bottom")
 ```
@@
 ```{r}
-pred_sr_rho_ct %>%
-  ggplot(aes(x = rho, y = ct_alive)) +
-  geom_raster(aes(fill = slope_richness)) +
-  scale_fill_gradient2(
-    low = "red",
-    mid = "white",
-    high = "blue",
-    midpoint = 0,
-    space = "Lab",
-    na.value = "grey50",
-    guide = "colourbar",
-    aesthetics = "fill") +
-  labs(
-    x = "Environmental correlation",
-    y = "Avg trophic level",
-    fill = "Slope Stability-Richness"
-  ) +
-theme(legend.position = "bottom")
-```
-
-```{r}
-p_pred_sr_rho_int <- tar_read(pred_sr_rho_int) %>%
-  ggplot(aes(x = rho, y = avg_int_strength)) +
-  geom_raster(aes(fill = slope_richness)) +
-  scale_fill_gradient2(
-    low = "red",
-    mid = "white",
-    high = "blue",
-    midpoint = 0,
-    space = "Lab",
-    na.value = "grey50",
-    guide = "colourbar",
-    aesthetics = "fill") +
-  labs(
-    x = "Environmental correlation",
-    y = "Avg interaction strength",
-    fill = "Slope Stability-Richness"
-  ) +
-theme(legend.position = "bottom")
-ggsave(
-  here("paper", "figures", "p_pred_sr_rho_int.pdf"),
-  plot = p_pred_sr_rho_int,
-  scale = 2.4,
-  width = 88,
-  height = 88 * 1,
-  units = "mm"
-)
-
-```
-
-```{r}
 tar_load(pred_data)
@@
   geom_line(linewidth = 1) +
-  scale_alpha_manual(values=c(1, 1), guide = "none") +
+  scale_alpha_manual(values = c(1, 1), guide = "none") +
   facet_grid(cols = vars(env_stoch), labeller = label_both) +

### 2023-10-13 _targets.Rmd
Compute slope richness for async and pop_stab

@@
     )
+    ),
+  tar_target(pred_stab_comp_rho,
+    fix_fw_stab_comp %>%
+      left_join(
+        list(
+          response = fix_fw_stab_comp$response,
+          variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive")
+          ) %>%
+        expand.grid() %>%
+        left_join(
+          tibble(
+            variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive"),
+            values = list(
+              seq(0.01, 0.2, length.out = 50),
+              seq(1.5, 3.5, length.out = 50),
+              seq(.02, .3, length.out = 50)
+            )
+          )
+        )
+        ) %>%
+    mutate(slope = pmap(
+        list(
+          param_name = variable,
+          param_values = values,
+          coeff = fix_effect
+          ),
+        function(param_name, param_values, coeff) {
+          param <- list(
+            seq(0, 1, length.out = length(param_values)),
+            param_values
+          )
+          names(param) <- c("rho", param_name)
+
+          encaps_get_slope_change(
+            param_list = param,
+            coeff_data = coeff,
+            slope_term = "richness",
+            default_variable_values = c(
+              "rho" = 0,
+              "env_stoch" = .1,
+              "ct_alive" = .2,
+              "avg_int_strength" = .01,
+              "h" = 2,
+              "w_avg_tlvl" = 1.5,
+              "Z" = 100
+            )
+          )
+        }
+        )
+    ) %>%
+    select(-fix_effect, -values)
   )
@@
 ```{r}
-tar_load(model_fw_stab_scaled_coeff)
+tar_load(fix_fw_stab)
+tar_load(fix_fw_stab_comp)
+
+```
+
+```{r}
+tar_load(model_fw_stab_comp_scaled_coeff)
 
@@
 ```{r}
-model_fw_stab_scaled_coeff %>%
+model_fw_stab_comp_scaled_coeff %>%
+  unnest(cols = c(coeff)) %>%
   rename(lower_ci = `2.5 %`, upper_ci = `97.5 %`) %>%
@@
   filter(type == "interaction") %>%
-  ggplot(aes(x = estimate, y = term, xmin = lower_ci, xmax = upper_ci)) +
+  ggplot(aes(
+      y = term, x = estimate,
+      xmin = lower_ci, xmax = upper_ci,
+      color = response)) +
   geom_vline(xintercept = 0, linetype = "dashed") +
@@
   theme(axis.title.y = element_blank())
+```
+
+```{r}
+p_model_fw_stab_com <- model_fw_stab_comp_scaled_coeff %>%
+  filter(response == "stab_com") %>%
+  unnest(cols = c(coeff)) %>%
+  rename(lower_ci = `2.5 %`, upper_ci = `97.5 %`) %>%
+  rename_with(tolower) %>%
+  filter(!str_detect(term, "(Intercept)")) %>%
+  mutate(
+    type = ifelse(str_detect(term, ":"), "interaction", "single"),
+    term = str_replace_all(term, pattern)
+    ) %>%
+  filter(type == "interaction") %>%
+  ggplot(aes(
+      y = term, x = estimate,
+      xmin = lower_ci, xmax = upper_ci
+      )) +
+  geom_vline(xintercept = 0, linetype = "dashed") +
+  geom_pointrange() +
+  labs(x = "Standardised coefficients") +
+  theme_bw() +
+  theme(axis.title.y = element_blank())
+ggsave_multiple(
+  paste0("p_model_fw_stab_com", c(".png", ".pdf")),
+  plot = p_model_fw_stab_com,
+  path = here::here("report", "figures"),
+  scale = 1.8,
+  dpi = 400,
+  width = 80,
+  height = 80 * 1.3,
+  units = "mm")
 ```

### 2023-10-13 R/model_helpers.R

@@ -121,3 +121,40 @@ plot_effect_type <- function(x) {
   p
 }
 
+encaps_get_slope_change <- function(
+  param_list = list(
+    rho = seq(0, 1, length.out = 50),
+    avg_int_strength = seq(0.01, 0.2, length.out = 50)
+    ),
+  coeff_data = fix_fw_stab,
+  slope_term = "richness",
+  default_variable_values = c(
+    "rho" = 0,
+    "env_stoch" = .1,
+    "ct_alive" = .2,
+    "avg_int_strength" = .01,
+    "h" = 2,
+    "w_avg_tlvl" = 1.5,
+    "Z" = 100)
+
+  ) {
+
+  param_df <- param_list %>%
+    expand.grid()
+  param_list_name <- names(param_list)
+  param_df$slope <- map2_dbl(
+    param_df[[param_list_name[1]]],
+    param_df[[param_list_name[2]]],
+    function(x, y) {
+      mask <- names(default_variable_values) %in% param_list_name
+      default_variable_values[mask] <- c(x, y)
+
+      get_slope_change(
+        coeff = coeff_data,
+        gen_term = slope_term,
+        coeff_values = default_variable_values
+      )
+    }
+  )
+  param_df
+}

### 2023-10-13 _targets.Rmd
Add sem total effect for simplified sem

@@
       kable_styling()
-  )
+  ),
+  tar_target(sem_simplified_eff_file, here::here("data", "sem_simplified_eff"), format = "file"),
+  tar_target(sem_simplified_eff, {
+    readRDS(sem_simplified_eff_file)
+    #semEff(sem_simplified, ci.type = "perc", R = 10, seed = 13, parallel = "no", data = sim_fw_sem)
+    }
+    ),
+  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
 )
@@
     select(-fix_effect, -values)
+  ),
+  tar_target(pred_stab_comp_rho_tbl,
+  pred_stab_comp_rho %>%
+  select(-variable) %>%
+  mutate(slope = map(slope,
+      ~pivot_longer(.x,
+        -c(rho, slope),
+        names_to = "variable",
+        values_to = "variable_values"
+      )
+    )
+  ) %>%
+  unnest(cols = slope)
+
   )
@@
 tar_load(fix_fw_stab_comp)
-
+tar_load(pred_stab_comp_rho)
+```
+
+```{r}
+tar_read(sem_simplified_eff_tab) %>%
+  filter(effect_type == "total") %>%
+  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
+  filter(!predictor %in% c("rho", "env_stoch","cpe", "sae_total", "evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async", "S", "ct")) %>%
+  mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
+  ggplot(aes(
+      x = predictor,
+      y = effect,
+      ymin = lower_ci,
+      ymax = upper_ci)
+    ) +
+  geom_pointrange() +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  facet_grid(cols = vars(response)) +
+  labs(x = "Predictor", y = "Total effect") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 20, hjust = 1))
+```
+
+```{r}
+cols <- c("Community stability" = "black", "Asynchrony" = "blue", "Population stability" = "darkgreen")
+alpha <- c("Community stability" = 1, "Asynchrony" = .3, "Population stability" = .3)
+
+p_sem_tot_stab <- tar_read(sem_simplified_eff_tab) %>%
+  filter(effect_type == "total") %>%
+  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
+  filter(!predictor %in% c("rho", "env_stoch","cpe", "sae_total", "evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async", "S", "ct")) %>%
+  mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
+  ggplot(aes(
+      y = predictor,
+      x = effect,
+      color = response,
+      alpha = response,
+      ymin = lower_ci,
+      ymax = upper_ci)
+    ) +
+  geom_pointrange() +
+  scale_colour_manual(values = cols) +
+  scale_alpha_manual(values = alpha) +
+  #geom_hline(yintercept = 0, linetype = "dashed") +
+  geom_vline(xintercept = 0, linetype = "dashed") +
+  #facet_grid(cols = vars(response)) +
+  labs(
+    x = "Total standardised effect",
+    color = "Stability component",
+    alpha = "Stability component"
+    ) +
+  theme_bw() +
+  theme(
+    axis.title.y = element_blank(),
+    legend.position = "bottom",
+    legend.justification = "right"
+  )
+ggsave_multiple(
+  paste0("p_sem_tot_stab", c(".png", ".pdf")),
+  plot = p_sem_tot_stab,
+  path = here::here("report", "figures"),
+  scale = 1.8,
+  dpi = 400,
+  width = 80,
+  height = 80 * 1.1,
+  units = "mm")
+```
+
+```{r}
+tar_load(pred_stab_comp_rho_tbl)
+p_pred_stab_comp_rho <-
+  pred_stab_comp_rho_tbl %>%
+  mutate(
+    response = var_replacement()[response],
+    variable = var_replacement()[variable],
+    ) %>%
+  ggplot(aes(x = rho, y = variable_values, fill = slope)) +
+  geom_raster() +
+  facet_grid(cols = vars(response), rows = vars(variable), scales = "free") +
+  coord_cartesian(expand = FALSE) +
+  scale_fill_gradient2(
+    low = "red",
+    mid = "white",
+    high = "blue",
+    midpoint = 0,
+    space = "Lab",
+    na.value = "grey50",
+    guide = "colourbar",
+    aesthetics = "fill") +
+  labs(
+    x = "Environmental correlation",
+    y = "Food-web structure",
+    fill = "Slope Stability-Richness"
+    ) +
+  theme_bw() +
+  theme(legend.position = "bottom")
+ggsave_multiple(
+  paste0("p_pred_stab_comp_rho", c(".png", ".pdf")),
+  plot = p_pred_stab_comp_rho,
+  path = here::here("report", "figures"),
+  scale = 2.0,
+  dpi = 400,
+  width = 80,
+  height = 80 * 1.1,
+  units = "mm")
 ```

### 2023-10-13 _targets.Rmd
Begin to update manuscript figures

@@
 ```{r}
+library(ggbreak)
 cols <- c("Community stability" = "black", "Asynchrony" = "blue", "Population stability" = "darkgreen")
 alpha <- c("Community stability" = 1, "Asynchrony" = .3, "Population stability" = .3)
-
 p_sem_tot_stab <- tar_read(sem_simplified_eff_tab) %>%
@@
   filter(response %in% c("async", "pop_stab", "stab_com")) %>%
-  filter(!predictor %in% c("rho", "env_stoch","cpe", "sae_total", "evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async", "S", "ct")) %>%
+  filter(!predictor %in% c("cpe", "sae_total", "evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async", "S", "ct")) %>%
   mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
@@
     axis.title.y = element_blank(),
-    legend.position = "bottom",
-    legend.justification = "right"
+    #legend.justification = "right",
+    legend.position = "bottom"
+  ) +
+  scale_x_break(c(-0.3, -0.6))
+p_sem_tot_stab_leg <- plot_grid(
+  print(p_sem_tot_stab + theme(legend.position = "none")),
+  get_legend(p_sem_tot_stab),
+  nrow = 2,
+  rel_heights = c(1, .05)
 )
@@
   paste0("p_sem_tot_stab", c(".png", ".pdf")),
-  plot = p_sem_tot_stab,
+  plot = print(p_sem_tot_stab_leg),
   path = here::here("report", "figures"),
@@
   width = 80,
-  height = 80 * 1.1,
+  height = 80 * .7,
   units = "mm")
@@
   units = "mm")
+```
+
+```{r}
 ```

### 2023-10-13 paper/manuscript.Rmd
Begin to update manuscript figures

@@
 ```{r, results = FALSE}
-
 sapply(c("targets", "tidyverse", "magrittr", "cowplot", "here", "piecewiseSEM", "semEff", "ggcorrplot", "kableExtra"), require, character.only = TRUE)
@@
 ```{r}
-sem_cap <- paste0("Structural equation model. Only standardized coefficients
-  whose absolute values are superior to 0.1 are displayed. [To complete with the links from initial structure]")
+sem_cap <- paste0(
+  "Structural Equation Model linking initial model parameters to resulting
+  temporal stability of biomass. Arrows display positive (continuous) and
+  negative (dashed) standardised effects. Initial parameters were initial
+  species richness, initial connectance, Prey-Predator Mass Ration (PPMR), hill
+  exponent, variance of stochastic mortality rates (Env. stochasticity), and
+  cross-correlation among species mortality rates (Env. correlation). We only
+  displayed standardised coefficients whose absolute values are superior to 0.1
+  are displayed. SEM containing containing further partition of Statistical
+  Averaging Effect and Compensatory effects is displayed in Fig. SXX.")
 ```
@@
 ```{r sem, fig.cap=sem_cap}
-knitr::include_graphics(here("report", "figures", "sem_stab2.pdf"))
+knitr::include_graphics(here("report", "figures", "sem_stab_simplified.pdf"))
 ```
@@
 ```{r}
-tar_load(sem_eff_tab)
+#TODO: change most of it for simplified SEM
+tar_load(c(sem_eff_tab, sem_simplified_eff_tab))
 
-get_eff <- function(y = "pop_stab", x = "richness", d = 2, effect_type = "direct") {
-  mask <- sem_eff_tab$response == y & sem_eff_tab$predictor == x &
-    sem_eff_tab$effect_type == effect_type
-  round(sem_eff_tab[mask, ]$effect, d)
+get_eff <- function(y = "pop_stab", x = "richness", d = 2, effect_type = "direct", tab = sem_eff_tab) {
+  mask <- tab$response == y & tab$predictor == x &
+    tab$effect_type == effect_type
+  round(tab[mask, ]$effect, d)
 }
@@
 ```{r}
-semtot_cap <- "Total effect of food-web structure and stressors on community
-stability, asynchony, and population stability. The total effects were derived
-from the structural equation model."
+semtot_cap <- "Total effect of food-web structure on community stability,
+asynchony, and population stability. The total effects were derived from the
+structural equation model."
 ```
@@
 ```{r semtot, fig.cap = semtot_cap}
-tar_read(p_sem_tot_stab)
+knitr::include_graphics(here::here("report", "figures", "p_sem_tot_stab.png"))
 ```

### 2023-10-16 _targets.Rmd
Update manuscript figures and SEM results

@@
             "rho" = .x,
-            "env_stoch" = .1,
+            "env_stoch" = .3,
             "ct_alive" = .y,
@@
             "h" = 2,
-            "w_avg_tlvl" = 1.5,
+            "w_avg_tlvl" = 2.0,
             "Z" = 100))))),
@@
         pivot_longer(2, names_to = "variable", values_to = "values")
+    )
+    ),
+  tar_target(default_variable_values_pred,
+    c(
+      "rho" = 0,
+      "env_stoch" = .3,
+      "ct_alive" = .2,
+      "avg_int_strength" = .01,
+      "h" = 2,
+      "w_avg_tlvl" = 2,
+      "Z" = 100
     )
@@
             slope_term = "richness",
-            default_variable_values = c(
-              "rho" = 0,
-              "env_stoch" = .1,
-              "ct_alive" = .2,
-              "avg_int_strength" = .01,
-              "h" = 2,
-              "w_avg_tlvl" = 1.5,
-              "Z" = 100
-            )
+            default_variable_values = default_variable_values_pred
           )
@@
     ) %>%
-    select(-fix_effect, -values)
-  ),
-  tar_target(pred_stab_comp_rho_tbl,
-  pred_stab_comp_rho %>%
+    select(-fix_effect, -values) %>%
     select(-variable) %>%
@@
   unnest(cols = slope)
-
   )
@@
 ```{r}
-tar_load(pred_stab_comp_rho_tbl)
+tar_load(pred_stab_comp_rho)
 p_pred_stab_comp_rho <-
-  pred_stab_comp_rho_tbl %>%
+  pred_stab_comp_rho %>%
   mutate(
@@
 ```{r}
-p_model_fw_stab_com <- model_fw_stab_comp_scaled_coeff %>%
+p_model_fw_stab_com_int <- model_fw_stab_comp_scaled_coeff %>%
   filter(response == "stab_com") %>%
@@
 ggsave_multiple(
-  paste0("p_model_fw_stab_com", c(".png", ".pdf")),
-  plot = p_model_fw_stab_com,
+  paste0("p_model_fw_stab_com_int", c(".png", ".pdf")),
+  plot = p_model_fw_stab_com_int,
   path = here::here("report", "figures"),
@@
 ```{r}
+p_model_fw_stab_com_single <- model_fw_stab_comp_scaled_coeff %>%
+  filter(response == "stab_com") %>%
+  unnest(cols = c(coeff)) %>%
+  rename(lower_ci = `2.5 %`, upper_ci = `97.5 %`) %>%
+  rename_with(tolower) %>%
+  filter(!str_detect(term, "(Intercept)")) %>%
+  mutate(
+    type = ifelse(str_detect(term, ":"), "interaction", "single"),
+    term = str_replace_all(term, pattern)
+    ) %>%
+  filter(type == "single") %>%
+  ggplot(aes(
+      y = term, x = estimate,
+      xmin = lower_ci, xmax = upper_ci
+      )) +
+  geom_vline(xintercept = 0, linetype = "dashed") +
+  geom_pointrange() +
+  labs(x = "Standardised coefficients") +
+  theme_bw() +
+  theme(axis.title.y = element_blank())
+p_model_fw_stab_com <- plot_grid(
+  p_model_fw_stab_com_int,
+  plot_grid(p_model_fw_stab_com_single, NULL, nrow = 2),
+  ncol = 2,
+  labels = "auto"
+)
+ggsave_multiple(
+  paste0("p_model_fw_stab_com", c(".png", ".pdf")),
+  plot = p_model_fw_stab_com,
+  path = here::here("report", "figures"),
+  scale = 2.4,
+  dpi = 400,
+  width = 80,
+  height = 80 * 1,
+  units = "mm")
+```
+
+```{r}
 tar_load(fix_fw_stab)
@@
 ```{r}
-tar_load(pred_sr_rho)
-p_pred_sr_rho <- pred_sr_rho %>%
+tar_load(pred_stab_comp_rho)
+p_pred_sr_rho <- pred_stab_comp_rho %>%
+  filter(response == "stab_com") %>%
   mutate(variable = var_replacement()[variable]) %>%
-  ggplot(aes(x = rho, y = values, fill = slope_richness)) +
+  ggplot(aes(x = rho, y = variable_values, fill = slope)) +
   geom_raster() +
@@
     ) +
-  theme(legend.position = "bottom")
+  theme(
+    legend.position = "bottom",
+    legend.key.width = unit(2.5, "cm"),
+    plot.margin = margin(l = 10, r = 10, unit = "pt")
+  )
 ggsave_multiple(
@@
   dpi = 400,
-  width = 88,
-  height = 88 * .45,
+  width = 120,
+  height = 120 * .45,
   units = "mm")
@@
 tar_load(pred_data)
-pred_data %>%
+p_pred_sr_rho_int_env <- pred_data %>%
   filter(
@@
     richness >= 1,
-    Z == 10,
-    h %in% c(3),
+    Z == 100,
+    h %in% c(2),
     avg_int_strength %in% c(.01, .1),
-    w_avg_tlvl == 1.5
+    w_avg_tlvl == 2.0
     ) %>%
@@
       x = richness, y = stab_com,
-      color = as.factor(resp_div),
+      color = as.factor(rho),
+      fill = as.factor(rho),
       linetype = as.factor(avg_int_strength),
@@
   ylim(2, 8) +
-  geom_line(linewidth = 1) +
+  geom_line(linewidth = .8) +
+  geom_ribbon(aes(ymin = stab_com - stab_com_se, ymax = stab_com + stab_com_se), alpha = .3, color = NA) +
   scale_alpha_manual(values = c(1, 1), guide = "none") +
-  facet_grid(cols = vars(env_stoch), labeller = label_both) +
+  facet_grid(
+    cols = vars(env_stoch),
+    labeller = as_labeller(function(x) paste0("Environmental stochasticity: ", x))) +
   labs(
@@
     linetype = "Avg. Interaction strength",
-    color = "Response diversity"
+    color = "Environmental correlation", fill = "Environmental correlation"
   ) +
@@
 #pred_data$pop_stab <- predict(mod_tot_pop_stab, newdata = pred_data)
+
+```
+```{r}
+p_pred_sr <- plot_grid(
+  p_pred_sr_rho_int_env + theme(legend.position = "right"),
+  p_pred_sr_rho,
+  nrow = 2,
+  labels = "auto"
+)
+ggsave_multiple(
+  paste0("p_pred_sr", c(".png", ".pdf")),
+  plot = p_pred_sr,
+  path = here::here("report", "figures"),
+  scale = 2.0,
+  dpi = 400,
+  width = 120,
+  height = 120 * .8,
+  units = "mm")
 ```

### 2023-10-16 paper/manuscript.Rmd
Update manuscript figures and SEM results

@@
   negative (dashed) standardised effects. Initial parameters were initial
-  species richness, initial connectance, Prey-Predator Mass Ration (PPMR), hill
+  species richness, initial connectance, Prey-Predator Mass Ratio (PPMR), hill
   exponent, variance of stochastic mortality rates (Env. stochasticity), and
@@
 
-get_eff <- function(y = "pop_stab", x = "richness", d = 2, effect_type = "direct", tab = sem_eff_tab) {
+get_eff <- function(
+  y = "pop_stab", x = "richness",
+  d = 2, effect_type = "direct",
+  tab = sem_simplified_eff_tab) {
   mask <- tab$response == y & tab$predictor == x &
@@
 rpe <- get_eff(y = "pop_stab", x = "env_stoch")
-rsr <- get_eff(y = "sae_even", x = "richness")
-ret <- get_eff(y = "evenness_sae", x = "w_avg_tlvl")
-rer <- get_eff(y = "evenness_sae", x = "richness")
-rea <- get_eff(y = "evenness_sae", x = "avg_int_strength")
-rec <- get_eff(y = "evenness_sae", x = "ct_alive")
-reh <- get_eff(y = "evenness_sae", x = "h")
 
-ria <- get_eff(y = "cpe_int", x = "avg_int_strength")
-ric <- get_eff(y = "cpe_int", x = "ct_alive")
-rih <- get_eff(y = "cpe_int", x = "h")
-rir <- get_eff(y = "cpe_int", x = "richness")
+rsr <- get_eff(y = "sae_total", x = "richness")
+rst <- get_eff(y = "sae_total", x = "w_avg_tlvl")
+rsi <- get_eff(y = "sae_total", x = "avg_int_strength")
+rsc <- get_eff(y = "sae_total", x = "ct_alive")
 
-rvr <- get_eff(y = "cpe_env", x = "richness")
-rvo <- get_eff(y = "cpe_env", x = "rho")
+rcr <- get_eff(y = "cpe", x = "richness")
+rci <- get_eff(y = "cpe", x = "avg_int_strength")
+rco <- get_eff(y = "cpe", x = "rho")
+
+# Detailled SEM coefficients
+rsr <- get_eff(y = "sae_even", x = "richness", tab = sem_eff_tab)
+ret <- get_eff(y = "evenness_sae", x = "w_avg_tlvl", tab = sem_eff_tab)
+rer <- get_eff(y = "evenness_sae", x = "richness", tab = sem_eff_tab)
+rea <- get_eff(y = "evenness_sae", x = "avg_int_strength", tab = sem_eff_tab)
+rec <- get_eff(y = "evenness_sae", x = "ct_alive", tab = sem_eff_tab)
+reh <- get_eff(y = "evenness_sae", x = "h", tab = sem_eff_tab)
+
+ria <- get_eff(y = "cpe_int", x = "avg_int_strength", tab = sem_eff_tab)
+ric <- get_eff(y = "cpe_int", x = "ct_alive", tab = sem_eff_tab)
+rih <- get_eff(y = "cpe_int", x = "h", tab = sem_eff_tab)
+rir <- get_eff(y = "cpe_int", x = "richness", tab = sem_eff_tab)
+
+rvr <- get_eff(y = "cpe_env", x = "richness", tab = sem_eff_tab)
+rvo <- get_eff(y = "cpe_env", x = "rho", tab = sem_eff_tab)
 ```
 ```{r, eval = FALSE}
-sem_eff_tab %>%
+sem_simplified_eff_tab %>%
   filter(abs(effect) > .1, effect_type == "direct")
@@
 We found that food-web structure had significant effect on temporal population
-stability such as average trophic level and type III functional response (i.e. h = 3)
+stability such as average trophic level and type III functional response (i.e. hill exponent = 3)
 increase population stability (resp. $r_\delta$= `r rpt` and `r rph`, $r_\delta$
@@
 averaging effects, which raises from independant species fluctuations weigthed
-the evenness of their biomass. As expected the mathematical relationship (eq. XX),
-species richness was the only driver of even statistical averaging effect
-($r_\delta$= `r rsr`, Fig. \@ref(fig:sem)). Average trophic level had a strong negative effect on
-evenness ($r_\delta$= `r ret`), meaning that biomass are more inequally
-distributed among species, thereby downplaying the portefolio effect raised from
-species richness. But richness had also a small negative effect on evenness
-($r_\delta$= `r rer`). Constrastingly, connectance, average interaction
-strength, and type III functional response all increased biomass evenness
-(resp. $r_\delta$= `r rec`, `r rea`, and `r reh`).
-
-Food-web structure and cross-correlation among species mortality rates had
-strong effects on compensatory dynamics. Average trophic level, connectance and
-type III functional response had a negative effect on compensatory effect
-raising from species interaction (resp. $r_\delta$= `r ria`, `r ric`, `r rih`,
-Fig. \@ref(fig:sem)) there decreasing asynchony, while richness had a positive
-effect ($r_\delta$= `r rir`), there increasingasynchrony. In turn, richness and
-cross-correlation among species mortality rates had a negative effect on
-compensatory dynamic raising from environmental stochasticity
-($r_\delta$= `r rvr` and `r rvo`).
+the evenness of their biomass. As expected the mathematical relationship (eq.
+XX), species richness was a main positive driver of statistical averaging effect
+($r_\delta$= `r rsr`, Fig. \@ref(fig:sem)), thereby increasing asynchrony.
+Average trophic level and average interaction strength had strong negative
+effects on statistical averaging effects (resp. $r_\delta$= `r rst` and
+`r rsi`), thereby downplaying the portefolio effect raised from species
+richness. In turn, we found that average interaction strength had a small
+positive effect on compensatory dynamics ($r_\delta$= `r rci`, Fig.
+\@ref(fig:sem)). Cross-correlation among species mortality rates had a
+strong negative effect on compensatory dynamics ($r_\delta$= `r rco`), meaning
+that the loss of response diversity result in a strong decrease in compensatory
+dynamics.
 
 ```{r}
-rscp <- get_eff(y = "stab_com", x = "pop_stab")
-rsca <- get_eff(y = "stab_com", x = "async")
 
-rav <- get_eff(y = "async", x = "cpe_env")
-rae <- get_eff(y = "async", x = "evenness_sae")
+rscp <- get_eff(y = "stab_com", x = "pop_stab", tab = sem_eff_tab)
+rsca <- get_eff(y = "stab_com", x = "async", tab = sem_eff_tab)
 
-rass <- get_eff(y = "async", x = "sae_even")
-rasi <- get_eff(y = "async", x = "cpe_int")
+rac <- get_eff(y = "async", x = "cpe")
+ras <- get_eff(y = "async", x = "sae_total")
+
+#
+rav <- get_eff(y = "async", x = "cpe_env", tab = sem_eff_tab)
+rae <- get_eff(y = "async", x = "evenness_sae", tab = sem_eff_tab)
+
+rass <- get_eff(y = "async", x = "sae_even", tab = sem_eff_tab)
+rasi <- get_eff(y = "async", x = "cpe_int", tab = sem_eff_tab)
 ```
@@
 Population stability had a positive effect twice higher than asynchrony on the
-temporal stability of community (resp. $r_\delta$= `r rscp` and `r rsca`). In turn, asynchrony
-was mostly driven by evenness of biomass distribution and compensatory dynamics
-raising from environmental stochasticity (resp. $r_\delta$= `r rae` and `r rav`, Fig.
-\@ref(fig:sem)) than from statistical averaging emerging from species richness
-(i.e. even) and compensatory dynamics emerging from species interaction (resp.
-$r_\delta$= `r rass` and `r rasi`).
+temporal stability of community (resp. $r_\delta$= `r rscp` and `r rsca`). In
+turn, asynchrony was equally driven by statistical averaging effects and
+compensatory dynamics (resp.
+$r_\delta$= `r rac` and `r ras`, Fig. \@ref(fig:sem)).
 
@@
 ```{r}
-pred_cap <- "Relationship between community stability and species richness
-according to environmental stochasticity and response diversity. (a) Simulation [add parameters selected], (b) Prediction from the linear model. "
+tar_load(default_variable_values_pred)
+pv <- default_variable_values_pred
+pv_cap <- paste0(
+  "connectance = ", pv["ct_alive"],
+  ", average interaction strength = ", pv["avg_int_strength"],
+  ", average trophic level = ", pv["w_avg_tlvl"],
+  ", hill exponent = ", pv["h"],
+  ", Predator-Prey Mass Ration = ", pv["Z"],
+  ", environmental correlation = ", pv["rho"],
+  ", and environmental stochasticity = ", pv["env_stoch"]
+
+)
+pred_cap <- paste0("Prediction of the statistical model linking the temporal stability
+  of community biomass and species richness. Default parameter values: ", pv_cap, ".") %>%
+  str_replace_all("\\s+", " ")
 ```
@@
 ```{r pred, fig.cap = pred_cap}
-knitr::include_graphics(here("report", "figures", "p_sim_pred.pdf"))
+knitr::include_graphics(here("report", "figures", "p_pred_sr.pdf"))
 ```
 
-Using a more complex linear model (i.e. containing interaction), we investigated more
+Using a more complex linear model (i.e. including interactions), we investigated more
 in detail the relationship between community stability and species richness and
@@
 correlation among species mortality rates. We found that environmental
-stochasticity decrease overall community stability but does not change the shape
-of the community stability-species richness relationship (put some numbers, Fig.
-\@ref(fig:pred)a and b). In contrasts, cross correlation among species mortality rates
-both decreases overall community stability and nullifies the community
-stability-species richness relationship. Surpringly, we found that
+stochasticity decrease overall community stability but has only little effect on
+the shape of the community stability-species richness relationship (put some
+numbers, Fig. \@ref(fig:pred)a and b). In contrasts, cross correlation among
+species mortality rates both decreases overall community stability and nullifies
+the community stability-species richness relationship. Surpringly, we found that
 despite average interaction strength has a small overall effect on

### 2023-10-19 paper/manuscript.Rmd
Reshape introduction

@@
 
-# IDEA, meeting with Sonia
-
-- Simplifying SEM in main text, move details to appendix
-- State diagram for stability - richness relationships along two food-web
-  metrics and panels varying response diversity.
-- Look at the french data for portefolio and compensatory dynamics effects.
-- Mid-October
+---
+## IDEA, meeting with Sonia
+#- Simplifying SEM in main text, move details to appendix
+#- State diagram for stability - richness relationships along two food-web
+#  metrics and panels varying response diversity.
+#- Look at the french data for portefolio and compensatory dynamics effects.
+#- Mid-October
+---
 
@@
 
-Global change and its simultaneous increasing stressors constitute a major
-threat to biodiversity and ecosystem functioning [@pachauri_climate_2015;
-@simmons_refocusing_2021]. Among them, climate change is predicted to lead
-dramatically more variable environments [@pachauri_climate_2015]. Understanding
-how environmental variability will affect ecosystem
-stability is then a timely question.
+Global environmental change including climate, land use and invasive species
+constitutes a suite of major threats to biodiversity and ecosystem functioning
+[@pachauri_climate_2015; @simmons_refocusing_2021]. A central feature of these
+threats is that they are predicted to dramatically increase variability in the
+environment that species face [@pachauri_climate_2015] with potential impacts on
+the stability of communities and associated impacts on biodiversity and
+functioning in these communities. Assessing the impacts of this variability on
+communities is challenging for several reasons.
 
-Biodiversity, in terms of species richness, has been repeatedly shown to drive
-higher temporal stability of ecological communities, across various taxa and
-ecosystems. Species richness can dampen the effects of perturbations on the
-temporal variability of community biomass because more diverse communities
-contain species with more diversity of responses to perturbations, which
-generates asynchrony in population fluctuations, thereby stabilizing community
-biomass fluctuations [@loreau_species_2008; @thibaut_understanding_2013;
-@zhao_biodiversity_2022]. In turn, the effects of human pressures on biotic
-homogenization reported in various ecosystems [@buisson_toward_2013;
-@muthukrishnan_invasive_2020; @saladin_rapid_2020] is another threat, which
-might in turn affect dampens the effects of species richness on ecosystem
-stability. However, the joint effects of external stressors such as
-environmental variability and internal stressors such as the
-loss response diversity has been rarely assessed in temporal stability areas.
+First, there are numerous definitions of community stability depending of the
+stressors considered. For example, resistance and resilience are typically used
+when a pulse perturbation is considered [@kefi_advancing_2019]. While in natural
+settings where press and pulse perturbations are simultaneously present,
+community variability measured as the coefficient of variation is typically used
+[@thibaut_understanding_2013]. Defined at the community scale, community
+variability can be partioned into population stability and asynchrony
+[@thibaut_understanding_2013]. Synchronous population fluctuations will amplify
+the negative effects of environmental fluctuations on temporal community
+stability while compensatory dynamics and portefolio effects (i.e. asynchrony)
+will stabilise temporal fluctuations of community biomass [@shoemaker_long_2022;
+@zhao_biodiversity_2022]. Environmental forcing (such as food availability and
+warming) and land-use intensity was reported to synchronise population
+fluctuations [@benton_population_2001; @bluthgen_land_2016; @song_reduced_2015;
+@liu_aridity_2023] while habitat degradation tends to decrease population
+stability [@olivier_urbanization_2020]. Understanding the effects of global
+change on community temporal stability therefore require to account for their
+simultaneous effects on community and population scales [@kefi_advancing_2019;
+@simmons_refocusing_2021].
 
-The question of stressors can even become complex in multitrophic communities,
-where species richness corresponds both to horizontal and vertical diversity.
-Food-web structure has been shown to have tremendous effect on community
-stability. The degree of generalism of predator was shown to modulate
-stability-richness relationships [@thebault_trophic_2005]. The strength and
-distribution of interaction strength was also shown to be strong driver of
-community stability [@mccann_weak_1998]. Omnivory was also shown to drive higher
-stability [@mccann_reevaluating_1997]. The effects of food-web structure on
-ecosystem stability has been mostly assessed with small modules [but see
-@eschenbrenner_diversity_nodate], and we know very little how food-web structure
-affects the relationships between species richness and temporal stability in
-complex food-webs.
+Second, the relation between community stability and biodiversity in variable
+environment is contingent on species richness per se, on the effects of species
+richness on population stability and asynchrony, and ultimately
+on the diversity of species responses to enviromental fluctuations [response
+diversity, @ives_stability_1999; @elmqvist_response_2003]. Increasing
+species richness has been reported to decrease population stability in
+experimental grasslands [@tilman_biodiversity_2006; @rosher_identifying_2011],
+while increasing population stability in natural settings
+[@houlahan_negative_2018] [add mechanisms?]. In turn, higher species richness
+often results in higher asynchrony, through portfolio effects (i.e. statistical
+averaging effects due to independant species fluctuations) and compensatory
+dynamics (due to species interactions and response
+diversity of species due to the environment) [@loreau_species_2008;
+@thibaut_understanding_2013]. Systematic increase in asynchrony with species
+richness is the mechanism that drives reported positive relationships between
+community stability and species richness [ref]. Anthropogenic pressures, such as
+eutrophication, has been reported to weakens the relationship between species
+richness and asynchony in grasslands [@hautier_eutrophication_2014] but such
+empiricial evidence remains scarced. However, stressors such as biotic
+homogenization [@buisson_toward_2013; @muthukrishnan_invasive_2020;
+@saladin_rapid_2020] and environmental forcing that decrease species response
+diversity should dampens the relationships between asynchrony and species
+richness [@ives_stability_2000; @thibaut_understanding_2013] due to a decrease
+in portefolio effects and compensatory effects. [Talk about the effects of
+evenness in temporal variability and evenness in abundance? e.g.,
+@zhao_biodiversity_2022; @thibaut_understanding_2013]. Because stressors can
+affect both community stability per se and how community stability scales with
+species richness, improving our understanding require to study both
+[@ives_stability_2007; @hautier_anthropogenic_2015].
 
-Both stressors and food-web structure are expected to have different effects on
-temporal stability. Stability of community biomass can itself be partitioned in
-several components, i.e. population stability and population asynchrony
-[@thibaut_understanding_2013; @zhao_biodiversity_2022]. Population stability can
-be itself partioned in total biomass and population variability effect.
-Population asynchrony can further be partioned in statistical averaging effect
-and compensatory dynamics effects [@zhao_biodiversity_2022]. Partitioning
-stability allows to better understand how food-web structure and external
-factors affect stability. We expect that environmental variability will
-primarily affect. For exemple, environmental stochasticity is expected to
-primarily affect population variance. Response diversity is expected to act
-primarily on compensatory dynamics in the food-webs, as low response diversity
-will decrease the effects. Higher connectance and interaction strength are
-expected to dampens population variability but to lead to higher synchrony at
-the same time.
+Third, the structure of species trophic interactions, that determines the
+distribution of biomass fluxes through communities, can also control stability.
+including levels of generalism, the distribution of interaction strengths and
+the prevalence of omnivory, can also influence stability. The degree of
+generalism of predator was shown to modulate stability-richness relationships
+[@thebault_trophic_2005]. The strength and distribution of interaction strength
+was also shown to be strong driver of community stability, such as stronger
+interaction strengths can be destabilizing [@may_will_1972; @mccann_weak_1998]. Omnivory was also
+shown to drive higher population stability [@mccann_reevaluating_1997].
+The effects of food-web structure on ecosystem stability has been mostly
+assessed with small modules [but see @eschenbrenner_diversity_nodate], and we
+know very little how food-web structure affects the relationships between
+species richness and temporal stability in complex food-webs.
 
----
-#Understanding the mechanisms that determine temporal
-#stability of ecosystem functioning is a long standing
-#question in Ecology [@may_will_1972; @angelis_stability_1975;
-#@mccann_diversitystability_2000; @tilman_biodiversity_2006;
-#@donohue_navigating_2016; @kefi_advancing_2019].
----
-
-In this study, we investigated both the effects of stressors ( environnmental
-variability and response diversity) and of food-web structure (connectance,
-average interaction strength, average trophic level) on species
-richness-stability relationships. To do, we used a bioenergetic food-web model
-[@yodzis_body_1992; @brose_allometric_2006; @delmas_simulations_2017] added to
-environmental stochasticity.
-
-```{r}
-concept_cap <- "Food-web structure, response diversity and enviromental gradient
-can modulate stability-richness relationships. (a & b) Food-web structure may
-modulate stability-richness relationships additively (a) or interactively (b).
-(c) Decrease in response diversity and increase in environmental variability
-should dampen stability-richness relationships. While the loss of response
-diversity should dampen the effect of species richness on asynchrony, the
-increase in environmental variability should decrease primarily population
-stability. (d) Increase in productivity should increase species richness
-(trophic energy hypothesis) but also dampens the relationship between stability
-and species richness (paradox of enrichment). (e) Summary of the framework, how
-food-web structure and external perturbations modulate the effects of species
-richness on community stability. More precisely, how they affect the different
-components of stability: total biomass, population variability, statistical
-averaging effects and compensatory dynamics."
-```
-
-```{r, eval = FALSE, fig.cap=concept_cap}
-knitr::include_graphics(here("report", "figures", "conceptual_figures.pdf"))
-```
-
-```{r, eval = FALSE}
-tribble(
-  ~Type, ~`Food-web structure`, ~`Effect on stability-richness`,
-  "Food-web structure", "Connectance", "Strengthen (Miele et al., 2016) / No effect (Thébault & Loreau, 2005)",
-  "Food-web structure", "Omnivory", "Strengthen (Mccann et al., 1997)",
-  "Food-web structure", "Interaction strength", "Destabilising (Mccann et al., 1998) / Stabilising in
-  productive (Binzer et al., 2012; Binzer et al., 2016; Tabi et al., 2019)",
-  "Response diversity", "", "Dampens",
-  "Productivity", "", "Dampens (Binzer et al., 2012; Binzer et al., 2016; Tabi et al., 2019)",
-  "Environmental variability", "", "Dampens",) %>%
-kbl(caption = "Predictions of stability-richness relationship from the literature.") %>%
-kable_styling()
-```
+Here we deliver inference from modelling of complex biodiverse communities on
+how food-web structure (connectance, average interaction strength, average
+trophic level), response diversity, and environmental stochasticity combine to
+shape species richness-stability relationships.
 

### 2023-10-19 paper/manuscript.Rmd
Update SEM results

@@
 on the diversity of species responses to enviromental fluctuations [response
-diversity, @ives_stability_1999; @elmqvist_response_2003]. Increasing
+diversity, @ives_stability_2000; @elmqvist_response_2003]. Increasing
 species richness has been reported to decrease population stability in
-experimental grasslands [@tilman_biodiversity_2006; @rosher_identifying_2011],
+experimental grasslands [@tilman_biodiversity_2006; @roscher_identifying_2011],
 while increasing population stability in natural settings
@@
 generalism of predator was shown to modulate stability-richness relationships
-[@thebault_trophic_2005]. The strength and distribution of interaction strength
-was also shown to be strong driver of community stability, such as stronger
-interaction strengths can be destabilizing [@may_will_1972; @mccann_weak_1998]. Omnivory was also
-shown to drive higher population stability [@mccann_reevaluating_1997].
-The effects of food-web structure on ecosystem stability has been mostly
-assessed with small modules [but see @eschenbrenner_diversity_nodate], and we
-know very little how food-web structure affects the relationships between
-species richness and temporal stability in complex food-webs.
+[@thebault_trophic_2005], and generalist predators can synchronise the dynamics
+of their preys[@raimondo_interspecific_2004]. The strength and distribution of
+interaction strength was also shown to be strong driver of community stability,
+such as stronger interaction strengths can be destabilizing [@may_will_1972;
+@mccann_weak_1998]. Omnivory was also shown to drive higher population stability
+[@mccann_reevaluating_1997]. The effects of food-web structure on ecosystem
+stability has been mostly assessed with small modules [but see
+@eschenbrenner_diversity_nodate], and we know very little how food-web structure
+affects the relationships between species richness and temporal stability in
+complex food-webs. So understanding the effects of stressors on community
+stability and on community stability-richness relationships necessitate to
+account for food-web structure.
 
@@
 
-## The model
+## Bioenergenetic model
 
@@
 
-We added a stochastic natural mortality rate to the species dynamics, that
-represent variation in mortality due to variation in environment. Based on the
-litterature and previous models [@vasseur_environmental_2007], we assumed that
+## Environmental stochasticity and response diversity
+
+We added a stochastic natural mortality rate to the species dynamics,
+representing a fluctuating environment. Based on the litterature and previous
+models [@vasseur_environmental_2007], we assumed that
 natural mortality rates scales inversely with the species body mass ($d_i =
@@
 studies[@vasseur_environmental_2007].
-
-## Environmental stochasticity and response diversity
 
@@
 Response diversity was controlled by the correlation among species stochastic
-mortality rates ($\rho_{ij, i \neq j}$) such as response diversity is maximal when species mortality
-rates are uncorrelated ($\rho = 0$) and null when species mortality
-rates are perfectly correlated ($\rho = 1$) [@ripa_food_2003;
+mortality rates ($\rho_{ij, i \neq j}$) such as response diversity is maximal
+when species mortality rates are uncorrelated ($\rho = 0$) and null when species
+mortality rates are perfectly correlated ($\rho = 1$) [@ripa_food_2003;
 @vasseur_environmental_2007; @gouhier_synchrony_2010]. So the species mortality
@@
 We generated food-web structure using the niche model [@williams_simple_2000]
-with species richness from 10 to 60, and connectance from $0.02$ to $.32$. We
-generated food-webs without cannibalistic links and checked for the absence of
-disconnected species.
+with an initial species richness from $10$ to $60$, and connectance from $0.02$
+to $.32$. We generated food-webs without cannibalistic links and discarded
+food-webs that contained disconnected species.
 
@@
 [@brose_allometric_2006]. We set $K = XX$ to ensure that consumers were not
-limited by the biomass input in the food-web.
+limited by the biomass input from primary producers.
 
@@
 
-We numerically solved the simulation with a $dt$ = .1 during 5000 timesteps
+We numerically solved the simulations with a $dt$ = .1 during 5000 timesteps
 and collected the last 500 timesteps. We set extinction threshold to $10^{-5}$
@@
 
-To further get a mechanistic insight about the effects of stressors and food-web structure on stability,
-we partionned asynchrony into statistical averaging effect (SAE) and compensatory
-dynamics effect (CPE) [@zhao_biodiversity_2022]. SAE controls for ..., while CPE describes compensatory
-dynamics emerging from species interactions and differential responses to
-environmental stochasticity.
+To further get a mechanistic insight about the effects of stressors and food-web
+structure on stability, we partionned asynchrony into statistical averaging
+effect (SAE) and compensatory dynamics effect (CPE) [@zhao_biodiversity_2022].
+SAE quantities the portfolio effect emerging from independant species
+fluctuations, while CPE describes compensatory dynamics emerging from species
+interactions and differential responses to environmental stochasticity.
 
@@
 S_{com} = S_{pop} \times SAE \times CPE
-(\#eq:scom)
+(\#eq:scom2)
 \end{aligned}
@@
 
-As SAE is further dependant of biomass evenness in food-webs, we
+As SAE is further dependant on the evenness of species variance, we
 partionned $SAE$ into $SAE_{even}$ and evenness $EVN$, such as $SAE_{even} =
@@
 paths of the path of the model according to theorical expectations. We tested
-the effects of species richness, connectance, and the Predator-Prey size ratio
-on secondary structure of the food-webs, the average trophic level, the average
-omnivory and the interaction strength. We also tested the effects of  on  We
-expected that richness affect population stability by modifying the average
-population biomass for exemple [@thibaut_understanding_2013]. Grounded in
-theoretical ecological, we expected that average trophic level, the average
-omnivory and the interaction strength modulated population stability
-[@mccann_weak_1998; @mccann_reevaluating_1997; @shanafelt_stability_2018].
-Previous studies have also the Predator-Prey size ratio modulate population
-stability [@brose_allometric_2006]. Finally, the effect of enviromental
-stochasticity was assumed to be mainly associated to population stability (i.e.
-by increasing amplitude of population fluctuations).
+the effects of initial species richness, initial connectance, Predator-Prey size
+ratio on secondary structure of the food-webs, i.e. realized species richness
+and connectance, the average trophic level, the average omnivory and the
+interaction strength. Further, we expected those food-web structure to alter
+population stability and synchrony. Grounded in theoretical ecology, we expected
+that higher average trophic level, average omnivory, lower interaction strength,
+and type III functional response (relative to type II) increase population
+stability [@mccann_weak_1998; @mccann_reevaluating_1997;
+@shanafelt_stability_2018]. Higher Predator-Prey size ratio was also expected to
+increase population stability [@brose_allometric_2006]. Finally, the effect of
+enviromental stochasticity was assumed to be mainly associated to population
+stability (i.e. by increasing amplitude of population fluctuations).
 
 Regarding asynchrony, we tested the effects of species richness, connectance,
-weighted average trophic level and interaction strength on the evenness of
-biomass which in turn affect total statistical averaging effects. We expected
-that those same food-web structural properties also affected compensatory
-dynamics due to interactions ($CPE_{int}$). Finally, we tested the effects of
-species richness and species cross-correlation in mortality rates on the
-compensatory dynamics due to stochastic fluctuations ($CPE_{env}$). We completed
-the structural equation model with the mathematical relationship linking
-compensatory dynamics and statistical averaging effects to asynchrony, and from
-asynchrony and population stability to community stability.
+average trophic level and interaction strength on statistical averaging effects.
+We expected that those same food-web structural properties affected
+compensatory dynamics due to interactions ($CPE_{int}$). Finally, we tested the
+effects of species richness and species cross-correlation in mortality rates on
+the compensatory dynamics due to stochastic fluctuations ($CPE_{env}$). We
+completed the structural equation model with the mathematical relationship
+linking compensatory dynamics and statistical averaging effects to asynchrony,
+and from asynchrony and population stability to community stability.
 
@@
 environmental stochasticity and response diversity. We modelled temporal
-stability of biomass according to food-web structure: species richness, weighted average trophic
-level, connectance, hill exponent, predator-prey size ratio, and average
-interaction strength, as well as enviromental stochasticity and species
+stability of biomass according to food-web structure: species richness, weighted
+average trophic level, connectance, hill exponent, predator-prey size ratio, and
+average interaction strength, as well as enviromental stochasticity and species
 cross-correlation. We further included the two way interactions between species
@@
 We found that food-web structure had significant effect on temporal population
-stability such as average trophic level and type III functional response (i.e. hill exponent = 3)
-increase population stability (resp. $r_\delta$= `r rpt` and `r rph`, $r_\delta$
-being the standardized coefficient, Fig. \@ref(fig:sem)). However the strength
-of environmental stochasticity had a strong negative effect on population
-stability ($r_\delta$= `r rpe`).
+stability such as average trophic level and type III functional response (i.e.
+hill exponent = 3) increase population stability (resp. $r_\delta$= `r rpt` and
+`r rph`, $r_\delta$ being the standardized coefficient, Fig. \@ref(fig:sem)).
+In turn, the variance of environmental stochasticity had a strong negative effect
+on population stability ($r_\delta$= `r rpe`).
 
@@
 averaging effects, which raises from independant species fluctuations weigthed
-the evenness of their biomass. As expected the mathematical relationship (eq.
+the evenness of their variance. As expected the mathematical relationship (eq.
 XX), species richness was a main positive driver of statistical averaging effect
@@
 positive effect on compensatory dynamics ($r_\delta$= `r rci`, Fig.
-\@ref(fig:sem)). Cross-correlation among species mortality rates had a
-strong negative effect on compensatory dynamics ($r_\delta$= `r rco`), meaning
-that the loss of response diversity result in a strong decrease in compensatory
-dynamics.
+\@ref(fig:sem)). Cross-correlation among species mortality rates (i.e. lower
+response diversity) had a strong negative effect on compensatory dynamics
+($r_\delta$= `r rco`), meaning that the loss of response diversity result in a
+strong decrease in compensatory dynamics.
 
@@
 
-rscp <- get_eff(y = "stab_com", x = "pop_stab", tab = sem_eff_tab)
-rsca <- get_eff(y = "stab_com", x = "async", tab = sem_eff_tab)
+rscp <- get_eff(y = "stab_com", x = "pop_stab")
+rsca <- get_eff(y = "stab_com", x = "async")
+#rscp <- get_eff(y = "stab_com", x = "pop_stab", tab = sem_eff_tab)
+#rsca <- get_eff(y = "stab_com", x = "async", tab = sem_eff_tab)
 
@@
 ras <- get_eff(y = "async", x = "sae_total")
+#rac <- get_eff(y = "async", x = "cpe")
+#ras <- get_eff(y = "async", x = "sae_total")
 
@@
 turn, asynchrony was equally driven by statistical averaging effects and
-compensatory dynamics (resp.
-$r_\delta$= `r rac` and `r ras`, Fig. \@ref(fig:sem)).
+compensatory dynamics (resp. $r_\delta$= `r rac` and `r ras`, Fig.
+\@ref(fig:sem)).
 
@@
 
+```{r}
+rtsrho <- get_eff(y = "stab_com", x = "rho", effect_type = "total")
+rtsenv <- get_eff(y = "stab_com", x = "env_stoch", effect_type = "total")
+
+rtsr <- get_eff(y = "stab_com", x = "richness", effect_type = "total")
+rtst <- get_eff(y = "stab_com", x = "w_avg_tlvl", effect_type = "total")
+rtsz <- get_eff(y = "stab_com", x = "Z", effect_type = "total")
+rtsh <- get_eff(y = "stab_com", x = "h", effect_type = "total")
+rtsc <- get_eff(y = "stab_com", x = "ct_alive", effect_type = "total")
+rtsi <- get_eff(y = "stab_com", x = "avg_int_strength", effect_type = "total")
+
+rtpr <- get_eff(y = "pop_stab", x = "richness", effect_type = "total")
+rtpt <- get_eff(y = "pop_stab", x = "w_avg_tlvl", effect_type = "total")
+rtpz <- get_eff(y = "pop_stab", x = "Z", effect_type = "total")
+rtph <- get_eff(y = "pop_stab", x = "h", effect_type = "total")
+rtpc <- get_eff(y = "pop_stab", x = "ct_alive", effect_type = "total")
+rtpi <- get_eff(y = "pop_stab", x = "avg_int_strength", effect_type = "total")
+
+rtar <- get_eff(y = "async", x = "richness", effect_type = "total")
+rtat <- get_eff(y = "async", x = "w_avg_tlvl", effect_type = "total")
+rtaz <- get_eff(y = "async", x = "Z", effect_type = "total")
+rtah <- get_eff(y = "async", x = "h", effect_type = "total")
+rtac <- get_eff(y = "async", x = "ct_alive", effect_type = "total")
+rtai <- get_eff(y = "async", x = "avg_int_strength", effect_type = "total")
+```
+
 Deriving the sum of direct and indirect effects from the structural equation
 model, we show that both enviromental stochasticity and cross-correlation among
-species had by far the most negative effect on community stability (XX, Fig.
-\@ref(fig:semtot)). Average trophic level, type III functional response and
-predator prey bodysize ratio had total positive effects on community stability.
-Those positive effects are raising from sometimes contrasting effects on
-population stability and asynchrony such as Average trophic level, type III
-functional response and predator prey bodysize ratio which have positive effects
-on population stability (resp. XXX) but a negative one on asynchrony (resp. XXX).
+species had by far the most negative effect on community stability (resp.
+$r_\delta$= `r rtsenv` and `r rtsrho`, Fig. \@ref(fig:semtot)). Species richness
+had a low overall positive total effect on community stability (`r rtsr`)
+because its strong total positive effect on asynchony (`r rtar`) was downplayed
+by its total negative effect on population stability (`r rtpr`) and that the
+weigtht of population stability on community stability is twice higher than the
+one of asynchony. Average trophic level, type III functional response and
+predator prey bodysize ratio had positive effects on community stability in
+total (resp. `r rtst`, `r rtsh`, `r rtsz`, Fig. \@ref(fig:semtot)), driven by
+their positive effects on population stability that were weakly counterbalanced
+by their negative effects on asynchrony. In turn, connectance and average
+interaction strength had low total negative effects on community stability (resp.
+`r rtsc` and `r rtsi`, Fig. \@ref(fig:semtot)). While connectance had negative
+effects both on population stability and asynchrony, average interaction
+strength had a low total positive effect on population stability counterbalanced
+by a stronger negative effect on asynchrony.
 
@@
 the feeding rates of consumers when their preys have a low biomass which leads
-to a less dramatic fluctuations of prey biomass [@uszco_effects_2017;
+to a less dramatic fluctuations of prey biomass [@uszko_effects_2017;
 @brose_allometric_2006]. We however found no big effect of species richness on

### 2023-10-26 paper/manuscript.Rmd
Refurbished Discussion

@@
 ---
-title: Food-web structure, stochasticity and response diversity drive temporal stability in complex communities
-author: Alain Danet, Andrew P. Beckerman
+title: Food-web structure, stochasticity and response diversity drive temporal community stability in complex communities
+author: Alain Danet, (Sonia Kéfi, Thomas F Johnson), Andrew P. Beckerman
 output:
-  bookdown::pdf_document2
+  officedown::rdocx_document:
+    base_format: "bookdown::word_document2"
+    number_sections: false
+  bookdown::pdf_document2:
+    latex_engine: xelatex
+    keep_tex: true
+    spacing: double
+    number_sections: false
 always_allow_html: true
+bibliography: references.bib
+link-citations: true
 toc: false
-bibliography: references.bib
+linestretch: 2.0
 header-includes:
@@
   - \linenumbers
+  - \hypersetup{backref=true}
   - \usepackage{setspace}\doublespacing
@@
 ```{r, results = FALSE}
-sapply(c("targets", "tidyverse", "magrittr", "cowplot", "here", "piecewiseSEM", "semEff", "ggcorrplot", "kableExtra"), require, character.only = TRUE)
+sapply(c("targets", "tidyverse", "magrittr", "cowplot", "here", "piecewiseSEM",
+    "semEff", "ggcorrplot", "kableExtra", "officedown"),
+  require,
+  character.only = TRUE)
 
@@
 [@thibaut_understanding_2013]. Defined at the community scale, community
-variability can be partioned into population stability and asynchrony
+variability can be partitioned into population stability and asynchrony
 [@thibaut_understanding_2013]. Synchronous population fluctuations will amplify
 the negative effects of environmental fluctuations on temporal community
-stability while compensatory dynamics and portefolio effects (i.e. asynchrony)
+stability while compensatory dynamics and portfolio effects (i.e. asynchrony)
 will stabilise temporal fluctuations of community biomass [@shoemaker_long_2022;
@@
 richness on population stability and asynchrony, and ultimately
-on the diversity of species responses to enviromental fluctuations [response
+on the diversity of species responses to environmental fluctuations [response
 diversity, @ives_stability_2000; @elmqvist_response_2003]. Increasing
@@
 often results in higher asynchrony, through portfolio effects (i.e. statistical
-averaging effects due to independant species fluctuations) and compensatory
+averaging effects due to independent species fluctuations) and compensatory
 dynamics (due to species interactions and response
@@
 eutrophication, has been reported to weakens the relationship between species
-richness and asynchony in grasslands [@hautier_eutrophication_2014] but such
-empiricial evidence remains scarced. However, stressors such as biotic
+richness and asynchrony in grasslands [@hautier_eutrophication_2014] but such
+empirical evidence remains scarce. However, stressors such as biotic
 homogenization [@buisson_toward_2013; @muthukrishnan_invasive_2020;
@@
 richness [@ives_stability_2000; @thibaut_understanding_2013] due to a decrease
-in portefolio effects and compensatory effects. [Talk about the effects of
+in portfolio effects and compensatory effects. [Talk about the effects of
 evenness in temporal variability and evenness in abundance? e.g.,
@@
 trophic level), response diversity, and environmental stochasticity combine to
-shape species richness-stability relationships.
+shape temporal stability of community biomass, as well as its partition into
+asynchrony and population stability. We then assess how food-web complexity and
+response diversity shape stability-richness relationships.
 
@@
 We added a stochastic natural mortality rate to the species dynamics,
-representing a fluctuating environment. Based on the litterature and previous
+representing a fluctuating environment. Based on the literature and previous
 models [@vasseur_environmental_2007], we assumed that
@@
 stochastic differential equation: $d\epsilon_t = (0 - \epsilon_t)d_t + \sigma_e
-dW_t$, where $dW_t$ is a Browian motion. The strength of environmental
+dW_t$, where $dW_t$ is a Brownian motion. The strength of environmental
 stochasticity was then controlled by $\sigma_e$.
@@
 we varied the Predator-Prey Bodysize Ratio (PPBR) from 1 to 100. We further
-varied the functional reponse of consumer from type II to type III (resp. $h=2$
+varied the functional response of consumer from type II to type III (resp. $h=2$
 and $h=3$, eq XX) as it was shown to have a tremendous role on stability
@@
 To further get a mechanistic insight about the effects of stressors and food-web
-structure on stability, we partionned asynchrony into statistical averaging
+structure on stability, we partitioned asynchrony into statistical averaging
 effect (SAE) and compensatory dynamics effect (CPE) [@zhao_biodiversity_2022].
-SAE quantities the portfolio effect emerging from independant species
+SAE quantities the portfolio effect emerging from independent species
 fluctuations, while CPE describes compensatory dynamics emerging from species
@@
 Statistical averaging effect is the share of asynchrony assuming that species are
-independant, meaning that the variance total of the community is equal to the
+independent, meaning that the variance total of the community is equal to the
 sum of species variances only (i.e. species covariances are null). We can
@@
 As SAE is further dependant on the evenness of species variance, we
-partionned $SAE$ into $SAE_{even}$ and evenness $EVN$, such as $SAE_{even} =
+partitioned $SAE$ into $SAE_{even}$ and evenness $EVN$, such as $SAE_{even} =
 \sqrt{S}$ and $EVN = SAE / SAE_{even}$.
 
-Compensatory dynamics in the food-webs is then the remaining part of asynchony:
+Compensatory dynamics in the food-webs is then the remaining part of asynchrony:
 
@@
 Compensatory dynamics can arise from predator-prey interactions
-($CPE_{int}$) or from differential response of species to enviromental
+($CPE_{int}$) or from differential response of species to environmental
 stochasticity ($CPE_{env}$). From the deterministic and stochastic parts of
@@
 
-Using a structural equation model, we disantengled the complex effects of
+Using a structural equation model, we disentangled the complex effects of
 food-web structure, environmental stochasticity and response diversity on the
@@
 statistical averaging effects and compensatory dynamic effects). We set the
-paths of the path of the model according to theorical expectations. We tested
+paths of the path of the model according to theoretical expectations. We tested
 the effects of initial species richness, initial connectance, Predator-Prey size
@@
 increase population stability [@brose_allometric_2006]. Finally, the effect of
-enviromental stochasticity was assumed to be mainly associated to population
+environmental stochasticity was assumed to be mainly associated to population
 stability (i.e. by increasing amplitude of population fluctuations).
@@
 average trophic level, connectance, hill exponent, predator-prey size ratio, and
-average interaction strength, as well as enviromental stochasticity and species
+average interaction strength, as well as environmental stochasticity and species
 cross-correlation. We further included the two way interactions between species
@@
 structure and stressors. The VIF were inferior to 5, indicating low
-multicollinearity.
+multicollinearity. We then used the coefficients of the model to predict the shape
+of the relationship between community stability and species richness according
+to a gradient of response diversity and of food-web structure.
 
@@
 ```{r}
-#TODO: change most of it for simplified SEM
 tar_load(c(sem_eff_tab, sem_simplified_eff_tab))
@@
 We further found that food-web structure had a strong impact on statistical
-averaging effects, which raises from independant species fluctuations weigthed
+averaging effects, which raises from independent species fluctuations weighted
 the evenness of their variance. As expected the mathematical relationship (eq.
@@
 effects on statistical averaging effects (resp. $r_\delta$= `r rst` and
-`r rsi`), thereby downplaying the portefolio effect raised from species
+`r rsi`), thereby downplaying the portfolio effect raised from species
 richness. In turn, we found that average interaction strength had a small
@@
 semtot_cap <- "Total effect of food-web structure on community stability,
-asynchony, and population stability. The total effects were derived from the
+asynchrony, and population stability. The total effects were derived from the
 structural equation model."
@@
 Deriving the sum of direct and indirect effects from the structural equation
-model, we show that both enviromental stochasticity and cross-correlation among
+model, we show that both environmental stochasticity and cross-correlation among
 species had by far the most negative effect on community stability (resp.
@@
 had a low overall positive total effect on community stability (`r rtsr`)
-because its strong total positive effect on asynchony (`r rtar`) was downplayed
+because its strong total positive effect on asynchrony (`r rtar`) was downplayed
 by its total negative effect on population stability (`r rtpr`) and that the
-weigtht of population stability on community stability is twice higher than the
-one of asynchony. Average trophic level, type III functional response and
+weight of population stability on community stability is twice higher than the
+one of asynchrony. Average trophic level, type III functional response and
 predator prey bodysize ratio had positive effects on community stability in
@@
 species mortality rates both decreases overall community stability and nullifies
-the community stability-species richness relationship. Surpringly, we found that
+the community stability-species richness relationship. Surprisingly, we found that
 despite average interaction strength has a small overall effect on
@@
 
-## Food-web structure and stressors affects population stability and asynchony
+## Food-web structure and stressors affects population stability and asynchrony
 
-Our results shows that community stability in complex food-webs is mainly driven
+Our results show that community stability in complex food-webs is mainly driven
 by population stability rather than synchrony, confirming previous results in
-empirical data [@danet_species_2021]. We further found that average trophic
-level and functional response of type III increased average population
-stability, confirming previous results [@brose_allometric_2006;
-@shanafelt_stability_2018; @danet_species_2021;
-@eschenbrenner_diversity_nodate]. Higher average trophic level stabilises
-populations because higher predator are themselves more stable and because they
-control the amplitude of the fluctuations of their prey [REF, we can test
-that?]. Furthermore, average omnivory was strongly correlated with average
-trophic level, suggesting that average omnivory also stabilise population
-stability, in line with previous theoretical results in small modules
-[@mccann_reevaluating_1997]. In turn, functional response of type III decreases
-the feeding rates of consumers when their preys have a low biomass which leads
-to a less dramatic fluctuations of prey biomass [@uszko_effects_2017;
-@brose_allometric_2006]. We however found no big effect of species richness on
-population stability, which has been reported to be negative, positive or
-neutral in previous studies [@ruijven_contrasting_2007;
-@houlahan_negative_2018].
+empirical fish communities [@danet_species_2021], which contrasts with empirical
+data in birds and bats assemblages that reported a equivalent influence of
+population stability and asynchrony on community stability
+[@olivier_urbanization_2020]. Although the number of empirical and theoretical
+studies is still limited to compare the respective contribution of asynchrony and
+population stability to community stability in competitive assemblages and
+food-webs, we suggest two non-exclusive and complementary explanations that
+might drive a lower contribution of asynchrony in food-webs compared to
+competitive assemblages. First, the range of bodymasses is much higher in
+food-webs, which typically include species that differ by several order of
+magnitude [@brose_predator_2019], which in turn creates highly uneven biomass
+distribution, thereby creating uneven contributions of species to asynchrony
+[@thibaut_understanding_2013] and limits the raise of high portfolio effects and
+compensatory dynamics in species rich communities [@zhao_biodiversity_2022].
+Second, the trophic interactions characterising food-webs create strong
+interdependence among species, which in turn limits the raise of independent
+fluctuations (i.e. portfolio effects) and compensatory dynamics. The question of
+which mechanisms and community structure features drive differences in the
+contribution of asynchrony and population stability in food-webs and competitive
+assemblages is still a open question that might be crucial to accurately
+address diagnostics and conservation measures. On top of food-web structure,
+we found that environmental stochasticity and environmental correlation among
+species was the main drivers of community stability, suggesting that stressors
+are the first source of stability. This result is in accordance with previous
+studies showing strong effects on environmental stochasticity
+[@vasseur_environmental_2007] and the loss of response diversity decrease
+community stability in tri-trophic food-webs [@ives_stability_2000;
+@thebault_trophic_2005].
 
-Our results shows that asynchrony is mainly decreased by the cross-correlation
-among species mortality rates and mediated by compensatory dynamics, indicating
-that the loss of response diversity suppressed the positive effects of species
-richness on stability. Our result shows that evenness of biomass plays an
-significant role in driving statistical averaging effect (i.e. portefolio
-effects). Our results shows that average trophic level decreases strongly the
-evenness of biomass variability, thereby limiting the effect of species richness on the
-portefolio effects. Furthermore, increase in species richness also resulted in
-less even biomass variability. Our results also suggest that stronger species
-interaction, higher generalism, and functional response of type III are
-associated with a more even variability, thereby raising the portefolio
-effects. The importance of evenness in driving portefolio effects has been
-recognised early by theoretical studies [@thibaut_understanding_2013], but
-rather in terms of abundance than in variability [@zhao_biodiversity_2022].
-We suggest that higher average trophic level decreases evenness of variability
-because the model assumes that species of higher trophic level have a lower
-overall mortality rates, similarly to previous studies [@vasseur_environmental_2007].
+We further found that average trophic level increased average population
+stability, confirming previous theoreical [@brose_allometric_2006;
+@shanafelt_stability_2018; @eschenbrenner_diversity_nodate] and
+[@danet_species_2021] empirical results. Higher average trophic level can
+stabilise populations because higher predators  are themselves more stable due
+to lower mortality rates with in turn makes them less sensible stochastic
+perturbation and because they control the amplitude of the fluctuations of their
+prey [@shanafelt_stability_2018, we can test that?]. In turn, we found that that
+average trophic level decreases strongly asynchrony through a negative effect on
+statistical averaging effect. Further analysis showed that average trophic level
+limited statistical averaging effect by decreasing the evenness of biomass
+variability. It is linked to the model assumption that species of higher trophic
+level have a lower overall mortality rates, similarly to previous studies
+[@vasseur_environmental_2007], stabilising populations and simultaneously
+synchronising them. The fact that Predator Size Mass Ratio displays the same
+effect, thereby building food-webs with bigger species having lower mortality
+rates, further lends toward this hypothesis. Furthermore, average omnivory was
+strongly correlated with average trophic level, suggesting that average omnivory
+also stabilise population stability, in line with previous theoretical results
+in small modules [@mccann_reevaluating_1997]. Our results further suggest that
+higher average trophic level results in lower compensatory dynamics raising from
+species interactions. It might be explained by the fact that average trophic
+level is strongly associated with average omnivory, which might tamper
+synchronized predator-prey oscillations that can raise compensatory dynamics
+[@mccann_reevaluating_1997].
 
-Our results further suggest that higher average trophic level results in lower
-compensatory dynamics raising from species interactions. It might be explained
-by the fact that average trophic level is strongly associated with average
-omnivory, which might tamper synchronized predator-prey oscillations that can
-raise compensatory dynamics [@mccann_reevaluating_1997]. Higher generalism in
-also drives lower compensatory dynamics due to species interaction and then lend
-to the same hypothesis such as more trophic links per consumer should decrease
-overall amplitude of oscillations due to prey switching. Furthermore, functional
-response of type III which drives prey switching at low abundance of the
-prefered prey also lend toward this interpretation
-[@mccann_diversitystability_2000]. [Do not have clear idea for richness at this
-time]. Surpringly however, average interaction strength had no effects on
-compensatory dynamics that is not already captured by other food-web structural
-properties. Compensatory dynamics due to environment was decreased by both
-species richness and cross-correlation among species mortality rates (i.e. loss
-of response diversity). Our interpretation is that higher species richness
-syncronize more species fluctuations due to mortality because each added species
-adds (S - 1, S being richness) positive covariance terms in the stochastic
-mortality rates, thereby increasing the overall synchrony in mortality rates
-when cross correlation are not null.
+We however found no big effect of species richness on population stability,
+which has been reported to be negative, positive or neutral in previous studies
+[@ruijven_contrasting_2007; @houlahan_negative_2018]. [interpretation?].
+However, species richness had a strong positive on asynchrony, by raising
+statistical averaging effects. [add blabla about richness asynchrony]. In turn,
+we found that species richness magnified the effect of the loss of response
+diversity on the compensatory dynamics due to environment. Our interpretation is
+that higher species richness synchronizes more species fluctuations due to
+environmental mortality when species are not independent because each added
+species adds (S - 1, S being richness) positive covariance terms in the
+stochastic mortality rates, thereby increasing the overall synchrony in
+mortality rates when cross correlation are not null. This assumption that each
+species are equally correlated to each other seems unlikely to be true but as
+far we know, there is compelling evidence yet for alternative correlation
+structures. Connectance, quantifying generalism in food-web, had negative
+effects on both asynchrony and population stability. We further found that
+higher connectance leaded to less even biomass variability, thereby limiting the
+raise of the portfolio effects, and leaded to lower compensatory dynamics due
+to species interactions. This results in accordance with empirical finding that
+a generalist predator can indeed synchronises the dynamics of a large number of
+preys [@raimondo_interspecific_2004]. [No idea about connectance decreasing
+population stability]. However, the overall effect of connectance on overall
+stability was quite low, similarly to previous empirical findings
+[@danet_species_2021], but in apparent disagreement with the predominant role of
+connectance on stability in theoretical studies [complexity-stability paradox,
+@may_will_1972].
 
-## Stochasticity and response diversity affect stability-richness relationship
+Food-web dynamical features, functional response of type III and average
+interaction strength, also had an effect on community stability. Our results
+confirms the stabilising effect of the functional response of type III on
+populations [@uszko_effects_2017; @brose_allometric_2006]. Compared to type II,
+functional response of type III models a decrease of the feeding rates of
+consumers when their preys have a low biomass which leads to a less dramatic
+fluctuations of prey biomass. Furthermore, we found that functional response of
+type III decreased asynchrony by decreasing compensatory dynamics due to species
+interaction. This effect might be due to prey switching of consumers when one of
+them reach low abundance [@mccann_diversitystability_2000]. Average interaction
+strength, as connectance, had overall little effect on community stability.
+Average interaction strength was found to decrease asynchrony by decreasing the
+evenness of biomass variability, thereby decreasing the portfolio effect,
+despite having a small positive effect on compensatory dynamics. In turn, we
+surprisingly found that average interaction strength had little effects on
+population stability, which contrasts with the importance of this parameter in
+complexity-stability relationship [@may_will_1972].
 
-Our results suggest that, confirming the result of the structural equation
-model, that in maximal response diversity environmental stochasticity primarily
-drives average stability, without changing the shape of the stability-richess
-relationship. The reason is that the strength of environmental stochasticity
-only affect population stability and not asynchrony, the latter being the driver
-of species-richness relationships. In turn, a decrease in response diversity
-dampens the stability-richness relationship [@thibaut_understanding_2013].
-Interestingly, our results also suggest that high response diversity also
-decrease the destabilising effects of average interaction strength on
-stability-richness relationships. Indeed, in low response diversity, we found
-high interaction strength leads to negative stability-richness relationships.
+## Stability-richness relationship
 
-## Implication for real world
+We found that environmental stochasticity does not affect the shape of the
+community stability - richness but rather control the overall community
+stability (i.e. the intercept of the relation). At the opposite, In turn, a
+decrease in response diversity dampens the stability-richness relationship. The
+reason is that the strength of environmental stochasticity only affect
+population stability and not asynchrony, the latter being the driver of
+species-richness relationships [@ives_stability_2000; @thebault_trophic_2005;
+@thibaut_understanding_2013]. Average interaction strength and connectance that
+were found to have little effects on overall stability, were found to have a
+strong effect on stability-richness relationships. This result is in accordance
+with the complexity-stability theory that predicts that community stability
+(i.e. measured as the dominant eigen value of the jacobian matrix) should
+decrease as the community is species diversity, has higher connectance, and
+higher interaction strength [@may_will_1972]. However, we found that the
+negative effects of complexity on stability-richness relationship are cancelled
+when response diversity is high. A interpretation is that environmental
+stochasticity itself does not override the negative complexity-stability
+relationships, but it the presence of response diversity and resulting
+asynchrony in species fluctuations which overrides the negative effects of
+complexity on stability-richness relationship. Response diversity might then one
+mechanism that explains why so much positive relationship between stability and
+species richness are found in empirical settings while food-web theoretical
+model that do not often include environmental stochasticity and response
+diversity finds negative complexity stability relationships
+[@ives_stability_2007].
+
+# Conclusion and perspectives
+
+Our study presents the effects of food-web structure on temporal community
+stability and its partition into population stability and asynchrony in complex
+food-web, added to two pressing stressors in the context of global change, the
+strength of environmental variability and the level of response diversity of
+species facing this environmental variability. Our results confirm the results
+of previous theoretical models modelling small food-web modules or food-chain,
+as we report that average trophic level, omnivory, predator-prey size ratio, and
+functional response of type III increase temporal community stability by
+stabilising population fluctuations. In turn, our study confirm that species
+richness increase temporal community stability by increasing asynchrony due to
+portfolio effects and thanks to response diversity. Our study reports that
+connectance and average interaction strength have little effects on overall
+community stability while they have a strong effect on the sign of the community
+stability-richness relationship, in accordance with the complexity-stability
+paradox, but only in the absence of response diversity. Overall, it suggests that
+high response diversity of species facing environmental stochasticity, on top of
+being the essential ingredient driving positive stability-richness relationship,
+also cancel the negative effects of food-web complexity on stability-richness
+relationship.
 
@@
 biotic homogenization [@olden_homogocene_2018; @muthukrishnan_invasive_2020;
-@wang_biotic_2021] is also suggested to descrease response diversity
+@wang_biotic_2021] is also suggested to decrease response diversity
 [@wang_biotic_2021; @su_human_2021], which in turn is expected to further
-decrease stability despite high species richness, even more in food-web
-communities composed of high interaction strength. Then, our study reinforces
-that the restauration of ecosystems along with a restauration of landscape
-complexity that provides refuges from extrem environment are key to maintain
-temporal stability of ecological communities [@ryser_landscape_2021].
-
-# Conclusion
-
-TODO
+decrease stability despite high species richness, even more in complex food-webs
+having high interaction strength, high connectance and high average trophic
+level. Then, our study reinforces that the restoration of ecosystems along with
+a restoration of landscape complexity that provides refuges from extreme
+environment are key to maintain temporal stability of ecological communities
+[@ryser_landscape_2021].
 

### 2023-11-22 _targets.Rmd
Clarify Figure SR

@@
 
+```{targets r}
+list(
+  tar_target(p_pop_stab_w_avg_tlvl,
+    sim_fw %>%
+      filter(env_stoch == .3) %>%
+      ggplot(aes(x = w_avg_tlvl, y = log(pop_stab))) +
+      geom_point(alpha = .2) +
+      geom_smooth(method = "lm") +
+      labs(
+        x = var_replacement()["w_avg_tlvl"],
+        y = var_replacement()["pop_stab"]
+        ) +
+      theme_bw()
+    ),
+  tar_target(p_pop_stab_h,
+    sim_fw %>%
+      filter(env_stoch == .3) %>%
+      ggplot(aes(x = as.factor(h), y = log(pop_stab))) +
+      geom_boxplot(alpha = .2) +
+      labs(
+        x = var_replacement()["h"],
+        y = var_replacement()["pop_stab"]
+        ) +
+      theme_bw()
+    ),
+  tar_target(p_pop_stab_env_stoch,
+    sim_fw %>%
+      ggplot(aes(x = as.factor(env_stoch), y = log(pop_stab))) +
+      geom_boxplot(alpha = .2) +
+      labs(
+        x = var_replacement()["env_stoch"],
+        y = var_replacement()["pop_stab"]
+        ) +
+      theme_bw()
+    ),
+  tar_target(p_even_sae_richness,
+    sim_fw %>%
+      filter(rho == 0) %>%
+      ggplot(aes(x = as.factor(richness), y = log(evenness_sae))) +
+      geom_boxplot(alpha = .2) +
+      geom_smooth(method = "lm") +
+      labs(
+        x = var_replacement()["richness"],
+        y = var_replacement()["evenness_sae"]
+        ) +
+      theme_bw()
+    ),
+  tar_target(p_sae_total_richness,
+    sim_fw %>%
+      filter(rho == 0) %>%
+      ggplot(aes(x = as.factor(richness), y = log(sae_total))) +
+      geom_boxplot(alpha = .2) +
+      geom_smooth(method = "lm") +
+      scale_x_discrete(breaks = seq(0, 35, 5)) +
+      labs(
+        x = var_replacement()["richness"],
+        y = var_replacement()["sae_total"]
+        ) +
+      theme_bw()
+    ),
+  tar_target(p_even_sae_w_avg_tlvl,
+    sim_fw %>%
+      filter(rho == 0) %>%
+      ggplot(aes(x = w_avg_tlvl, y = log(evenness_sae))) +
+      geom_point(alpha = .2) +
+      geom_smooth(method = "lm") +
+      labs(
+        x = var_replacement()["w_avg_tlvl"],
+        y = var_replacement()["evenness_sae"]
+        ) +
+      theme_bw()
+    ),
+  tar_target(p_sae_total_w_avg_tlvl,
+    sim_fw %>%
+      filter(rho == 0) %>%
+      ggplot(aes(x = w_avg_tlvl, y = log(sae_total))) +
+      geom_point(alpha = .2) +
+      geom_smooth(method = "lm") +
+      labs(
+        x = var_replacement()["w_avg_tlvl"],
+        y = var_replacement()["sae_total"]
+        ) +
+      theme_bw()
+    ),
+  tar_target(p_even_sae_avg_int,
+    sim_fw %>%
+      filter(rho == 0) %>%
+      ggplot(aes(x = avg_int_strength, y = log(evenness_sae))) +
+      geom_point(alpha = .2) +
+      geom_smooth(method = "lm") +
+      labs(
+        x = var_replacement()["avg_int_strength"],
+        y = var_replacement()["evenness_sae"]
+        ) +
+      theme_bw()
+    ),
+  tar_target(p_sae_total_avg_int,
+    sim_fw %>%
+      filter(rho == 0) %>%
+      ggplot(aes(x = avg_int_strength, y = log(sae_total))) +
+      geom_point(alpha = .2) +
+      geom_smooth(method = "lm") +
+      labs(
+        x = var_replacement()["avg_int_strength"],
+        y = var_replacement()["sae_total"]
+        ) +
+      theme_bw()
+    ),
+  tar_target(p_sae_total_ct_alive,
+    sim_fw %>%
+      filter(rho == 0) %>%
+      ggplot(aes(x = ct_alive, y = log(sae_total))) +
+      geom_point(alpha = .2) +
+      geom_smooth(method = "lm") +
+      labs(
+        x = var_replacement()["ct_alive"],
+        y = var_replacement()["sae_total"]
+        ) +
+      theme_bw()
+    ),
+  tar_target(p_cpe_int_avg_int,
+    sim_fw %>%
+      ggplot(aes(x = avg_int_strength, y = log(cpe_int))) +
+      geom_point(alpha = .2) +
+      geom_smooth(method = "lm") +
+      labs(
+        x = var_replacement()["avg_int_strength"],
+        y = var_replacement()["cpe_int"]
+        ) +
+      theme_bw()
+    ),
+  tar_target(p_cpe_avg_int,
+    sim_fw %>%
+      ggplot(aes(x = avg_int_strength, y = log(cpe))) +
+      geom_point(alpha = .2) +
+      geom_smooth(method = "lm") +
+      labs(
+        x = var_replacement()["avg_int_strength"],
+        y = var_replacement()["cpe"]
+        ) +
+      theme_bw()
+    ),
+  tar_target(p_cpe_rho,
+    sim_fw %>%
+      ggplot(aes(x = rho, y = log(cpe), group = rho)) +
+      geom_boxplot() +
+      labs(
+        x = var_replacement()["rho"],
+        y = var_replacement()["cpe"]
+        ) +
+      theme_bw()
+    ),
+  tar_target(p_sem_bivariate_relations,
+    plot_grid(
+      p_pop_stab_w_avg_tlvl, p_pop_stab_h, p_pop_stab_env_stoch,
+      p_sae_total_richness, p_sae_total_ct_alive, p_sae_total_w_avg_tlvl,
+      p_sae_total_avg_int, p_cpe_avg_int, p_cpe_rho
+    )
+    )
+)
+```
+
+```{r}
+
+```
+
 ```{targets p-stab}
@@
     )
-
 )
@@
   theme(axis.text.x = element_text(angle = 20, hjust = 1))
+```
+
+```{r}
+ggsave_multiple(
+  paste0("p_sem_bivariate_relations", c(".png", ".pdf")),
+  plot = tar_read(p_sem_bivariate_relations),
+  path = here::here("report", "figures"),
+  scale = 3,
+  dpi = 400,
+  width = 80,
+  height = 80 * .9,
+  units = "mm")
 ```
@@
   filter(response == "stab_com") %>%
-  mutate(variable = var_replacement()[variable]) %>%
-  ggplot(aes(x = rho, y = variable_values, fill = slope)) +
+  mutate(
+    variable = var_replacement()[variable],
+    resp_div = 1 - rho
+    ) %>%
+  ggplot(aes(x = resp_div, y = variable_values, fill = slope)) +
   geom_raster() +
@@
   scale_fill_gradient2(
-    low = "red",
+    low = rho_cat_colors()["Low"],
     mid = "white",
-    high = "blue",
+    high = rho_cat_colors()["High"],
     midpoint = 0,
@@
   labs(
-    x = "Environmental correlation",
+    x = var_replacement()["resp_div"],
     y = "Food-web structure",
-    fill = "Slope Stability-Richness"
+    fill = "Slope community stability - Richness"
     ) +
@@
 ```
+
+```{r}
+pred_data_sr_fw <- pred_data %>%
+  filter(
+    ct_alive %in% c(.1, .3),
+    rho %in% c(0, .75),
+    richness >= 1,
+    Z == 100,
+    h %in% c(2),
+    avg_int_strength %in% c(.01, .1),
+    env_stoch == .1,
+    w_avg_tlvl %in% c(2.0, 3.0)
+    ) %>%
+mutate(
+  group_ct_alive = case_when(
+    ct_alive == .3 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "High",
+    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
+    ),
+  group_avg_int_strength = case_when(
+    ct_alive == .1 & avg_int_strength == .1 & w_avg_tlvl == 2.0 ~ "High",
+    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
+    ),
+  group_w_avg_tlvl = case_when(
+    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 3.0 ~ "High",
+    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
+    )) %>%
+pivot_longer(starts_with("group_")) %>%
+filter(!is.na(value)) %>%
+mutate(name = str_remove(name, "group_"))
+p_pred_data_sr_fw <- pred_data_sr_fw %>%
+  mutate(name = var_replacement()[name]) %>%
+  ggplot(aes(
+      x = richness, y = stab_com,
+      color = resp_div,
+      fill = resp_div,
+      linetype = value,
+      #alpha = as.factor(avg_int_strength)
+      )) +
+  geom_line(linewidth = .8) +
+  geom_ribbon(
+    aes(ymin = stab_com - stab_com_se, ymax = stab_com + stab_com_se),
+    alpha = .3, color = NA) +
+  scale_color_manual(values = rho_cat_colors()) +
+  scale_fill_manual(values = rho_cat_colors()) +
+  facet_grid(cols = vars(name)) +
+  labs(
+    x = var_replacement()["richness"],
+    y = var_replacement()["stab_com"],
+    fill = var_replacement()["resp_div"],
+    color = var_replacement()["resp_div"],
+    linetype = "Food-web structure value"
+  ) +
+  theme_bw() +
+  theme(legend.position = "bottom") +
+  guides(
+    linetype = guide_legend(keywidth = 2,
+      override.aes = list(fill = NA, alpha = 1)
+      ),
+    fill = guide_legend(override.aes = list(linetype = 0, alpha = 1))
+  )
+
+ggsave_multiple(
+  paste0("p_pred_data_sr_fw", c(".png", ".pdf")),
+  plot = p_pred_data_sr_fw,
+  path = here::here("report", "figures"),
+  scale = 3,
+  dpi = 400,
+  width = 80,
+  height = 80 * .4,
+  units = "mm")
+```
+
+## Figure SR
+
 ```{r}
 p_pred_sr <- plot_grid(
-  p_pred_sr_rho_int_env + theme(legend.position = "right"),
+  p_pred_data_sr_fw + theme(legend.position = "right"),
   p_pred_sr_rho,
   nrow = 2,
+  rel_heights = c(.7, 1),
   labels = "auto"
@@
   width = 120,
-  height = 120 * .8,
+  height = 120 * .7,
   units = "mm")

### 2023-11-22 paper/manuscript.Rmd
Clarify Figure SR

@@
 title: Food-web structure, stochasticity and response diversity drive temporal community stability in complex communities
-author: Alain Danet, (Sonia Kéfi, Thomas F Johnson), Andrew P. Beckerman
+author: "Alain Danet, (Sonia Kéfi, Thomas F Johnson), Andrew P. Beckerman"
+date: ""
 output:
@@
 sapply(c("targets", "tidyverse", "magrittr", "cowplot", "here", "piecewiseSEM",
-    "semEff", "ggcorrplot", "kableExtra", "officedown"),
+    "semEff", "ggcorrplot", "kableExtra", "rmarkdown", "officedown"),
   require,
   character.only = TRUE)
-
 mytheme <- theme_cowplot(font_size = 8) +
@@
   displayed standardised coefficients whose absolute values are superior to 0.1
-  are displayed. SEM containing containing further partition of Statistical
+  are displayed. A more complete SEM containing further partition of Statistical
   Averaging Effect and Compensatory effects is displayed in Fig. SXX.")
@@
 
-```{r sem, fig.cap=sem_cap}
+```{r sem, fig.cap=sem_cap, fig.id = "sem"}
 knitr::include_graphics(here("report", "figures", "sem_stab_simplified.pdf"))
@@
 
-```{r semtot, fig.cap = semtot_cap}
+```{r semtot, fig.cap = semtot_cap, fig.id = "semtot"}
 knitr::include_graphics(here::here("report", "figures", "p_sem_tot_stab.png"))
@@
 
-```{r pred, fig.cap = pred_cap}
+```{r pred, fig.cap = pred_cap, fig.id = "pred"}
 knitr::include_graphics(here("report", "figures", "p_pred_sr.pdf"))

### 2023-11-22 R/plotting_methods.R

@@ -1,3 +1,10 @@
 ggsave_multiple <- function(fns, ...) {
   map(fns, function(x) ggsave(x, ...))
 }
+
+rho_cat_colors <- function() {
+  c(
+    "Low" = "#FF0000",
+    "High" = "#02A5E0"
+  )
+}

### 2023-11-22 R/string_replacements.R

@@ -31,7 +31,10 @@ var_replacement <- function() {
     productivityenrichment = "Enrichment",
     env_stoch = "Env variance",
     Z = "PPMR",
-    h = "Hill exponent"
+    h = "Hill exponent",
+    S = "Initial species richness",
+    ct = "Initial connectance",
+    resp_div = "Response diversity"
   )
 }
 

### 2023-11-22 _targets.Rmd
Update graphs with response diversity

@@
 tar_target(sim_fw_file, here::here("data", "sim_fw"), format = "file"),
-  tar_target(sim_fw, readRDS(sim_fw_file)),
+  tar_target(sim_fw, {
+    x <- readRDS(sim_fw_file)
+    x %>%
+      mutate(resp_div = 1 - rho)
+  }),
   tar_target(sim_fw_df, as.data.frame(sim_fw)),
@@
       cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
-      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_sem),
+      cpe_env = lm(cpe_env ~ richness + resp_div, sim_fw_sem),
       async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_sem),
@@
       sae_total = lm(sae_total ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_sem),
-      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + rho, sim_fw_sem),
+      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + resp_div, sim_fw_sem),
       async = lm(async ~ sae_total + cpe, sim_fw_sem),
@@
         rand_effect = TRUE,
-        term_to_del = "richness : rho : Z +"),
+        term_to_del = "richness : resp_div : Z +"),
       data = mutate(sim_fw, across(c(stab_com, richness), log))
@@
       rand_effect = TRUE,
-      term_to_del = "richness : rho : Z +"),
+      term_to_del = "richness : resp_div : Z +"),
       data = mutate(sim_fw,
@@
         rand_effect = TRUE,
-        term_to_del = "richness : rho : Z +"
+        term_to_del = "richness : resp_div : Z +"
         ),
@@
           across(c(stab_com, richness,
-              env_stoch, rho, Z,
+              env_stoch, resp_div, Z,
               ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
@@
           across(c(stab_com, pop_stab, async, richness,
-              env_stoch, rho, Z, h,
+              env_stoch, resp_div, Z, h,
               ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
@@
       ct_alive = c(.05, .10, .30),
-      rho = c(0, .75, 1),
+      resp_div = 1 - c(0, .75, 1),
       avg_int_strength = c(.01, .02, .05, .1),
@@
     to$stab_com_se <- ti$se.fit
-    to$resp_div <- rho_replacement()[as.character(to$rho)]
     to
@@
   ),
-  tar_target(pred_sr_rho_int,
+  tar_target(pred_sr_resp_div_int,
     list(
-      rho = seq(0, 1, length.out = 50),
+      resp_div = seq(0, 1, length.out = 50),
       avg_int_strength = seq(0.01, 0.2, length.out = 50)
@@
     mutate(
-      slope_richness = map2_dbl(rho, avg_int_strength,
+      slope_richness = map2_dbl(resp_div, avg_int_strength,
         ~get_slope_change(
@@
           coeff_values = c(
-            "rho" = .x,
+            "resp_div" = .x,
             "env_stoch" = .1,
@@
             "Z" = 100))))),
-  tar_target(pred_sr_rho_tlvl,
+  tar_target(pred_sr_resp_div_tlvl,
     list(
-      rho = seq(0, 1, length.out = 50),
+      resp_div = seq(0, 1, length.out = 50),
       w_avg_tlvl = seq(1.5, 3.5, length.out = 50)
@@
     mutate(
-      slope_richness = map2_dbl(rho, w_avg_tlvl,
+      slope_richness = map2_dbl(resp_div, w_avg_tlvl,
         ~get_slope_change(
@@
             "Z" = 100))))),
-  tar_target(pred_sr_rho_ct,
+  tar_target(pred_sr_resp_div_ct,
     list(
-      rho = seq(0, 1, length.out = 50),
+      resp_div = seq(0, 1, length.out = 50),
       ct_alive = seq(.02, .3, length.out = 50)
@@
     mutate(
-      slope_richness = map2_dbl(rho, ct_alive,
+      slope_richness = map2_dbl(resp_div, ct_alive,
         ~get_slope_change(
@@
           coeff_values = c(
-            "rho" = .x,
+            "resp_div" = .x,
             "env_stoch" = .3,
@@
             "Z" = 100))))),
-  tar_target(pred_sr_rho,
-    map_dfr(list(pred_sr_rho_int, pred_sr_rho_ct, pred_sr_rho_tlvl),
+  tar_target(pred_sr_resp_div,
+    map_dfr(list(pred_sr_resp_div_int, pred_sr_resp_div_ct, pred_sr_resp_div_tlvl),
       ~.x %>%
@@
     c(
-      "rho" = 0,
+      "resp_div" = 0,
       "env_stoch" = .3,
@@
   ),
-  tar_target(pred_stab_comp_rho,
+  tar_target(pred_stab_comp_resp_div,
     fix_fw_stab_comp %>%
@@
           )
-          names(param) <- c("rho", param_name)
+          names(param) <- c("resp_div", param_name)
 
@@
       ~pivot_longer(.x,
-        -c(rho, slope),
+        -c(resp_div, slope),
         names_to = "variable",
@@
     sim_fw %>%
-      filter(rho == 0) %>%
+      filter(resp_div == 0) %>%
       ggplot(aes(x = as.factor(richness), y = log(evenness_sae))) +
@@
     sim_fw %>%
-      filter(rho == 0) %>%
+      filter(resp_div == 0) %>%
       ggplot(aes(x = as.factor(richness), y = log(sae_total))) +
@@
     sim_fw %>%
-      filter(rho == 0) %>%
+      filter(resp_div == 0) %>%
       ggplot(aes(x = w_avg_tlvl, y = log(evenness_sae))) +
@@
     sim_fw %>%
-      filter(rho == 0) %>%
+      filter(resp_div == 0) %>%
       ggplot(aes(x = w_avg_tlvl, y = log(sae_total))) +
@@
     sim_fw %>%
-      filter(rho == 0) %>%
+      filter(resp_div == 0) %>%
       ggplot(aes(x = avg_int_strength, y = log(evenness_sae))) +
@@
     sim_fw %>%
-      filter(rho == 0) %>%
+      filter(resp_div == 0) %>%
       ggplot(aes(x = avg_int_strength, y = log(sae_total))) +
@@
     sim_fw %>%
-      filter(rho == 0) %>%
+      filter(resp_div == 0) %>%
       ggplot(aes(x = ct_alive, y = log(sae_total))) +
@@
     ),
-  tar_target(p_cpe_rho,
-    sim_fw %>%
-      ggplot(aes(x = rho, y = log(cpe), group = rho)) +
+  tar_target(p_cpe_resp_div,
+    sim_fw %>%
+      ggplot(aes(x = resp_div, y = log(cpe), group = resp_div)) +
       geom_boxplot() +
       labs(
-        x = var_replacement()["rho"],
+        x = var_replacement()["resp_div"],
         y = var_replacement()["cpe"]
@@
       p_sae_total_richness, p_sae_total_ct_alive, p_sae_total_w_avg_tlvl,
-      p_sae_total_avg_int, p_cpe_avg_int, p_cpe_rho
+      p_sae_total_avg_int, p_cpe_avg_int, p_cpe_resp_div
     )
@@
 tar_read(sem_simplified_eff_tab) %>%
-  filter(effect_type == "total") %>%
-  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
-  filter(!predictor %in% c("rho", "env_stoch","cpe", "sae_total", "evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async", "S", "ct")) %>%
-  mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
-  ggplot(aes(
-      x = predictor,
-      y = effect,
-      ymin = lower_ci,
-      ymax = upper_ci)
-    ) +
-  geom_pointrange() +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  facet_grid(cols = vars(response)) +
-  labs(x = "Predictor", y = "Total effect") +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 20, hjust = 1))
+  filter(effect_type == "direct") %>%
+  #filter(response %in% c("async", "pop_stab", "stab_com")) %>%
+  filter(predictor %in% c("resp_div")) %>%
+  mutate(across(c(response, predictor), ~var_replacement()[.x]))
 ```
@@
 ```{r}
+library(RColorBrewer)
 library(ggbreak)
-cols <- c("Community stability" = "black", "Asynchrony" = "blue", "Population stability" = "darkgreen")
-alpha <- c("Community stability" = 1, "Asynchrony" = .3, "Population stability" = .3)
+#cols <- c("Community stability" = "black",
+#  "Asynchrony" = "blue",
+#  "Population stability" = "darkgreen"
+#)
+custom_stab_color <- c(
+  "Community stability" = "black", #"#ffffbf"
+  "Asynchrony" = "#91bfdb",
+  "Population stability" = "#fc8d59"
+)
+alpha <- c("Community stability" = 1, "Asynchrony" = 1, "Population stability" = 1)
+
+sem_tot_predictor <- c("richness", "avg_int_strength", "w_avg_tlvl",
+  "ct_alive", "Z", "h", "resp_div", "env_stoch")
+var_replacement()[sem_tot_predictor]
 p_sem_tot_stab <- tar_read(sem_simplified_eff_tab) %>%
@@
   filter(response %in% c("async", "pop_stab", "stab_com")) %>%
-  filter(!predictor %in% c("cpe", "sae_total", "evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async", "S", "ct")) %>%
-  mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
+  filter(predictor %in% sem_tot_predictor) %>%
+  mutate(
+    response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
+    predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor)], .ordered = TRUE)
+) %>%
   ggplot(aes(
@@
   geom_pointrange() +
-  scale_colour_manual(values = cols) +
+  scale_colour_manual(values = custom_stab_color) +
   scale_alpha_manual(values = alpha) +
-  #geom_hline(yintercept = 0, linetype = "dashed") +
+#  geom_hline(yintercept = 0, linetype = "dashed") +
   geom_vline(xintercept = 0, linetype = "dashed") +
@@
   labs(
-    x = "Total standardised effect",
+    x = "Total standardised effects",
     color = "Stability component",
@@
     #legend.justification = "right",
-    legend.position = "bottom"
-  ) +
-  scale_x_break(c(-0.3, -0.6))
+    legend.position = "bottom") +
+  guides(
+    color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
+    ) +
+  theme(
+    legend.title = element_blank(),
+    legend.position = c(.005, .995),
+    legend.justification = c("left", "top")
+  )
 p_sem_tot_stab_leg <- plot_grid(
-  print(p_sem_tot_stab + theme(legend.position = "none")),
+  print(p_sem_tot_stab +
+    theme(
+      legend.position = "none",
+    )
+  ),
   get_legend(p_sem_tot_stab),
@@
   paste0("p_sem_tot_stab", c(".png", ".pdf")),
-  plot = print(p_sem_tot_stab_leg),
+  plot = print(
+    p_sem_tot_stab +
+      guides(
+        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
+      ) +
+      theme(
+        legend.title = element_blank(),
+        legend.position = c(.005, .995),
+        legend.justification = c("left", "top"),
+
+      )
+    ),
   path = here::here("report", "figures"),
-  scale = 1.8,
+  scale = 2.4,
   dpi = 400,
   width = 80,
-  height = 80 * .7,
+  height = 80 * .4,
   units = "mm")
@@
 ```{r}
-tar_load(pred_stab_comp_rho)
-p_pred_sr_rho <- pred_stab_comp_rho %>%
+tar_load(pred_stab_comp_resp_div)
+p_pred_sr_resp_div <- pred_stab_comp_resp_div %>%
   filter(response == "stab_com") %>%
   mutate(
-    variable = var_replacement()[variable],
-    resp_div = 1 - rho
+    variable = var_replacement()[variable]
     ) %>%
@@
   scale_fill_gradient2(
-    low = rho_cat_colors()["Low"],
+    low = resp_div_cat_colors()["Low"],
     mid = "white",
-    high = rho_cat_colors()["High"],
+    high = resp_div_cat_colors()["High"],
     midpoint = 0,
@@
 ggsave_multiple(
-  paste0("p_pred_sr_rho", c(".png", ".pdf")),
-  plot = p_pred_sr_rho,
+  paste0("p_pred_sr_resp_div", c(".png", ".pdf")),
+  plot = p_pred_sr_resp_div,
   path = here::here("report", "figures"),
@@
 tar_load(pred_data)
-p_pred_sr_rho_int_env <- pred_data %>%
+p_pred_sr_resp_div_int_env <- pred_data %>%
   filter(
     ct_alive %in% c(.1),
-    rho %in% c(0, .75),
+    resp_div %in% c(0, .75),
     richness >= 1,
@@
       x = richness, y = stab_com,
-      color = as.factor(rho),
-      fill = as.factor(rho),
+      color = as.factor(resp_div),
+      fill = as.factor(resp_div),
       linetype = as.factor(avg_int_strength),
@@
     ct_alive %in% c(.1, .3),
-    rho %in% c(0, .75),
+    resp_div %in% c(1, .25),
     richness >= 1,
@@
 filter(!is.na(value)) %>%
-mutate(name = str_remove(name, "group_"))
+mutate(
+  name = str_remove(name, "group_"),
+  resp_div_cat = str_replace_all(resp_div, resp_div_replacement())
+)
+
+breaks_log_richness <- log(c(3, 6, 20))
+breaks_log_stab_com <- log(c(250, 500, 1000))
+
 p_pred_data_sr_fw <- pred_data_sr_fw %>%
-  mutate(name = var_replacement()[name]) %>%
+  mutate(
+    name = var_replacement()[name]
+    ) %>%
   ggplot(aes(
       x = richness, y = stab_com,
-      color = resp_div,
-      fill = resp_div,
+      color = resp_div_cat,
+      fill = resp_div_cat,
       linetype = value,
@@
     alpha = .3, color = NA) +
-  scale_color_manual(values = rho_cat_colors()) +
-  scale_fill_manual(values = rho_cat_colors()) +
+  scale_color_manual(values = resp_div_cat_colors()) +
+  scale_fill_manual(values = resp_div_cat_colors()) +
+  scale_x_continuous(breaks = breaks_log_richness, label = exp(breaks_log_richness)) +
+  scale_y_continuous(breaks = breaks_log_stab_com, label = exp(breaks_log_stab_com)) +
   facet_grid(cols = vars(name)) +
@@
   p_pred_data_sr_fw + theme(legend.position = "right"),
-  p_pred_sr_rho,
+  p_pred_sr_resp_div,
   nrow = 2,
@@
 
-```{r}
+```{r, eval = FALSE}
 tar_load(c(sim_fw_sem, sim_fw))
@@
 
-```{r}
+```{r, eval = FALSE}
 p_pred_sr_int <- pred_data %>%
@@
 
-```{r}
+```{r, eval = FALSE}
 p_pred_sr_int1 <- pred_data %>%

### 2023-11-22 R/model_helpers.R

@@ -1,25 +1,25 @@
 formula_stab_fw_model <- function(
   resp = "stab_com",
   rand_effect = TRUE,
-  term_to_del = "richness : rho : Z +"
+  term_to_del = "richness : resp_div : Z +"
   ) {
 
-  fixed_part <- "richness + rho + env_stoch +
+  fixed_part <- "richness + resp_div + env_stoch +
   ct_alive + w_avg_tlvl + Z +
   avg_int_strength +
   h +
-  richness : rho +
+  richness : resp_div +
   richness : env_stoch +
   richness : ct_alive +
   richness : avg_int_strength +
   richness : h +
   richness : w_avg_tlvl +
   richness : Z +
-  richness : rho : ct_alive +
-  richness : rho : w_avg_tlvl +
-  richness : rho : avg_int_strength +
-  richness : rho : h +
-  richness : rho : Z +
+  richness : resp_div : ct_alive +
+  richness : resp_div : w_avg_tlvl +
+  richness : resp_div : avg_int_strength +
+  richness : resp_div : h +
+  richness : resp_div : Z +
   richness : env_stoch : ct_alive +
   richness : env_stoch : Z +
   richness : env_stoch : avg_int_strength +

### 2023-11-22 R/plotting_methods.R

@@ -8,3 +8,7 @@ rho_cat_colors <- function() {
     "High" = "#02A5E0"
   )
 }
+
+resp_div_cat_colors <- function() {
+  rho_cat_colors()
+}

### 2023-11-22 R/string_replacements.R

@@ -6,35 +6,35 @@ var_replacement <- function() {
     pop_stab = "Population stability",
     log_stab_pop = "Population stability",
     log_avg_cv_sp = "Population variability",
+    async = "Asynchrony",
+    log_async = "Asynchrony",
     sync = "Synchrony",
     log_sync = "Synchrony",
-    log_async = "Asynchrony",
-    async = "Asynchrony",
     cpe = "Compensatory effect",
     cpe_int = "Comp effect (Interaction)",
     cpe_env = "Comp effect (Environment)",
     sae_total = "Stat Avg effect",
     sae_even = "Stat Avg effect (Even)",
     evenness_sae = "Stat Avg effect (Evenness)",
-    log1_avg_max_int_alive = "Avg interaction strength",
-    avg_max_int_alive = "Avg interaction strength",
+    richness = "Richness",
+    log_richness = "Richness",
     avg_int_strength = "Avg interaction strength",
+    avg_max_int_alive = "Avg interaction strength",
+    log1_avg_max_int_alive = "Avg interaction strength",
     sd_max_int_alive = "SD interaction strength",
+    w_avg_tlvl = "Avg trophic level",
     w_avg_tlvl_alive = "Avg trophic level",
     ct_alive = "Connectance",
     max_tlvl = "Max trophic level",
-    w_avg_tlvl = "Avg trophic level",
     avg_omnivory = "Avg omnivory",
-    log_richness = "Richness",
-    richness = "Richness",
-    rho = "Env Corr",
     productivityenrichment = "Enrichment",
+    resp_div = "Response diversity",
+    rho = "Env Corr",
     env_stoch = "Env variance",
     Z = "PPMR",
     h = "Hill exponent",
     S = "Initial species richness",
-    ct = "Initial connectance",
-    resp_div = "Response diversity"
+    ct = "Initial connectance"
   )
 }
 
@@ -48,6 +48,15 @@ rho_replacement <- function() {
     `0.5` = "Medium",
     `0.75` = "Low",
     `1` = "No"
+  )
+}
+
+resp_div_replacement <- function() {
+  c(
+    `1` = "High",
+    `0.5` = "Medium",
+    `0.25` = "Low",
+    `0` = "No"
   )
 }
 

### 2023-11-23 _targets.Rmd
Add a method figure

@@
 
+```{r plot-sim}
+load(here("data","sim_for_plot"))
+sim_for_plot %<>%
+  select(-c(avg_cv_sp, sync)) %>%
+  left_join(
+    tar_read(sim_fw) %>%
+      select(sim_id, ct_alive)
+  )
+```
+```{r}
+sim_for_plot %>%
+  filter(env_stoch == .6, h == 2, Z == 1, S == 10, rho == 0) %>%
+  arrange(desc(async))
+low_z_low_rich <- sim_for_plot %>%
+  filter(env_stoch == .6, Z == 1, S == 10, rho == 0) %>%
+  arrange(desc(async))
+
+tu <- timespecies_mat_to_long_tibble(low_z_low_rich$species[[1]])
+plot_timeseries_lg_tbl(tu)
+```
+
+```{r}
+sim_for_plot %>%
+  filter(env_stoch == .6, h == 2, Z == 100, S == 10, rho == 0) %>%
+  arrange(desc(async))
+high_z_low_rich <- sim_for_plot %>%
+  filter(env_stoch == .6, h == 2, Z == 100, S == 10, rho == 0) %>%
+  arrange(desc(async))
+
+plot_timeseries_lg_tbl(timespecies_mat_to_long_tibble(high_z_low_rich$species[[1]]))
+```
+
+```{r}
+sim_for_plot %>%
+  filter(env_stoch == .6, h == 2, Z == 100, S == 40, rho == 0) %>%
+  arrange(desc(async))
+high_z_high_rich <- sim_for_plot %>%
+  filter(env_stoch == .6, h == 2, Z == 100, S == 40, rho == 0) %>%
+  arrange(desc(async))
+plot_timeseries_lg_tbl(timespecies_mat_to_long_tibble(high_z_high_rich))
+```
+
+```{r}
+low_z_high_rich <- sim_for_plot %>%
+  filter(env_stoch == .6, h == 2, Z == 1, S == 40, rho == 0) %>%
+  arrange(desc(async))
+
+low_z_high_rich_mat <- get_mat_list(low_z_high_rich)
+plot_timeseries_lg_tbl(timespecies_mat_to_long_tibble(low_z_high_rich_mat[[1]]))
+```
+
+```{r}
+p_low_z_low_rich <- plot_sim(x = sim_for_plot,
+  id = low_z_low_rich$sim_id[[1]],
+  col_palette = NULL,
+  node_size_scale = .3
+)
+p_low_z_high_rich <- plot_sim(x = sim_for_plot,
+  id = low_z_high_rich$sim_id[[2]],
+  col_palette = NULL,
+  node_size_scale = .5
+)
+p_high_z_low_rich <- plot_sim(
+  x = sim_for_plot,
+  id = high_z_low_rich$sim_id[[1]],
+  col_palette = NULL,
+  node_size_scale = .3)
+p_high_z_high_rich <- plot_sim(
+  x = sim_for_plot,
+  id = high_z_high_rich$sim_id[[1]],
+  col_palette = NULL,
+  node_size_scale = .4
+)
+
+p_sim_example <- plot_grid(
+  p_low_z_low_rich, p_low_z_high_rich,
+  p_high_z_low_rich, p_high_z_high_rich,
+  labels = c("b", "", "", ""),
+  align = "hv"
+)
+
+ggsave_multiple(
+  paste0("p_sim_example", c(".png", ".pdf")),
+  plot = p_sim_example,
+  path = here::here("report", "figures"),
+  scale = 2.6,
+  dpi = 400,
+  width = 80,
+  height = 80 * .5,
+  units = "mm")
+```
+
+```{r}
+sim_for_plot %>%
+  filter(Z == 100, env_stoch == 0.6, rho %in% c(0, 1), S == 10, h == 2) %>%
+  group_by(fw_id) %>%
+  summarise(n = n()) %>%
+  filter(n > 1)
+sim_for_plot %>%
+  filter(env_stoch == 0.6, rho %in% c(0, .75), S == 10, h == 3) %>%
+  group_by(fw_id) %>%
+  summarise(n = n()) %>%
+  filter(n > 1)
+fwid <- 549
+z <- 25
+sim_for_plot %>%
+  filter(fw_id == fwid, Z == z, env_stoch == 0.6, rho %in% c(0, 1), S == 10, h == 2)
+
+high_resp_div_low_rich <- sim_for_plot %>%
+  filter(fw_id == fwid, Z == z, env_stoch == 0.6, rho == 0)
+  #filter(env_stoch == .6, Z == 1, S == 10, rho == 0) %>%
+  #arrange(desc(async))
+p_high_resp_div_low_rich <- plot_sim(
+  x = sim_for_plot,
+  id = high_resp_div_low_rich$sim_id[[1]],
+  col_palette = NULL,
+  node_size_scale = .2
+)
+
+low_resp_div_low_rich <- sim_for_plot %>%
+  filter(fw_id == fwid, Z == z, env_stoch == 0.6, rho == 1) %>%
+  arrange(desc(async))
+p_low_resp_div_low_rich <- plot_sim(
+  x = sim_for_plot,
+  id = low_resp_div_low_rich$sim_id[[1]],
+  col_palette = NULL,
+  node_size_scale = .2
+)
+
+p_sim_rho_example <- plot_grid(
+  p_low_resp_div_low_rich, p_high_resp_div_low_rich,
+  labels = c("a", ""),
+  align = "hv"
+)
+ggsave_multiple(
+  paste0("p_sim_rho_example", c(".png", ".pdf")),
+  plot = p_sim_rho_example,
+  path = here::here("report", "figures"),
+  scale = 2.6,
+  dpi = 400,
+  width = 80,
+  height = 80 * .3,
+  units = "mm")
+```
+
+```{r}
+p_methods <- plot_grid(p_sim_rho_example, p_sim_example, nrow = 2, rel_heights = c(1, 2))
+ggsave_multiple(
+  paste0("p_methods", c(".png", ".pdf")),
+  plot = p_methods,
+  path = here::here("report", "figures"),
+  scale = 2.6,
+  dpi = 400,
+  width = 80,
+  height = 80 * .6,
+  units = "mm")
+```
+
+```{r}
+tar_read(sim_fw) %>%
+  filter(env_stoch == .6, S == 10, Z == 100) %>%
+  ggplot(aes(y = pop_stab, x = as.factor(resp_div), color = as.factor(h))) +
+  geom_boxplot()
+```
+
 ```{r}

### 2023-11-23 R/plotting_methods.R

@@ -12,3 +12,132 @@ rho_cat_colors <- function() {
 resp_div_cat_colors <- function() {
   rho_cat_colors()
 }
+
+timespecies_mat_to_long_tibble <- function(x) {
+  x %>%
+    as_tibble() %>%
+    mutate(timestep = seq_len(nrow(.))) %>%
+    pivot_longer(
+      -timestep,
+      names_to = "species",
+      values_to = "biomass"
+    )
+}
+
+plot_timeseries_lg_tbl <- function(x, text_font_size = 8) {
+  x %>%
+    ggplot(aes(x = timestep, y = biomass, color = species)) +
+    geom_line() +
+    labs(x = "Timesteps", y = "Biomass") +
+    theme_half_open(font_size = text_font_size) +
+    theme(legend.position = "none")
+
+}
+
+get_stab_fw_label <- function(
+  x = sim_for_plot,
+  id = 1,
+  var = c(
+    "richness", "Z", "ct_alive", "w_avg_tlvl", "avg_int_strength",
+    "stab_com", "pop_stab", "async", "sae_total", "cpe"
+    ),
+  sep = ": "
+  ) {
+  out <- x %>%
+    filter(sim_id == id) %>%
+    select(where(is.numeric)) %>%
+    pivot_longer(everything()) %>%
+    deframe()
+  out <- out[var]
+  paste0(
+    var_replacement()[names(out)], sep,
+    map_chr(signif(out, digits = 2), ~format(.x, scientific = FALSE)),
+    collapse = "\n"
+)
+}
+
+get_mat_list <- function(x, var = species) {
+  out <- x %>%
+    pull({{var}})
+  names(out) <- x %>%
+    pull(sim_id)
+  out
+}
+
+# Code to plot network
+source("https://raw.githubusercontent.com/alaindanet/fishcom/master/R/codeWeb.R")
+
+plot_sim <- function(x = sim_for_plot,
+  id = 6827,
+  col_palette = NULL,
+  node_size_scale = .5,
+  font_size = 10
+  ) {
+  # get the good sim
+  sim <- x %>%
+    filter(sim_id == id)
+  # Get the matrix
+  mat <- get_mat_list(sim)[[1]]
+
+  # Get species color
+  if (is.null(col_palette)) {
+    col_palette <- paletteer::paletteer_dynamic("cartography::multi.pal", ncol(mat))
+    col_palette <- setNames(col_palette, paste0("V", seq(1, ncol(mat))))
+  }
[…]

### 2023-11-24 use_case/cpe_decomposition.Rmd

@@
 ```{r}
-data_raw <- open_dataset(here::here("res", "simCSZenrich2", "sim_toy_compensatory_dyn.arrow"),
+data_raw <- open_dataset(
+  here::here("use_case", "sim_toy_compensatory_dyn.arrow"),
   format = "arrow") %>%
@@
 ```
+
+```{r}
+source(here::here("R", "plotting_methods.R"))
+```
+
+```{r}
+ti <- data_raw %>%
+  filter(rho == 0, Z == 10, env_stoch == .6)
+nice_ts <- ti$species[[2]] %>%
+  .[, colSums(.) > 0] %>%
+  as_tibble() %>%
+  mutate(time = 1:n()) %>%
+  pivot_longer(-time, names_to = "species", values_to = "biomass")
+p_nice_ts_sp <- nice_ts %>%
+  ggplot(aes(y = biomass, x = time, color = species)) +
+  geom_line() +
+  labs(y = "Biomass", x = "Time") +
+  theme_half_open() +
+  theme(
+    legend.position = "none",
+    axis.ticks = element_blank(),
+    axis.text = element_blank(),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank()
+  )
+ggsave_multiple(
+  c("p_nice_ts_sp.png", "p_nice_ts_sp.pdf"),
+  plot = p_nice_ts_sp,
+  path = here::here("use_case", "figures"),
+  scale = 1.5,
+  dpi = 600,
+  width = 88,
+  height = 88 * .5,
+  units = "mm"
+)
+
+sum_nice_ts <- nice_ts %>%
+  group_by(time) %>%
+  summarise(biomass = sum(biomass))
+
+p_sum_nice_ts <- sum_nice_ts %>%
+  ggplot(aes(y = biomass, x = time)) +
+  geom_line(color = "black") +
+  labs(y = "Biomass", x = "Time") +
+  theme_half_open() +
+  theme(
+    axis.ticks = element_blank(),
+    axis.text = element_blank(),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank()
+  )
+ggsave_multiple(
+  c("p_sum_nice_ts.png", "p_sum_nice_ts.pdf"),
+  plot = p_sum_nice_ts,
+  path = here::here("use_case", "figures"),
+  scale = 1.5,
+  dpi = 600,
+  width = 88,
+  height = 88 * .5,
+  units = "mm"
+)
+
+p_hist_biomass <- sum_nice_ts %>%
+  ggplot(aes(x = biomass)) +
+  geom_histogram(bins = 50, fill = "black") +
+  labs(x = "Biomass", y = "") +
+  theme_void() +
+  theme(
+    axis.ticks = element_blank(),
+    axis.text = element_blank(),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank()
+  )
+
+ggsave_multiple(
+  c("p_hist_biomass.png", "p_hist_biomass.pdf"),
+  plot = p_hist_biomass,
+  path = here::here("use_case", "figures"),
+  scale = 1,
+  dpi = 600,
+  width = 88,
+  height = 88 * 1,
+  units = "mm"
+)
+```

### 2023-12-06 _targets.Rmd
Update figures with new sims

--- 2023-11-22 _targets.Rmd
@@
       data = sim_fw %>%
-        select(-productivity) %>%
         mutate(across(c(stab_com, richness), log)) %>%
@@
       env_stoch = c(.1, .6),
-      w_avg_tlvl = c(1.5, 2, 3),
-      Z = c(10, 100),
+      w_avg_tlvl = c(1.0, 1.5, 2.3),
+      Z = c(1, 10, 100),
       h = c(2, 3),
@@
       resp_div = seq(0, 1, length.out = 50),
-      w_avg_tlvl = seq(1.5, 3.5, length.out = 50)
+      w_avg_tlvl = seq(1.0, 2.5, length.out = 50)
       ) %>%
@@
       "env_stoch" = .3,
-      "ct_alive" = .2,
+      "ct_alive" = .1,
       "avg_int_strength" = .01,
       "h" = 2,
-      "w_avg_tlvl" = 2,
+      "w_avg_tlvl" = 1,
       "Z" = 100
@@
             values = list(
-              seq(0.01, 0.2, length.out = 50),
-              seq(1.5, 3.5, length.out = 50),
-              seq(.02, .3, length.out = 50)
+              seq(0.01, 0.1, length.out = 50),
+              seq(1.0, 2.5, length.out = 50),
+              seq(.02, .35, length.out = 50)
             )
@@
       theme_bw()),
-    tar_target(p_prod_bm,
-      sim_fw %>%
-        filter(bm_total > 10^-5) %>%
-        ggplot(aes(x = as.factor(productivity), y = log(bm_total))) +
-        geom_boxplot() +
-        labs(x = "Productivity", y = "Total biomass") +
-        theme_bw()
-      ),
-    tar_target(p_prod_pop_stab,
-      sim_fw %>%
-        ggplot(aes(x = as.factor(productivity), y = log(pop_stab))) +
-        geom_boxplot() +
-        labs(x = "Productivity", y = "Population stability") +
-        theme_bw()
-    ),
     tar_target(p_stab_comp_stress,
@@
         p_stoch_pop_stab,
-        p_prod_bm,
-        p_prod_pop_stab,
         labels = "auto"
@@
         sim_fw %>%
-          filter(rho %in% c(0, 1), productivity == 5, env_stoch == .5) %>%
+          filter(rho %in% c(0, 1), env_stoch == .5) %>%
           ggplot(aes(x = richness, y = stab_com, color = as.factor(1 - rho))) +
@@
 sim_fw %>%
-  filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
+  filter(rho %in% c(0), env_stoch == .5) %>%
   pivot_longer(c(stab_com, async, sae_total, cpe,
@@
 sim_fw %>%
-  filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
+  filter(rho %in% c(0), env_stoch == .5) %>%
   pivot_longer(c(richness, ct_alive, max_tlvl, avg_omnivory, w_avg_tlvl
@@
 tar_make()
+tar_make_future(workers = 3)
 ```
@@
 
+```{r debug, eval = FALSE}
+tar_load(sim_fw)
+ti <- sim_fw %>%
+  mutate(across(c(stab_com, richness), log)) %>%
+  mutate(across(c(sim_id, fw_id), as.factor)) %>%
+  mutate(
+    across(c(stab_com, richness,
+        env_stoch, resp_div, Z,
+        ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
+      ~scale(.x)[, 1])
+  )
+tar_load(stab_com_part_var)
+tu <- map(stab_com_part_var,
+  ~glmmTMB(formula_stab_fw_model(
+      resp = .x,
+      rand_effect = TRUE,
+      term_to_del = "richness : resp_div : Z +"
+      ),
+    data = ti
+    ))
+```
+
 ```{r}
@@
 tar_load(pred_stab_comp_rho)
+```
+
+```{r plot-sim}
+load(here("data", "sim_for_plot"))
+length(unique(sim_for_plot$sim_id))
+sim_for_plot %<>%
+  left_join(
+    tar_read(sim_fw)
+  )
+stoch <- 0.3
+hill <- 2
+env_corr <- 0
+unique(sim_for_plot$env_stoch)
+```
+
+```{r}
+sim_for_plot %>%
+  filter()
+
+```
+
+```{r}
+sim_for_plot %>%
+  filter(env_stoch == !!stoch, h == hill, Z == 1, rho == env_corr) %>%
+  arrange(fw_id)
+low_z_low_rich <- sim_for_plot %>%
+  filter(env_stoch == !!stoch, h == hill, Z == 1, rho == env_corr, richness == 10) %>%
+  arrange(desc(max_tlvl), richness)
+tu <- timespecies_mat_to_long_tibble(low_z_low_rich$species[[1]])
+plot_timeseries_lg_tbl(tu)
+```
+
+```{r}
+low_z_high_rich <- sim_for_plot %>%
+  filter(env_stoch == !!stoch, h == hill, Z == 1, rho == env_corr) %>%
+  # For plotting purpose, not too much species
+  filter(richness > 15) %>%
+  arrange(desc(max_tlvl), desc(richness))
+
+low_z_high_rich_mat <- get_mat_list(low_z_high_rich)
+plot_timeseries_lg_tbl(timespecies_mat_to_long_tibble(low_z_high_rich_mat[[2]]))
+```
+
+```{r}
+sim_for_plot %>%
+  filter(env_stoch == !!stoch, h == hill, Z == 100,
+    rho == env_corr, richness == 10) %>%
+  arrange(desc(max_tlvl))
+high_z_low_rich <- sim_for_plot %>%
+  filter(env_stoch == !!stoch, h == hill, Z == 100,
+    rho == env_corr, richness == 10) %>%
+  arrange(desc(max_tlvl))
+
+plot_timeseries_lg_tbl(timespecies_mat_to_long_tibble(high_z_low_rich$species[[3]]))
+```
+
+```{r}
+sim_for_plot %>%
+  filter(env_stoch == !!stoch, h == hill, Z == 100, rho == env_corr) %>%
+  # For plotting purpose, not too much species
+  filter(richness <= 20) %>%
+  arrange(desc(max_tlvl))
+high_z_high_rich <- sim_for_plot %>%
+  filter(env_stoch == !!stoch, h == hill, Z == 100, rho == env_corr) %>%
+  # For plotting purpose, not too much species
+  filter(richness == 20) %>%
+  arrange(desc(max_tlvl))
+plot_timeseries_lg_tbl(timespecies_mat_to_long_tibble(high_z_high_rich$species[[3]]))
+```
+
+```{r}
+sim_for_plot$int_strength[[1]] %>% dim
+p_low_z_low_rich <- plot_sim(x = sim_for_plot,
+  id = low_z_low_rich$sim_id[[1]],
+  col_palette = NULL,
+  node_size_scale = .3,
+  tmax = 200
+)
+p_low_z_high_rich <- plot_sim(x = sim_for_plot,
+  id = low_z_high_rich$sim_id[[2]],
+  col_palette = NULL,
+  node_size_scale = .5
+)
+p_high_z_low_rich <- plot_sim(
+  x = sim_for_plot,
+  id = high_z_low_rich$sim_id[[5]],
+  col_palette = NULL,
+  node_size_scale = .3)
+p_high_z_high_rich <- plot_sim(
+  x = sim_for_plot,
+  id = high_z_high_rich$sim_id[[3]],
+  col_palette = NULL,
+  node_size_scale = .4
+)
+
+word_label_size <- 11
+p_sim_example <- plot_grid(
+  p_low_z_low_rich + draw_label(
+    "Low PPMR", fontface = 'bold', x = 0, y = .5,
+    hjust = .5, vjust = 1, angle = 90, size = word_label_size) +
+  draw_label("Low richness", fontface = 'bold', x = 0.5, y = 1,
+    hjust = 0.5, vjust = 1, angle = 0, size = word_label_size),
+  p_low_z_high_rich + draw_label("High richness", fontface = 'bold', x = 0.5, y = 1,
+    hjust = 0.5, vjust = 1, angle = 0, size = word_label_size),
+  p_high_z_low_rich + draw_label(
+    "High PPMR", fontface = 'bold', x = 0, y = .5,
+    hjust = .5, vjust = 1, angle = 90, size = word_label_size),
+  p_high_z_high_rich,
+  labels = c("b", "", "", ""),
+  align = "hv"
+)
+
+ggsave_multiple(
+  paste0("p_sim_example", c(".png", ".pdf")),
+  plot = p_sim_example,
+  path = here::here("report", "figures"),
+  scale = 2.6,
+  dpi = 400,
+  width = 80,
+  height = 80 * .5,
+  units = "mm")
+```
+
+```{r}
+sim_for_plot %>%
+  filter(Z == 100, env_stoch == 0.3, rho %in% c(0, 1), S == 10, h == 2) %>%
+  group_by(fw_id) %>%
+  summarise(n = n()) %>%
+  filter(n > 1)
+sim_for_plot %>%
+  filter(env_stoch == 0.3, rho %in% c(0, 1), S == 10, h == 3) %>%
+  group_by(fw_id) %>%
+  summarise(n = n()) %>%
+  filter(n > 1)
+fwid <- 6
+z <- 10
+sim_for_plot %>%
+  filter(fw_id == fwid, Z == z, env_stoch == 0.6, rho %in% c(0, 1), S == 10, h == 2)
+
+high_resp_div_low_rich <- sim_for_plot %>%
+  filter(fw_id == fwid, Z == z, env_stoch == 0.6, rho == 0)
+  #filter(env_stoch == .6, Z == 1, S == 10, rho == 0) %>%
+  #arrange(desc(async))
+p_high_resp_div_low_rich <- plot_sim(
+  x = sim_for_plot,
+  id = high_resp_div_low_rich$sim_id[[1]],
+  col_palette = NULL,
+  node_size_scale = .2,
+  title = "High response diversity"
+)
+
+low_resp_div_low_rich <- sim_for_plot %>%
+  filter(fw_id == fwid, Z == z, env_stoch == 0.6, rho == 1) %>%
+  arrange(desc(async))
+p_low_resp_div_low_rich <- plot_sim(
+  x = sim_for_plot,
+  id = low_resp_div_low_rich$sim_id[[1]],
+  col_palette = NULL,
+  node_size_scale = .2,
+  title = "Low response diversity"
+)
+
+p_sim_rho_example <- plot_grid(
+  p_low_resp_div_low_rich,
+  p_high_resp_div_low_rich,
+  labels = c("a", ""),
+  align = "hv"
+)
+ggsave_multiple(
+  paste0("p_sim_rho_example", c(".png", ".pdf")),
+  plot = p_sim_rho_example,
+  path = here::here("report", "figures"),
+  scale = 2.6,
+  dpi = 400,
+  width = 80,
+  height = 80 * .3,
+  units = "mm")
+```
+
+```{r}
+p_methods <- plot_grid(p_sim_rho_example, p_sim_example, nrow = 2, rel_heights = c(1, 2))
+ggsave_multiple(
+  paste0("p_methods", c(".png", ".pdf")),
+  plot = p_methods,
+  path = here::here("report", "figures"),
+  scale = 3.0,
+  dpi = 400,
+  width = 80,
+  height = 80 * .6,
+  units = "mm")
+```
+
+```{r}
+tar_read(sim_fw) %>%
+  filter(env_stoch == .6, S == 10, Z == 100) %>%
+  ggplot(aes(y = pop_stab, x = as.factor(resp_div), color = as.factor(h))) +
+  geom_boxplot()
 ```
@@
   units = "mm")
-```
-
-```{r}
 ```
@@
 ```{r}
-tar_load(pred_data)
-p_pred_sr_resp_div_int_env <- pred_data %>%
+fw_values_bin <- list(
+  ct_alive = c(low = .05, high = 0.30),
+  avg_int_strength = c(low = .01, high = .1),
+  w_avg_tlvl = c(low = 1, high = 2.3),
+  resp_div = c(low = .25, high = 1)
+)
+
+pred_data_sr_fw <- pred_data %>%
   filter(
-    ct_alive %in% c(.1),
-    resp_div %in% c(0, .75),
+    ct_alive %in% fw_values_bin$ct_alive,
+    resp_div %in% fw_values_bin$resp_div,
     richness >= 1,
@@
     h %in% c(2),
-    avg_int_strength %in% c(.01, .1),
-    w_avg_tlvl == 2.0
-    ) %>%
-  ggplot(aes(
-      x = richness, y = stab_com,
-      color = as.factor(resp_div),
-      fill = as.factor(resp_div),
-      linetype = as.factor(avg_int_strength),
-      alpha = as.factor(avg_int_strength)
-      )) +
-  ylim(2, 8) +
-  geom_line(linewidth = .8) +
-  geom_ribbon(aes(ymin = stab_com - stab_com_se, ymax = stab_com + stab_com_se), alpha = .3, color = NA) +
-  scale_alpha_manual(values = c(1, 1), guide = "none") +
-  facet_grid(
-    cols = vars(env_stoch),
-    labeller = as_labeller(function(x) paste0("Environmental stochasticity: ", x))) +
-  labs(
-    x = "Species richness (Log)", y = "Community stability (Log)",
-    linetype = "Avg. Interaction strength",
-    color = "Environmental correlation", fill = "Environmental correlation"
-  ) +
-  theme_bw() +
-  theme(legend.position = "bottom")
-
-#pred_data$async <- predict(mod_tot_async, newdata = pred_data)
-#pred_data$pop_stab <- predict(mod_tot_pop_stab, newdata = pred_data)
-
-```
-
-```{r}
-pred_data_sr_fw <- pred_data %>%
-  filter(
-    ct_alive %in% c(.1, .3),
-    resp_div %in% c(1, .25),
-    richness >= 1,
-    Z == 100,
-    h %in% c(2),
-    avg_int_strength %in% c(.01, .1),
+    avg_int_strength %in% fw_values_bin$avg_int_strength,
     env_stoch == .1,
-    w_avg_tlvl %in% c(2.0, 3.0)
+    w_avg_tlvl %in% fw_values_bin$w_avg_tlvl
     ) %>%
@@
   group_ct_alive = case_when(
-    ct_alive == .3 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "High",
-    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
+    ct_alive == fw_values_bin$ct_alive["high"] &
+      avg_int_strength == fw_values_bin$avg_int_strength["low"] &
+      w_avg_tlvl == fw_values_bin$w_avg_tlvl["low"] ~ "High",
+    ct_alive == fw_values_bin$ct_alive["low"] &
+      avg_int_strength == fw_values_bin$avg_int_strength["low"] &
+      w_avg_tlvl == fw_values_bin$w_avg_tlvl["low"] ~ "Low"
     ),
   group_avg_int_strength = case_when(
-    ct_alive == .1 & avg_int_strength == .1 & w_avg_tlvl == 2.0 ~ "High",
-    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
+    ct_alive == fw_values_bin$ct_alive["low"] &
+      avg_int_strength == fw_values_bin$avg_int_strength["high"] &
+      w_avg_tlvl == fw_values_bin$w_avg_tlvl["low"] ~ "High",
+    ct_alive == fw_values_bin$ct_alive["low"] &
+      avg_int_strength == fw_values_bin$avg_int_strength["low"] &
+      w_avg_tlvl == fw_values_bin$w_avg_tlvl["low"] ~ "Low"
     ),
   group_w_avg_tlvl = case_when(
-    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 3.0 ~ "High",
-    ct_alive == .1 & avg_int_strength == .01 & w_avg_tlvl == 2.0 ~ "Low"
+    ct_alive == fw_values_bin$ct_alive["low"] &
+      avg_int_strength == fw_values_bin$avg_int_strength["low"] &
+      w_avg_tlvl == fw_values_bin$w_avg_tlvl["high"] ~ "High",
+    ct_alive == fw_values_bin$ct_alive["low"] &
+      avg_int_strength == fw_values_bin$avg_int_strength["low"] &
+      w_avg_tlvl == fw_values_bin$w_avg_tlvl["low"] ~ "Low"
     )) %>%
@@
   name = str_remove(name, "group_"),
-  resp_div_cat = str_replace_all(resp_div, resp_div_replacement())
+  resp_div_cat = str_replace_all(resp_div, resp_div_replacement()),
+  variable_values = case_when(
+    name == "ct_alive" & value == "Low" ~ fw_values_bin$ct_alive["low"],
+    name == "ct_alive" & value == "High" ~ fw_values_bin$ct_alive["high"],
+    name == "avg_int_strength" & value == "Low" ~ fw_values_bin$avg_int_strength["low"],
+    name == "avg_int_strength" & value == "High" ~ fw_values_bin$avg_int_strength["high"],
+    name == "w_avg_tlvl" & value == "Low" ~ fw_values_bin$w_avg_tlvl["low"],
+    name == "w_avg_tlvl" & value == "High" ~ fw_values_bin$w_avg_tlvl["high"]
+  )
 )
@@
 ```{r}
+pred_stab_comp_resp_div
+p_pred_sr_resp_div +
+  geom_point(
+    data = pred_data_sr_fw %>%
+      filter(richness == min(richness)) %>%
+      mutate(name = var_replacement()[name]) %>%
+      rename(variable = name),
+    aes(color = NULL, fill = NULL)
+  )
+
 p_pred_sr <- plot_grid(
   p_pred_data_sr_fw + theme(legend.position = "right"),
-  p_pred_sr_resp_div,
+  # Add location of the fw values of p_pred_data_sr_fw
+  p_pred_sr_resp_div +
+  geom_point(
+    data = pred_data_sr_fw %>%
+      filter(richness == min(richness)) %>%
+      mutate(name = var_replacement()[name]) %>%
+      rename(variable = name),
+    aes(color = NULL, fill = NULL)
+  ),
   nrow = 2,
@@
 sim_fw %>%
-  filter(env_stoch == 0.3, rho %in% c(0, .5, 1), productivity == 5) %>%
+  filter(env_stoch == 0.3, rho %in% c(0, .5, 1)) %>%
   ggplot(aes(x = richness, y = cpe_env, color = as.factor(rho))) +
@@
 
-sim_fw %>%
-  filter(env_stoch == .6, rho == 0) %>%
-  ggplot(aes(x = as.factor(productivity), y = pop_stab, color = as.factor(Z))) +
-  geom_boxplot() +
-  labs(x = "Productivity", y = "Population stability") +
-  theme_bw()
-
-sim_fw %>%
-  filter(env_stoch == .3, rho == 0) %>%
-  ggplot(aes(x = as.factor(productivity), y = stab_com, color = as.factor(Z))) +
-  geom_boxplot() +
-  labs(x = "Productivity", y = "Population stability") +
-  theme_bw()
-
-sim_fw %>%
-  filter(env_stoch == .2, rho == 0) %>%
-  ggplot(aes(x = as.factor(Z), y = pop_stab, color = as.factor(productivity))) +
-  geom_boxplot() +
-  labs(x = "Productivity", y = "Population stability") +
-  theme_bw()
-
-sim_fw %>%
-  filter(env_stoch == .2, rho == 0) %>%
-  ggplot(aes(x = as.factor(Z), y = avg_int_strength, color = as.factor(productivity))) +
-  geom_boxplot() +
-  labs(x = "Productivity", y = "Population stability") +
-  theme_bw()
-
-sim_fw %>%
-  filter(env_stoch == .2, rho == 0, bm_total > 10^-5) %>%
-  ggplot(aes(x = as.factor(Z), y = bm_total, color = as.factor(productivity))) +
-  geom_boxplot() +
-  labs(x = "Productivity", y = "Population stability") +
-  theme_bw()
-
-sim_fw %>%
-  filter(env_stoch == .2, rho == 0) %>%
-  ggplot(aes(x = as.factor(Z), y = evenness_sae, color = as.factor(productivity))) +
-  geom_boxplot() +
-  labs(x = "Productivity", y = "Population stability") +
-  theme_bw()
-
-sim_fw %>%
-  filter(env_stoch == .2, rho == 0) %>%
-  ggplot(aes(x = as.factor(productivity), y = cpe_int, color = as.factor(Z))) +
-  geom_boxplot() +
-  labs(x = "Productivity", y = "Population stability") +
-  theme_bw()
 ```

### 2023-12-06 R/plotting_methods.R

@@ -71,13 +71,25 @@ plot_sim <- function(x = sim_for_plot,
   id = 6827,
   col_palette = NULL,
   node_size_scale = .5,
-  font_size = 10
+  font_size = 10,
+  tmax = 200,
+  replace0by = 1e-6,
+  title = NULL
   ) {
   # get the good sim
   sim <- x %>%
     filter(sim_id == id)
   # Get the matrix
   mat <- get_mat_list(sim)[[1]]
+
+  if (!is.null(tmax)) {
+    mat <- mat[(nrow(mat) - tmax):nrow(mat), ]
+  }
+
+  if (!is.null(replace0by)) {
+    mat[mat == 0] <- replace0by
+  }
+
 
   # Get species color
   if (is.null(col_palette)) {
@@ -91,6 +103,11 @@ plot_sim <- function(x = sim_for_plot,
     scale_color_manual(values = col_palette) +
     scale_y_continuous(trans = "log10")
 
+  if (!is.null(title)) {
+    ts_plot <- ts_plot +
+      ggtitle(title)
+  }
+
   # Add the stability and food-web metrics
   ts_plot_metric <- ts_plot +
     coord_cartesian(
@@ -99,7 +116,7 @@ plot_sim <- function(x = sim_for_plot,
       clip = "off") +
     # This widens the right margin
     theme(plot.margin = unit(c(1, 12, 1, 1), "lines")) +
-    annotate("text", x = 202, y = 0,
+    annotate("text", x = nrow(mat) + 2, y = 0,
       label = get_stab_fw_label(x = x, id = id),
       #https://stackoverflow.com/a/65077171
       size = font_size / .pt - 1,
@@ -107,6 +124,7 @@ plot_sim <- function(x = sim_for_plot,
       lineheight = .8,
       vjust = 0
     )
+
 
   # Get the Food-web
   ## Adjency matrix

### 2023-12-07 paper/manuscript.Rmd
New introduction: highlighting research gap

@@
 
-Global environmental change including climate, land use and invasive species
-constitutes a suite of major threats to biodiversity and ecosystem functioning
-[@pachauri_climate_2015; @simmons_refocusing_2021]. A central feature of these
-threats is that they are predicted to dramatically increase variability in the
-environment that species face [@pachauri_climate_2015] with potential impacts on
-the stability of communities and associated impacts on biodiversity and
-functioning in these communities. Assessing the impacts of this variability on
-communities is challenging for several reasons.
+Global environmental change constitutes a suite of major threats to biodiversity
+and ecosystem functioning [@lee_ipcc_2023; @simmons_refocusing_2021]. A central
+feature of these threats is that they are predicted to dramatically increase
+variability in the environment that species face [@lee_ipcc_2023] with potential
+impacts on the stability of communities and associated impacts on biodiversity
+and functioning in these communities. Assessing the impacts of this variability
+on communities is challenging for several reasons.
 
-First, there are numerous definitions of community stability depending of the
-stressors considered. For example, resistance and resilience are typically used
-when a pulse perturbation is considered [@kefi_advancing_2019]. While in natural
-settings where press and pulse perturbations are simultaneously present,
-community variability measured as the coefficient of variation is typically used
-[@thibaut_understanding_2013]. Defined at the community scale, community
-variability can be partitioned into population stability and asynchrony
-[@thibaut_understanding_2013]. Synchronous population fluctuations will amplify
-the negative effects of environmental fluctuations on temporal community
-stability while compensatory dynamics and portfolio effects (i.e. asynchrony)
-will stabilise temporal fluctuations of community biomass [@shoemaker_long_2022;
-@zhao_biodiversity_2022]. Environmental forcing (such as food availability and
-warming) and land-use intensity was reported to synchronise population
-fluctuations [@benton_population_2001; @bluthgen_land_2016; @song_reduced_2015;
-@liu_aridity_2023] while habitat degradation tends to decrease population
-stability [@olivier_urbanization_2020]. Understanding the effects of global
-change on community temporal stability therefore require to account for their
-simultaneous effects on community and population scales [@kefi_advancing_2019;
-@simmons_refocusing_2021].
+First, the stability of communities is often evaluated using temporal
+variability the metric of interest (e.g. abundance or biomass), because most
+natural communities face persistent perturbations so that other stability
+metrics such as resilience and resistance are not always applicable
+[@arnoldi_resilience_2016]. Understanding temporal community variability,
+measured as the inverse of the coefficient of variation
+[@tilman_biodiversity_2006; @roscher_identifying_2011;
+@thibaut_understanding_2013; @zhao_biodiversity_2022], requires to scale down
+the focus to populations. Community stability can be mathematically partitionned
+into average population stability and asynchrony [@loreau_species_2008;
+@thibaut_understanding_2013; @zhao_biodiversity_2022], asynchrony measuring how
+much each species fluctuations are compensating each other at the community
+level. Population stability and asynchrony depend both on the number of species
+and their dominance [@loreau_species_2008; @thibaut_understanding_2013; @zhao_biodiversity_2022],
+the interactions among them [@thebault_trophic_2005;
+@thebault_relationship_2006; @loreau_species_2008; @danet_species_2021;
+@eschenbrenner_diversity_nodate] and on the way that species respond to
+environmental perturbations [response diversity, @ives_stability_2000;
+@elmqvist_response_2003; @ross_how_2023]. Therefore, accounting for the effects
+on community structure on population stability and asynchrony is crucial to
+improve our understanding of community stability in face of environmental
+change.
 
-Second, the relation between community stability and biodiversity in variable
-environment is contingent on species richness per se, on the effects of species
-richness on population stability and asynchrony, and ultimately
-on the diversity of species responses to environmental fluctuations [response
-diversity, @ives_stability_2000; @elmqvist_response_2003]. Increasing
-species richness has been reported to decrease population stability in
-experimental grasslands [@tilman_biodiversity_2006; @roscher_identifying_2011],
-while increasing population stability in natural settings
-[@houlahan_negative_2018] [add mechanisms?]. In turn, higher species richness
-often results in higher asynchrony, through portfolio effects (i.e. statistical
-averaging effects due to independent species fluctuations) and compensatory
-dynamics (due to species interactions and response
-diversity of species due to the environment) [@loreau_species_2008;
-@thibaut_understanding_2013]. Systematic increase in asynchrony with species
-richness is the mechanism that drives reported positive relationships between
-community stability and species richness [ref]. Anthropogenic pressures, such as
-eutrophication, has been reported to weakens the relationship between species
-richness and asynchrony in grasslands [@hautier_eutrophication_2014] but such
-empirical evidence remains scarce. However, stressors such as biotic
-homogenization [@buisson_toward_2013; @muthukrishnan_invasive_2020;
-@saladin_rapid_2020] and environmental forcing that decrease species response
-diversity should dampens the relationships between asynchrony and species
-richness [@ives_stability_2000; @thibaut_understanding_2013] due to a decrease
-in portfolio effects and compensatory effects. [Talk about the effects of
-evenness in temporal variability and evenness in abundance? e.g.,
-@zhao_biodiversity_2022; @thibaut_understanding_2013]. Because stressors can
-affect both community stability per se and how community stability scales with
-species richness, improving our understanding require to study both
-[@ives_stability_2007; @hautier_anthropogenic_2015].
+Average population stability is decreased by external forcing, such as the
+intensity and the frequency of perturbations [@ref]. Species richness can
+decrease [@tilman_biodiversity_2006; @loreau_species_2008], increase
+[@houlahan_negative_2018], or have little effects on population stability. This
+effect of species richness on population stability depends on the evenness of
+the community such as dominant species contribute more the average of the
+community than surbordinate species. At the core of ecological theory,
+population stability depends on internal forcing, here species interactions. The
+topogical structure and the distribution of interaction strength have tremendous
+effects on population stability, such as strong interaction strength are
+generally destabilising [@mccann_weak_1998; @mccann_reevaluating_1997;
+@thebault_trophic_2005]. In particular for food-webs, top-down and bottom-up
+controls can increase population stability.
 
-Third, the structure of species trophic interactions, that determines the
-distribution of biomass fluxes through communities, can also control stability.
-including levels of generalism, the distribution of interaction strengths and
-the prevalence of omnivory, can also influence stability. The degree of
-generalism of predator was shown to modulate stability-richness relationships
-[@thebault_trophic_2005], and generalist predators can synchronise the dynamics
-of their preys[@raimondo_interspecific_2004]. The strength and distribution of
-interaction strength was also shown to be strong driver of community stability,
-such as stronger interaction strengths can be destabilizing [@may_will_1972;
-@mccann_weak_1998]. Omnivory was also shown to drive higher population stability
-[@mccann_reevaluating_1997]. The effects of food-web structure on ecosystem
-stability has been mostly assessed with small modules [but see
-@eschenbrenner_diversity_nodate], and we know very little how food-web structure
-affects the relationships between species richness and temporal stability in
-complex food-webs. So understanding the effects of stressors on community
-stability and on community stability-richness relationships necessitate to
-account for food-web structure.
+Asynchrony in turn can be partitionned into portefolio effects and compensatory
+dynamics and is mostly determine by internal factors. Portefolio effects stems
+from the statistical averaging of independent population fluctuations
+[@doak_statistical_1998; @zhao_biodiversity_2022], thereby increasing
+asynchrony. Compensatory dynamics in turn captures population fluctuations that
+are more synchronous or asynchronous than expected for independant fluctuations,
+and can stem from species interactions and species responses to perturbations
+[@zhao_biodiversity_2022]. Response diversity captures how among species’
+differences in their response to the environmental variation, can underpin
+asynchronous dynamics if their responses are different but synchronous if their
+responses are similar. Theory and empirical data emerging around response
+diversity suggests it is  “core ecological mechanism underpinning many of the
+statistical explanations of the diversity–stability relationships”
+[@ives_stability_2000; @elmqvist_response_2003; @ross_how_2023]. In turn,
+the distribution and strength of species interactions can also modulate
+asynchrony through compensatory dynamics such as a strong asymetry of consumer
+preference can generate asynchrony in resource fluctuations [@mccann_weak_1998;
+@vasseur_environmental_2007], and a generalist consumer can in turn generate
+synchrony among its prey [@raimondo_interspecific_2004]. Competition can also
+have synchronising effects in strong species growth rates regime
+[@loreau_species_2008]. Finally, portefolio and compensatory effects can also be
+affected by the population evenness such as fluctuations of a dominant
+species will be hardly compensated by a subordinate species. Improving our
+understanding of community stability facing perturbations therefore requires to
+articulate the effect response diversity, species interactions, species
+richness and evenness on the different components of stability.
 
-Here we deliver inference from modelling of complex biodiverse communities on
-how food-web structure (connectance, average interaction strength, average
-trophic level), response diversity, and environmental stochasticity combine to
-shape temporal stability of community biomass, as well as its partition into
-asynchrony and population stability. We then assess how food-web complexity and
-response diversity shape stability-richness relationships.
+The stability of ecological communities facing perturbations stems from two
+parallel bodies of work: species interactions and response diversity. These two
+bodies of work share the common thread of community structure acting through a
+filter to drive stability. However, the filter is different in each space; in
+the first, the filter is the topology and the strength of species interactions
+and in the second variation in species’ responses. Moreover, the theory has been
+developed largely in theoretical or empirical communities characterised by a
+limited array of interactions (e.g. often lacking in consumers) and by limited
+species diversity/richness. Thus, ecology lacks a body of theory integrating
+across structure and response diversity frameworks and reflecting species rich
+communities. Here, we integrate these two perspectives on diversity - stability
+to evaluate the combined effects of community structure and response diversity on
+temporal stability in species rich, complex communities characterised by
+competition and predation.
+
+The ability to do this is supported by a key statistical advance: it is now
+possible to partition asynchrony into two component sources, the statistical
+averaging effect (SAE) and compensatory dynamics effect (CPE)
+[@zhao_biodiversity_2022]. SAE quantifies the portfolio effect emerging from
+independent species fluctuations, while CPE describes compensatory dynamics
+emerging from species interactions and differential responses to environmental
+stochasticity. This allows an unprecedented opportunity to obtain mechanistic
+insight about the effects of stressors and food-web structure on stability in
+complex, species rich communities.
+
+Our primary objective is to derive theory that predicts how the components of
+community stability, that can differentially drive patterns of stability, deliver novel
+insights into the source and patterns of diversity-stability relationships in
+complex communities facing environmental stochasticity. Our approach delivers
+revised insight into diversity-productivity relationships in species rich
+communities when both community structure per se, and species
+responses can vary. In the following sections, we begin by introducing the
+multi-species model and the features of the model that allow us to integrate
+across variation in community structure and response diversity. We
+then introduce assumptions we use to implement environmental stochasticity,
+response diversity, variation in community structure and variation in the
+distribution of interaction types and strengths. Next we define our in-silico
+experimental design that specifically aligns with three core questions and
+associated analyses: (1) What are the direct effects of food-web structure and
+interaction strength on population stability, compensatory dynamics,
+and statistical averaging effects (i.e. portefolio effects)? (2) What are the
+total effects of food-web structure, reponse diversity, environmental
+stochasticity on community stability. Finally merging the two parallel bodies of
+work, we asked (3) How do response diversity and food-web structure interact to
+drive the sign of the relation between community stability and
+species richness?
+
+---
+
+#Here we deliver inference from modelling of complex biodiverse communities on
+#how food-web structure (connectance, average interaction strength, average
+#trophic level), response diversity, and environmental stochasticity combine to
+#shape temporal stability of community biomass, as well as its partition into
+#asynchrony and population stability. We then assess how food-web complexity and
+#response diversity shape stability-richness relationships.
+
+#Environmental forcing (such as food availability and
+#warming) and land-use intensity was reported to synchronise population
+#fluctuations [@benton_population_2001; @bluthgen_land_2016; @song_reduced_2015;
+#@liu_aridity_2023] while habitat degradation tends to decrease population
+#stability [@olivier_urbanization_2020]. Understanding the effects of global
+#change on community temporal stability therefore require to account for their
+#simultaneous effects on community and population scales [@kefi_advancing_2019;
+#@simmons_refocusing_2021].
+
+#Increasing species richness has been reported to decrease population stability
+#in experimental grasslands [@tilman_biodiversity_2006;
+#@roscher_identifying_2011], while increasing population stability in natural
+#settings [@houlahan_negative_2018] [add mechanisms?]. In turn, higher species
+#richness often results in higher asynchrony, through portfolio effects (i.e.
+#statistical averaging effects due to independent species fluctuations) and
+#compensatory dynamics (due to species interactions and response diversity of
+#species due to the environment) [@loreau_species_2008;
+#@thibaut_understanding_2013]. Systematic increase in asynchrony with species
+#richness is the mechanism that drives reported positive relationships between
+#community stability and species richness [ref]. Anthropogenic pressures, such as
+#eutrophication, has been reported to weakens the relationship between species
+#richness and asynchrony in grasslands [@hautier_eutrophication_2014] but such
+#empirical evidence remains scarce. However, stressors such as biotic
+#homogenization [@buisson_toward_2013; @muthukrishnan_invasive_2020;
+#@saladin_rapid_2020] and environmental forcing that decrease species response
+#diversity should dampens the relationships between asynchrony and species
+#richness [@ives_stability_2000; @thibaut_understanding_2013] due to a decrease
+#in portfolio effects and compensatory effects. [Talk about the effects of
+#evenness in temporal variability and evenness in abundance? e.g.,
+#@zhao_biodiversity_2022; @thibaut_understanding_2013]. Because stressors can
+#affect both community stability per se and how community stability scales with
+#species richness, improving our understanding require to study both
+#[@ives_stability_2007; @hautier_anthropogenic_2015].
+
+#including levels of generalism, the distribution of interaction strengths and
+#the prevalence of omnivory, can also influence stability. The degree of
+#generalism of predator was shown to modulate stability-richness relationships
+#[@thebault_trophic_2005], and generalist predators can synchronise the dynamics
+#of their preys[@raimondo_interspecific_2004]. The strength and distribution of
+#interaction strength was also shown to be strong driver of community stability,
+#such as stronger interaction strengths can be destabilizing [@may_will_1972;
+#@mccann_weak_1998]. Omnivory was also shown to drive higher population stability
+#[@mccann_reevaluating_1997]. The effects of food-web structure on ecosystem
+#stability has been mostly assessed with small modules [but see
+#@eschenbrenner_diversity_nodate], and we know very little how food-web structure
+#affects the relationships between species richness and temporal stability in
+#complex food-webs. So understanding the effects of stressors on community
+#stability and on community stability-richness relationships necessitate to
+#account for food-web structure.
+---
 
 \pagebreak
+
+```{r}
+met_cap <- "Examples of stochastic food-web simulations. a, Simulations with low
+and high response diversity. b, simulations with low and high predator-prey mass
+ratio (upper and bottom panels), low and high species richness (left and right
+  panels). The food-web are displayed on the side with the node size
+being proportional to the average species biomass across the simulation. We
+also display the food-web structure and the stability metrics. Across all
+simulations, $h = 2$, $\\sigma_e = .3$. Low and high response diversity were
+respectively $\\rho = 1$ and $\\rho = 0$. Low and high PPMR were respectively 1 and 100." %>%
+  str_replace_all("\\s+", " ")
+```
+
+```{r met, fig.cap = met_cap}
+knitr::include_graphics(here("report", "figures", "p_methods.pdf"))
+```
 
@@
 natural mortality rates scales inversely with the species body mass ($d_i =
-d_0M_i^{-1/4}$, ), as all other physiological parameters. We used a basal
+d_0M_i^{-1/4}$), as all other physiological parameters. We used a basal
 natural mortality rate of $d_0 = .4$, as done in previous
@@
 and $h=3$, eq XX) as it was shown to have a tremendous role on stability
-[@brose_allometric_2006]. We set $K = XX$ to ensure that consumers were not
+[@brose_allometric_2006]. We set $K = 10$ to ensure that consumers were not
 limited by the biomass input from primary producers.
@@
 
-We numerically solved the simulations with a $dt$ = .1 during 5000 timesteps
-and collected the last 500 timesteps. We set extinction threshold to $10^{-5}$
-and if an extinction happened in the last 500 timesteps, we continued to run the
-simulation for another 500 timesteps until there was no extinction events.
+We numerically solved the simulations during 5000 timesteps
+and collected the last 500 timesteps. We set $d_t = .1$, and $d_t = .05$ when
+instability was detected during the simulations. We set extinction threshold to
+$10^{-6}$ and if an extinction happened in the last 500 timesteps, we continued
+to run the simulation for another 1000 timesteps until there was no extinction
+events. When we found disconnected species at the end of the simulation (i.e. a
+primary producer without consumer or a consumer without prey), we removed them
+and re-run simulation for another 1000 timesteps.
 
@@
 compensatory dynamics due to interactions ($CPE_{int}$). Finally, we tested the
-effects of species richness and species cross-correlation in mortality rates on
+effects of species richness and species response diversity in mortality rates on
 the compensatory dynamics due to stochastic fluctuations ($CPE_{env}$). We
@@
 average interaction strength, as well as environmental stochasticity and species
-cross-correlation. We further included the two way interactions between species
+response diversity. We further included the two way interactions between species
 richness and food-web structure, plus between species richness and stressors.
@@
   exponent, variance of stochastic mortality rates (Env. stochasticity), and
-  cross-correlation among species mortality rates (Env. correlation). We only
+  species response diversity. We only
   displayed standardised coefficients whose absolute values are superior to 0.1
@@
 rci <- get_eff(y = "cpe", x = "avg_int_strength")
-rco <- get_eff(y = "cpe", x = "rho")
+rcd <- get_eff(y = "cpe", x = "resp_div")
 
@@
 rvr <- get_eff(y = "cpe_env", x = "richness", tab = sem_eff_tab)
-rvo <- get_eff(y = "cpe_env", x = "rho", tab = sem_eff_tab)
+rvd <- get_eff(y = "cpe_env", x = "resp_div", tab = sem_eff_tab)
 ```
@@
 positive effect on compensatory dynamics ($r_\delta$= `r rci`, Fig.
-\@ref(fig:sem)). Cross-correlation among species mortality rates (i.e. lower
-response diversity) had a strong negative effect on compensatory dynamics
-($r_\delta$= `r rco`), meaning that the loss of response diversity result in a
-strong decrease in compensatory dynamics.
+\@ref(fig:sem)). Species response diversity had a strong positive effect on compensatory dynamics
+($r_\delta$= `r rcd`).
 
@@
 ```{r}
-rtsrho <- get_eff(y = "stab_com", x = "rho", effect_type = "total")
+rtsdiv <- get_eff(y = "stab_com", x = "resp_div", effect_type = "total")
 rtsenv <- get_eff(y = "stab_com", x = "env_stoch", effect_type = "total")
@@
 Deriving the sum of direct and indirect effects from the structural equation
-model, we show that both environmental stochasticity and cross-correlation among
-species had by far the most negative effect on community stability (resp.
-$r_\delta$= `r rtsenv` and `r rtsrho`, Fig. \@ref(fig:semtot)). Species richness
+model, we show that both environmental stochasticity and response diversity among
+species had by far the most important effect on community stability (resp.
+$r_\delta$= `r rtsenv` and `r rtsdiv`, Fig. \@ref(fig:semtot)). Species richness
 had a low overall positive total effect on community stability (`r rtsr`)
@@
   ", Predator-Prey Mass Ration = ", pv["Z"],
-  ", environmental correlation = ", pv["rho"],
+  ", response diversity = ", pv["resp_div"],
   ", and environmental stochasticity = ", pv["env_stoch"]
@@
 
-Using a more complex linear model (i.e. including interactions), we investigated more
-in detail the relationship between community stability and species richness and
-how this relation is affected by environmental stochasticity and cross
-correlation among species mortality rates. We found that environmental
-stochasticity decrease overall community stability but has only little effect on
-the shape of the community stability-species richness relationship (put some
-numbers, Fig. \@ref(fig:pred)a and b). In contrasts, cross correlation among
-species mortality rates both decreases overall community stability and nullifies
-the community stability-species richness relationship. Surprisingly, we found that
-despite average interaction strength has a small overall effect on
-community stability, high average interaction strength change the shape of the
-community stability-species richness relationship from positive to negative when
-response diversity is low (put some numbers, Fig. \@ref(fig:pred)b).
+Using a more complex linear model (i.e. including interactions), we investigated
+more in detail the relationship between community stability and species richness
+and how this relation is affected by environmental stochasticity and species
+response diversity. We found that environmental stochasticity decrease overall
+community stability but has only little effect on the shape of the community
+stability-species richness relationship (put some numbers, Fig. \@ref(fig:pred)a
+and b). In contrasts, species response diversity both increases overall
+community stability and leads to positive community stability-species richness
+relationships. Surprisingly, we found that despite average interaction strength
+has a small overall effect on community stability, high average interaction
+strength change the shape of the community stability-species richness
+relationship from positive to negative when response diversity is low (put some
+numbers, Fig. \@ref(fig:pred)b).
 

### 2023-12-12 _targets.Rmd
New SEM figure and prettier method figure

@@
       "env_stoch" = .3,
-      "ct_alive" = .1,
+      "ct_alive" = .05,
       "avg_int_strength" = .01,
       "h" = 2,
-      "w_avg_tlvl" = 1,
+      "w_avg_tlvl" = 1.0,
       "Z" = 100
@@
 
-```{r}
-
+## Partial residuals SEM
+
+```{targets partial_sem_relations}
+list(
+  tar_target(scaled_sim_fw_sem,
+    sim_fw_sem %>%
+      mutate(across(where(is.numeric), ~scale(.x)[, 1]))
+    ),
+  tar_target(scaled_sem_simplified_model_list,
+    map(sem_simplified_model_list,
+      ~update(.x, data = scaled_sim_fw_sem)
+      )),
+  tar_target(scaled_sem_simplified,
+    as.psem(scaled_sem_simplified_model_list)
+    ),
+  tar_target(formula_sem_bivariate_relations,
+    c(
+      "pop_stab ~ w_avg_tlvl",
+      "pop_stab ~ h",
+      "pop_stab ~ env_stoch",
+      "sae_total ~ richness",
+      "sae_total ~ ct_alive",
+      "sae_total ~ w_avg_tlvl",
+      "sae_total ~ avg_int_strength",
+      "cpe ~ avg_int_strength",
+      "cpe ~ resp_div"
+    )
+    )#,
+  #tar_target(partial_resid_sem_simplified, {
+  #  partialResid(as.formula(formula_sem_bivariate_relations),
+  #          modelList = scaled_sem_simplified,
+  #          data = scaled_sim_fw_sem
+  #        )},
+  #        pattern = map(formula_sem_bivariate_relations)
+  #),
+  #tar_target(sem_simplified_bivariate_relations,
+  #  tibble(sem_formula = formula_sem_bivariate_relations) %>%
+  #    separate(
+  #      col = sem_formula,
+  #      into = c("response", "predictor"),
+  #      sep = " ~ ", remove = FALSE) %>%
+  #  mutate(
+  #    data = partial_resid_sem_simplified,
+  #    coefs = map2(response, predictor,
+  #      ~coefficients(scaled_sem_simplified[[.x]])[c("(Intercept)", .y)]
+  #      ),
+    #  plot = pmap(list(
+    #      data = data,
+    #      response = response,
+    #      predictor = predictor,
+    #      coef = coefs
+    #      ),
+    #    function (data, response, predictor, coef, ext_data) {
+    #      if (predictor %in% c("h", "env_stoch", "resp_div")) {
+    #        p <- data %>%
+    #          ggplot(aes(
+    #              y = yresid, x = xresid,
+    #              group = cut(round(xresid, 1),
+    #                breaks = length(unique(ext_data[[predictor]]))
+    #              )
+    #              )) +
+    #          geom_boxplot(alpha = .1)
+    #      } else {
+    #        p <- data %>%
+    #          ggplot(aes(y = yresid, x = xresid)) +
+    #          geom_point(alpha = .1)
+    #      }
+    #      p +
+    #        geom_abline(
+    #          intercept = coef["(Intercept)"],
+    #          slope = coef[2],
+    #          linewidth = 1
+    #          ) +
+    #        labs(
+    #          x = var_replacement()[predictor],
+    #          y = var_replacement()[response]
+    #          ) +
+    #        coord_cartesian(expand = FALSE) +
+    #        theme_half_open()
+
+    #    }, ext_data = scaled_sim_fw_sem)
+    #)
+  #)
+)
 ```
@@
 ```{r tar-make}
-tar_make()
+#tar_make()
 tar_make_future(workers = 3)
@@
 ```{r}
+tar_load(c(formula_sem_bivariate_relations, scaled_sem_simplified, scaled_sim_fw_sem))
+sem_simplified_bivariate_relations <- tibble(formula = formula_sem_bivariate_relations) %>%
+      separate(
+        col = formula,
+        into = c("response", "predictor"),
+        sep = " ~ ", remove = FALSE) %>%
+    mutate(
+      data = map(formula_sem_bivariate_relations,
+        ~partialResid(as.formula(.x),
+            modelList = scaled_sem_simplified,
+            data = scaled_sim_fw_sem
+          )
+        ),
+      coefs = map2(response, predictor,
+        ~coefficients(scaled_sem_simplified[[.x]])[c("(Intercept)", .y)]
+        ),
+      plot = pmap(list(
+          data = data,
+          response = response,
+          predictor = predictor,
+          coef = coefs
+          ),
+        function (data, response, predictor, coef, ext_data) {
+          if (predictor %in% c("h", "env_stoch", "resp_div")) {
+            p <- data %>%
+              ggplot(aes(
+                  y = yresid, x = xresid,
+                  group = cut(round(xresid, 1),
+                    breaks = length(unique(ext_data[[predictor]]))
+                  )
+                  )) +
+              geom_boxplot(alpha = .1)
+          } else {
+            p <- data %>%
+              ggplot(aes(y = yresid, x = xresid)) +
+              geom_point(alpha = .1)
+          }
+          p +
+            geom_abline(
+              intercept = coef["(Intercept)"],
+              slope = coef[2],
+              linewidth = 1
+              ) +
+            labs(
+              x = var_replacement()[predictor],
+              y = var_replacement()[response]
+              ) +
+            coord_cartesian(expand = FALSE) +
+            theme_half_open()
+
+        }, ext_data = scaled_sim_fw_sem)
+    )
+```
+
+```{r}
+label_sem <- as.character(as.roman(seq_len(nrow(sem_simplified_bivariate_relations))))
+p_sem_simplified_bivariate_relations <-
+  plot_grid(
+    plotlist = sem_simplified_bivariate_relations$plot,
+    label_x = 1, hjust = 1.0,
+    labels = label_sem
+  )
+sem_file <- here("report", "figures", "sem_stab_simplified.pdf")
+p_sem <- ggdraw() +
+  draw_image(magick::image_read_pdf(sem_file, density = 600),
+    x = 0, y = 0,
+    width = 1, height = 1,
+    hjust = 0, halign = 0, valign = 0
+  )
+p_sem_tot <- plot_grid(
+  p_sem, p_sem_simplified_bivariate_relations,
+  nrow = 2, rel_heights = c(.6, 1),
+  labels = "auto"
+)
+ggsave_multiple(
+  paste0("p_sem_tot", c(".png", ".pdf")),
+  plot = p_sem_tot,
+  path = here::here("report", "figures"),
+  scale = 2.4,
+  dpi = 400,
+  width = 80,
+  height = 80 * 1.6,
+  units = "mm")
+```
+
+```{r}
+ggsave_multiple(
+  paste0("p_sem_bivariate_relations", c(".png", ".pdf")),
+  plot = tar_read(p_sem_bivariate_relations),
+  path = here::here("report", "figures"),
+  scale = 3,
+  dpi = 400,
+  width = 80,
+  height = 80 * .9,
+  units = "mm")
+```
+
+```{r}
+library(RColorBrewer)
+library(ggbreak)
+#cols <- c("Community stability" = "black",
+#  "Asynchrony" = "blue",
+#  "Population stability" = "darkgreen"
+#)
+custom_stab_color <- c(
+  "Community stability" = "black", #"#ffffbf"
+  "Asynchrony" = "#91bfdb",
+  "Population stability" = "#fc8d59"
+)
+alpha <- c("Community stability" = 1, "Asynchrony" = 1, "Population stability" = 1)
+
+sem_tot_predictor <- c("richness", "avg_int_strength", "w_avg_tlvl",
+  "ct_alive", "Z", "h", "resp_div", "env_stoch")
+var_replacement()[sem_tot_predictor]
+p_sem_tot_stab <- tar_read(sem_simplified_eff_tab) %>%
+  filter(effect_type == "total") %>%
+  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
+  filter(predictor %in% sem_tot_predictor) %>%
+  mutate(
+    response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
+    predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor)], .ordered = TRUE)
+) %>%
+  ggplot(aes(
+      y = predictor,
+      x = effect,
+      color = response,
+      alpha = response,
+      ymin = lower_ci,
+      ymax = upper_ci)
+    ) +
+  geom_pointrange() +
+  scale_colour_manual(values = custom_stab_color) +
+  scale_alpha_manual(values = alpha) +
+#  geom_hline(yintercept = 0, linetype = "dashed") +
+  geom_vline(xintercept = 0, linetype = "dashed") +
+  #facet_grid(cols = vars(response)) +
+  labs(
+    x = "Total standardised effects",
+    color = "Stability component",
+    alpha = "Stability component"
+    ) +
+  theme_bw() +
+  theme(
+    axis.title.y = element_blank(),
+    #legend.justification = "right",
+    legend.position = "bottom") +
+  guides(
+    color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
+    ) +
+  theme(
+    legend.title = element_blank(),
+    legend.position = c(.005, .995),
+    legend.justification = c("left", "top")
+  )
+p_sem_tot_stab_leg <- plot_grid(
+  print(p_sem_tot_stab +
+    theme(
+      legend.position = "none",
+    )
+  ),
+  get_legend(p_sem_tot_stab),
+  nrow = 2,
+  rel_heights = c(1, .05)
+)
+ggsave_multiple(
+  paste0("p_sem_tot_stab", c(".png", ".pdf")),
+  plot = print(
+    p_sem_tot_stab +
+      guides(
+        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
+      ) +
+      theme(
+        legend.title = element_blank(),
+        legend.position = c(.005, .995),
+        legend.justification = c("left", "top"),
+
+      )
+    ),
+  path = here::here("report", "figures"),
+  scale = 2.4,
+  dpi = 400,
+  width = 80,
+  height = 80 * .4,
+  units = "mm")
+```
+
+```{r}
+p_sem_fig <- plot_grid(
+  p_sem, p_sem_simplified_bivariate_relations,
+  print(
+    p_sem_tot_stab +
+      guides(
+        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
+      ) +
+      theme(
+        legend.title = element_blank(),
+        legend.position = c(.005, .995),
+        legend.justification = c("left", "top"),
+
+      )
+    ),
+  nrow = 3, rel_heights = c(.7, 1, .6),
+  labels = "auto"
+)
+ggsave_multiple(
+  paste0("p_sem_fig", c(".png", ".pdf")),
+  plot = p_sem_fig,
+  path = here::here("report", "figures"),
+  scale = 2.4,
+  dpi = 400,
+  width = 80,
+  height = 80 * 2.0,
+  units = "mm")
+```
+
+```{r}
 tar_load(fix_fw_stab)
@@
 env_corr <- 0
+label_var <- c("w_avg_tlvl", "stab_com", "pop_stab", "async", "sae_total", "cpe")
 unique(sim_for_plot$env_stoch)
-```
-
-```{r}
-sim_for_plot %>%
-  filter()
-
 ```
@@
   node_size_scale = .3,
-  tmax = 200
+  tmax = 200,
+  var_label = label_var
 )
@@
   col_palette = NULL,
-  node_size_scale = .5
+  node_size_scale = .5,
+  var_label = label_var
 )
@@
   col_palette = NULL,
-  node_size_scale = .3)
+  node_size_scale = .3,
+  var_label = label_var)
 p_high_z_high_rich <- plot_sim(
@@
   col_palette = NULL,
-  node_size_scale = .4
+  node_size_scale = .4,
+  var_label = label_var
 )
@@
   node_size_scale = .2,
-  title = "High response diversity"
+  title = "High response diversity",
+  var_label = label_var
 )
@@
   node_size_scale = .2,
-  title = "Low response diversity"
+  title = "Low response diversity",
+  var_label = label_var
 )
@@
   mutate(across(c(response, predictor), ~var_replacement()[.x]))
-```
-
-```{r}
-ggsave_multiple(
-  paste0("p_sem_bivariate_relations", c(".png", ".pdf")),
-  plot = tar_read(p_sem_bivariate_relations),
-  path = here::here("report", "figures"),
-  scale = 3,
-  dpi = 400,
-  width = 80,
-  height = 80 * .9,
-  units = "mm")
-```
-
-```{r}
-library(RColorBrewer)
-library(ggbreak)
-#cols <- c("Community stability" = "black",
-#  "Asynchrony" = "blue",
-#  "Population stability" = "darkgreen"
-#)
-custom_stab_color <- c(
-  "Community stability" = "black", #"#ffffbf"
-  "Asynchrony" = "#91bfdb",
-  "Population stability" = "#fc8d59"
-)
-alpha <- c("Community stability" = 1, "Asynchrony" = 1, "Population stability" = 1)
-
-sem_tot_predictor <- c("richness", "avg_int_strength", "w_avg_tlvl",
-  "ct_alive", "Z", "h", "resp_div", "env_stoch")
-var_replacement()[sem_tot_predictor]
-p_sem_tot_stab <- tar_read(sem_simplified_eff_tab) %>%
-  filter(effect_type == "total") %>%
-  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
-  filter(predictor %in% sem_tot_predictor) %>%
-  mutate(
-    response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
-    predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor)], .ordered = TRUE)
-) %>%
-  ggplot(aes(
-      y = predictor,
-      x = effect,
-      color = response,
-      alpha = response,
-      ymin = lower_ci,
-      ymax = upper_ci)
-    ) +
-  geom_pointrange() +
-  scale_colour_manual(values = custom_stab_color) +
-  scale_alpha_manual(values = alpha) +
-#  geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  #facet_grid(cols = vars(response)) +
-  labs(
-    x = "Total standardised effects",
-    color = "Stability component",
-    alpha = "Stability component"
-    ) +
-  theme_bw() +
-  theme(
-    axis.title.y = element_blank(),
-    #legend.justification = "right",
-    legend.position = "bottom") +
-  guides(
-    color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
-    ) +
-  theme(
-    legend.title = element_blank(),
-    legend.position = c(.005, .995),
-    legend.justification = c("left", "top")
-  )
-p_sem_tot_stab_leg <- plot_grid(
-  print(p_sem_tot_stab +
-    theme(
-      legend.position = "none",
-    )
-  ),
-  get_legend(p_sem_tot_stab),
-  nrow = 2,
-  rel_heights = c(1, .05)
-)
-ggsave_multiple(
-  paste0("p_sem_tot_stab", c(".png", ".pdf")),
-  plot = print(
-    p_sem_tot_stab +
-      guides(
-        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
-      ) +
-      theme(
-        legend.title = element_blank(),
-        legend.position = c(.005, .995),
-        legend.justification = c("left", "top"),
-
-      )
-    ),
-  path = here::here("report", "figures"),
-  scale = 2.4,
-  dpi = 400,
-  width = 80,
-  height = 80 * .4,
-  units = "mm")
 ```

### 2023-12-12 paper/manuscript.Rmd
New SEM figure and prettier method figure

@@
   "Structural Equation Model linking initial model parameters to resulting
-  temporal stability of biomass. Arrows display positive (continuous) and
+  temporal stability of biomass. (a) Arrows display positive (continuous) and
   negative (dashed) standardised effects. Initial parameters were initial
@@
   exponent, variance of stochastic mortality rates (Env. stochasticity), and
-  species response diversity. We only
-  displayed standardised coefficients whose absolute values are superior to 0.1
-  are displayed. A more complete SEM containing further partition of Statistical
-  Averaging Effect and Compensatory effects is displayed in Fig. SXX.")
+  species response diversity. Only the standardised coefficients whose absolute
+  values are superior to 0.1 are displayed. A more complete SEM containing
+  further partition of Statistical Averaging Effect and Compensatory effects is
+  displayed in Fig. SXX. (b) Partial relationships derived from the SEM, points
+  displaying the partial standardized residuals.")
 ```
@@
 ```{r sem, fig.cap=sem_cap, fig.id = "sem"}
-knitr::include_graphics(here("report", "figures", "sem_stab_simplified.pdf"))
+knitr::include_graphics(here("report", "figures", "p_sem_tot.pdf"))
 ```

### 2023-12-12 R/plotting_methods.R

@@ -74,7 +74,10 @@ plot_sim <- function(x = sim_for_plot,
   font_size = 10,
   tmax = 200,
   replace0by = 1e-6,
-  title = NULL
+  title = NULL,
+  var_label = NULL,
+  plot_label = TRUE,
+  plot_fw = TRUE
   ) {
   # get the good sim
   sim <- x %>%
@@ -109,22 +112,30 @@ plot_sim <- function(x = sim_for_plot,
   }
 
   # Add the stability and food-web metrics
-  ts_plot_metric <- ts_plot +
-    coord_cartesian(
-      expand = FALSE,
-      # Do not cut the annotations below
-      clip = "off") +
-    # This widens the right margin
-    theme(plot.margin = unit(c(1, 12, 1, 1), "lines")) +
-    annotate("text", x = nrow(mat) + 2, y = 0,
-      label = get_stab_fw_label(x = x, id = id),
-      #https://stackoverflow.com/a/65077171
-      size = font_size / .pt - 1,
-      hjust = 0,
-      lineheight = .8,
-      vjust = 0
-    )
-
+  if (plot_label) {
+    ## Get labels
+    if (!is.null(var_label)) {
+      stab_fw_label <- get_stab_fw_label(x = x, id = id, var = var_label)
+    } else {
+      stab_fw_label <- get_stab_fw_label(x = x, id = id)
+    }
+    ## Add them to the plot
+    ts_plot <- ts_plot +
+      coord_cartesian(
+        expand = FALSE,
+        # Do not cut the annotations below
+        clip = "off") +
+      # This widens the right margin
+      theme(plot.margin = unit(c(1, 12, 1, 1), "lines")) +
+      annotate("text", x = nrow(mat) + 2, y = 0,
+        label = stab_fw_label,
+        #https://stackoverflow.com/a/65077171
+        size = font_size / .pt - 1,
+        hjust = 0,
+        lineheight = .8,
+        vjust = 0
+      )
+  }
 
   # Get the Food-web
   ## Adjency matrix
@@ -149,7 +160,8 @@ plot_sim <- function(x = sim_for_plot,
   }
 
   # Combine timeseries and food-web
-  ggdraw(ts_plot_metric) +
+  if (plot_fw) {
+  ggdraw(ts_plot) +
     draw_plot(p,
       x = 1, y = 1,
       scale = .4,
@@ -157,5 +169,8 @@ plot_sim <- function(x = sim_for_plot,
[…]

### 2023-12-12 R/string_replacements.R

@@ -6,35 +6,35 @@ var_replacement <- function() {
     pop_stab = "Population stability",
     log_stab_pop = "Population stability",
     log_avg_cv_sp = "Population variability",
-    async = "Asynchrony",
-    log_async = "Asynchrony",
     sync = "Synchrony",
     log_sync = "Synchrony",
+    log_async = "Asynchrony",
+    async = "Asynchrony",
     cpe = "Compensatory effect",
     cpe_int = "Comp effect (Interaction)",
     cpe_env = "Comp effect (Environment)",
     sae_total = "Stat Avg effect",
     sae_even = "Stat Avg effect (Even)",
     evenness_sae = "Stat Avg effect (Evenness)",
-    richness = "Richness",
-    log_richness = "Richness",
-    avg_int_strength = "Avg interaction strength",
-    avg_max_int_alive = "Avg interaction strength",
     log1_avg_max_int_alive = "Avg interaction strength",
+    avg_max_int_alive = "Avg interaction strength",
+    avg_int_strength = "Avg interaction strength",
     sd_max_int_alive = "SD interaction strength",
-    w_avg_tlvl = "Avg trophic level",
     w_avg_tlvl_alive = "Avg trophic level",
     ct_alive = "Connectance",
     max_tlvl = "Max trophic level",
+    w_avg_tlvl = "Avg trophic level",
     avg_omnivory = "Avg omnivory",
-    productivityenrichment = "Enrichment",
-    resp_div = "Response diversity",
+    log_richness = "Richness",
+    richness = "Richness",
     rho = "Env Corr",
+    productivityenrichment = "Enrichment",
     env_stoch = "Env variance",
     Z = "PPMR",
     h = "Hill exponent",
     S = "Initial species richness",
-    ct = "Initial connectance"
+    ct = "Initial connectance",
+    resp_div = "Response diversity"
   )
 }
 

### 2024-01-10 _targets.Rmd
Update SEM figure

@@
 ggsave_multiple(
-  paste0("p_sem_tot", c(".png", ".pdf")),
+  paste0("p_sem_tot", c(".jpg", ".png", ".pdf")),
   plot = p_sem_tot,
@@
 ```{r}
+
 ggsave_multiple(
-  paste0("p_sem_bivariate_relations", c(".png", ".pdf")),
-  plot = tar_read(p_sem_bivariate_relations),
+  paste0("p_sem_simplified_bivariate_relations", c(".jpg", ".png", ".pdf")),
+  plot = p_sem_simplified_bivariate_relations + theme(axis.title = element_text(size = 7)),
   path = here::here("report", "figures"),
-  scale = 3,
-  dpi = 400,
-  width = 80,
-  height = 80 * .9,
+  scale = 3.5,
+  dpi = 300,
+  width = 70,
+  height = 70 * .9,
   units = "mm")
@@
 ```{r}
+bivariate_rel_file <- here("report", "figures", "p_sem_simplified_bivariate_relations.jpg")
+p_bivariate_rel <- ggdraw() +
+  draw_image(magick::image_read(bivariate_rel_file, density = 300),
+    x = 0, y = 0,
+    width = 1, height = 1,
+    hjust = 0, halign = 0, valign = 0
+  )
+
 p_sem_fig <- plot_grid(
-  p_sem, p_sem_simplified_bivariate_relations,
+  p_sem, p_bivariate_rel,
   print(
@@
 )
+
+p_sem_fig <- plot_grid(p_sem,
+  print(
+    p_sem_tot_stab +
+      guides(
+        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
+      ) +
+      theme(
+        legend.title = element_blank(),
+        legend.position = c(.005, .995),
+        legend.justification = c("left", "top"),
+
+      )
+    ),
+  p_bivariate_rel,
+  NULL,
+  nrow = 2, rel_heights = c(.7, 1),
+  labels = c("a", "b", "c", ""),
+  align = "h", axis = "tblr"
+)
 ggsave_multiple(
@@
   path = here::here("report", "figures"),
-  scale = 2.4,
+  scale = 3.4,
   dpi = 400,
   width = 80,
-  height = 80 * 2.0,
+  height = 80 * .8,
   units = "mm")

### 2024-01-10 paper/manuscript.Rmd
Review discussion, figures and legends, describe the bioenergetic model

@@
 output:
-  officedown::rdocx_document:
-    base_format: "bookdown::word_document2"
-    number_sections: false
   bookdown::pdf_document2:
@@
     spacing: double
+    number_sections: false
+  officedown::rdocx_document:
+    base_format: "bookdown::word_document2"
     number_sections: false
@@
   - \linenumbers
+  - \usepackage{hyperref}
   - \hypersetup{backref=true}
@@
 @thebault_relationship_2006; @loreau_species_2008; @danet_species_2021;
-@eschenbrenner_diversity_nodate] and on the way that species respond to
+@eschenbrenner_diversity_2023] and on the way that species respond to
 environmental perturbations [response diversity, @ives_stability_2000;
@@
 Average population stability is decreased by external forcing, such as the
-intensity and the frequency of perturbations [@ref]. Species richness can
+intensity and the frequency of perturbations [@loreau_species_2008]. Species richness can
 decrease [@tilman_biodiversity_2006; @loreau_species_2008], increase
@@
 ---
-
 #Here we deliver inference from modelling of complex biodiverse communities on
@@
 model [@yodzis_body_1992; @brose_allometric_2006; @delmas_simulations_2017].
-[DESCRIPTION of the  MODEL]
+This model is widely used to simulate the dynamics of complex ecological
+communities because of the simplicity of its parametrisation and that its
+parameters are rooted in the metabolic theory of ecology [@brown_toward_2004].
+The model describes species biomass dynamics over time with two master equations (eq. \@ref(eq:dbdt)), one for the
+primary producers (eq. \@ref(eq:prod)) and one for the consumers (eq. \@ref(eq:prod)):
+
+\begin{subequations}
+    \label{eq:dbdt}
+
+    \begin{equation}
+        \label{eq:cons}
+        \frac{dB_i}{dt} =
+        \sum_{j \in \{\mathrm{res}\}_i} x_i y_i B_k F_{ij}
+        - \sum_{j \in \{\mathrm{cons}\}_i} \frac{x_j y_j B_j F_{ji}}{e_{ij}}
+        - x_i B_i - d_i B_i
+    \end{equation}
+
+    \begin{equation}
+    	\label{eq:prod}
+    	\frac{dB_i}{dt} =
+	r_i B_i G_i
+	- \sum_{j \in \{\mathrm{cons}\}_i} \frac{x_j y_j B_j F_{ji}}{e_{ij}}
+        - d_i B_i
+    \end{equation}
+\end{subequations}
+
+The consumers gain biomass by consumming resources (i.e. their preys) at a rate
+that depends on their mass specific metabolic rate ($x_i$),  maximum cumsumption
+rate ($y_i$) and on the functional response ($F_ij$) describing how the rate of
+consumption of a consumer $i$ on a resource $j$ vary with the biomass of this resource.
+Consumers then loses biomass by being consumed, $e_ij$ being the assimilisation
+efficiency of the consumer $j$ on the resource $i$. Consumers also lose biomass
+over time through metabolic losses ($-x_iB_i$) and by natural mortality due to
+environment ($-d_iB_i$). The primary producers gain biomass over time with a
+growth rate ($r_i$, eq. \@ref(eq:prod)) and a functional response ($G_i$)
+describing how the growth of the producers vary with their biomass. They lose
+biomass by being consumed by consumers and by natural mortality.
+
+\begin{subequations}
+    \label{eq:func}
+    \begin{equation}
+        \label{eq:growth}
+        G_i = (1 - \dfrac{\sum_{j \in \{\mathrm{prod}\}} \alpha_{ij} B_j}{K_i})
+    \end{equation}
+
+    \begin{equation}
+    	\label{eq:holling}
+        F_{ij} = \frac{\omega_{ij} B_j^h}
+        {B_0^h + c_i B_i
+        	+ \sum_{k \in \{\mathrm{res}\}_i} \omega_{ik} B_k^h}
+    \end{equation}
+\end{subequations}
+
+The growth function of the primary producers (eq. \@ref(eq:growth)) has the shape of a logistic growth
+where the growth rate is maximal and null when
+$\sum_{j \in \{\mathrm{prod}\}} \alpha_{ij} B_j$ are respectively close to 0 and 1. $\alpha_{ij}$ is the
+per capita effect of the producer $j$ on the producer $i$, $K_i$ being the
+carrying capacity for the producer $j$. The functional response of a consumer
+feeding on a resource (eq. \@ref(eq:holling)) depends on the relative preference
+of the consumer on the resource ($\omega_ij$) is limited by an half-saturation
+rate ($B_0$), intraspecific interference coefficient ($c_i$), and on the
+availability of its other resources
+($\sum_{k \in \{\mathrm{res}\}_i} \omega_{ik} B_k^h$). Finally, the $h$ exponent
+controls the shape of the functional response from a saturating function
+(Holling type II) to a sigmoid (Holling type III).
 
@@
 As SAE is further dependant on the evenness of species variance, we
-partitioned $SAE$ into $SAE_{even}$ and evenness $EVN$, such as $SAE_{even} =
-\sqrt{S}$ and $EVN = SAE / SAE_{even}$.
+partitioned $SAE$ into $SAE_{even}$ and evenness $EVN$, such as  $EVN = SAE / SAE_{even}$.
+$SAE_{even}$ corresponds to the $SAE$ when species quantities are perfectly
+even such as from eq. \@ref(eq:sae2), we can obtain $SAE_{even}$ from which $EVN$ can be computed:
+
+\begin{equation}
+\begin{aligned}
+SAE &= \dfrac{\sum_i \sigma_i}{\sqrt{\sum_i \sigma^2_i}} = \sqrt{\dfrac{1}{\sum_i (\sigma_i\sigma^2_i})^2} = \sqrt{\dfrac{1}{\sum_i (p_i)^2}}\\
+SAE_{even} &= \sqrt{\dfrac{1}{\sum_i (1/S)^2}}\\
+SAE_{even} &= \sqrt{S}\\
+(\#eq:sae-even)
+\end{aligned}
+\end{equation}
 
@@
   further partition of Statistical Averaging Effect and Compensatory effects is
-  displayed in Fig. SXX. (b) Partial relationships derived from the SEM, points
-  displaying the partial standardized residuals.")
+  displayed in Fig. SXX. (b) Total effect of food-web structure on community stability,
+  asynchrony, and population stability. The total effects were derived from the
+  structural equation model. (c) Partial relationships derived from the SEM, points
+  displaying the partial standardized residuals while lines displays the linear
+  relationship derived from the SEM.")
 ```
@@
 ```{r sem, fig.cap=sem_cap, fig.id = "sem"}
-knitr::include_graphics(here("report", "figures", "p_sem_tot.pdf"))
+knitr::include_graphics(here("report", "figures", "p_sem_fig.pdf"))
 ```
@@
 hill exponent = 3) increase population stability (resp. $r_\delta$= `r rpt` and
-`r rph`, $r_\delta$ being the standardized coefficient, Fig. \@ref(fig:sem)).
+`r rph`, $r_\delta$ being the standardized coefficient, Fig. \@ref(fig:sem)a).
 In turn, the variance of environmental stochasticity had a strong negative effect
@@
 the evenness of their variance. As expected the mathematical relationship (eq.
-XX), species richness was a main positive driver of statistical averaging effect
-($r_\delta$= `r rsr`, Fig. \@ref(fig:sem)), thereby increasing asynchrony.
-Average trophic level and average interaction strength had strong negative
-effects on statistical averaging effects (resp. $r_\delta$= `r rst` and
-`r rsi`), thereby downplaying the portfolio effect raised from species
-richness. In turn, we found that average interaction strength had a small
-positive effect on compensatory dynamics ($r_\delta$= `r rci`, Fig.
-\@ref(fig:sem)). Species response diversity had a strong positive effect on compensatory dynamics
+\@ref(eq:sae-even)), species richness was a main positive driver of statistical
+averaging effect ($r_\delta$= `r rsr`, Fig. \@ref(fig:sem)a), thereby increasing
+asynchrony. Average trophic level and average interaction strength had strong
+negative effects on statistical averaging effects (resp. $r_\delta$= `r rst` and
+`r rsi`), thereby downplaying the portfolio effect raised from species richness.
+In turn, we found that average interaction strength had a small positive effect
+on compensatory dynamics ($r_\delta$= `r rci`, Fig. \@ref(fig:sem)). Species
+response diversity had a strong positive effect on compensatory dynamics
 ($r_\delta$= `r rcd`).
@@
 compensatory dynamics (resp. $r_\delta$= `r rac` and `r ras`, Fig.
-\@ref(fig:sem)).
+\@ref(fig:sem)a).
 
-```{r}
+```{r, eval = FALSE}
 semtot_cap <- "Total effect of food-web structure on community stability,
@@
 
-```{r semtot, fig.cap = semtot_cap, fig.id = "semtot"}
+```{r semtot, eval = FALSE, fig.cap = semtot_cap, fig.id = "semtot"}
 knitr::include_graphics(here::here("report", "figures", "p_sem_tot_stab.png"))
@@
 species had by far the most important effect on community stability (resp.
-$r_\delta$= `r rtsenv` and `r rtsdiv`, Fig. \@ref(fig:semtot)). Species richness
+$r_\delta$= `r rtsenv` and `r rtsdiv`, Fig. \@ref(fig:sem)b). Species richness
 had a low overall positive total effect on community stability (`r rtsr`)
@@
 predator prey bodysize ratio had positive effects on community stability in
-total (resp. `r rtst`, `r rtsh`, `r rtsz`, Fig. \@ref(fig:semtot)), driven by
+total (resp. `r rtst`, `r rtsh`, `r rtsz`, Fig. \@ref(fig:sem)b), driven by
 their positive effects on population stability that were weakly counterbalanced
@@
 interaction strength had low total negative effects on community stability (resp.
-`r rtsc` and `r rtsi`, Fig. \@ref(fig:semtot)). While connectance had negative
+`r rtsc` and `r rtsi`, Fig. \@ref(fig:sem)b). While connectance had negative
 effects both on population stability and asynchrony, average interaction
@@
 )
-pred_cap <- paste0("Prediction of the statistical model linking the temporal stability
-  of community biomass and species richness. Default parameter values: ", pv_cap, ".") %>%
+pred_cap <- paste0("Relationship between community stability and species
+  richness according to food-web structure and response diversity. a,
+  Predictions of the statistical model linking the temporal stability of
+  community biomass and species richness. The values chosen for high/low
+  response diversity and food-web structure are indicated by the black point in
+  (b). Lines display the mean predictions of the model, ribbons display the
+  confidence intervals at 95\\% (to recheck). b, Diagrams displaying the slope
+  coefficients of the effect of species richness on community stability. Default
+  parameter values for the predictions: ", pv_cap, ".") %>%
   str_replace_all("\\s+", " ")
@@
 
-Using a more complex linear model (i.e. including interactions), we investigated
-more in detail the relationship between community stability and species richness
-and how this relation is affected by environmental stochasticity and species
-response diversity. We found that environmental stochasticity decrease overall
-community stability but has only little effect on the shape of the community
-stability-species richness relationship (put some numbers, Fig. \@ref(fig:pred)a
-and b). In contrasts, species response diversity both increases overall
-community stability and leads to positive community stability-species richness
-relationships. Surprisingly, we found that despite average interaction strength
-has a small overall effect on community stability, high average interaction
-strength change the shape of the community stability-species richness
-relationship from positive to negative when response diversity is low (put some
-numbers, Fig. \@ref(fig:pred)b).
+Using a more complex linear model (i.e. including interactions), We found strong
+interactions between food-web structure and response diversity on the
+relationship between community stability and species richness. We found that
+high response diversity almost always leads to positive relationships between
+community stability and species richness, no matter the values of average
+interaction strength, average trophic level or connectance (Fig.
+\@ref(fig:pred)). Furthermore, we found that higher response diversity increased
+community stability in average (Fig. \@ref(fig:pred)a). Surprisingly, despite
+the relatively small effects of food-web structure on overall community
+stability (Fig. \@ref(fig:sem)c \@ref(fig:pred)a), we found that response
+diversity dramatically change the shape of the community stability-species
+richness relationship from positive to negative when response diversity is low
+(Fig. \@ref(fig:pred)b).
+
+---
+#We found that
+#environmental stochasticity decrease overall community stability but has only
+#little effect on the shape of the community stability-species richness
+#relationship (Fig. \@ref(fig:pred)a)
+---
 
@@
 competitive assemblages. First, the range of bodymasses is much higher in
-food-webs, which typically include species that differ by several order of
+food-webs, which typically include species that differ in bodymass by several order of
 magnitude [@brose_predator_2019], which in turn creates highly uneven biomass
@@
 interdependence among species, which in turn limits the raise of independent
-fluctuations (i.e. portfolio effects) and compensatory dynamics. The question of
-which mechanisms and community structure features drive differences in the
+fluctuations (i.e. portfolio effects, but rise compensatory dynamics). The question of
+which mechanisms and community features drive differences in the
 contribution of asynchrony and population stability in food-webs and competitive
 assemblages is still a open question that might be crucial to accurately
-address diagnostics and conservation measures. On top of food-web structure,
+address diagnostics and conservation issues. On top of food-web structure,
 we found that environmental stochasticity and environmental correlation among
-species was the main drivers of community stability, suggesting that stressors
-are the first source of stability. This result is in accordance with previous
+species were the main drivers of community stability, suggesting that stressors
+are the main drivers of temporal stability. This result is in accordance with previous
 studies showing strong effects on environmental stochasticity
@@
 stability, confirming previous theoreical [@brose_allometric_2006;
-@shanafelt_stability_2018; @eschenbrenner_diversity_nodate] and
+@shanafelt_stability_2018; @eschenbrenner_diversity_2023] and
 [@danet_species_2021] empirical results. Higher average trophic level can
@@
 perturbation and because they control the amplitude of the fluctuations of their
-prey [@shanafelt_stability_2018, we can test that?]. In turn, we found that that
+preys [@shanafelt_stability_2018, we can test that?]. In turn, we found that
 average trophic level decreases strongly asynchrony through a negative effect on
@@
 level have a lower overall mortality rates, similarly to previous studies
-[@vasseur_environmental_2007], stabilising populations and simultaneously
-synchronising them. The fact that Predator Size Mass Ratio displays the same
+[@vasseur_environmental_2007], thereby increasing average population stability and simultaneously
+synchronising populations. The fact that Predator Size Mass Ratio displays the same
 effect, thereby building food-webs with bigger species having lower mortality
@@
 However, species richness had a strong positive on asynchrony, by raising
-statistical averaging effects. [add blabla about richness asynchrony]. In turn,
-we found that species richness magnified the effect of the loss of response
-diversity on the compensatory dynamics due to environment. Our interpretation is
-that higher species richness synchronizes more species fluctuations due to
-environmental mortality when species are not independent because each added
-species adds (S - 1, S being richness) positive covariance terms in the
-stochastic mortality rates, thereby increasing the overall synchrony in
-mortality rates when cross correlation are not null. This assumption that each
-species are equally correlated to each other seems unlikely to be true but as
-far we know, there is compelling evidence yet for alternative correlation
-structures. Connectance, quantifying generalism in food-web, had negative
-effects on both asynchrony and population stability. We further found that
-higher connectance leaded to less even biomass variability, thereby limiting the
-raise of the portfolio effects, and leaded to lower compensatory dynamics due
-to species interactions. This results in accordance with empirical finding that
-a generalist predator can indeed synchronises the dynamics of a large number of
-preys [@raimondo_interspecific_2004]. [No idea about connectance decreasing
-population stability]. However, the overall effect of connectance on overall
-stability was quite low, similarly to previous empirical findings
-[@danet_species_2021], but in apparent disagreement with the predominant role of
-connectance on stability in theoretical studies [complexity-stability paradox,
-@may_will_1972].
+statistical averaging effects. This result is common in empirical systems
+[@tilman_biodiversity_2006; @olivier_urbanization_2020], but strongly depends on
+the presence of response diversity [@loreau_species_2008;
+@thibaut_understanding_2013; @zhao_biodiversity_2022]. Connectance, quantifying
+the generalism in food-webs, had negative effects on both asynchrony and population
+stability. We further found that higher connectance leaded to less even biomass
+variability, thereby limiting the raise of the portfolio effects, and leaded to
+lower compensatory dynamics due to species interactions. This result is in
+accordance with empirical findings that a generalist predator can indeed
+synchronises the dynamics of a large number of preys
+[@raimondo_interspecific_2004]. [No idea about connectance decreasing population
+stability]. However, the overall effect of connectance on overall stability was
+quite low, similarly to previous empirical findings [@danet_species_2021], but
+in apparent disagreement with the predominant role of connectance on stability
+in theoretical studies [complexity-stability paradox, @may_will_1972].
 
-Food-web dynamical features, functional response of type III and average
+---
+#In turn,
+#we found that species richness magnified the effect of the loss of response
+#diversity on the compensatory dynamics due to environment. Our interpretation is
+#that higher species richness synchronizes more species fluctuations due to
+#environmental mortality when species are not independent because each added
+#species adds (S - 1, S being richness) positive covariance terms in the
+#stochastic mortality rates, thereby increasing the overall synchrony in
+#mortality rates when cross correlation are not null. This assumption that each
+#species are equally correlated to each other seems unlikely to be true but as
+#far we know, there is compelling evidence yet for alternative correlation
+#structures.
+---
+
+Food-web dynamical features, the type of functional response (from II to III) and average
 interaction strength, also had an effect on community stability. Our results
-confirms the stabilising effect of the functional response of type III on
+confirm the stabilising effect of the functional response of type III on
 populations [@uszko_effects_2017; @brose_allometric_2006]. Compared to type II,
@@
 type III decreased asynchrony by decreasing compensatory dynamics due to species
-interaction. This effect might be due to prey switching of consumers when one of
+interactions. This effect might be due to prey switching of consumers when one of
 them reach low abundance [@mccann_diversitystability_2000]. Average interaction
@@
 Average interaction strength was found to decrease asynchrony by decreasing the
-evenness of biomass variability, thereby decreasing the portfolio effect,
+evenness of biomass variability, thereby decreasing portfolio effects,
 despite having a small positive effect on compensatory dynamics. In turn, we
@@
 community stability - richness but rather control the overall community
-stability (i.e. the intercept of the relation). At the opposite, In turn, a
-decrease in response diversity dampens the stability-richness relationship. The
-reason is that the strength of environmental stochasticity only affect
-population stability and not asynchrony, the latter being the driver of
+stability (i.e. the intercept of the relation). At the opposite, variation in
+response diversity had a strong impact on the relationship between stability and
+richness. The reason is that the strength of environmental stochasticity mainly
+affect population stability and less asynchrony, the latter being the driver of
 species-richness relationships [@ives_stability_2000; @thebault_trophic_2005;
@@
 (i.e. measured as the dominant eigen value of the jacobian matrix) should
-decrease as the community is species diversity, has higher connectance, and
+decrease as the community is species diverse, has higher connectance, and
 higher interaction strength [@may_will_1972]. However, we found that the
@@
 asynchrony in species fluctuations which overrides the negative effects of
-complexity on stability-richness relationship. Response diversity might then one
+complexity on stability-richness relationships. Response diversity might then be one
 mechanism that explains why so much positive relationship between stability and
@@
 stability and its partition into population stability and asynchrony in complex
-food-web, added to two pressing stressors in the context of global change, the
+food-webs, added to two pressing stressors in the context of global change, the
 strength of environmental variability and the level of response diversity of
@@
 having high interaction strength, high connectance and high average trophic
-level. Then, our study reinforces that the restoration of ecosystems along with
-a restoration of landscape complexity that provides refuges from extreme
-environment are key to maintain temporal stability of ecological communities
-[@ryser_landscape_2021].
+level. Then, the results of our study reinforces that the restoration of
+ecosystems along with a restoration of landscape complexity that provides
+refuges from extreme environmental changes will be key to maintain temporal stability of
+ecological communities in the coming decades [@ryser_landscape_2021].
 

### 2024-01-12 _targets.Rmd
Complete methods with food-web metrics

@@
   }),
+  tar_target(sim_param, readRDS(here::here("data", "sim_param_d2"))),
   tar_target(sim_fw_df, as.data.frame(sim_fw)),
@@
 
+# Table
+
+```{targets}
+list(
+  tar_target(sim_param_tab,
+    sim_param %>%
+      mutate(resp_div = 1 - rho) %>%
+      select(-A) %>%
+      pivot_longer(everything(), names_to = "Parameter", values_to = "values") %>%
+      group_by(Parameter) %>%
+      summarise(
+        u = list(unique(values)),
+        n = length(unique(round(values, 2))),
+        min = min(values),
+        max = max(values)
+        )
+    ),
+  tar_target(tab_sim_param,
+    sim_param_tab %>%
+      mutate(Values = pmap_chr(list(u = u, min = min, max = max, n = n),
+          function(u, min, max, n) {
+            if (length(u) < 10) {
+              out <- paste0("[", paste(round(u, 2), collapse = ", "), "]")
+            } else {
+              out <- paste0("(", round(min, 2), ", ", round(max, 2), ")", ", N = ", n)
+            }
+            out
+          }
+          )) %>%
+      filter(!Parameter %in% c("sim_id", "fw_id", "rho")) %>%
+      select(Parameter, Values) %>%
+      mutate(Parameter = recode_factor(Parameter, !!!var_replacement()))
+  )
+)
+```
+
 # Pipeline
@@
 
-```{r, message = FALSE}
+```{r output-load, message = FALSE}
 library(targets)
@@
 library(ggcorrplot)
+library(kableExtra)
 lapply(list.files(here::here("R"), full.names = TRUE), source)
@@
     ))
+```
+
+```{r}
+tar_load(sim_param_tab)
 ```
@@
 ```{r}
-
 ggsave_multiple(
@@
 ```
-
 ```{r}
 tar_load(pred_stab_comp_resp_div)
+```
+
+```{r}
 p_pred_sr_resp_div <- pred_stab_comp_resp_div %>%
@@
   height = 120 * .45,
+  units = "mm")
+```
+
+```{r}
+p_pred_sr_resp_div_supp <- pred_stab_comp_resp_div %>%
+  mutate(
+    variable = var_replacement()[variable],
+    response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
+    ) %>%
+  ggplot(aes(x = resp_div, y = variable_values, fill = slope)) +
+  geom_raster() +
+  facet_grid(cols = vars(response), rows = vars(variable), scales = "free") +
+  coord_cartesian(expand = FALSE) +
+  scale_x_continuous(
+    breaks = c(0, .5, 1),
+    labels = c(0, 0.5, 1)
+    ) +
+  scale_fill_gradient2(
+    low = resp_div_cat_colors()["Low"],
+    mid = "white",
+    high = resp_div_cat_colors()["High"],
+    midpoint = 0,
+    space = "Lab",
+    na.value = "grey50",
+    guide = "colourbar",
+    aesthetics = "fill") +
+  labs(
+    x = var_replacement()["resp_div"],
+    y = "Food-web structure",
+    fill = "Slope stability - Richness"
+    ) +
+  theme(
+    legend.position = "bottom",
+    legend.key.width = unit(2.0, "cm"),
+    plot.margin = margin(l = 10, r = 10, unit = "pt")
+  )
+ggsave_multiple(
+  paste0("p_pred_sr_resp_div_supp", c(".png", ".pdf")),
+  plot = p_pred_sr_resp_div_supp,
+  path = here::here("report", "figures"),
+  scale = 2.4,
+  dpi = 400,
+  width = 80,
+  height = 80 * 1,
   units = "mm")
@@
 
+```{r, eval=FALSE}
+tar_load(sim_param)
+sim_param %<>%
+  select(-A)
+sim_param %>%
+  group_by(h, rho, env_stoch, Z) %>%
+  summarise(
+    nb_fw = length(unique(fw_id)),
+    n = length(fw_id)
+  )
+
+sim_param %>%
+  group_by(fw_id) %>%
+  summarise(n = n())
+
+```
+
 The `targets` dependency graph helps your readers understand the steps of your pipeline at a high level.

### 2024-01-12 paper/manuscript.Rmd
Complete methods with food-web metrics

@@
 
-\pagebreak
-
-```{r}
-met_cap <- "Examples of stochastic food-web simulations. a, Simulations with low
-and high response diversity. b, simulations with low and high predator-prey mass
-ratio (upper and bottom panels), low and high species richness (left and right
-  panels). The food-web are displayed on the side with the node size
-being proportional to the average species biomass across the simulation. We
-also display the food-web structure and the stability metrics. Across all
-simulations, $h = 2$, $\\sigma_e = .3$. Low and high response diversity were
-respectively $\\rho = 1$ and $\\rho = 0$. Low and high PPMR were respectively 1 and 100." %>%
-  str_replace_all("\\s+", " ")
-```
-
-```{r met, fig.cap = met_cap}
-knitr::include_graphics(here("report", "figures", "p_methods.pdf"))
-```
-
 # Methods
@@
 
-$$
+\begin{equation}
+\begin{aligned}
 \epsilon_{i, t} =
@@
   \end{bmatrix}
-$$
+S_{com} = S_{pop} \times \phi
+(\#eq:rho)
+\end{aligned}
+\end{equation}
 
@@
 
+```{r}
+tar_load(sim_param_tab)
+spt <- sim_param_tab
+get_sim_par_val <- function(x = "S", data = sim_param_tab) {
+  x <- data[data$Parameter == x,][c("min", "max", "n")]
+  setNames(unlist(x), c("min", "max", "n"))
+
+}
+pS <- get_sim_par_val(x = "S")
+pct <- round(get_sim_par_val(x = "ct"), 2)
+pZ <- get_sim_par_val(x = "Z")
+ph <- get_sim_par_val(x = "h")
+pe <- get_sim_par_val(x = "env_stoch")
+prd <- get_sim_par_val(x = "resp_div")
+pr <- get_sim_par_val(x = "rho")
+```
+\pagebreak
+
+```{r}
+met_cap <- "Examples of stochastic food-web simulations. a, Simulations with low
+and high response diversity. b, simulations with low and high predator-prey mass
+ratio (upper and bottom panels), low and high species richness (left and right
+  panels). The food-web are displayed on the side with the node size
+being proportional to the average species biomass across the simulation. We
+also display the food-web structure and the stability metrics. Across all
+simulations, $h = 2$, $\\sigma_e = .3$. Low and high response diversity were
+respectively $\\rho = 1$ and $\\rho = 0$. Low and high PPMR were respectively 1 and 100." %>%
+  str_replace_all("\\s+", " ")
+```
+
+```{r met, fig.cap = met_cap}
+knitr::include_graphics(here("report", "figures", "p_methods.pdf"))
+```
+
+(ref:eq-rho) (eq. \@ref(eq:rho))
+
+```{r}
+tar_read(tab_sim_param) %>%
+  kable(
+    booktabs = TRUE,
+    caption = "Parameter values used in the simulation experiment. Numbers
+    between squared brackets display all the values. Two numbers between
+    brackets are the minumum and maximal values, N being the number of unique
+    values. PPMR: Predator Prey Mass Ratio. We defined response diversity as \\protect$1-\\rho$
+    (ref:eq-rho).",
+    label = "param") %>%
+  kable_styling(latex_options = c("striped", "hold_position"))
+```
+
 We generated food-web structure using the niche model [@williams_simple_2000]
-with an initial species richness from $10$ to $60$, and connectance from $0.02$
-to $.32$. We generated food-webs without cannibalistic links and discarded
-food-webs that contained disconnected species.
-
-To vary interaction strength and mortality rates in the community,
-we varied the Predator-Prey Bodysize Ratio (PPBR) from 1 to 100. We further
-varied the functional response of consumer from type II to type III (resp. $h=2$
-and $h=3$, eq XX) as it was shown to have a tremendous role on stability
-[@brose_allometric_2006]. We set $K = 10$ to ensure that consumers were not
-limited by the biomass input from primary producers.
+with an initial species richness from $`r pS["min"]`$ to $`r pS["max"]`$, and
+connectance from $`r pct["min"]`$ to $`r pct["max"]`$ (Table
+\@ref(tab:param)). We generated food-webs without cannibalistic links and
+discarded food-webs that contained disconnected species.
 
 We varied the strength of environmental stochasticity by varying $\sigma_e$ from
-0.1 to 0.6, the range of mortality rates observed in
+$`r pe["min"]`$ to $`r pe["max"]`$, the range of mortality rates observed in
 protists [@vasseur_environmental_2007]. We decreased response diversity by
-increasing $\rho$ from 0 to 1.
-
-We numerically solved the simulations during 5000 timesteps
-and collected the last 500 timesteps. We set $d_t = .1$, and $d_t = .05$ when
-instability was detected during the simulations. We set extinction threshold to
-$10^{-6}$ and if an extinction happened in the last 500 timesteps, we continued
-to run the simulation for another 1000 timesteps until there was no extinction
-events. When we found disconnected species at the end of the simulation (i.e. a
-primary producer without consumer or a consumer without prey), we removed them
-and re-run simulation for another 1000 timesteps.
+increasing $\rho$ from $`r pr["min"]`$ to $`r pr["max"]`$ (i.e. response
+diversity being $1 - \rho$) (Fig. \@ref(fig:met)a).
+
+To vary interaction strength and mortality rates (i.e. allometrically
+scaled mortality rate $d$) in the community, we varied the Predator-Prey
+Bodysize Ratio (PPBR) from $`r pZ["min"]`$ to $`r pZ["max"]`$ (Fig. \@ref(fig:met)b). We further varied
+the functional response of consumer from type II to type III (resp.
+$`r ph["min"]`$ to $`r ph["max"]`$, eq. \@ref(eq:holling)) as it was shown to
+have a tremendous role on stability [@brose_allometric_2006]. We set a global
+carrying capacity of $K' = 10$ to ensure that consumers were not limited by the
+biomass input from primary producers. We standardised the carrying capacity by
+the number of primary producers and by the interspecific competition among
+producers to ensure that the effects of species richness on temporal stability
+are not driven by the increase in the number of primary producers, thereby
+trivially increase biomass input for consumers. We then standardised $K'$ such as
+$K_i = \frac{1 + \alpha_{ij} (S - 1)}{S}K'$ [@ives_stability_2000].
+
+We numerically solved the stochastic differential equation systems during 5000
+timesteps and collected the last 500 timesteps. We set $d_t = .1$, and $d_t =
+.05$ when instability was detected during the simulations due to stiff changes
+in biomass. We set extinction threshold to $10^{-6}$ and if an extinction
+happened in the last 500 timesteps, we continued to run the simulation for
+another 1000 timesteps until there was no extinction events. When we found
+disconnected species at the end of the simulation (i.e. a primary producer
+without consumer or a consumer without prey), we removed them and re-run the
+simulation for another 1000 timesteps.
 
@@
 average trophic level weighted by biomass, average omnivory and average per
-capita interaction strength.
+capita interaction strength. Connectance was computed as $C = L / S(S-1)$, $L$
+being the number of trophic links and $S$ being the number of species in the
+community. Species trophic level was computed recursevily from the bottom of the
+food-web, such as the trophic level of a consumer was equal to the average
+trophic level of its resources added to 1, the trophic level of primary
+producers being set to 1 [@christensen_ecopath_1992]. Average trophic level was then equal to:
+$1/\hat{B}_i\sum_{i}\mathrm{TL}_i$, $\mathrm{TL}_i$ being the trophic level and
+$\hat{B}_i$ the average biomass of the species $i$. The degree of omnivory of a
+consumer was computed  such as the sum of square of its
+resource trophic levels weighted by the relative preference of the consumer for
+this resource: $\sum_i (\mathrm{TL}_i - \hat{\mathrm{TL}})^2 \omega_i/ \sum \omega_i$ [@christensen_ecopath_1992].
+Interaction strength was computed was quantified as the biomass fluxes going
+from a resource to a consumer, such as: $I = x_i y_i B_k F_{ij}$ (eq.
+\@ref(eq:cons)), and averaged over time. Per capita interaction strength was
+obtained by dividing average interaction strength by the average biomass of the
+consumer. Finally, the average interaction strength of a community was computed
+as the average per capita interaction strength at the exclusion of null
+interaction strengths (i.e. non present trophic interactions).
 

### 2024-01-12 draft.jl

@@ -18,6 +18,12 @@ include("src/sim.jl")
 include("src/plot.jl")
 include("src/get_modules.jl")
 
+m = (t = 0, b = 0)
+m[:t]
+dictionary = Dict(1 => 77, 2 => 66, 3 => 1)
+keys(dictionary)
+dictionary[:1]
+
 param = DataFrame(Arrow.Table("scripts/param_comb_ct_S_h_d3.arrow"))
 
 filter([:S, :sigma, :h] => (rich, s, h) -> rich == 40 && s == .6 && h == 2, param)

### 2024-01-15 _targets.Rmd
Cleaning for sending to coauthors

@@
     map_dfr(sem_simplified_model_list, rsquared) %>%
-      mutate(Response = var_replacement()[Response]) %>%
+      mutate(
+      Response = var_replacement()[Response],
+      R.squared = round(R.squared, 2)
+      ) %>%
       select(Response, R.squared)
@@
         response = var_replacement()[response],
-        Term = var_replacement()[Term]
-        ) %>%
-      kable(
-        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
-      kable_styling()
+        Term = var_replacement()[Term],
+        VIF = round(VIF, 2),
+        SE_factor = round(SE_factor, 2)
+        ) %>%
+        rename(Response = response)
     ),
@@
   sim_fw %>%
-    select(c(richness, ct_alive, Z, bm_total,
-        avg_int_strength, avg_omnivory, max_tlvl,
+    select(c(
+        bm_total, stab_com, pop_stab, async, sae_total, sae_even,
+        evenness_sae, cpe, cpe_int, cpe_env,
+        richness, ct_alive, avg_int_strength, avg_omnivory, max_tlvl,
         w_avg_tlvl,
-        rho, env_stoch, h,
-        stab_com, pop_stab, async, sae_total, sae_even,
-        evenness_sae, cpe, cpe_int, cpe_env)) %>%
+        Z, resp_div, env_stoch, h
+        )) %>%
   na.omit() %>%
@@
 cor(ti$rotated$scores[, "RC1"], sim_fw_df[,"richness"])
+```
+
+## Correlation matrix
+
+```{r}
+ggsave_multiple(
+  paste0("p_cor", c(".png", ".pdf")),
+  plot = tar_read(p_cor),
+  path = here::here("report", "figures"),
+  scale = 3.4,
+  dpi = 400,
+  width = 80,
+  height = 80 * .9,
+  units = "mm")
 ```

### 2024-01-15 paper/manuscript.Rmd
Cleaning for sending to coauthors

@@
 output:
+  officedown::rdocx_document:
+    number_sections: false
   bookdown::pdf_document2:
@@
     number_sections: false
-  officedown::rdocx_document:
-    base_format: "bookdown::word_document2"
-    number_sections: false
 always_allow_html: true
@@
 link-citations: true
+csl: ecology-letters.csl
 toc: false
@@
 [@tilman_biodiversity_2006; @roscher_identifying_2011;
-@thibaut_understanding_2013; @zhao_biodiversity_2022], requires to scale down
-the focus to populations. Community stability can be mathematically partitionned
+@thibaut_understanding_2013; @zhao_biodiversity_2022], requires scaling down
+the focus to populations. Community stability can be mathematically partitioned
 into average population stability and asynchrony [@loreau_species_2008;
@@
 level. Population stability and asynchrony depend both on the number of species
-and their dominance [@loreau_species_2008; @thibaut_understanding_2013; @zhao_biodiversity_2022],
-the interactions among them [@thebault_trophic_2005;
+and their dominance [@loreau_species_2008; @thibaut_understanding_2013;
+@zhao_biodiversity_2022], the interactions among them [@thebault_trophic_2005;
 @thebault_relationship_2006; @loreau_species_2008; @danet_species_2021;
@@
 the community such as dominant species contribute more the average of the
-community than surbordinate species. At the core of ecological theory,
+community than subordinate species. At the core of ecological theory,
 population stability depends on internal forcing, here species interactions. The
-topogical structure and the distribution of interaction strength have tremendous
+topological structure and the distribution of interaction strength have tremendous
 effects on population stability, such as strong interaction strength are
@@
 
-Asynchrony in turn can be partitionned into portefolio effects and compensatory
-dynamics and is mostly determine by internal factors. Portefolio effects stems
+Asynchrony in turn can be partitioned into portfolio effects and compensatory
+dynamics and is mostly determined by internal factors. Portfolio effects stems
 from the statistical averaging of independent population fluctuations
@@
 asynchrony. Compensatory dynamics in turn captures population fluctuations that
-are more synchronous or asynchronous than expected for independant fluctuations,
+are more synchronous or asynchronous than expected for independent fluctuations,
 and can stem from species interactions and species responses to perturbations
@@
 the distribution and strength of species interactions can also modulate
-asynchrony through compensatory dynamics such as a strong asymetry of consumer
+asynchrony through compensatory dynamics such as a strong asymmetry of consumer
 preference can generate asynchrony in resource fluctuations [@mccann_weak_1998;
@@
 have synchronising effects in strong species growth rates regime
-[@loreau_species_2008]. Finally, portefolio and compensatory effects can also be
+[@loreau_species_2008]. Finally, portfolio and compensatory effects can also be
 affected by the population evenness such as fluctuations of a dominant
-species will be hardly compensated by a subordinate species. Improving our
+species will hardly be compensated by a subordinate species. Improving our
 understanding of community stability facing perturbations therefore requires to
@@
 across variation in community structure and response diversity. We
-then introduce assumptions we use to implement environmental stochasticity,
+then introduce assumptions we used to implement environmental stochasticity,
 response diversity, variation in community structure and variation in the
@@
 interaction strength on population stability, compensatory dynamics,
-and statistical averaging effects (i.e. portefolio effects)? (2) What are the
-total effects of food-web structure, reponse diversity, environmental
-stochasticity on community stability. Finally merging the two parallel bodies of
+and statistical averaging effects (i.e. portfolio effects)? (2) What are the
+total effects of food-web structure, response diversity, environmental
+stochasticity on community stability. Finally, merging the two parallel bodies of
 work, we asked (3) How do response diversity and food-web structure interact to
@@
 
-The consumers gain biomass by consumming resources (i.e. their preys) at a rate
-that depends on their mass specific metabolic rate ($x_i$),  maximum cumsumption
+The consumers gain biomass by consuming resources (i.e. their preys) at a rate
+that depends on their mass specific metabolic rate ($x_i$),  maximum consumption
 rate ($y_i$) and on the functional response ($F_ij$) describing how the rate of
 consumption of a consumer $i$ on a resource $j$ vary with the biomass of this resource.
-Consumers then loses biomass by being consumed, $e_ij$ being the assimilisation
+Consumers then loses biomass by being consumed, $e_ij$ being the assimilation
 efficiency of the consumer $j$ on the resource $i$. Consumers also lose biomass
@@
 feeding on a resource (eq. \@ref(eq:holling)) depends on the relative preference
-of the consumer on the resource ($\omega_ij$) is limited by an half-saturation
+of the consumer on the resource ($\omega_ij$) is limited by a half-saturation
 rate ($B_0$), intraspecific interference coefficient ($c_i$), and on the
@@
 controls the shape of the functional response from a saturating function
-(Holling type II) to a sigmoid (Holling type III).
+($h = 2$, Holling type II) to a sigmoid ($h = 3$, Holling type III).
 
@@
 representing a fluctuating environment. Based on the literature and previous
-models [@vasseur_environmental_2007], we assumed that
-natural mortality rates scales inversely with the species body mass ($d_i =
-d_0M_i^{-1/4}$), as all other physiological parameters. We used a basal
-natural mortality rate of $d_0 = .4$, as done in previous
-studies[@vasseur_environmental_2007].
+models [@vasseur_environmental_2007], we assumed that natural mortality rates
+scales inversely with the species body mass ($d_i = d_0M_i^{-1/4}$), as all
+other physiological parameters. We used a basal natural mortality rate of $d_0 =
+.4$, as done in previous studies[@vasseur_environmental_2007].
 
@@
 ($\epsilon_{i, t}$) follow a normal distribution 0 centered
-($\epsilon_{i, t} \sim N(0,\sigma^2_e)$) with a variance ($\sigma^2_e$). The mortality rate each
+($\epsilon_{i, t} \sim N(0,\sigma^2_e)$) with a variance ($\sigma^2_e$). The mortality rates each
 species at the time $t$ equals to $d_{i,t} = d_i e^{\epsilon_{i, t}}$. We did so
@@
 simulated $\epsilon$ using an Ornstein-Uhlenbeck process, which is a modified
-browian motion where the stochastic values tend to come back to the central
+Brownian motion where the stochastic values tend to come back to the central
 value (i.e. $\epsilon = 0$) such as $\epsilon_t$ varies according to this
@@
 
-where $a_{i,t}$ the stochastic value generated by the Ornstein-Uhlenbeck
-process at time $t$, $\rho_{ii} = 1.0$ while all $\rho_{ij, i \neq j}$ were equal and control
-the level of response diversity.
+Where $a_{i,t}$ the stochastic value generated by the Ornstein-Uhlenbeck process
+at time $t$, $\rho_{ii} = 1.0$ while all $\rho_{ij, i \neq j}$ were equal and
+control the level of response diversity.
 
@@
     between squared brackets display all the values. Two numbers between
-    brackets are the minumum and maximal values, N being the number of unique
+    brackets are the minimum and maximal values, N being the number of unique
     values. PPMR: Predator Prey Mass Ratio. We defined response diversity as \\protect$1-\\rho$
@@
 scaled mortality rate $d$) in the community, we varied the Predator-Prey
-Bodysize Ratio (PPBR) from $`r pZ["min"]`$ to $`r pZ["max"]`$ (Fig. \@ref(fig:met)b). We further varied
-the functional response of consumer from type II to type III (resp.
-$`r ph["min"]`$ to $`r ph["max"]`$, eq. \@ref(eq:holling)) as it was shown to
+Mass Ratio (PPMR) from $`r pZ["min"]`$ to $`r pZ["max"]`$ (Fig. \@ref(fig:met)b). We further varied
+the functional response of consumer from type II to type III (i.e. from
+$h = `r ph["min"]`$ to $h = `r ph["max"]`$, eq. \@ref(eq:holling)) as it was shown to
 have a tremendous role on stability [@brose_allometric_2006]. We set a global
@@
 being the number of trophic links and $S$ being the number of species in the
-community. Species trophic level was computed recursevily from the bottom of the
+community. Species trophic level was computed recursively from the bottom of the
 food-web, such as the trophic level of a consumer was equal to the average
@@
 $\hat{B}_i$ the average biomass of the species $i$. The degree of omnivory of a
-consumer was computed  such as the sum of square of its
+consumer was computed  such as the sum of squares of its
 resource trophic levels weighted by the relative preference of the consumer for
-this resource: $\sum_i (\mathrm{TL}_i - \hat{\mathrm{TL}})^2 \omega_i/ \sum \omega_i$ [@christensen_ecopath_1992].
+each resource: $\sum_i (\mathrm{TL}_i - \hat{\mathrm{TL}})^2 \omega_i/ \sum \omega_i$ [@christensen_ecopath_1992].
 Interaction strength was computed was quantified as the biomass fluxes going
@@
 obtained by dividing average interaction strength by the average biomass of the
-consumer. Finally, the average interaction strength of a community was computed
-as the average per capita interaction strength at the exclusion of null
-interaction strengths (i.e. non present trophic interactions).
+consumer. Our way of measuring per interaction strength is very similar to
+previous metrics used in previous studies, at the difference here that we
+average fluxes over time and not the maximal interaction strength
+[@mccann_weak_1998]. Finally, the average interaction strength of a community
+was computed as the average per capita interaction strength at the exclusion of
+null interaction strengths (i.e. excluding absence of trophic interactions).
 
@@
 
-As SAE is further dependant on the evenness of species variance, we
+As SAE is further dependent on the evenness of species variance, we
 partitioned $SAE$ into $SAE_{even}$ and evenness $EVN$, such as  $EVN = SAE / SAE_{even}$.
@@
 
-with $\mathbf{B}$ and $\mathbf{E}$ being the matrices time x species for species biomass
+With $\mathbf{B}$ and $\mathbf{E}$ being the matrices time x species for species biomass
 and stochastic mortality rates respectively. Then compensatory dynamics raising
@@
 Prior to test the structural equation model, we logged all the stability
-components to transform their relation from multiplicative to additive (eq XX).
+components to transform their relation from multiplicative to additive (eq.
+\@ref(eq:scom2)).
 We ensure that all the linear models composing the structural equation model
-presented low multicollinearity (Variance Inflation Factor < 5, Table SXX). The
+presented low to moderate multicollinearity (Variance Inflation Factor < 10, Table SXX). The
 structural equation model using the R package `PiecewiseSEM`
@@
 and indirect effects using `semEff` R package [@murphy_semeff_2021]. In the
-main text, we reported standardized coefficients which are obtained by scaling
-the coefficients by the stardard deviation of the response and predictor
-variable (add formula). Finally, because we analyzed simulation, we reported
-only the direct standardized coefficients that had an absolute value above $0.1$.
+main text, we reported standardised coefficients which are obtained by scaling
+the coefficients by the standard deviation of the response and predictor
+variable (add formula). Finally, because we analysed simulation, we reported
+only the direct standardised coefficients that had an absolute value above $0.1$.
 
@@
 relationships were modulated by food-web structure and the two stressors:
-environmental stochasticity and response diversity. We modelled temporal
+environmental stochasticity and response diversity. We then modelled temporal
 stability of biomass according to food-web structure: species richness, weighted
-average trophic level, connectance, hill exponent, predator-prey size ratio, and
+average trophic level, connectance, hill exponent, predator-prey mass ratio, and
 average interaction strength, as well as environmental stochasticity and species
-response diversity. We further included the two way interactions between species
+response diversity. We further included the two-way interactions between species
 richness and food-web structure, plus between species richness and stressors.
-Finally we added the three way interaction between species richness, food-web
+Finally, we added the three-way interaction between species richness, food-web
 structure and stressors. The VIF were inferior to 5, indicating low
-multicollinearity. We then used the coefficients of the model to predict the shape
-of the relationship between community stability and species richness according
-to a gradient of response diversity and of food-web structure.
+multicollinearity. We then used the linear equation of the model and associated
+slope coefficients to predict the shape of the relationship between community
+stability and species richness according to a gradient of response diversity and
+of food-web structure. To do so, we summed all the coefficients involving species
+richness in the model, i.e. the one, two, and three-way terms. The values of the
+control variables were set to the values indicated in the Fig. \@ref(fig:pred).
 
@@
 hill exponent = 3) increase population stability (resp. $r_\delta$= `r rpt` and
-`r rph`, $r_\delta$ being the standardized coefficient, Fig. \@ref(fig:sem)a).
+`r rph`, $r_\delta$ being the standardised coefficient, Fig. \@ref(fig:sem)a).
 In turn, the variance of environmental stochasticity had a strong negative effect
@@
 one of asynchrony. Average trophic level, type III functional response and
-predator prey bodysize ratio had positive effects on community stability in
+predator prey mass ratio had positive effects on community stability in
 total (resp. `r rtst`, `r rtsh`, `r rtsz`, Fig. \@ref(fig:sem)b), driven by
@@
 empirical fish communities [@danet_species_2021], which contrasts with empirical
-data in birds and bats assemblages that reported a equivalent influence of
+data in birds and bats assemblages that reported an equivalent influence of
 population stability and asynchrony on community stability
@@
 competitive assemblages. First, the range of bodymasses is much higher in
-food-webs, which typically include species that differ in bodymass by several order of
+food-webs, which typically include species that differ in bodymass by several orders of
 magnitude [@brose_predator_2019], which in turn creates highly uneven biomass
@@
 contribution of asynchrony and population stability in food-webs and competitive
-assemblages is still a open question that might be crucial to accurately
+assemblages is still an open question that might be crucial to accurately
 address diagnostics and conservation issues. On top of food-web structure,
@@
 We further found that average trophic level increased average population
-stability, confirming previous theoreical [@brose_allometric_2006;
+stability, confirming previous theoretical [@brose_allometric_2006;
 @shanafelt_stability_2018; @eschenbrenner_diversity_2023] and
@@
 #diversity on the compensatory dynamics due to environment. Our interpretation is
-#that higher species richness synchronizes more species fluctuations due to
+#that higher species richness synchronises more species fluctuations due to
 #environmental mortality when species are not independent because each added
@@
 consumers when their preys have a low biomass which leads to a less dramatic
-fluctuations of prey biomass. Furthermore, we found that functional response of
+fluctuation of prey biomass. Furthermore, we found that functional response of
 type III decreased asynchrony by decreasing compensatory dynamics due to species
@@
 negative effects of complexity on stability-richness relationship are cancelled
-when response diversity is high. A interpretation is that environmental
+when response diversity is high. An interpretation is that environmental
 stochasticity itself does not override the negative complexity-stability

### 2024-01-15 R/string_replacements.R

@@ -1,5 +1,6 @@
 var_replacement <- function() {
   c(
+    bm_total = "Total biomass",
     stab_com = "Community stability",
     log_stab_com = "Community stability",
     stab_pop = "Population stability",

### 2024-02-16 _targets.Rmd
Update figures

@@
 list(
-  tar_target(formula_fixed_rho, "log_richness +
-    ct_alive +
-    log1_avg_max_int_alive +
-    productivity +
-    rho +
-    I(rho^2) +
-    env_stoch +
-
-    log_richness:ct_alive +
-    log_richness:log1_avg_max_int_alive +
-    log_richness:productivity +
-    log_richness:rho +
-
-    log1_avg_max_int_alive:ct_alive +
-    log1_avg_max_int_alive:productivity +
-    log1_avg_max_int_alive:rho +
-
-    ct_alive:rho +
-    ct_alive:productivity +
-    rho:productivity +
-    I(rho^2):productivity +
-
-    log_richness:log1_avg_max_int_alive:ct_alive +
-    log_richness:log1_avg_max_int_alive:productivity +
-    log_richness:log1_avg_max_int_alive:rho +
-    log_richness:ct_alive:productivity +
-    log_richness:ct_alive:rho +
-    log_richness:rho:productivity +
-
-    log1_avg_max_int_alive:ct_alive:rho +
-    log1_avg_max_int_alive:ct_alive:productivity +
-    log1_avg_max_int_alive:rho:productivity +
-
-    ct_alive:rho:productivity"
-    ),
+  tar_target(formula_fixed_rho, formula_mod_rho_fixed_effect()),
   tar_target(formula_rand_rho, "(1 | Z)"),
@@
 # plot
+
+```{targets sem_tot_predictor, tar_simple = TRUE}
+c("richness", "avg_int_strength", "w_avg_tlvl", "ct_alive", "Z", "h",
+  "resp_div", "env_stoch")
+```
+
+```{targets plot-sem-tot}
+list(
+  tar_target(p_sem_tot_stab,
+    sem_simplified_eff_tab %>%
+      filter(effect_type == "total") %>%
+      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
+      filter(predictor %in% sem_tot_predictor()) %>%
+      mutate(
+        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
+        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE)
+        ) %>%
+      ggplot(aes(
+          y = predictor,
+          x = effect,
+          color = response,
+          alpha = response,
+          ymin = lower_ci,
+          ymax = upper_ci)
+        ) +
+      geom_pointrange() +
+      scale_colour_manual(values = stab_color()) +
+      scale_alpha_manual(values = stab_alpha()) +
+      #  geom_hline(yintercept = 0, linetype = "dashed") +
+      geom_vline(xintercept = 0, linetype = "dashed") +
+      #facet_grid(cols = vars(response)) +
+      labs(
+        x = "Total standardised effects",
+        color = "Stability component",
+        alpha = "Stability component"
+        ) +
+      theme_bw() +
+      theme(
+        axis.title.y = element_blank(),
+        #legend.justification = "right",
+        legend.position = "bottom") +
+      guides(
+        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
+        ) +
+      theme(
+        legend.title = element_blank(),
+        legend.position = c(.005, .995),
+        legend.justification = c("left", "top")
+      )
+    ),
+  tar_target(p_sem_tot_stab_leg,
+    plot_grid(
+      print(p_sem_tot_stab +
+        theme(
+          legend.position = "none",
+        )
+        ),
+      get_legend(p_sem_tot_stab),
+      nrow = 2,
+      rel_heights = c(1, .05)
+      )
+  )
+)
+```
 
@@
 list(
-#  tar_target(p_stab_s_prod,
-#    sim_fw %>%
-#      filter(productivity %in% c(5, 30), rho == 0, env_stoch == .3) %>%
-#      ggplot(aes(x = richness, y = stab_com, color = as.factor(productivity))) +
-#      geom_point() +
-#      geom_smooth() +
-#      labs(x = "Species richness", y = "Community stability", color = "Productivity") +
-#      theme_bw()),
     tar_target(p_stab_s_env_stoch,
@@
          plot_grid(
-#           p_stab_s_prod,
            p_stab_s_env_stoch,
@@
 
-```{targets p_sem_tot_stab, tar_simple=TRUE}
-tar_read(sem_eff_tab) %>%
-  filter(effect_type == "total") %>%
-  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
-  filter(!predictor %in% c("evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async", "S", "ct")) %>%
-  mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
-  ggplot(aes(
-      x = predictor,
-      y = effect,
-      ymin = lower_ci,
-      ymax = upper_ci)
-    ) +
-  geom_pointrange() +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  facet_grid(cols = vars(response)) +
-  labs(x = "Predictor", y = "Total effect") +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 20, hjust = 1))
-```
-
 # Table
@@
 ```{r tar-make}
-#tar_make()
+tar_make()
+tar_visnetwork()
 tar_make_future(workers = 3)
@@
 
-```{r}
-tar_load(c(formula_sem_bivariate_relations, scaled_sem_simplified, scaled_sim_fw_sem))
+## SEM plot
+
+The partial residual function does not work inside targets unfortunately,
+
+>   Last error: ℹ In argument: `data = map(...)`.
+> Caused by error in `map()`:
+> ℹ In index: 1.
+> Caused by error in `is.data.frame()`:
+> ! object 'scaled_sim_fw_sem' not found
+
+```{r}
+tar_load(
+  c(
+    formula_sem_bivariate_relations,
+    scaled_sem_simplified,
+    scaled_sim_fw_sem
+  )
+)
 sem_simplified_bivariate_relations <- tibble(formula = formula_sem_bivariate_relations) %>%
@@
     into = c("response", "predictor"),
-        sep = " ~ ", remove = FALSE) %>%
+    sep = " ~ ", remove = FALSE
+    ) %>%
 mutate(
@@
 label_sem <- as.character(as.roman(seq_len(nrow(sem_simplified_bivariate_relations))))
-p_sem_simplified_bivariate_relations <-
-  plot_grid(
+p_sem_simplified_bivariate_relations <- plot_grid(
   plotlist = sem_simplified_bivariate_relations$plot,
@@
 )
+```
+
+```{r}
 sem_file <- here("report", "figures", "sem_stab_simplified.pdf")
@@
 )
+```
+
+```{r fig-sem}
 ggsave_multiple(
@@
 ```{r}
-library(RColorBrewer)
-library(ggbreak)
-#cols <- c("Community stability" = "black",
-#  "Asynchrony" = "blue",
-#  "Population stability" = "darkgreen"
-#)
-custom_stab_color <- c(
-  "Community stability" = "black", #"#ffffbf"
-  "Asynchrony" = "#91bfdb",
-  "Population stability" = "#fc8d59"
-)
-alpha <- c("Community stability" = 1, "Asynchrony" = 1, "Population stability" = 1)
-
-sem_tot_predictor <- c("richness", "avg_int_strength", "w_avg_tlvl",
-  "ct_alive", "Z", "h", "resp_div", "env_stoch")
-var_replacement()[sem_tot_predictor]
-p_sem_tot_stab <- tar_read(sem_simplified_eff_tab) %>%
-  filter(effect_type == "total") %>%
-  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
-  filter(predictor %in% sem_tot_predictor) %>%
-  mutate(
-    response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
-    predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor)], .ordered = TRUE)
-) %>%
-  ggplot(aes(
-      y = predictor,
-      x = effect,
-      color = response,
-      alpha = response,
-      ymin = lower_ci,
-      ymax = upper_ci)
-    ) +
-  geom_pointrange() +
-  scale_colour_manual(values = custom_stab_color) +
-  scale_alpha_manual(values = alpha) +
-#  geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  #facet_grid(cols = vars(response)) +
-  labs(
-    x = "Total standardised effects",
-    color = "Stability component",
-    alpha = "Stability component"
-    ) +
-  theme_bw() +
-  theme(
-    axis.title.y = element_blank(),
-    #legend.justification = "right",
-    legend.position = "bottom") +
-  guides(
-    color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
-    ) +
-  theme(
-    legend.title = element_blank(),
-    legend.position = c(.005, .995),
-    legend.justification = c("left", "top")
-  )
-p_sem_tot_stab_leg <- plot_grid(
-  print(p_sem_tot_stab +
-    theme(
-      legend.position = "none",
-    )
-  ),
-  get_legend(p_sem_tot_stab),
-  nrow = 2,
-  rel_heights = c(1, .05)
-)
 ggsave_multiple(
@@
   plot = print(
-    p_sem_tot_stab +
+    tar_read(p_sem_tot_stab) +
       guides(
@@
   print(
-    p_sem_tot_stab +
+    tar_read(p_sem_tot_stab) +
       guides(

### 2024-02-16 paper/manuscript.Rmd
Update figures

@@
 ---
-## IDEA, meeting with Sonia
-#- Simplifying SEM in main text, move details to appendix
-#- State diagram for stability - richness relationships along two food-web
-#  metrics and panels varying response diversity.
-#- Look at the french data for portefolio and compensatory dynamics effects.
-#- Mid-October
+## IDEA:
+# Talk about about how stochasticity minor interaction effects similar to
+# dispersal (Holt, 1985; other papers I guess)
 ---

### 2024-02-16 R/model_helpers.R

@@ -1,3 +1,41 @@
+formula_mod_rho_fixed_effect <- function() {
+  "log_richness +
+  ct_alive +
+  log1_avg_max_int_alive +
+  productivity +
+  rho +
+  I(rho^2) +
+  env_stoch +
+
+  log_richness:ct_alive +
+  log_richness:log1_avg_max_int_alive +
+  log_richness:productivity +
+  log_richness:rho +
+
+  log1_avg_max_int_alive:ct_alive +
+  log1_avg_max_int_alive:productivity +
+  log1_avg_max_int_alive:rho +
+
+  ct_alive:rho +
+  ct_alive:productivity +
+  rho:productivity +
+  I(rho^2):productivity +
+
+
+  log_richness:log1_avg_max_int_alive:ct_alive +
+  log_richness:log1_avg_max_int_alive:productivity +
+  log_richness:log1_avg_max_int_alive:rho +
+  log_richness:ct_alive:productivity +
+  log_richness:ct_alive:rho +
+  log_richness:rho:productivity +
+
+  log1_avg_max_int_alive:ct_alive:rho +
+  log1_avg_max_int_alive:ct_alive:productivity +
+  log1_avg_max_int_alive:rho:productivity +
+
+  ct_alive:rho:productivity"
+
+}
 formula_stab_fw_model <- function(
   resp = "stab_com",
   rand_effect = TRUE,

### 2024-02-16 R/plotting_methods.R

@@ -9,6 +9,28 @@ rho_cat_colors <- function() {
   )
 }
 
+stab_color <- function() {
+  c(
+    "Community stability" = "black", #"#ffffbf"
+    "Asynchrony" = setNames(rho_cat_colors()["High"], NULL),
+    "Population stability" = setNames(rho_cat_colors()["Low"], NULL)
+  )
+}
+
+stab_alpha <- function () {
+  c(
+    "Community stability" = 1,
+    "Asynchrony" = 1,
+    "Population stability" = 1
+  )
+}
+
+sem_tot_predictor <- function () {
+c("richness", "avg_int_strength", "w_avg_tlvl", "ct_alive", "Z", "h",
+  "resp_div", "env_stoch")
+
+}
+
 resp_div_cat_colors <- function() {
   rho_cat_colors()
 }

### 2024-02-16 R/string_replacements.R

@@ -14,9 +14,9 @@ var_replacement <- function() {
     cpe = "Compensatory effect",
     cpe_int = "Comp effect (Interaction)",
     cpe_env = "Comp effect (Environment)",
-    sae_total = "Stat Avg effect",
-    sae_even = "Stat Avg effect (Even)",
-    evenness_sae = "Stat Avg effect (Evenness)",
+    sae_total = "Portfolio effect",
+    sae_even = "Portfolio effect (Even)",
+    evenness_sae = "Portfolio effect (Evenness)",
     log1_avg_max_int_alive = "Avg interaction strength",
     avg_max_int_alive = "Avg interaction strength",
     avg_int_strength = "Avg interaction strength",
@@ -30,7 +30,7 @@ var_replacement <- function() {
     richness = "Richness",
     rho = "Env Corr",
     productivityenrichment = "Enrichment",
-    env_stoch = "Env variance",
+    env_stoch = "Env stochasticity",
     Z = "PPMR",
     h = "Hill exponent",
     S = "Initial species richness",

### 2024-02-16 draft.jl

@@ -1,3 +1,4 @@
+using EcologicalNetworksDynamics: simulate_deter
 using Revise
 using EcologicalNetworksDynamics
 using SparseArrays
@@ -17,6 +18,14 @@ include("src/interaction_strength.jl")
 include("src/sim.jl")
 include("src/plot.jl")
 include("src/get_modules.jl")
+
+fw = FoodWeb(nichemodel, 10, C = .4, Z = 100)
+p = ModelParameters(fw)
+tmax = 1000
+m = simulate_deter(p, rand(richness(fw)))
+coefficient_of_variation(m, last = 100)
+
+simulate(p, rand(richness(fw)), saveat = (0:1:tmax))
 
 m = (t = 0, b = 0)
 m[:t]

### 2024-02-16 scripts/ct_S_h_d_allometric_array.jl

@@ -1,25 +1,4 @@
-println("Rundir is $(pwd())")
-
-import Pkg
-using Distributed, Serialization
-
-first_sim = parse(Int, ARGS[1])
-last_sim = parse(Int, ARGS[2])
-
-println("Running parameters combination from $(ARGS[1]) to $(ARGS[2])")
-
-#ncpu = maximum([length(Sys.cpu_info()), 15])
-ncpu = 20
-
-#Dir
-proj_dir = expanduser("~/xStressorsStabBEFW")
-
-#Flag enables all the workers to start on the project of the current dir
-flag = "--project=" * proj_dir
-println("Workers run with flag: $(flag)")
-addprocs(ncpu - 1, exeflags=flag)
-#addprocs(5, exeflags=flag)
-println("Using $(ncpu -1) cores")
+include("../scripts/sim_setup.jl")
 
 # Prepare saving
 dest_dir = "/mnt/parscratch/users/bi1ahd/sim/simCSh_allo_d5/"
@@ -27,19 +6,6 @@ dest_dir = "/mnt/parscratch/users/bi1ahd/sim/simCSh_allo_d5/"
 if !isdir(dest_dir)
     mkdir(dest_dir)
 end
-
-
-
-
-@everywhere import Pkg, Random.seed!
-@everywhere using DifferentialEquations, EcologicalNetworksDynamics, SparseArrays
-@everywhere using LinearAlgebra, DataFrames
-@everywhere using Distributions, ProgressMeter
-@everywhere using StatsBase, CSV, Arrow
-@everywhere include("../src/stochastic_mortality_model.jl")
-@everywhere include("../src/sim.jl")
-@everywhere include("../src/interaction_strength.jl")
-
 
 param = DataFrame(Arrow.Table(joinpath(proj_dir, "scripts/param_comb_ct_S_h_d3.arrow")))
 

### 2024-02-21 _targets.Rmd
Add complete table of parameters

@@
       summarise(
-        u = list(unique(values)),
+        u = list(sort(unique(values))),
         n = length(unique(round(values, 2))),
@@
       mutate(Parameter = recode_factor(Parameter, !!!var_replacement()))
+  ),
+  tar_target(fix_parameter,
+    tibble(
+      c = 0,
+      B0 = 0.5,
+      r = 1.0,
+      K = 10,
+      alpha_ij = 0.5,
+      prod_mass = 1.0
+    )
+  ),
+  tar_target(allometric_parameter,
+    tibble(
+      d0 = 0.4,
+      allo_slope = -0.25,
+      ax = list(c(producer = 0, ectotherm = 0.88)), #, endotherm = 0.314
+      ay = list(c(producer = 0.0, ectotherm = 4.0)), #, endotherm = 8.0 #not allometric
+      eij = list(c(carnivory = 0.85, herbivory = 0.45))
+    )
+  ),
+  tar_target(param_table,
+    fix_parameter %>%
+      bind_cols(allometric_parameter) %>%
+      mutate(across(where(is.list), ~map_chr(.x, function(x) paste_named_vector(x)))) %>%
+      mutate(across(where(is.double), ~as.character(.x))) %>%
+      pivot_longer(everything(), names_to = "Parameter", values_to = "Values") %>%
+      mutate(
+        Parameter = latex_symbol_replacement()[Parameter],
+        Parameter = surround_latex_math(Parameter)
+      ) %>%
+      bind_rows(tab_sim_param)
   )
@@
 tar_load(sim_param_tab)
+tar_load(tab_sim_param)
+tar_load(param_table)
+kable(param_table, "html", booktabs = T, escape = FALSE) %>%
+  kable_styling()
+```
+
+```{r}
 ```

### 2024-02-22 _targets.Rmd

@@
   )
+)
+```
+
+```{targets all-analysis}
+library(tarchetypes)
+tar_map(
+  values = tibble::tibble(
+  names = c("no_rerun", "non_allo_no_rerun", "rerun")
+    ),
+  names = names,
+  tar_target(sim_files, here::here("data", paste0("sim_fw_", names)), format = "file"),
+  tar_target(sim_fw, readRDS(sim_files)),
+  tar_target(sem_simplified_eff_file, here::here("data", paste0("sem_simplified_eff_", names)), format = "file"),
+  tar_target(sem_simplified_eff, {
+    readRDS(sem_simplified_eff_file)
+    }
+  ),
+  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
+)
+```
+
+```{r, eval = FALSE}
+tar_load(c(sem_simplified_eff_tab_no_rerun, sem_simplified_eff_tab_rerun,
+    sem_simplified_eff_tab_non_allo_no_rerun))
+sem_simplified_eff_tab_no_rerun %>%
+  filter(effect_type == "total", response %in% c("pop_stab"))
+sem_simplified_eff_tab_rerun %>%
+  filter(effect_type == "total", response %in% c("pop_stab"))
+sem_simplified_eff_tab_non_allo_no_rerun %>%
+  filter(effect_type == "total", response %in% c("pop_stab"))
+```
+
+```{r, eval = FALSE}
+library(tidyverse)
+library(magrittr)
+tar_load(c(sim_fw_no_rerun, sim_fw_rerun))
+sim_id <- intersect(sim_fw_no_rerun$sim_id, sim_fw_rerun$sim_id)
+cor(
+  sim_fw_no_rerun[sim_fw_no_rerun$sim_id %in% sim_id, ]$stab_com, sim_fw_rerun[sim_fw_rerun$sim_id %in% sim_id, ]$stab_com, use = "pairwise.complete.obs"
+)
+cor(
+  sim_fw_no_rerun[sim_fw_no_rerun$sim_id %in% sim_id, ]$richness, sim_fw_rerun[sim_fw_rerun$sim_id %in% sim_id, ]$richness, use = "pairwise.complete.obs"
+)
+cor(
+  sim_fw_no_rerun[sim_fw_no_rerun$sim_id %in% sim_id, ]$async, sim_fw_rerun[sim_fw_rerun$sim_id %in% sim_id, ]$async, use = "pairwise.complete.obs"
+)
+cor(
+  sim_fw_no_rerun[sim_fw_no_rerun$sim_id %in% sim_id, ]$stab_pop, sim_fw_rerun[sim_fw_rerun$sim_id %in% sim_id, ]$stab_pop, use = "pairwise.complete.obs"
 )

### 2024-02-22 _targets.Rmd
Add SEM sensibility analysis

@@
 lapply(list.files(here::here("R"), full.names = TRUE), source)
+map_tibble <- tibble::tibble(
+  names = c("no_rerun", "non_allo_no_rerun", "rerun")
+    )
 ```
@@
 tar_map(
-  values = tibble::tibble(
-  names = c("no_rerun", "non_allo_no_rerun", "rerun")
-    ),
+  values = map_tibble,
   names = names,
@@
   tar_target(sem_simplified_eff_file, here::here("data", paste0("sem_simplified_eff_", names)), format = "file"),
-  tar_target(sem_simplified_eff, {
-    readRDS(sem_simplified_eff_file)
-    }
-  ),
+  tar_target(sem_simplified_eff, { readRDS(sem_simplified_eff_file) }),
+  tar_target(sem_simplified_collinearity_file, here::here("data", paste0("sem_simplified_collinearity_", names)), format = "file"),
+  tar_target(sem_simplified_collinearity, { readRDS(sem_simplified_collinearity_file) }),
+  tar_target(sem_simplified_rsquared_file, here::here("data", paste0("sem_simplified_rsquared_", names)), format = "file"),
+  tar_target(sem_simplified_rsquared, { readRDS(sem_simplified_rsquared_file) }),
   tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
 )
+```
+
+```{r targets group-all-analysis}
+list(
+  tar_target(sem_simplified_eff_tab_tot,
+    tibble(
+      sim_type = map_tibble$names,
+      data = list(sem_simplified_eff_tab_no_rerun,
+        sem_simplified_eff_tab_non_allo_no_rerun, sem_simplified_eff_tab_rerun)
+      ) %>%
+    unnest(cols = data)),
+  tar_target(p_sem_simplified_eff_tab_tot,
+    sem_simplified_eff_tab_tot %>%
+      filter(effect_type == "total") %>%
+      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
+      filter(predictor %in% sem_tot_predictor()) %>%
+      mutate(
+        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
+        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE),
+        sim_type = recode_factor(sim_type, !!!sim_type_replacement(), .ordered = TRUE)
+        ) %>%
+      ggplot(aes(
+          y = predictor,
+          x = effect,
+          color = response,
+          shape = sim_type
+        )
+        ) +
+      geom_point(alpha = .5) +
+      scale_colour_manual(values = stab_color()) +
+      scale_alpha_manual(values = stab_alpha()) +
+      #  geom_hline(yintercept = 0, linetype = "dashed") +
+      geom_vline(xintercept = 0, linetype = "dashed") +
+      facet_grid(cols = vars(response)) +
+      labs(
+        x = "Total standardised effects",
+        color = "Stability component",
+        alpha = "Stability component"
+        ) +
+      theme_bw() +
+      theme(
+        axis.title.y = element_blank(),
+        #legend.justification = "right",
+        legend.position = "bottom") +
+      guides(
+        color = FALSE
+        ) +
+      theme(
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        legend.justification = c("left", "top")
+      )
+  )
+)
+
+```
+
+```{r, eval = FALSE}
+tar_load(c(sem_simplified_collinearity_no_rerun, sem_simplified_collinearity_rerun,
+    sem_simplified_collinearity_non_allo_no_rerun))
+sem_simplified_collinearity_no_rerun %>%
+  print(n = 30)
+sem_simplified_collinearity_rerun %>%
+  print(n = 30)
+sem_simplified_collinearity_non_allo_no_rerun %>%
+  print(n = 30)
 ```
@@
   filter(effect_type == "total", response %in% c("pop_stab"))
+```
+
+```{r, eval = FALSE}
+tar_load(sem_simplified_eff_tab_tot)
+
 ```
@@
 ```
+```{r fig-sem-tot-sensibility}
+ggsave_multiple(
+  paste0("p_sem_simplified_eff_tab_tot", c(".jpg", ".png", ".pdf")),
+  plot = tar_read(p_sem_simplified_eff_tab_tot),
+  path = here::here("report", "figures"),
+  scale = 2.4,
+  dpi = 400,
+  width = 80,
+  height = 80 * .5,
+  units = "mm")
+```
 

### 2024-02-22 R/string_replacements.R

@@ -96,3 +96,12 @@ latex_symbol_replacement <- function() {
     prod_mass = "M_p"
   )
 }
+
+sim_type_replacement <- function() {
+  c(
+    "no_rerun" = "Default (5000 timesteps)",
+    "rerun" = "Until no extinction",
+    "non_allo_no_rerun" = "Fixed death rate"
+  )
+
+}

### 2024-03-05 _targets.Rmd
Update SEM figures

--- 2024-02-21 _targets.Rmd
@@
 lapply(list.files(here::here("R"), full.names = TRUE), source)
+map_tibble <- tibble::tibble(
+  names = c("no_rerun", "non_allo_no_rerun", "rerun", "no_rerun_short",
+  "no_rerun_no_disconnected")
+    )
 ```
@@
 list(
-  tar_target(sim_fw_file, here::here("data", "sim_fw"), format = "file"),
-  tar_target(sim_fw, {
-    x <- readRDS(sim_fw_file)
-    x %>%
-      mutate(resp_div = 1 - rho)
-  }),
+  tar_target(sim_fw, sim_fw_rerun),
   tar_target(sim_param, readRDS(here::here("data", "sim_param_d2"))),
-  tar_target(sim_fw_df, as.data.frame(sim_fw)),
-  tar_target(sim_fw_cons, readRDS(here::here("data", "sim_fw_cons"))),
-  tar_target(sim_fw_cons_df, as.data.frame(sim_fw_cons))
+  tar_target(sim_fw_df, as.data.frame(sim_fw))
   )
@@
 
+```{targets all-analysis}
+library(tarchetypes)
+tar_map(
+  values = map_tibble,
+  names = names,
+  tar_target(sim_files, here::here("data", paste0("sim_fw_", names)), format = "file"),
+  tar_target(sim_fw, readRDS(sim_files)),
+  tar_target(sem_simplified_eff_file, here::here("data", paste0("sem_simplified_eff_", names)), format = "file"),
+  tar_target(sem_simplified_eff, { readRDS(sem_simplified_eff_file) }),
+  tar_target(sem_simplified_collinearity_file, here::here("data", paste0("sem_simplified_collinearity_", names)), format = "file"),
+  tar_target(sem_simplified_collinearity, { readRDS(sem_simplified_collinearity_file) }),
+  tar_target(sem_simplified_rsquared_file, here::here("data", paste0("sem_simplified_rsquared_", names)), format = "file"),
+  tar_target(sem_simplified_rsquared, { readRDS(sem_simplified_rsquared_file) }),
+  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
+)
+```
+
+```{targets group-all-analysis}
+list(
+  tar_target(sem_simplified_tot,
+    tibble(
+      sim_type = c(
+        "no_rerun",
+        "non_allo_no_rerun",
+        "rerun",
+        "no_rerun_short",
+        "no_rerun_no_disconnected"),
+      eff = list(
+        sem_simplified_eff_tab_no_rerun,
+        sem_simplified_eff_tab_non_allo_no_rerun,
+        sem_simplified_eff_tab_rerun,
+        sem_simplified_eff_tab_no_rerun_short,
+        sem_simplified_eff_tab_no_rerun_no_disconnected
+        ),
+      rsq = list(
+        sem_simplified_rsquared_no_rerun,
+        sem_simplified_rsquared_non_allo_no_rerun,
+        sem_simplified_rsquared_rerun,
+        sem_simplified_rsquared_no_rerun_short,
+        sem_simplified_rsquared_no_rerun_no_disconnected
+        ),
+      collinearity = list(
+        sem_simplified_collinearity_no_rerun,
+        sem_simplified_collinearity_non_allo_no_rerun,
+        sem_simplified_collinearity_rerun,
+        sem_simplified_collinearity_no_rerun_short,
+        sem_simplified_collinearity_no_rerun_no_disconnected
+        ),
+    )
+  ),
+  tar_target(sem_simplified_eff_tab_tot,
+    sem_simplified_tot %>%
+      select(sim_type, eff) %>%
+      unnest(cols = eff)),
+  tar_target(p_sem_simplified_eff_tab_tot,
+    sem_simplified_eff_tab_tot %>%
+      filter(effect_type == "total") %>%
+      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
+      filter(predictor %in% sem_tot_predictor()) %>%
+      mutate(
+        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
+        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE),
+        sim_type = recode_factor(sim_type, !!!sim_type_replacement(), .ordered = TRUE)
+        ) %>%
+      ggplot(aes(
+          y = predictor,
+          x = effect,
+          color = response,
+          shape = sim_type
+        )
+        ) +
+      geom_point(alpha = .5) +
+      scale_colour_manual(values = stab_color()) +
+      scale_alpha_manual(values = stab_alpha()) +
+      #  geom_hline(yintercept = 0, linetype = "dashed") +
+      geom_vline(xintercept = 0, linetype = "dashed") +
+      facet_grid(cols = vars(response)) +
+      labs(
+        x = "Total standardised effects",
+        color = "Stability component",
+        alpha = "Stability component"
+        ) +
+      theme_bw() +
+      theme(
+        axis.title.y = element_blank(),
+        #legend.justification = "right",
+        legend.position = "bottom") +
+      guides(
+        color = FALSE
+        ) +
+      theme(
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        legend.justification = c("left", "top")
+      )
+  )
+)
+```
+
 ```{targets simplified-sem}
@@
       richness = lm(richness ~ ct + S, sim_fw_sem),
-      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
       w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
@@
       pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_sem),
-      sae_total = lm(sae_total ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_sem),
+      #sae_even = lm(sae_even ~ richness, sim_fw_sem),
+      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_sem),
+      sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
       cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + resp_div, sim_fw_sem),
@@
     ),
-  tar_target(sem_simplified_coeff, {
-    ti <- summary(sem_simplified)$coefficients[, c(1, 2, 8, 9)]
-    colnames(ti)[4] <- "Signif"
-    ti
-    }),
+  tar_target(sem_main_text_model_list,
+    list(
+      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch, sim_fw_sem),
+      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive, sim_fw_sem),
+      sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
+      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div, sim_fw_sem),
+      async = lm(async ~ sae_total + cpe, sim_fw_sem),
+      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
+    )
+  ),
+  tar_target(sem_main_text, {
+    ti <- as.psem(sem_main_text_model_list)
+    #update(ti, avg_omnivory %~~% w_avg_tlvl)
+    }
+    ),
   tar_target(sem_simplified_collinearity,
-    map_dfr(setNames(sem_simplified_model_list, names(sem_simplified_model_list)),
-      performance::check_collinearity,
-      .id = "response") %>%
-    as_tibble),
+    sem_simplified_collinearity_no_rerun
+    ),
   tar_target(sem_simplified_rsquared,
-    map_dfr(sem_simplified_model_list, rsquared) %>%
+    sem_simplified_rsquared_no_rerun %>%
       mutate(
@@
   ),
-  tar_target(sem_simplified_eff_file, here::here("data", "sem_simplified_eff"), format = "file"),
-  tar_target(sem_simplified_eff, {
-    readRDS(sem_simplified_eff_file)
-    #semEff(sem_simplified, ci.type = "perc", R = 10, seed = 13, parallel = "no", data = sim_fw_sem)
-    }
-    ),
-  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
-)
+  tar_target(sem_simplified_eff_tab, sem_simplified_eff_tab_no_rerun)
+)
+```
+
+```{r, eval = FALSE}
+tar_load(sem_main_text)
+m <- list(
+  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch, sim_fw_sem),
+  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive, sim_fw_sem),
+  sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
+  cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div, sim_fw_sem),
+  async = lm(async ~ sae_total + cpe, sim_fw_sem),
+  stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
+)
+ti <- as.psem(m)
+update(ti, avg_omnivory %~~% w_avg_tlvl)
+summary(ti)
 ```
@@
     }),
-  tar_target(fix_fw_stab, fixef(model_fw_stab)$cond),
-  tar_target(fix_fw_stab_comp,
+  tar_target(fixed_effect_fw_stab, fixef(model_fw_stab)$cond),
+  tar_target(fixed_effect_fw_stab_comp,
     model_fw_stab_comp %>%
@@
         ~get_slope_change(
-          coeff = fix_fw_stab,
+          coeff = fixed_effect_fw_stab,
           gen_term = "richness",
@@
   tar_target(pred_stab_comp_resp_div,
-    fix_fw_stab_comp %>%
+    fixed_effect_fw_stab_comp %>%
       left_join(
         list(
-          response = fix_fw_stab_comp$response,
+          response = fixed_effect_fw_stab_comp$response,
           variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive")
@@
 
-```{targets sem_tot_predictor, tar_simple = TRUE}
-c("richness", "avg_int_strength", "w_avg_tlvl", "ct_alive", "Z", "h",
-  "resp_div", "env_stoch")
+```{r, eval = FALSE}
+tar_load(sem_simplified_tot)
+sem_simplified_tot %>%
+  select(sim_type, collinearity) %>%
+  unnest(cols = c(collinearity)) %>%
+  group_by(sim_type) %>%
+  summarise(
+    med = median(VIF),
+    max = max(VIF)
+  )
 ```
@@
   tar_target(p_sem_tot_stab,
-    sem_simplified_eff_tab %>%
+    sem_simplified_eff_tab_no_rerun %>%
       filter(effect_type == "total") %>%
@@
       )
+  ),
+  tar_target(sem_file, here("report", "figures", "sem_stab_simplified_simple.pdf"), format = "file"),
+  tar_target(p_sem,
+    ggdraw() +
+      draw_image(magick::image_read_pdf(sem_file, density = 600),
+        x = 0, y = 0,
+        width = 1, height = 1,
+        hjust = 0, halign = 0, valign = 0
+      )
+  ),
+  tar_target(p_sem_fig,
+    plot_grid(
+      p_sem,
+      print(
+        tar_read(p_sem_tot_stab) +
+          guides(
+            color = guide_legend(override.aes = list(linetype = 0, alpha = 1)),
+            y = "none",
+            y.sec = "axis"
+          ) +
+          theme(
+            legend.title = element_blank(),
+            legend.position = c(.005, .995),
+            legend.justification = c("left", "top"),
+
+          )
+        ),
+      nrow = 2, rel_heights = c(1, .8),
+      labels = "auto"
+  )
+
   )
@@
 
+```{r, eval=FALSE}
+tar_load(sem_simplified_eff_tab_no_rerun_short)
+sem_simplified_eff_tab_rerun %>%
+  filter(
+    effect_type == "direct",
+    predictor %in% c(sem_tot_predictor(), "async", "stab_com", "sae_total", "cpe", "evenness_sae", "sae_even")
+    ) %>%
+select(response, predictor, effect) %>%
+filter(abs(effect) > .05) %>%
+mutate(effect = round(effect, 2))
+```
+
 ```{r debug, eval = FALSE}
@@
 ```{r}
-sem_file <- here("report", "figures", "sem_stab_simplified.pdf")
-p_sem <- ggdraw() +
-  draw_image(magick::image_read_pdf(sem_file, density = 600),
-    x = 0, y = 0,
-    width = 1, height = 1,
-    hjust = 0, halign = 0, valign = 0
-  )
 p_sem_tot <- plot_grid(
@@
 
-```{r}
+```{r, eval = FALSE}
 bivariate_rel_file <- here("report", "figures", "p_sem_simplified_bivariate_relations.jpg")
@@
   )
-
-p_sem_fig <- plot_grid(
-  p_sem, p_bivariate_rel,
-  print(
-    tar_read(p_sem_tot_stab) +
-      guides(
-        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
-      ) +
-      theme(
-        legend.title = element_blank(),
-        legend.position = c(.005, .995),
-        legend.justification = c("left", "top"),
-
-      )
-    ),
-  nrow = 3, rel_heights = c(.7, 1, .6),
-  labels = "auto"
-)
-
-p_sem_fig <- plot_grid(p_sem,
-  print(
-    tar_read(p_sem_tot_stab) +
-      guides(
-        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
-      ) +
-      theme(
-        legend.title = element_blank(),
-        legend.position = c(.005, .995),
-        legend.justification = c("left", "top"),
-
-      )
-    ),
-  p_bivariate_rel,
-  NULL,
-  nrow = 2, rel_heights = c(.7, 1),
-  labels = c("a", "b", "c", ""),
-  align = "h", axis = "tblr"
-)
+```
+
+```{r}
+
 ggsave_multiple(
   paste0("p_sem_fig", c(".png", ".pdf")),
-  plot = p_sem_fig,
+  plot = tar_read(p_sem_fig),
   path = here::here("report", "figures"),
@@
   width = 80,
-  height = 80 * .8,
+  height = 80 * 1,
   units = "mm")
@@
 ```{r}
-tar_load(fix_fw_stab)
-tar_load(fix_fw_stab_comp)
+tar_load(fixed_effect_fw_stab)
+tar_load(fixed_effect_fw_stab_comp)
 tar_load(pred_stab_comp_rho)
@@
 ```{r}
-tar_load(fix_fw_stab)
+tar_load(fixed_effect_fw_stab)
 ```

### 2024-03-05 paper/manuscript.Rmd
Update SEM figures

@@
 output:
-  officedown::rdocx_document:
-    number_sections: false
   bookdown::pdf_document2:
@@
     spacing: double
+    number_sections: false
+  officedown::rdocx_document:
     number_sections: false
@@
 tar_load(c(sem_eff_tab, sem_simplified_eff_tab))
+#TODO: change for main text SEM, other SEM in appendix
 
@@
 ```{r, eval = FALSE}
-sem_simplified_eff_tab %>%
-  filter(abs(effect) > .1, effect_type == "direct")
+tar_load(c(sem_main_text, sem_simplified))
+get_coeff_psem <- function(x = NULL) {
+  ti <- summary(x)$coefficients
+  ti[[9]] <- NULL
+  janitor::clean_names(ti)
+}
+
+ti <- get_coeff_psem(sem_main_text)
+ti %>%
+  filter(abs(std_estimate) > .05) %>%
+  select(response, predictor, std_estimate) %>%
+  mutate(std_estimate = round(std_estimate, 1))
+to <- get_coeff_psem(sem_simplified)
+to %>%
+  filter(
+    abs(std_estimate) > .05,
+    predictor %in% c(
+      "env_stoch", "resp_div", "ct_alive", "avg_int_strength", "w_avg_tlvl", "richness",
+      "sae_total", "evenness_sae", "cpe", "pop_stab", "async", "stab_com"
+    )) %>%
+  select(response, predictor, std_estimate) %>%
+  mutate(std_estimate = round(std_estimate, 1))
 ```

### 2024-03-05 R/plotting_methods.R

@@ -12,8 +12,8 @@ rho_cat_colors <- function() {
 stab_color <- function() {
   c(
     "Community stability" = "black", #"#ffffbf"
-    "Asynchrony" = setNames(rho_cat_colors()["High"], NULL),
-    "Population stability" = setNames(rho_cat_colors()["Low"], NULL)
+    "Asynchrony" = "#44AA99",
+    "Population stability" = "#E1BE6A"
   )
 }
 
@@ -26,9 +26,8 @@ stab_alpha <- function () {
 }
 
 sem_tot_predictor <- function () {
-c("richness", "avg_int_strength", "w_avg_tlvl", "ct_alive", "Z", "h",
-  "resp_div", "env_stoch")
-
+  c("resp_div", "ct_alive", "w_avg_tlvl", "avg_int_strength", "richness",
+    "env_stoch")
 }
 
 resp_div_cat_colors <- function() {

### 2024-03-05 R/string_replacements.R

@@ -101,7 +101,9 @@ sim_type_replacement <- function() {
   c(
     "no_rerun" = "Default (5000 timesteps)",
     "rerun" = "Until no extinction",
-    "non_allo_no_rerun" = "Fixed death rate"
+    "non_allo_no_rerun" = "Fixed death rate",
+    "no_rerun_short" = "2000 timesteps",
+    "no_rerun_no_disconnected" = "Disconnected species not removed"
   )
 
 }

### 2024-03-07 _targets.Rmd
Option to remove or kill disconnected species + fix h

@@
   tar_target(sim_fw, readRDS(sim_files)),
+  tar_target(sem_simplified_file, here::here("data", paste0("sem_simplified_", names)), format = "file"),
+  tar_target(sem_simplified, { readRDS(sem_simplified_file) }),
   tar_target(sem_simplified_eff_file, here::here("data", paste0("sem_simplified_eff_", names)), format = "file"),
@@
 tar_load(sim_fw)
-ti <- sim_fw %>%
-  mutate(across(c(stab_com, richness), log)) %>%
-  mutate(across(c(sim_id, fw_id), as.factor)) %>%
-  mutate(
-    across(c(stab_com, richness,
-        env_stoch, resp_div, Z,
-        ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
-      ~scale(.x)[, 1])
-  )
-tar_load(stab_com_part_var)
-tu <- map(stab_com_part_var,
-  ~glmmTMB(formula_stab_fw_model(
-      resp = .x,
-      rand_effect = TRUE,
-      term_to_del = "richness : resp_div : Z +"
-      ),
-    data = ti
+tar_load(c(sim_fw_no_rerun,
+    sim_fw_rerun,
+    sim_fw_no_rerun_short,
+    sim_fw_no_rerun_no_disconnected,
+    sim_fw_non_allo_no_rerun))
+tar_load(c(
+    sem_simplified_no_rerun,
+    sem_simplified_rerun,
+    sem_simplified_no_rerun_short,
+    sem_simplified_no_rerun_no_disconnected,
+    sem_simplified_non_allo_no_rerun
     ))
@@
 ```{r}
-```
-
-```{r}
 tar_load(sem_eff_tab)

### 2024-03-07 draft.jl

@@ -19,28 +19,6 @@ include("src/sim.jl")
 include("src/plot.jl")
 include("src/get_modules.jl")
 
-fw = FoodWeb(nichemodel, 10, C = .1, Z = 1)
-bioener = BioenergeticResponse(fw,
-                               h = 3,
-                               # Predator interference
-                               c = 0
-                              )
-p = ModelParameters(fw,
-                    functional_response = bioener,
-                    env_stoch = EnvStoch(.3))
-tmax = 500
-m = simulate(p, rand(richness(fw));
-         rho = 0,
-         dt = .1,
-         tmax = tmax
-        )
-
-species_persistence(m)
-
-pm = get_parameters(m)
-alive_species = trophic_structure(m, last = 1).alive_species
-check_disconnected_species(pm.network.A, alive_species)
-
 ti = [
  0 0 0 0;
  0 0 0 0;
@@ -48,7 +26,6 @@ ti = [
  0 1 0 0
 ]
 pu = check_disconnected_species(ti, [1, 2, 3, 4])
-
 
 bm = [1, 1, 3, 4]
 alive = [1, 3, 4]
@@ -64,23 +41,11 @@ bm_to_set_to_zero = 1:length(bm) .∉ [tu]
 bm[bm_to_set_to_zero] .= 0
 1:length(bm)
 
-idxs = alive_species
-ti = filter_model_parameters(p, idxs = alive_species)
-ti.environment.K
-
-coefficient_of_variation(m, last = 100)
-
-simulate(p, rand(richness(fw)), saveat = (0:1:tmax))
-
-m = (t = 0, b = 0)
-m[:t]
-dictionary = Dict(1 => 77, 2 => 66, 3 => 1)
-keys(dictionary)
-dictionary[:1]
 
 param = DataFrame(Arrow.Table("scripts/param_comb_ct_S_h_d3.arrow"))
 
-filter([:S, :sigma, :h] => (rich, s, h) -> rich == 40 && s == .6 && h == 2, param)
+param = filter([:S, :sigma, :h, :Z] => (rich, s, h, z) -> rich == 40 && s == .3 && h == 2 && z == 100,
+               param)
 
 #toy_param = param[[2, 30, 58, 362, 390, 742, 750, 766, 1082, 1098],:]
 toy_param = param[[1, 3, 4, 6, 7, 10, 11, 13, 14],:]
@@ -97,6 +62,39 @@ toy_param[!, :A] = map(x -> reshape_array(x), toy_param[!, :A])
[…]

### 2024-03-07 scripts/param_comb_ct_S_h_d_allometric2.jl

@@ -4,7 +4,7 @@ nrep = 5
 sigma = .1:.1:0.6#[0.1, 0.3, 0.6]#.1:.2:0.6
 Z = [1, 5, 10, 25, 50, 100]
 ρ = 0:.25:1
-h = 2.0:.25:3.0#[2.0, 3.0]
+h = 1.0:.25:2.0#[2.0, 3.0]
 S = [10, 20, 30, 40, 50]
 C = 0.02:.02:.32
 
@@ -26,7 +26,7 @@ param = map(p -> (;Dict(k => v for (k, v) in zip(names, p))...),
 
 fw_test = map(p -> try
                   FoodWeb(nichemodel, p.richness, C = p.connectance,
-                          Z = 100, tol_C = .02,
+                          Z = 100, tol_C = .05,
                           check_cycle = true,
                           check_disconnected = true)
               catch

### 2024-03-07 src/sim.jl

@@ -108,7 +108,7 @@ function sim_int_mat_check_disconnected(A;
         gc_thre = .02,
         return_sol = false,
         re_run = true,
-        keep_K_omega = false,
+        remove_disconnected = true,
         dt_rescue = 0.05,
         digits = nothing
     )
@@ -149,23 +149,37 @@ function sim_int_mat_check_disconnected(A;
             return m
             break
         end
+        # Retrieve network
         old_A = m.omega .> 0
         alive_species = m.alive_species
+        # Check
         disconnected_species = check_disconnected_species(old_A, alive_species)
         ti = length(disconnected_species) == 0
+        # Build the vector of biomasses
         biomass_vector = zeros(dim(old_A))
         biomass_vector[alive_species] = m.bm_sp
-        starting_bm = kill_disconnected_species(old_A;
-                                                alive_species = alive_species,
-                                                bm = biomass_vector)
-
-        @assert length(starting_bm) == dim(A)
-
+        killed_species = kill_disconnected_species(old_A;
+                                                    alive_species = alive_species,
+                                                    bm = biomass_vector)
         if ti == true
             println("all species connected: $ti, nb alive species: $(length(alive_species))")
             return m
             break
         end
+
+        # Rebuilding network or set disconnected species to 0
+        if remove_disconnected == true
+            A = remove_disconnected_species(old_A, alive_species)
+            mask = killed_species .!= 0
+            starting_bm = biomass_vector[mask]
+            println("Rebuilding model without disconnected species.")
+        else
+            starting_bm = killed_species
+            A = A
+            println("Rebuilding model with disconnected species having a biomass of 0.")
+        end
+
+        @assert length(starting_bm) == dim(A)
         i = i + 1
     end
     m
@@ -554,6 +568,20 @@ kill_disconnected_species(ti, alive_species = [], bm = bm) == [0, 0, 0, 0]
 kill_disconnected_species(ti, alive_species = [1, 3, 4], bm = bm) == [1, 0, 3, 0]
 kill_disconnected_species(ti, alive_species = [1, 2, 4], bm = bm) == [0, 1, 0, 4]
 kill_disconnected_species(ti, alive_species = [1, 2, 4], bm = bm) == [0, 1, 0, 4]
+
[…]

### 2024-04-02 _targets.Rmd
Begin to analyse interference simulations

@@
 options(tidyverse.quiet = TRUE)
-tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"))
+tar_option_set(
+  error = "null",
+  packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra")
+)
 # Load custom functions
@@
 map_tibble <- tibble::tibble(
-  names = c("no_rerun", "non_allo_no_rerun", "rerun", "no_rerun_short",
-  "no_rerun_no_disconnected")
+  names = c("csc_rerun", "csc_kno", "csc_non_allo", "csc_rebuild")
     )
@@
 Our first target borrows the `airquality` dataset built into base R.
-
-```{targets raw-data}
-list(
-  tar_target(sim_list, {
-    sim_files <- list.files(here("res", "simCSZenrich"))
-    map(sim_files,
-      function (x) {
-        open_dataset(here::here("res", "simCSZenrich", x),
-          format = "arrow") %>%
-        collect()
-      })
-}
-    ),
-  tar_target(simZ_prep,
-    map_dfr(sim_list,
-      function (x) {
-        x %>%
-          # Remove simulation that have failed to run
-          filter(!is.na(richness)) %>%
-          # Transform back interaction strength into matrices
-          mutate(across(where(is.list), as.list)) %>%
-          mutate(across(c(int_strength, max_int),
-              ~map2(.x, S,
-                function(y, rich) {
-                  matrix(y, nrow = rich)
-                }
-              )
-          )
-            ) %>%
-          # Get matrix of alive species
-          mutate(max_int_alive  = map2(max_int, bm_sp,
-              function(mat, bm) {
-                mask <- bm > 10^-6
-                mat[mask, mask, drop = FALSE]
-              }
-            )
-          )
-      }
-    )
-    ),
-  tar_target(simZ,
-    simZ_prep %>%
-      mutate(
-        persistence = richness / S,
-        async = 1 / sync,
-        stab_pop = 1 / avg_cv_sp,
-        ct_alive = map_dbl(max_int_alive,
-          ~ifelse(sum(.x) == 0, 0,
-            sum(.x > 0) / ((ncol(.x))^2))),
-        bm_sp_alive = map(bm_sp, ~.x[.x > 10^-6]),
-        tlvl_alive = map2(tlvl, bm_sp, ~.x[.y > 10^-6]),
-        max_tlvl_alive = map_dbl(tlvl_alive, max),
-        w_avg_tlvl_alive = map2_dbl(tlvl_alive, bm_sp_alive,
-          ~sum(.x * (.y / sum(.y)))
-          ),
-        max_max_int_alive = map_dbl(max_int_alive,
-          ~ifelse(length(.x[.x > 0]) == 0, 0, max(.x[.x > 0]))
-          ),
-        avg_max_int_alive = map_dbl(max_int_alive,
-          ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
-          ),
-        sd_max_int_alive = map_dbl(max_int_alive,
-          ~ifelse(length(.x[.x > 0]) <= 1, 0, sd(.x[.x > 0]))
-          ),
-        cv_max_int_alive = sd_max_int_alive / avg_max_int_alive,
-        inv_sd_max_int_alive = 1 / sd_max_int_alive,
-        gini_max_int_alive = map_dbl(max_int_alive,
-          ~ifelse(length(.x[.x > 0]) == 0, 0, gini(.x[.x > 0])))
-      )
-  )
-)
-```
-
-```{targets sim_rho, tar_simple = TRUE}
-simZ %>%
-  filter(ct_alive != 0, avg_max_int_alive != 0) %>%
-  mutate(across(c(async, sync, stab_pop, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
-  mutate(
-    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
-    productivity_f = factor(productivity)
-    ) %>%
-  select(c(
-      ct_alive, log_richness, max_tlvl_alive, Z, rho,
-      gini_max_int, avg_max_int_alive, log1_avg_max_int_alive, env_stoch,
-      log_stab_com, log_sync, log_async, log_stab_pop, log_avg_cv_sp, productivity, productivity_f,
-      persistence)
-  )
-```
-
-```{targets sim_rho_scaled, tar_simple = TRUE}
-sim_rho %>%
-  mutate(across(where(is.double), ~scale(.x)[,1]))
-```
-
-```{targets rho_model}
-list(
-  tar_target(formula_fixed_rho, formula_mod_rho_fixed_effect()),
-  tar_target(formula_rand_rho, "(1 | Z)"),
-  tar_target(mod_rho, map(setNames(
-    c("log_stab_com", "log_stab_pop", "log_async"),
-    c("log_stab_com", "log_stab_pop", "log_async")
-    ),
-  function (x) {
-    glmmTMB(formula(paste0(x, " ~ ", formula_fixed_rho, " + ", formula_rand_rho)),
-      sim_rho)
-  }
-  )),
-  tar_target(coef_mod_rho, map_dfr(mod_rho, ~model2tibble(.x))),
-  tar_target(r2_mod_rho, map_dfr(mod_rho, ~as.data.frame(r2_nakagawa(.x)), .id = "response") %>%
-  mutate(response = var_replacement()[response])),
-  tar_target(p_mod_rho, plot_effect_type(coef_mod_rho)),
-  tar_target(mod_rho_scaled, map(setNames(
-    c("log_stab_com", "log_stab_pop", "log_async"),
-    c("log_stab_com", "log_stab_pop", "log_async")
-    ),
-  function (x) {
-    glmmTMB(formula(paste0(x, " ~ ", formula_fixed_rho, " + ", formula_rand_rho)),
-      sim_rho_scaled)
-  }
-)
-    ),
-  tar_target(coef_mod_rho_scaled, map_dfr(mod_rho_scaled, ~model2tibble(.x))),
-  tar_target(r2_mod_rho_scaled,
-    map_dfr(mod_rho_scaled, ~as.data.frame(r2_nakagawa(.x)), .id = "response") %>%
-      mutate(response = var_replacement()[response])),
-  tar_target(colin_rho, performance::check_collinearity(lm(formula(str_replace_all(paste0("log_stab_com ~ ", formula_fixed_rho), "(\\*|:)", "+")),
-  sim_rho_scaled))),
-    tar_target(p_mod_rho_scaled, plot_effect_type(coef_mod_rho_scaled))
-)
-```
-
-```{targets pred_rho}
-tar_target(pred_rho,
-  {
-  pred_rho <- list(
-    log_richness = c(log(1), log(5), log(10), log(20), log(30), log(50)),
-    ct_alive = c(.05, .10, .40),
-    rho = c(0, .5, 1),
-    log1_avg_max_int_alive = c(log(0.2 + 1), round(log(.81 + 1), 1), round(log(5.65 + 1), 1)),
-    env_stoch = .5,
-    productivity = c("basic", "enrichment"),
-    Z = 100
-    ) %>% expand.grid() %>%
-  filter(
-    !(log1_avg_max_int_alive == 0 & ct_alive != 0 | ct_alive == 0 & log1_avg_max_int_alive != 0)
-  )
-  pred_rho$log_stab_com <- predict(mod_rho[["log_stab_com"]], newdata = pred_rho)
-  pred_rho
-  }
-)
-```
-
-# New simulation
-
-```{targets raw_sim}
-list(
-  tar_target(sim_fw, sim_fw_rerun),
-  tar_target(sim_param, readRDS(here::here("data", "sim_param_d2"))),
-  tar_target(sim_fw_df, as.data.frame(sim_fw))
-  )
-```
 
@@
 list(
+  tar_target(sim_fw, sim_fw_csc_rerun),
   tar_target(sim_fw_sem,
-    sim_fw_df %>%
+    sim_fw %>%
+      as.data.frame() %>%
       mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
@@
     ),
-  tar_target(sem_model_list,
-    list(
-      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
-      richness = lm(richness ~ ct + S, sim_fw_sem),
-      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
-      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
-      avg_omnivory = lm(avg_omnivory ~ ct + S, sim_fw_sem),
-      avg_int_strength = lm(avg_int_strength ~ ct + S + h + Z, sim_fw_sem),
-      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h + Z, sim_fw_sem),
-      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
-      sae_even = lm(sae_even ~ richness, sim_fw_sem),
-      cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
-      cpe_env = lm(cpe_env ~ richness + resp_div, sim_fw_sem),
-      async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_sem),
-      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
-    )
-    ),
-  tar_target(sem, {
-    ti <- as.psem(sem_model_list)
-    update(ti, avg_omnivory %~~% w_avg_tlvl)
-    }
-    ),
-  tar_target(sem_coeff, {
-    ti <- summary(sem)$coefficients[, c(1, 2, 8, 9)]
-    colnames(ti)[4] <- "Signif"
-    ti #%>%
-    #filter(abs(Std.Estimate) > 0.1)# %>%
-    #  mutate(
-    #    Response = var_replacement()[Response],
-    #    Predictor = var_replacement()[Predictor]
-    #  ) %>%
-    }),
-  tar_target(sim_eff_file, here::here("data", "sem_eff"), format = "file"),
-  tar_target(sem_eff, {
-    readRDS(sim_eff_file)
-    #semEff(sem, ci.type = "perc", R = 10, seed = 13, parallel = "no", data = sim_fw_sem)
-    }
-    ),
-  tar_target(sem_eff_tab, from_semEff_to_table(sem_eff)),
+  tar_target(sem_eff,  sem_main_text_eff_csc_rerun),
+  tar_target(sem_eff_tab, sem_main_text_eff_tab_csc_rerun),
+  tar_target(sem_eff_coeff, sem_main_text_eff_tab_csc_rerun),
   tar_target(tab_sem_coeff,
-    sem_coeff %>%
+    sem_main_text_coeff_csc_rerun %>%
       kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
@@
     ),
-  tar_target(sem_collinearity,
-    map_dfr(setNames(sem_model_list, names(sem_model_list)),
-      performance::check_collinearity,
-      .id = "response") %>%
-    as_tibble),
-  tar_target(sem_rsquared,
-    map_dfr(sem_model_list, rsquared) %>%
-      mutate(Response = var_replacement()[Response]) %>%
-      select(Response, R.squared)
-    ),
+  tar_target(sem_collinearity, sem_main_text_collinearity_csc_rerun),
+  tar_target(sem_rsquared, sem_main_text_rsquared_csc_rerun),
   tar_target(tab_sem_vif,
@@
 )
+```
+
+```{r, eval = FALSE}
+library(targets)
+tar_load_globals()
+tar_load(starts_with("sim_fw_csc"))
+sim_fw_csc_rerun
+sim_fw_csc_rebuild
+sim_fw_csc_kno
+sim_fw_csc_non_allo
+sim_fw_csc_non_allo
 ```
@@
   tar_target(sem_simplified_rsquared, { readRDS(sem_simplified_rsquared_file) }),
-  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
-)
-```
-
-```{targets group-all-analysis}
+  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff)),
+  tar_target(sem_main_text_file, here::here("data", paste0("sem_main_text_", names)), format = "file"),
+  tar_target(sem_main_text, { readRDS(sem_main_text_file) }),
+  tar_target(sem_main_text_eff_file, here::here("data", paste0("sem_main_text_eff_", names)), format = "file"),
+  tar_target(sem_main_text_eff, { readRDS(sem_main_text_eff_file) }),
+  tar_target(sem_main_text_collinearity_file, here::here("data", paste0("sem_main_text_collinearity_", names)), format = "file"),
+  tar_target(sem_main_text_collinearity, { readRDS(sem_main_text_collinearity_file) }),
+  tar_target(sem_main_text_rsquared_file, here::here("data", paste0("sem_main_text_rsquared_", names)), format = "file"),
+  tar_target(sem_main_text_rsquared, { readRDS(sem_main_text_rsquared_file) }),
+  tar_target(sem_main_text_coeff_file, here::here("data", paste0("sem_main_text_coeff_", names)), format = "file"),
+  tar_target(sem_main_text_coeff, { readRDS(sem_main_text_coeff_file) }),
+  tar_target(sem_main_text_eff_tab, from_semEff_to_table(sem_main_text_eff))
+)
+```
+
+```{targets group-all-analysis, eval = FALSE}
 list(
-  tar_target(sem_simplified_tot,
+  tar_target(sem_main_text_tot,
     tibble(
       sim_type = c(
-        "no_rerun",
-        "non_allo_no_rerun",
         "rerun",
+        "non_allo",
+        "rebuild",
         "no_rerun_short",
-        "no_rerun_no_disconnected"),
+        "kno"),
       eff = list(
-        sem_simplified_eff_tab_no_rerun,
-        sem_simplified_eff_tab_non_allo_no_rerun,
-        sem_simplified_eff_tab_rerun,
-        sem_simplified_eff_tab_no_rerun_short,
-        sem_simplified_eff_tab_no_rerun_no_disconnected
+        sem_main_text_eff_tab_csc_rerun,
+        sem_main_text_eff_tab_csc_non_allo,
+        sem_main_text_eff_tab_csc_rebuild,
+        sem_main_text_eff_tab_csc_kno
         ),
       rsq = list(
-        sem_simplified_rsquared_no_rerun,
-        sem_simplified_rsquared_non_allo_no_rerun,
-        sem_simplified_rsquared_rerun,
-        sem_simplified_rsquared_no_rerun_short,
-        sem_simplified_rsquared_no_rerun_no_disconnected
+        sem_main_text_rquared_csc_rerun,
+        sem_main_text_rquared_csc_non_allo,
+        sem_main_text_rquared_csc_rebuild,
+        sem_main_text_rquared_csc_kno
         ),
       collinearity = list(
-        sem_simplified_collinearity_no_rerun,
-        sem_simplified_collinearity_non_allo_no_rerun,
-        sem_simplified_collinearity_rerun,
-        sem_simplified_collinearity_no_rerun_short,
-        sem_simplified_collinearity_no_rerun_no_disconnected
-        ),
-    )
-  ),
-  tar_target(sem_simplified_eff_tab_tot,
-    sem_simplified_tot %>%
+        sem_main_text_collinearity_csc_rerun,
+        sem_main_text_collinearity_csc_non_allo,
+        sem_main_text_collinearity_csc_rebuild,
+        sem_main_text_collinearity_csc_kno
+        ),
+    )
+  ),
+  tar_target(sem_main_text_eff_tab_tot,
+    sem_main_text_tot %>%
       select(sim_type, eff) %>%
       unnest(cols = eff)),
-  tar_target(p_sem_simplified_eff_tab_tot,
-    sem_simplified_eff_tab_tot %>%
+  tar_target(p_sem_main_text_eff_tab_tot,
+    sem_main_text_eff_tab_tot %>%
       filter(effect_type == "total") %>%
@@
 list(
-  tar_target(sem_simplified_model_list,
-    list(
-      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
-      richness = lm(richness ~ ct + S, sim_fw_sem),
-      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
-      avg_omnivory = lm(avg_omnivory ~ ct + S + Z, sim_fw_sem),
-      avg_int_strength = lm(avg_int_strength ~ ct + S + Z, sim_fw_sem),
-      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_sem),
-      #sae_even = lm(sae_even ~ richness, sim_fw_sem),
-      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_sem),
+  tar_target(sem_simplified_eff_tab, sem_simplified_eff_tab_csc_rerun),
+  tar_target(sem_main_text_eff_tab, sem_main_text_eff_tab_csc_rerun)
+)
+```
+
+```{r, eval = FALSE}
+tar_load(sem_main_text)
+tar_load(sim_fw_sem)
+
+m <- list(
+  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + c + Z, sim_fw_sem),
+  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + c + Z, sim_fw_sem),
   sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
-      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + resp_div, sim_fw_sem),
+  cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z, sim_fw_sem),
   async = lm(async ~ sae_total + cpe, sim_fw_sem),
@@
 )
-    ),
-  tar_target(sem_simplified, {
-    ti <- as.psem(sem_simplified_model_list)
-    update(ti, avg_omnivory %~~% w_avg_tlvl)
-    }
-    ),
-  tar_target(sem_main_text_model_list,
-    list(
-      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch, sim_fw_sem),
-      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive, sim_fw_sem),
+
+m2 <- list(
+  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + c + Z + resp_div, sim_fw_sem),
+  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + c + Z + env_stoch + resp_div, sim_fw_sem),
   sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
-      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div, sim_fw_sem),
+  cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z + env_stoch, sim_fw_sem),
   async = lm(async ~ sae_total + cpe, sim_fw_sem),
@@
 )
-  ),
-  tar_target(sem_main_text, {
-    ti <- as.psem(sem_main_text_model_list)
+
+ti <- as.psem(m)
+ti2 <- as.psem(m2)
 #update(ti, avg_omnivory %~~% w_avg_tlvl)
-    }
-    ),
-  tar_target(sem_simplified_collinearity,
-    sem_simplified_collinearity_no_rerun
-    ),
-  tar_target(sem_simplified_rsquared,
-    sem_simplified_rsquared_no_rerun %>%
-      mutate(
-      Response = var_replacement()[Response],
-      R.squared = round(R.squared, 2)
-      ) %>%
-      select(Response, R.squared)
-    ),
-  tar_target(tab_sem_simplified_vif,
-    sem_simplified_collinearity %>%
-      mutate(
-        response = var_replacement()[response],
-        Term = var_replacement()[Term],
-        VIF = round(VIF, 2),
-        SE_factor = round(SE_factor, 2)
-        ) %>%
-        rename(Response = response)
-    ),
-  tar_target(tab_sem_simplified_rsquared,
-    sem_simplified_rsquared %>%
-      kable(caption = "Rsquared for the Structural Equation Model.") %>%
-      kable_styling()
-  ),
-  tar_target(sem_simplified_eff_tab, sem_simplified_eff_tab_no_rerun)
-)
-```
-
-```{r, eval = FALSE}
-tar_load(sem_main_text)
-m <- list(
-  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch, sim_fw_sem),
-  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive, sim_fw_sem),
+summary(ti)
+summary(ti2)
+tar_load(sim_fw_sem)
+
+m3 <- list(
+  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + c + Z + resp_div, sim_fw_sem),
+  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + c + Z + env_stoch + resp_div, sim_fw_sem),
   sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
-  cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div, sim_fw_sem),
+  cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z + env_stoch, sim_fw_sem),
+  cpe_env = lm(cpe_env ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z + env_stoch, sim_fw_sem),
+  #cpe = lm(cpe ~ cpe_env + cpe_int, sim_fw_sem),
   async = lm(async ~ sae_total + cpe, sim_fw_sem),
@@
 )
-ti <- as.psem(m)
-update(ti, avg_omnivory %~~% w_avg_tlvl)
-summary(ti)
+summary(as.psem(m3))
+
 ```
@@
 list(
-  tar_target(model_fw_stab,
-    glmmTMB(formula_stab_fw_model(
-        rand_effect = TRUE,
-        term_to_del = "richness : resp_div : Z +"),
-      data = mutate(sim_fw, across(c(stab_com, richness), log))
-      )),
   tar_target(stab_com_part_var, c("stab_com", "pop_stab", "async")),
@@
   ),
-  tar_target(model_fw_stab_scaled,
-    glmmTMB(formula_stab_fw_model(
-        rand_effect = TRUE,
-        term_to_del = "richness : resp_div : Z +"
-        ),
-      data = sim_fw %>%
-        mutate(across(c(stab_com, richness), log)) %>%
-        mutate(across(c(sim_id, fw_id), as.factor)) %>%
-        mutate(
-          across(c(stab_com, richness,
-              env_stoch, resp_div, Z,
-              ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
-            ~scale(.x)[, 1])
-        )
-        )
-    ),
   tar_target(model_fw_stab_comp_scaled,
@@
       data = sim_fw %>%
-        mutate(across(c(stab_com, richness), log)) %>%
+        mutate(across(c(stab_com, richness, pop_stab, async), log)) %>%
         mutate(across(c(sim_id, fw_id), as.factor)) %>%
@@
           across(c(stab_com, pop_stab, async, richness,
-              env_stoch, resp_div, Z, h,
+              env_stoch, resp_div, Z, c,
               ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
@@
   ),
-  tar_target(model_fw_stab_scaled_coeff,
-    confint(tar_read(model_fw_stab_scaled), level = 0.95) %>%
-      as.data.frame() %>%
-      rownames_to_column("term") %>%
-      as_tibble() %>%
-      mutate(term = str_replace(term, "cond\\.", ""))
-    ),
-  tar_target(pred_data, {
-    to <- list(
-      richness = log(seq(1, 30, 1)),
-      ct_alive = c(.05, .10, .30),
-      resp_div = 1 - c(0, .75, 1),
-      avg_int_strength = c(.01, .02, .05, .1),
-      env_stoch = c(.1, .6),
-      w_avg_tlvl = c(1.0, 1.5, 2.3),
-      Z = c(1, 10, 100),
-      h = c(2, 3),
-      fw_id = NA) %>% expand.grid()
-    ti <- predict(model_fw_stab,
-      se.fit = TRUE, re.form = NA,
-      newdata = to)
-    to$stab_com <- ti$fit
-    to$stab_com_se <- ti$se.fit
-    to
-    }),
-  tar_target(fixed_effect_fw_stab, fixef(model_fw_stab)$cond),
   tar_target(fixed_effect_fw_stab_comp,
@@
   ),
-  tar_target(pred_sr_resp_div_int,
-    list(
-      resp_div = seq(0, 1, length.out = 50),
-      avg_int_strength = seq(0.01, 0.2, length.out = 50)
-      ) %>%
-    expand.grid() %>%
-    mutate(
-      slope_richness = map2_dbl(resp_div, avg_int_strength,
-        ~get_slope_change(
-          coeff = fixed_effect_fw_stab,
-          gen_term = "richness",
-          coeff_values = c(
-            "resp_div" = .x,
-            "env_stoch" = .1,
-            "ct_alive" = .2,
-            "avg_int_strength" = .y,
-            "h" = 2,
-            "w_avg_tlvl" = 1.5,
-            "Z" = 100))))),
-  tar_target(pred_sr_resp_div_tlvl,
-    list(
-      resp_div = seq(0, 1, length.out = 50),
-      w_avg_tlvl = seq(1.0, 2.5, length.out = 50)
-      ) %>%
-    expand.grid() %>%
-    mutate(
-      slope_richness = map2_dbl(resp_div, w_avg_tlvl,
-        ~get_slope_change(
-          coeff = fixed_effect_fw_stab,
-          gen_term = "richness",
-          coeff_values = c(
-            "resp_div" = .x,
-            "env_stoch" = .1,
-            "ct_alive" = .2,
-            "avg_int_strength" = .01,
-            "h" = 2,
-            "w_avg_tlvl" = .y,
-            "Z" = 100))))),
-  tar_target(pred_sr_resp_div_ct,
-    list(
-      resp_div = seq(0, 1, length.out = 50),
-      ct_alive = seq(.02, .3, length.out = 50)
-      ) %>%
-    expand.grid() %>%
-    mutate(
-      slope_richness = map2_dbl(resp_div, ct_alive,
-        ~get_slope_change(
-          coeff = fixed_effect_fw_stab,
-          gen_term = "richness",
-          coeff_values = c(
-            "resp_div" = .x,
-            "env_stoch" = .3,
-            "ct_alive" = .y,
-            "avg_int_strength" = .01,
-            "h" = 2,
-            "w_avg_tlvl" = 2.0,
-            "Z" = 100))))),
-  tar_target(pred_sr_resp_div,
-    map_dfr(list(pred_sr_resp_div_int, pred_sr_resp_div_ct, pred_sr_resp_div_tlvl),
-      ~.x %>%
-        pivot_longer(2, names_to = "variable", values_to = "values")
-    )
-    ),
   tar_target(default_variable_values_pred,
     c(
-      "resp_div" = 0,
-      "env_stoch" = .3,
-      "ct_alive" = .05,
-      "avg_int_strength" = .01,
-      "h" = 2,
-      "w_avg_tlvl" = 1.0,
-      "Z" = 100
+      "resp_div" = mean(sim_fw$resp_div),
+      "env_stoch" = mean(sim_fw$env_stoch),
+      "ct_alive" = mean(sim_fw$ct_alive),
+      "avg_int_strength" = mean(sim_fw$avg_int_strength),
+      "c" = mean(sim_fw$c),
+      "w_avg_tlvl" = mean(sim_fw$w_avg_tlvl),
+      "Z" = mean(sim_fw$Z)
     )
@@
             values = list(
-              seq(0.01, 0.1, length.out = 50),
-              seq(1.0, 2.5, length.out = 50),
-              seq(.02, .35, length.out = 50)
+              seq(quantile(sim_fw$avg_int_strength)["25%"], quantile(sim_fw$avg_int_strength)["75%"], length.out = 50),
+              seq(quantile(sim_fw$w_avg_tlvl)["25%"], quantile(sim_fw$w_avg_tlvl)["75%"], length.out = 50),
+              seq(quantile(sim_fw$ct_alive)["25%"], quantile(sim_fw$ct_alive)["75%"], length.out = 50)
             )
@@
   )
+tar_read(sem_main_text_eff_rerun)
 ```
@@
   tar_target(p_sem_tot_stab,
-    sem_simplified_eff_tab_no_rerun %>%
+    sem_main_text_eff_tab_csc_rerun %>%
       filter(effect_type == "total") %>%
@@
   )
-
+  ),
+  tar_target(p_sem_tot_stab_file,
+    ggsave_multiple(
+  paste0("p_sem_tot_stab", c(".png", ".pdf")),
+  plot = print(
+    p_sem_tot_stab +
+      guides(
+        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
+      ) +
+      theme(
+        legend.title = element_blank(),
+        legend.position = c(.005, .995),
+        legend.justification = c("left", "top"),
+
+      )
+    ),
+  path = here::here("report", "figures"),
+  scale = 2.4,
+  dpi = 400,
+  width = 80,
+  height = 80 * .4,
+  units = "mm"),
+  format = "file")
+)
+```
+
+```{targets plot-repro}
+list(
+  tar_target(p_pred_sr_resp_div,
+    pred_stab_comp_resp_div %>%
+      filter(response == "stab_com") %>%
+      mutate(
+        variable = var_replacement()[variable]
+        ) %>%
+      ggplot(aes(x = resp_div, y = variable_values, fill = slope)) +
+      geom_raster() +
+      facet_wrap(~variable, scales = "free_y") +
+      coord_cartesian(expand = FALSE) +
+      scale_fill_gradient2(
+        low = resp_div_cat_colors()["Low"],
+        mid = "white",
+        high = resp_div_cat_colors()["High"],
+        midpoint = 0,
+        space = "Lab",
+        na.value = "grey50",
+        guide = "colourbar",
+        aesthetics = "fill") +
+      labs(
+        x = var_replacement()["resp_div"],
+        y = "Food-web structure",
+        fill = "Slope community stability - Richness"
+        ) +
+      theme(
+        legend.position = "bottom",
+        legend.key.width = unit(2.5, "cm"),
+        plot.margin = margin(l = 10, r = 10, unit = "pt")
+      )
+    ),
+  tar_target(p_pred_sr_resp_div_file,
+    ggsave_multiple(
+      paste0("p_pred_sr_resp_div", c(".png", ".pdf")),
+      plot = p_pred_sr_resp_div,
+      path = here::here("report", "figures"),
+      scale = 2.2,
+      dpi = 400,
+      width = 120,
+      height = 120 * .45,
+      units = "mm"),
+    format = "file"),
+  tar_target(p_pred_sr_resp_div_supp,
+    pred_stab_comp_resp_div %>%
+      mutate(
+        variable = var_replacement()[variable],
+        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
+        ) %>%
+    ggplot(aes(x = resp_div, y = variable_values, fill = slope)) +
+    geom_raster() +
+    facet_grid(cols = vars(response), rows = vars(variable), scales = "free") +
+    coord_cartesian(expand = FALSE) +
+    scale_x_continuous(
+      breaks = c(0, .5, 1),
+      labels = c(0, 0.5, 1)
+      ) +
+    scale_fill_gradient2(
+      low = resp_div_cat_colors()["Low"],
+      mid = "white",
+      high = resp_div_cat_colors()["High"],
+      midpoint = 0,
+      space = "Lab",
+      na.value = "grey50",
+      guide = "colourbar",
+      aesthetics = "fill") +
+    labs(
+      x = var_replacement()["resp_div"],
+      y = "Food-web structure",
+      fill = "Slope stability - Richness"
+      ) +
+    theme(
+      legend.position = "bottom",
+      legend.key.width = unit(2.0, "cm"),
+      plot.margin = margin(l = 10, r = 10, unit = "pt")
+      )),
+  tar_target(p_pred_sr_resp_div_supp_file,
+    ggsave_multiple(
+      paste0("p_pred_sr_resp_div_supp", c(".png", ".pdf")),
+      plot = p_pred_sr_resp_div_supp,
+      path = here::here("report", "figures"),
+      scale = 2.4,
+      dpi = 400,
+      width = 80,
+      height = 80 * 1,
+      units = "mm"),
+    format = "file"
   )
@@
 
-```{targets partial_sem_relations}
+```{targets partial_sem_relations, eval = FALSE}
 list(
@@
       "pop_stab ~ w_avg_tlvl",
-      "pop_stab ~ h",
+      "pop_stab ~ c",
       "pop_stab ~ env_stoch",
@@
 sim_fw %>%
-  filter(env_stoch %in% c(.1, .6), rho %in% c(0, .75), h == 3, Z == 100) %>%
+  filter(env_stoch %in% c(.1, .6), rho %in% c(0, .75), c == 1, Z == 100) %>%
   ggplot(aes(x = log(richness), y = log(stab_com), color = as.factor(rho))) +
@@
       sae_even, evenness_sae,
-      cpe_int, cpe_env, stab_pop
+      cpe_int, cpe_env, pop_stab
       ), names_to = "async_decomp", values_to = "values") %>%
@@
           sae_even, evenness_sae,
-          cpe_int, cpe_env, stab_pop
+          cpe_int, cpe_env, pop_stab
           ), names_to = "async_decomp", values_to = "values") %>%
@@
   filter(Z == 100) %>%
-  ggplot(aes(x = as.factor(h), y = avg_int_strength)) +
+  ggplot(aes(x = as.factor(c), y = avg_int_strength)) +
   geom_boxplot() +
@@
         w_avg_tlvl,
-        Z, resp_div, env_stoch, h
+        Z, resp_div, env_stoch, c
         )) %>%
@@
 ```
+```{targets p_cor_file, tar_simple = TRUE, format = "file"}
+ggsave_multiple(
+  paste0("p_cor", c(".png", ".pdf")),
+  plot = p_cor,
+  path = here::here("report", "figures"),
+  scale = 3.4,
+  dpi = 400,
+  width = 80,
+  height = 80 * .9,
+  units = "mm")
+```
 
@@
 list(
+  tar_target(sim_param_file, here::here("data", "sim_param_csc_rerun"), format = "file"),
+  tar_target(sim_param, {readRDS(sim_param_file)}),
   tar_target(sim_param_tab,
@@
 ```{r, eval=FALSE}
-tar_load(sem_simplified_eff_tab_no_rerun_short)
-sem_simplified_eff_tab_rerun %>%
+#tar_load_globals()
+tar_load(sem_main_text_eff_tab)
+sem_main_text_eff_tab %>%
   filter(
     effect_type == "direct",
-    predictor %in% c(sem_tot_predictor(), "async", "stab_com", "sae_total", "cpe", "evenness_sae", "sae_even")
+    predictor %in% c(sem_tot_predictor(), "async", "stab_com", "pop_stab", "sae_total", "cpe", "evenness_sae", "sae_even")
     ) %>%
 select(response, predictor, effect) %>%
-filter(abs(effect) > .05) %>%
-mutate(effect = round(effect, 2))
+mutate(effect = round(effect, 2)) %>%
+filter(abs(effect) > .02)
+```
+
+```{r}
+tar_load(sem_main_text_collinearity_csc_rerun)
+sem_main_text_collinearity_csc_rerun %>%
+  select(response, Term, VIF) %>%
+  filter(VIF > 3)
+```
+
+```{r}
+tar_load(sim_fw_sem)
+ti <- lm(stab_com ~ richness + resp_div + env_stoch + ct_alive + w_avg_tlvl + Z +
+  avg_int_strength + c, data = sim_fw_sem)
+check_collinearity(ti)
+
+library(DHARMa)
+tar_load(model_fw_stab_comp)
+tu <- simulateResiduals(model_fw_stab_comp$model[[3]])
+plot(tu)
 ```
@@
 ```{r}
-ggsave_multiple(
-  paste0("p_sem_tot_stab", c(".png", ".pdf")),
-  plot = print(
-    tar_read(p_sem_tot_stab) +
-      guides(
-        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
-      ) +
-      theme(
-        legend.title = element_blank(),
-        legend.position = c(.005, .995),
-        legend.justification = c("left", "top"),
-
-      )
-    ),
-  path = here::here("report", "figures"),
-  scale = 2.4,
-  dpi = 400,
-  width = 80,
-  height = 80 * .4,
-  units = "mm")
 ```
@@
 sim_for_plot %>%
-  filter(env_stoch == !!stoch, h == hill, Z == 1, rho == env_corr) %>%
+  filter(env_stoch == !!stoch, c == hill, Z == 1, rho == env_corr) %>%
   arrange(fw_id)
 low_z_low_rich <- sim_for_plot %>%
-  filter(env_stoch == !!stoch, h == hill, Z == 1, rho == env_corr, richness == 10) %>%
+  filter(env_stoch == !!stoch, c == hill, Z == 1, rho == env_corr, richness == 10) %>%
   arrange(desc(max_tlvl), richness)
@@
 low_z_high_rich <- sim_for_plot %>%
-  filter(env_stoch == !!stoch, h == hill, Z == 1, rho == env_corr) %>%
+  filter(env_stoch == !!stoch, c == hill, Z == 1, rho == env_corr) %>%
   # For plotting purpose, not too much species
@@
 sim_for_plot %>%
-  filter(env_stoch == !!stoch, h == hill, Z == 100,
+  filter(env_stoch == !!stoch, c == hill, Z == 100,
     rho == env_corr, richness == 10) %>%
@@
 high_z_low_rich <- sim_for_plot %>%
-  filter(env_stoch == !!stoch, h == hill, Z == 100,
+  filter(env_stoch == !!stoch, c == hill, Z == 100,
     rho == env_corr, richness == 10) %>%
@@
 sim_for_plot %>%
-  filter(env_stoch == !!stoch, h == hill, Z == 100, rho == env_corr) %>%
+  filter(env_stoch == !!stoch, c == hill, Z == 100, rho == env_corr) %>%
   # For plotting purpose, not too much species
@@
 high_z_high_rich <- sim_for_plot %>%
-  filter(env_stoch == !!stoch, h == hill, Z == 100, rho == env_corr) %>%
+  filter(env_stoch == !!stoch, c == hill, Z == 100, rho == env_corr) %>%
   # For plotting purpose, not too much species
@@
 tar_read(sim_fw) %>%
-  filter(env_stoch == .6, S == 10, Z == 100) %>%
-  ggplot(aes(y = pop_stab, x = as.factor(resp_div), color = as.factor(h))) +
+  filter(env_stoch == .6, S == 40, Z == 100) %>%
+  ggplot(aes(y = pop_stab, x = as.factor(resp_div), color = as.factor(c))) +
   geom_boxplot()
@@
 ```{r}
+tar_load_globals()
 tar_load(pred_stab_comp_resp_div)
-```
-
-```{r}
-p_pred_sr_resp_div <- pred_stab_comp_resp_div %>%
-  filter(response == "stab_com") %>%
-  mutate(
-    variable = var_replacement()[variable]
-    ) %>%
-  ggplot(aes(x = resp_div, y = variable_values, fill = slope)) +
-  geom_raster() +
-  facet_wrap(~variable, scales = "free_y") +
-  coord_cartesian(expand = FALSE) +
-  scale_fill_gradient2(
-    low = resp_div_cat_colors()["Low"],
-    mid = "white",
-    high = resp_div_cat_colors()["High"],
-    midpoint = 0,
-    space = "Lab",
-    na.value = "grey50",
-    guide = "colourbar",
-    aesthetics = "fill") +
-  labs(
-    x = var_replacement()["resp_div"],
-    y = "Food-web structure",
-    fill = "Slope community stability - Richness"
-    ) +
-  theme(
-    legend.position = "bottom",
-    legend.key.width = unit(2.5, "cm"),
-    plot.margin = margin(l = 10, r = 10, unit = "pt")
-  )
-ggsave_multiple(
-  paste0("p_pred_sr_resp_div", c(".png", ".pdf")),
-  plot = p_pred_sr_resp_div,
-  path = here::here("report", "figures"),
-  scale = 2.2,
-  dpi = 400,
-  width = 120,
-  height = 120 * .45,
-  units = "mm")
-```
-
-```{r}
-p_pred_sr_resp_div_supp <- pred_stab_comp_resp_div %>%
-  mutate(
-    variable = var_replacement()[variable],
-    response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
-    ) %>%
-  ggplot(aes(x = resp_div, y = variable_values, fill = slope)) +
-  geom_raster() +
-  facet_grid(cols = vars(response), rows = vars(variable), scales = "free") +
-  coord_cartesian(expand = FALSE) +
-  scale_x_continuous(
-    breaks = c(0, .5, 1),
-    labels = c(0, 0.5, 1)
-    ) +
-  scale_fill_gradient2(
-    low = resp_div_cat_colors()["Low"],
-    mid = "white",
-    high = resp_div_cat_colors()["High"],
-    midpoint = 0,
-    space = "Lab",
-    na.value = "grey50",
-    guide = "colourbar",
-    aesthetics = "fill") +
-  labs(
-    x = var_replacement()["resp_div"],
-    y = "Food-web structure",
-    fill = "Slope stability - Richness"
-    ) +
-  theme(
-    legend.position = "bottom",
-    legend.key.width = unit(2.0, "cm"),
-    plot.margin = margin(l = 10, r = 10, unit = "pt")
-  )
-ggsave_multiple(
-  paste0("p_pred_sr_resp_div_supp", c(".png", ".pdf")),
-  plot = p_pred_sr_resp_div_supp,
-  path = here::here("report", "figures"),
-  scale = 2.4,
-  dpi = 400,
-  width = 80,
-  height = 80 * 1,
-  units = "mm")
 ```
@@
 ```{r}
-ggsave_multiple(
-  paste0("p_cor", c(".png", ".pdf")),
-  plot = tar_read(p_cor),
-  path = here::here("report", "figures"),
-  scale = 3.4,
-  dpi = 400,
-  width = 80,
-  height = 80 * .9,
-  units = "mm")
-```
-
-```{r}
 tar_load(c(sim_fw))
@@
   filter(env_stoch == .2) %>%
-  select(c(var_fw_struct, var_fw_emergent_struct, var_fw_flux, stab_pop)))
+  select(c(var_fw_struct, var_fw_emergent_struct, var_fw_flux, pop_stab)))
 ```
@@
     ) %>%
-  ggplot(aes(y = stab_pop, x = as.factor(Z))) +
+  ggplot(aes(y = pop_stab, x = as.factor(Z))) +
   geom_boxplot()
@@
 
-```{r, eval = FALSE}
-tar_load(c(sim_fw_sem, sim_fw))
-mod_tot_scaled <- lm(stab_com ~
-  richness + rho + env_stoch +
-  ct_alive + avg_int_strength + w_avg_tlvl +
-  richness : rho +
-  richness : env_stoch +
-  richness : ct_alive +
-  richness : avg_int_strength +
-  richness : w_avg_tlvl +
-  richness : rho : ct_alive +
-  richness : rho : w_avg_tlvl +
-  richness : rho : avg_int_strength +
-  richness : env_stoch : ct_alive +
-  richness : env_stoch : w_avg_tlvl +
-  richness : env_stoch : avg_int_strength,
-sim_fw_sem %>%
-  mutate(across(c("stab_com", "richness", "productivity", "rho", "env_stoch", "ct_alive", "avg_int_strength", "avg_omnivory", "w_avg_tlvl"), scale))
-
-  )
-summary(sim_fw$stab_com)
-summary(sim_fw$avg_int_strength)
-summary(sim_fw$w_avg_tlvl)
-summary(sim_fw$avg_omnivory)
-
-mod_tot <- lm(stab_com ~
-  richness  + rho + env_stoch +
-  ct_alive + w_avg_tlvl + Z +
-  avg_int_strength +
-  h +
-  richness * rho +
-  richness * env_stoch +
-  richness * ct_alive +
-  richness * avg_int_strength +
-  richness * h +
-  richness * w_avg_tlvl +
-  richness * Z +
-  richness * rho * ct_alive +
-  richness * rho * w_avg_tlvl +
-  richness * rho * avg_int_strength +
-  richness * rho * h +
-  richness * rho * Z +
-  richness * env_stoch * ct_alive +
-  richness * env_stoch * Z +
-  richness * env_stoch * avg_int_strength+
-  richness * env_stoch * h +
-  richness * env_stoch * w_avg_tlvl,
-  mutate(sim_fw, across(c(stab_com, richness), log)) #, richness
-  )
-mod_tot_async <- lm(async ~
-  richness  + rho + env_stoch +
-  ct_alive + w_avg_tlvl + Z +
-  avg_int_strength +
-  h +
-  richness * rho +
-  richness * env_stoch +
-  richness * ct_alive +
-  richness * avg_int_strength +
-  richness * h +
-  richness * w_avg_tlvl +
-  richness * Z +
-  richness * rho * ct_alive +
-  richness * rho * w_avg_tlvl +
-  richness * rho * avg_int_strength +
-  richness * rho * h +
-  richness * rho * Z +
-  richness * env_stoch * ct_alive +
-  richness * env_stoch * Z +
-  richness * env_stoch * avg_int_strength+
-  richness * env_stoch * h +
-  richness * env_stoch * w_avg_tlvl,
-  mutate(sim_fw, across(c(async, richness), log)) #, richness
-  )
-mod_tot_pop_stab <- lm(pop_stab ~
-  richness  + rho + env_stoch +
-  ct_alive + w_avg_tlvl + Z +
-  avg_int_strength +
-  h +
-  richness * rho +
-  richness * env_stoch +
-  richness * ct_alive +
-  richness * avg_int_strength +
-  richness * h +
-  richness * w_avg_tlvl +
-  richness * Z +
-  richness * rho * ct_alive +
-  richness * rho * w_avg_tlvl +
-  richness * rho * avg_int_strength +
-  richness * rho * h +
-  richness * rho * Z +
-  richness * env_stoch * ct_alive +
-  richness * env_stoch * Z +
-  richness * env_stoch * avg_int_strength+
-  richness * env_stoch * h +
-  richness * env_stoch * w_avg_tlvl,
-  mutate(sim_fw, across(c(pop_stab, richness), log)) #, richness
-  )
-check_collinearity(lm(stab_com ~ richness + rho +
-    env_stoch + avg_int_strength +
-  ct_alive + w_avg_tlvl + Z + h, sim_fw))
-plot(mod_tot)
-
-pred_data <- list(
-  richness = log(seq(1, 30, 1)),
-  ct_alive = c(.05, .10, .30),
-  rho = c(0, .75, 1),
-  avg_int_strength = c(.01, .02, .05, .1),
-  env_stoch = c(.1, .6),
-  w_avg_tlvl = c(1.5, 2, 3),
-  Z = c(10, 100),
-  h = c(2, 3)
-  ) %>% expand.grid()
-pred_data$stab_com <- predict(mod_tot, newdata = pred_data)
-pred_data$async <- predict(mod_tot_async, newdata = pred_data)
-pred_data$pop_stab <- predict(mod_tot_pop_stab, newdata = pred_data)
-pred_data$resp_div <- rho_replacement()[as.character(pred_data$rho)]
-```
-
-```{r, eval = FALSE}
-p_pred_sr_int <- pred_data %>%
-  filter(
-    ct_alive %in% c(.1),
-    rho %in% c(0, .75),
-    richness >= 1,
-    Z == 10,
-    h %in% c(3),
-    avg_int_strength %in% c(.01, .1),
-    w_avg_tlvl == 1.5
-    ) %>%
-  ggplot(aes(
-      x = richness, y = stab_com,
-      color = as.factor(resp_div),
-      linetype = as.factor(avg_int_strength),
-      alpha = as.factor(avg_int_strength)
-      )) +
-  ylim(2, 8) +
-  geom_line(linewidth = 1) +
-   scale_alpha_manual(values=c(1, 0), guide = "none") +
-  facet_grid(cols = vars(env_stoch), labeller = label_both) +
-  labs(
-    x = "Species richness (Log)", y = "Community stability (Log)",
-    linetype = "Avg. Interaction strength",
-    color = "Response diversity"
-  ) +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-```{r, eval = FALSE}
-p_pred_sr_int1 <- pred_data %>%
-  filter(
-    ct_alive %in% c(.1),
-    rho %in% c(0, .75),
-    Z == 10,
-    h %in% c(3),
-    avg_int_strength %in% c(.01, .1),
-    w_avg_tlvl == 1.5
-    ) %>%
-  ggplot(aes(
-      x = richness, y = stab_com,
-      color = as.factor(resp_div),
-      linetype = as.factor(avg_int_strength),
-      alpha = as.factor(avg_int_strength)
-      )) +
-  geom_line(linewidth = 1) +
-   scale_alpha_manual(values=c(1, 0), guide = "none") +
-  facet_grid(cols = vars(env_stoch), labeller = label_both) +
-  labs(
-    x = "Species richness (Log)", y = "Community stability (Log)",
-    linetype = "Avg. Interaction strength",
-    color = "Response diversity"
-  ) +
-  theme_bw() +
-  theme(legend.position = "bottom")
-p_pred_sr_int2 <- p_pred_sr_int1 +
-   scale_alpha_manual(values=c(1, 1), guide = "none")
-ggsave(
-  here("report", "figures", "p_pred_sr_int1.png"),
-  plot = p_pred_sr_int1,
-  scale = 2.4,
-  width = 88,
-  height = 88 * .5,
-  units = "mm"
-)
-ggsave(
-  here("report", "figures", "p_pred_sr_int2.png"),
-  plot = p_pred_sr_int2,
-  scale = 2.4,
-  width = 88,
-  height = 88 * .5,
-  units = "mm"
-)
-```
-
-```{r}
-pred_data_show <- pred_data %>%
-  filter(
-    ct_alive %in% c(.3),
-    rho %in% c(0, .75),
-    Z == 100,
-    h %in% c(3),
-    avg_int_strength %in% c(.01, .1),
-    w_avg_tlvl == 1.5
-    )
-
-sim_fw %>%
-  filter(env_stoch %in% c(.1, .6), rho %in% c(0, .75), h == 3, Z == 100) %>%
-  ggplot(aes(x = log(richness), y = log(stab_com), color = as.factor(rho))) +
-  geom_point(alpha = .3) +
-  geom_line(data = pred_data_show,
-    aes(x = richness, y = stab_com,
-      color = as.factor(rho),
-      linetype = as.factor(avg_int_strength),
-      alpha = as.factor(avg_int_strength))
-    ) +
-  scale_alpha_manual(values=c(1, 0), guide = "none") +
-  facet_grid(cols = vars(env_stoch), labeller = label_both) +
-  labs(
-    x = "Species richness (Log)", y = "Community stability (Log)",
-    color = "Environmental correlation"
-  ) +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-```{r}
-leg_pred <- get_legend(p_pred_sr_int)
-p_sim_pred <- plot_grid(
-  plot_grid(
-    tar_read(p_stab_rich_env_rho) + theme(legend.position = "none"),
-    p_pred_sr_int + theme(legend.position = "none"),
-  labels = "auto"
-  ),
-  leg_pred,
-  nrow = 2,
-  rel_heights = c(1, .1)
-)
-ggsave(
-  here("report", "figures", "p_sim_pred.pdf"),
-  plot = p_sim_pred,
-  scale = 2.4,
-  width = 88,
-  height = 88 * .4,
-  units = "mm"
-)
-```
-
-```{r}
-p_pred_sr_int_async <- pred_data %>%
-  filter(
-    ct_alive %in% c(.1),
-    rho %in% c(0, .75),
-    Z == 10,
-    h %in% c(3),
-    avg_int_strength %in% c(.01, .1),
-    w_avg_tlvl == 1.5
-    ) %>%
-  ggplot(aes(
-      x = richness, y = async,
-      color = as.factor(rho),
-      linetype = as.factor(avg_int_strength),
-      )) +
-  geom_line(linewidth = 1) +
-  facet_grid(cols = vars(env_stoch), labeller = label_both) +
-  labs(
-    x = "Species richness (Log)", y = "Asynchrony (Log)",
-    linetype = "Avg. Interaction strength",
-    color = "Environmental correlation"
-  ) +
-  theme_bw() +
-  theme(legend.position = "bottom")
-ggsave(
-  here("report", "figures", "p_pred_sr_int_async.png"),
-  plot = p_pred_sr_int_async,
-  scale = 2.4,
-  width = 88,
-  height = 88 * .5,
-  units = "mm"
-)
-```
-
-```{r}
-p_pred_sr_int_pop_stab <- pred_data %>%
-  filter(
-    ct_alive %in% c(.1),
-    rho %in% c(0, .75),
-    Z == 10,
-    h %in% c(3),
-    avg_int_strength %in% c(.01, .1),
-    w_avg_tlvl == 1.5
-    ) %>%
-  ggplot(aes(
-      x = richness, y = pop_stab,
-      color = as.factor(rho),
-      linetype = as.factor(avg_int_strength),
-      )) +
-  geom_line(linewidth = 1) +
-  facet_grid(cols = vars(env_stoch), labeller = label_both) +
-  labs(
-    x = "Species richness (Log)", y = "Population stability (Log)",
-    linetype = "Avg. Interaction strength",
-    color = "Environmental correlation"
-  ) +
-  theme_bw() +
-  theme(legend.position = "bottom")
-ggsave(
-  here("report", "figures", "p_pred_sr_int_pop_stab.png"),
-  plot = p_pred_sr_int_pop_stab,
-  scale = 2.4,
-  width = 88,
-  height = 88 * .5,
-  units = "mm"
-)
-```
-
-```{r}
-p_pred_sr_avg_tlvl_h <- pred_data %>%
-  filter(
-    ct_alive %in% c(.1),
-    h == c(3),
-    rho %in% c(0, .75),
-    Z == 10,
-    avg_int_strength %in% c(.1),
-    w_avg_tlvl == c(1.5, 3)) %>%
-  ggplot(aes(x = richness, y = stab_com,
-      linetype = as.factor(w_avg_tlvl), color = as.factor(rho))) +
-  geom_line() +
-  facet_grid(cols = vars(env_stoch), labeller = label_both) +
-  theme_bw()
-ggsave(
-  here("report", "figures", "p_pred_sr_avg_tlvl_h.png"),
-  plot = p_pred_sr_avg_tlvl_h,
-  scale = 2.4,
-  width = 88,
-  height = 88 * 1,
-  units = "mm"
-)
-```
-
-```{r}
-tar_load(sem_eff_tab)
-sem_eff_tab %>%
-  filter(abs(effect) > .1) %>%
-  filter(effect_type == "direct") %>%
-  print(., n = 30)
-
-```
-
-```{r, eval=FALSE}
-tar_load(sim_param)
-sim_param %<>%
-  select(-A)
-sim_param %>%
-  group_by(h, rho, env_stoch, Z) %>%
-  summarise(
-    nb_fw = length(unique(fw_id)),
-    n = length(fw_id)
-  )
-
-sim_param %>%
-  group_by(fw_id) %>%
-  summarise(n = n())
+```{r}
+tar_load_globals()
+tar_load(pred_stab_comp_resp_div)
+pred_data_show <- pred_stab_comp_resp_div %>%
+  filter(response == "stab_com") %>%
+  select(-response) %>%
+  pivot_wider(names_from = "variable", values_from = "variable_values") %>%
+  filter(!is.na(w_avg_tlvl))
+unique(pred_data_show$w_avg_tlvl) %>% round(., 3)
+unique(pred_data_show$resp_div) %>% round(., 2)
 

### 2024-04-02 R/model_helpers.R

@@ -45,23 +45,23 @@ formula_stab_fw_model <- function(
   fixed_part <- "richness + resp_div + env_stoch +
   ct_alive + w_avg_tlvl + Z +
   avg_int_strength +
-  h +
+  c +
   richness : resp_div +
   richness : env_stoch +
   richness : ct_alive +
   richness : avg_int_strength +
-  richness : h +
+  richness : c +
   richness : w_avg_tlvl +
   richness : Z +
   richness : resp_div : ct_alive +
   richness : resp_div : w_avg_tlvl +
   richness : resp_div : avg_int_strength +
-  richness : resp_div : h +
+  richness : resp_div : c +
   richness : resp_div : Z +
   richness : env_stoch : ct_alive +
   richness : env_stoch : Z +
   richness : env_stoch : avg_int_strength +
-  richness : env_stoch : h +
+  richness : env_stoch : c +
   richness : env_stoch : w_avg_tlvl"
 
   if (rand_effect) {

### 2024-04-04 _targets.Rmd
Update figures with interference sims

@@
   error = "null",
-  packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra")
+  packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra", "DHARMa")
 )
@@
     sem_collinearity %>%
-      mutate(
-        response = var_replacement()[response],
-        Term = var_replacement()[Term]
-        ) %>%
+      mutate(across(c("response", "Term"), ~var_replacement()[.x])) %>%
+      mutate(VIF = round(VIF, 1)) %>%
+      select(Response = response, Term, VIF) %>%
       kable(
-        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
+        caption = "Variance Inflation Factor for the Structural Equation Model.") %>%
       kable_styling()
@@
     sem_rsquared %>%
+      rename(`$R^2$` = R.squared) %>%
       kable(caption = "Rsquared for the Structural Equation Model.") %>%
@@
 sim_fw_csc_non_allo
+tar_read(sem_rsquared) %>%
+  rename(`$R^2$` = R.squared) %>%
+  kable(caption = "Rsquared for the Structural Equation Model.") %>%
+  kable_styling()
 ```
@@
 
-```{r, eval = FALSE}
-tar_load(sem_main_text)
-tar_load(sim_fw_sem)
-
-m <- list(
-  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + c + Z, sim_fw_sem),
-  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + c + Z, sim_fw_sem),
-  sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
-  cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z, sim_fw_sem),
-  async = lm(async ~ sae_total + cpe, sim_fw_sem),
-  stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
-)
-
-m2 <- list(
-  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + c + Z + resp_div, sim_fw_sem),
-  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + c + Z + env_stoch + resp_div, sim_fw_sem),
-  sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
-  cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z + env_stoch, sim_fw_sem),
-  async = lm(async ~ sae_total + cpe, sim_fw_sem),
-  stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
-)
-
-ti <- as.psem(m)
-ti2 <- as.psem(m2)
-#update(ti, avg_omnivory %~~% w_avg_tlvl)
-summary(ti)
-summary(ti2)
-tar_load(sim_fw_sem)
-
-m3 <- list(
-  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + c + Z + resp_div, sim_fw_sem),
-  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + c + Z + env_stoch + resp_div, sim_fw_sem),
-  sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
-  cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z + env_stoch, sim_fw_sem),
-  cpe_env = lm(cpe_env ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z + env_stoch, sim_fw_sem),
-  #cpe = lm(cpe ~ cpe_env + cpe_int, sim_fw_sem),
-  async = lm(async ~ sae_total + cpe, sim_fw_sem),
-  stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
-)
-summary(as.psem(m3))
-
-```
-
 ```{targets model-to-pred}
@@
       data = mutate(sim_fw,
-      across(c(stab_com, pop_stab, async, richness), log)
+      across(c(stab_com, pop_stab, async), log)
       ))
@@
       data = sim_fw %>%
-        mutate(across(c(stab_com, richness, pop_stab, async), log)) %>%
+        mutate(across(c(stab_com, pop_stab, async), log)) %>%
         mutate(across(c(sim_id, fw_id), as.factor)) %>%
@@
   ),
+  tar_target(pred_range_fw,
+    map(rlang::set_names(c("avg_int_strength", "ct_alive", "w_avg_tlvl")),
+      ~quantile(sim_fw[[.x]], probs = c(.05, .95))
+    )
+  ),
   tar_target(pred_stab_comp_resp_div,
@@
             values = list(
-              seq(quantile(sim_fw$avg_int_strength)["25%"], quantile(sim_fw$avg_int_strength)["75%"], length.out = 50),
-              seq(quantile(sim_fw$w_avg_tlvl)["25%"], quantile(sim_fw$w_avg_tlvl)["75%"], length.out = 50),
-              seq(quantile(sim_fw$ct_alive)["25%"], quantile(sim_fw$ct_alive)["75%"], length.out = 50)
+              seq(
+                min(pred_range_fw$avg_int_strength),
+                max(pred_range_fw$avg_int_strength),
+                length.out = 50
+                ),
+              seq(
+                min(pred_range_fw$w_avg_tlvl),
+                max(pred_range_fw$w_avg_tlvl),
+                length.out = 50
+              ),
+              seq(
+                min(pred_range_fw$ct_alive),
+                max(pred_range_fw$ct_alive),
+                length.out = 50
+              )
             )
@@
 ```{r, eval = FALSE}
-tar_load(sem_simplified_tot)
+tar_load(sem_main_text_tot)
 sem_simplified_tot %>%
@@
 tar_read(sem_main_text_eff_rerun)
+tar_load(pred_stab_comp_resp_div)
 ```
@@
     plot_grid(
-      print(p_sem_tot_stab +
+      p_sem_tot_stab +
         theme(
           legend.position = "none",
-        )
         ),
@@
   ),
-  tar_target(sem_file, here("report", "figures", "sem_stab_simplified_simple.pdf"), format = "file"),
+  tar_target(sem_file, here("report", "figures", "sem_stab_main_text.pdf"), format = "file"),
   tar_target(p_sem,
@@
       p_sem,
-      print(
-        tar_read(p_sem_tot_stab) +
+      p_sem_tot_stab +
         guides(
@@
             legend.justification = c("left", "top"),
-
-          )
         ),
@@
   )
+  ),
+  tar_target(p_sem_fig_file,
+    ggsave_multiple(
+      paste0("p_sem_fig", c(".png", ".pdf")),
+      plot = p_sem_fig,
+      path = here::here("report", "figures"),
+      scale = 3.4,
+      dpi = 400,
+      width = 80,
+      height = 80 * 1,
+      units = "mm")
   ),
@@
   paste0("p_sem_tot_stab", c(".png", ".pdf")),
-  plot = print(
-    p_sem_tot_stab +
+  plot = p_sem_tot_stab +
       guides(
@@
 
-      )
     ),
@@
   height = 80 * .4,
-  units = "mm"),
-  format = "file")
+  units = "mm"))
 )
@@
   geom_raster() +
-      facet_wrap(~variable, scales = "free_y") +
+  facet_wrap(~variable, scales = "free_y", strip.position = "left") +
   coord_cartesian(expand = FALSE) +
@@
     legend.key.width = unit(2.5, "cm"),
-        plot.margin = margin(l = 10, r = 10, unit = "pt")
+    plot.margin = margin(l = 10, r = 10, t = 5, unit = "pt"),
+    strip.placement = "outside",
+    strip.background = element_blank(),
+    strip.text = element_text(size = 11),
+    axis.title.y = element_blank()
   )
@@
       height = 120 * .45,
-      units = "mm"),
-    format = "file"),
+      units = "mm")),
   tar_target(p_pred_sr_resp_div_supp,
@@
       height = 80 * 1,
-      units = "mm"),
-    format = "file"
+      units = "mm")
+  )
+)
+```
+
+```{targets fig-stab-sr}
+tar_load(default_variable_values_pred)
+tar_load(model_fw_stab_comp)
+tar_load(p_pred_sr_resp_div)
+list(
+  tar_target(richness_gradient_pred_show, seq(1, 30, length.out = 20)),
+  tar_target(pred_data_show, {
+    low_resp_example <- rbind(default_variable_values_pred) %>%
+      as_tibble() %>%
+      mutate(resp_div = .1, w_avg_tlvl = 2.0, fw_id = "new") %>%
+      slice(rep(1, length(richness_gradient_pred_show))) %>%
+      mutate(richness = richness_gradient_pred_show)
+    high_resp_example <- rbind(default_variable_values_pred) %>%
+      as_tibble() %>%
+      mutate(resp_div = .9, w_avg_tlvl = 1.2, fw_id = "new") %>%
+      slice(rep(1, length(richness_gradient_pred_show))) %>%
+      mutate(richness = richness_gradient_pred_show)
+    out <- rbind(low_resp_example, high_resp_example)
+    out$stab_com <- predict(
+      model_fw_stab_comp[model_fw_stab_comp$response == "stab_com", ]$model[[1]],
+      out,
+      allow.new.levels = TRUE
+    )
+    out
+  }
+    ),
+  tar_target(p_pred_data_show_low_resp,
+    pred_data_show %>%
+      filter(resp_div == .1) %>%
+      ggplot(aes(x = richness, y = exp(stab_com))) +
+      geom_line(color = resp_div_cat_colors()["Low"]) +
+      ylim(10, 25) +
+      labs(x = "Species richness", y = "Community stability") +
+      theme_half_open()
+    ),
+  tar_target(p_pred_data_show_low_resp_file,
+    ggsave_multiple(
+      paste0("p_pred_data_show_low_resp", c(".png", ".pdf")),
+      plot = p_pred_data_show_low_resp,
+      path = here::here("report", "figures"),
+      scale = 1.4,
+      dpi = 400,
+      width = 80,
+      height = 80 * .9,
+      units = "mm")
+    ),
+  tar_target(p_pred_data_show_high_resp,
+    pred_data_show %>%
+      filter(resp_div == .9) %>%
+      ggplot(aes(x = richness, y = exp(stab_com))) +
+      geom_line(color = resp_div_cat_colors()["High"]) +
+      ylim(10, 25) +
+      labs(x = "Species richness", y = "Community stability") +
+      theme_half_open()
+    ),
+  tar_target(p_pred_data_show_high_resp_file,
+    ggsave_multiple(
+      paste0("p_pred_data_show_high_resp", c(".png", ".pdf")),
+      plot = p_pred_data_show_high_resp,
+      path = here::here("report", "figures"),
+      scale = 1.4,
+      dpi = 400,
+      width = 80,
+      height = 80 * .9,
+      units = "mm")
+    ),
+  tar_target(data_label_pred_show,
+    pred_data_show %>%
+      select(resp_div, richness, w_avg_tlvl) %>%
+      filter(richness == min(richness)) %>%
+      pivot_longer(c(w_avg_tlvl), names_to = "variable",
+        values_to = "variable_values") %>%
+      mutate(variable = var_replacement()[variable],
+        label = c("b", "c")
+      )
+    ),
+  tar_target(p_fig3,
+    plot_grid(
+      p_pred_sr_resp_div +
+        theme(
+          legend.position = "bottom",
+          legend.title = element_text(vjust = .75),
+          legend.key.width = unit(2.0, "cm")
+          ) +
+        geom_label(
+          data = data_label_pred_show,
+          aes(color = NULL, fill = NULL, label = label),
+          fontface = "bold"
+          ),
+        plot_grid(NULL,p_pred_data_show_low_resp,
+          p_pred_data_show_high_resp, NULL,
+          labels = c("", "b", "c", ""), nrow = 1,
+          rel_widths = c(.25, 1, 1, .25)
+          ),
+        labels = c("a"),
+        rel_heights = c(1, .75),
+        nrow = 2
+    )
+    ),
+  tar_target(p_fig3_file,
+    ggsave_multiple(
+      paste0("p_fig3", c(".png", ".pdf")),
+      plot = p_fig3,
+      path = here::here("report", "figures"),
+      scale = 2.6,
+      dpi = 400,
+      width = 80,
+      height = 80 * .8,
+      units = "mm")
   )
@@
     ),
-  tar_target(p_pop_stab_h,
+  tar_target(p_pop_stab_c,
     sim_fw %>%
       filter(env_stoch == .3) %>%
-      ggplot(aes(x = as.factor(h), y = log(pop_stab))) +
+      ggplot(aes(x = as.factor(c), y = log(pop_stab))) +
       geom_boxplot(alpha = .2) +
@@
     ),
-  tar_target(p_sem_bivariate_relations,
+  tar_target(p_raw_bivariate_relations,
     plot_grid(
-      p_pop_stab_w_avg_tlvl, p_pop_stab_h, p_pop_stab_env_stoch,
+      p_pop_stab_w_avg_tlvl, p_pop_stab_c, p_pop_stab_env_stoch,
       p_sae_total_richness, p_sae_total_ct_alive, p_sae_total_w_avg_tlvl,
@@
       )
-
     )
@@
 ```
-```{targets p_cor_file, tar_simple = TRUE, format = "file"}
+```{targets p_cor_file, tar_simple = TRUE}
 ggsave_multiple(
@@
 
+```{targets p_model_fw_stab_comp_scaled_coeff, tar_simple=TRUE}
+pattern <- c(var_replacement(), get_term_replacement())
+names(pattern) <- paste0("\\b", names(pattern), "\\b")
+model_fw_stab_comp_scaled_coeff %>%
+  unnest(cols = c(coeff)) %>%
+  rename(lower_ci = `2.5 %`, upper_ci = `97.5 %`) %>%
+  rename_with(tolower) %>%
+  filter(!str_detect(term, "(Intercept)")) %>%
+  mutate(
+    type = ifelse(str_detect(term, ":"), "interaction", "single"),
+    term = str_replace_all(term, pattern),
+    response = recode_factor(response, !!!var_replacement(), .ordered = TRUE)
+    ) %>%
+  ggplot(aes(
+      y = term, x = estimate,
+      xmin = lower_ci, xmax = upper_ci,
+      color = response)) +
+  geom_vline(xintercept = 0, linetype = "dashed") +
+  geom_pointrange() +
+  scale_colour_manual(values = stab_color()) +
+  labs(x = "Standardised coefficients") +
+  theme_bw() +
+  theme(
+    axis.title.y = element_blank(),
+    legend.title = element_blank(),
+    legend.position = "bottom"
+  )
+```
+
+```{targets p_model_fw_stab_comp_scaled_coeff_file, tar_simple = TRUE}
+ggsave_multiple(
+  paste0("p_model_fw_stab_comp_scaled_coeff", c(".png", ".pdf")),
+  plot = p_model_fw_stab_comp_scaled_coeff,
+  path = here::here("report", "figures"),
+  scale = 2.2,
+  dpi = 400,
+  width = 80,
+  height = 80 * 1.4,
+  units = "mm")
+```
+
 # Table
+
+```{targets sem_fig_coeff, tar_simple=TRUE}
+sem_main_text_eff_tab %>%
+  filter(effect_type == "direct",
+    predictor %in% c(
+      sem_tot_predictor(),
+      "async", "stab_com", "pop_stab", "sae_total", "cpe", "evenness_sae", "sae_even"
+      )) %>%
+select(response, predictor, effect) %>%
+mutate(effect = round(effect, 2)) %>%
+filter(abs(effect) >= .05)
+```
+
+```{targets check-model-pred-sr}
+list(
+  tar_target(model_fw_stab_comp_wo_int,
+    lm(stab_com ~ richness + resp_div + env_stoch + ct_alive + w_avg_tlvl + Z +
+      avg_int_strength + c, data = sim_fw_sem)),
+  tar_target(tab_model_fw_stab_comp_wo_int_vif,
+    model_fw_stab_comp_wo_int %>%
+      performance::check_collinearity() %>%
+      as_tibble() %>%
+      mutate(Term = var_replacement()[Term]) %>%
+      mutate(VIF = round(VIF, 1)) %>%
+      select(Term, VIF) %>%
+      kable(
+        caption = "Variance Inflation Factor for the linear model predicting the
+        relationship between stability and richness.") %>%
+        kable_styling()
+      ),
+    tar_target(sim_res_model_fw_stab_comp,
+      model_fw_stab_comp %>%
+        mutate(
+          res = map(model, DHARMa::simulateResiduals),
+          ) %>%
+      select(-model)
+    ),
+    tar_target(plot_diagnotisc_model_fw_stab_comp,
+    {
+      p <- map(sim_res_model_fw_stab_comp$res,
+            function(x) {
+              plot(x)
+              out <- recordPlot()
+              ggdraw(out)
+            }
+      )
+      plot_grid(plotlist = p,
+        nrow = 3,
+        labels = "auto")
+      }),
+  tar_target(p_diagnotisc_model_fw_stab_comp_file,
+    ggsave_multiple(
+      paste0("p_diagnotisc_model_fw_stab_comp", c(".png", ".pdf")),
+      plot = plot_diagnotisc_model_fw_stab_comp,
+      path = here::here("report", "figures"),
+      scale = 2.4,
+      dpi = 400,
+      width = 80,
+      height = 80 * 1.8,
+      units = "mm")
+  )
+)
+```
 
@@
 
-```{r, eval=FALSE}
-#tar_load_globals()
-tar_load(sem_main_text_eff_tab)
-sem_main_text_eff_tab %>%
-  filter(
-    effect_type == "direct",
-    predictor %in% c(sem_tot_predictor(), "async", "stab_com", "pop_stab", "sae_total", "cpe", "evenness_sae", "sae_even")
-    ) %>%
-select(response, predictor, effect) %>%
-mutate(effect = round(effect, 2)) %>%
-filter(abs(effect) > .02)
-```
-
-```{r}
-tar_load(sem_main_text_collinearity_csc_rerun)
-sem_main_text_collinearity_csc_rerun %>%
-  select(response, Term, VIF) %>%
-  filter(VIF > 3)
-```
-
 ```{r}
 tar_load(sim_fw_sem)
-ti <- lm(stab_com ~ richness + resp_div + env_stoch + ct_alive + w_avg_tlvl + Z +
-  avg_int_strength + c, data = sim_fw_sem)
-check_collinearity(ti)
-
-library(DHARMa)
-tar_load(model_fw_stab_comp)
-tu <- simulateResiduals(model_fw_stab_comp$model[[3]])
-plot(tu)
+```
+
+```{r}
+# Does not work in targets
+tar_load(sim_res_model_fw_stab_comp)
+tmp_diagnotisc_model_fw_stab_comp <- map(sim_res_model_fw_stab_comp$res,
+            function(x) {
+              plot(x)
+              out <- recordPlot()
+              ggdraw(out)
+            }
+      )
+plot_diagnotisc_model_fw_stab_comp <- plot_grid(
+  plotlist = tmp_diagnotisc_model_fw_stab_comp,
+  nrow = 3,
+  labels = "auto")
+ggsave_multiple(
+  paste0("p_diagnotisc_model_fw_stab_comp", c(".png", ".pdf")),
+  plot = plot_diagnotisc_model_fw_stab_comp,
+  path = here::here("report", "figures"),
+  scale = 2.6,
+  dpi = 400,
+  width = 80,
+  height = 80 * 1.3,
+  units = "mm")
 ```
@@
 ```{r}
+tar_meta(fields = error, complete_only = TRUE) %>%
+  print(n = 40)
+```
+
+```{r}
 label_sem <- as.character(as.roman(seq_len(nrow(sem_simplified_bivariate_relations))))
@@
   )
-```
-
-```{r}
-
-ggsave_multiple(
-  paste0("p_sem_fig", c(".png", ".pdf")),
-  plot = tar_read(p_sem_fig),
-  path = here::here("report", "figures"),
-  scale = 3.4,
-  dpi = 400,
-  width = 80,
-  height = 80 * 1,
-  units = "mm")
-```
-
-```{r}
-tar_load(fixed_effect_fw_stab)
-tar_load(fixed_effect_fw_stab_comp)
-tar_load(pred_stab_comp_rho)
 ```
@@
 ```{r}
-tar_load(model_fw_stab_comp_scaled_coeff)
-
-pattern <- c(var_replacement(), get_term_replacement())
-names(pattern) <- paste0("\\b", names(pattern), "\\b")
-```
-
-```{r}
-model_fw_stab_comp_scaled_coeff %>%
-  unnest(cols = c(coeff)) %>%
-  rename(lower_ci = `2.5 %`, upper_ci = `97.5 %`) %>%
-  rename_with(tolower) %>%
-  filter(!str_detect(term, "(Intercept)")) %>%
-  mutate(
-    type = ifelse(str_detect(term, ":"), "interaction", "single"),
-    term = str_replace_all(term, pattern)
-    ) %>%
-  filter(type == "interaction") %>%
-  ggplot(aes(
-      y = term, x = estimate,
-      xmin = lower_ci, xmax = upper_ci,
-      color = response)) +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_pointrange() +
-  labs(x = "Standardised coefficients") +
-  theme_bw() +
-  theme(axis.title.y = element_blank())
-```
-
-```{r}
-p_model_fw_stab_com_int <- model_fw_stab_comp_scaled_coeff %>%
-  filter(response == "stab_com") %>%
-  unnest(cols = c(coeff)) %>%
-  rename(lower_ci = `2.5 %`, upper_ci = `97.5 %`) %>%
-  rename_with(tolower) %>%
-  filter(!str_detect(term, "(Intercept)")) %>%
-  mutate(
-    type = ifelse(str_detect(term, ":"), "interaction", "single"),
-    term = str_replace_all(term, pattern)
-    ) %>%
-  filter(type == "interaction") %>%
-  ggplot(aes(
-      y = term, x = estimate,
-      xmin = lower_ci, xmax = upper_ci
-      )) +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_pointrange() +
-  labs(x = "Standardised coefficients") +
-  theme_bw() +
-  theme(axis.title.y = element_blank())
-ggsave_multiple(
-  paste0("p_model_fw_stab_com_int", c(".png", ".pdf")),
-  plot = p_model_fw_stab_com_int,
-  path = here::here("report", "figures"),
-  scale = 1.8,
-  dpi = 400,
-  width = 80,
-  height = 80 * 1.3,
-  units = "mm")
-```
-
-```{r}
-p_model_fw_stab_com_single <- model_fw_stab_comp_scaled_coeff %>%
-  filter(response == "stab_com") %>%
-  unnest(cols = c(coeff)) %>%
-  rename(lower_ci = `2.5 %`, upper_ci = `97.5 %`) %>%
-  rename_with(tolower) %>%
-  filter(!str_detect(term, "(Intercept)")) %>%
-  mutate(
-    type = ifelse(str_detect(term, ":"), "interaction", "single"),
-    term = str_replace_all(term, pattern)
-    ) %>%
-  filter(type == "single") %>%
-  ggplot(aes(
-      y = term, x = estimate,
-      xmin = lower_ci, xmax = upper_ci
-      )) +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_pointrange() +
-  labs(x = "Standardised coefficients") +
-  theme_bw() +
-  theme(axis.title.y = element_blank())
-p_model_fw_stab_com <- plot_grid(
-  p_model_fw_stab_com_int,
-  plot_grid(p_model_fw_stab_com_single, NULL, nrow = 2),
-  ncol = 2,
-  labels = "auto"
-)
-ggsave_multiple(
-  paste0("p_model_fw_stab_com", c(".png", ".pdf")),
-  plot = p_model_fw_stab_com,
-  path = here::here("report", "figures"),
-  scale = 2.4,
-  dpi = 400,
-  width = 80,
-  height = 80 * 1,
-  units = "mm")
-```
-
-```{r}
 tar_load(fixed_effect_fw_stab)
@@
 tar_load_globals()
+tar_visnetwork()
 tar_load(pred_stab_comp_resp_div)
@@
 
+tar_read(pred_data)
 pred_data_sr_fw <- pred_data %>%
@@
     Z == 100,
-    h %in% c(2),
+    c %in% c(1),
     avg_int_strength %in% fw_values_bin$avg_int_strength,

### 2024-04-04 R/model_helpers.R

@@ -50,18 +50,12 @@ formula_stab_fw_model <- function(
   richness : env_stoch +
   richness : ct_alive +
   richness : avg_int_strength +
-  richness : c +
   richness : w_avg_tlvl +
-  richness : Z +
   richness : resp_div : ct_alive +
   richness : resp_div : w_avg_tlvl +
   richness : resp_div : avg_int_strength +
-  richness : resp_div : c +
-  richness : resp_div : Z +
   richness : env_stoch : ct_alive +
-  richness : env_stoch : Z +
   richness : env_stoch : avg_int_strength +
-  richness : env_stoch : c +
   richness : env_stoch : w_avg_tlvl"
 
   if (rand_effect) {

### 2024-04-04 R/plotting_methods.R

@@ -26,7 +26,7 @@ stab_alpha <- function () {
 }
 
 sem_tot_predictor <- function () {
-  c("resp_div", "ct_alive", "w_avg_tlvl", "avg_int_strength", "richness",
+  c("resp_div", "avg_int_strength", "w_avg_tlvl", "ct_alive", "richness",
     "env_stoch")
 }
 

### 2024-04-04 draft.jl

@@ -22,6 +22,19 @@ include("src/get_modules.jl")
 ti = missing
 isnothing(ti)
 
+typeof([.1])
+tu = [missing, .1, [.1]]
+new = Vector{Union{Missing, Vector{Float64}}}(missing, length(tu))
+for i in 1:length(tu)
+    if (typeof(tu[i]) == Float64)
+        new[i] = [tu[i]]
+    else
+        new[i] = tu[i]
+    end
+end
+new
+convert(Vector{Union{Missing, Vector{Float64}}}, ti)
+
 fw = FoodWeb(nichemodel, 20, C = .2, Z = 10)
 p = ModelParameters(fw)
 filter_model_parameters(p; idxs=[1, 2, 20])

### 2024-04-04 _targets.Rmd
Update manuscript and supplementary figures

@@
     sem_main_text_coeff_csc_rerun %>%
-      kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
-      collapse_rows(1, valign = "middle") %>%
-      kable_styling()
+      filter(!str_detect(Response, "~~")) %>% #Remove correlation w_avg_tlvl ~~ avg_omnivory
+      mutate(across(c("Response", "Predictor"), ~var_replacement()[.x])) %>%
+      mutate(Std.Estimate = round(Std.Estimate, 2)) %>%
+      rename(`Std estimate` = Std.Estimate) %>%
+      select(-Signif)
     ),
@@
       mutate(VIF = round(VIF, 1)) %>%
-      select(Response = response, Term, VIF) %>%
-      kable(
-        caption = "Variance Inflation Factor for the Structural Equation Model.") %>%
-      kable_styling()
+      select(Response = response, Term, VIF)
     ),
@@
       kable_styling()
+  ),
+  tar_target(tab_sem_simplified_eff,
+    sem_simplified_eff_tab %>%
+      filter(effect_type == "direct") %>%
+      mutate(across(c("response", "predictor"), ~var_replacement()[.x])) %>%
+      mutate(effect = round(effect, 2)) %>%
+      select(
+        Response = response,
+        Predictor = predictor,
+        `Std estimate` = effect
+      )
   )
@@
 
-```{targets group-all-analysis, eval = FALSE}
+```{targets group-all-analysis}
 list(
@@
         "rebuild",
-        "no_rerun_short",
         "kno"),
@@
         sem_main_text_eff_tab_csc_kno
-        ),
-      rsq = list(
-        sem_main_text_rquared_csc_rerun,
-        sem_main_text_rquared_csc_non_allo,
-        sem_main_text_rquared_csc_rebuild,
-        sem_main_text_rquared_csc_kno
         ),
@@
 ```{targets fig-stab-sr}
-tar_load(default_variable_values_pred)
-tar_load(model_fw_stab_comp)
-tar_load(p_pred_sr_resp_div)
 list(
@@
 
+```{targets p_sem_main_text_eff_tab_tot_file, tar_simple = TRUE}
+ggsave_multiple(
+  paste0("p_sem_main_text_eff_tab_tot", c(".png", ".pdf")),
+  plot = p_sem_main_text_eff_tab_tot,
+  path = here::here("report", "figures"),
+  scale = 2.4,
+  dpi = 400,
+  width = 80,
+  height = 80 * .5,
+  units = "mm"
+  )
+```
+
 # Table
@@
       mutate(VIF = round(VIF, 1)) %>%
-      select(Term, VIF) %>%
-      kable(
-        caption = "Variance Inflation Factor for the linear model predicting the
-        relationship between stability and richness.") %>%
-        kable_styling()
+      select(Term, VIF)
       ),
@@
     ggsave_multiple(
-      paste0("p_diagnotisc_model_fw_stab_comp", c(".png", ".pdf")),
+      paste0("p_diagnotisc_model_fw_stab_comp", c(".jpg", ".pdf")),
       plot = plot_diagnotisc_model_fw_stab_comp,
@@
   height = 80 * 1.6,
-  units = "mm")
-```
-```{r fig-sem-tot-sensibility}
-ggsave_multiple(
-  paste0("p_sem_simplified_eff_tab_tot", c(".jpg", ".png", ".pdf")),
-  plot = tar_read(p_sem_simplified_eff_tab_tot),
-  path = here::here("report", "figures"),
-  scale = 2.4,
-  dpi = 400,
-  width = 80,
-  height = 80 * .5,
   units = "mm")

### 2024-04-04 paper/manuscript.Rmd
Update manuscript and supplementary figures

--- 2024-02-16 paper/manuscript.Rmd
@@
 title: Food-web structure, stochasticity and response diversity drive temporal community stability in complex communities
-author: "Alain Danet, (Sonia Kéfi, Thomas F Johnson), Andrew P. Beckerman"
+author: "Alain Danet (1), Sonia Kéfi (2,3), Thomas F Johnson (1), Andrew P. Beckerman (1)"
 date: ""
@@
     number_sections: false
+    base_format: "bookdown::word_document2"
   bookdown::pdf_document2:
@@
 
+- 1 School of Biosciences, Ecology and Evolutionary Biology, University of Sheffield, Western Bank, Sheffield, S10 2TN, UK
+- 2 ISEM, CNRS, Univ. Montpellier, IRD, EPHE, Montpellier, France
+- 3 Santa Fe Institute, 1399 Hyde Park Road, Santa Fe, NM 87501, USA
+
 ---
@@
 
-Current biotic homogenization and increasing frequency of extreme events are
-projected to dramatically destabilize ecological communities. Understanding how
-complex communities such as food-webs respond to such threats is crucial to take
-adequate conservation measures. We then investigated how response diversity,
-environmental stochasticity, and food-web structure drive temporal stability of
-biomass in complex food-webs, using a stochastic bioenergetic food-web model. We
-found that higher average trophic level, omnivory degree and generalism
-increased  average population stability while species richness had little
-effects. At the opposite higher average trophic level, omnivory degree and
-generalism decreased asynchrony and compensatory dynamics raising trophic
-interactions. We further found that that high interaction strength drive
-negative stability-species richness when response diversity is low but that high
-response diversity always drive positive stability-richness relationship. Our
-study reveals that response diversity and food-web structure drive temporal
+Empirical and theoretical evidence suggests that current and projected
+environmental changes and biotic homogenisation will dramatically destabilise
+ecological communities. However, this evidence is largely based on
+oversimplified communities (i.e. food chains, guild assemblages), which lack the
+complexity of natural communities.We characterise the dynamics of complex
+food-webs under a stochastic bioenergetic food-web model, and investigate how
+response diversity, environmental stochasticity, and food-web structure drive
+temporal stability. We found that higher average trophic level, omnivory degree
+and generalism increased average population stability, but decreased asynchrony,
+triggering compensatory dynamics that raised trophic interactions.  Species
+richness had little effect on average population stability, but a large one on
+synchrony. Further, when response diversity is low, high interaction strength,
+average trophic level, and connectance all lead to negative stability-species
+richness relationships, but when response diversity is high, we observe positive
+stability-species richness relationships regardless of the food-web structure.
+Our study reveals that response diversity and food-web structure drive temporal
 stability and further improve our understanding of biodiversity-stability
@@
 impacts on the stability of communities and associated impacts on biodiversity
-and functioning in these communities. Assessing the impacts of this variability
-on communities is challenging for several reasons.
-
-First, the stability of communities is often evaluated using temporal
-variability the metric of interest (e.g. abundance or biomass), because most
-natural communities face persistent perturbations so that other stability
-metrics such as resilience and resistance are not always applicable
-[@arnoldi_resilience_2016]. Understanding temporal community variability,
-measured as the inverse of the coefficient of variation
+and functioning in these communities. Assessing the impacts of this increased
+variability on ecological communities is challenging for several reasons.
+
+First, the stability of communities is often evaluated using the temporal
+variability of a metric of interest (e.g. abundance or biomass), because other
+stability metrics such as resilience and resistance are not always applicable,
+as most natural communities face persistent perturbations [@arnoldi_resilience_2016].
+Understanding this temporal community variability (hereafter referred to as
+community stability), measured as the inverse of the coefficient of variation
 [@tilman_biodiversity_2006; @roscher_identifying_2011;
-@thibaut_understanding_2013; @zhao_biodiversity_2022], requires scaling down
-the focus to populations. Community stability can be mathematically partitioned
-into average population stability and asynchrony [@loreau_species_2008;
-@thibaut_understanding_2013; @zhao_biodiversity_2022], asynchrony measuring how
-much each species fluctuations are compensating each other at the community
-level. Population stability and asynchrony depend both on the number of species
+@thibaut_understanding_2013; @zhao_biodiversity_2022], requires scaling down the
+focus from communities to populations.
+Community stability can be mathematically partitioned into average population
+stability and asynchrony [@loreau_species_2008;
+@thibaut_understanding_2013; @zhao_biodiversity_2022] - asynchrony measuring how
+much each species fluctuations’ are compensating for each other at the community
+level. Population stability and asynchrony both depend on the number of species
 and their dominance [@loreau_species_2008; @thibaut_understanding_2013;
-@zhao_biodiversity_2022], the interactions among them [@thebault_trophic_2005;
+@zhao_biodiversity_2022], on the interactions among species [@thebault_trophic_2005;
 @thebault_relationship_2006; @loreau_species_2008; @danet_species_2021;
-@eschenbrenner_diversity_2023] and on the way that species respond to
-environmental perturbations [response diversity, @ives_stability_2000;
+@eschenbrenner_diversity_2023] and on the way species respond to environmental
+perturbations [@ives_stability_2000; so-called response diversity,
 @elmqvist_response_2003; @ross_how_2023]. Therefore, accounting for the effects
-on community structure on population stability and asynchrony is crucial to
-improve our understanding of community stability in face of environmental
-change.
-
-Average population stability is decreased by external forcing, such as the
-intensity and the frequency of perturbations [@loreau_species_2008]. Species richness can
-decrease [@tilman_biodiversity_2006; @loreau_species_2008], increase
+of community structure on population stability and asynchrony is crucial to
+improve our understanding of community stability in facing environmental change.
+
+Average population stability decreases with environmental stochasticity, such as the
+intensity and the frequency of perturbations [@loreau_species_2008]. Theorerical
+and empiral evidence suggests that species richness can decrease
+[@tilman_biodiversity_2006; @loreau_species_2008], increase
 [@houlahan_negative_2018], or have little effects on population stability. This
 effect of species richness on population stability depends on the evenness of
-the community such as dominant species contribute more the average of the
-community than subordinate species. At the core of ecological theory,
-population stability depends on internal forcing, here species interactions. The
-topological structure and the distribution of interaction strength have tremendous
+the community since dominant species contribute more to the average of the
+community than subordinate species. Species interactions also have tremendous
 effects on population stability, such as strong interaction strength are
 generally destabilising [@mccann_weak_1998; @mccann_reevaluating_1997;
-@thebault_trophic_2005]. In particular for food-webs, top-down and bottom-up
-controls can increase population stability.
-
-Asynchrony in turn can be partitioned into portfolio effects and compensatory
-dynamics and is mostly determined by internal factors. Portfolio effects stems
-from the statistical averaging of independent population fluctuations
-[@doak_statistical_1998; @zhao_biodiversity_2022], thereby increasing
-asynchrony. Compensatory dynamics in turn captures population fluctuations that
-are more synchronous or asynchronous than expected for independent fluctuations,
-and can stem from species interactions and species responses to perturbations
-[@zhao_biodiversity_2022]. Response diversity captures how among species’
-differences in their response to the environmental variation, can underpin
-asynchronous dynamics if their responses are different but synchronous if their
-responses are similar. Theory and empirical data emerging around response
-diversity suggests it is  “core ecological mechanism underpinning many of the
-statistical explanations of the diversity–stability relationships”
-[@ives_stability_2000; @elmqvist_response_2003; @ross_how_2023]. In turn,
-the distribution and strength of species interactions can also modulate
-asynchrony through compensatory dynamics such as a strong asymmetry of consumer
-preference can generate asynchrony in resource fluctuations [@mccann_weak_1998;
+@thebault_trophic_2005]. The shape of food-webs can also modulate population
+stability, such as higher trophic level was generally found to be stabilising
+[@shanafelt_stability_2018; @danet_species_2021; @eschenbrenner_diversity_2023],
+as top-down and bottom-up controls can increase population stability
+[@shanafelt_stability_2018].
+
+Asynchrony is mostly determined by the characteristics of the network. Response
+diversity captures how species’ differences in their response to the
+environmental variation can lead to asynchronous dynamics if their responses are
+different but synchronous dynamics if their responses are similar. Theory and
+empirical data emerging around response diversity suggest that it is a “core
+ecological mechanism underpinning many of the statistical explanations of the
+diversity–stability relationships” [@ives_stability_2000;
+@elmqvist_response_2003; @ross_how_2023]. In turn, the network structural
+properties and strength of species interactions can also modulate asynchrony
+through compensatory dynamics such as a strong asymmetry of consumer preference
+can generate asynchrony in resource fluctuations [@mccann_weak_1998;
 @vasseur_environmental_2007], and a generalist consumer can in turn generate
@@
 [@loreau_species_2008]. Finally, portfolio and compensatory effects can also be
-affected by the population evenness such as fluctuations of a dominant
-species will hardly be compensated by a subordinate species. Improving our
-understanding of community stability facing perturbations therefore requires to
-articulate the effect response diversity, species interactions, species
-richness and evenness on the different components of stability.
-
-The stability of ecological communities facing perturbations stems from two
-parallel bodies of work: species interactions and response diversity. These two
-bodies of work share the common thread of community structure acting through a
-filter to drive stability. However, the filter is different in each space; in
-the first, the filter is the topology and the strength of species interactions
-and in the second variation in species’ responses. Moreover, the theory has been
-developed largely in theoretical or empirical communities characterised by a
-limited array of interactions (e.g. often lacking in consumers) and by limited
-species diversity/richness. Thus, ecology lacks a body of theory integrating
-across structure and response diversity frameworks and reflecting species rich
-communities. Here, we integrate these two perspectives on diversity - stability
-to evaluate the combined effects of community structure and response diversity on
-temporal stability in species rich, complex communities characterised by
-competition and predation.
+affected by the population evenness such as fluctuations by dominant species
+will hardly be compensated by a subordinate species
+[@thibaut_understanding_2013; @zhao_biodiversity_2022]. Improving our
+understanding of community stability facing perturbations therefore requires
+articulating the effects of response diversity, species interactions, species
+richness and evenness on the different components of stability. Predicting the
+effects of species richness on community stability thus requires understanding
+the relationship between species richness, population stability and asynchrony.
+
+Empirical evidence suggest by increasing asynchrony, species richness
+drives positive relationships between community stability and species richness
+[@tilman_biodiversity_2006; @isbell_biodiversity_2009]. In contrast population stability was
+found to either decrease, increase, or not change with species richness
+[@houlahan_negative_2018; @tilman_biodiversity_2006; @roscher_identifying_2011].
+We note, however, that evidence for both asynchrony-richness and population
+stability-richness is derived from data on species assemblages.  These data thus
+do not account for food-web structure, which can have significant impact on
+population stability and asynchrony [but see @danet_species_2021]. Thus, ecology
+lacks a body of theory of temporal stability integrating across structure and
+response diversity frameworks and reflecting species rich communities. Here, we
+integrate these two perspectives on diversity- stability to evaluate the
+combined effects of community structure and response diversity on temporal
+stability in species rich, complex communities characterised by competition and
+predation.
 
 The ability to do this is supported by a key statistical advance: it is now
-possible to partition asynchrony into two component sources, the statistical
-averaging effect (SAE) and compensatory dynamics effect (CPE)
-[@zhao_biodiversity_2022]. SAE quantifies the portfolio effect emerging from
-independent species fluctuations, while CPE describes compensatory dynamics
-emerging from species interactions and differential responses to environmental
-stochasticity. This allows an unprecedented opportunity to obtain mechanistic
-insight about the effects of stressors and food-web structure on stability in
-complex, species rich communities.
+possible to partition asynchrony into two component sources: the portfolio
+effects (rising from statistical averaging effects, SAE) and the compensatory
+dynamics effect (CPE) [@zhao_biodiversity_2022]. Portfolio effects stem from the
+statistical averaging of independent population fluctuations [@doak_statistical_1998;
+@zhao_biodiversity_2022], thereby increasing asynchrony. Compensatory dynamics
+in turn capture population fluctuations that are more synchronous or
+asynchronous than expected for independent fluctuations, and can stem from
+species interactions and species responses to perturbations [@zhao_biodiversity_2022].
+This allows an unprecedented opportunity to obtain mechanistic insight about the
+effects of stressors and food-web structure on stability in complex, species
+rich communities.
 
 Our primary objective is to derive theory that predicts how the components of
-community stability, that can differentially drive patterns of stability, deliver novel
-insights into the source and patterns of diversity-stability relationships in
-complex communities facing environmental stochasticity. Our approach delivers
-revised insight into diversity-productivity relationships in species rich
-communities when both community structure per se, and species
-responses can vary. In the following sections, we begin by introducing the
-multi-species model and the features of the model that allow us to integrate
-across variation in community structure and response diversity. We
-then introduce assumptions we used to implement environmental stochasticity,
-response diversity, variation in community structure and variation in the
-distribution of interaction types and strengths. Next we define our in-silico
-experimental design that specifically aligns with three core questions and
-associated analyses: (1) What are the direct effects of food-web structure and
-interaction strength on population stability, compensatory dynamics,
-and statistical averaging effects (i.e. portfolio effects)? (2) What are the
-total effects of food-web structure, response diversity, environmental
-stochasticity on community stability. Finally, merging the two parallel bodies of
-work, we asked (3) How do response diversity and food-web structure interact to
-drive the sign of the relation between community stability and
-species richness?
+community stability, that can differentially drive patterns of stability,
+deliver novel insights into the source and patterns of diversity-stability
+relationships in complex communities facing environmental stochasticity, a
+necessary ingredient to generate species fluctuations. Our approach delivers
+revised insight into diversity-stability relationships in species rich
+communities when both community structure per se, and species responses can
+vary. In the following sections, we begin by introducing the multi-species model
+and the features of the model that allow us to integrate across variation in
+community structure and response diversity. We then introduce assumptions we
+used to implement environmental stochasticity, response diversity, variation in
+community structure and variation in the distribution of interaction types and
+strengths. Next, we define our in-silico experimental design that specifically
+aligns with three core questions and associated analyses. Considering four
+drivers, namely food-web structure, interaction strength, environmental
+stochasticity and response diversity, we investigated (1) What are their direct
+effects on population stability, portfolio and compensatory effects ? (2) What
+are their total effects on community stability, population stability and
+asynchrony? Finally, merging the two parallel bodies of work, we asked (3) How
+do they interact to drive the sign of the relation between community stability
+and species richness?
 
@@
 We simulated the dynamics of complex food-webs using the allometric bioenergetic
-model [@yodzis_body_1992; @brose_allometric_2006; @delmas_simulations_2017].
-This model is widely used to simulate the dynamics of complex ecological
-communities because of the simplicity of its parametrisation and that its
-parameters are rooted in the metabolic theory of ecology [@brown_toward_2004].
-The model describes species biomass dynamics over time with two master equations (eq. \@ref(eq:dbdt)), one for the
-primary producers (eq. \@ref(eq:prod)) and one for the consumers (eq. \@ref(eq:prod)):
+model [@yodzis_body_1992; @brose_allometric_2006; @delmas_simulations_2017]. This model
+is widely used to simulate the dynamics of complex ecological communities
+because of the simplicity  and because it can be parametrized using  the
+metabolic theory of ecology [@brown_toward_2004]. The model describes species
+biomass dynamics over time with two master equations (eq. \@ref(eq:dbdt)), one
+for the primary producers (eq. \@ref(eq:prod)) and one for the consumers (eq.
+\@ref(eq:prod)):
 
@@
 consumption of a consumer $i$ on a resource $j$ vary with the biomass of this resource.
-Consumers then loses biomass by being consumed, $e_ij$ being the assimilation
+Consumers then lose biomass by being consumed, $e_ij$ being the assimilation
 efficiency of the consumer $j$ on the resource $i$. Consumers also lose biomass
@@
 
-The growth function of the primary producers (eq. \@ref(eq:growth)) has the shape of a logistic growth
+The growth of the primary producers (eq. \@ref(eq:growth)) is logistic
 where the growth rate is maximal and null when
@@
 controls the shape of the functional response from a saturating function
-($h = 2$, Holling type II) to a sigmoid ($h = 3$, Holling type III).
+($h = 1$, Holling type II) to a sigmoid ($h = 2$, Holling type III).
 
@@
 
-We introduced environmental stochasticity by
-considering stochastic variation of mortality rates. Doing so allows to consider
-stochasticity without modifying species interactions themselves
+We introduced environmental stochasticity by considering stochastic variation of
+mortality rates. Doing so allows to consider stochasticity without modifying
+species interactions themselves
 [@vasseur_environmental_2007]. The stochastic part of the mortality rates
 ($\epsilon_{i, t}$) follow a normal distribution 0 centered
-($\epsilon_{i, t} \sim N(0,\sigma^2_e)$) with a variance ($\sigma^2_e$). The mortality rates each
-species at the time $t$ equals to $d_{i,t} = d_i e^{\epsilon_{i, t}}$. We did so
-to ensure to not have negative mortality rates [@vasseur_environmental_2007]. We
+($\epsilon_{i, t} \sim N(0,\sigma^2_e)$) with a variance ($\sigma^2_e$). The
+mortality rates of each species at the time $t$ equals to $d_{i,t} = d_i
+e^{\epsilon_{i, t}}$, which ensured that the mortality rates never become
+negative [@vasseur_environmental_2007]. We
 simulated $\epsilon$ using an Ornstein-Uhlenbeck process, which is a modified
@@
   \end{bmatrix}
-S_{com} = S_{pop} \times \phi
 (\#eq:rho)
@@
 pZ <- get_sim_par_val(x = "Z")
-ph <- get_sim_par_val(x = "h")
+pc <- get_sim_par_val(x = "c")
 pe <- get_sim_par_val(x = "env_stoch")
@@
 scaled mortality rate $d$) in the community, we varied the Predator-Prey
-Mass Ratio (PPMR) from $`r pZ["min"]`$ to $`r pZ["max"]`$ (Fig. \@ref(fig:met)b). We further varied
-the functional response of consumer from type II to type III (i.e. from
-$h = `r ph["min"]`$ to $h = `r ph["max"]`$, eq. \@ref(eq:holling)) as it was shown to
-have a tremendous role on stability [@brose_allometric_2006]. We set a global
-carrying capacity of $K' = 10$ to ensure that consumers were not limited by the
-biomass input from primary producers. We standardised the carrying capacity by
-the number of primary producers and by the interspecific competition among
-producers to ensure that the effects of species richness on temporal stability
-are not driven by the increase in the number of primary producers, thereby
-trivially increase biomass input for consumers. We then standardised $K'$ such as
-$K_i = \frac{1 + \alpha_{ij} (S - 1)}{S}K'$ [@ives_stability_2000].
-
-We numerically solved the stochastic differential equation systems during 5000
-timesteps and collected the last 500 timesteps. We set $d_t = .1$, and $d_t =
-.05$ when instability was detected during the simulations due to stiff changes
-in biomass. We set extinction threshold to $10^{-6}$ and if an extinction
-happened in the last 500 timesteps, we continued to run the simulation for
-another 1000 timesteps until there was no extinction events. When we found
+Mass Ratio (PPMR) from $`r pZ["min"]`$ to $`r pZ["max"]`$ (Fig. \@ref(fig:met)b).
+We set $h = 2$, i.e. a functional response of type III (eq. \@ref(eq:holling)),
+and varied predator interference (i.e. from $c = `r pc["min"]`$ to $c = `r
+pc["max"]`$, eq. \@ref(eq:holling)), as predator interference was shown to have
+a tremendous role on population stability [@brose_allometric_2006]. We set a global
+carrying capacity of $K' = 10$ to ensure that consumers were not
+limited by the biomass input from primary producers. We standardised the
+carrying capacity by the number of primary producers and by the interspecific
+competition among producers to ensure that the effects of species richness on
+temporal stability are not driven by the increase in the number of primary
+producers, thereby trivially increase biomass input for consumers. We then
+standardised $K'$ such as $K_i = \frac{1 + \alpha_{ij} (S - 1)}{S}K'$
+[@ives_stability_2000]. However, we found that our results were not affected
+when removing the standardisation of carrying capacity (Fig. S1).
+
+We numerically solved the stochastic differential equation systems during 2000
+timesteps and collected the last 500 timesteps, similarly to previous studies
+[@brose_allometric_2006]. We set $d_t = .1$, and $d_t = .05$ when instability
+was detected during the simulations due to stiff changes in biomass. We set
+extinction threshold to $10^{-6}$ and if an extinction happened in the last 500
+timesteps, we continued to run the simulation for another 1000 timesteps until
+there was no extinction events during the last 500 timesteps. When we found
 disconnected species at the end of the simulation (i.e. a primary producer
-without consumer or a consumer without prey), we removed them and re-run the
-simulation for another 1000 timesteps.
+without consumer or a consumer without prey), we set their biomass to 0 and
+re-run the simulation for another 1000 timesteps. Except in the case of
+disconnected species, we re-ran simulations with species starting biomass equals
+to their biomass at the last timestep of the previous simulation. Supplementary
+analysis showed that alternative choices of simulation processes, such as longer
+simulations, rebuilding food-webs (i.e. resetting consumer preferences,
+recomputing species bodymass according to the new food-web) after removing
+disconnected species did not affect our results (Fig. S1). The food-web
+generation and simulations were done using the `Julia` package
+`EcologicalNetworkDynamics.jl` [@lajaaiti_ecologicalnetworksdynamicsjl_2024].
 
@@
 
-We measured food-web structure and dynamics that have been shown to be linked
-with stability. We collected total biomass, species richness, connectance,
-average trophic level weighted by biomass, average omnivory and average per
-capita interaction strength. Connectance was computed as $C = L / S(S-1)$, $L$
-being the number of trophic links and $S$ being the number of species in the
-community. Species trophic level was computed recursively from the bottom of the
-food-web, such as the trophic level of a consumer was equal to the average
-trophic level of its resources added to 1, the trophic level of primary
-producers being set to 1 [@christensen_ecopath_1992]. Average trophic level was then equal to:
+We measured food-web properties that have been linked with stability in the
+literature.  We measured total biomass, species richness, connectance, average
+trophic level weighted by biomass, average omnivory and average interaction
+strength. Food-web properties were measured at each of the 500 timesteps and
+then averaged, except connectance and trophic level that were static.
+Connectance was computed as $C = L / S(S-1)$, $L$ being the number of trophic
+links and $S$ being the number of species in the community. Species trophic
+level was computed recursively from the bottom of the food-web, such as the
+trophic level of a consumer was equal to the average trophic level of its
+resources added to 1, the trophic level of primary producers being set to 1
+[@christensen_ecopath_1992]. Average trophic level was then equal to:
 $1/\hat{B}_i\sum_{i}\mathrm{TL}_i$, $\mathrm{TL}_i$ being the trophic level and
 $\hat{B}_i$ the average biomass of the species $i$. The degree of omnivory of a
-consumer was computed  such as the sum of squares of its
-resource trophic levels weighted by the relative preference of the consumer for
-each resource: $\sum_i (\mathrm{TL}_i - \hat{\mathrm{TL}})^2 \omega_i/ \sum \omega_i$ [@christensen_ecopath_1992].
-Interaction strength was computed was quantified as the biomass fluxes going
-from a resource to a consumer, such as: $I = x_i y_i B_k F_{ij}$ (eq.
-\@ref(eq:cons)), and averaged over time. Per capita interaction strength was
-obtained by dividing average interaction strength by the average biomass of the
-consumer. Our way of measuring per interaction strength is very similar to
-previous metrics used in previous studies, at the difference here that we
-average fluxes over time and not the maximal interaction strength
-[@mccann_weak_1998]. Finally, the average interaction strength of a community
-was computed as the average per capita interaction strength at the exclusion of
-null interaction strengths (i.e. excluding absence of trophic interactions).
+consumer was computed  such as the sum of squares of its resource trophic levels
+weighted by the relative preference of the consumer for each resource: $\sum_i
+(\mathrm{TL}_i - \hat{\mathrm{TL}})^2 \omega_i/ \sum \omega_i$
+[@christensen_ecopath_1992]. Interaction strength was computed was quantified as
+the biomass fluxes going from a resource to a consumer, such as: $I = x_i y_i
+B_k F_{ij}$ (eq. \@ref(eq:cons)), and averaged over time. Our way of measuring
+interaction strength is very similar to previous metrics used in previous
+studies, at the difference here that we average fluxes over time and not the
+maximal interaction strength [@mccann_weak_1998]. Finally, the average
+interaction strength of a community was computed as the average interaction
+strength at the exclusion of null interaction strengths (i.e. excluding absence
+of trophic interactions).
 
@@
 To further get a mechanistic insight about the effects of stressors and food-web
-structure on stability, we partitioned asynchrony into statistical averaging
-effect (SAE) and compensatory dynamics effect (CPE) [@zhao_biodiversity_2022].
+structure on stability, we partitioned asynchrony into portfolio effects (measured by statistical averaging
+effect, SAE) and compensatory dynamics effect (CPE) [@zhao_biodiversity_2022].
 SAE quantities the portfolio effect emerging from independent species
-fluctuations, while CPE describes compensatory dynamics emerging from species
-interactions and differential responses to environmental stochasticity.
+fluctuations, while CPE describes compensatory dynamics deviating from portfolio
+effects, and emerging from species interactions and differential responses to
+environmental stochasticity.
 
@@
 $SAE_{even}$ corresponds to the $SAE$ when species quantities are perfectly
-even such as from eq. \@ref(eq:sae2), we can obtain $SAE_{even}$ from which $EVN$ can be computed:
+even such as from eq. \@ref(eq:sae2), we can obtain $SAE_{even}$ from which
+$EVN$ can be computed:
 
@@
 different facets of temporal stability of biomass (i.e. population stability,
-statistical averaging effects and compensatory dynamic effects). We set the
-paths of the path of the model according to theoretical expectations. We tested
-the effects of initial species richness, initial connectance, Predator-Prey size
-ratio on secondary structure of the food-webs, i.e. realized species richness
-and connectance, the average trophic level, the average omnivory and the
-interaction strength. Further, we expected those food-web structure to alter
-population stability and synchrony. Grounded in theoretical ecology, we expected
-that higher average trophic level, average omnivory, lower interaction strength,
-and type III functional response (relative to type II) increase population
-stability [@mccann_weak_1998; @mccann_reevaluating_1997;
-@shanafelt_stability_2018]. Higher Predator-Prey size ratio was also expected to
-increase population stability [@brose_allometric_2006]. Finally, the effect of
-environmental stochasticity was assumed to be mainly associated to population
-stability (i.e. by increasing amplitude of population fluctuations).
-
-Regarding asynchrony, we tested the effects of species richness, connectance,
-average trophic level and interaction strength on statistical averaging effects.
-We expected that those same food-web structural properties affected
-compensatory dynamics due to interactions ($CPE_{int}$). Finally, we tested the
-effects of species richness and species response diversity in mortality rates on
-the compensatory dynamics due to stochastic fluctuations ($CPE_{env}$). We
+portfolio effects and compensatory dynamic effects). We tested the
+effects of food-web structure (average interaction strength, average trophic
+level, connectance) on population stability and asynchrony partitions (portfolio and
+compensatory effects). Grounded in theoretical ecology, we expected that higher
+average trophic level lower interaction strength, lower connectance[@mccann_weak_1998;
+@mccann_reevaluating_1997; @shanafelt_stability_2018]. We further added
+simulation parameters as control variables because higher Predator-Prey Mass
+Ratio and predator interference were also expected to increase population
+stability [@brose_allometric_2006]. Finally, we tested the effects of environmental
+stochasticity and response diversity on population stability and asynchrony
+partitions, although there were predicted to mainly affect to population stability
+(i.e. by increasing amplitude of population fluctuations) and asynchrony (i.e.
+by generating independent population fluctuations) respectively. We
 completed the structural equation model with the mathematical relationship
 linking compensatory dynamics and statistical averaging effects to asynchrony,
-and from asynchrony and population stability to community stability.
+and from asynchrony and population stability to community stability. We further
+developed a more detailled SEM including the effects omnivory and partition of
+compensatory dynamics due to species interactions ($CPE_{int}$) and due to
+environmental fluctuations ($CPE_{env}$).
 
@@
 components to transform their relation from multiplicative to additive (eq.
-\@ref(eq:scom2)).
-We ensure that all the linear models composing the structural equation model
-presented low to moderate multicollinearity (Variance Inflation Factor < 10, Table SXX). The
-structural equation model using the R package `PiecewiseSEM`
-[@lefcheck_piecewisesem_2016]. We then bootstrapped (N = 100) the SEM to obtain
-confidence interval on the estimated effects and computed the sum of the direct
-and indirect effects using `semEff` R package [@murphy_semeff_2021]. In the
-main text, we reported standardised coefficients which are obtained by scaling
-the coefficients by the standard deviation of the response and predictor
-variable (add formula). Finally, because we analysed simulation, we reported
-only the direct standardised coefficients that had an absolute value above $0.1$.
+\@ref(eq:scom2)). We ensured that all the linear models composing the structural
+equation model presented low multicollinearity (Variance Inflation
+Factor < 3, Table S1), altough interaction strength and species richness were
+highly correlated (Fig. S2). The structural equation model using the R package
+`PiecewiseSEM` [@lefcheck_piecewisesem_2016]. We then bootstrapped (N = 100) the
+SEM to obtain confidence interval on the estimated effects and computed the sum
+of the direct and indirect effects using `semEff` R package
+[@murphy_semeff_2021]. In the main text, we reported standardised coefficients
+which were obtained by scaling the coefficients by the standard deviation of the
+response and predictor variable. Finally, we reported only the direct
+standardised coefficients that had an absolute value above $0.05$, because
+almost all linked were statistically significant given the high numbers of
+simulations.
 
@@
 environmental stochasticity and response diversity. We then modelled temporal
-stability of biomass according to food-web structure: species richness, weighted
-average trophic level, connectance, hill exponent, predator-prey mass ratio, and
-average interaction strength, as well as environmental stochasticity and species
-response diversity. We further included the two-way interactions between species
-richness and food-web structure, plus between species richness and stressors.
-Finally, we added the three-way interaction between species richness, food-web
-structure and stressors. The VIF were inferior to 5, indicating low
-multicollinearity. We then used the linear equation of the model and associated
-slope coefficients to predict the shape of the relationship between community
-stability and species richness according to a gradient of response diversity and
-of food-web structure. To do so, we summed all the coefficients involving species
-richness in the model, i.e. the one, two, and three-way terms. The values of the
-control variables were set to the values indicated in the Fig. \@ref(fig:pred).
+stability of community biomass according to food-web structure: species
+richness, weighted average trophic level, connectance and average interaction
+strength, as well as environmental stochasticity and species response diversity.
+We further included the two-way interactions between species richness and
+food-web structure, plus between species richness and stressors. Finally, we
+added the three-way interaction between species richness, food-web structure and
+stressors. We added predator interference, predator-prey mass ratio as control
+variables. We further added the id of the food-web as a random intercept.  We
+then used the linear equation of the model and associated slope coefficients to
+predict the shape of the relationship between community stability and species
+richness according to a gradient of response diversity and of food-web
+structure. To do so, we summed all the coefficients involving species richness
+in the model, i.e. the one, two, and three-way terms. The values of the other
+variables were set to the values indicated in the Fig. \@ref(fig:pred). The VIF
+were inferior to 3, indicating low multicollinearity (Table S2), we checked the
+distribution of the residuals (Fig. S3) using `DHARMa` R package. The model was
+implemented using the R package `glmmTMB` [@brooks_glmmtmb_2017].
 
@@
 sem_cap <- paste0(
-  "Structural Equation Model linking initial model parameters to resulting
-  temporal stability of biomass. (a) Arrows display positive (continuous) and
-  negative (dashed) standardised effects. Initial parameters were initial
-  species richness, initial connectance, Prey-Predator Mass Ratio (PPMR), hill
-  exponent, variance of stochastic mortality rates (Env. stochasticity), and
-  species response diversity. Only the standardised coefficients whose absolute
-  values are superior to 0.1 are displayed. A more complete SEM containing
-  further partition of Statistical Averaging Effect and Compensatory effects is
-  displayed in Fig. SXX. (b) Total effect of food-web structure on community stability,
-  asynchrony, and population stability. The total effects were derived from the
-  structural equation model. (c) Partial relationships derived from the SEM, points
-  displaying the partial standardized residuals while lines displays the linear
-  relationship derived from the SEM.")
+  "Structural Equation Model food-web struture and stressors to temporal
+  stability of community biomass. (a) Continuous red arrows display positive and
+  dashed blue arrows display negative standardised effects, width of the arrows
+  being proportional to the absolute values of the standardised effects. Only
+  the standardised coefficients whose absolute values are superior to 0.05 are
+  displayed. The full table of coefficients including control variables is
+  displayed in Table S3. A more complete SEM containing further partition of
+  compensatory effects and control variables is displayed in Table S4. (b) Total
+  effect of food-web structure on community stability, asynchrony, and
+  population stability. N = ", nrow(tar_read(sim_fw)), " simulations.") %>%
+  str_replace_all("\\s+", " ")
 ```
@@
 ```{r}
-tar_load(c(sem_eff_tab, sem_simplified_eff_tab))
+tar_load(c(sem_main_text_eff_tab, sem_simplified_eff_tab))
 
@@
   d = 2, effect_type = "direct",
-  tab = sem_simplified_eff_tab) {
+  tab = sem_main_text_eff_tab) {
   mask <- tab$response == y & tab$predictor == x &
@@
 rpt <- get_eff(y = "pop_stab", x = "w_avg_tlvl")
-rph <- get_eff(y = "pop_stab", x = "h")
+rpc <- get_eff(y = "pop_stab", x = "c")
 rpe <- get_eff(y = "pop_stab", x = "env_stoch")
+rpd <- get_eff(y = "pop_stab", x = "resp_div")
 
@@
 # Detailled SEM coefficients
-rsr <- get_eff(y = "sae_even", x = "richness", tab = sem_eff_tab)
-ret <- get_eff(y = "evenness_sae", x = "w_avg_tlvl", tab = sem_eff_tab)
-rer <- get_eff(y = "evenness_sae", x = "richness", tab = sem_eff_tab)
-rea <- get_eff(y = "evenness_sae", x = "avg_int_strength", tab = sem_eff_tab)
-rec <- get_eff(y = "evenness_sae", x = "ct_alive", tab = sem_eff_tab)
-reh <- get_eff(y = "evenness_sae", x = "h", tab = sem_eff_tab)
-
-ria <- get_eff(y = "cpe_int", x = "avg_int_strength", tab = sem_eff_tab)
-ric <- get_eff(y = "cpe_int", x = "ct_alive", tab = sem_eff_tab)
-rih <- get_eff(y = "cpe_int", x = "h", tab = sem_eff_tab)
-rir <- get_eff(y = "cpe_int", x = "richness", tab = sem_eff_tab)
-
-rvr <- get_eff(y = "cpe_env", x = "richness", tab = sem_eff_tab)
-rvd <- get_eff(y = "cpe_env", x = "resp_div", tab = sem_eff_tab)
-```
+rsr <- get_eff(y = "sae_total", x = "richness")
+ret <- get_eff(y = "evenness_sae", x = "w_avg_tlvl")
+rer <- get_eff(y = "evenness_sae", x = "richness")
+rea <- get_eff(y = "evenness_sae", x = "avg_int_strength")
+rect <- get_eff(y = "evenness_sae", x = "ct_alive")
+rec <- get_eff(y = "evenness_sae", x = "c")
+red <- get_eff(y = "evenness_sae", x = "resp_div")
+
+```
+
 ```{r, eval = FALSE}
-sem_simplified_eff_tab %>%
-  filter(abs(effect) > .1, effect_type == "direct")
+tar_load(c(sem_fig_coeff))
 ```
@@
 We found that food-web structure had significant effect on temporal population
-stability such as average trophic level and type III functional response (i.e.
-hill exponent = 3) increase population stability (resp. $r_\delta$= `r rpt` and
-`r rph`, $r_\delta$ being the standardised coefficient, Fig. \@ref(fig:sem)a).
-In turn, the variance of environmental stochasticity had a strong negative effect
-on population stability ($r_\delta$= `r rpe`).
-
-We further found that food-web structure had a strong impact on statistical
-averaging effects, which raises from independent species fluctuations weighted
-the evenness of their variance. As expected the mathematical relationship (eq.
-\@ref(eq:sae-even)), species richness was a main positive driver of statistical
-averaging effect ($r_\delta$= `r rsr`, Fig. \@ref(fig:sem)a), thereby increasing
-asynchrony. Average trophic level and average interaction strength had strong
-negative effects on statistical averaging effects (resp. $r_\delta$= `r rst` and
-`r rsi`), thereby downplaying the portfolio effect raised from species richness.
-In turn, we found that average interaction strength had a small positive effect
-on compensatory dynamics ($r_\delta$= `r rci`, Fig. \@ref(fig:sem)). Species
-response diversity had a strong positive effect on compensatory dynamics
-($r_\delta$= `r rcd`).
+stability such as average trophic level increase population stability (resp.
+$r_\delta$= `r rpt`, $r_\delta$ being the standardised coefficient,
+Fig. \@ref(fig:sem)a). In turn, the variance of environmental stochasticity had
+a strong negative effect on population stability ($r_\delta$= `r rpe`). We
+further found that response diversity had a small negative effect on population
+stability ($r_\delta$= `r rpd`).
+
+We further found that food-web structure had a strong impact asynchrony, raising
+from portfolio and compensatory effects. As
+expected the mathematical relationship (eq. \@ref(eq:sae-even)), species
+richness was a main positive driver of portfolio effects ($r_\delta$= `r rsr`,
+Fig. \@ref(fig:sem)a), thereby increasing
+asynchrony. In turn, species richness, average trophic level and connectance had
+negative effects on the evenness of species variability (resp. $r_\delta$= `r rer`,
+`r ret`, and `r rect`), thereby downplaying the portfolio effect raised from
+species richness alone in a scenario of even species variabilities. In turn, we found
+that response diversity had a positive effect on evenness of species variability
+($r_\delta$=`r red`), thereby maximising the portfolio effect. We found
+that species response diversity had a strong positive effect on compensatory
+dynamics ($r_\delta$= `r rcd`), while average interaction strength had a small
+positive effect ($r_\delta$= `r rci`, Fig.
+\@ref(fig:sem)).
 
@@
 rsca <- get_eff(y = "stab_com", x = "async")
-#rscp <- get_eff(y = "stab_com", x = "pop_stab", tab = sem_eff_tab)
-#rsca <- get_eff(y = "stab_com", x = "async", tab = sem_eff_tab)
 
@@
 ras <- get_eff(y = "async", x = "sae_total")
-#rac <- get_eff(y = "async", x = "cpe")
-#ras <- get_eff(y = "async", x = "sae_total")
-
-#
-rav <- get_eff(y = "async", x = "cpe_env", tab = sem_eff_tab)
-rae <- get_eff(y = "async", x = "evenness_sae", tab = sem_eff_tab)
-
-rass <- get_eff(y = "async", x = "sae_even", tab = sem_eff_tab)
-rasi <- get_eff(y = "async", x = "cpe_int", tab = sem_eff_tab)
-```
-
-Population stability had a positive effect twice higher than asynchrony on the
-temporal stability of community (resp. $r_\delta$= `r rscp` and `r rsca`). In
-turn, asynchrony was equally driven by statistical averaging effects and
-compensatory dynamics (resp. $r_\delta$= `r rac` and `r ras`, Fig.
+
+```
+
+Overall, we found that population stability had a positive effect twice higher
+than asynchrony on the temporal stability of community (resp. $r_\delta$=
+`r rscp` and `r rsca`). In turn, asynchrony was more driven by compensatory
+dynamics than portfolio effects (resp. $r_\delta$= `r rac` and `r ras`, Fig.
 \@ref(fig:sem)a).
-
-```{r, eval = FALSE}
-semtot_cap <- "Total effect of food-web structure on community stability,
-asynchrony, and population stability. The total effects were derived from the
-structural equation model."
-```
-
-```{r semtot, eval = FALSE, fig.cap = semtot_cap, fig.id = "semtot"}
-knitr::include_graphics(here::here("report", "figures", "p_sem_tot_stab.png"))
-```
 
@@
 rtsz <- get_eff(y = "stab_com", x = "Z", effect_type = "total")
-rtsh <- get_eff(y = "stab_com", x = "h", effect_type = "total")
-rtsc <- get_eff(y = "stab_com", x = "ct_alive", effect_type = "total")
+rtsc <- get_eff(y = "stab_com", x = "c", effect_type = "total")
+rtsct <- get_eff(y = "stab_com", x = "ct_alive", effect_type = "total")
 rtsi <- get_eff(y = "stab_com", x = "avg_int_strength", effect_type = "total")
@@
 rtpt <- get_eff(y = "pop_stab", x = "w_avg_tlvl", effect_type = "total")
+rtpi <- get_eff(y = "pop_stab", x = "avg_int_strength", effect_type = "total")
 rtpz <- get_eff(y = "pop_stab", x = "Z", effect_type = "total")
-rtph <- get_eff(y = "pop_stab", x = "h", effect_type = "total")
-rtpc <- get_eff(y = "pop_stab", x = "ct_alive", effect_type = "total")
-rtpi <- get_eff(y = "pop_stab", x = "avg_int_strength", effect_type = "total")
+rtpc <- get_eff(y = "pop_stab", x = "c", effect_type = "total")
+rtpct <- get_eff(y = "pop_stab", x = "ct_alive", effect_type = "total")
 
@@
 rtat <- get_eff(y = "async", x = "w_avg_tlvl", effect_type = "total")
+rtai <- get_eff(y = "async", x = "avg_int_strength", effect_type = "total")
 rtaz <- get_eff(y = "async", x = "Z", effect_type = "total")
-rtah <- get_eff(y = "async", x = "h", effect_type = "total")
-rtac <- get_eff(y = "async", x = "ct_alive", effect_type = "total")
-rtai <- get_eff(y = "async", x = "avg_int_strength", effect_type = "total")
+rtac <- get_eff(y = "async", x = "c", effect_type = "total")
+rtact <- get_eff(y = "async", x = "ct_alive", effect_type = "total")
 ```
@@
 Deriving the sum of direct and indirect effects from the structural equation
-model, we show that both environmental stochasticity and response diversity among
-species had by far the most important effect on community stability (resp.
-$r_\delta$= `r rtsenv` and `r rtsdiv`, Fig. \@ref(fig:sem)b). Species richness
-had a low overall positive total effect on community stability (`r rtsr`)
-because its strong total positive effect on asynchrony (`r rtar`) was downplayed
-by its total negative effect on population stability (`r rtpr`) and that the
-weight of population stability on community stability is twice higher than the
-one of asynchrony. Average trophic level, type III functional response and
-predator prey mass ratio had positive effects on community stability in
-total (resp. `r rtst`, `r rtsh`, `r rtsz`, Fig. \@ref(fig:sem)b), driven by
-their positive effects on population stability that were weakly counterbalanced
-by their negative effects on asynchrony. In turn, connectance and average
-interaction strength had low total negative effects on community stability (resp.
-`r rtsc` and `r rtsi`, Fig. \@ref(fig:sem)b). While connectance had negative
-effects both on population stability and asynchrony, average interaction
-strength had a low total positive effect on population stability counterbalanced
-by a stronger negative effect on asynchrony.
+model, we show that both environmental stochasticity and species response
+diversity to environmental fluctuations had by far the most important effects on
+community stability (resp. $r_\delta$= `r rtsenv` and `r rtsdiv`, Fig.
+\@ref(fig:sem)b). Species richness had a overall positive total effect on
+community stability ($r_\delta$=`r rtsr`), steming from its strong total positive effect on
+asynchrony ($r_\delta$=`r rtar`) and downplayed by its small total negative effect on population
+stability ($r_\delta$=`r rtpr`), but the fact that population stability effect on community
+stability was twice higher than the one of asynchrony. Average trophic level and
+average interaction strength had small positive effects on community stability in
+total (resp. $r_\delta$=`r rtst`, `r rtsi`, Fig. \@ref(fig:sem)b), driven by their positive
+effects on population stability (resp. $r_\delta$=`r rtpt`, `r rtsi`). However,
+we found that average trophic level had a negative total effect on asynchrony
+($r_\delta$=`r rtat`), average interaction strength had a positive total effect
+($r_\delta$=`r rtai`). In turn, connectance had a small negative total effect on
+community stability ($r_\delta$=`r rtsct`), raising from a negative total effect
+on population stability ($r_\delta$=`r rtpct`) and a positive one on asynchrony
+($r_\delta$=`r rtact`, Fig. \@ref(fig:sem)b).
 
@@
 pv <- default_variable_values_pred
+
 pv_cap <- paste0(
-  "connectance = ", pv["ct_alive"],
-  ", average interaction strength = ", pv["avg_int_strength"],
-  ", average trophic level = ", pv["w_avg_tlvl"],
-  ", hill exponent = ", pv["h"],
-  ", Predator-Prey Mass Ration = ", pv["Z"],
-  ", response diversity = ", pv["resp_div"],
-  ", and environmental stochasticity = ", pv["env_stoch"]
+  "connectance = ", round(pv["ct_alive"], 2),
+  ", average interaction strength = ", round(pv["avg_int_strength"], 3),
+  ", average trophic level = ", round(pv["w_avg_tlvl"], 2),
+  ", predator interference = ", round(pv["c"], 1),
+  ", Predator-Prey Mass Ratio = ", round(pv["Z"]),
+  ", and environmental stochasticity = ", round(pv["env_stoch"], 1)
 
 )
-pred_cap <- paste0("Relationship between community stability and species
-  richness according to food-web structure and response diversity. a,
-  Predictions of the statistical model linking the temporal stability of
-  community biomass and species richness. The values chosen for high/low
-  response diversity and food-web structure are indicated by the black point in
-  (b). Lines display the mean predictions of the model, ribbons display the
-  confidence intervals at 95\\% (to recheck). b, Diagrams displaying the slope
-  coefficients of the effect of species richness on community stability. Default
-  parameter values for the predictions: ", pv_cap, ".") %>%
+pred_cap <- paste0("Slope of the community stability - species
+  richness relationship according to food-web structure and response diversity. (a),
+  Diagrams displaying the slope coefficients of the effect of species richness
+  on community stability. The average values of the control variables were used
+  to generate the predictions: ", pv_cap, ". (b, c): Examples of predictions
+  from the model for two combinations of average trophic level and response
+  diversity (values displayed in panel (a)). Lines display the mean predictions
+  of the model. The coefficients of the linear model are displayed in Fig. S4.
+  Relationships between population stability, asynchrony and species richness
+  are displayed in Fig. S5."
+  ) %>%
   str_replace_all("\\s+", " ")
@@
 ```{r pred, fig.cap = pred_cap, fig.id = "pred"}
-knitr::include_graphics(here("report", "figures", "p_pred_sr.pdf"))
+knitr::include_graphics(here("report", "figures", "p_fig3.pdf"))
 ```
@@
 interaction strength, average trophic level or connectance (Fig.
-\@ref(fig:pred)). Furthermore, we found that higher response diversity increased
-community stability in average (Fig. \@ref(fig:pred)a). Surprisingly, despite
-the relatively small effects of food-web structure on overall community
-stability (Fig. \@ref(fig:sem)c \@ref(fig:pred)a), we found that response
-diversity dramatically change the shape of the community stability-species
-richness relationship from positive to negative when response diversity is low
-(Fig. \@ref(fig:pred)b).
+\@ref(fig:pred)a). Surprisingly, despite the relatively small effects of
+food-web structure on overall community stability (Fig. \@ref(fig:sem)b), we
+found that response diversity dramatically change the shape of the community
+stability-species richness relationship from positive to negative when response
+diversity is low (Fig. \@ref(fig:pred)b).
 
@@
 
+One of the key question in Ecology is what drive temporal stability in complex
+communities?, especially in food-webs. We provide an answer to that question by
+investigating how the structure of complex food-webs affects the temporal
+stability of ecological communities using a bioenergetic model. We added
+environmental stochasticity to this model and modulated the species response
+diversity, i.e. the capacity of species to answer differently to environmental
+fluctuations. We found that that food-web structure, apart from species richness,
+had little effects on overall stability. However we found that the interplay
+between food-web structure and response diversity was critical to determine
+positive or negative relationships between community stability and species
+richness.
+
 ## Food-web structure and stressors affects population stability and asynchrony
@@
 by population stability rather than synchrony, confirming previous results in
-empirical fish communities [@danet_species_2021], which contrasts with empirical
-data in birds and bats assemblages that reported an equivalent influence of
-population stability and asynchrony on community stability
-[@olivier_urbanization_2020]. Although the number of empirical and theoretical
-studies is still limited to compare the respective contribution of asynchrony and
-population stability to community stability in competitive assemblages and
-food-webs, we suggest two non-exclusive and complementary explanations that
-might drive a lower contribution of asynchrony in food-webs compared to
-competitive assemblages. First, the range of bodymasses is much higher in
-food-webs, which typically include species that differ in bodymass by several orders of
-magnitude [@brose_predator_2019], which in turn creates highly uneven biomass
+empirical fish communities [@danet_species_2021] and theoretical models
+[@eschenbrenner_diversity_2023], which contrasts with empirical data in birds
+and bats assemblages that reported an equivalent influence of population
+stability and asynchrony on community stability [@olivier_urbanization_2020].
+Although the number of empirical and theoretical studies is still limited to
+compare the respective contribution of asynchrony and population stability to
+community stability in single-trophic assemblages and food-webs, we suggest two
+non-exclusive and complementary explanations that might drive a lower
+contribution of asynchrony in food-webs compared to single-trophic assemblages.
+First, the range of bodymasses is much higher in food-webs, which typically
+include species that differ in bodymass by several orders of magnitude
+[@brose_predator_2019], which in turn creates highly uneven biomass
 distribution, thereby creating uneven contributions of species to asynchrony
@@
 interdependence among species, which in turn limits the raise of independent
-fluctuations (i.e. portfolio effects, but rise compensatory dynamics). The question of
-which mechanisms and community features drive differences in the
-contribution of asynchrony and population stability in food-webs and competitive
-assemblages is still an open question that might be crucial to accurately
-address diagnostics and conservation issues. On top of food-web structure,
-we found that environmental stochasticity and environmental correlation among
-species were the main drivers of community stability, suggesting that stressors
-are the main drivers of temporal stability. This result is in accordance with previous
-studies showing strong effects on environmental stochasticity
-[@vasseur_environmental_2007] and the loss of response diversity decrease
-community stability in tri-trophic food-webs [@ives_stability_2000;
+fluctuations (i.e. portfolio effects, but rise compensatory dynamics). The fact
+that that compensatory dynamics had stronger effects on asynchrony than
+portfolio effects, in contrast with findings in experimental grasslands
+[@zhao_biodiversity_2022], lends toward this interpretation. The question of
+which mechanisms and community features drive differences in the contribution of
+asynchrony and population stability in food-webs and single-trophic assemblages
+is still an open question that might be crucial to accurately address
+diagnostics and conservation issues. On top of food-web structure, we found that
+environmental stochasticity and environmental correlation among species were the
+main drivers of community stability, suggesting that stressors are the main
+drivers of temporal stability. This result is in accordance with previous
+studies showing strong effects of environmental stochasticity
+[@vasseur_environmental_2007] and of the loss of response diversity community
+stability in tri-trophic food-webs [@ives_stability_2000;
 @thebault_trophic_2005].
@@
 [@danet_species_2021] empirical results. Higher average trophic level can
-stabilise populations because higher predators are themselves more stable due
-to lower mortality rates with in turn makes them less sensible stochastic
+stabilise populations because higher predators are themselves more stable due to
+lower mortality rates with in turn makes them less sensible stochastic
 perturbation and because they control the amplitude of the fluctuations of their
-preys [@shanafelt_stability_2018, we can test that?]. In turn, we found that
-average trophic level decreases strongly asynchrony through a negative effect on
-statistical averaging effect. Further analysis showed that average trophic level
-limited statistical averaging effect by decreasing the evenness of biomass
-variability. It is linked to the model assumption that species of higher trophic
-level have a lower overall mortality rates, similarly to previous studies
-[@vasseur_environmental_2007], thereby increasing average population stability and simultaneously
-synchronising populations. The fact that Predator Size Mass Ratio displays the same
-effect, thereby building food-webs with bigger species having lower mortality
-rates, further lends toward this hypothesis. Furthermore, average omnivory was
-strongly correlated with average trophic level, suggesting that average omnivory
-also stabilise population stability, in line with previous theoretical results
-in small modules [@mccann_reevaluating_1997]. Our results further suggest that
-higher average trophic level results in lower compensatory dynamics raising from
-species interactions. It might be explained by the fact that average trophic
-level is strongly associated with average omnivory, which might tamper
-synchronized predator-prey oscillations that can raise compensatory dynamics
-[@mccann_reevaluating_1997].
+preys [@shanafelt_stability_2018]. Additional simulations with equal mortality
+rates for all species suggest a prevalence of the former explanation (Fig. S1).
+In turn, we found that average trophic level decreases strongly asynchrony
+through a negative effect on portfolio effects, by decreasing the evenness of
+biomass variability. It is linked to the model assumption that species of higher
+trophic levels have lower overall mortality rates, similarly to previous
+studies [@vasseur_environmental_2007], thereby increasing average population
+stability and simultaneously synchronising populations. Furthermore, average
+omnivory was strongly correlated with average trophic level (Fig. S2),
+suggesting that average omnivory also stabilise population stability, in line
+with previous theoretical results in small modules [@mccann_reevaluating_1997].
+Our results further suggest that higher average trophic level results in lower
+compensatory dynamics raising from species interactions, this results could be
+related by the fact that average trophic level is strongly associated with
+average omnivory, which might tamper synchronized predator-prey oscillations
+that can raise compensatory dynamics [@mccann_reevaluating_1997].
 
@@
 which has been reported to be negative, positive or neutral in previous studies
-[@ruijven_contrasting_2007; @houlahan_negative_2018]. [interpretation?].
-However, species richness had a strong positive on asynchrony, by raising
-statistical averaging effects. This result is common in empirical systems
-[@tilman_biodiversity_2006; @olivier_urbanization_2020], but strongly depends on
+[@ruijven_contrasting_2007; @houlahan_negative_2018]. However, species richness
+had a strong positive on asynchrony, by raising portfolio effects.
+This result is common in empirical systems [@tilman_biodiversity_2006;
+@olivier_urbanization_2020; @zhao_biodiversity_2022], but strongly depends on
 the presence of response diversity [@loreau_species_2008;
 @thibaut_understanding_2013; @zhao_biodiversity_2022]. Connectance, quantifying
-the generalism in food-webs, had negative effects on both asynchrony and population
-stability. We further found that higher connectance leaded to less even biomass
-variability, thereby limiting the raise of the portfolio effects, and leaded to
-lower compensatory dynamics due to species interactions. This result is in
-accordance with empirical findings that a generalist predator can indeed
-synchronises the dynamics of a large number of preys
-[@raimondo_interspecific_2004]. [No idea about connectance decreasing population
-stability]. However, the overall effect of connectance on overall stability was
-quite low, similarly to previous empirical findings [@danet_species_2021], but
-in apparent disagreement with the predominant role of connectance on stability
-in theoretical studies [complexity-stability paradox, @may_will_1972].
+the generalism in food-webs, had small negative effects population
+stability but small positive on asynchrony. We further found that higher connectance
+leaded to less even biomass variability, thereby limiting the raise of the
+portfolio effects, and leaded to lower compensatory dynamics due to species
+interactions (Table. S4). This result is in accordance with empirical findings
+that a generalist predator can indeed synchronises the dynamics of a large
+number of preys [@raimondo_interspecific_2004], thereby potentially limiting compensatory
+dynamics raising from species interactions. However, the overall effect of
+connectance on overall stability was quite low, similarly to previous empirical
+findings [@danet_species_2021], but in apparent disagreement with the
+predominant role of connectance on stability in theoretical studies
+[complexity-stability paradox, @may_will_1972].
+
+```{r, eval = FALSE}
+tar_load(sem_simplified_eff_tab)
+sem_simplified_eff_tab %>%
+  filter(effect_type == "total") %>%
+  print(n = 100)
+```
 
@@
 
-Food-web dynamical features, the type of functional response (from II to III) and average
-interaction strength, also had an effect on community stability. Our results
-confirm the stabilising effect of the functional response of type III on
-populations [@uszko_effects_2017; @brose_allometric_2006]. Compared to type II,
-functional response of type III models a decrease of the feeding rates of
-consumers when their preys have a low biomass which leads to a less dramatic
-fluctuation of prey biomass. Furthermore, we found that functional response of
-type III decreased asynchrony by decreasing compensatory dynamics due to species
-interactions. This effect might be due to prey switching of consumers when one of
-them reach low abundance [@mccann_diversitystability_2000]. Average interaction
-strength, as connectance, had overall little effect on community stability.
-Average interaction strength was found to decrease asynchrony by decreasing the
-evenness of biomass variability, thereby decreasing portfolio effects,
-despite having a small positive effect on compensatory dynamics. In turn, we
-surprisingly found that average interaction strength had little effects on
-population stability, which contrasts with the importance of this parameter in
-complexity-stability relationship [@may_will_1972].
+Predator interference, taken in this study as a control variable, had also a
+strong effects on community stability. Our results confirm the stabilising
+effect of self-limiting processes on populations [@uszko_effects_2017;
+@brose_allometric_2006]. Furthermore, we found that predator interference
+decreased asynchrony by strongly decreasing compensatory effects due to species
+interactions. Predator interference models a decrease of the feeding rates of
+consumers when predator biomass increases which might lead to a less dramatic
+fluctuation of prey biomass. All toghether, this result suggest that
+self-limitation mechanisms that increase population stability might in turn have
+opposite effect on asynchrony, and that it is the balance between the two
+effects weighted by the relative importance of population stability and
+asynchrony that will determine the overall effect on community stability.
 
@@
 richness. The reason is that the strength of environmental stochasticity mainly
-affect population stability and less asynchrony, the latter being the driver of
-species-richness relationships [@ives_stability_2000; @thebault_trophic_2005;
-@thibaut_understanding_2013]. Average interaction strength and connectance that
-were found to have little effects on overall stability, were found to have a
-strong effect on stability-richness relationships. This result is in accordance
-with the complexity-stability theory that predicts that community stability
-(i.e. measured as the dominant eigen value of the jacobian matrix) should
-decrease as the community is species diverse, has higher connectance, and
-higher interaction strength [@may_will_1972]. However, we found that the
-negative effects of complexity on stability-richness relationship are cancelled
-when response diversity is high. An interpretation is that environmental
-stochasticity itself does not override the negative complexity-stability
-relationships, but it the presence of response diversity and resulting
+affect population stability and less asynchrony, asynchrony being the driver of
+species-richness relationships [@ives_stability_2000; @tilman_biodiversity_2006; @loreau_species_2008;
+@thibaut_understanding_2013; @zhao_biodiversity_2022]. Average interaction
+strength and connectance that were found to have little effects on overall
+stability, were found to have a strong effect on stability-richness
+relationships. This result is in accordance with the complexity-stability theory
+that predicts that community stability (i.e. measured as the dominant eigen
+value of the jacobian matrix) should decrease as the community is species
+diverse, has higher connectance, and higher interaction strength
+[@may_will_1972]. However, we found that the negative effects of complexity on
+stability-richness relationship are cancelled when response diversity is high.
+An possible explanation is the presence of response diversity and resulting
 asynchrony in species fluctuations which overrides the negative effects of
-complexity on stability-richness relationships. Response diversity might then be one
-mechanism that explains why so much positive relationship between stability and
-species richness are found in empirical settings while food-web theoretical
-model that do not often include environmental stochasticity and response
-diversity finds negative complexity stability relationships
+complexity on stability-richness relationships. Response diversity might then be
+one mechanism that explains why positive relationship between stability
+and species richness are so prevalent in empirical settings while food-web
+theoretical model that do not often include environmental stochasticity and
+response diversity finds negative complexity stability relationships
 [@ives_stability_2007].
@@
 stability and its partition into population stability and asynchrony in complex
-food-webs, added to two pressing stressors in the context of global change, the
-strength of environmental variability and the level of response diversity of
+communities, added to two pressing stressors in the context of global change,
+the strength of environmental variability and the level of response diversity of
 species facing this environmental variability. Our results confirm the results
-of previous theoretical models modelling small food-web modules or food-chain,
+of previous theoretical models modelling small food-web modules or food-chains,
 as we report that average trophic level, omnivory, predator-prey size ratio, and
-functional response of type III increase temporal community stability by
-stabilising population fluctuations. In turn, our study confirm that species
-richness increase temporal community stability by increasing asynchrony due to
-portfolio effects and thanks to response diversity. Our study reports that
-connectance and average interaction strength have little effects on overall
-community stability while they have a strong effect on the sign of the community
-stability-richness relationship, in accordance with the complexity-stability
-paradox, but only in the absence of response diversity. Overall, it suggests that
-high response diversity of species facing environmental stochasticity, on top of
-being the essential ingredient driving positive stability-richness relationship,
-also cancel the negative effects of food-web complexity on stability-richness
-relationship.
-
-Our results highlight that population stability is the primary driver of
-community stability. In the context of global changes in which environmental
-variability is expected to increase tremendously, we expect to see a strong
-decrease in community stability, despite high response diversity. But ongoing
-biotic homogenization [@olden_homogocene_2018; @muthukrishnan_invasive_2020;
-@wang_biotic_2021] is also suggested to decrease response diversity
-[@wang_biotic_2021; @su_human_2021], which in turn is expected to further
-decrease stability despite high species richness, even more in complex food-webs
-having high interaction strength, high connectance and high average trophic
-level. Then, the results of our study reinforces that the restoration of
-ecosystems along with a restoration of landscape complexity that provides
-refuges from extreme environmental changes will be key to maintain temporal stability of
+predator interference increase temporal community stability by stabilising
+population fluctuations. In turn, our study confirm that species richness
+increase temporal community stability by increasing asynchrony due to portfolio
+effects and thanks to response diversity. Our study reports that connectance and
+average interaction strength have little effects on overall community stability
+while they have a strong effect on the sign of the community stability-richness
+relationship, in accordance with the complexity-stability paradox, modulated by
+response diversity. Overall, it suggests that high response diversity of species
+facing environmental stochasticity, on top of being the essential ingredient
+driving positive stability-richness relationship, also exceeds the negative
+effects of food-web complexity on stability-richness relationship.
+
+Our results highlight that the strength of environmental fluctuations is the
+primary driver of community stability. In the context of global changes in which
+environmental variability is expected to increase tremendously, our study
+suggests a strong decrease in community stability, despite high response
+diversity and response diversity. But ongoing biotic homogenization
+[@olden_homogocene_2018; @muthukrishnan_invasive_2020; @wang_biotic_2021] is
+also suggested to decrease response diversity [@wang_biotic_2021;
+@su_human_2021], which in turn is expected to further decrease stability despite
+high species richness, even more in complex food-webs having high interaction
+strength, high connectance and high average trophic level. Then, the results of
+our study reinforce that the idea that restoration of ecosystems along with a
+restoration of landscape complexity that provides refuges from extreme
+environmental fluctuations will be key to maintain temporal stability of
 ecological communities in the coming decades [@ryser_landscape_2021].

### 2024-04-04 paper/supplementary_figures.Rmd
Update manuscript and supplementary figures

---
title: "Supplementary information"
subtitle: ""
author: ""
date: ""
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    keep_tex: true
    spacing: double
    number_sections: false
  officedown::rdocx_document:
bibliography: "bibliography.bib"
link-citations: true
toc: false
linestretch: 2.0
header-includes:
  - \usepackage{float}
  - \renewcommand{\thefigure}{S\arabic{figure}}
  - \renewcommand{\thetable}{S\arabic{table}}
---

```{r setup, include=FALSE}
library(tidyverse)
library(magrittr)
library(rmarkdown)
library(officedown)
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      comment = "#>",
                      fig.path = "graphics/knitr-",
                      fig.retina = 1.618, # Control using dpi
                      fig.width = 6,  # generated images
                      fig.pos = "H",  # pdf mode
                      #fig.align = "center",
                      dpi = if (knitr::is_latex_output()) 72 else 300,
                      out.width = "100%",
                      dev = "png",
                      dev.args = list(png = list(type = "cairo-png")),
                      optipng = "-o1 -quiet")

library(here)
library(cowplot)
library(targets)
library(kableExtra)
library(coda)
library(ggbreak)

sapply(list.files(here("R"), full.names = TRUE), source)
if (Sys.info()["login"] == "alain") {
  file.copy(
    from = "~/Documents/post-these/references.bib",
    to = here("paper", "bibliography.bib"),
    overwrite = TRUE
  )
}
```

# Figures

(ref:sem-sens-cap) Total standardised effects for the sem displayed in main text
according to different simulation set-ups. Default: simulations used in main
text; Fixed death rate: non-allometric death rate, meaning that all species have
the same death rate, here $d = 0.1$; K not standardised: carrying capacity not
standardised; rebuild FW after removing disconnected species: instead of setting
starting biomass of disconnected species to 0, we removed them from the
food-webs, and then recompute species trophic level, species bodymass and then
their metabolic rates, prey preferences, producer carrying capacity.

```{r p-sem-sensibility, fig.cap="(ref:sem-sens-cap)"}
knitr::include_graphics(here("report", "figures", "p_sem_main_text_eff_tab_tot.pdf"))
```

(ref:cor-cap) Spearman's correlation coeffients among stability components,
food-web structure, and model parameters.

```{r p-cor, fig.cap="(ref:cor-cap)"}
knitr::include_graphics(here("report", "figures", "p_cor.pdf"))
```

(ref:dharma-lm-cap) Distribution of residuals for the linear models predicting the
relationship between community stability and species richness (Fig. 3). a,b,c
for respectively community stability, population stabilty and asynchrony. Left
panels display the distribution of the quantiles, and indicate that residuals
are quite well distributed. Right panels display the scaled residuals versus the
predicted values. The slight U-shape might indicate the lack of a polynomial
term in the model, but overall the model looks to have appropriate fitting.

```{r dharma-lm, fig.cap="(ref:dharma-lm-cap)"}
knitr::include_graphics(here("report", "figures", "p_diagnotisc_model_fw_stab_comp.jpg"))
```

(ref:coeff-lm-cap) Standardised coefficients for the linear model predicting the
relationship between community stability and species richness (Fig. 3).

```{r coeff-lm, fig.cap="(ref:coeff-lm-cap)"}
knitr::include_graphics(here("report", "figures", "p_model_fw_stab_comp_scaled_coeff.pdf"))
```

```{r}
tar_load(default_variable_values_pred)
pv <- default_variable_values_pred

pv_cap <- paste0(
  "connectance = ", round(pv["ct_alive"], 2),
  ", average interaction strength = ", round(pv["avg_int_strength"], 3),
  ", average trophic level = ", round(pv["w_avg_tlvl"], 2),
  ", predator interference = ", round(pv["c"], 1),
  ", Predator-Prey Mass Ratio = ", round(pv["Z"]),
  ", and environmental stochasticity = ", round(pv["env_stoch"], 1)
)

p_pred_stab_comp_rho_cap <- paste0("Prediction of the statistical model linking
  the temporal stability of community biomass and species richness. Compared to
  Fig.3, we added the prediction of the slope of the relation population
  stability-species richness and asynchrony-species richness. Default
  parameter values: ", pv_cap,
  ".") %>%
str_replace_all("\\s+", " ")
```

```{r stab-comp-pred, fig.cap = p_pred_stab_comp_rho_cap}
knitr::include_graphics(here("report", "figures", "p_pred_sr_resp_div_supp.pdf"))
```

\pagebreak

# Table

```{r}
tar_read(tab_sem_vif) %>%
  kable(booktabs = TRUE,
    format = "latex",
    caption = "Variance Inflation Factors for the Structural Equation Model
    displayed in main text (Fig. 2). All VIF were inferior to 3, indicating low
    multicollinearity.",
    label = "sem-vif"
    ) %>%
  column_spec(1, bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major", valign = "middle") %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

```{r}
tar_read(tab_model_fw_stab_comp_wo_int_vif) %>%
  kable(booktabs = TRUE,
    format = "latex",
    caption = "Variance Inflation Factors for the linear model predicting the
    relationship between community stability and species richness (Fig. 3). All
    VIF were inferior to 3, indicating low multicollinearity.",
    label = "lm-vif"
    ) %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

```{r}
tar_read(tab_sem_coeff) %>%
  kable(booktabs = TRUE,
    format = "latex",
    caption = "Standardised estimates from the Structural Equation Model
    displayed in main text (Fig. 2).",
    label = "sem-coeff"
    ) %>%
collapse_rows(columns = 1, latex_hline = "major", valign = "middle") %>%
kable_styling(latex_options = c("striped", "hold_position"))
```

```{r}
tar_read(tab_sem_simplified_eff) %>%
  kable(booktabs = TRUE,
    format = "latex",
    caption = "Standardised estimates from the supplementary Structural Equation
    Model which includes the partition of compensatory effects rising from
    environmental fluctuations and species interactions.",
    label = "sem-supp-coeff") %>%
collapse_rows(columns = 1, latex_hline = "major", valign = "middle") %>%
kable_styling(latex_options = c("striped", "hold_position"))
```

### 2024-04-04 R/string_replacements.R

@@ -99,11 +99,10 @@ latex_symbol_replacement <- function() {
 
 sim_type_replacement <- function() {
   c(
-    "no_rerun" = "Default (5000 timesteps)",
-    "rerun" = "Until no extinction",
-    "non_allo_no_rerun" = "Fixed death rate",
-    "no_rerun_short" = "2000 timesteps",
-    "no_rerun_no_disconnected" = "Disconnected species not removed"
+    "rerun" = "Default",
+    "non_allo" = "Fixed death rate",
+    "kno" = "K not standardised",
+    "rebuild" = "rebuild FW after removing\n disconnected species"
   )
 
 }

### 2024-04-06 _targets.Rmd
Update manuscript and supplementary material

@@
 
+```{r, eval = FALSE}
+tar_load(sim_param)
+```
+
 ```{targets}
@@
   tar_target(sim_param, {readRDS(sim_param_file)}),
+  tar_target(param_comb_nb,
+    sim_param %>%
+      group_by(Z, rho, env_stoch, c, S) %>%
+      summarise(n = n())
+  ),
   tar_target(sim_param_tab,
@@
           )) %>%
-      filter(!Parameter %in% c("sim_id", "fw_id", "rho")) %>%
+      filter(!Parameter %in% c("sim_id", "fw_id", "rho", "rep")) %>%
       select(Parameter, Values) %>%
-      mutate(Parameter = recode_factor(Parameter, !!!var_replacement()))
+      mutate(
+        parameter_name = parameter_name_replacement()[Parameter],
+        Parameter = latex_symbol_replacement()[Parameter],
+        Parameter = paste0(parameter_name, " (", surround_latex_math(Parameter), ")")
+        ) %>%
+      select(-parameter_name)
   ),
@@
     tibble(
-      c = 0,
+      h = 2,
       B0 = 0.5,
@@
   mutate(
+    parameter_name = parameter_name_replacement()[Parameter],
     Parameter = latex_symbol_replacement()[Parameter],
-        Parameter = surround_latex_math(Parameter)
+    Parameter = paste0(parameter_name, " (", surround_latex_math(Parameter), ")")
     ) %>%
+  select(-parameter_name) %>%
   bind_rows(tab_sim_param)
@@
 )
+```
+
+```{r}
+
 ```
@@
 tar_load(sim_param_tab)
+tar_load(sim_param)
 tar_load(tab_sim_param)
@@
 kable(param_table, "html", booktabs = T, escape = FALSE) %>%
+  kable_styling()
+tar_load(c(fix_parameter, allometric_parameter, tab_sim_param))
+ti <- fix_parameter %>%
+  bind_cols(allometric_parameter) %>%
+  mutate(across(where(is.list), ~map_chr(.x, function(x) paste_named_vector(x)))) %>%
+  mutate(across(where(is.double), ~as.character(.x))) %>%
+  pivot_longer(everything(), names_to = "Parameter", values_to = "Values") %>%
+  mutate(
+    parameter_name = parameter_name_replacement()[Parameter],
+    Parameter = latex_symbol_replacement()[Parameter],
+    Parameter = paste0(parameter_name, " (", surround_latex_math(Parameter), ")")
+    ) %>%
+  select(-parameter_name) %>%
+  bind_rows(tab_sim_param)
+ti %>%
+  kable("html", booktabs = T, escape = FALSE) %>%
   kable_styling()

### 2024-04-06 paper/manuscript.Rmd
Update manuscript and supplementary material

@@
 
-# Abstract
-
-Empirical and theoretical evidence suggests that current and projected
-environmental changes and biotic homogenisation will dramatically destabilise
-ecological communities. However, this evidence is largely based on
-oversimplified communities (i.e. food chains, guild assemblages), which lack the
-complexity of natural communities.We characterise the dynamics of complex
-food-webs under a stochastic bioenergetic food-web model, and investigate how
-response diversity, environmental stochasticity, and food-web structure drive
-temporal stability. We found that higher average trophic level, omnivory degree
-and generalism increased average population stability, but decreased asynchrony,
-triggering compensatory dynamics that raised trophic interactions.  Species
-richness had little effect on average population stability, but a large one on
-synchrony. Further, when response diversity is low, high interaction strength,
-average trophic level, and connectance all lead to negative stability-species
-richness relationships, but when response diversity is high, we observe positive
-stability-species richness relationships regardless of the food-web structure.
-Our study reveals that response diversity and food-web structure drive temporal
-stability and further improve our understanding of biodiversity-stability
-relationships in complex trophic communities.
+# Abstract (150/150 words)
+
+Empirical and theoretical evidence suggests environmental changes will
+dramatically destabilise ecological communities. However, this evidence is
+largely based on oversimplified communities, which lack the complexity of
+natural communities. We characterise the dynamics of complex food-webs under a
+stochastic food-web model, and investigate how response diversity,
+stochasticity, and food-web structure drive temporal stability. We found that
+higher average trophic level increased community stability by increasing
+population stability, at the expense of asynchrony. Species richness had little
+effect on population stability, but a large one on asynchrony. Interaction
+strength and connectance had little effects on temporal stability overall, but
+interacted strongly with response diversity to determine stability-richness
+relationships. Absence of response diversity all leaded to negative
+stability-richness relationships, but high response diversity resulted in high
+prevalence of positive stability-richness relationships. Our study reveals that
+response diversity and food-web structure drive temporal stability overall, and
+together determine the sign of the stability-richness relationship.
 
@@
 possible to partition asynchrony into two component sources: the portfolio
-effects (rising from statistical averaging effects, SAE) and the compensatory
-dynamics effect (CPE) [@zhao_biodiversity_2022]. Portfolio effects stem from the
-statistical averaging of independent population fluctuations [@doak_statistical_1998;
-@zhao_biodiversity_2022], thereby increasing asynchrony. Compensatory dynamics
-in turn capture population fluctuations that are more synchronous or
-asynchronous than expected for independent fluctuations, and can stem from
-species interactions and species responses to perturbations [@zhao_biodiversity_2022].
-This allows an unprecedented opportunity to obtain mechanistic insight about the
-effects of stressors and food-web structure on stability in complex, species
-rich communities.
+and the compensatory dynamics effects [@zhao_biodiversity_2022]. Portfolio
+effects stem from the statistical averaging of independent population
+fluctuations [@doak_statistical_1998; @zhao_biodiversity_2022], thereby
+increasing asynchrony. Compensatory dynamics in turn capture population
+fluctuations that are more synchronous or asynchronous than expected for
+independent fluctuations, and can stem from species interactions and species
+responses to perturbations [@zhao_biodiversity_2022]. This allows an
+unprecedented opportunity to obtain mechanistic insight about the effects of
+stressors and food-web structure on stability in complex, species rich
+communities.
 
@@
 ratio (upper and bottom panels), low and high species richness (left and right
-  panels). The food-web are displayed on the side with the node size
+  panels). The food-webs are displayed on the side with the node size
 being proportional to the average species biomass across the simulation. We
@@
 simulations, $h = 2$, $\\sigma_e = .3$. Low and high response diversity were
-respectively $\\rho = 1$ and $\\rho = 0$. Low and high PPMR were respectively 1 and 100." %>%
+respectively $\\rho = 1$ and $\\rho = 0$. Low and high PPMR were respectively 1
+and 100." %>%
 str_replace_all("\\s+", " ")
@@
 
-(ref:eq-rho) (eq. \@ref(eq:rho))
-
-```{r}
-tar_read(tab_sim_param) %>%
-  kable(
-    booktabs = TRUE,
-    caption = "Parameter values used in the simulation experiment. Numbers
-    between squared brackets display all the values. Two numbers between
-    brackets are the minimum and maximal values, N being the number of unique
-    values. PPMR: Predator Prey Mass Ratio. We defined response diversity as \\protect$1-\\rho$
-    (ref:eq-rho).",
-    label = "param") %>%
-  kable_styling(latex_options = c("striped", "hold_position"))
-```
-
 We generated food-web structure using the niche model [@williams_simple_2000]
 with an initial species richness from $`r pS["min"]`$ to $`r pS["max"]`$, and
-connectance from $`r pct["min"]`$ to $`r pct["max"]`$ (Table
-\@ref(tab:param)). We generated food-webs without cannibalistic links and
-discarded food-webs that contained disconnected species.
+connectance from $`r pct["min"]`$ to $`r pct["max"]`$ (Table S1). We generated
+food-webs without cannibalistic links and discarded food-webs that contained
+disconnected species.
 
@@
 We set $h = 2$, i.e. a functional response of type III (eq. \@ref(eq:holling)),
-and varied predator interference (i.e. from $c = `r pc["min"]`$ to $c = `r
-pc["max"]`$, eq. \@ref(eq:holling)), as predator interference was shown to have
-a tremendous role on population stability [@brose_allometric_2006]. We set a global
-carrying capacity of $K' = 10$ to ensure that consumers were not
+and varied predator interference (i.e. from $c = `r pc["min"]`$ to
+$c = `r pc["max"]`$, eq. \@ref(eq:holling)), as predator interference was shown
+to have a tremendous role on population stability [@brose_allometric_2006]. We
+set a global carrying capacity of $K' = 10$ to ensure that consumers were not
 limited by the biomass input from primary producers. We standardised the
@@
 re-run the simulation for another 1000 timesteps. Except in the case of
-disconnected species, we re-ran simulations with species starting biomass equals
+disconnected species, we re-ran simulations with species starting biomass equal
 to their biomass at the last timestep of the previous simulation. Supplementary
@@
 compensatory effects). Grounded in theoretical ecology, we expected that higher
-average trophic level lower interaction strength, lower connectance[@mccann_weak_1998;
+average trophic level, lower interaction strength, lower connectance[@mccann_weak_1998;
 @mccann_reevaluating_1997; @shanafelt_stability_2018]. We further added
@@
 equation model presented low multicollinearity (Variance Inflation
-Factor < 3, Table S1), altough interaction strength and species richness were
+Factor < 3, Table S2), although interaction strength and species richness were
 highly correlated (Fig. S2). The structural equation model using the R package
 `PiecewiseSEM` [@lefcheck_piecewisesem_2016]. We then bootstrapped (N = 100) the
-SEM to obtain confidence interval on the estimated effects and computed the sum
+SEM to obtain confidence intervals on the estimated effects and computed the sum
 of the direct and indirect effects using `semEff` R package
@@
 variables were set to the values indicated in the Fig. \@ref(fig:pred). The VIF
-were inferior to 3, indicating low multicollinearity (Table S2), we checked the
+were inferior to 3, indicating low multicollinearity (Table S3), we checked the
 distribution of the residuals (Fig. S3) using `DHARMa` R package. The model was
@@
 sem_cap <- paste0(
-  "Structural Equation Model food-web struture and stressors to temporal
-  stability of community biomass. (a) Continuous red arrows display positive and
+  "Structural Equation Model linking food-web structure and stressors to temporal
+  stability of community biomass. a, continuous red arrows display positive and
   dashed blue arrows display negative standardised effects, width of the arrows
@@
   displayed. The full table of coefficients including control variables is
-  displayed in Table S3. A more complete SEM containing further partition of
-  compensatory effects and control variables is displayed in Table S4. (b) Total
-  effect of food-web structure on community stability, asynchrony, and
+  displayed in Table S4. A more complete SEM containing further partition of
+  compensatory effects and control variables is displayed in Table S5. b, total
+  effects of food-web structure on community stability, asynchrony, and
   population stability. N = ", nrow(tar_read(sim_fw)), " simulations.") %>%
@@
 
-We found that food-web structure had significant effect on temporal population
+We found that food-web structure had significant effects on temporal population
 stability such as average trophic level increase population stability (resp.
@@
 dynamics ($r_\delta$= `r rcd`), while average interaction strength had a small
-positive effect ($r_\delta$= `r rci`, Fig.
-\@ref(fig:sem)).
+positive effect ($r_\delta$= `r rci`, Fig. \@ref(fig:sem)).
 
@@
 \@ref(fig:sem)b). Species richness had a overall positive total effect on
-community stability ($r_\delta$=`r rtsr`), steming from its strong total positive effect on
+community stability ($r_\delta$=`r rtsr`), stemming from its strong total positive effect on
 asynchrony ($r_\delta$=`r rtar`) and downplayed by its small total negative effect on population
-stability ($r_\delta$=`r rtpr`), but the fact that population stability effect on community
+stability ($r_\delta$=`r rtpr`), but population stability effect on community
 stability was twice higher than the one of asynchrony. Average trophic level and
@@
 
-One of the key question in Ecology is what drive temporal stability in complex
+One of the key questions in Ecology is what drives temporal stability in complex
 communities?, especially in food-webs. We provide an answer to that question by
@@
 diversity, i.e. the capacity of species to answer differently to environmental
-fluctuations. We found that that food-web structure, apart from species richness,
+fluctuations. We found that food-web structure, apart from species richness,
 had little effects on overall stability. However we found that the interplay
@@
 stabilise populations because higher predators are themselves more stable due to
-lower mortality rates with in turn makes them less sensible stochastic
+lower mortality rates which in turn makes them less sensible stochastic
 perturbation and because they control the amplitude of the fluctuations of their
@@
 omnivory was strongly correlated with average trophic level (Fig. S2),
-suggesting that average omnivory also stabilise population stability, in line
+suggesting that average omnivory also stabilises population stability, in line
 with previous theoretical results in small modules [@mccann_reevaluating_1997].
@@
 related by the fact that average trophic level is strongly associated with
-average omnivory, which might tamper synchronized predator-prey oscillations
+average omnivory, which might tamper synchronised predator-prey oscillations
 that can raise compensatory dynamics [@mccann_reevaluating_1997].
@@
 [@ruijven_contrasting_2007; @houlahan_negative_2018]. However, species richness
-had a strong positive on asynchrony, by raising portfolio effects.
+had a strong positive effect on asynchrony, by raising portfolio effects.
 This result is common in empirical systems [@tilman_biodiversity_2006;
@@
 @thibaut_understanding_2013; @zhao_biodiversity_2022]. Connectance, quantifying
-the generalism in food-webs, had small negative effects population
-stability but small positive on asynchrony. We further found that higher connectance
-leaded to less even biomass variability, thereby limiting the raise of the
-portfolio effects, and leaded to lower compensatory dynamics due to species
+the generalism in food-webs, had small negative effects on population
+stability but a small positive on on asynchrony. We further found that higher connectance
+led to less even biomass variability, thereby limiting the rise of the
+portfolio effects, and led to lower compensatory dynamics due to species
 interactions (Table. S4). This result is in accordance with empirical findings
-that a generalist predator can indeed synchronises the dynamics of a large
-number of preys [@raimondo_interspecific_2004], thereby potentially limiting compensatory
-dynamics raising from species interactions. However, the overall effect of
+that a generalist predator can indeed synchronise the dynamics of a large
+number of prey [@raimondo_interspecific_2004], thereby potentially limiting compensatory
+dynamics arising from species interactions. However, the overall effect of
 connectance on overall stability was quite low, similarly to previous empirical
@@
 Predator interference, taken in this study as a control variable, had also a
-strong effects on community stability. Our results confirm the stabilising
+strong effect on community stability. Our results confirm the stabilising
 effect of self-limiting processes on populations [@uszko_effects_2017;
@@
 consumers when predator biomass increases which might lead to a less dramatic
-fluctuation of prey biomass. All toghether, this result suggest that
+fluctuation of prey biomass. All together, this result suggests that
 self-limitation mechanisms that increase population stability might in turn have
-opposite effect on asynchrony, and that it is the balance between the two
+opposite effects on asynchrony, and that it is the balance between the two
 effects weighted by the relative importance of population stability and
@@
 We found that environmental stochasticity does not affect the shape of the
-community stability - richness but rather control the overall community
+community stability - richness but rather controls the overall community
 stability (i.e. the intercept of the relation). At the opposite, variation in
@@
 [@may_will_1972]. However, we found that the negative effects of complexity on
-stability-richness relationship are cancelled when response diversity is high.
-An possible explanation is the presence of response diversity and resulting
+stability-richness relationships are cancelled when response diversity is high.
+A possible explanation is the presence of response diversity and resulting
 asynchrony in species fluctuations which overrides the negative effects of
 complexity on stability-richness relationships. Response diversity might then be
-one mechanism that explains why positive relationship between stability
+one mechanism that explains why positive relationships between stability
 and species richness are so prevalent in empirical settings while food-web
-theoretical model that do not often include environmental stochasticity and
+theoretical models that do not often include environmental stochasticity and
 response diversity finds negative complexity stability relationships
@@
 predator interference increase temporal community stability by stabilising
-population fluctuations. In turn, our study confirm that species richness
-increase temporal community stability by increasing asynchrony due to portfolio
+population fluctuations. In turn, our study confirms that species richness
+increases temporal community stability by increasing asynchrony due to portfolio
 effects and thanks to response diversity. Our study reports that connectance and
@@
 strength, high connectance and high average trophic level. Then, the results of
-our study reinforce that the idea that restoration of ecosystems along with a
+our study reinforce the idea that restoration of ecosystems along with a
 restoration of landscape complexity that provides refuges from extreme

### 2024-04-06 paper/supplementary_figures.Rmd
Update manuscript and supplementary material

@@
 
-# Table
+# Tables
+
+```{r}
+tar_load(param_comb_nb)
+param_comb_chr <- paste0("$",
+  paste0(latex_symbol_replacement()[colnames(param_comb_nb)[colnames(param_comb_nb) != "n"]], collapse = " \\times "),
+  " =$ ", nrow(param_comb_nb), " parameter combinations."
+)
+nb_fw_per_comb <- unique(param_comb_nb$n)
+
+param_table_cap <- paste0(
+  "Parameter values used in the simulation experiment. N = ",
+  nrow(tar_read(sim_fw)), " simulations. ", param_comb_chr,
+  " We generated ", nb_fw_per_comb, " food-webs of varying connectance for each
+  parameter combination.") %>%
+  str_replace_all("\\s+", " ")
+
+tar_read(param_table) %>%
+  kable(
+    booktabs = TRUE,
+    format = "latex",
+    escape = FALSE,
+    caption = param_table_cap,
+    label = "param") %>%
+  kable_styling(latex_options = c("striped", "hold_position"))
+```
 
@@
 tar_read(tab_sem_vif) %>%
-  kable(booktabs = TRUE,
+  kable(
+    booktabs = TRUE,
     format = "latex",

### 2024-04-06 R/string_replacements.R

@@ -88,12 +88,42 @@ latex_symbol_replacement <- function() {
     d0 = "d_0",
     r = "r",
     c = "c",
+    h = "h",
     K = "K",
     eij = "e_{ij}",
     ay = "y",
     ax = "a_x",
     allo_slope = "b",
-    prod_mass = "M_p"
+    prod_mass = "M_p",
+    S = "S",
+    ct = "C",
+    Z = "Z",
+    env_stoch = "\\sigma_{e}",
+    resp_div = "1 - \\rho",
+    rho = "\\rho"
+  )
+}
+
+parameter_name_replacement <- function() {
+  c(
+    alpha_ij = "Producer inter-competition",
+    B0 = "Half-saturation rate",
+    d0 = "Basal natural death rate",
+    r = "Producer maximum growth rate",
+    c = "Predator interference",
+    h = "Hill exponent",
+    K = "Carrying capacity",
+    eij = "Assimilation efficiency",
+    ay = "Maximum consumption rate",
+    ax = "Basal metabolic rate",
+    allo_slope = "Allometric slope",
+    prod_mass = "Producer body mass",
+    S = "Initial richness",
+    ct = "Initial connectance",
+    Z = "Predator-Prey Mass Ratio",
+    env_stoch = "Environmental stochasticity",
+    resp_div = "Response diversity",
+    rho = "Species environmental correlation"
   )
 }
 

### 2024-04-10 paper/manuscript.Rmd
Reframe introduction: shorter and more general

@@
 link-citations: true
+#csl: nature.csl
 csl: ecology-letters.csl
@@
 
+- Putative titles:
+  - Community stability is driven by biodiversity and response diversity in
+    complex stochastic food-webs
+  - Response diversity and community structure drive community stability in
+    complex food-webs
+
+- Two strong results:
+  - Community stability raises primary from richness and average trophic level
+    but average interaction strength and connectance have little effects
+  - Response diversity and community structure interact strongly to determine
+    the sign of the relationship between community stability and species
+    richness
+
 # Abstract (150/150 words)
 
-Empirical and theoretical evidence suggests environmental changes will
+[NOT CHANGED] Empirical and theoretical evidence suggests environmental changes will
 dramatically destabilise ecological communities. However, this evidence is
@@
 
-Global environmental change constitutes a suite of major threats to biodiversity
-and ecosystem functioning [@lee_ipcc_2023; @simmons_refocusing_2021]. A central
-feature of these threats is that they are predicted to dramatically increase
-variability in the environment that species face [@lee_ipcc_2023] with potential
-impacts on the stability of communities and associated impacts on biodiversity
-and functioning in these communities. Assessing the impacts of this increased
-variability on ecological communities is challenging for several reasons.
-
-First, the stability of communities is often evaluated using the temporal
-variability of a metric of interest (e.g. abundance or biomass), because other
-stability metrics such as resilience and resistance are not always applicable,
-as most natural communities face persistent perturbations [@arnoldi_resilience_2016].
-Understanding this temporal community variability (hereafter referred to as
-community stability), measured as the inverse of the coefficient of variation
-[@tilman_biodiversity_2006; @roscher_identifying_2011;
-@thibaut_understanding_2013; @zhao_biodiversity_2022], requires scaling down the
-focus from communities to populations.
-Community stability can be mathematically partitioned into average population
-stability and asynchrony [@loreau_species_2008;
-@thibaut_understanding_2013; @zhao_biodiversity_2022] - asynchrony measuring how
-much each species fluctuations’ are compensating for each other at the community
-level. Population stability and asynchrony both depend on the number of species
-and their dominance [@loreau_species_2008; @thibaut_understanding_2013;
-@zhao_biodiversity_2022], on the interactions among species [@thebault_trophic_2005;
-@thebault_relationship_2006; @loreau_species_2008; @danet_species_2021;
-@eschenbrenner_diversity_2023] and on the way species respond to environmental
-perturbations [@ives_stability_2000; so-called response diversity,
-@elmqvist_response_2003; @ross_how_2023]. Therefore, accounting for the effects
-of community structure on population stability and asynchrony is crucial to
-improve our understanding of community stability in facing environmental change.
-
-Average population stability decreases with environmental stochasticity, such as the
-intensity and the frequency of perturbations [@loreau_species_2008]. Theorerical
-and empiral evidence suggests that species richness can decrease
-[@tilman_biodiversity_2006; @loreau_species_2008], increase
-[@houlahan_negative_2018], or have little effects on population stability. This
-effect of species richness on population stability depends on the evenness of
-the community since dominant species contribute more to the average of the
-community than subordinate species. Species interactions also have tremendous
-effects on population stability, such as strong interaction strength are
-generally destabilising [@mccann_weak_1998; @mccann_reevaluating_1997;
-@thebault_trophic_2005]. The shape of food-webs can also modulate population
-stability, such as higher trophic level was generally found to be stabilising
-[@shanafelt_stability_2018; @danet_species_2021; @eschenbrenner_diversity_2023],
-as top-down and bottom-up controls can increase population stability
-[@shanafelt_stability_2018].
-
-Asynchrony is mostly determined by the characteristics of the network. Response
-diversity captures how species’ differences in their response to the
-environmental variation can lead to asynchronous dynamics if their responses are
-different but synchronous dynamics if their responses are similar. Theory and
-empirical data emerging around response diversity suggest that it is a “core
-ecological mechanism underpinning many of the statistical explanations of the
-diversity–stability relationships” [@ives_stability_2000;
-@elmqvist_response_2003; @ross_how_2023]. In turn, the network structural
-properties and strength of species interactions can also modulate asynchrony
-through compensatory dynamics such as a strong asymmetry of consumer preference
-can generate asynchrony in resource fluctuations [@mccann_weak_1998;
-@vasseur_environmental_2007], and a generalist consumer can in turn generate
-synchrony among its prey [@raimondo_interspecific_2004]. Competition can also
-have synchronising effects in strong species growth rates regime
-[@loreau_species_2008]. Finally, portfolio and compensatory effects can also be
-affected by the population evenness such as fluctuations by dominant species
-will hardly be compensated by a subordinate species
-[@thibaut_understanding_2013; @zhao_biodiversity_2022]. Improving our
-understanding of community stability facing perturbations therefore requires
-articulating the effects of response diversity, species interactions, species
-richness and evenness on the different components of stability. Predicting the
-effects of species richness on community stability thus requires understanding
-the relationship between species richness, population stability and asynchrony.
-
-Empirical evidence suggest by increasing asynchrony, species richness
-drives positive relationships between community stability and species richness
-[@tilman_biodiversity_2006; @isbell_biodiversity_2009]. In contrast population stability was
-found to either decrease, increase, or not change with species richness
-[@houlahan_negative_2018; @tilman_biodiversity_2006; @roscher_identifying_2011].
-We note, however, that evidence for both asynchrony-richness and population
-stability-richness is derived from data on species assemblages.  These data thus
-do not account for food-web structure, which can have significant impact on
-population stability and asynchrony [but see @danet_species_2021]. Thus, ecology
-lacks a body of theory of temporal stability integrating across structure and
-response diversity frameworks and reflecting species rich communities. Here, we
-integrate these two perspectives on diversity- stability to evaluate the
-combined effects of community structure and response diversity on temporal
-stability in species rich, complex communities characterised by competition and
-predation.
-
-The ability to do this is supported by a key statistical advance: it is now
-possible to partition asynchrony into two component sources: the portfolio
-and the compensatory dynamics effects [@zhao_biodiversity_2022]. Portfolio
-effects stem from the statistical averaging of independent population
-fluctuations [@doak_statistical_1998; @zhao_biodiversity_2022], thereby
-increasing asynchrony. Compensatory dynamics in turn capture population
-fluctuations that are more synchronous or asynchronous than expected for
-independent fluctuations, and can stem from species interactions and species
-responses to perturbations [@zhao_biodiversity_2022]. This allows an
-unprecedented opportunity to obtain mechanistic insight about the effects of
-stressors and food-web structure on stability in complex, species rich
-communities.
-
-Our primary objective is to derive theory that predicts how the components of
-community stability, that can differentially drive patterns of stability,
-deliver novel insights into the source and patterns of diversity-stability
-relationships in complex communities facing environmental stochasticity, a
-necessary ingredient to generate species fluctuations. Our approach delivers
-revised insight into diversity-stability relationships in species rich
-communities when both community structure per se, and species responses can
-vary. In the following sections, we begin by introducing the multi-species model
-and the features of the model that allow us to integrate across variation in
-community structure and response diversity. We then introduce assumptions we
-used to implement environmental stochasticity, response diversity, variation in
-community structure and variation in the distribution of interaction types and
-strengths. Next, we define our in-silico experimental design that specifically
-aligns with three core questions and associated analyses. Considering four
-drivers, namely food-web structure, interaction strength, environmental
-stochasticity and response diversity, we investigated (1) What are their direct
-effects on population stability, portfolio and compensatory effects ? (2) What
-are their total effects on community stability, population stability and
-asynchrony? Finally, merging the two parallel bodies of work, we asked (3) How
-do they interact to drive the sign of the relation between community stability
-and species richness?
+Ever-growing anthropogenic pressures have resulted in alteration of biodiversity
+[@newbold_global_2015; @services_summary_2019], community changes
+[@dornelas_assemblage_2014], and climate change will result in dramatic
+environmental fluctuations [@lee_ipcc_2023]. How ecological communities will
+respond to those threats is then a pressing, but challenging question
+[@simmons_refocusing_2021; @yang_predictability_2019]. The temporal stability of
+ecological communities is an emerging property that indeed results of the
+complex interplay between anthropogenic pressures [@olivier_urbanization_2020;
+@hautier_anthropogenic_2015; @yang_predictability_2019], community size
+[@tilman_biodiversity_2006; @isbell_biodiversity_2009;
+@olivier_urbanization_2020; @pennekamp_biodiversity_2018] and community
+structure [@thebault_trophic_2005; @thebault_relationship_2006;
+@thibaut_understanding_2013; @danet_species_2021;
+@eschenbrenner_diversity_2023].
+
+Understanding emerging temporal community stability (hereafter referred to as
+community stability) requires scaling down the focus to population scale
+[@doak_statistical_1998; @thibaut_understanding_2013; @zhao_biodiversity_2022].
+Community stability can be partitioned into average population
+stability and asynchrony [@loreau_species_2008; @thibaut_understanding_2013;
+@zhao_biodiversity_2022], asynchrony measuring how much population
+fluctuations’ are compensating at the community level. The question of how
+global change will respectively affect population stability and asynchrony is
+still open.
+
+Asynchrony among species is the central pattern that drive the positive
+community stability-diversity relation documented across many species assemblages
+[@tilman_biodiversity_2006; @olivier_urbanization_2020;
+@pennekamp_biodiversity_2018]. Asynchrony does not emerge by species richness
+itself, but by its interplay with response diversity of species to perturbations
+[@elmqvist_response_2003; @loreau_species_2008; @ives_stability_2000;
+@ross_how_2023], and compensatory dynamics raising from species interactions.
+Asynchrony can then stem from statistical averaging of independent species
+fluctuations ["portfolio effects", @doak_statistical_1998;
+@tilman_ecological_1999] or compensatory dynamics resulting from response
+diversity and species interactions [@zhao_biodiversity_2022]. Among other
+reasons, it might explain why reports of neutral or negative stability-richness
+relationships are also common in empirical settings [@houlahan_negative_2018].
+However, most of our knowledge comes from simplified community
+structure, i.e. which does not account for the multiple trophic
+levels constituting ecological communities [but see @danet_species_2021;
+@thebault_trophic_2005; @ives_stability_2007; @eschenbrenner_diversity_2023],
+thereby limiting our understanding of the drivers of both community stability
+and stability-richness relationships in more complex communities.
+
+The structure of community also shapes communities
+[@macarthur_fluctuations_1955; @may_will_1972; @angelis_stability_1975;
+@mccann_weak_1998; @vasseur_environmental_2007; @thebault_trophic_2005], such as
+the strength [@may_will_1972; @mccann_weak_1998; @thebault_trophic_2005] and
+distribution [@may_will_1972; @angelis_stability_1975; @mccann_weak_1998;
+@mccann_reevaluating_1997] of species interactions determine population
+stability and stability-richness relationship [two trophic level systems,
+@thebault_trophic_2005; @ives_stability_2007], while the number of trophic
+levels determine population stability [@shanafelt_stability_2018]. Community
+structure also interact with response diversity to population stability in
+diamond shaped food-webs [@ripa_food_2003; @vasseur_environmental_2007;
+@ruokolainen_environmental_2013]. However, the work on community structure
+lacked the complexity in terms of species richness or trophic levels, and
+focused more on population stability than on asynchrony.
+
+Then, the two body of work focusing on the effects of (1) species richness or
+the effects of (2) community structure on community stability have been
+developed in isolation. While (1) highlighted the importance of asynchrony
+stemming response diversity ("insurance hypothesis"), (2) highlighted the
+importance of population stability arising from species interactions (top-down
+and bottom-up controls). Two keys advances allow to overcome that limitation:
+the development of the Bioenergenetic model that enable to model arbitrary
+complex communities [@yodzis_body_1992; @brose_allometric_2006] and the
+development of statistical tools that enables to partition community stability
+into population stability and asynchrony [@thibaut_understanding_2013;
+@zhao_biodiversity_2022].
+
+Here, we investigated the effects of species richness and community structure on
+community stability and on stability-richness relationship in complex stochastic
+food-web. To do so, we developed an extension of the Bioenergetic model
+[@brose_allometric_2006; @lajaaiti_ecologicalnetworksdynamicsjl_2024] which
+includes environmental stochasticity and response diversity
+[@vasseur_environmental_2007]. We modelled food-web varying in size (species
+richness XX) and structure (Connectance XX, Predator-Prey Mass Ratio: XX) to
+create a diversity of community structure. We additionally varied the
+variability of environmental stochasticity (standard deviation of mortality
+rates) and response diversity ($1-\rho$, $\rho$ being the correlation among
+species mortality rates). We performed XXXXX simulations over a minimum 2000
+timesteps (Table S1) and collected the 500 last timesteps to compute community
+stability and structure. Using a structural equation model, we deciphered the
+ways in which stressors (environmental stochasticity, decreasing response
+diversity) and community structure (species richness, average interaction
+strength, average trophic level, connectance) determine community stability. In
+a second time, we used a linear model to investigate how community structure
+interact with response diversity to determine the sign of the stability-richness
+relationship.
 

### 2024-04-12 paper/manuscript.Rmd
Rewrite intro and abstract in NEE style

@@
     complex stochastic food-webs
-  - Response diversity and community structure drive community stability in
-    complex food-webs
+  - Response diversity and food-web structure drive stability and
+    stability-richness relationships in fluctuating environments
 
@@
 
-[NOT CHANGED] Empirical and theoretical evidence suggests environmental changes will
-dramatically destabilise ecological communities. However, this evidence is
-largely based on oversimplified communities, which lack the complexity of
-natural communities. We characterise the dynamics of complex food-webs under a
-stochastic food-web model, and investigate how response diversity,
-stochasticity, and food-web structure drive temporal stability. We found that
-higher average trophic level increased community stability by increasing
-population stability, at the expense of asynchrony. Species richness had little
-effect on population stability, but a large one on asynchrony. Interaction
-strength and connectance had little effects on temporal stability overall, but
-interacted strongly with response diversity to determine stability-richness
-relationships. Absence of response diversity all leaded to negative
-stability-richness relationships, but high response diversity resulted in high
-prevalence of positive stability-richness relationships. Our study reveals that
-response diversity and food-web structure drive temporal stability overall, and
-together determine the sign of the stability-richness relationship.
+The diversity of species responses to environmental stochasticity is key to
+understand temporal community stability and stability-diversity relationships.
+While we know quite well how response diversity and species richness drive
+community stability in plant communities, whether these effects also operate
+in complex food-webs remains an open question. Using a stochastic Bioenergenetic
+model, we show that response diversity and species richness are also strong drivers
+of overall community stability in complex food-webs. In contrast, we found that
+interaction strength and connectance had little effects on temporal stability
+overall. Negative stability-richness relationships always emerged in the absence
+of response diversity, but we found that interaction strength, connectance,
+average trophic level strongly interact with response diversity to determine the
+sign of stability-diversity relationships. Our study disentangles the complex
+effects of food-web structure on community stability and its pathway, showing
+that response diversity is a mechanism that generate positive
+stability-diversity relationships, beyond plant communities.
 
@@
 
-Ever-growing anthropogenic pressures have resulted in alteration of biodiversity
-[@newbold_global_2015; @services_summary_2019], community changes
-[@dornelas_assemblage_2014], and climate change will result in dramatic
-environmental fluctuations [@lee_ipcc_2023]. How ecological communities will
-respond to those threats is then a pressing, but challenging question
-[@simmons_refocusing_2021; @yang_predictability_2019]. The temporal stability of
-ecological communities is an emerging property that indeed results of the
-complex interplay between anthropogenic pressures [@olivier_urbanization_2020;
-@hautier_anthropogenic_2015; @yang_predictability_2019], community size
-[@tilman_biodiversity_2006; @isbell_biodiversity_2009;
-@olivier_urbanization_2020; @pennekamp_biodiversity_2018] and community
-structure [@thebault_trophic_2005; @thebault_relationship_2006;
-@thibaut_understanding_2013; @danet_species_2021;
-@eschenbrenner_diversity_2023].
+Predicting how ecological communities respond ever-growing anthropogenic
+pressures is a central focus in Ecology [@newbold_global_2015;
+@services_summary_2019]. Most approaches so-far involve static environment and
+simplified species assemblages, overlooking environmental stochasticity and the
+complex structure of ecological communities. However, the effects of
+stochasticity is much more than noise and lead to emerging properties at the
+community level. The key mechanism is the way that species respond to
+environmental stochasticity, the so called response diversity
+[@elmqvist_response_2003; @loreau_species_2008; @ives_stability_2000;
+@ross_how_2023]. Response diversity, even considered as pure random species
+fluctuations, generate asynchrony in species fluctuations at the community
+level. Coined as "statistical averaging", "portfolio effects" or "insurance
+hypothesis", it is responsible for the positive relationships between temporal
+stability of community and species richness in plant communities
+[@doak_statistical_1998; @yachi_biodiversity_1999; @tilman_biodiversity_2006;
+@zhao_biodiversity_2022]. But species responses to environmental fluctuations is
+also constrained by species interactions, and so community structure
+[@loreau_species_2008; @vasseur_environmental_2007; @thebault_trophic_2005;
+@thebault_relationship_2006]. A pioneer example by @vasseur_environmental_2007,
+in which they present a counter-intuitive example, where the lack of response
+diversity can dampen species oscillations and then increase the temporal
+stability in a four species diamond food-web [@mccann_weak_1998]. Despite its
+overarching importance on community stability and stability-richness
+relationships, the effects of stochasticity and response diversity in complex
+communities, such as food-webs, remain mostly unknown.
 
@@
 [@doak_statistical_1998; @thibaut_understanding_2013; @zhao_biodiversity_2022].
-Community stability can be partitioned into average population
-stability and asynchrony [@loreau_species_2008; @thibaut_understanding_2013;
-@zhao_biodiversity_2022], asynchrony measuring how much population
-fluctuations’ are compensating at the community level. The question of how
-global change will respectively affect population stability and asynchrony is
-still open.
-
-Asynchrony among species is the central pattern that drive the positive
-community stability-diversity relation documented across many species assemblages
-[@tilman_biodiversity_2006; @olivier_urbanization_2020;
-@pennekamp_biodiversity_2018]. Asynchrony does not emerge by species richness
-itself, but by its interplay with response diversity of species to perturbations
-[@elmqvist_response_2003; @loreau_species_2008; @ives_stability_2000;
-@ross_how_2023], and compensatory dynamics raising from species interactions.
-Asynchrony can then stem from statistical averaging of independent species
-fluctuations ["portfolio effects", @doak_statistical_1998;
+Community stability, measured as the inverse of the coefficient of variation,
+can be partitioned into average population stability and asynchrony
+[@thibaut_understanding_2013; @zhao_biodiversity_2022], which respectively
+measures the amplitude of species fluctuations relative to their
+biomass/abundance and how much species fluctuations’ are compensating each other
+at the community level. Asynchrony can then stem from statistical averaging of
+independent species fluctuations ["portfolio effects", @doak_statistical_1998;
 @tilman_ecological_1999] or compensatory dynamics resulting from response
-diversity and species interactions [@zhao_biodiversity_2022]. Among other
-reasons, it might explain why reports of neutral or negative stability-richness
-relationships are also common in empirical settings [@houlahan_negative_2018].
-However, most of our knowledge comes from simplified community
-structure, i.e. which does not account for the multiple trophic
-levels constituting ecological communities [but see @danet_species_2021;
-@thebault_trophic_2005; @ives_stability_2007; @eschenbrenner_diversity_2023],
-thereby limiting our understanding of the drivers of both community stability
-and stability-richness relationships in more complex communities.
-
-The structure of community also shapes communities
-[@macarthur_fluctuations_1955; @may_will_1972; @angelis_stability_1975;
-@mccann_weak_1998; @vasseur_environmental_2007; @thebault_trophic_2005], such as
-the strength [@may_will_1972; @mccann_weak_1998; @thebault_trophic_2005] and
-distribution [@may_will_1972; @angelis_stability_1975; @mccann_weak_1998;
-@mccann_reevaluating_1997] of species interactions determine population
-stability and stability-richness relationship [two trophic level systems,
+diversity to environmental fluctuations and species interactions
+[@zhao_biodiversity_2022]. The body of theory of BEF, focusing mainly on plants,
+showed that response diversity and species richness give rise to asynchrony and
+thereby increase community stability, despite that species richness can decrease
+population stability in the same time [@tilman_biodiversity_2006;
+@houlahan_negative_2018]. On the other side, food-web theory focused more on
+population stability. It shows that the strength [@may_will_1972;
+@mccann_weak_1998; @thebault_trophic_2005] and distribution [@may_will_1972;
+@angelis_stability_1975; @mccann_weak_1998; @mccann_reevaluating_1997] of
+species interactions determine population stability ("complexity-stability"
+theory) and stability-richness relationship [two trophic level systems,
 @thebault_trophic_2005; @ives_stability_2007], while the number of trophic
-levels determine population stability [@shanafelt_stability_2018]. Community
-structure also interact with response diversity to population stability in
-diamond shaped food-webs [@ripa_food_2003; @vasseur_environmental_2007;
-@ruokolainen_environmental_2013]. However, the work on community structure
-lacked the complexity in terms of species richness or trophic levels, and
-focused more on population stability than on asynchrony.
-
-Then, the two body of work focusing on the effects of (1) species richness or
-the effects of (2) community structure on community stability have been
-developed in isolation. While (1) highlighted the importance of asynchrony
-stemming response diversity ("insurance hypothesis"), (2) highlighted the
-importance of population stability arising from species interactions (top-down
-and bottom-up controls). Two keys advances allow to overcome that limitation:
-the development of the Bioenergenetic model that enable to model arbitrary
-complex communities [@yodzis_body_1992; @brose_allometric_2006] and the
-development of statistical tools that enables to partition community stability
-into population stability and asynchrony [@thibaut_understanding_2013;
+levels determine population stability [@shanafelt_stability_2018]. Food-web
+structure also interacts with response diversity to determine population
+stability in diamond shaped food-webs [@ripa_food_2003;
+@vasseur_environmental_2007; @ruokolainen_environmental_2013]. So far, food-web
+theory overlooked the effects of food-web structure on response diversity and
+asynchrony while BEF theory overlooked the complex effects of food-web structure
+on population stability and asynchrony. Two keys advances allow to overcome that
+limitation: the development of the Bioenergenetic model that enable to model
+arbitrary complex communities [@yodzis_body_1992; @brose_allometric_2006] and
+the development of statistical tools that enables to partition community
+stability into population stability and asynchrony [@thibaut_understanding_2013;
 @zhao_biodiversity_2022].
@@
 We further found that food-web structure had a strong impact asynchrony, raising
-from portfolio and compensatory effects. As
-expected the mathematical relationship (eq. \@ref(eq:sae-even)), species
-richness was a main positive driver of portfolio effects ($r_\delta$= `r rsr`,
-Fig. \@ref(fig:sem)a), thereby increasing
-asynchrony. In turn, species richness, average trophic level and connectance had
-negative effects on the evenness of species variability (resp. $r_\delta$= `r rer`,
-`r ret`, and `r rect`), thereby downplaying the portfolio effect raised from
-species richness alone in a scenario of even species variabilities. In turn, we found
-that response diversity had a positive effect on evenness of species variability
-($r_\delta$=`r red`), thereby maximising the portfolio effect. We found
-that species response diversity had a strong positive effect on compensatory
-dynamics ($r_\delta$= `r rcd`), while average interaction strength had a small
-positive effect ($r_\delta$= `r rci`, Fig. \@ref(fig:sem)).
+from portfolio and compensatory effects. As expected the mathematical
+relationship (eq. \@ref(eq:sae-even)), species richness was a main positive
+driver of portfolio effects ($r_\delta$= `r rsr`, Fig. \@ref(fig:sem)a), thereby
+increasing asynchrony. In turn, species richness, average trophic level and
+connectance had negative effects on the evenness of species variability (resp.
+$r_\delta$= `r rer`, `r ret`, and `r rect`), thereby downplaying the portfolio
+effect raised from species richness alone in a scenario of even species
+variabilities. In turn, we found that response diversity had a positive effect
+on evenness of species variability ($r_\delta$=`r red`), thereby maximising the
+portfolio effect. We found that species response diversity had a strong positive
+effect on compensatory dynamics ($r_\delta$= `r rcd`), while average interaction
+strength had a small positive effect ($r_\delta$= `r rci`, Fig. \@ref(fig:sem)).
 

### 2024-04-24 _targets.Rmd
Update manuscript results, discussion and methods

@@
   tar_target(sem_eff_coeff, sem_main_text_eff_tab_csc_rerun),
-  tar_target(tab_sem_coeff,
-    sem_main_text_coeff_csc_rerun %>%
-      filter(!str_detect(Response, "~~")) %>% #Remove correlation w_avg_tlvl ~~ avg_omnivory
-      mutate(across(c("Response", "Predictor"), ~var_replacement()[.x])) %>%
-      mutate(Std.Estimate = round(Std.Estimate, 2)) %>%
-      rename(`Std estimate` = Std.Estimate) %>%
-      select(-Signif)
-    ),
   tar_target(sem_collinearity, sem_main_text_collinearity_csc_rerun),
@@
     sem_simplified_eff_tab %>%
+      filter(effect_type == "direct") %>%
+      mutate(across(c("response", "predictor"), ~var_replacement()[.x])) %>%
+      mutate(effect = round(effect, 2)) %>%
+      select(
+        Response = response,
+        Predictor = predictor,
+        `Std estimate` = effect
+      )
+  ),
+  tar_target(tab_sem_doak_eff,
+    sem_doak_eff_tab %>%
       filter(effect_type == "direct") %>%
@@
   tar_target(sem_main_text_coeff_file, here::here("data", paste0("sem_main_text_coeff_", names)), format = "file"),
-  tar_target(sem_main_text_coeff, { readRDS(sem_main_text_coeff_file) }),
-  tar_target(sem_main_text_eff_tab, from_semEff_to_table(sem_main_text_eff))
+  tar_target(sem_main_text_eff_tab, from_semEff_to_table(sem_main_text_eff)),
+
+  tar_target(sem_doak_file, here::here("data", paste0("sem_doak_", names)), format = "file"),
+  tar_target(sem_doak, { readRDS(sem_doak_file) }),
+  tar_target(sem_doak_eff_file, here::here("data", paste0("sem_doak_eff_", names)), format = "file"),
+  tar_target(sem_doak_eff, { readRDS(sem_doak_eff_file) }),
+  tar_target(sem_doak_eff_tab, from_semEff_to_table(sem_doak_eff)),
+  tar_target(sem_doak_collinearity_file, here::here("data", paste0("sem_doak_collinearity_", names)), format = "file"),
+  tar_target(sem_doak_collinearity, { readRDS(sem_doak_collinearity_file) }),
+  tar_target(sem_doak_rsquared_file, here::here("data", paste0("sem_doak_rsquared_", names)), format = "file"),
+  tar_target(sem_doak_rsquared, { readRDS(sem_doak_rsquared_file) })
 )
@@
   ),
+  tar_target(sem_doak_tot,
+    tibble(
+      sim_type = c(
+        "rerun",
+        "non_allo",
+        "rebuild",
+        "kno"),
+      eff = list(
+        sem_doak_eff_tab_csc_rerun,
+        sem_doak_eff_tab_csc_non_allo,
+        sem_doak_eff_tab_csc_rebuild,
+        sem_doak_eff_tab_csc_kno
+        ),
+      collinearity = list(
+        sem_doak_collinearity_csc_rerun,
+        sem_doak_collinearity_csc_non_allo,
+        sem_doak_collinearity_csc_rebuild,
+        sem_doak_collinearity_csc_kno
+        ),
+    )
+  ),
   tar_target(sem_main_text_eff_tab_tot,
@@
       )
+  ),
+  tar_target(sem_doak_eff_tab_tot,
+    sem_doak_tot %>%
+      select(sim_type, eff) %>%
+      unnest(cols = eff)),
+  tar_target(p_sem_doak_eff_tab_tot,
+    sem_doak_eff_tab_tot %>%
+      filter(effect_type == "total") %>%
+      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
+      filter(predictor %in% sem_tot_predictor()) %>%
+      mutate(
+        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
+        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE),
+        sim_type = recode_factor(sim_type, !!!sim_type_replacement(), .ordered = TRUE)
+        ) %>%
+      ggplot(aes(
+          y = predictor,
+          x = effect,
+          color = response,
+          shape = sim_type
+        )
+        ) +
+      geom_point(alpha = .5) +
+      scale_colour_manual(values = stab_color()) +
+      scale_alpha_manual(values = stab_alpha()) +
+      #  geom_hline(yintercept = 0, linetype = "dashed") +
+      geom_vline(xintercept = 0, linetype = "dashed") +
+      facet_grid(cols = vars(response)) +
+      labs(
+        x = "Total standardised effects",
+        color = "Stability component",
+        alpha = "Stability component"
+        ) +
+      theme_bw() +
+      theme(
+        axis.title.y = element_blank(),
+        #legend.justification = "right",
+        legend.position = "bottom") +
+      guides(
+        color = FALSE
+        ) +
+      theme(
+        legend.title = element_blank(),
+        legend.position = "bottom",
+        legend.justification = c("left", "top")
+      )
   )
@@
   tar_target(sem_simplified_eff_tab, sem_simplified_eff_tab_csc_rerun),
-  tar_target(sem_main_text_eff_tab, sem_main_text_eff_tab_csc_rerun)
+  tar_target(sem_main_text_eff_tab, sem_main_text_eff_tab_csc_rerun),
+  tar_target(sem_doak_eff_tab, sem_doak_eff_tab_csc_rerun)
 )
@@
               env_stoch, resp_div, Z, c,
-              ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
+              ct_alive, w_avg_tlvl, avg_int_strength),
             ~scale(.x)[, 1])
@@
 
+```{targets full-model-pred}
+list(
+  tar_target(model_fw_stab_comp_full,
+    tibble(
+      response = stab_com_part_var,
+      model = list(glmmTMB(formula_stab_fw_model(
+      resp = stab_com_part_var,
+      rand_effect = TRUE,
+      term_to_del = "richness : resp_div : Z +"),
+      data = mutate(sim_fw,
+      across(c(stab_com, pop_stab, async), log)
+      ))
+        )),
+        pattern = stab_com_part_var
+  ),
+  tar_target(model_fw_stab_comp_full_scaled,
+    tibble(
+      response = stab_com_part_var,
+      model = list(glmmTMB(formula_stab_fw_model(
+        resp = stab_com_part_var,
+        rand_effect = TRUE,
+        term_to_del = "richness : resp_div : Z +"
+        ),
+      data = sim_fw %>%
+        mutate(across(c(stab_com, pop_stab, async), log)) %>%
+        mutate(across(c(sim_id, fw_id), as.factor)) %>%
+        mutate(
+          across(c(stab_com, pop_stab, async, richness,
+              env_stoch, resp_div, Z, c,
+              ct_alive, w_avg_tlvl, avg_int_strength),
+            ~scale(.x)[, 1])
+        )
+        ))),
+        pattern = stab_com_part_var
+  ),
+  tar_target(model_fw_stab_comp_full_scaled_coeff,
+    model_fw_stab_comp_full_scaled %>%
+      mutate(
+        coeff = map(model, function(x) {
+          confint(x, level = 0.95) %>%
+          as.data.frame() %>%
+          rownames_to_column("term") %>%
+          as_tibble() %>%
+          mutate(term = str_replace(term, "cond\\.", ""))
+        })
+      ) %>%
+      select(-model)
+  ),
+  tar_target(fixed_effect_fw_stab_comp_full,
+    model_fw_stab_comp_full %>%
+      mutate(
+      fix_effect = map(model, ~fixef(.x)$cond)
+      ) %>%
+      select(-model)
+  ),
+  tar_target(pred_stab_comp_full_resp_div,
+    fixed_effect_fw_stab_comp_full %>%
+      left_join(
+        list(
+          response = fixed_effect_fw_stab_comp_full$response,
+          variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive")
+          ) %>%
+        expand.grid() %>%
+        left_join(
+          tibble(
+            variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive"),
+            values = list(
+              seq(
+                min(pred_range_fw$avg_int_strength),
+                max(pred_range_fw$avg_int_strength),
+                length.out = 50
+                ),
+              seq(
+                min(pred_range_fw$w_avg_tlvl),
+                max(pred_range_fw$w_avg_tlvl),
+                length.out = 50
+              ),
+              seq(
+                min(pred_range_fw$ct_alive),
+                max(pred_range_fw$ct_alive),
+                length.out = 50
+              )
+            )
+          )
+        )
+        ) %>%
+    mutate(slope = pmap(
+        list(
+          param_name = variable,
+          param_values = values,
+          coeff = fix_effect
+          ),
+        function(param_name, param_values, coeff) {
+          param <- list(
+            seq(0, 1, length.out = length(param_values)),
+            param_values
+          )
+          names(param) <- c("resp_div", param_name)
+
+          encaps_get_slope_change(
+            param_list = param,
+            coeff_data = coeff,
+            slope_term = "richness",
+            default_variable_values = default_variable_values_pred
+          )
+        }
+        )
+    ) %>%
+    select(-fix_effect, -values) %>%
+    select(-variable) %>%
+    mutate(slope = map(slope,
+      ~pivot_longer(.x,
+        -c(resp_div, slope),
+        names_to = "variable",
+        values_to = "variable_values"
+      )
+    )
+  ) %>%
+  unnest(cols = slope)
+  ),
+  tar_target(p_pred_stab_comp_full_resp_div,
+    pred_stab_comp_full_resp_div %>%
+  filter(response == "stab_com") %>%
+  mutate(
+    variable = var_replacement()[variable]
+    ) %>%
+  ggplot(aes(x = resp_div, y = variable_values, fill = slope)) +
+  geom_raster() +
+  facet_wrap(~variable, scales = "free_y", strip.position = "left") +
+  coord_cartesian(expand = FALSE) +
+  scale_fill_gradient2(
+    low = resp_div_cat_colors()["Low"],
+    mid = "white",
+    high = resp_div_cat_colors()["High"],
+    midpoint = 0,
+    space = "Lab",
+    na.value = "grey50",
+    guide = "colourbar",
+    aesthetics = "fill") +
+  labs(
+    x = var_replacement()["resp_div"],
+    y = "Food-web structure",
+    fill = "Slope community stability - Richness"
+    ) +
+  theme(
+    legend.position = "bottom",
+    legend.key.width = unit(2.5, "cm"),
+    plot.margin = margin(l = 10, r = 10, t = 5, unit = "pt"),
+    strip.placement = "outside",
+    strip.background = element_blank(),
+    strip.text = element_text(size = 11),
+    axis.title.y = element_blank()
+  )
+    )
+)
+```
+
 # plot
@@
 tar_load(pred_stab_comp_resp_div)
+library(targets)
+tar_load(sem_doak_eff_tab_csc_rerun)
+sem_doak_eff_tab_csc_rerun %>%
+  filter(effect_type == "direct", abs(effect) > .05) %>%
+  print(n = 40)
+
+sem_doak_eff_tab_csc_rerun %>%
+  filter(effect_type == "direct") %>%
+  print(n = 40)
 ```
@@
   tar_target(p_sem_tot_stab,
-    sem_main_text_eff_tab_csc_rerun %>%
+    sem_doak_eff_tab_csc_rerun %>%
       filter(effect_type == "total") %>%
@@
   ),
-  tar_target(sem_file, here("report", "figures", "sem_stab_main_text.pdf"), format = "file"),
+  tar_target(sem_file, here("report", "figures", "sem_stab_doak.pdf"), format = "file"),
   tar_target(p_sem,
@@
       units = "mm")
+  )
+)
+```
+```{targets pred_show_full}
+list(
+  tar_target(pred_data_show_full, {
+    low_resp_example_full <- rbind(default_variable_values_pred) %>%
+      as_tibble() %>%
+      mutate(resp_div = .1, w_avg_tlvl = 2.0, fw_id = "new") %>%
+      slice(rep(1, length(richness_gradient_pred_show))) %>%
+      mutate(richness = richness_gradient_pred_show)
+    high_resp_example_full <- rbind(default_variable_values_pred) %>%
+      as_tibble() %>%
+      mutate(resp_div = .9, w_avg_tlvl = 1.2, fw_id = "new") %>%
+      slice(rep(1, length(richness_gradient_pred_show))) %>%
+      mutate(richness = richness_gradient_pred_show)
+    out <- rbind(low_resp_example_full, high_resp_example_full)
+    out$stab_com <- predict(
+      model_fw_stab_comp[model_fw_stab_comp_full$response == "stab_com", ]$model[[1]],
+      out,
+      allow.new.levels = TRUE
+    )
+    out
+  }
+    ),
+  tar_target(p_pred_data_show_low_resp_full,
+    pred_data_show_full %>%
+      filter(resp_div == .1) %>%
+      ggplot(aes(x = richness, y = exp(stab_com))) +
+      geom_line(color = resp_div_cat_colors()["Low"]) +
+      ylim(10, 25) +
+      labs(x = "Species richness", y = "Community stability") +
+      theme_half_open()
+    ),
+  tar_target(p_pred_data_show_low_resp_file_full,
+    ggsave_multiple(
+      paste0("p_pred_data_show_low_resp_full", c(".png", ".pdf")),
+      plot = p_pred_data_show_low_resp_full,
+      path = here::here("report", "figures"),
+      scale = 1.4,
+      dpi = 400,
+      width = 80,
+      height = 80 * .9,
+      units = "mm")
+    ),
+  tar_target(p_pred_data_show_high_resp_full,
+    pred_data_show_full %>%
+      filter(resp_div == .9) %>%
+      ggplot(aes(x = richness, y = exp(stab_com))) +
+      geom_line(color = resp_div_cat_colors()["High"]) +
+      ylim(10, 25) +
+      labs(x = "Species richness", y = "Community stability") +
+      theme_half_open()
+    ),
+  tar_target(p_pred_data_show_high_resp_file_full,
+    ggsave_multiple(
+      paste0("p_pred_data_show_high_resp_full", c(".png", ".pdf")),
+      plot = p_pred_data_show_high_resp_full,
+      path = here::here("report", "figures"),
+      scale = 1.4,
+      dpi = 400,
+      width = 80,
+      height = 80 * .9,
+      units = "mm")
+    ),
+  tar_target(data_label_pred_show_full,
+    pred_data_show_full %>%
+      select(resp_div, richness, w_avg_tlvl) %>%
+      filter(richness == min(richness)) %>%
+      pivot_longer(c(w_avg_tlvl), names_to = "variable",
+        values_to = "variable_values") %>%
+      mutate(variable = var_replacement()[variable],
+        label = c("b", "c")
+      )
       )
@@
     select(c(
-        bm_total, stab_com, pop_stab, async, sae_total, sae_even,
-        evenness_sae, cpe, cpe_int, cpe_env,
+        bm_total, stab_com, pop_stab, async, sae_total, sae_doak, cpe, cpe_int, cpe_env,
         richness, ct_alive, avg_int_strength, avg_omnivory, max_tlvl,
-        w_avg_tlvl,
-        Z, resp_div, env_stoch, c
+        w_avg_tlvl, Z, resp_div, env_stoch, c
         )) %>%
@@
 
+```{targets p_sem_doak_eff_tab_tot_file, tar_simple = TRUE}
+ggsave_multiple(
+  paste0("p_sem_doak_eff_tab_tot", c(".png", ".pdf")),
+  plot = p_sem_doak_eff_tab_tot,
+  path = here::here("report", "figures"),
+  scale = 2.4,
+  dpi = 400,
+  width = 80,
+  height = 80 * .5,
+  units = "mm"
+  )
+```
+
 # Table
@@
 ```{targets sem_fig_coeff, tar_simple=TRUE}
-sem_main_text_eff_tab %>%
+sem_doak_eff_tab %>%
   filter(effect_type == "direct",
     predictor %in% c(
-      sem_tot_predictor(),
-      "async", "stab_com", "pop_stab", "sae_total", "cpe", "evenness_sae", "sae_even"
-      )) %>%
+      sem_tot_predictor(), "async", "stab_com", "pop_stab", "sae_doak",
+      "cpe_int")) %>%
 select(response, predictor, effect) %>%
@@
 )
-```
-
-```{r, eval = FALSE}
-tar_load(sim_param)
 ```
@@
   bind_rows(tab_sim_param)
-  )
-)
-```
-
-```{r}
-
+  ),
+  tar_target(sim_summary_stat, get_sim_summary_stat(x = sim_fw)),
+  tar_target(tab_sim_summary_stat,
+  sim_summary_stat %>%
+    mutate(
+      var = var_replacement()[var],
+      type = str_to_sentence(type)
+      ) %>%
+    select(Type = type, `Metric` = var, N = n, `Median (5%, 95%)`)
+  )
+)
+```
+
+```{r, eval = FALSE}
+tar_load(sim_summary_stat)
+tar_load(sim_fw)
 ```
@@
 tar_meta(fields = error, complete_only = TRUE) %>%
-  print(n = 40)
+  print(n = 100)
 ```
@@
 tar_load(fixed_effect_fw_stab)
-```
-```{r}
-tar_load_globals()
-tar_visnetwork()
-tar_load(pred_stab_comp_resp_div)
 ```
@@
   theme_bw()
-
 ```
@@
 unique(pred_data_show$resp_div) %>% round(., 2)
-
 ```

### 2024-04-24 paper/manuscript.Rmd
Update manuscript results, discussion and methods

@@
 ---
-title: Food-web structure, stochasticity and response diversity drive temporal community stability in complex communities
+title: Response diversity and food-web structure drive stability and stability-richness relationships in complex communities
 author: "Alain Danet (1), Sonia Kéfi (2,3), Thomas F Johnson (1), Andrew P. Beckerman (1)"
@@
 output:
-  officedown::rdocx_document:
-    number_sections: false
-    base_format: "bookdown::word_document2"
   bookdown::pdf_document2:
@@
     number_sections: false
+  officedown::rdocx_document:
+    number_sections: false
+    base_format: "bookdown::word_document2"
 always_allow_html: true
@@
 link-citations: true
-#csl: nature.csl
-csl: ecology-letters.csl
+csl: nature.csl
+#csl: ecology-letters.csl
 toc: false
@@
 
-- Putative titles:
-  - Community stability is driven by biodiversity and response diversity in
-    complex stochastic food-webs
-  - Response diversity and food-web structure drive stability and
-    stability-richness relationships in fluctuating environments
-
-- Two strong results:
-  - Community stability raises primary from richness and average trophic level
-    but average interaction strength and connectance have little effects
-  - Response diversity and community structure interact strongly to determine
-    the sign of the relationship between community stability and species
-    richness
-
-# Abstract (150/150 words)
-
-The diversity of species responses to environmental stochasticity is key to
-understand temporal community stability and stability-diversity relationships.
-While we know quite well how response diversity and species richness drive
-community stability in plant communities, whether these effects also operate
-in complex food-webs remains an open question. Using a stochastic Bioenergenetic
-model, we show that response diversity and species richness are also strong drivers
-of overall community stability in complex food-webs. In contrast, we found that
-interaction strength and connectance had little effects on temporal stability
-overall. Negative stability-richness relationships always emerged in the absence
-of response diversity, but we found that interaction strength, connectance,
-average trophic level strongly interact with response diversity to determine the
-sign of stability-diversity relationships. Our study disentangles the complex
-effects of food-web structure on community stability and its pathway, showing
-that response diversity is a mechanism that generate positive
+# Abstract (179/200 words)
+
+Global environmental change constitutes a suite of major threats to biodiversity
+and ecosystem functioning. These threats can materialised via changes to the
+stability of communities and the services they provide. Despite independent
+advances in understanding the impact on stability of community size and
+structure, synchrony and responses to environmental variation, there remains no
+core theory connecting these key processes. Developing this theory requires
+combining concepts from diversity - stability relationships, synchrony and the
+portfolio effect, and the emerging field of response diversity. Using a
+stochastic Bioenergenetic food-web model of 20-50 interacting species, we show
+that response diversity and species richness are also strong drivers of overall
+community stability in complex food-webs. We further show that connectance and
+average trophic level consistently dampened asynchrony but that average trophic
+level stabilises population stability. Positive stability-richness relationships
+always emerged only in presence of response diversity, but interaction strength,
+connectance, average trophic level strongly interact with response diversity to
+determine the sign of stability-diversity relationships. Our study disentangles
+the complex effects of food-web structure on community stability and its
+pathway, showing that response diversity is a mechanism that generates positive
 stability-diversity relationships, beyond plant communities.
@@
 
-Predicting how ecological communities respond ever-growing anthropogenic
-pressures is a central focus in Ecology [@newbold_global_2015;
-@services_summary_2019]. Most approaches so-far involve static environment and
-simplified species assemblages, overlooking environmental stochasticity and the
-complex structure of ecological communities. However, the effects of
-stochasticity is much more than noise and lead to emerging properties at the
-community level. The key mechanism is the way that species respond to
-environmental stochasticity, the so called response diversity
-[@elmqvist_response_2003; @loreau_species_2008; @ives_stability_2000;
-@ross_how_2023]. Response diversity, even considered as pure random species
-fluctuations, generate asynchrony in species fluctuations at the community
-level. Coined as "statistical averaging", "portfolio effects" or "insurance
-hypothesis", it is responsible for the positive relationships between temporal
-stability of community and species richness in plant communities
-[@doak_statistical_1998; @yachi_biodiversity_1999; @tilman_biodiversity_2006;
-@zhao_biodiversity_2022]. But species responses to environmental fluctuations is
-also constrained by species interactions, and so community structure
-[@loreau_species_2008; @vasseur_environmental_2007; @thebault_trophic_2005;
-@thebault_relationship_2006]. A pioneer example by @vasseur_environmental_2007,
-in which they present a counter-intuitive example, where the lack of response
-diversity can dampen species oscillations and then increase the temporal
-stability in a four species diamond food-web [@mccann_weak_1998]. Despite its
-overarching importance on community stability and stability-richness
-relationships, the effects of stochasticity and response diversity in complex
-communities, such as food-webs, remain mostly unknown.
-
-Understanding emerging temporal community stability (hereafter referred to as
-community stability) requires scaling down the focus to population scale
-[@doak_statistical_1998; @thibaut_understanding_2013; @zhao_biodiversity_2022].
-Community stability, measured as the inverse of the coefficient of variation,
-can be partitioned into average population stability and asynchrony
-[@thibaut_understanding_2013; @zhao_biodiversity_2022], which respectively
-measures the amplitude of species fluctuations relative to their
-biomass/abundance and how much species fluctuations’ are compensating each other
-at the community level. Asynchrony can then stem from statistical averaging of
-independent species fluctuations ["portfolio effects", @doak_statistical_1998;
-@tilman_ecological_1999] or compensatory dynamics resulting from response
-diversity to environmental fluctuations and species interactions
-[@zhao_biodiversity_2022]. The body of theory of BEF, focusing mainly on plants,
-showed that response diversity and species richness give rise to asynchrony and
-thereby increase community stability, despite that species richness can decrease
-population stability in the same time [@tilman_biodiversity_2006;
-@houlahan_negative_2018]. On the other side, food-web theory focused more on
-population stability. It shows that the strength [@may_will_1972;
-@mccann_weak_1998; @thebault_trophic_2005] and distribution [@may_will_1972;
-@angelis_stability_1975; @mccann_weak_1998; @mccann_reevaluating_1997] of
-species interactions determine population stability ("complexity-stability"
-theory) and stability-richness relationship [two trophic level systems,
-@thebault_trophic_2005; @ives_stability_2007], while the number of trophic
-levels determine population stability [@shanafelt_stability_2018]. Food-web
-structure also interacts with response diversity to determine population
-stability in diamond shaped food-webs [@ripa_food_2003;
-@vasseur_environmental_2007; @ruokolainen_environmental_2013]. So far, food-web
-theory overlooked the effects of food-web structure on response diversity and
-asynchrony while BEF theory overlooked the complex effects of food-web structure
-on population stability and asynchrony. Two keys advances allow to overcome that
-limitation: the development of the Bioenergenetic model that enable to model
-arbitrary complex communities [@yodzis_body_1992; @brose_allometric_2006] and
-the development of statistical tools that enables to partition community
-stability into population stability and asynchrony [@thibaut_understanding_2013;
-@zhao_biodiversity_2022].
-
-Here, we investigated the effects of species richness and community structure on
-community stability and on stability-richness relationship in complex stochastic
-food-web. To do so, we developed an extension of the Bioenergetic model
-[@brose_allometric_2006; @lajaaiti_ecologicalnetworksdynamicsjl_2024] which
-includes environmental stochasticity and response diversity
-[@vasseur_environmental_2007]. We modelled food-web varying in size (species
-richness XX) and structure (Connectance XX, Predator-Prey Mass Ratio: XX) to
-create a diversity of community structure. We additionally varied the
-variability of environmental stochasticity (standard deviation of mortality
-rates) and response diversity ($1-\rho$, $\rho$ being the correlation among
-species mortality rates). We performed XXXXX simulations over a minimum 2000
-timesteps (Table S1) and collected the 500 last timesteps to compute community
-stability and structure. Using a structural equation model, we deciphered the
-ways in which stressors (environmental stochasticity, decreasing response
-diversity) and community structure (species richness, average interaction
-strength, average trophic level, connectance) determine community stability. In
-a second time, we used a linear model to investigate how community structure
-interact with response diversity to determine the sign of the stability-richness
-relationship.
-
----
-#Here we deliver inference from modelling of complex biodiverse communities on
-#how food-web structure (connectance, average interaction strength, average
-#trophic level), response diversity, and environmental stochasticity combine to
-#shape temporal stability of community biomass, as well as its partition into
-#asynchrony and population stability. We then assess how food-web complexity and
-#response diversity shape stability-richness relationships.
-
-#Environmental forcing (such as food availability and
-#warming) and land-use intensity was reported to synchronise population
-#fluctuations [@benton_population_2001; @bluthgen_land_2016; @song_reduced_2015;
-#@liu_aridity_2023] while habitat degradation tends to decrease population
-#stability [@olivier_urbanization_2020]. Understanding the effects of global
-#change on community temporal stability therefore require to account for their
-#simultaneous effects on community and population scales [@kefi_advancing_2019;
-#@simmons_refocusing_2021].
-
-#Increasing species richness has been reported to decrease population stability
-#in experimental grasslands [@tilman_biodiversity_2006;
-#@roscher_identifying_2011], while increasing population stability in natural
-#settings [@houlahan_negative_2018] [add mechanisms?]. In turn, higher species
-#richness often results in higher asynchrony, through portfolio effects (i.e.
-#statistical averaging effects due to independent species fluctuations) and
-#compensatory dynamics (due to species interactions and response diversity of
-#species due to the environment) [@loreau_species_2008;
-#@thibaut_understanding_2013]. Systematic increase in asynchrony with species
-#richness is the mechanism that drives reported positive relationships between
-#community stability and species richness [ref]. Anthropogenic pressures, such as
-#eutrophication, has been reported to weakens the relationship between species
-#richness and asynchrony in grasslands [@hautier_eutrophication_2014] but such
-#empirical evidence remains scarce. However, stressors such as biotic
-#homogenization [@buisson_toward_2013; @muthukrishnan_invasive_2020;
-#@saladin_rapid_2020] and environmental forcing that decrease species response
-#diversity should dampens the relationships between asynchrony and species
-#richness [@ives_stability_2000; @thibaut_understanding_2013] due to a decrease
-#in portfolio effects and compensatory effects. [Talk about the effects of
-#evenness in temporal variability and evenness in abundance? e.g.,
-#@zhao_biodiversity_2022; @thibaut_understanding_2013]. Because stressors can
-#affect both community stability per se and how community stability scales with
-#species richness, improving our understanding require to study both
-#[@ives_stability_2007; @hautier_anthropogenic_2015].
-
-#including levels of generalism, the distribution of interaction strengths and
-#the prevalence of omnivory, can also influence stability. The degree of
-#generalism of predator was shown to modulate stability-richness relationships
-#[@thebault_trophic_2005], and generalist predators can synchronise the dynamics
-#of their preys[@raimondo_interspecific_2004]. The strength and distribution of
-#interaction strength was also shown to be strong driver of community stability,
-#such as stronger interaction strengths can be destabilizing [@may_will_1972;
-#@mccann_weak_1998]. Omnivory was also shown to drive higher population stability
-#[@mccann_reevaluating_1997]. The effects of food-web structure on ecosystem
-#stability has been mostly assessed with small modules [but see
-#@eschenbrenner_diversity_nodate], and we know very little how food-web structure
-#affects the relationships between species richness and temporal stability in
-#complex food-webs. So understanding the effects of stressors on community
-#stability and on community stability-richness relationships necessitate to
-#account for food-web structure.
----
+Ecological communities are facing ever-growing environmental variability caused
+by climate and environmental change[@lee_ipcc_2023;
+@simmons_refocusing_2021]. Decreases in the temporal stability of communities
+are increasingly documented[@olivier_urbanization_2020;
+@de_boeck_patterns_2018; @hansen_climate_2013; @bluthgen_land_2016; @harris_biological_2018], raising
+concerns about the long-term consequences at the ecosystem scale. Repeated calls
+have been made to clarify the role of environmental stochasticity in driving the
+temporal stability of ecological communities[@yang_predictability_2019]. It
+remains challenging because species have a diversity of response to
+environmental change [@elmqvist_response_2003; @loreau_species_2008;
+@ives_stability_2000; @ross_how_2023] (“response diversity”) and they are
+entangled in complex communities such as food-webs, that both ultimately drive
+community stability[@may_will_1972; @angelis_stability_1975; @mccann_weak_1998;
+@mccann_reevaluating_1997; @thebault_stability_2010] and stability-richness
+relationships[@thebault_trophic_2005; @thebault_relationship_2006]. Despite the
+overarching effects of response diversity and food-web structure on temporal
+community stability, they have been so far studied in isolation.
+
+The temporal stability of ecological communities stems from average population
+stability and asynchrony of population fluctuations[@thibaut_understanding_2013;
+@zhao_biodiversity_2022]. While higher environmental stochasticity/variability
+decrease population stability by increasing the amplitude species oscillations,
+higher species response diversity increases asynchrony of species
+fluctuations[@doak_statistical_1998; @loreau_species_2008;
+@thibaut_understanding_2013]. This is increasingly well-established in
+simplified species assemblages, where high response diversity increases
+asynchrony and is the determinant of positive stability-diversity relationships
+across many taxa[@tilman_biodiversity_2006; @olivier_urbanization_2020;
+@zhao_biodiversity_2022]. However, it remains largely unknown how the effects of
+environmental stochasticity and response diversity on population stability and
+asynchrony are mediated in the context of complex communities, such as
+food-webs.
+
+Complexity-stability theory well documented that the structure of food-webs
+determines population stability [@may_will_1972; @angelis_stability_1975;
+@mccann_weak_1998; @mccann_reevaluating_1997; @vasseur_environmental_2007;
+@eschenbrenner_diversity_2023], and stability-richness relationships
+[@thebault_trophic_2005; @thebault_relationship_2006]. Population stability is
+indeed documented to decrease with increasing interaction strength
+[@may_will_1972; @mccann_weak_1998], connectance [@may_will_1972], but to be
+higher at higher trophic level [@shanafelt_stability_2018; @danet_species_2021].
+In result, the distribution and strength of species interactions, as well as
+trophic level might have a strong effect on community stability and
+stability-richness relationships [@thebault_trophic_2005;
+@thebault_relationship_2006]. This expectation is reinforced by documented
+examples where predators can mediate the effect of response diversity on
+asynchrony [@vasseur_environmental_2007], and synchronise the dynamics of their
+prey [@raimondo_interspecific_2004; @korpimaki_predatorinduced_2005]. Recent
+study in plant communities suggests that asynchrony stems mainly from the
+statistical averaging of independent species fluctuations (“portfolio effects”),
+rather than compensatory dynamics resulting from response diversity and species
+interactions [@zhao_biodiversity_2022]. But we might expect that prey switching
+and trophic cascades arising in food-webs lead to higher compensatory dynamics
+than in plant communities [@mccann_diversitystability_2000;
+@fahimipour_compensation_2017].
+
+Here, we investigated the effects of response diversity and food-web structure
+on community stability and on stability-richness relationships in stochastic
+environment. To do so, we developed an extension of the Bioenergetic food web
+model [@brose_allometric_2006; @lajaaiti_ecologicalnetworksdynamicsjl_2024]
+which includes environmental stochasticity and response diversity
+[@loreau_species_2008; @vasseur_environmental_2007; @ripa_food_2003]. We
+included environmental stochasticity on allometric natural death rate, such as
+species of higher trophic level had lower death rate in
+average[@vasseur_environmental_2007], response diversity was included as the
+inverse of species correlation in their mortality rates.  We first decipher the
+respective effects of food-web structure, environmental stochasticity, and
+response diversity on community stability and its partition into population
+stability and asynchrony (i.e. portfolio and compensatory effects). We then
+investigate how food-web structure and response diversity interact to determine
+the sign of stability-richness relationship.
+
+```{r}
+tar_load(sim_param_tab)
+p_mm <- function(
+  v = "S",
+  data = sim_param_tab
+) {
+  out <- data[data$Parameter %in% v, ]
+  paste0("", signif(out[["min"]], 1), "-", signif(out[["max"]], 1), "")
+}
+```
+
+```{r, eval = FALSE}
+p_mm("ct")
+```
+
+# Results
+
+```{r}
+sem_cap <- paste0(
+  "Structural Equation Model linking food-web structure and stressors to temporal
+  stability of community biomass. a, continuous red arrows display positive and
+  dashed blue arrows display negative standardised effects, width of the arrows
+  being proportional to the absolute values of the standardised effects. Only
+  the standardised coefficients whose absolute values are superior to 0.05 are
+  displayed. The full table of coefficients including control variables is
+  displayed in Table S4. A more complete SEM containing further partition of
+  compensatory effects and control variables is displayed in Table S5. b, total
+  effects of food-web structure on community stability, asynchrony, and
+  population stability. N = ", nrow(tar_read(sim_fw)), " simulations.") %>%
+  str_replace_all("\\s+", " ")
+```
+
+```{r sem, fig.cap=sem_cap, fig.id = "sem"}
+knitr::include_graphics(here("report", "figures", "p_sem_fig.pdf"))
+```
+
+```{r}
+tar_load(c(sem_doak_eff_tab, sem_simplified_eff_tab))
+
+```
+
+```{r fig2-coeff, eval = FALSE}
+tar_read(sem_fig_coeff)
+tar_read(sem_doak_rsquared_csc_rerun)
+```
+
+```{r}
+tar_load(sim_summary_stat)
+m_sim <- function(
+  v = "stab_com",
+  data = sim_summary_stat,
+  col = "Median (5%, 95%)"
+  ) {
+  data[data$var %in% v, ][[col]]
+}
+```
+```{r, eval = FALSE}
+m_sim(v = c("stab_com", "async"))
+m_sim(c("stab_com", "async"))
+m_sim(col = "n")
+```
+
+## Drivers of community stability, population stability and asynchrony
+
+```{r}
+get_eff <- function(
+  y = "pop_stab", x = "richness",
+  d = 2, effect_type = "direct",
+  tab = sem_doak_eff_tab) {
+  mask <- tab$response == y & tab$predictor == x &
+    tab$effect_type == effect_type
+  round(tab[mask, ]$effect, d)
+}
+
+rpt <- get_eff(y = "pop_stab", x = "w_avg_tlvl")
+rpc <- get_eff(y = "pop_stab", x = "c")
+rpe <- get_eff(y = "pop_stab", x = "env_stoch")
+rpd <- get_eff(y = "pop_stab", x = "resp_div")
+
+rsr <- get_eff(y = "sae_doak", x = "richness")
+rst <- get_eff(y = "sae_doak", x = "w_avg_tlvl")
+rsi <- get_eff(y = "sae_doak", x = "avg_int_strength")
+rsc <- get_eff(y = "sae_doak", x = "ct_alive")
+
+rcr <- get_eff(y = "cpe_int", x = "richness")
+rci <- get_eff(y = "cpe_int", x = "avg_int_strength")
+rct <- get_eff(y = "cpe_int", x = "w_avg_tlvl")
+rcd <- get_eff(y = "cpe_int", x = "resp_div")
+rcc <- get_eff(y = "cpe_int", x = "ct_alive")
+
+# Detailled SEM coefficients
+rsr <- get_eff(y = "sae_doak", x = "richness")
+rst <- get_eff(y = "sae_doak", x = "w_avg_tlvl")
+rsr <- get_eff(y = "sae_doak", x = "richness")
+rsa <- get_eff(y = "sae_doak", x = "avg_int_strength")
+rsct <- get_eff(y = "sae_doak", x = "ct_alive")
+rsc <- get_eff(y = "sae_doak", x = "c")
+rsd <- get_eff(y = "sae_doak", x = "resp_div")
+
+```
+
+```{r}
+rscp <- get_eff(y = "stab_com", x = "pop_stab")
+rsca <- get_eff(y = "stab_com", x = "async")
+
+rac <- get_eff(y = "async", x = "cpe")
+ras <- get_eff(y = "async", x = "sae_total")
+```
+
+The `r format(m_sim(col = "n"), scientific = FALSE)` simulations generated a
+wide range of food-web structure (Median (5%, 95%), species richness:
+`r m_sim("richness")`, connectance: `r m_sim("ct_alive")`, average interaction
+strength: `r m_sim("avg_int_strength")`, maximum trophic level:
+`r m_sim("max_tlvl")`). We quantified the  (1) the respective effects of
+population
+stability and asynchrony on community stability, (2) the source of asynchrony,
+either portfolio effects or compensatory dynamics, and disentangled (3) how
+stressors (environmental stochasticity, response diversity) and food-web
+structure (species richness, average interaction strength, average trophic
+level, connectance) determine average population stability, portfolio effects
+(using Doak's definition), and compensatory dynamics stemming from species
+interactions. We did so by using a structural equation model which included all
+the simulation variables as control (i.e. predator interference, predator-prey
+mass ratio) to avoid the detection of spurious non-causal effects (See Methods,
+Table/Figure SXX). Overall, we found that population stability had a positive
+effect twice higher than asynchrony on the temporal stability of community
+biomass (resp. $r_\delta$= `r rscp` and `r rsca`, $r_\delta$ being the
+standardised coefficient, Fig. \@ref(fig:sem)a). We further found that
+asynchrony was driven more by portfolio effects than by compensatory dynamics
+stemming from species interactions (resp. $r_\delta$= `r rac` and `r ras`).
+However, we found opposite results, i.e. that compensatory dynamics contributed
+more than portfolio effects to asynchrony, using an alternative portfolio
+effects definition that attributes the effects of response diversity to
+compensatory effects instead of portfolio effects (Fig. SXX).
+
+Food-web structure had consistent negative effects on asynchrony, mainly through
+portfolio and compensatory effects (Fig. \@ref(fig:sem)a). Indeed, average
+trophic level and connectance had negative effects on the compensatory effects
+stemming from species interactions (resp. $r_\delta$= `r rct` and `r rcc`, Fig.
+\@ref(fig:sem)a), while average interaction strength had a small negative
+effects on portfolio effects ($r_\delta$= `r rsi`). In contrast, response
+diversity and species richness had strong positive effects on asynchrony,
+mainly through portfolio effects. Response diversity had a strong positive
+effect on portfolio effects ($r_\delta$= `r rsd`), and a negative one on
+compensatory dynamics ($r_\delta$= `r rcd`). In turn, species richness had a
+positive effect on both portfolio and compensatory effects (resp.
+$r_\delta$=`r rsr` and `r rcr`). Finally, environmental stochasticity had a
+small negative effect on compensatory dynamics.
+
+In turn, we found little effect of food-web structure on population stability,
+except for average trophic level having a strong positive effect on
+population stability ($r_\delta$= `r rpt`, Fig. \@ref(fig:sem)a). In turn, the
+variance of environmental stochasticity had a strong negative effect on
+population stability ($r_\delta$= `r rpe`), while response diversity had a small
+positive effect on population stability ($r_\delta$= `r rpd`).
+
+```{r}
+rtsdiv <- get_eff(y = "stab_com", x = "resp_div", effect_type = "total")
+rtsenv <- get_eff(y = "stab_com", x = "env_stoch", effect_type = "total")
+
+rtsr <- get_eff(y = "stab_com", x = "richness", effect_type = "total")
+rtst <- get_eff(y = "stab_com", x = "w_avg_tlvl", effect_type = "total")
+rtsz <- get_eff(y = "stab_com", x = "Z", effect_type = "total")
+rtsc <- get_eff(y = "stab_com", x = "c", effect_type = "total")
+rtsct <- get_eff(y = "stab_com", x = "ct_alive", effect_type = "total")
+rtsi <- get_eff(y = "stab_com", x = "avg_int_strength", effect_type = "total")
+
+rtpr <- get_eff(y = "pop_stab", x = "richness", effect_type = "total")
+rtpt <- get_eff(y = "pop_stab", x = "w_avg_tlvl", effect_type = "total")
+rtpi <- get_eff(y = "pop_stab", x = "avg_int_strength", effect_type = "total")
+rtpz <- get_eff(y = "pop_stab", x = "Z", effect_type = "total")
+rtpc <- get_eff(y = "pop_stab", x = "c", effect_type = "total")
+rtpct <- get_eff(y = "pop_stab", x = "ct_alive", effect_type = "total")
+
+rtar <- get_eff(y = "async", x = "richness", effect_type = "total")
+rtat <- get_eff(y = "async", x = "w_avg_tlvl", effect_type = "total")
+rtai <- get_eff(y = "async", x = "avg_int_strength", effect_type = "total")
+rtaz <- get_eff(y = "async", x = "Z", effect_type = "total")
+rtac <- get_eff(y = "async", x = "c", effect_type = "total")
+rtact <- get_eff(y = "async", x = "ct_alive", effect_type = "total")
+```
+
+Deriving the sum of direct and indirect effects from the structural equation
+model, we show that both the variance of environmental stochasticity and species response
+diversity had by far the most important effects on community stability (resp.
+$r_\delta$= `r rtsenv` and `r rtsdiv`, Fig. \@ref(fig:sem)b). Species richness
+and average trophic level had similar positive total effects on community stability
+($r_\delta$=`r rtsr`), but through opposite pathways and antagonistic effects on
+asynchrony and population stability. While species richness increased community
+stability through a strong positive effect on asynchrony ($r_\delta$=`r rtar`), it
+also weakly decreased population stability ($r_\delta$=`r rtpr`). At the opposite, average
+trophic level increased community stability through strong positive effect on
+population stability ($r_\delta$=`r rtpt`), but dampened by a negative total
+effect on asynchrony ($r_\delta$=`r rtat`). Interestingly, average interaction
+strength also had a positive effect on population stability and a negative one
+on asynchrony (resp. $r_\delta$= `r rtpi` and `r rtai`), but resulting in a
+total negative effect on community stability ($r_\delta$= `r rtsi`).
+Connectance, instead, had a negative effect on community stability ($r_\delta$=
+`r rtsct`) through consistent negative effects on asynchrony and population
+stability (resp. $r_\delta$=`r rtact` and `r rtpct`).
+
+## Stability-richness relationship
+
+```{r}
+tar_load(default_variable_values_pred)
+pv <- default_variable_values_pred
+
+pv_cap <- paste0(
+  "connectance = ", round(pv["ct_alive"], 2),
+  ", average interaction strength = ", round(pv["avg_int_strength"], 3),
+  ", average trophic level = ", round(pv["w_avg_tlvl"], 2),
+  ", predator interference = ", round(pv["c"], 1),
+  ", Predator-Prey Mass Ratio = ", round(pv["Z"]),
+  ", and environmental stochasticity = ", round(pv["env_stoch"], 1)
+
+)
+pred_cap <- paste0("Slope of the community stability - species
+  richness relationship according to food-web structure and response diversity. (a),
+  Diagrams displaying the slope coefficients of the effect of species richness
+  on community stability. The average values of the control variables were used
+  to generate the predictions: ", pv_cap, ". (b, c): Examples of predictions
+  from the model for two combinations of average trophic level and response
+  diversity (values displayed in panel (a)). Lines display the mean predictions
+  of the model. The coefficients of the linear model are displayed in Fig. S4.
+  Relationships between population stability, asynchrony and species richness
+  are displayed in Fig. S5."
+  ) %>%
+  str_replace_all("\\s+", " ")
+```
+
+```{r pred, fig.cap = pred_cap, fig.id = "pred"}
+knitr::include_graphics(here("report", "figures", "p_fig3.pdf"))
+```
+
+Using a more complex linear model including interactions among food-web
+structure, response diversity and environmental stochasticity, we found that
+food-web structure strongly interacts with response diversity to determine the
+sign of the stability-richness relationships. In the absence of response
+diversity, we found only negative stability-richness, regardless of the food-web
+structure (Fig. \@ref(fig:pred)a). Response diversity enabled the rise of
+positive stability-richness relationships, enhanced by average interaction
+strength and dampened by average trophic level and connectance. Higher
+interaction strength led to positive stability-richness relationships for lower
+values of response diversity, interaction strength enhanced asynchrony-richness
+relationships (Fig. SXX), so that the stronger positive stability-richness
+relationships were found at both high interaction strength and response
+diversity. In contrast, higher average trophic level and connectance both led to
+negative stability-richness relationships, because they led to more negative
+population stability-richness relationships and weaker positive
+asynchrony-richness relationships (Fig. SXX). Overall, our results highlight
+strong contrast between the relatively small effects of food-web structure on overall
+community stability (Fig. \@ref(fig:sem)b) and their strong effects on
+stability-richness relationships (Fig. \@ref(fig:pred)a).
+
+```{r, eval = FALSE}
+tar_read(p_int_fw_str)
+```
+
+# Discussion
+
+Temporal community stability is well documented in simplified assemblages
+such as plant communities, where community stability is driven by asynchrony in
+species fluctuations. In contrast, our results show that community stability in
+complex food-webs was mainly driven population stability rather than asynchrony.
+In the range of our simulations, we identified that environmental variability
+and response diversity were the main driver of community stability, far more
+than any food-web structure component, a result consistent across methodological
+choices (Fig. SXX). Moreover, we found that species richness and food-web
+structure have antagonistic but consistent effect on community stability.
+Finally, we found that the sign of the stability-richness relationship is
+strongly mediated by the interaction between food-web structure and response
+diversity. These results highlight the need to account for both food-web
+structure and response diversity to improve our understanding of the stability
+of ecological communities in variable environments.
+
+Our results show that community stability in complex food-webs is mainly driven
+by population stability rather than synchrony, which contrasts with empirical
+data that reported an equivalent influence of population stability and
+asynchrony on community stability in birds and bats assemblages
+[@olivier_urbanization_2020]. However, our results are in accordance with
+previous findings in empirical food-webs [@danet_species_2021] and
+food-web models [@eschenbrenner_diversity_2023]. Are there fundamental
+differences between single trophic and food-web in the contribution of
+population stability and asynchrony? We found that all food-web metrics, i.e.
+average trophic level, connectance, and average interaction strength all
+decreased asynchrony. In line with previous studies showing that predators can
+synchronise their preys [@raimondo_interspecific_2004;
+@kortsch_disentangling_2021], and that predator-prey couples are more
+synchronous [@danet_species_2021], those results suggest that trophic links
+might dampen overall asynchrony in ecological communities. A complementary
+explanation could be related to the biomass structure of food-webs. Food-webs
+typically includes range of bodymasses much larger than in species assemblages,
+differing in bodymass by several orders of magnitude [@brose_predator_2019].
+This highly uneven biomass distribution can translate in uneven species
+variability, thereby creating uneven contributions of species to asynchrony
+[@thibaut_understanding_2013] and limits portfolio effects and compensatory
+dynamics in species rich communities [@zhao_biodiversity_2022]. The fact that
+average trophic level, connectance, and average interaction strength all
+decreased evenness of portfolio effects lends toward this hypothesis. Our
+results then reinforce the evidence that community stability in food-web might
+be driven more by population stability than asynchrony.
+
+We further found that asynchrony was driven more by portfolio effects than
+compensatory dynamics. But this results was dependant of the definition of
+portfolio effects, as we found the opposite while taking Tilman's
+definition[@tilman_ecological_1999; @zhao_biodiversity_2022] instead of Doak's
+one[@doak_statistical_1998], in contrast with previous assessment in
+experimental plant communities[@zhao_biodiversity_2022]. Portfolio effects is
+supposed to measure stabilising effects of species richness in the absence of
+species interactions[@loreau_biodiversity_2021]. While Tilman's considers that
+portfolio effects are emerging from statistical averaging of independent species
+fluctuations alone (i.e. in the absence of covariance among species), Doak's
+explicitly states that statistical averaging can only emerge if compensatory
+dynamics hold by response diversity is present[@zhao_biodiversity_2022]. While
+the definition of portfolio effects is a long-standing
+debate[@zhao_biodiversity_2022], our results show that the importance of
+portfolio effects depends on where response diversity acts. In agreement with
+previous studies[@loreau_species_2008; @doak_statistical_1998;
+@thibaut_understanding_2013; @loreau_biodiversity_2021], we believe that the
+definition of portfolio effects standing from statistical averaging and
+environmental compensatory dynamics generated by response diversity is the more
+appropriate as the absence of species interactions does not guarantee independent
+species fluctuations, because common environment tend to generate positive
+covariances among species[@loreau_biodiversity_2021]. The fact that
+environmental stochasticity alone had a really small effect on asynchrony to the
+difference of response lends toward this interpretation. So, our study suggests
+that response diversity is a key ingredient to generate asynchrony, not only in
+plant communities, but also in food-webs. We further show that explicitly
+manipulating response diversity highlight that it is the main driver of
+asynchrony, and that the respective contribution of portfolio effects and
+compensatory dynamics to asynchrony depends on the decision to consider that
+response diversity is part of portfolio effects or compensatory dynamics.
+
+We further found that higher average trophic level lead to higher community
+stability by increasing average population stability, confirming previous
+theoretical[@brose_allometric_2006; @shanafelt_stability_2018;
+@eschenbrenner_diversity_2023] and empirical[@danet_species_2021] results. But
+this effect disappeared when we simulated community dynamics with equal
+mortality rates for all species instead of allometric ones (Fig. S1). It then
+suggests that higher stability of food-web with higher average trophic level is
+because of species life-history traits and not directly by species interactions.
+The assumption that natural mortality rates decreased with bodymass is well
+documented across eukaryotes[@hatton_linking_2019] and seems to be a necessary
+ingredient for the stabilising effects of higher trophic levels. In turn, we
+found that average trophic level and connectance decreases strongly asynchrony
+mainly through a negative effect on compensatory dynamics generated by species
+interactions. Both higher connectance and average trophic level lead to greater
+generalism of predators in the niche model that we used to build food-webs. The
+synchronising effects of average trophic level and connectance echo with
+empirical findings that a generalist predator can indeed synchronise the
+dynamics of numerous preys[@raimondo_interspecific_2004;
+@korpimaki_predatorinduced_2005]. The overall effect of connectance on overall
+community stability was quite low, in agreement with previous empirical
+findings[@danet_species_2021]. Similarly, we found very low effects
+of the average interaction strength on community stability which in apparent
+disagreement with the predominant role of interaction strength and connectance
+on stability in the complexity-stability debate [complexity-stability paradox,
+@may_will_1972]. But our study focused on the temporal stability of coexisting
+species at steady state, which might mask connectance and interaction strength
+values that led to species extinctions during the transient phase.
+
+We found that species richness had a positive effect on community stability of
+the same importance as average trophic level, but through opposite pathways.
+Species richness had strong positive effects on asynchrony through positive
+effects on portfolio and compensatory effects. It is in agreement with previous
+study showing that species richness can promote asynchrony by both
+pathways[@zhao_biodiversity_2022]. Furthermore, our study shows that the positive
+effects of species richness on asynchrony is three times lower than the effects
+of response diversity. Our model predictions further indicates that in absence
+of response diversity, we only observe negative relationships between
+community stability and species richness. Therefore, it reinforces the idea that
+response diversity is the crucial ingredient that hold the observed
+positive effects of species richness on community stability and not species
+richness alone[@thebault_trophic_2005; @loreau_species_2008;
+@loreau_biodiversity_2021]. In return, species richness had a small negative
+effect on average population stability. It is in agreement with previous
+meta-analysis reporting that such negative effects are common in natural systems
+but weak[@houlahan_negative_2018], but the mechanisms behind this relationship
+are still debated. Overall our study highlights that the central role of
+response diversity and species richness on asynchrony and thus community
+stability also extends to complex food-webs.
+
+Our results further show that food-web structure interact strongly with response
+diversity to determine the sign of stability-richness relationships. We found
+surprisingly that higher average interaction strength enhance positive
+stability-richness relationships, by enhancing asynchrony-richness
+relationships. At the opposite, higher average trophic level and higher
+connectance both led to negative stability-richness, by dampening
+asynchrony-richness relationships. Our result echoes with previous results
+showing negative stability-richness relationship in freshwater
+food-webs[@danet_species_2021]. Those results also echo with the
+complexity-stability debate where population stability decreases as the
+community is more species diverse, has higher connectance, and higher
+interaction strength[@may_will_1972]. However, we found that the negative
+effects of complexity on stability-richness relationships are dampened in
+presence of high response diversity. Response diversity might then be one of the
+mechanisms that explains why positive relationships between stability and
+species richness are so prevalent in empirical settings while food-web
+theoretical models that do not often include environmental stochasticity and
+response diversity finds negative complexity-stability
+relationships[@ives_stability_2007]. It is also in agreement previous studies
+showing that higher connectance in low response diversity can drive negative
+stability-richness in plant-herbivore systems[@thebault_trophic_2005]. Finally,
+found that the strength of environmental stochasticity itself does not
+affect the shape of the community stability-richness but rather controls the
+overall community stability through its effects on population stability.
+
+In conclusion, our study uncovers complex but consistent effects of response
+diversity and food-web structure on the temporal stability of complex
+communities. We showed that community stability was more driven by population
+stability than asynchrony. We further showed that species richness and average
+trophic level both increase community stability but by opposite pathways. Our
+study also demonstrates that response diversity is the core mechanism driving
+the buffering effects of biodiversity on environmental stochasticity also in
+complex food-webs. Finally, our study shows that food-web structure and response
+diversity interact to drive a continuum from negative to positive
+stability-richness relationships. Looking to practical applications, our study
+highlights that species richness without response diversity does not lead to
+positive community-richness relations. So that assessment on how ecological
+communities widespread recomposition[@dornelas_assemblage_2014;
+@blowes_geography_2019] and homogenisation[@olden_homogocene_2018;
+@muthukrishnan_invasive_2020; @wang_biotic_2021] is affecting response diversity
+would be crucial to accurately predict long-term consequences on community
+stability. The second take away to be drawn is that the variance of
+environmental stochasticity was the main driver of community stability,
+suggesting that increase in species richness and the maintenance of high
+response diversity would be not enough to compensate for strong increase in
+environmental variability in the coming decades[@lee_ipcc_2023].
 
@@
 metabolic theory of ecology [@brown_toward_2004]. The model describes species
-biomass dynamics over time with two master equations (eq. \@ref(eq:dbdt)), one
-for the primary producers (eq. \@ref(eq:prod)) and one for the consumers (eq.
-\@ref(eq:prod)):
-
-\begin{subequations}
-    \label{eq:dbdt}
+biomass dynamics over time with two master equations, one for the primary
+producers (eq. \@ref(eq:prod)) and one for the consumers (eq.\@ref(eq:cons)):
 
 \begin{equation}
-        \label{eq:cons}
+    (\#eq:cons)
         \frac{dB_i}{dt} =
@@
 \begin{equation}
-    	\label{eq:prod}
+    (\#eq:prod)
 	\frac{dB_i}{dt} =
@@
 \end{equation}
-\end{subequations}
 
@@
 
-\begin{subequations}
-    \label{eq:func}
 \begin{equation}
-        \label{eq:growth}
+    (\#eq:growth)
     G_i = (1 - \dfrac{\sum_{j \in \{\mathrm{prod}\}} \alpha_{ij} B_j}{K_i})
@@
 \begin{equation}
-    	\label{eq:holling}
+    (\#eq:holling)
     F_{ij} = \frac{\omega_{ij} B_j^h}
@@
 To further get a mechanistic insight about the effects of stressors and food-web
-structure on stability, we partitioned asynchrony into portfolio effects (measured by statistical averaging
-effect, SAE) and compensatory dynamics effect (CPE) [@zhao_biodiversity_2022].
-SAE quantities the portfolio effect emerging from independent species
-fluctuations, while CPE describes compensatory dynamics deviating from portfolio
-effects, and emerging from species interactions and differential responses to
-environmental stochasticity.
+structure on stability, we partitioned asynchrony into portfolio effects and
+compensatory dynamics stemming from species interaction[@zhao_biodiversity_2022]
+($CPE_{int}$). The measurement of portfolio effects has been a topic of
+debate[@loreau_biodiversity_2021;@zhao_biodiversity_2022]. Doak's
+definition[@doak_statistical_1998] defines portfolio effects as the product of
+statistical averaging effects ($SAE$) and compensatory effects arising from
+response diversity[@zhao_biodiversity_2022; @doak_statistical_1998]
+($CPE_{env}$). It then quantities the portfolio effect ($PFE = SAE \times
+CPE_{env}$) emerging from independent species fluctuations, i.e. the statistical
+averaging effect ($SAE$), weighted by the effects of response diversity of
+species to environmental fluctuations, such as portfolio effects are dampened if
+species have correlated responses. For completeness and comparison with previous
+studies, we also measured portfolio effects according to Tilman's
+definition[@tilman_ecological_1999] which consider that portfolio effects stem
+solely from a pure statistical averaging of independent species fluctuations
+($SAE$).
 
@@
 
-\begin{equation}
-\begin{aligned}
-SAE = SAE_{even} \times EVN
-(\#eq:sae)
-\end{aligned}
-\end{equation}
-
 Statistical averaging effect is the share of asynchrony assuming that species are
@@
 SAE &= \dfrac{S_{com, IP}}{S_{pop}} = \dfrac{\sum_i \sigma_i}{\sqrt{\sum_i \sigma^2_i}}\\
+\end{aligned}
 (\#eq:sae2)
-\end{aligned}
-\end{equation}
-
-As SAE is further dependent on the evenness of species variance, we
-partitioned $SAE$ into $SAE_{even}$ and evenness $EVN$, such as  $EVN = SAE / SAE_{even}$.
-$SAE_{even}$ corresponds to the $SAE$ when species quantities are perfectly
-even such as from eq. \@ref(eq:sae2), we can obtain $SAE_{even}$ from which
-$EVN$ can be computed:
-
-\begin{equation}
-\begin{aligned}
-SAE &= \dfrac{\sum_i \sigma_i}{\sqrt{\sum_i \sigma^2_i}} = \sqrt{\dfrac{1}{\sum_i (\sigma_i\sigma^2_i})^2} = \sqrt{\dfrac{1}{\sum_i (p_i)^2}}\\
-SAE_{even} &= \sqrt{\dfrac{1}{\sum_i (1/S)^2}}\\
-SAE_{even} &= \sqrt{S}\\
-(\#eq:sae-even)
-\end{aligned}
 \end{equation}
@@
 CPE &= \dfrac{S_{com}}{SAE \times S_{pop}} = \dfrac{\sqrt{\sum_i \sigma^2_i}}{\sigma_{tot}}\\
+\end{aligned}
 (\#eq:cpe)
-\end{aligned}
 \end{equation}
@@
 \begin{aligned}
-CPE_{env} = \mathbf{B} \times \mathrm{diag}(d_i) \times e^\mathbf{E}
+CPE_{env} &= \mathbf{B} \times \mathrm{diag}(d_i) \times e^\mathbf{E}
+\end{aligned}
 (\#eq:cpenv)
-\end{aligned}
 \end{equation}
@@
 from species interactions were computed as: $CPE_{int} = CPE / CPE_{env}$.
+Finally, portfolio effects was computed as: $SAE \times CPE_{env}$ and
+compensatory dynamics raising from species interactions as $CPE_{int}$.
 
@@
 and from asynchrony and population stability to community stability. We further
-developed a more detailled SEM including the effects omnivory and partition of
-compensatory dynamics due to species interactions ($CPE_{int}$) and due to
-environmental fluctuations ($CPE_{env}$).
+developed a more detailed SEM including the partition of compensatory dynamics
+due to species interactions ($CPE_{int}$) and due to environmental fluctuations
+($CPE_{env}$).
 
@@
 
-# Results
-
-## Drivers of stability
-
-```{r}
-sem_cap <- paste0(
-  "Structural Equation Model linking food-web structure and stressors to temporal
-  stability of community biomass. a, continuous red arrows display positive and
-  dashed blue arrows display negative standardised effects, width of the arrows
-  being proportional to the absolute values of the standardised effects. Only
-  the standardised coefficients whose absolute values are superior to 0.05 are
-  displayed. The full table of coefficients including control variables is
-  displayed in Table S4. A more complete SEM containing further partition of
-  compensatory effects and control variables is displayed in Table S5. b, total
-  effects of food-web structure on community stability, asynchrony, and
-  population stability. N = ", nrow(tar_read(sim_fw)), " simulations.") %>%
-  str_replace_all("\\s+", " ")
-```
-
-```{r sem, fig.cap=sem_cap, fig.id = "sem"}
-knitr::include_graphics(here("report", "figures", "p_sem_fig.pdf"))
-```
-
-```{r}
-tar_load(c(sem_main_text_eff_tab, sem_simplified_eff_tab))
-
-get_eff <- function(
-  y = "pop_stab", x = "richness",
-  d = 2, effect_type = "direct",
-  tab = sem_main_text_eff_tab) {
-  mask <- tab$response == y & tab$predictor == x &
-    tab$effect_type == effect_type
-  round(tab[mask, ]$effect, d)
-}
-
-rpt <- get_eff(y = "pop_stab", x = "w_avg_tlvl")
-rpc <- get_eff(y = "pop_stab", x = "c")
-rpe <- get_eff(y = "pop_stab", x = "env_stoch")
-rpd <- get_eff(y = "pop_stab", x = "resp_div")
-
-rsr <- get_eff(y = "sae_total", x = "richness")
-rst <- get_eff(y = "sae_total", x = "w_avg_tlvl")
-rsi <- get_eff(y = "sae_total", x = "avg_int_strength")
-rsc <- get_eff(y = "sae_total", x = "ct_alive")
-
-rcr <- get_eff(y = "cpe", x = "richness")
-rci <- get_eff(y = "cpe", x = "avg_int_strength")
-rcd <- get_eff(y = "cpe", x = "resp_div")
-
-# Detailled SEM coefficients
-rsr <- get_eff(y = "sae_total", x = "richness")
-ret <- get_eff(y = "evenness_sae", x = "w_avg_tlvl")
-rer <- get_eff(y = "evenness_sae", x = "richness")
-rea <- get_eff(y = "evenness_sae", x = "avg_int_strength")
-rect <- get_eff(y = "evenness_sae", x = "ct_alive")
-rec <- get_eff(y = "evenness_sae", x = "c")
-red <- get_eff(y = "evenness_sae", x = "resp_div")
-
-```
-
-```{r, eval = FALSE}
-tar_load(c(sem_fig_coeff))
-```
-
-We found that food-web structure had significant effects on temporal population
-stability such as average trophic level increase population stability (resp.
-$r_\delta$= `r rpt`, $r_\delta$ being the standardised coefficient,
-Fig. \@ref(fig:sem)a). In turn, the variance of environmental stochasticity had
-a strong negative effect on population stability ($r_\delta$= `r rpe`). We
-further found that response diversity had a small negative effect on population
-stability ($r_\delta$= `r rpd`).
-
-We further found that food-web structure had a strong impact asynchrony, raising
-from portfolio and compensatory effects. As expected the mathematical
-relationship (eq. \@ref(eq:sae-even)), species richness was a main positive
-driver of portfolio effects ($r_\delta$= `r rsr`, Fig. \@ref(fig:sem)a), thereby
-increasing asynchrony. In turn, species richness, average trophic level and
-connectance had negative effects on the evenness of species variability (resp.
-$r_\delta$= `r rer`, `r ret`, and `r rect`), thereby downplaying the portfolio
-effect raised from species richness alone in a scenario of even species
-variabilities. In turn, we found that response diversity had a positive effect
-on evenness of species variability ($r_\delta$=`r red`), thereby maximising the
-portfolio effect. We found that species response diversity had a strong positive
-effect on compensatory dynamics ($r_\delta$= `r rcd`), while average interaction
-strength had a small positive effect ($r_\delta$= `r rci`, Fig. \@ref(fig:sem)).
-
-```{r}
-
-rscp <- get_eff(y = "stab_com", x = "pop_stab")
-rsca <- get_eff(y = "stab_com", x = "async")
-
-rac <- get_eff(y = "async", x = "cpe")
-ras <- get_eff(y = "async", x = "sae_total")
-
-```
-
-Overall, we found that population stability had a positive effect twice higher
-than asynchrony on the temporal stability of community (resp. $r_\delta$=
-`r rscp` and `r rsca`). In turn, asynchrony was more driven by compensatory
-dynamics than portfolio effects (resp. $r_\delta$= `r rac` and `r ras`, Fig.
-\@ref(fig:sem)a).
-
-```{r}
-rtsdiv <- get_eff(y = "stab_com", x = "resp_div", effect_type = "total")
-rtsenv <- get_eff(y = "stab_com", x = "env_stoch", effect_type = "total")
-
-rtsr <- get_eff(y = "stab_com", x = "richness", effect_type = "total")
-rtst <- get_eff(y = "stab_com", x = "w_avg_tlvl", effect_type = "total")
-rtsz <- get_eff(y = "stab_com", x = "Z", effect_type = "total")
-rtsc <- get_eff(y = "stab_com", x = "c", effect_type = "total")
-rtsct <- get_eff(y = "stab_com", x = "ct_alive", effect_type = "total")
-rtsi <- get_eff(y = "stab_com", x = "avg_int_strength", effect_type = "total")
-
-rtpr <- get_eff(y = "pop_stab", x = "richness", effect_type = "total")
-rtpt <- get_eff(y = "pop_stab", x = "w_avg_tlvl", effect_type = "total")
-rtpi <- get_eff(y = "pop_stab", x = "avg_int_strength", effect_type = "total")
-rtpz <- get_eff(y = "pop_stab", x = "Z", effect_type = "total")
-rtpc <- get_eff(y = "pop_stab", x = "c", effect_type = "total")
-rtpct <- get_eff(y = "pop_stab", x = "ct_alive", effect_type = "total")
-
-rtar <- get_eff(y = "async", x = "richness", effect_type = "total")
-rtat <- get_eff(y = "async", x = "w_avg_tlvl", effect_type = "total")
-rtai <- get_eff(y = "async", x = "avg_int_strength", effect_type = "total")
-rtaz <- get_eff(y = "async", x = "Z", effect_type = "total")
-rtac <- get_eff(y = "async", x = "c", effect_type = "total")
-rtact <- get_eff(y = "async", x = "ct_alive", effect_type = "total")
-```
-
-Deriving the sum of direct and indirect effects from the structural equation
-model, we show that both environmental stochasticity and species response
-diversity to environmental fluctuations had by far the most important effects on
-community stability (resp. $r_\delta$= `r rtsenv` and `r rtsdiv`, Fig.
-\@ref(fig:sem)b). Species richness had a overall positive total effect on
-community stability ($r_\delta$=`r rtsr`), stemming from its strong total positive effect on
-asynchrony ($r_\delta$=`r rtar`) and downplayed by its small total negative effect on population
-stability ($r_\delta$=`r rtpr`), but population stability effect on community
-stability was twice higher than the one of asynchrony. Average trophic level and
-average interaction strength had small positive effects on community stability in
-total (resp. $r_\delta$=`r rtst`, `r rtsi`, Fig. \@ref(fig:sem)b), driven by their positive
-effects on population stability (resp. $r_\delta$=`r rtpt`, `r rtsi`). However,
-we found that average trophic level had a negative total effect on asynchrony
-($r_\delta$=`r rtat`), average interaction strength had a positive total effect
-($r_\delta$=`r rtai`). In turn, connectance had a small negative total effect on
-community stability ($r_\delta$=`r rtsct`), raising from a negative total effect
-on population stability ($r_\delta$=`r rtpct`) and a positive one on asynchrony
-($r_\delta$=`r rtact`, Fig. \@ref(fig:sem)b).
-
-## Stability-richness relationship
-
-```{r}
-tar_load(default_variable_values_pred)
-pv <- default_variable_values_pred
-
-pv_cap <- paste0(
-  "connectance = ", round(pv["ct_alive"], 2),
-  ", average interaction strength = ", round(pv["avg_int_strength"], 3),
-  ", average trophic level = ", round(pv["w_avg_tlvl"], 2),
-  ", predator interference = ", round(pv["c"], 1),
-  ", Predator-Prey Mass Ratio = ", round(pv["Z"]),
-  ", and environmental stochasticity = ", round(pv["env_stoch"], 1)
-
-)
-pred_cap <- paste0("Slope of the community stability - species
-  richness relationship according to food-web structure and response diversity. (a),
-  Diagrams displaying the slope coefficients of the effect of species richness
-  on community stability. The average values of the control variables were used
-  to generate the predictions: ", pv_cap, ". (b, c): Examples of predictions
-  from the model for two combinations of average trophic level and response
-  diversity (values displayed in panel (a)). Lines display the mean predictions
-  of the model. The coefficients of the linear model are displayed in Fig. S4.
-  Relationships between population stability, asynchrony and species richness
-  are displayed in Fig. S5."
-  ) %>%
-  str_replace_all("\\s+", " ")
-```
-
-```{r pred, fig.cap = pred_cap, fig.id = "pred"}
-knitr::include_graphics(here("report", "figures", "p_fig3.pdf"))
-```
-
-Using a more complex linear model (i.e. including interactions), We found strong
-interactions between food-web structure and response diversity on the
-relationship between community stability and species richness. We found that
-high response diversity almost always leads to positive relationships between
-community stability and species richness, no matter the values of average
-interaction strength, average trophic level or connectance (Fig.
-\@ref(fig:pred)a). Surprisingly, despite the relatively small effects of
-food-web structure on overall community stability (Fig. \@ref(fig:sem)b), we
-found that response diversity dramatically change the shape of the community
-stability-species richness relationship from positive to negative when response
-diversity is low (Fig. \@ref(fig:pred)b).
-
----
-#We found that
-#environmental stochasticity decrease overall community stability but has only
-#little effect on the shape of the community stability-species richness
-#relationship (Fig. \@ref(fig:pred)a)
----
-
-```{r, eval = FALSE}
-tar_read(p_int_fw_str)
-```
-
-# Discussion
-
-One of the key questions in Ecology is what drives temporal stability in complex
-communities?, especially in food-webs. We provide an answer to that question by
-investigating how the structure of complex food-webs affects the temporal
-stability of ecological communities using a bioenergetic model. We added
-environmental stochasticity to this model and modulated the species response
-diversity, i.e. the capacity of species to answer differently to environmental
-fluctuations. We found that food-web structure, apart from species richness,
-had little effects on overall stability. However we found that the interplay
-between food-web structure and response diversity was critical to determine
-positive or negative relationships between community stability and species
-richness.
-
-## Food-web structure and stressors affects population stability and asynchrony
-
-Our results show that community stability in complex food-webs is mainly driven
-by population stability rather than synchrony, confirming previous results in
-empirical fish communities [@danet_species_2021] and theoretical models
-[@eschenbrenner_diversity_2023], which contrasts with empirical data in birds
-and bats assemblages that reported an equivalent influence of population
-stability and asynchrony on community stability [@olivier_urbanization_2020].
-Although the number of empirical and theoretical studies is still limited to
-compare the respective contribution of asynchrony and population stability to
-community stability in single-trophic assemblages and food-webs, we suggest two
-non-exclusive and complementary explanations that might drive a lower
-contribution of asynchrony in food-webs compared to single-trophic assemblages.
-First, the range of bodymasses is much higher in food-webs, which typically
-include species that differ in bodymass by several orders of magnitude
-[@brose_predator_2019], which in turn creates highly uneven biomass
-distribution, thereby creating uneven contributions of species to asynchrony
-[@thibaut_understanding_2013] and limits the raise of high portfolio effects and
-compensatory dynamics in species rich communities [@zhao_biodiversity_2022].
-Second, the trophic interactions characterising food-webs create strong
-interdependence among species, which in turn limits the raise of independent
-fluctuations (i.e. portfolio effects, but rise compensatory dynamics). The fact
-that that compensatory dynamics had stronger effects on asynchrony than
-portfolio effects, in contrast with findings in experimental grasslands
-[@zhao_biodiversity_2022], lends toward this interpretation. The question of
-which mechanisms and community features drive differences in the contribution of
-asynchrony and population stability in food-webs and single-trophic assemblages
-is still an open question that might be crucial to accurately address
-diagnostics and conservation issues. On top of food-web structure, we found that
-environmental stochasticity and environmental correlation among species were the
-main drivers of community stability, suggesting that stressors are the main
-drivers of temporal stability. This result is in accordance with previous
-studies showing strong effects of environmental stochasticity
-[@vasseur_environmental_2007] and of the loss of response diversity community
-stability in tri-trophic food-webs [@ives_stability_2000;
-@thebault_trophic_2005].
-
-We further found that average trophic level increased average population
-stability, confirming previous theoretical [@brose_allometric_2006;
-@shanafelt_stability_2018; @eschenbrenner_diversity_2023] and
-[@danet_species_2021] empirical results. Higher average trophic level can
-stabilise populations because higher predators are themselves more stable due to
-lower mortality rates which in turn makes them less sensible stochastic
-perturbation and because they control the amplitude of the fluctuations of their
-preys [@shanafelt_stability_2018]. Additional simulations with equal mortality
-rates for all species suggest a prevalence of the former explanation (Fig. S1).
-In turn, we found that average trophic level decreases strongly asynchrony
-through a negative effect on portfolio effects, by decreasing the evenness of
-biomass variability. It is linked to the model assumption that species of higher
-trophic levels have lower overall mortality rates, similarly to previous
-studies [@vasseur_environmental_2007], thereby increasing average population
-stability and simultaneously synchronising populations. Furthermore, average
-omnivory was strongly correlated with average trophic level (Fig. S2),
-suggesting that average omnivory also stabilises population stability, in line
-with previous theoretical results in small modules [@mccann_reevaluating_1997].
-Our results further suggest that higher average trophic level results in lower
-compensatory dynamics raising from species interactions, this results could be
-related by the fact that average trophic level is strongly associated with
-average omnivory, which might tamper synchronised predator-prey oscillations
-that can raise compensatory dynamics [@mccann_reevaluating_1997].
-
-We however found no big effect of species richness on population stability,
-which has been reported to be negative, positive or neutral in previous studies
-[@ruijven_contrasting_2007; @houlahan_negative_2018]. However, species richness
-had a strong positive effect on asynchrony, by raising portfolio effects.
-This result is common in empirical systems [@tilman_biodiversity_2006;
-@olivier_urbanization_2020; @zhao_biodiversity_2022], but strongly depends on
-the presence of response diversity [@loreau_species_2008;
-@thibaut_understanding_2013; @zhao_biodiversity_2022]. Connectance, quantifying
-the generalism in food-webs, had small negative effects on population
-stability but a small positive on on asynchrony. We further found that higher connectance
-led to less even biomass variability, thereby limiting the rise of the
-portfolio effects, and led to lower compensatory dynamics due to species
-interactions (Table. S4). This result is in accordance with empirical findings
-that a generalist predator can indeed synchronise the dynamics of a large
-number of prey [@raimondo_interspecific_2004], thereby potentially limiting compensatory
-dynamics arising from species interactions. However, the overall effect of
-connectance on overall stability was quite low, similarly to previous empirical
-findings [@danet_species_2021], but in apparent disagreement with the
-predominant role of connectance on stability in theoretical studies
-[complexity-stability paradox, @may_will_1972].
-
-```{r, eval = FALSE}
-tar_load(sem_simplified_eff_tab)
-sem_simplified_eff_tab %>%
-  filter(effect_type == "total") %>%
-  print(n = 100)
-```
-
----
-#In turn,
-#we found that species richness magnified the effect of the loss of response
-#diversity on the compensatory dynamics due to environment. Our interpretation is
-#that higher species richness synchronises more species fluctuations due to
-#environmental mortality when species are not independent because each added
-#species adds (S - 1, S being richness) positive covariance terms in the
-#stochastic mortality rates, thereby increasing the overall synchrony in
-#mortality rates when cross correlation are not null. This assumption that each
-#species are equally correlated to each other seems unlikely to be true but as
-#far we know, there is compelling evidence yet for alternative correlation
-#structures.
----
-
-Predator interference, taken in this study as a control variable, had also a
-strong effect on community stability. Our results confirm the stabilising
-effect of self-limiting processes on populations [@uszko_effects_2017;
-@brose_allometric_2006]. Furthermore, we found that predator interference
-decreased asynchrony by strongly decreasing compensatory effects due to species
-interactions. Predator interference models a decrease of the feeding rates of
-consumers when predator biomass increases which might lead to a less dramatic
-fluctuation of prey biomass. All together, this result suggests that
-self-limitation mechanisms that increase population stability might in turn have
-opposite effects on asynchrony, and that it is the balance between the two
-effects weighted by the relative importance of population stability and
-asynchrony that will determine the overall effect on community stability.
-
-## Stability-richness relationship
-
-We found that environmental stochasticity does not affect the shape of the
-community stability - richness but rather controls the overall community
-stability (i.e. the intercept of the relation). At the opposite, variation in
-response diversity had a strong impact on the relationship between stability and
-richness. The reason is that the strength of environmental stochasticity mainly
-affect population stability and less asynchrony, asynchrony being the driver of
-species-richness relationships [@ives_stability_2000; @tilman_biodiversity_2006; @loreau_species_2008;
-@thibaut_understanding_2013; @zhao_biodiversity_2022]. Average interaction
-strength and connectance that were found to have little effects on overall
-stability, were found to have a strong effect on stability-richness
-relationships. This result is in accordance with the complexity-stability theory
-that predicts that community stability (i.e. measured as the dominant eigen
-value of the jacobian matrix) should decrease as the community is species
-diverse, has higher connectance, and higher interaction strength
-[@may_will_1972]. However, we found that the negative effects of complexity on
-stability-richness relationships are cancelled when response diversity is high.
-A possible explanation is the presence of response diversity and resulting
-asynchrony in species fluctuations which overrides the negative effects of
-complexity on stability-richness relationships. Response diversity might then be
-one mechanism that explains why positive relationships between stability
-and species richness are so prevalent in empirical settings while food-web
-theoretical models that do not often include environmental stochasticity and
-response diversity finds negative complexity stability relationships
-[@ives_stability_2007].
-
-# Conclusion and perspectives
-
-Our study presents the effects of food-web structure on temporal community
-stability and its partition into population stability and asynchrony in complex
-communities, added to two pressing stressors in the context of global change,
-the strength of environmental variability and the level of response diversity of
-species facing this environmental variability. Our results confirm the results
-of previous theoretical models modelling small food-web modules or food-chains,
-as we report that average trophic level, omnivory, predator-prey size ratio, and
-predator interference increase temporal community stability by stabilising
-population fluctuations. In turn, our study confirms that species richness
-increases temporal community stability by increasing asynchrony due to portfolio
-effects and thanks to response diversity. Our study reports that connectance and
-average interaction strength have little effects on overall community stability
-while they have a strong effect on the sign of the community stability-richness
-relationship, in accordance with the complexity-stability paradox, modulated by
-response diversity. Overall, it suggests that high response diversity of species
-facing environmental stochasticity, on top of being the essential ingredient
-driving positive stability-richness relationship, also exceeds the negative
-effects of food-web complexity on stability-richness relationship.
-
-Our results highlight that the strength of environmental fluctuations is the
-primary driver of community stability. In the context of global changes in which
-environmental variability is expected to increase tremendously, our study
-suggests a strong decrease in community stability, despite high response
-diversity and response diversity. But ongoing biotic homogenization
-[@olden_homogocene_2018; @muthukrishnan_invasive_2020; @wang_biotic_2021] is
-also suggested to decrease response diversity [@wang_biotic_2021;
-@su_human_2021], which in turn is expected to further decrease stability despite
-high species richness, even more in complex food-webs having high interaction
-strength, high connectance and high average trophic level. Then, the results of
-our study reinforce the idea that restoration of ecosystems along with a
-restoration of landscape complexity that provides refuges from extreme
-environmental fluctuations will be key to maintain temporal stability of
-ecological communities in the coming decades [@ryser_landscape_2021].
-
 # References {-}

### 2024-04-24 paper/supplementary_figures.Rmd
Update manuscript results, discussion and methods

@@
 ```{r}
+sim_summary_stat_cap <- paste0(
+  "Summary statistics of the food-web and stability metrics.") %>%
+  str_replace_all("\\s+", " ")
+tar_read(tab_sim_summary_stat) %>%
+  rename_with(~str_replace_all(.x, "\\%", "\\\\%")) %>%
+  kable(
+    booktabs = TRUE,
+    format = "latex",
+    escape = FALSE,
+    caption = sim_summary_stat_cap,
+    label = "param") %>%
+  column_spec(1, bold = TRUE) %>%
+  collapse_rows(columns = 1, latex_hline = "major", valign = "middle") %>%
+  kable_styling(latex_options = c("striped", "hold_position"))
+```
+
+```{r}
 tar_read(tab_sem_vif) %>%
@@
 ```{r}
-tar_read(tab_sem_coeff) %>%
+tar_read(tab_sem_doak_eff) %>%
   kable(booktabs = TRUE,

### 2024-04-24 R/model_helpers.R

@@ -39,13 +39,11 @@ formula_mod_rho_fixed_effect <- function() {
 formula_stab_fw_model <- function(
   resp = "stab_com",
   rand_effect = TRUE,
-  term_to_del = "richness : resp_div : Z +"
+  term_to_del = NULL
   ) {
 
   fixed_part <- "richness + resp_div + env_stoch +
-  ct_alive + w_avg_tlvl + Z +
-  avg_int_strength +
-  c +
+  ct_alive + w_avg_tlvl + Z + avg_int_strength + c +
   richness : resp_div +
   richness : env_stoch +
   richness : ct_alive +
@@ -57,6 +55,35 @@ formula_stab_fw_model <- function(
   richness : env_stoch : ct_alive +
   richness : env_stoch : avg_int_strength +
   richness : env_stoch : w_avg_tlvl"
+
+  if (rand_effect) {
+   rand_part <- "+\n (1|fw_id)"
+  } else {
+   rand_part <- ""
+  }
+
+  form <- paste0(resp, " ~\n", fixed_part, rand_part)
+  if (!is.null(term_to_del)) {
+    form <- str_remove(form, term_to_del)
+  }
+  as.formula(form)
+
+}
+
+formula_stab_fw_model_full <- function(
+  resp = "stab_com",
+  rand_effect = TRUE,
+  term_to_del = NULL
+  ) {
+
+  fixed_part <- "richness + resp_div + env_stoch +
+  ct_alive + w_avg_tlvl + Z + avg_int_strength + c +
+  richness * resp_div * ct_alive +
+  richness * resp_div * w_avg_tlvl +
+  richness * resp_div * avg_int_strength +
+  richness * env_stoch * ct_alive +
+  richness * env_stoch * avg_int_strength +
+  richness * env_stoch * w_avg_tlvl"
 
   if (rand_effect) {
    rand_part <- "+\n (1|fw_id)"

### 2024-04-24 R/plotting_methods.R

@@ -26,8 +26,8 @@ stab_alpha <- function () {
 }
 
 sem_tot_predictor <- function () {
-  c("resp_div", "avg_int_strength", "w_avg_tlvl", "ct_alive", "richness",
-    "env_stoch")
+  c("resp_div", "avg_int_strength", "w_avg_tlvl", "avg_omnivory", "ct_alive",
+    "richness", "env_stoch")
 }
 
 resp_div_cat_colors <- function() {

### 2024-04-24 R/string_replacements.R

@@ -14,8 +14,9 @@ var_replacement <- function() {
     cpe = "Compensatory effect",
     cpe_int = "Comp effect (Interaction)",
     cpe_env = "Comp effect (Environment)",
-    sae_total = "Portfolio effect",
+    sae_total = "Portfolio effect (Tilman)",
     sae_even = "Portfolio effect (Even)",
+    sae_doak = "Portfolio effect (Doak)",
     evenness_sae = "Portfolio effect (Evenness)",
     log1_avg_max_int_alive = "Avg interaction strength",
     avg_max_int_alive = "Avg interaction strength",

### 2024-04-24 src/sim.jl

@@ -610,6 +610,15 @@ end
 """
 kill_disconnected_species(A; alive_species = nothing, bm = nothing)
 
+Returns a vector of species biomass, all the disconnected and extinct species being set to a
+biomass of 0.
+
+# Arguments:
+
+  - `A`: Adjacency matrix
+  - `alive_species`: vector of alive species indices. See [`living_species`](@ref)
+  - `bm`: vector of species biomass
+
 # Examples
 
 ti = [
@@ -627,12 +636,16 @@ kill_disconnected_species(ti, alive_species = [1, 3, 4], bm = bm) == [1, 0, 3, 0
 kill_disconnected_species(ti, alive_species = [1, 2, 4], bm = bm) == [0, 1, 0, 4]
 kill_disconnected_species(ti, alive_species = [1, 2, 4], bm = bm) == [0, 1, 0, 4]
 
-# Filter network and biomass
+# Filter species biomass and then adjacency matrix
+
+## Case 1
 to = kill_disconnected_species(ti, alive_species = [1, 2, 3, 4], bm = bm)
 mask = to .== 0
 A = ti[mask, mask]
 new_bm = bm[mask]
 dim(A) == length(new_bm)
+
+## Case 2
 to = kill_disconnected_species(ti, alive_species = [1, 2, 4], bm = bm)
 mask = to .== 0
 A = ti[mask, mask]
@@ -641,6 +654,7 @@ dim(A) == length(new_bm)
 
 
 """
+
 
 function kill_disconnected_species(A; alive_species = nothing, bm = nothing)
     bm = deepcopy(bm)

### 2024-08-14 _targets.Rmd
Plotting methods

@@
           theme(
+            text = element_text(size = 20),
             legend.title = element_blank(),
@@
       nrow = 2, rel_heights = c(1, .8),
-      labels = "auto"
+      labels = "auto", hjust = -.7, vjust = 1.7
   )
@@
 ```{r plot-sim}
-load(here("data", "sim_for_plot"))
+sim_for_plot <- readRDS(here("data", "sim_for_plot"))
 length(unique(sim_for_plot$sim_id))
@@
   left_join(
-    tar_read(sim_fw)
+    tar_read(sim_fw_csc_rerun)
   )

### 2024-08-14 R/plotting_methods.R

@@ -26,8 +26,8 @@ stab_alpha <- function () {
 }
 
 sem_tot_predictor <- function () {
-  c("resp_div", "avg_int_strength", "w_avg_tlvl", "avg_omnivory", "ct_alive",
-    "richness", "env_stoch")
+  c("resp_div", "richness", "avg_int_strength", "ct_alive", "w_avg_tlvl",
+     "env_stoch")
 }
 
 resp_div_cat_colors <- function() {

### 2024-08-14 draft.jl

@@ -22,6 +22,76 @@ include("src/get_modules.jl")
 ti = missing
 isnothing(ti)
 
+function gen_adj_matrix_plant_herbivore_carnivore(nprod;
+        herbivores = false,
+        carnivores = false
+    )
+    if carnivores
+        nspecies = 3 * nprod
+        # If there are carnivores, herbivores are present
+        herbivores = true
+    elseif herbivores
+        nspecies = 2 * nprod
+    else
+        nspecies = nprod
+    end
+
+    mat = zeros(Int64, nspecies, nspecies)
+
+    if herbivores & !carnivores
+        mat[nprod+1 : 2*nprod, 1:nprod] .= 1
+    elseif carnivores
+        mat[nprod+1 : 2*nprod, 1:nprod] .= 1
+        mat[2*nprod+1 : 3*nprod, nprod+1 : 2*nprod] .= 1
+    end
+
+    mat
+
+end
+ti = gen_adj_matrix_plant_herbivore_carnivore(3, herbivores = false)
+gen_adj_matrix_plant_herbivore_carnivore(3, carnivores = true)
+
+function set_pref_matrix_plant_herbivore_carnivore(mat;
+        pref_herbivores = 1,
+        pref_carnivores = 1)
+    nspecies = size(mat, 1)
+    nprod = sum([sum(mat[i,:]) == 0 for i in 1:nspecies])
+    pref_mat = zeros(Float64, nspecies, nspecies)
+
+    secondary_pref_herb = (1 - pref_herbivores) / nprod
+    secondary_pref_carn = (1 - pref_carnivores) / nprod
+
+    if pref_herbivores < secondary_pref_herb
+        println("oups! Main pref ($pref_herbivores) lower than secondary pref ($secondary_pref_herb)")
+    end
+    if pref_carnivores < secondary_pref_carn
+        println("oups! Main pref ($pref_herbivores) lower than secondary pref ($secondary_pref_herb)")
+    end
+
+    if nprod == nspecies
+        # nothing zeros
+    elseif nspecies == 2*nprod # herbivores
+        for i in 1:nprod
+            pref_mat[nprod + i, 1:nprod] .= secondary_pref_herb
+            pref_mat[nprod + i, i] = pref_herbivores
+        end
+    elseif nspecies == 3*nprod # herbivores-carnivores
+        for i in 1:nprod
+            pref_mat[nprod + i, 1:nprod] .= secondary_pref_herb
[…]

### 2024-08-29 _targets.Rmd
Cleaning targets pipeline (removing old code not used)

@@
 
-If you are using old versions of `targets` (<= 0.7.0) and/or `knitr` (<= 1.33), you will need to load the `targets` package in the R Markdown document in order for Target Markdown code chunks to work.
-
 ```{r}
@@
 
-Near the top of the document, you may also wish to remove the `_targets_r` directory previously written by non-interactive runs of the report. Otherwise, your pipeline may contain superfluous targets.
+Near the top of the document, you may also wish to remove the `_targets_r` directory
+previously written by non-interactive runs of the report. Otherwise, your pipeline may
+contain superfluous targets.
 
@@
   tar_target(tab_sem_vif,
-    sem_collinearity %>%
+    sem_doak_collinearity_csc_rerun %>%
       mutate(across(c("response", "Term"), ~var_replacement()[.x])) %>%
@@
   tar_target(tab_sem_rsquared,
-    sem_rsquared %>%
+    sem_doak_rsquared_csc_rerun %>%
       rename(`$R^2$` = R.squared) %>%
@@
 )
-```
-
-```{r, eval = FALSE}
-library(targets)
-tar_load_globals()
-tar_load(starts_with("sim_fw_csc"))
-sim_fw_csc_rerun
-sim_fw_csc_rebuild
-sim_fw_csc_kno
-sim_fw_csc_non_allo
-sim_fw_csc_non_allo
-tar_read(sem_rsquared) %>%
-  rename(`$R^2$` = R.squared) %>%
-  kable(caption = "Rsquared for the Structural Equation Model.") %>%
-  kable_styling()
 ```
@@
 
-```{r, eval = FALSE}
-tar_load(sem_main_text_tot)
-sem_simplified_tot %>%
-  select(sim_type, collinearity) %>%
-  unnest(cols = c(collinearity)) %>%
-  group_by(sim_type) %>%
-  summarise(
-    med = median(VIF),
-    max = max(VIF)
-  )
-tar_read(sem_main_text_eff_rerun)
-tar_load(pred_stab_comp_resp_div)
-library(targets)
-tar_load(sem_doak_eff_tab_csc_rerun)
-sem_doak_eff_tab_csc_rerun %>%
-  filter(effect_type == "direct", abs(effect) > .05) %>%
-  print(n = 40)
-
-sem_doak_eff_tab_csc_rerun %>%
-  filter(effect_type == "direct") %>%
-  print(n = 40)
-```
-
 ```{targets plot-sem-tot}
@@
 
-## Partial residuals SEM
-
-```{targets partial_sem_relations, eval = FALSE}
-list(
-  tar_target(scaled_sim_fw_sem,
-    sim_fw_sem %>%
-      mutate(across(where(is.numeric), ~scale(.x)[, 1]))
-    ),
-  tar_target(scaled_sem_simplified_model_list,
-    map(sem_simplified_model_list,
-      ~update(.x, data = scaled_sim_fw_sem)
-      )),
-  tar_target(scaled_sem_simplified,
-    as.psem(scaled_sem_simplified_model_list)
-    ),
-  tar_target(formula_sem_bivariate_relations,
-    c(
-      "pop_stab ~ w_avg_tlvl",
-      "pop_stab ~ c",
-      "pop_stab ~ env_stoch",
-      "sae_total ~ richness",
-      "sae_total ~ ct_alive",
-      "sae_total ~ w_avg_tlvl",
-      "sae_total ~ avg_int_strength",
-      "cpe ~ avg_int_strength",
-      "cpe ~ resp_div"
-    )
-    )#,
-  #tar_target(partial_resid_sem_simplified, {
-  #  partialResid(as.formula(formula_sem_bivariate_relations),
-  #          modelList = scaled_sem_simplified,
-  #          data = scaled_sim_fw_sem
-  #        )},
-  #        pattern = map(formula_sem_bivariate_relations)
-  #),
-  #tar_target(sem_simplified_bivariate_relations,
-  #  tibble(sem_formula = formula_sem_bivariate_relations) %>%
-  #    separate(
-  #      col = sem_formula,
-  #      into = c("response", "predictor"),
-  #      sep = " ~ ", remove = FALSE) %>%
-  #  mutate(
-  #    data = partial_resid_sem_simplified,
-  #    coefs = map2(response, predictor,
-  #      ~coefficients(scaled_sem_simplified[[.x]])[c("(Intercept)", .y)]
-  #      ),
-    #  plot = pmap(list(
-    #      data = data,
-    #      response = response,
-    #      predictor = predictor,
-    #      coef = coefs
-    #      ),
-    #    function (data, response, predictor, coef, ext_data) {
-    #      if (predictor %in% c("h", "env_stoch", "resp_div")) {
-    #        p <- data %>%
-    #          ggplot(aes(
-    #              y = yresid, x = xresid,
-    #              group = cut(round(xresid, 1),
-    #                breaks = length(unique(ext_data[[predictor]]))
-    #              )
-    #              )) +
-    #          geom_boxplot(alpha = .1)
-    #      } else {
-    #        p <- data %>%
-    #          ggplot(aes(y = yresid, x = xresid)) +
-    #          geom_point(alpha = .1)
-    #      }
-    #      p +
-    #        geom_abline(
-    #          intercept = coef["(Intercept)"],
-    #          slope = coef[2],
-    #          linewidth = 1
-    #          ) +
-    #        labs(
-    #          x = var_replacement()[predictor],
-    #          y = var_replacement()[response]
-    #          ) +
-    #        coord_cartesian(expand = FALSE) +
-    #        theme_half_open()
-
-    #    }, ext_data = scaled_sim_fw_sem)
-    #)
-  #)
-)
-```
-
-```{targets p-stab}
-list(
-  tar_target(p_cpe_env_rho, sim_fw %>%
-    ggplot(aes(x = as.factor(1 - rho), y = cpe_env)) +
-    geom_hline(yintercept = 1, linetype = "dashed") +
-    geom_hline(yintercept = .5, linetype = "dashed", color = "red") +
-    geom_boxplot() +
-    labs(x = "Response diversity", y = "Env. Compensatory effect") +
-    theme_bw()),
-  tar_target(p_stoch_pop_stab,
-    sim_fw %>%
-      ggplot(aes(x = as.factor(env_stoch), y = pop_stab)) +
-      geom_boxplot() +
-      labs(x = "Environmental stochasticity", y = "Population stability") +
-      theme_bw()),
-    tar_target(p_stab_comp_stress,
-      plot_grid(
-        p_cpe_env_rho,
-        p_stoch_pop_stab,
-        labels = "auto"
-      )
-    )
-)
-```
-
 ## Stability-diversity relationship
@@
 
-```{targets p_stab_rich_env_rho, tar_simple = TRUE}
-sim_fw %>%
-  filter(env_stoch %in% c(.1, .6), rho %in% c(0, .75), c == 1, Z == 100) %>%
-  ggplot(aes(x = log(richness), y = log(stab_com), color = as.factor(rho))) +
-  geom_point(alpha = .3) +
-  geom_smooth(method = "lm") +
-  facet_grid(cols = vars(env_stoch), labeller = label_both) +
-  labs(
-    x = "Species richness (Log)", y = "Community stability (Log)",
-    color = "Environmental correlation"
-  ) +
-  theme_bw() +
-  theme(legend.position = "bottom")
-```
-
-## Interaction strength effect
-
-```{targets p_int_stab, tar_simple = TRUE}
-sim_fw %>%
-  filter(rho %in% c(0), env_stoch == .5) %>%
-  pivot_longer(c(stab_com, async, sae_total, cpe,
-      sae_even, evenness_sae,
-      cpe_int, cpe_env, pop_stab
-      ), names_to = "async_decomp", values_to = "values") %>%
-  mutate(async_decomp = var_replacement()[async_decomp]) %>%
-  ggplot(aes(x = avg_int_strength, y = values)) +
-  geom_point() +
-  geom_smooth() +
-  labs(x = "Avg feeding rate", y = "Asynchrony component") +
-  facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
-  theme_bw()
-```
-
-```{targets p_int_fw, tar_simple = TRUE}
-sim_fw %>%
-  filter(rho %in% c(0), env_stoch == .5) %>%
-  pivot_longer(c(richness, ct_alive, max_tlvl, avg_omnivory, w_avg_tlvl
-      ), names_to = "fw_str", values_to = "values") %>%
-  mutate(fw_str = var_replacement()[fw_str]) %>%
-  ggplot(aes(x = avg_int_strength, y = values)) +
-  geom_point() +
-  geom_smooth() +
-  labs(x = "Avg feeding rate", y = "Food-web structure") +
-  facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
-  theme_bw()
-```
-
-## Avg Omnivory
-
-```{targets p-omn}
-list(
-  tar_target(p_omn_stab,
-    sim_fw %>%
-      filter(rho %in% c(0), env_stoch == .5) %>%
-      pivot_longer(c(stab_com, pop_stab, async
-          ), names_to = "stab_comp", values_to = "values") %>%
-      mutate(stab_comp = var_replacement()[stab_comp]) %>%
-      ggplot(aes(x = avg_omnivory, y = values)) +
-      geom_point() +
-      geom_smooth() +
-      labs(x = "Avg omnivory", y = "Stability component") +
-      facet_wrap(~stab_comp, ncol = 3, scales = "free_y") +
-      theme_bw()),
-  tar_target(p_omn_fw,
-    sim_fw %>%
-      filter(rho %in% c(0), env_stoch == .5) %>%
-      pivot_longer(c(richness, ct_alive, w_avg_tlvl, max_tlvl
-          ), names_to = "fw_str", values_to = "values") %>%
-      mutate(fw_str = var_replacement()[fw_str]) %>%
-      ggplot(aes(x = avg_omnivory, y = values)) +
-      geom_point() +
-      geom_smooth() +
-      labs(x = "Avg. Omnivory", y = "Food-web structure") +
-      facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
-      theme_bw()
-  )
-)
-```
-
-```{targets p-ct-rich-stab}
-list(
-  tar_target(p_ct_stab,
-    sim_fw %>%
-      filter(rho %in% c(0), env_stoch == .1) %>%
-      pivot_longer(c(stab_com, async, sae_total, cpe,
-          sae_even, evenness_sae,
-          cpe_int, cpe_env, pop_stab
-          ), names_to = "async_decomp", values_to = "values") %>%
-      mutate(async_decomp = var_replacement()[async_decomp]) %>%
-      ggplot(aes(x = ct_alive, y = values)) +
-      geom_point() +
-      geom_smooth() +
-      labs(x = "Connectance", y = "Asynchrony component") +
-      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
-      theme_bw()
-    ),
-  tar_target(p_rich_stab,
-    sim_fw %>%
-      filter(rho %in% c(0), env_stoch == .1) %>%
-      pivot_longer(c(stab_com, async, sae_total, cpe,
-          sae_even, evenness_sae,
-          cpe_int, cpe_env, pop_stab
-          ), names_to = "async_decomp", values_to = "values") %>%
-      mutate(async_decomp = var_replacement()[async_decomp]) %>%
-      ggplot(aes(x = richness, y = values)) +
-      geom_point() +
-      geom_smooth() +
-      labs(x = "Species richness", y = "Asynchrony component") +
-      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
-      theme_bw()
-    )
-)
-```
-
-```{targets p_int_fw_str, tar_simple = TRUE}
-p1 <- sim_fw %>%
-  ggplot(aes(x = as.factor(richness), y = avg_int_strength)) +
-  geom_point() +
-  labs(x = "Species richness", y = "Avg. Interaction strength") +
-  theme_bw()
-p2 <- sim_fw %>%
-  ggplot(aes(x = as.factor(Z), y = avg_int_strength)) +
-  geom_boxplot() +
-  labs(x = "PPBR", y = "Avg. Interaction strength") +
-  theme_bw()
-p3 <- sim_fw %>%
-  filter(Z == 100) %>%
-  ggplot(aes(x = as.factor(c), y = avg_int_strength)) +
-  geom_boxplot() +
-  labs(x = "Hill exponent", y = "Avg. Interaction strength") +
-  theme_bw()
-plot_grid(p1, p2, p3, ncol = 2)
-```
-
 ```{targets p_cor, tar_simple = TRUE}
@@
   sim_summary_stat %>%
+    ungroup() %>%
     mutate(
-      var = var_replacement()[var],
+      var = recode_factor(var, !!!var_replacement(), .ordered = TRUE),
       type = str_to_sentence(type)
@@
 
+```{targets render, eval = FALSE}
+# does not work properly, have to run it by hand
+list(
+  tar_render(manuscript, here::here("paper","manuscript.Rmd")),
+  tar_render(supp, here::here("paper","supplementary_figures.Rmd"))
+)
+```
+
 # Pipeline
@@
 tar_make()
-tar_visnetwork()
-tar_make_future(workers = 3)
 ```

### 2024-08-29 paper/manuscript.Rmd
Cleaning targets pipeline (removing old code not used)

@@
 ---
-title: Response diversity and food-web structure drive stability and stability-richness relationships in complex communities
-author: "Alain Danet (1), Sonia Kéfi (2,3), Thomas F Johnson (1), Andrew P. Beckerman (1)"
+title: Response diversity is a major driver of temporal stability in complex food webs
+author: "Alain Danet (1), Sonia Kéfi (2,3), Thomas F. Johnson (1), Andrew P. Beckerman (1)"
 date: ""
@@
 
-# Abstract (179/200 words)
+# Abstract
 
-Global environmental change constitutes a suite of major threats to biodiversity
-and ecosystem functioning. These threats can materialised via changes to the
-stability of communities and the services they provide. Despite independent
-advances in understanding the impact on stability of community size and
-structure, synchrony and responses to environmental variation, there remains no
-core theory connecting these key processes. Developing this theory requires
-combining concepts from diversity - stability relationships, synchrony and the
-portfolio effect, and the emerging field of response diversity. Using a
-stochastic Bioenergenetic food-web model of 20-50 interacting species, we show
-that response diversity and species richness are also strong drivers of overall
-community stability in complex food-webs. We further show that connectance and
-average trophic level consistently dampened asynchrony but that average trophic
-level stabilises population stability. Positive stability-richness relationships
-always emerged only in presence of response diversity, but interaction strength,
-connectance, average trophic level strongly interact with response diversity to
-determine the sign of stability-diversity relationships. Our study disentangles
-the complex effects of food-web structure on community stability and its
-pathway, showing that response diversity is a mechanism that generates positive
-stability-diversity relationships, beyond plant communities.
+Global change constitutes a suite of major threats to biodiversity and ecosystem
+functioning. These threats can materialise via changes in the temporal stability
+of ecological communities and the services they provide. However, the majority
+of research on stability has focused on single trophic level communities and has
+not yet integrated classic theory about species richness and food web structure
+with more recent theory centred on response diversity and stochasticity. Using a
+stochastic bioenergenetic food-web model, we reveal that response diversity is a
+major driver of community stability. Moreover, positive stability-richness
+relationships emerge only in the presence of response diversity. In contrast to
+previous work,  food-web structural properties are only secondary drivers of
+overall community stability, but interact with response diversity to determine
+the sign of the stability-richness relationship. Our study highlights the
+complex pathways by which food-web structure and response diversity drive
+community stability, and raises concerns about how the loss of response
+diversity may lead to a breakdown of stability and the capacity for these
+communities to deliver functions and services to human societies.
 
@@
 
-Ecological communities are facing ever-growing environmental variability caused
-by climate and environmental change[@lee_ipcc_2023;
-@simmons_refocusing_2021]. Decreases in the temporal stability of communities
-are increasingly documented[@olivier_urbanization_2020;
-@de_boeck_patterns_2018; @hansen_climate_2013; @bluthgen_land_2016; @harris_biological_2018], raising
-concerns about the long-term consequences at the ecosystem scale. Repeated calls
-have been made to clarify the role of environmental stochasticity in driving the
-temporal stability of ecological communities[@yang_predictability_2019]. It
-remains challenging because species have a diversity of response to
-environmental change [@elmqvist_response_2003; @loreau_species_2008;
-@ives_stability_2000; @ross_how_2023] (“response diversity”) and they are
-entangled in complex communities such as food-webs, that both ultimately drive
-community stability[@may_will_1972; @angelis_stability_1975; @mccann_weak_1998;
-@mccann_reevaluating_1997; @thebault_stability_2010] and stability-richness
-relationships[@thebault_trophic_2005; @thebault_relationship_2006]. Despite the
-overarching effects of response diversity and food-web structure on temporal
-community stability, they have been so far studied in isolation.
+Global change, characterised by multiple, simultaneous threats to
+biodiversity[@lee_ipcc_2023; @simmons_refocusing_2021], is having impacts on the
+temporal stability of complex ecological communities[@olivier_urbanization_2020;
+@de_boeck_patterns_2018; @hansen_climate_2013; @bluthgen_land_2016;
+@harris_biological_2018]. A breakdown of stability impacts the capacity for
+these communities to deliver functions and services to human
+societies[@loreau_ecological_2022]. Predicting and managing the stability and
+services provided by biodiverse communities requires reconciling multiple
+concepts and theories about temporal stability in species diverse and
+structurally complex communities. These include classic ideas about the role of
+trophic structure and interaction strengths[@may_will_1972;
+@angelis_stability_1975; @mccann_weak_1998; @mccann_reevaluating_1997;
+@thebault_trophic_2005; @thebault_relationship_2006; @thebault_stability_2010],
+newer concepts of response diversity, average population stability, asynchrony
+and portfolio effects and integrative theories about the relationship between
+stability, structure and diversity.
 
-The temporal stability of ecological communities stems from average population
-stability and asynchrony of population fluctuations[@thibaut_understanding_2013;
-@zhao_biodiversity_2022]. While higher environmental stochasticity/variability
-decrease population stability by increasing the amplitude species oscillations,
-higher species response diversity increases asynchrony of species
-fluctuations[@doak_statistical_1998; @loreau_species_2008;
-@thibaut_understanding_2013]. This is increasingly well-established in
-simplified species assemblages, where high response diversity increases
-asynchrony and is the determinant of positive stability-diversity relationships
-across many taxa[@tilman_biodiversity_2006; @olivier_urbanization_2020;
-@zhao_biodiversity_2022]. However, it remains largely unknown how the effects of
-environmental stochasticity and response diversity on population stability and
-asynchrony are mediated in the context of complex communities, such as
-food-webs.
+An abundant literature has established that species diversity can buffer the
+effect of environmental perturbations on ecological communities, thereby
+increasing the temporal stability (hereafter “stability”) of
+communities[@yachi_biodiversity_1999; @doak_statistical_1998;
+@tilman_ecological_1999; @de_mazancourt_predicting_2013;
+@thibaut_diversity_2012; @zhao_biodiversity_2022]. Because different species
+have diverse niches and environmental preferences, they may react differently to
+the same environmental change [@elmqvist_response_2003; @ross_how_2023]. This
+diversity of species responses to environmental change, coined as “response
+diversity”, has been identified as a crucial mechanism that buffers the response
+of ecological communities to environmental perturbations
+[@yachi_biodiversity_1999; @thibaut_diversity_2012;
+@thibaut_understanding_2013]. For example, in a given community, some species
+will respond positively and others negatively to changes in temperature,
+depending on their thermal niche [@frund_response_2013]. Furthermore, it has
+also been shown recently that the stability of communities can be decomposed
+into the average population stability and the asynchrony of population
+fluctuations [@thibaut_understanding_2013; @zhao_biodiversity_2022]. Average
+population stability quantifies the average variability in species abundances,
+while asynchrony refers to how much the temporal fluctuations of the different
+species of the community are buffering each other. Recent studies have shown
+that asynchrony can be further resolved into “portfolio effects”, the
+statistical averaging of independent species fluctuations in response to
+environmental perturbations, and “compensatory dynamics”, where one species’
+decrease can be compensated for by the increase in another
+species[@doak_statistical_1998; @thibaut_understanding_2013;
+@zhao_biodiversity_2022].
 
-Complexity-stability theory well documented that the structure of food-webs
-determines population stability [@may_will_1972; @angelis_stability_1975;
-@mccann_weak_1998; @mccann_reevaluating_1997; @vasseur_environmental_2007;
-@eschenbrenner_diversity_2023], and stability-richness relationships
-[@thebault_trophic_2005; @thebault_relationship_2006]. Population stability is
-indeed documented to decrease with increasing interaction strength
-[@may_will_1972; @mccann_weak_1998], connectance [@may_will_1972], but to be
-higher at higher trophic level [@shanafelt_stability_2018; @danet_species_2021].
-In result, the distribution and strength of species interactions, as well as
-trophic level might have a strong effect on community stability and
-stability-richness relationships [@thebault_trophic_2005;
-@thebault_relationship_2006]. This expectation is reinforced by documented
-examples where predators can mediate the effect of response diversity on
-asynchrony [@vasseur_environmental_2007], and synchronise the dynamics of their
-prey [@raimondo_interspecific_2004; @korpimaki_predatorinduced_2005]. Recent
-study in plant communities suggests that asynchrony stems mainly from the
-statistical averaging of independent species fluctuations (“portfolio effects”),
-rather than compensatory dynamics resulting from response diversity and species
-interactions [@zhao_biodiversity_2022]. But we might expect that prey switching
-and trophic cascades arising in food-webs lead to higher compensatory dynamics
-than in plant communities [@mccann_diversitystability_2000;
+These mechanisms have been well-established in data from single trophic level
+(e.g. competitive) communities, such as grasslands, butterflies, birds, and bats
+communities[@de_mazancourt_predicting_2013; @olivier_urbanization_2020]. In
+these studies, response diversity increases asynchrony, and is a more important
+driver of community stability than population
+stability[@olivier_urbanization_2020]. In these same studies, the portfolio
+effect was found to play a key role in the emergence of positive
+diversity-stability relationships in experimental
+grasslands[@zhao_biodiversity_2022].
+
+Despite these data, there is limited evidence and understanding for how these
+collections of theories integrate to define stability in food webs with
+substantial diversity and vertical complexity (i.e. trophic levels)
+[@yang_predictability_2019; @danet_species_2021; @eschenbrenner_diversity_2023;
+@srednick_understanding_2024]. Classic theory and concepts about
+stability-complexity [@may_will_1972; @angelis_stability_1975],
+stability-structure [@mccann_weak_1998; @mccann_reevaluating_1997;
+@thebault_trophic_2005; @eschenbrenner_diversity_2023] and stability-richness [@ives_stability_2000;
+@thebault_trophic_2005; @thebault_relationship_2006] offer some expectation.
+They suggest that population stability is expected to decrease with increasing
+interaction strength[@may_will_1972; @mccann_reevaluating_1997;
+@mccann_weak_1998] and food web connectance[@thebault_trophic_2005] but to
+increase with average trophic level [@shanafelt_stability_2018;
+@danet_species_2021]. As a result, the distribution and strength of species
+interactions, as well as the average trophic level, can have strong effects on
+community stability as well as on stability-richness
+relationships[@thebault_trophic_2005; @thebault_relationship_2006]. These
+relationships indicate that the structure of food-webs strongly influences
+population stability and stability-richness relationships.
+
+The more recent theory and concepts centred on response diversity and asynchrony
+add further predictions[@thibaut_understanding_2013; @zhao_biodiversity_2022].
+With vertical structure and trophic interactions, consumers can synchronise the
+dynamics of their prey[@raimondo_interspecific_2004;
+@korpimaki_predatorinduced_2005], can offset the effects of response diversity
+on asynchrony and can generate substantial compensatory dynamics via prey
+switching and trophic cascades[@mccann_weak_1998; @mccann_diversitystability_2000;
 @fahimipour_compensation_2017].
 
-Here, we investigated the effects of response diversity and food-web structure
-on community stability and on stability-richness relationships in stochastic
-environment. To do so, we developed an extension of the Bioenergetic food web
-model [@brose_allometric_2006; @lajaaiti_ecologicalnetworksdynamicsjl_2024]
-which includes environmental stochasticity and response diversity
-[@loreau_species_2008; @vasseur_environmental_2007; @ripa_food_2003]. We
-included environmental stochasticity on allometric natural death rate, such as
-species of higher trophic level had lower death rate in
-average[@vasseur_environmental_2007], response diversity was included as the
-inverse of species correlation in their mortality rates.  We first decipher the
-respective effects of food-web structure, environmental stochasticity, and
-response diversity on community stability and its partition into population
-stability and asynchrony (i.e. portfolio and compensatory effects). We then
-investigate how food-web structure and response diversity interact to determine
-the sign of stability-richness relationship.
+Despite this collection of historical and more modern theory, we don’t know what
+determines stability in vertically structured, species rich communities.
+Against this gap in understanding, we specifically investigate the effects of
+response diversity and food-web structure on community stability and on
+stability-richness relationships in a variable  environment. The key question is
+whether the new concepts of environmental stochasticity, response diversity and
+asynchrony are the main mechanisms driving community stability versus more
+classic concepts tied to food-web structure and diversity.
+
+We explore this key question by extending  the  bioenergetic food web
+model[@brose_allometric_2006; @yodzis_body_1992], to incorporate environmental
+stochasticity and response diversity[@vasseur_environmental_2007;
+@ives_stability_2007; @ripa_food_2003]. We introduced environmental
+stochasticity by making species death rates
+stochastic[@vasseur_environmental_2007]. Response diversity is
+introduced as the correlation of stochasticity among species, so that species
+that experience environmental changes in the same way show positively correlated
+variations in their death rates.
+
+We generated over 45000 in-silico communities with diverse richness, trophic
+levels and connectance and experimentally simulated variable degrees of
+interaction strength, response diversity and environmental stochasticity.  For
+each community, we evaluated the effects on stability of species richness,
+response diversity, community structure and stochasticity.  Stability was itself
+partitioned in our analyses into population stability and asynchrony (i.e.
+portfolio and compensatory effects). Finally, we also evaluated the occurrence
+of negative and positive relationships between community stability and species
+richness.
 
@@
 ```{r}
+
 sem_cap <- paste0(
-  "Structural Equation Model linking food-web structure and stressors to temporal
-  stability of community biomass. a, continuous red arrows display positive and
-  dashed blue arrows display negative standardised effects, width of the arrows
-  being proportional to the absolute values of the standardised effects. Only
-  the standardised coefficients whose absolute values are superior to 0.05 are
-  displayed. The full table of coefficients including control variables is
-  displayed in Table S4. A more complete SEM containing further partition of
-  compensatory effects and control variables is displayed in Table S5. b, total
-  effects of food-web structure on community stability, asynchrony, and
-  population stability. N = ", nrow(tar_read(sim_fw)), " simulations.") %>%
+  "Structural Equation Model linking food-web structure and stressors to the
+  temporal stability of community biomass. a, Continuous blue arrows display
+  positive and dashed red arrows display negative standardised effects, width of
+  the arrows being proportional to the absolute values of the standardised
+  effects. Only the standardised coefficients whose absolute values are superior
+  to 0.05 are displayed. The full table of coefficients including control
+  variables is displayed in Table S2. b, Total effects of food-web structure on
+  community stability, asynchrony, and population stability derived from the
+  structural equation model. N = ", nrow(tar_read(sim_fw)), " simulations.") %>%
   str_replace_all("\\s+", " ")
@@
 ```{r sem, fig.cap=sem_cap, fig.id = "sem"}
-knitr::include_graphics(here("report", "figures", "p_sem_fig.pdf"))
+knitr::include_graphics(here::here("report", "figures", "p_sem_fig.pdf"))
 ```
@@
 ```
-
-## Drivers of community stability, population stability and asynchrony
 
@@
 
-rac <- get_eff(y = "async", x = "cpe")
-ras <- get_eff(y = "async", x = "sae_total")
+rac <- get_eff(y = "async", x = "cpe_int")
+ras <- get_eff(y = "async", x = "sae_doak")
 ```
 
-The `r format(m_sim(col = "n"), scientific = FALSE)` simulations generated a
-wide range of food-web structure (Median (5%, 95%), species richness:
-`r m_sim("richness")`, connectance: `r m_sim("ct_alive")`, average interaction
-strength: `r m_sim("avg_int_strength")`, maximum trophic level:
-`r m_sim("max_tlvl")`). We quantified the  (1) the respective effects of
-population
-stability and asynchrony on community stability, (2) the source of asynchrony,
-either portfolio effects or compensatory dynamics, and disentangled (3) how
-stressors (environmental stochasticity, response diversity) and food-web
-structure (species richness, average interaction strength, average trophic
-level, connectance) determine average population stability, portfolio effects
-(using Doak's definition), and compensatory dynamics stemming from species
-interactions. We did so by using a structural equation model which included all
-the simulation variables as control (i.e. predator interference, predator-prey
-mass ratio) to avoid the detection of spurious non-causal effects (See Methods,
-Table/Figure SXX). Overall, we found that population stability had a positive
-effect twice higher than asynchrony on the temporal stability of community
-biomass (resp. $r_\delta$= `r rscp` and `r rsca`, $r_\delta$ being the
-standardised coefficient, Fig. \@ref(fig:sem)a). We further found that
-asynchrony was driven more by portfolio effects than by compensatory dynamics
-stemming from species interactions (resp. $r_\delta$= `r rac` and `r ras`).
-However, we found opposite results, i.e. that compensatory dynamics contributed
-more than portfolio effects to asynchrony, using an alternative portfolio
-effects definition that attributes the effects of response diversity to
-compensatory effects instead of portfolio effects (Fig. SXX).
+Applying a structural equation model on the outcomes of food web simulations
+(see Methods) revealed that the temporal stability of community biomass is
+positively influenced by both population stability and asynchrony, and that
+population stability has twice the effect of asynchrony (resp. $r_\delta$=
+`r rscp` and `r rsca`, $r_\delta$ being the standardised coefficient, Fig.
+\@ref(fig:sem)a).
 
-Food-web structure had consistent negative effects on asynchrony, mainly through
-portfolio and compensatory effects (Fig. \@ref(fig:sem)a). Indeed, average
-trophic level and connectance had negative effects on the compensatory effects
-stemming from species interactions (resp. $r_\delta$= `r rct` and `r rcc`, Fig.
-\@ref(fig:sem)a), while average interaction strength had a small negative
-effects on portfolio effects ($r_\delta$= `r rsi`). In contrast, response
-diversity and species richness had strong positive effects on asynchrony,
-mainly through portfolio effects. Response diversity had a strong positive
-effect on portfolio effects ($r_\delta$= `r rsd`), and a negative one on
-compensatory dynamics ($r_\delta$= `r rcd`). In turn, species richness had a
-positive effect on both portfolio and compensatory effects (resp.
-$r_\delta$=`r rsr` and `r rcr`). Finally, environmental stochasticity had a
-small negative effect on compensatory dynamics.
+We further found that asynchrony is driven more by portfolio effects than by
+compensatory dynamics (resp. $r_\delta$= `r ras` and `r rac`). In more details, response
+diversity has strong positive effects on asynchrony, mainly through portfolio
+effects ($r_\delta$= `r rsd`), but also through a weaker positive effect on compensatory
+dynamics ($r_\delta$= `r rcd`). All other studied properties were found to have relatively
+much weaker effects on asynchrony. Food web structural properties – namely
+average trophic level, connectance and average interaction strength – have
+consistent negative effects on asynchrony, through both portfolio and
+compensatory effects (Fig. \@ref(fig:sem)a). Indeed, as average trophic level and connectance
+increase compensatory effects are reduced (resp. $r_\delta$= `r rct` and `r rcc`, Fig.
+\@ref(fig:sem)a), while average interaction strength has a small negative effect
+on portfolio effects ($r_\delta$= `r rsi`). Species richness has a positive
+effect on both portfolio and compensatory effects (resp. $r_\delta$=`r rsr` and
+`r rcr`). Finally, as expected, environmental stochasticity has little effect on
+asynchrony.
 
-In turn, we found little effect of food-web structure on population stability,
-except for average trophic level having a strong positive effect on
-population stability ($r_\delta$= `r rpt`, Fig. \@ref(fig:sem)a). In turn, the
-variance of environmental stochasticity had a strong negative effect on
-population stability ($r_\delta$= `r rpe`), while response diversity had a small
-positive effect on population stability ($r_\delta$= `r rpd`).
+Focusing on population stability, environmental stochasticity was found to have
+a strong negative effect on it ($r_\delta$= `r rpe`). All other studied properties were
+found to have little effect on population stability, except for the average
+trophic level which has a small positive effect ($r_\delta$= `r rpt`, Fig.
+\@ref(fig:sem)a, but see Fig. S1) and response diversity a small negative effect
+($r_\delta$= `r rpd`).
 
@@
 
-Deriving the sum of direct and indirect effects from the structural equation
-model, we show that both the variance of environmental stochasticity and species response
-diversity had by far the most important effects on community stability (resp.
-$r_\delta$= `r rtsenv` and `r rtsdiv`, Fig. \@ref(fig:sem)b). Species richness
-and average trophic level had similar positive total effects on community stability
-($r_\delta$=`r rtsr`), but through opposite pathways and antagonistic effects on
-asynchrony and population stability. While species richness increased community
-stability through a strong positive effect on asynchrony ($r_\delta$=`r rtar`), it
-also weakly decreased population stability ($r_\delta$=`r rtpr`). At the opposite, average
-trophic level increased community stability through strong positive effect on
-population stability ($r_\delta$=`r rtpt`), but dampened by a negative total
-effect on asynchrony ($r_\delta$=`r rtat`). Interestingly, average interaction
-strength also had a positive effect on population stability and a negative one
-on asynchrony (resp. $r_\delta$= `r rtpi` and `r rtai`), but resulting in a
-total negative effect on community stability ($r_\delta$= `r rtsi`).
-Connectance, instead, had a negative effect on community stability ($r_\delta$=
-`r rtsct`) through consistent negative effects on asynchrony and population
-stability (resp. $r_\delta$=`r rtact` and `r rtpct`).
-
-## Stability-richness relationship
+Deriving total effects from the sum of direct and indirect effects in the
+structural equation model (See Method), we showed that both environmental
+stochasticity and species response diversity have by far the strongest total
+effects on community stability (resp. $r_\delta$= `r rtsenv` and `r rtsdiv`,
+Fig. \@ref(fig:sem)b). Species richness and average trophic level have similar
+small but positive total effects on community stability ($r_\delta$=`r rtsr`),
+but through opposite pathways. While species richness increases community
+stability through a strong positive effect on asynchrony ($r_\delta$=`r rtar`),
+it also weakly decreases population stability ($r_\delta$=`r rtpr`). In
+contrast, average trophic level increases community stability through strong
+positive effect on population stability ($r_\delta$=`r rtpt`), but is dampened
+by a negative total effect on asynchrony ($r_\delta$=`r rtat`). Interestingly,
+average interaction strength also has a positive effect on population stability
+and a negative one on asynchrony (resp. $r_\delta$= `r rtpi` and `r rtai`). This
+results in a total negative effect on community stability ($r_\delta$=
+`r rtsi`). Connectance, instead, has a negative effect on community stability
+($r_\delta$= `r rtsct`) through negative effects on both asynchrony and
+population stability (resp. $r_\delta$=`r rtact` and `r rtpct`).
 
@@
 pred_cap <- paste0("Slope of the community stability - species
-  richness relationship according to food-web structure and response diversity. (a),
+  richness relationship based on food-web structure and response diversity. a,
   Diagrams displaying the slope coefficients of the effect of species richness
   on community stability. The average values of the control variables were used
-  to generate the predictions: ", pv_cap, ". (b, c): Examples of predictions
+  to generate the predictions: ", pv_cap, ". b, c: Examples of predictions
   from the model for two combinations of average trophic level and response
-  diversity (values displayed in panel (a)). Lines display the mean predictions
-  of the model. The coefficients of the linear model are displayed in Fig. S4.
+  diversity (values displayed in panel a). Lines display the mean predictions of
+  the model. The coefficients of the linear model are displayed in Fig. S3.
   Relationships between population stability, asynchrony and species richness
-  are displayed in Fig. S5."
+  are displayed in Fig. S2.
+  "
   ) %>%
@@
 
-Using a more complex linear model including interactions among food-web
-structure, response diversity and environmental stochasticity, we found that
-food-web structure strongly interacts with response diversity to determine the
-sign of the stability-richness relationships. In the absence of response
-diversity, we found only negative stability-richness, regardless of the food-web
-structure (Fig. \@ref(fig:pred)a). Response diversity enabled the rise of
-positive stability-richness relationships, enhanced by average interaction
-strength and dampened by average trophic level and connectance. Higher
-interaction strength led to positive stability-richness relationships for lower
-values of response diversity, interaction strength enhanced asynchrony-richness
-relationships (Fig. SXX), so that the stronger positive stability-richness
-relationships were found at both high interaction strength and response
-diversity. In contrast, higher average trophic level and connectance both led to
-negative stability-richness relationships, because they led to more negative
-population stability-richness relationships and weaker positive
-asynchrony-richness relationships (Fig. SXX). Overall, our results highlight
-strong contrast between the relatively small effects of food-web structure on overall
-community stability (Fig. \@ref(fig:sem)b) and their strong effects on
-stability-richness relationships (Fig. \@ref(fig:pred)a).
+We further assessed how environmental stochasticity and response diversity
+interacted with food-web structural properties to determine the sign of the
+stability-richness relationship, using a linear model including main effects and
+all interactions among food-web structural properties, response diversity and
+environmental stochasticity (see Methods). We found that there are strong
+interactions between response diversity and food-web structure, which jointly
+determine the sign of the stability-richness relationship.
+
+In the absence of response diversity, we found only negative stability-richness
+relationships, regardless of the food-web structure (Fig. \@ref(fig:pred)a).
+Response diversity enables the rise of positive stability-richness
+relationships, enhanced by average interaction strength and dampened by average
+trophic level and connectance. Higher interaction strength leads to positive
+stability-richness relationships for lower values of response diversity, and
+interaction strength enhances asynchrony-richness relationships (Fig. S2), so
+that the stronger positive stability-richness relationships are found at both
+high interaction strength and high response diversity levels. In contrast,
+higher average trophic level and connectance both lead to negative
+stability-richness relationships, because they drive more negative population
+stability-richness relationships and weaker positive asynchrony-richness
+relationships (Fig. S2). Overall, our results highlight a strong contrast
+between the relatively small effects of food-web structural properties on
+overall community stability (Fig. \@ref(fig:sem)b) but their strong effects on
+the slope of the stability-richness relationship (Fig. \@ref(fig:pred)a).
 
@@
 
-Temporal community stability is well documented in simplified assemblages
-such as plant communities, where community stability is driven by asynchrony in
-species fluctuations. In contrast, our results show that community stability in
-complex food-webs was mainly driven population stability rather than asynchrony.
-In the range of our simulations, we identified that environmental variability
-and response diversity were the main driver of community stability, far more
-than any food-web structure component, a result consistent across methodological
-choices (Fig. SXX). Moreover, we found that species richness and food-web
-structure have antagonistic but consistent effect on community stability.
-Finally, we found that the sign of the stability-richness relationship is
-strongly mediated by the interaction between food-web structure and response
-diversity. These results highlight the need to account for both food-web
-structure and response diversity to improve our understanding of the stability
-of ecological communities in variable environments.
+With the projected changes in climate and land use, and the expected resulting
+changes in community composition, it is important to understand the mechanisms
+which allow ecological communities to remain stable despite perturbations. The
+two components of temporal community stability are the average stability of the
+populations composing the community on the one hand, and the asynchrony of the
+population fluctuations on the other hand[@thibaut_understanding_2013;
+@zhao_biodiversity_2022]. In simplified assemblages, such as single trophic
+level communities, community stability has been shown to be driven by asynchrony
+in species fluctuations, rather than by population
+stability[@olivier_urbanization_2020]. However, whether this holds for more
+complex ecological communities, such as food webs, remains largely unknown.
+Here, we tackled this question using simulations of complex food-web dynamics
+with a stochastic bioenergetic model. Our model results show that, in complex
+food-webs, community stability is more driven by population stability than by
+asynchrony, in contrast with what was observed in single trophic level
+communities but in agreement with a previous food-web data
+study[@danet_species_2021]. Our results thereby contribute to reconcile models
+and data analyses. The study further reveals that the main drivers of community
+stability are environmental stochasticity and response diversity, respectively
+acting on population stability and asynchrony. Surprisingly, food-web structural
+properties have in turn much weaker effects, a result consistent across
+methodological choices (Fig. S1). Structural properties were however found to
+play an important role in the sign of the stability-richness relationship, which
+is strongly mediated by the interaction between food-web structure and response
+diversity. These results highlight the importance of response diversity to
+improve our understanding of the stability of ecological communities in variable
+environments.
 
-Our results show that community stability in complex food-webs is mainly driven
-by population stability rather than synchrony, which contrasts with empirical
-data that reported an equivalent influence of population stability and
-asynchrony on community stability in birds and bats assemblages
-[@olivier_urbanization_2020]. However, our results are in accordance with
-previous findings in empirical food-webs [@danet_species_2021] and
-food-web models [@eschenbrenner_diversity_2023]. Are there fundamental
-differences between single trophic and food-web in the contribution of
-population stability and asynchrony? We found that all food-web metrics, i.e.
-average trophic level, connectance, and average interaction strength all
-decreased asynchrony. In line with previous studies showing that predators can
-synchronise their preys [@raimondo_interspecific_2004;
-@kortsch_disentangling_2021], and that predator-prey couples are more
-synchronous [@danet_species_2021], those results suggest that trophic links
-might dampen overall asynchrony in ecological communities. A complementary
-explanation could be related to the biomass structure of food-webs. Food-webs
-typically includes range of bodymasses much larger than in species assemblages,
-differing in bodymass by several orders of magnitude [@brose_predator_2019].
-This highly uneven biomass distribution can translate in uneven species
-variability, thereby creating uneven contributions of species to asynchrony
-[@thibaut_understanding_2013] and limits portfolio effects and compensatory
-dynamics in species rich communities [@zhao_biodiversity_2022]. The fact that
-average trophic level, connectance, and average interaction strength all
-decreased evenness of portfolio effects lends toward this hypothesis. Our
-results then reinforce the evidence that community stability in food-web might
-be driven more by population stability than asynchrony.
+We found environmental stochasticity and response diversity to be the main
+overall drivers of community stability. While environmental stochasticity
+decreases population stability, response diversity generates asynchrony, thereby
+buffering environmental stochasticity. This result is in accordance with
+previous theoretical and empirical findings in competitive
+communities[@thibaut_diversity_2012; @thibaut_understanding_2013;
+@thebault_trophic_2005; @loreau_species_2008; @de_mazancourt_predicting_2013;
+@ives_stability_2000]. In turn, response diversity was found to operate on
+asynchrony mainly through portfolio effects in agreement with empirical findings
+in competitive assemblages[@thibaut_diversity_2012; @zhao_biodiversity_2022].
+This suggests that response diversity generates asynchrony mainly by the
+statistical averaging of random independent species fluctuations[@doak_statistical_1998].
 
-We further found that asynchrony was driven more by portfolio effects than
-compensatory dynamics. But this results was dependant of the definition of
-portfolio effects, as we found the opposite while taking Tilman's
-definition[@tilman_ecological_1999; @zhao_biodiversity_2022] instead of Doak's
-one[@doak_statistical_1998], in contrast with previous assessment in
-experimental plant communities[@zhao_biodiversity_2022]. Portfolio effects is
-supposed to measure stabilising effects of species richness in the absence of
-species interactions[@loreau_biodiversity_2021]. While Tilman's considers that
-portfolio effects are emerging from statistical averaging of independent species
-fluctuations alone (i.e. in the absence of covariance among species), Doak's
-explicitly states that statistical averaging can only emerge if compensatory
-dynamics hold by response diversity is present[@zhao_biodiversity_2022]. While
-the definition of portfolio effects is a long-standing
-debate[@zhao_biodiversity_2022], our results show that the importance of
-portfolio effects depends on where response diversity acts. In agreement with
-previous studies[@loreau_species_2008; @doak_statistical_1998;
-@thibaut_understanding_2013; @loreau_biodiversity_2021], we believe that the
-definition of portfolio effects standing from statistical averaging and
-environmental compensatory dynamics generated by response diversity is the more
-appropriate as the absence of species interactions does not guarantee independent
-species fluctuations, because common environment tend to generate positive
-covariances among species[@loreau_biodiversity_2021]. The fact that
-environmental stochasticity alone had a really small effect on asynchrony to the
-difference of response lends toward this interpretation. So, our study suggests
-that response diversity is a key ingredient to generate asynchrony, not only in
-plant communities, but also in food-webs. We further show that explicitly
-manipulating response diversity highlight that it is the main driver of
-asynchrony, and that the respective contribution of portfolio effects and
-compensatory dynamics to asynchrony depends on the decision to consider that
-response diversity is part of portfolio effects or compensatory dynamics.
+A consequence of the large effect of response diversity is that asynchrony in
+species fluctuations is driven more by the statistical averaging of independent
+species fluctuations (portfolio effects) than by compensatory dynamics emerging
+from species interactions. This finding is also coherent with previous studies
+in competitive communities[@thibaut_diversity_2012; @zhao_biodiversity_2022],
+but it was less expected to happen in food-webs. Trophic interactions are indeed
+expected to result in more compensatory dynamics resulting from oscillations
+between predators and prey[@vandermeer_coupled_2004] or prey switching from
+predators[@mccann_weak_1998; @mccann_diversitystability_2000]. However,
+pioneering theoretical studies have shown that environmental stochasticity can
+dampen prey switching[@vasseur_environmental_2007] and that trophic cascades
+between trophic levels in species rich food-webs are weak compared to
+food-chains and species poor food-web modules[@fahimipour_compensation_2017].
+So, the question of the importance of compensatory dynamics in complex food webs
+remains an open and interesting avenue for future research.
 
-We further found that higher average trophic level lead to higher community
-stability by increasing average population stability, confirming previous
-theoretical[@brose_allometric_2006; @shanafelt_stability_2018;
-@eschenbrenner_diversity_2023] and empirical[@danet_species_2021] results. But
-this effect disappeared when we simulated community dynamics with equal
-mortality rates for all species instead of allometric ones (Fig. S1). It then
-suggests that higher stability of food-web with higher average trophic level is
-because of species life-history traits and not directly by species interactions.
-The assumption that natural mortality rates decreased with bodymass is well
-documented across eukaryotes[@hatton_linking_2019] and seems to be a necessary
-ingredient for the stabilising effects of higher trophic levels. In turn, we
-found that average trophic level and connectance decreases strongly asynchrony
-mainly through a negative effect on compensatory dynamics generated by species
-interactions. Both higher connectance and average trophic level lead to greater
-generalism of predators in the niche model that we used to build food-webs. The
-synchronising effects of average trophic level and connectance echo with
-empirical findings that a generalist predator can indeed synchronise the
-dynamics of numerous preys[@raimondo_interspecific_2004;
-@korpimaki_predatorinduced_2005]. The overall effect of connectance on overall
-community stability was quite low, in agreement with previous empirical
-findings[@danet_species_2021]. Similarly, we found very low effects
-of the average interaction strength on community stability which in apparent
+In contrast to empirical evidence in competitive
+communities[@olivier_urbanization_2020], population stability (not asynchrony)
+was found to be  the dominant driver of community stability in our food web
+simulations. These results are in agreement with previous findings in empirical
+food-webs[@danet_species_2021] and food-web
+models[@eschenbrenner_diversity_2023], which suggests fundamental differences
+between competitive communities and food webs in the relative contributions of
+population stability and asynchrony to community stability. Our findings suggest
+that the presence of trophic links contributes to synchronise the species of the
+community because we found that the food-web metrics studied – namely average
+trophic level, connectance, and average interaction strength – all decrease
+asynchrony. These results are in line with empirical evidence that predators can
+synchronise their prey[@raimondo_interspecific_2004;
+@korpimaki_predatorinduced_2005], and that species pairs involved in trophic
+interactions are more synchronous than those that are not[@danet_species_2021].
+A complementary explanation for the relatively lower importance of asynchrony in
+food webs (compared to single trophic level communities) could be related to the
+biomass structure of food-webs. Food-webs typically include a larger range of
+body masses than single trophic level assemblages[@brose_predator_2019]. Such
+highly uneven biomass distribution can translate in uneven species temporal
+variability, thereby creating uneven species contributions to
+asynchrony[@thibaut_understanding_2013] and limiting portfolio effects and
+compensatory dynamics in species-rich communities[@zhao_biodiversity_2022].
+
+Investigating in more detail the drivers of community stability, our results
+suggest that species richness and the network structural properties investigated
+only have a weak effect on overall community stability. We found that higher
+average trophic level leads to higher community stability by increasing average
+population stability, confirming previous theoretical[@shanafelt_stability_2018;
+@eschenbrenner_diversity_2023; @brose_allometric_2006] and
+empirical[@danet_species_2021] results. However, this effect disappeared when we
+simulated community dynamics with equal mortality rates for all species instead
+of allometric ones (Fig. S1). This suggests that the higher stability of
+food-webs with higher average trophic levels stems more from their lower
+mortality rates rather than from their trophic role directly. The overall effect
+of connectance on overall community stability was found to be quite low, in
+agreement with previous empirical and theoretical findings[@danet_species_2021;
+@eschenbrenner_diversity_2023]. Similarly, we found very low effects of the
+average interaction strength on community stability, which is in apparent
 disagreement with the predominant role of interaction strength and connectance
-on stability in the complexity-stability debate [complexity-stability paradox,
-@may_will_1972]. But our study focused on the temporal stability of coexisting
-species at steady state, which might mask connectance and interaction strength
-values that led to species extinctions during the transient phase.
+on stability[@may_will_1972].
 
-We found that species richness had a positive effect on community stability of
-the same importance as average trophic level, but through opposite pathways.
-Species richness had strong positive effects on asynchrony through positive
-effects on portfolio and compensatory effects. It is in agreement with previous
-study showing that species richness can promote asynchrony by both
-pathways[@zhao_biodiversity_2022]. Furthermore, our study shows that the positive
-effects of species richness on asynchrony is three times lower than the effects
-of response diversity. Our model predictions further indicates that in absence
-of response diversity, we only observe negative relationships between
-community stability and species richness. Therefore, it reinforces the idea that
-response diversity is the crucial ingredient that hold the observed
-positive effects of species richness on community stability and not species
-richness alone[@thebault_trophic_2005; @loreau_species_2008;
-@loreau_biodiversity_2021]. In return, species richness had a small negative
-effect on average population stability. It is in agreement with previous
-meta-analysis reporting that such negative effects are common in natural systems
-but weak[@houlahan_negative_2018], but the mechanisms behind this relationship
-are still debated. Overall our study highlights that the central role of
-response diversity and species richness on asynchrony and thus community
-stability also extends to complex food-webs.
+Our results also allow us to revisit the old question of the relationship
+between the complexity of ecological communities and their
+stability[@may_will_1972; @angelis_stability_1975]. We found that response
+diversity enables the rise of positive stability-richness relationships,
+enhanced by average interaction strength and dampened by average trophic level
+and connectance. In the absence of response diversity, only negative
+relationships between community stability and species richness are observed.
+This reinforces the idea that increases in species richness increase community
+stability only if it adds species that respond differently to environmental
+perturbations, i.e. if there is response
+diversity[@de_mazancourt_predicting_2013; @thebault_trophic_2005]. Indeed, a
+community with numerous species which respond differently to environmental
+change is more likely to buffer a wide array of perturbations
+[@yachi_biodiversity_1999; @ives_stability_2000]. Despite its relatively weaker
+effect on community stability (than response diversity and environmental
+stochasticity), food-web structure interacts strongly with response diversity to
+determine the sign of stability-richness relationships. Surprisingly, we find
+that higher average interaction strength enhances positive stability-richness
+relationships by enhancing asynchrony-richness relationships. Conversely, higher
+average trophic level and higher connectance both led to negative
+stability-richness relationships by dampening asynchrony-richness relationships.
+Our results resonate with findings that some community structure can lead to
+negative stability-richness relationships, as previously reported in freshwater
+food-webs[@danet_species_2021]. Response diversity might therefore be one of the
+mechanisms that explains why positive relationships between stability and
+species richness are so prevalent in empirical settings[@elmqvist_response_2003;
+@thibaut_understanding_2013], while food-web theoretical models that do not
+often include environmental stochasticity and response diversity typically find
+negative complexity-stability relationships[@ives_stability_2007].
 
-Our results further show that food-web structure interact strongly with response
-diversity to determine the sign of stability-richness relationships. We found
-surprisingly that higher average interaction strength enhance positive
-stability-richness relationships, by enhancing asynchrony-richness
-relationships. At the opposite, higher average trophic level and higher
-connectance both led to negative stability-richness, by dampening
-asynchrony-richness relationships. Our result echoes with previous results
-showing negative stability-richness relationship in freshwater
-food-webs[@danet_species_2021]. Those results also echo with the
-complexity-stability debate where population stability decreases as the
-community is more species diverse, has higher connectance, and higher
-interaction strength[@may_will_1972]. However, we found that the negative
-effects of complexity on stability-richness relationships are dampened in
-presence of high response diversity. Response diversity might then be one of the
-mechanisms that explains why positive relationships between stability and
-species richness are so prevalent in empirical settings while food-web
-theoretical models that do not often include environmental stochasticity and
-response diversity finds negative complexity-stability
-relationships[@ives_stability_2007]. It is also in agreement previous studies
-showing that higher connectance in low response diversity can drive negative
-stability-richness in plant-herbivore systems[@thebault_trophic_2005]. Finally,
-found that the strength of environmental stochasticity itself does not
-affect the shape of the community stability-richness but rather controls the
-overall community stability through its effects on population stability.
-
-In conclusion, our study uncovers complex but consistent effects of response
-diversity and food-web structure on the temporal stability of complex
-communities. We showed that community stability was more driven by population
-stability than asynchrony. We further showed that species richness and average
-trophic level both increase community stability but by opposite pathways. Our
-study also demonstrates that response diversity is the core mechanism driving
-the buffering effects of biodiversity on environmental stochasticity also in
-complex food-webs. Finally, our study shows that food-web structure and response
-diversity interact to drive a continuum from negative to positive
-stability-richness relationships. Looking to practical applications, our study
-highlights that species richness without response diversity does not lead to
-positive community-richness relations. So that assessment on how ecological
-communities widespread recomposition[@dornelas_assemblage_2014;
-@blowes_geography_2019] and homogenisation[@olden_homogocene_2018;
-@muthukrishnan_invasive_2020; @wang_biotic_2021] is affecting response diversity
-would be crucial to accurately predict long-term consequences on community
-stability. The second take away to be drawn is that the variance of
-environmental stochasticity was the main driver of community stability,
-suggesting that increase in species richness and the maintenance of high
-response diversity would be not enough to compensate for strong increase in
-environmental variability in the coming decades[@lee_ipcc_2023].
+In conclusion, our study highlights the complex but consistent effects of
+response diversity and food-web structure on the temporal stability of species
+rich communities. At the core of the insurance
+hypothesis[@yachi_biodiversity_1999; @loreau_biodiversity_2021], our results
+suggest that environmental stochasticity and response diversity are the main
+mechanisms driving community stability, while food-web structural properties are
+only mediating them. This aligns with the idea that, in species-rich
+communities, community structure might be secondary in understanding the generic
+effects of biodiversity on ecosystem functioning[@barbier_generic_2018;
+@ives_stability_2000]. Our results further add to mounting evidence that
+population stability is a stronger driver of community stability than asynchrony
+in food-webs, in contrast with what was observed in competitive communities. The
+fact that environmental stochasticity was found to be the main driver of overall
+community stability raises concerns about the consequences of the current rise
+in the frequency and severity of environmental extreme events for ecological
+communities[@ghosh_temperature_2024; @lee_ipcc_2023]; indeed our results suggest
+that these changes are unlikely to be compensated by biotic mechanisms alone.
+Documenting how rapid biodiversity changes[@dornelas_assemblage_2014;
+@blowes_geography_2019] driven by human pressures[@danet_past_2024] – and in
+particular the reported homogenisation[@olden_homogocene_2018;
+@wang_biotic_2021] in community composition – affect response diversity will be
+key to accurately predict how it will affect, in turn, the stability of
+communities.
 
@@
 ```
-\pagebreak
 
-```{r}
-met_cap <- "Examples of stochastic food-web simulations. a, Simulations with low
-and high response diversity. b, simulations with low and high predator-prey mass
-ratio (upper and bottom panels), low and high species richness (left and right
-  panels). The food-webs are displayed on the side with the node size
-being proportional to the average species biomass across the simulation. We
-also display the food-web structure and the stability metrics. Across all
-simulations, $h = 2$, $\\sigma_e = .3$. Low and high response diversity were
-respectively $\\rho = 1$ and $\\rho = 0$. Low and high PPMR were respectively 1
-and 100." %>%
-str_replace_all("\\s+", " ")
-```
-
-```{r met, fig.cap = met_cap}
-knitr::include_graphics(here("report", "figures", "p_methods.pdf"))
-```
-
-We generated food-web structure using the niche model [@williams_simple_2000]
+We generated food-web structure using the niche model[@williams_simple_2000]
 with an initial species richness from $`r pS["min"]`$ to $`r pS["max"]`$, and
@@
 $`r pe["min"]`$ to $`r pe["max"]`$, the range of mortality rates observed in
-protists [@vasseur_environmental_2007]. We decreased response diversity by
+protists[@vasseur_environmental_2007]. We decreased response diversity by
 increasing $\rho$ from $`r pr["min"]`$ to $`r pr["max"]`$ (i.e. response
-diversity being $1 - \rho$) (Fig. \@ref(fig:met)a).
+diversity being $1 - \rho$) (Fig. S4).
 
@@
 scaled mortality rate $d$) in the community, we varied the Predator-Prey
-Mass Ratio (PPMR) from $`r pZ["min"]`$ to $`r pZ["max"]`$ (Fig. \@ref(fig:met)b).
+Mass Ratio (PPMR) from $`r pZ["min"]`$ to $`r pZ["max"]`$ (Fig. S5b).
 We set $h = 2$, i.e. a functional response of type III (eq. \@ref(eq:holling)),
@@
 $c = `r pc["max"]`$, eq. \@ref(eq:holling)), as predator interference was shown
-to have a tremendous role on population stability [@brose_allometric_2006]. We
+to have a tremendous role on population stability[@brose_allometric_2006]. We
 set a global carrying capacity of $K' = 10$ to ensure that consumers were not
@@
 generation and simulations were done using the `Julia` package
-`EcologicalNetworkDynamics.jl` [@lajaaiti_ecologicalnetworksdynamicsjl_2024].
+`EcologicalNetworkDynamics.jl`[@lajaaiti_ecologicalnetworksdynamicsjl_2024].
+
+In sum, we generated `r format(m_sim(col = "n"), scientific = FALSE)`
+simulations generated a wide range of food-web structure (Median (5%, 95%),
+species richness: `r m_sim("richness")`, connectance: `r m_sim("ct_alive")`,
+average interaction strength: `r m_sim("avg_int_strength")`, maximum trophic
+level: `r m_sim("max_tlvl")`) (Table S3).
 
@@
 species to environmental fluctuations, such as portfolio effects are dampened if
-species have correlated responses. For completeness and comparison with previous
-studies, we also measured portfolio effects according to Tilman's
-definition[@tilman_ecological_1999] which consider that portfolio effects stem
-solely from a pure statistical averaging of independent species fluctuations
-($SAE$).
+species have correlated responses.
 
@@
 from species interactions were computed as: $CPE_{int} = CPE / CPE_{env}$.
-Finally, portfolio effects was computed as: $SAE \times CPE_{env}$ and
-compensatory dynamics raising from species interactions as $CPE_{int}$.
+Finally, portfolio effects was computed as: $PFE = SAE \times CPE_{env}$ and
+compensatory dynamics raising from species interactions as $CPE_{int}$. The
+final stability decomposition reads as follows:
+
+\begin{equation}
+\begin{aligned}
+S_{com} = S_{pop} \times PFE \times CPE_{int}
+(\#eq:scom3)
+\end{aligned}
+\end{equation}
 
@@
 different facets of temporal stability of biomass (i.e. population stability,
-portfolio effects and compensatory dynamic effects). We tested the
+asynchrony, portfolio effects and compensatory dynamic effects). We tested the
 effects of food-web structure (average interaction strength, average trophic
-level, connectance) on population stability and asynchrony partitions (portfolio and
-compensatory effects). Grounded in theoretical ecology, we expected that higher
-average trophic level, lower interaction strength, lower connectance[@mccann_weak_1998;
-@mccann_reevaluating_1997; @shanafelt_stability_2018]. We further added
-simulation parameters as control variables because higher Predator-Prey Mass
-Ratio and predator interference were also expected to increase population
-stability [@brose_allometric_2006]. Finally, we tested the effects of environmental
-stochasticity and response diversity on population stability and asynchrony
-partitions, although there were predicted to mainly affect to population stability
-(i.e. by increasing amplitude of population fluctuations) and asynchrony (i.e.
-by generating independent population fluctuations) respectively. We
-completed the structural equation model with the mathematical relationship
-linking compensatory dynamics and statistical averaging effects to asynchrony,
-and from asynchrony and population stability to community stability. We further
-developed a more detailed SEM including the partition of compensatory dynamics
-due to species interactions ($CPE_{int}$) and due to environmental fluctuations
-($CPE_{env}$).
+level, connectance) on population stability and asynchrony partitions (portfolio
+and compensatory effects). Grounded in theoretical ecology, we expected that
+higher average trophic level, lower interaction strength, lower
+connectance result in higher population stability and lower asynchrony[@mccann_weak_1998; @mccann_reevaluating_1997;
+@mccann_diversitystability_2000; @fahimipour_compensation_2017]. We further
+added simulation parameters as control
+variables because higher Predator-Prey Mass Ratio and predator interference were
+also expected to increase population stability [@brose_allometric_2006].
+Finally, we tested the effects of environmental stochasticity and response
+diversity on population stability and asynchrony partitions, although there were
+predicted to mainly affect to population stability (i.e. by increasing amplitude
+of population fluctuations) and asynchrony (i.e. by generating independent
+population fluctuations) respectively. We completed the structural equation
+model with the mathematical relationship linking compensatory dynamics due to
+species interactions ($CPE_{int}$) and statistical averaging effects ($SAE
+\times CPE_{env}$) to asynchrony, and from asynchrony and population stability
+to community stability.
 
@@
 \@ref(eq:scom2)). We ensured that all the linear models composing the structural
-equation model presented low multicollinearity (Variance Inflation
-Factor < 3, Table S2), although interaction strength and species richness were
-highly correlated (Fig. S2). The structural equation model using the R package
-`PiecewiseSEM` [@lefcheck_piecewisesem_2016]. We then bootstrapped (N = 100) the
+equation model presented low multicollinearity (Variance Inflation Factor < 3,
+Table S4), although interaction strength and species richness were highly
+correlated (Fig. S5). The structural equation model using the R package
+`PiecewiseSEM`[@lefcheck_piecewisesem_2016]. We then bootstrapped (N = 100) the
 SEM to obtain confidence intervals on the estimated effects and computed the sum
-of the direct and indirect effects using `semEff` R package
-[@murphy_semeff_2021]. In the main text, we reported standardised coefficients
-which were obtained by scaling the coefficients by the standard deviation of the
-response and predictor variable. Finally, we reported only the direct
-standardised coefficients that had an absolute value above $0.05$, because
-almost all linked were statistically significant given the high numbers of
-simulations.
+of the direct and indirect effects using `semEff` R
+package[@murphy_semeff_2021]. In the main text, we reported standardised
+coefficients which were obtained by scaling the coefficients by the standard
+deviation of the response and predictor variable. Finally, we reported only the
+direct standardised coefficients that had an absolute value above $0.05$,
+because almost all linked were statistically significant given the high numbers
+of simulations.
 
-In a second analysis, we aimed to test how stability-species richness
-relationships were modulated by food-web structure and the two stressors:
-environmental stochasticity and response diversity. We then modelled temporal
-stability of community biomass according to food-web structure: species
-richness, weighted average trophic level, connectance and average interaction
-strength, as well as environmental stochasticity and species response diversity.
-We further included the two-way interactions between species richness and
-food-web structure, plus between species richness and stressors. Finally, we
-added the three-way interaction between species richness, food-web structure and
-stressors. We added predator interference, predator-prey mass ratio as control
-variables. We further added the id of the food-web as a random intercept. We
-then used the linear equation of the model and associated slope coefficients to
-predict the shape of the relationship between community stability and species
-richness according to a gradient of response diversity and of food-web
-structure. To do so, we summed all the coefficients involving species richness
-in the model, i.e. the one, two, and three-way terms. The values of the other
-variables were set to the values indicated in the Fig. \@ref(fig:pred). The VIF
-were inferior to 3, indicating low multicollinearity (Table S3), we checked the
-distribution of the residuals (Fig. S3) using `DHARMa` R package. The model was
-implemented using the R package `glmmTMB` [@brooks_glmmtmb_2017].
+In a second analysis, we tested how food-web structure, response diversity, and
+environmental stochasticity modulate stability-species richness relationships.
+We modelled temporal stability of community biomass according to food-web
+structure: species richness, weighted average trophic level, connectance and
+average interaction strength, as well as environmental stochasticity and
+response diversity. We further included the two-way interactions between species
+richness and food-web structure, between species richness and response
+diversity, between species richness and environmental stochasticity. Finally, we
+added the three-way interactions between species richness, food-web structure
+and response diversity, between species richness, food-web structure and
+environmental stochasticity. We added predator interference, predator-prey mass
+ratio as control variables. We further added the ID of the food-web as a random
+intercept. We then used the linear equation of the model and associated slope
+coefficients to predict the shape of the relationship between community
+stability and species richness according to a gradient of response diversity and
+of food-web structure. To do so, we summed all the coefficients involving
+species richness in the model, i.e. the one, two, and three-way terms. The
+values of the other variables were set to the values indicated in the Fig.
+\@ref(fig:pred). The VIF were inferior to 3, indicating low multicollinearity
+(Table S5), we checked the distribution of the residuals (Fig. S6) using
+`DHARMa` R package. The model was implemented using the R package
+`glmmTMB`[@brooks_glmmtmb_2017].
 

### 2024-08-29 paper/supplementary_figures.Rmd
Cleaning targets pipeline (removing old code not used)

@@
 
-(ref:cor-cap) Spearman's correlation coeffients among stability components,
-food-web structure, and model parameters.
-
-```{r p-cor, fig.cap="(ref:cor-cap)"}
-knitr::include_graphics(here("report", "figures", "p_cor.pdf"))
-```
-
-(ref:dharma-lm-cap) Distribution of residuals for the linear models predicting the
-relationship between community stability and species richness (Fig. 3). a,b,c
-for respectively community stability, population stabilty and asynchrony. Left
-panels display the distribution of the quantiles, and indicate that residuals
-are quite well distributed. Right panels display the scaled residuals versus the
-predicted values. The slight U-shape might indicate the lack of a polynomial
-term in the model, but overall the model looks to have appropriate fitting.
-
-```{r dharma-lm, fig.cap="(ref:dharma-lm-cap)"}
-knitr::include_graphics(here("report", "figures", "p_diagnotisc_model_fw_stab_comp.jpg"))
-```
-
-(ref:coeff-lm-cap) Standardised coefficients for the linear model predicting the
-relationship between community stability and species richness (Fig. 3).
-
-```{r coeff-lm, fig.cap="(ref:coeff-lm-cap)"}
-knitr::include_graphics(here("report", "figures", "p_model_fw_stab_comp_scaled_coeff.pdf"))
-```
-
 ```{r}
@@
 knitr::include_graphics(here("report", "figures", "p_pred_sr_resp_div_supp.pdf"))
+```
+
+(ref:coeff-lm-cap) Standardised coefficients for the linear model predicting the
+relationship between community stability and species richness (Fig. 3).
+
+```{r coeff-lm, fig.cap="(ref:coeff-lm-cap)"}
+knitr::include_graphics(here("report", "figures", "p_model_fw_stab_comp_scaled_coeff.pdf"))
+```
+
+```{r}
+met_cap <- "Examples of stochastic food-web simulations. a, Simulations with low
+and high response diversity. b, simulations with low and high predator-prey mass
+ratio (upper and bottom panels), low and high species richness (left and right
+  panels). The food-webs are displayed on the side with the node size
+being proportional to the average species biomass across the simulation. We
+also display the food-web structure and the stability metrics. Across all
+simulations, $h = 2$, $\\sigma_e = .3$. Low and high response diversity were
+respectively $\\rho = 1$ and $\\rho = 0$. Low and high PPMR were respectively 1
+and 100." %>%
+str_replace_all("\\s+", " ")
+```
+
+```{r met, fig.cap = met_cap}
+knitr::include_graphics(here("report", "figures", "p_methods.pdf"))
+```
+
+(ref:cor-cap) Spearman's correlation coeffients among stability components,
+food-web structure, and model parameters.
+
+```{r p-cor, fig.cap="(ref:cor-cap)"}
+knitr::include_graphics(here("report", "figures", "p_cor.pdf"))
+```
+
+(ref:dharma-lm-cap) Distribution of residuals for the linear models predicting the
+relationship between community stability and species richness (Fig. 3). a,b,c
+for respectively community stability, population stabilty and asynchrony. Left
+panels display the distribution of the quantiles, and indicate that residuals
+are quite well distributed. Right panels display the scaled residuals versus the
+predicted values. The slight U-shape might indicate the lack of a polynomial
+term in the model, but overall the model looks to have appropriate fitting.
+
+```{r dharma-lm, fig.cap="(ref:dharma-lm-cap)", out.width = "80%"}
+knitr::include_graphics(here("report", "figures", "p_diagnotisc_model_fw_stab_comp.jpg"))
 ```
@@
     label = "param") %>%
+  kable_styling(latex_options = c("striped", "hold_position"))
+```
+
+```{r}
+tar_read(tab_sem_doak_eff) %>%
+  kable(booktabs = TRUE,
+    format = "latex",
+    caption = "Standardised estimates from the Structural Equation Model
+    displayed in main text (Fig. 2).",
+    label = "sem-coeff"
+    ) %>%
+collapse_rows(columns = 1, latex_hline = "major", valign = "middle") %>%
+kable_styling(latex_options = c("striped", "hold_position"))
+```
+
+```{r, eval = FALSE}
+tar_read(tab_sem_simplified_eff) %>%
+  kable(booktabs = TRUE,
+    format = "latex",
+    caption = "Standardised estimates from the supplementary Structural Equation
+    Model which includes the partition of compensatory effects rising from
+    environmental fluctuations and species interactions, and partition of
+    statistical averaging effects (portfolio effects).", label =
+    "sem-supp-coeff") %>%
+  collapse_rows(columns = 1, latex_hline = "major", valign = "middle") %>%
   kable_styling(latex_options = c("striped", "hold_position"))
@@
 ```
-
-```{r}
-tar_read(tab_sem_doak_eff) %>%
-  kable(booktabs = TRUE,
-    format = "latex",
-    caption = "Standardised estimates from the Structural Equation Model
-    displayed in main text (Fig. 2).",
-    label = "sem-coeff"
-    ) %>%
-collapse_rows(columns = 1, latex_hline = "major", valign = "middle") %>%
-kable_styling(latex_options = c("striped", "hold_position"))
-```
-
-```{r}
-tar_read(tab_sem_simplified_eff) %>%
-  kable(booktabs = TRUE,
-    format = "latex",
-    caption = "Standardised estimates from the supplementary Structural Equation
-    Model which includes the partition of compensatory effects rising from
-    environmental fluctuations and species interactions.",
-    label = "sem-supp-coeff") %>%
-collapse_rows(columns = 1, latex_hline = "major", valign = "middle") %>%
-kable_styling(latex_options = c("striped", "hold_position"))
-```

### 2024-08-29 job/csc_arg.sh

@@ -28,6 +28,7 @@ END=$((${STEPSIZE} * ${SLURM_ARRAY_TASK_ID}))
 
 echo "Starting task from ${START} to ${END}"
 
+# Default simulation
 cd ${DIR_ENV} && ${JULIA} --project=${DIR_ENV} ${DIR_ENV}/${DIR_SCRIPT}/simulation_args.jl \
     --first_sim=${START} --last_sim=${END}\
     --param_file="scripts/param_comb_zc.arrow"\
@@ -39,6 +40,7 @@ cd ${DIR_ENV} && ${JULIA} --project=${DIR_ENV} ${DIR_ENV}/${DIR_SCRIPT}/simulati
     --re_run=true\
     --d=nothing
 
+# Rebuild food-web after removing disconnected species
 cd ${DIR_ENV} && ${JULIA} --project=${DIR_ENV} ${DIR_ENV}/${DIR_SCRIPT}/simulation_args.jl \
     --first_sim=${START} --last_sim=${END}\
     --param_file="scripts/param_comb_zc.arrow"\
@@ -50,6 +52,7 @@ cd ${DIR_ENV} && ${JULIA} --project=${DIR_ENV} ${DIR_ENV}/${DIR_SCRIPT}/simulati
     --re_run=true\
     --d=nothing
 
+# Do not standardise carrying capacity according the number of primary producers
 cd ${DIR_ENV} && ${JULIA} --project=${DIR_ENV} ${DIR_ENV}/${DIR_SCRIPT}/simulation_args.jl \
     --first_sim=${START} --last_sim=${END}\
     --param_file="scripts/param_comb_zc.arrow"\
@@ -61,6 +64,7 @@ cd ${DIR_ENV} && ${JULIA} --project=${DIR_ENV} ${DIR_ENV}/${DIR_SCRIPT}/simulati
     --re_run=true\
     --d=nothing
 
+# Death rates are fixed, i.e. are not allometric
 cd ${DIR_ENV} && ${JULIA} --project=${DIR_ENV} ${DIR_ENV}/${DIR_SCRIPT}/simulation_args.jl \
     --first_sim=${START} --last_sim=${END}\
     --param_file="scripts/param_comb_zc.arrow"\

### 2024-08-29 use_case/module.jl

@@ -4,7 +4,8 @@
 
 
 import Pkg
-using DifferentialEquations, BEFWM2, ProgressMeter, SparseArrays, LinearAlgebra, DataFrames, CSV, Arrow
+using DifferentialEquations, EcologicalNetworksDynamics, ProgressMeter, SparseArrays, LinearAlgebra, DataFrames, CSV, Arrow
+using Distributions
 include("src/stochastic_mortality_model.jl")
 include("src/sim.jl")
 include("src/interaction_strength.jl")
@@ -67,21 +68,23 @@ param = ModelParameters(foodweb,
 #sim_int_mat(A; σₑ = .5, alpha_ij = 0, Z = 100, h = 2.0, c = 1.0, K = 1.0, max = 50000, last = 25000, dt = 0.1, return_sol = false)
 #
 #
-alphaij = 0.8
+alphaij = 0.0
 sim = map(x -> sim_int_mat(x;
                            ρ = 0, alpha_ij = alphaij,
-                           σₑ = 0.9,
-                           d = 0.1,
-                           Z = 10, h = 2.0, c = 1.0,
-                           r = 1.8, K = 20.0,
+                           σₑ = 0.1,
+                           d = 0.05,
+                           Z = 100, h = 2.0, c = 1.0,
+                           r = 1.0, K = 10.0,
                            K_alpha_corrected = true,
-                           fun = stoch_d_dBdt!,
+                           dbdt = EcologicalNetworksDynamics.stoch_d_dBdt!,
                            max = 2000, last = 100, dt = 0.1,
                            return_sol = false),
           fw_module);
 
 df = DataFrame(sim)
 df[:, :name] = collect(keys(fw_module))
+
+df[:, [:name,:richness, :stab_com, :avg_cv_sp, :sync]]
 
 rep = 1:10
 fw_module_names = keys(fw_module)
@@ -98,7 +101,7 @@ sim = @showprogress pmap(p -> merge(
                                  σₑ = p.sigma,
                                  d = 0.1,
                                  Z = 100, h = 2.0, c = 1.0, K = 3.0,
-                                 fun = stoch_d_dBdt!,
+                                 dbdt = EcologicalNetworksDynamics.stoch_d_dBdt!,
                                  max = 1000, last = 100, dt = 0.1, return_sol = false)
                     ),
                          param
@@ -131,15 +134,18 @@ sim = @showprogress pmap(p -> merge(
                          param
                         )
 sim_competition = map(x -> sim_int_mat(zeros(x, x);
[…]

### 2024-08-29 use_case/two_species_kuramoto.jl

@@ -34,8 +34,8 @@ function get_parameters_two_species_kuramoto(;
     pref = [
             0 0 0 0;
             0 0 0 0;
-            1 B 0 0;
-            B 1 0 0;
+            1-B B 0 0;
+            B 1-B 0 0;
            ]
     # Foodweb
     foodweb = FoodWeb(A)
@@ -90,12 +90,13 @@ p1 = plot(m, idxs = [3, 4], legend = false, title = "Trophic coupling")
 coefficient_of_variation(m, idxs = [3, 4])
 
 # Resource coupling
-p = get_parameters_two_species_kuramoto(B = 0.00, α = .1)
+p = get_parameters_two_species_kuramoto(B = 0.00, α = .95)
 m = simulate(p, [.1, .3, .1, .3],
              tmax = 600,
              callback = nothing
             );
 p2 = plot(m, idxs = [3, 4], legend = false, title = "Resource coupling")
+coefficient_of_variation(m, idxs = [3, 4], last = 500)
 
 # No Ressource  nor trophic coupling
 p = get_parameters_two_species_kuramoto(B = 0.00, α = 0)

### 2024-08-29 paper/manuscript.Rmd
Add repo link to manuscript
Fix typos and clarify formulations in M&M

@@
 output:
+  officedown::rdocx_document:
+    number_sections: false
+    base_format: "bookdown::word_document2"
   bookdown::pdf_document2:
@@
     number_sections: false
-  officedown::rdocx_document:
-    number_sections: false
-    base_format: "bookdown::word_document2"
 always_allow_html: true
@@
 diversity has strong positive effects on asynchrony, mainly through portfolio
-effects ($r_\delta$= `r rsd`), but also through a weaker positive effect on compensatory
+effects ($r_\delta$= `r rsd`), at the expense of compensatory
 dynamics ($r_\delta$= `r rcd`). All other studied properties were found to have relatively
@@
 on portfolio effects ($r_\delta$= `r rsi`). Species richness has a positive
-effect on both portfolio and compensatory effects (resp. $r_\delta$=`r rsr` and
+effect on both portfolio and compensatory effects (resp. $r_\delta$= `r rsr` and
 `r rcr`). Finally, as expected, environmental stochasticity has little effect on
@@
 Fig. \@ref(fig:sem)b). Species richness and average trophic level have similar
-small but positive total effects on community stability ($r_\delta$=`r rtsr`),
+small but positive total effects on community stability ($r_\delta$= `r rtsr`),
 but through opposite pathways. While species richness increases community
-stability through a strong positive effect on asynchrony ($r_\delta$=`r rtar`),
-it also weakly decreases population stability ($r_\delta$=`r rtpr`). In
+stability through a strong positive effect on asynchrony ($r_\delta$= `r rtar`),
+it also weakly decreases population stability ($r_\delta$= `r rtpr`). In
 contrast, average trophic level increases community stability through strong
-positive effect on population stability ($r_\delta$=`r rtpt`), but is dampened
-by a negative total effect on asynchrony ($r_\delta$=`r rtat`). Interestingly,
+positive effect on population stability ($r_\delta$= `r rtpt`), but is dampened
+by a negative total effect on asynchrony ($r_\delta$= `r rtat`). Interestingly,
 average interaction strength also has a positive effect on population stability
@@
 ($r_\delta$= `r rtsct`) through negative effects on both asynchrony and
-population stability (resp. $r_\delta$=`r rtact` and `r rtpct`).
+population stability (resp. $r_\delta$= `r rtact` and `r rtpct`).
 
@@
 is widely used to simulate the dynamics of complex ecological communities
-because of the simplicity  and because it can be parametrized using  the
+because of the simplicity of its parametrisation, using the
 metabolic theory of ecology [@brown_toward_2004]. The model describes species
@@
 that depends on their mass specific metabolic rate ($x_i$),  maximum consumption
-rate ($y_i$) and on the functional response ($F_ij$) describing how the rate of
-consumption of a consumer $i$ on a resource $j$ vary with the biomass of this resource.
-Consumers then lose biomass by being consumed, $e_ij$ being the assimilation
-efficiency of the consumer $j$ on the resource $i$. Consumers also lose biomass
-over time through metabolic losses ($-x_iB_i$) and by natural mortality due to
-environment ($-d_iB_i$). The primary producers gain biomass over time with a
+rate ($y_i$) and on the functional response ($F_{ij}$) describing how the rate
+of consumption of a consumer $i$ on a resource $j$ vary with the biomass of this
+resource. Consumers then lose biomass by being consumed, $e_{ij}$ being the
+assimilation efficiency of the consumer $j$ on the resource $i$. Consumers also
+lose biomass over time through metabolic losses ($-x_iB_i$) and natural
+mortality ($-d_iB_i$). The primary producers gain biomass over time with a
 growth rate ($r_i$, eq. \@ref(eq:prod)) and a functional response ($G_i$)
@@
 representing a fluctuating environment. Based on the literature and previous
-models [@vasseur_environmental_2007], we assumed that natural mortality rates
+models[@vasseur_environmental_2007; @hatton_linking_2019], we assumed that natural mortality rates
 scales inversely with the species body mass ($d_i = d_0M_i^{-1/4}$), as all
 other physiological parameters. We used a basal natural mortality rate of $d_0 =
-.4$, as done in previous studies[@vasseur_environmental_2007].
+0.4$, as a previous study[@vasseur_environmental_2007].
 
-We introduced environmental stochasticity by considering stochastic variation of
+We introduced environmental stochasticity by considering stochastic variation in
 mortality rates. Doing so allows to consider stochasticity without modifying
-species interactions themselves
-[@vasseur_environmental_2007]. The stochastic part of the mortality rates
+species interactions themselves[@vasseur_environmental_2007]. The stochastic part of the mortality rates
 ($\epsilon_{i, t}$) follow a normal distribution 0 centered
@@
 e^{\epsilon_{i, t}}$, which ensured that the mortality rates never become
-negative [@vasseur_environmental_2007]. We
-simulated $\epsilon$ using an Ornstein-Uhlenbeck process, which is a modified
+negative[@vasseur_environmental_2007]. We
+simulated $\epsilon$ using an Ornstein-Uhlenbeck process, a modified
 Brownian motion where the stochastic values tend to come back to the central
@@
 mortality rates ($\rho_{ij, i \neq j}$) such as response diversity is maximal
-when species mortality rates are uncorrelated ($\rho = 0$) and null when species
-mortality rates are perfectly correlated ($\rho = 1$) [@ripa_food_2003;
-@vasseur_environmental_2007; @gouhier_synchrony_2010]. So the species mortality
-rates were a product of the stochastic mortality rates generated by the
-Ornstein-Uhlenbeck process and a variance-covariance matrix such as:
+when the stochastic component of species mortality rates ($\epsilon_{i, t}$)
+are uncorrelated ($\rho = 0$), and response diversity is null when the
+stochastic component of species mortality rates are perfectly
+correlated[@ripa_food_2003; @vasseur_environmental_2007; @gouhier_synchrony_2010] ($\rho = 1$).
+So the species mortality rates were a product of the stochastic mortality rates
+generated by the Ornstein-Uhlenbeck process and a variance-covariance matrix
+such as:
 
@@
 
-We numerically solved the stochastic differential equation systems during 2000
-timesteps and collected the last 500 timesteps, similarly to previous studies
-[@brose_allometric_2006]. We set $d_t = .1$, and $d_t = .05$ when instability
-was detected during the simulations due to stiff changes in biomass. We set
-extinction threshold to $10^{-6}$ and if an extinction happened in the last 500
-timesteps, we continued to run the simulation for another 1000 timesteps until
+We numerically solved the stochastic differential equation systems during at
+least 2000 timesteps and collected the last 500 timesteps, similarly to previous
+studies [@brose_allometric_2006]. We numerically solve the system with $\Delta t
+= 0.1$ or $\Delta t = 0.05$ when instability was detected during the simulations
+due to stiff changes in biomass. We set extinction threshold to $10^{-6}$ and if
+an extinction happened in the last 500 timesteps, we continued to run the
+simulation for another 1000 timesteps until
 there was no extinction events during the last 500 timesteps. When we found
@@
 disconnected species did not affect our results (Fig. S1). The food-web
-generation and simulations were done using the `Julia` package
+generation and simulations were done in Julia by developing an extension of the package
 `EcologicalNetworkDynamics.jl`[@lajaaiti_ecologicalnetworksdynamicsjl_2024].
@@
 literature. We measured total biomass, species richness, connectance, average
-trophic level weighted by biomass, average omnivory and average interaction
+trophic level weighted by biomass, and average interaction
 strength. Food-web properties were measured at each of the 500 timesteps and
@@
 $1/\hat{B}_i\sum_{i}\mathrm{TL}_i$, $\mathrm{TL}_i$ being the trophic level and
-$\hat{B}_i$ the average biomass of the species $i$. The degree of omnivory of a
-consumer was computed  such as the sum of squares of its resource trophic levels
-weighted by the relative preference of the consumer for each resource: $\sum_i
-(\mathrm{TL}_i - \hat{\mathrm{TL}})^2 \omega_i/ \sum \omega_i$
-[@christensen_ecopath_1992]. Interaction strength was computed was quantified as
+$\hat{B}_i$ the average biomass of the species $i$. Interaction strength was computed was quantified as
 the biomass fluxes going from a resource to a consumer, such as: $I = x_i y_i
@@
 We assessed the effects of food-web structure, environmental stochasticity and
-response diversity on temporal stability of biomass. We measured temporal stability of biomass
-as the inverse of the coefficient of variation. We further partitioned stability
-into population stability ($S_{pop}$) and asynchrony ($\phi$) such as:
+response diversity on temporal stability of biomass. We measured temporal
+stability of biomass as the inverse of the coefficient of variation. We further
+partitioned stability into population stability ($S_{pop}$) and asynchrony
+($\phi$) such as:
 
@@
 with $S_{com} = \mu_{tot} / \sigma_{tot}$, $S_{pop} = \mu_{tot} / \sum_i \sigma_i$,
-$\phi = \sum_i \sigma_i / \sigma_{tot}$.
-
-$\mu_{tot}$ and $\sigma_{tot}$ being respectively average total biomass and standard
-deviation of total biomass.
+$\phi = \sum_i \sigma_i / \sigma_{tot}$; $\mu_{tot}$ and $\sigma_{tot}$ being
+respectively average total biomass and standard deviation of total biomass.
 
@@
 structure on stability, we partitioned asynchrony into portfolio effects and
-compensatory dynamics stemming from species interaction[@zhao_biodiversity_2022]
+compensatory dynamics stemming from species interactions[@zhao_biodiversity_2022]
 ($CPE_{int}$). The measurement of portfolio effects has been a topic of
@@
 species to environmental fluctuations, such as portfolio effects are dampened if
-species have correlated responses.
+species have correlated responses to environmental fluctuations.
 
@@
 variables because higher Predator-Prey Mass Ratio and predator interference were
-also expected to increase population stability [@brose_allometric_2006].
+also expected to increase population stability[@brose_allometric_2006].
 Finally, we tested the effects of environmental stochasticity and response
@@
 correlated (Fig. S5). The structural equation model using the R package
-`PiecewiseSEM`[@lefcheck_piecewisesem_2016]. We then bootstrapped (N = 100) the
-SEM to obtain confidence intervals on the estimated effects and computed the sum
+`PiecewiseSEM`[@lefcheck_piecewisesem_2016]. We computed the sum
 of the direct and indirect effects using `semEff` R
@@
 deviation of the response and predictor variable. Finally, we reported only the
-direct standardised coefficients that had an absolute value above $0.05$,
-because almost all linked were statistically significant given the high numbers
+direct standardised coefficients with an absolute value equal or above $0.05$,
+because almost all effects were statistically significant given the high numbers
 of simulations.
@@
 values of the other variables were set to the values indicated in the Fig.
-\@ref(fig:pred). The VIF were inferior to 3, indicating low multicollinearity
-(Table S5), we checked the distribution of the residuals (Fig. S6) using
-`DHARMa` R package. The model was implemented using the R package
-`glmmTMB`[@brooks_glmmtmb_2017].
+\@ref(fig:pred). The coefficients of the models are displayed in Fig. S3. The
+VIF were inferior to 3, indicating low multicollinearity (Table S5), we checked
+the distribution of the residuals (Fig. S6) using `DHARMa` R package. The model
+was implemented using the R package `glmmTMB`[@brooks_glmmtmb_2017].
+
+# Code availability
+
+The code used to run the simulations, analyse the data and write the manuscript
+is available on Github (https://github.com/alaindanet/xStressorsStabBEFW) and
+archived on Zenodo (https://zenodo.org/records/13454946).
 
